### 2014-01-14 etc/abstract.tex
initial

Explain why Random

% Technical papers must be prepared in ACM conference format and must not exceed 10 pages
% (including figures and appendices but NOT including references). That is, any pages after
% the tenth must contain only references. All submissions must be in English. Submit your
% paper via the paper submission website. Submissions that do not adhere to these
% guidelines or that violate formatting will be declined without review.

### 2014-01-14 src/paper.Rnw
initial

\newcommand*\per{\scalebox{.5}{\%}}
\newcommand\Mua{Mutation analysis~}
\newcommand\mua{mutation analysis~}
\begin{comment}
<<setup, include=FALSE, cache=FALSE, message=FALSE, echo=FALSE>>=
#options(warn=-1)
options(digits=3)
opts_chunk$set(fig.path='figure/twocolumn-', fig.align='center', fig.show='hold', echo=FALSE)
render_listings()
logit<-function(x) log(x/(1-x))
@
<<chunk-hook, echo=2>>=
<<setup>>
@
\end{comment}

<<a,message=F, echo=F>>=
require(xtable)
require(data.table)
@

% 10 pages for the main text + 1 for references.
\section{Introduction}
% 1. Describe the problem
% 2. State your contributions

Research in software testing often involves comparison between different testing techniques.
\Mua originally proposed by Lipton \cite{lipton1971fault} involves systematic transformation of program through introduction of first order syntactical changes.
The ability of test suites to distinguish the variants -- mutation score -- thus produced is taken as the effectiveness of the test suite\cite{ammann2008introduction}, and is used as an indicator for the effectiveness of the test suite against real faults\cite{andrews2005mutation}.

\Mua relies on two main assumptions: competant programmer hypothesis, and coupling effect\cite{budd1979mutation}.
Competant programmer hypothesis suggests that the version of program produced by a competant programmar is close to the final version,
while coupling effect claims that a test suite capable of catching first order bugs will also detect higher order bugs that contain these first order bugs.

For \mua to be used as a successful tool for comparison of testing techniques, the mutants produced by \mua should be similar in charecteristics to the real faults found in software.
This was investigated by Andrews et al.\cite{andrews2005mutation}, where it was found in one of the programs under consideration `space.c' for which real faults were available, the ease of detecting mutants was very close to the ease of detecting real faults.
However, for the other programs under consideration from siemens suite, the faults seeded by hand were much more harder to detect than mutants.
From this, Andrews et al. concluded that mutants produced were similar in characteristic to the real faults in terms of ease of detection.
However, this has come under attack for various reasons.
For example, the analysis depended on a single program which may not be a good representative of the other programs.
Further, Namin et al.\cite{namin2011theuse} found that different factors such as different programming languages, test suite size, and mutation operators chosen has an impact on whether the mutants produced are similar to real faults in terms of ease of detection.

This has led us to investigate real faults in software in a larger scale, especially paying attention to programming langauges of four different kinds: C, Java, Python and Haskell.
We have used the revision control histories of open source projects as obtained from Github\cite{github}. From these, we have identified changes that correspond to bugfixes using machine learning techniques. We have also identified the changes that are simple.

This research makes the following contributions.

\begin{enumerate}
\item contrib
\end{enumerate}

\section{Related Work}
Related work.
\section{Methodology}
Our methodology

\section{Analysis}

Analysis

\section{Results}

Results

### 2014-01-14 src/paper.Rnw
update

@@
 require(data.table)
+load('data/mu.rda')
 @
@@
 
-Analysis
+<<prepare,echo=F>>=
+attach(m)
+sdl_f <- mut.avg~mut.avg.sdl + 0
+rnd_f <- mut.avg~mut.avg.rnd + 0
+
+sdl_all <- lm(sdl_f)
+rnd_all <- lm(rnd_f)
+
+sdl_s <- summary(sdl_all)
+rnd_s <- summary(rnd_all)
+
+avg.est <- sdl_s$coefficients['mut.avg.sdl','Estimate']
+rnd.est <- rnd_s$coefficients['mut.avg.rnd','Estimate']
+@
+
+\begin{figure*}[t]
+<<plots, fig.width=5, fig.height=5, out.width='.45\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+plot(sdl_f, main='SDL ~ ALL',pch='*')
+abline(sdl_all, col='red')
+plot(rnd_f, main='RND ~ ALL',pch='*')
+abline(rnd_all, col='blue')
+abline(sdl_all, col='red', lty=2)
+@
+\caption{Plots}
+\label{fig:caddrm}
+\end{figure*}
+
+\subsection{Correlation Analysis}
+
+$ \mu_{all} = 0 + \beta_0 \times \mu_{sample}  $
+
+The interesting part is (1) the $\beta_0$ coeff which tells how much we must multiply the  sampled/selected score to get original score, and $R^2$ which tells us how close the score   is.
+
+\subsubsection{mut.avg.sdl and mut.avg}
+
+$ \mu_{all} = 0 + \Sexpr{avg.est} \times \mu_{sdl}  $
+
+\subsubsection{mut.avg.rnd and mut.avg}
+
+$ \mu_{all} = 0 + \Sexpr{rnd.est} \times \mu_{rnd}  $
 
@@
 
-Results
+We see from the data that random sampling has a higher $R^2$, and also approximates the all  mutations score better.
+However, caveat emptor. There is a difference between the number of mutators for SDL and RAND. If our approximation was right, we should have gotten nearly same number of mutators. However
+The number of mutators in RND is \Sexpr{sum(m$pit.mutation.total.rnd) / sum(m$pit.mutation.total.sdl)} times SDL.

### 2014-01-14 src/paper.Rnw
update

@@
 
-Research in software testing often involves comparison between different testing techniques.
-\Mua originally proposed by Lipton \cite{lipton1971fault} involves systematic transformation of program through introduction of first order syntactical changes.
-The ability of test suites to distinguish the variants -- mutation score -- thus produced is taken as the effectiveness of the test suite\cite{ammann2008introduction}, and is used as an indicator for the effectiveness of the test suite against real faults\cite{andrews2005mutation}.
+Mutation analysis originally proposed by Lipton\cite{lipton1971fault} involves systematic transformation of program through introduction of first order syntactical changes\cite{ammann2008introduction}.
+Researchers have shown that the mutations thus introduced behave similarly to the real faults\cite{andrews2005mutation}, and hence can be used as a stand-in for real faults when determining the efficacy of a test suite against faults.
 
-\Mua relies on two main assumptions: competant programmer hypothesis, and coupling effect\cite{budd1979mutation}.
-Competant programmer hypothesis suggests that the version of program produced by a competant programmar is close to the final version,
-while coupling effect claims that a test suite capable of catching first order bugs will also detect higher order bugs that contain these first order bugs.
+While mutation analysis provides a useful metric, its use has been held back due to its high computational requirements\cite{jia2011analysis}.
+This has led researchers to search for ways of reducing the resource requirements of the analysis.
+The methods in this direction can be classified into ``Do faster'', ``Do fewer'', and ``Do smarter''\cite{offutt2001mutation}.
+The ``Do fewer'' approach has come in for special study, and various researchers have investigated different ways to reduce the number of mutants thus produced.
 
-For \mua to be used as a successful tool for comparison of testing techniques, the mutants produced by \mua should be similar in charecteristics to the real faults found in software.
-This was investigated by Andrews et al.\cite{andrews2005mutation}, where it was found in one of the programs under consideration `space.c' for which real faults were available, the ease of detecting mutants was very close to the ease of detecting real faults.
-However, for the other programs under consideration from siemens suite, the faults seeded by hand were much more harder to detect than mutants.
-From this, Andrews et al. concluded that mutants produced were similar in characteristic to the real faults in terms of ease of detection.
-However, this has come under attack for various reasons.
-For example, the analysis depended on a single program which may not be a good representative of the other programs.
-Further, Namin et al.\cite{namin2011theuse} found that different factors such as different programming languages, test suite size, and mutation operators chosen has an impact on whether the mutants produced are similar to real faults in terms of ease of detection.
+One of the main approaches is selective mutation, proposed by Mathur\cite{mathur1991performance}, and further refined by Offutt et al.\cite{offutt1993anexperimental}.
+This approach relies on the fact that some of the mutagens generate a large number of variants, and hence produce highly redundant test cases.
+Previous research suggested that elimination of mutagens with high fertility results in the reduction of total number of mutations produced, and hence reduces the computational requirements.
 
-This has led us to investigate real faults in software in a larger scale, especially paying attention to programming langauges of four different kinds: C, Java, Python and Haskell.
-We have used the revision control histories of open source projects as obtained from Github\cite{github}.
-From these, we have identified changes that correspond to bugfixes using machine learning techniques.
-We have also identified the changes that are simple.
+% TODO check the survey again on selective mutation.
 
-This research makes the following contributions.
+It was recently questioned whether this approach indeed resulted in a tangible improvement over random selection of mutants\cite{zhang2010operator}, which did not find operator based selection to be better than random selection.
+It was later found that using operator based selection and random sampling was better than using each strategy separately\cite{zhang2013ase}.
 
-\begin{enumerate}
-\item contrib
-\end{enumerate}
+Another research, initially by Unch\cite{untch2009onreduced} and recently by Deng et al.\cite{deng2013empirical} suggests using software deletion operator since it produces the least number of mutants (smallest neighborhood).
+The researchers were able to obtain a close approximation of original mutant score with significant savings with this approach.
+
+However, our previous research\cite{icse} suggests that mutation coverage is closely predicted by statement coverage, this suggests that any criteria that forces accounting of the impact of each statement should provide a close approximation to the full mutation score.
+Hence, our research suggests that SDL works because it forces accounting of each line, and a random sampling criteria that provides the same criteria should result in similar results.
+
+In our analysis, we find that a random sampling approach that randomly chose a single mutant per line was found to have a better correlation with the full mutation score than that obtained by SDL.
+Further it was also found that the mutation score produced by random sampling was closer to the full mutation score than that produced by SDL.
 

### 2014-01-15 etc/abstract.tex
update

@@
-Explain why Random
+% 1.Statetheproblem
+Mutation analysis is often used to analyze the quality of test suites.
+However, it has exorbitant computational requirements which makes it hard to use in practice.
+Operator selection, especially using only statement deletion operator has been shown to provide a close approximation to the full mutation score.
+%2.Saywhyit’saninterestingproblem
+However, our previous research suggests that any technique that forces accounting for the effect of each line, should achieve similar results.
+
+%3.Saywhatyoursolutionachieves
+Our research compares the mutation scores achieved using the full operator set, to that produced by a a set of operators that approximates statement deletion, and also to that produced by line based random sampling sampling.
+The analysis of the resulting model shows that the line based random sampling was slightly better at approximating the original mutation score.
+However, this difference was not statistically significant.
+
+%4.Saywhatfollowsfromyoursolution
+
+This result shows that operator selection based on reduced neighborhood strategy does not have an impact on the closeness of approximation.
 

### 2014-01-15 src/paper.Rnw
update

@@
 \section{Related Work}
-Related work.
+Mathur\cite{mathur1991performance, wong1993mutation, wong1995reducing} first mentioned the idea of constrained mutation in a one-pager.
+This was taken up by Offut et al.\cite{offutt1993experimental}.
+(Offutt states in his 1993 paper\cite{offutt1993experimental} that Mathur has in 1991\cite{mathur1991performance} suggested the constrined/selective mutation.
+However, that paper does not propose it at all.
+It says we are experimenting with an idea, and that is it.
+It is in 1995\cite{wong1995reducing} that the idea is actually proposed, notably after Offutt has written about its effectiveness.
+$\ddot\smile$ - time travel?).
+The idea is that normal mutation has quadratic complexity on variable references while eliminatng the most fecund mutagens (SVR and ASR) achieves linear complexity on program size, while still approximating the full mutation score closely.
+They propose N-selective mutation which avoids N most fertile mutagens.
+Wong \cite{wong1995reducing} compares the effect of x\% mutation selection, and abs/ror constrained mutation.
+According to Wong, this is different from selective mutation in that only the most fecund operators are included rather than excluded.
+He finds that there is no evidence to suggest one over the other.
+Offutt\cite{offutt1993experimental} does not compare the effectivenss of selective mutation with x\% mutation.
+He also defines the concept of {\it operator strength} for an operator, which is defined as the total number of mutants that are killed by test data that is generated to kill only the mutants generated by that operator.
+He further posits that the mutagens with greatest strength may be the most useful ones.
+%(test data generated to eliminate variants of one operator may remove the mutants of other kinds too.)
+
 \section{Methodology}
-Our methodology
+We collected a random sample of Java programs from Github\cite{github} that utilized the Maven\cite{maven} system for building.
+Next, we selected those programs from this set that passed all the unit test cases within them.
+We ran mutation analysis on this set of projects using PIT\cite{pitest}, with the mutators selected set to {\it all}.
+Because of the limitations of using a bytecode mutation engine, we could not implement statement deletion directly.
+Instead, we made use of the following mutation operators, that closely approximated statement deletion operator -- remove void method calls, remove non void method calls, remove conditionals, remove member variable assignments, remove increments and decrements.
+Finally, we modified the mutation engine to only choose one random mutation per line out of the set of applicable mutants for that line.
+For the second phase, we looked at the ratio between the number of mutants produced by the set of operators corresponding to statement deletion, and that of the random line mutants, and used this as a probability to add the mutants for the random line set.
+This was done to ensure that the results from the random sampling and statement deletion could be compared.
 
@@
 
-avg.est <- sdl_s$coefficients['mut.avg.sdl','Estimate']
+sdl.est <- sdl_s$coefficients['mut.avg.sdl','Estimate']
 rnd.est <- rnd_s$coefficients['mut.avg.rnd','Estimate']
+
+sdl.r <- sdl_s$r.squared
+rnd.r <- rnd_s$r.squared
+
 @
@@
 
+\begin{figure*}[t]
+<<mutnum, fig.width=5, fig.height=5, out.width='.45\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+hist(log(10,m$pit.mutation.total.sdl), breaks=50, col=rgb(0,0,1,1/4))
+hist(log(10,m$pit.mutation.num.sdl), breaks=50, add=T, col=rgb(1,0,0,1/4))
+
+hist(log(10,m$pit.mutation.total.rnd), breaks=50, col=rgb(0,0,1,1/4))
+hist(log(10,m$pit.mutation.num.rnd), breaks=50, add=T, col=rgb(1,0,0,1/4))
+
+hist(log(10,m$pit.mutation.total), breaks=50, col=rgb(0,0,1,1/4))
+hist(log(10,m$pit.mutation.num), breaks=50, add=T, col=rgb(1,0,0,1/4))
+@
+\caption{Plots}
+\label{fig:caddrm}
+\end{figure*}
+
 \subsection{Correlation Analysis}
 
-$ \mu_{all} = 0 + \beta_0 \times \mu_{sample}  $
+$ \mu\{ M_{all}| M_{sample} \} = 0 + \beta_1 \times M{sample}  $
 
-The interesting part is (1) the $\beta_0$ coeff which tells how much we must multiply the  sampled/selected score to get original score, and $R^2$ which tells us how close the score   is.
+The interesting part is (1) the $\beta_1$ coefficient which tells how much we must multiply the  sampled/selected score to get original score, and $R^2$ which tells us how close the score   is.
 
@@
 
-$ \mu_{all} = 0 + \Sexpr{avg.est} \times \mu_{sdl}  $
+$ \mu_\{M_{all} | M_{sdl}\} = 0 + \Sexpr{sdl.est} \times M_{sdl} \text{ with } R^2 = \Sexpr{sdl.r} $
 
@@
 
-$ \mu_{all} = 0 + \Sexpr{rnd.est} \times \mu_{rnd}  $
+$ \mu_\{M_{all} | M_{rnd}\} = 0 + \Sexpr{rnd.est} \times M_{rnd}  \text{ with } R^2 = \Sexpr{rnd.r} $
+
+\subsection{Regression Analysis}
+The next question we will tackle is if there exist a difference at all between SDL mutagen and the random sampling.
+We can perform two statistical tests to answer this question.
+For the first, we run a simple paired t-test.
+
+<<>>=
+s <- t.test(mut.avg.rnd, mut.avg.sdl, paired=T)
+@
+
+The paired t-test failed to sufficient difference between the two distributions with a two-sided p-value of \Sexpr{s$p.value}.
+That is, we do not have sufficient evidence to conclude that the two distributions are different.
+
+The second approch is convoluted (I am a little unclear here.). We try to predict the original mutation score using the mutation score from both sdl and random sampling.
+Our full model is
+
+$ \mu_\{M_{all} | M_{sdl}, M_{rnd}\} = 0 + \beta_1 {sdl} + \beta_2 M_{rnd} + \beta_3 M_{sdl} M_{rnd}  $
+<<results='asis'>>=
+s <- subset(m, select=c(mut.avg,mut.avg.sdl))
+s$type <- 'sdl'
+colnames(s) <- c('mut', 'sample', 'type')
+r <- subset(m, select=c(mut.avg,mut.avg.rnd))
+r$type <- 'rnd'
+colnames(r) <- c('mut', 'sample', 'type')
+all <- rbind(s, r)
+detach(m)
+fm <- with(all, lm(mut ~ sample + type + sample:type))
+sm <- anova(fm)
+xtable(sm)
+@
+
+We see that both type and sample:type are non-significant for predicting the final model, and sequentially removing them does not change the effectiveness.
+Hence, the techniques random sampling and statement deletion operator do not have any difference.
 
@@
 However, caveat emptor. There is a difference between the number of mutators for SDL and RAND. If our approximation was right, we should have gotten nearly same number of mutators. However
-The number of mutators in RND is \Sexpr{sum(m$pit.mutation.total.rnd) / sum(m$pit.mutation.total.sdl)} times SDL.
+The number of mutators in RND is
+ \Sexpr{sum(m$pit.mutation.total.rnd) / sum(m$pit.mutation.total.sdl)} times SDL.
+
+The total mutants for all is \Sexpr{sum(m$pit.mutation.total)}, for rnd is \Sexpr{sum(m$pit.mutation.total.rnd)} and for sdl is \Sexpr{sum(m$pit.mutation.total.sdl)}
+
+TODO: We should check if the distribution significantly different too.
+TODO: Use sampling
+TODO: Check on randoop samples too
+TODO: Implement bomb (athrow) and see its mutation score, and see how close it comes.

### 2014-01-15 src/paper.Rnw
update

@@
 
+Offutt\cite{offutt1996anexperimental} following the previous paper\cite{offutt1993experimental} compares the effectiveness of selecting different operators.
+He divides the total operators into operand, operation, and statement categories, with es-selective avoiding operands, rs-selective avoiding operations, and re-selective avoiding statements, and e-selective only operations.
+He finds that using only operation based mutation operators (numbering 5) is sufficient for close approximation of full mutation score.
+He suggests that the reason they are effective is that most statements contain operators.
+He further posits that another reason is the amount of semantic change accomplished by an operator, and perhaps the most interesting ones are those that produce the smallest semantic difference.
+% Replacement of Operand , Statement modification, Expression Modification: modify operators, ES-selective : not using operand, RS-Selective: not using expression, RE-Selective: not uinsg statement, E-selective : only expression..
+
+Unch\cite{untch2009onreduced} suggested using a single mutagen statement deletion.
+He compares the statement deletion with other selective mutagen sets, and finds statement deletion operator to provide the best prediction of original mutation score ($R^2 = 0.97$)
+
 \section{Methodology}
@@
 <<mutnum, fig.width=5, fig.height=5, out.width='.45\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-hist(log(10,m$pit.mutation.total.sdl), breaks=50, col=rgb(0,0,1,1/4))
+hist(log(10,m$pit.mutation.total.sdl), breaks=50, col=rgb(0,0,1,1/4), main='histogram of log(sdl) mutation score')
 hist(log(10,m$pit.mutation.num.sdl), breaks=50, add=T, col=rgb(1,0,0,1/4))
 
-hist(log(10,m$pit.mutation.total.rnd), breaks=50, col=rgb(0,0,1,1/4))
+hist(log(10,m$pit.mutation.total.rnd), breaks=50, col=rgb(0,0,1,1/4), main='histogram of log(rnd) mutation score')
 hist(log(10,m$pit.mutation.num.rnd), breaks=50, add=T, col=rgb(1,0,0,1/4))
 
-hist(log(10,m$pit.mutation.total), breaks=50, col=rgb(0,0,1,1/4))
+hist(log(10,m$pit.mutation.total), breaks=50, col=rgb(0,0,1,1/4), main='histogram of log(total) mutation score')
 hist(log(10,m$pit.mutation.num), breaks=50, add=T, col=rgb(1,0,0,1/4))

### 2014-01-15 src/paper.Rnw
update

@@
 
-However, our previous research\cite{icse} suggests that mutation coverage is closely predicted by statement coverage, this suggests that any criteria that forces accounting of the impact of each statement should provide a close approximation to the full mutation score.
+However, our previous research suggests that mutation coverage is closely predicted by statement coverage, this suggests that any criteria that forces accounting of the impact of each statement should provide a close approximation to the full mutation score.
 Hence, our research suggests that SDL works because it forces accounting of each line, and a random sampling criteria that provides the same criteria should result in similar results.
@@
 %(test data generated to eliminate variants of one operator may remove the mutants of other kinds too.)
+This is taken up later by Mresa\cite{mresa1999efficiency} et al.
+who used the cost of detection of mutants as a means of selection, and uses it to define another set of operators (san, aor, sdl, ror, uoi).
+They also find that if very high mutation score close to 100\% is required, x\% selective mutation is better than operator selection, and conversely for less stringent scores, operator selection would be better if const of mutant is considered.
+
+Barbosa et. al.\cite{barbosa2001toward} provides a set of guidelines for selecting mutagens.
+
+Namin et al.\cite{namin2006finding,siami2008sufficient} treats the operator selection as a variable reduction problem, and applying statistical approaches, finds 28 operators from a total of 108 operators that are sufficient for an adequate test suite.
 

### 2014-01-15 src/paper.Rnw
update

@@
 He compares the statement deletion with other selective mutagen sets, and finds statement deletion operator to provide the best prediction of original mutation score ($R^2 = 0.97$)
+This was carried forward by Deng et al\cite{deng2013empirical}, (according to whom, random sampling was weak when it was made low enough for appreciable mutant savings).
+They realize a mean mutation score of 92\% for adequate test suites with SDL alone, and generating a saving of 81\% in the number of mutants, and 41\% fewer equivalent mutants.
+
+Zhang et al.\cite{zhang2010operator}, compares operator based mutant selection to random mutant selection.
+They compare three diffrent operator based selection techniques from Offutt et al., Barbosa et al., and Namin et al.
+against random mutant selection, with equal mutant probability, and equal mutagen probaiblity.
+They find that none of these selection techniques are superior to random selection, with same number of mutants.
+They also find that equal mutation sampling is more effective for larger subjects compared to equal mutagen sampling and the reverse is true for smaller subjects.
+A second paper by Zhang et al.\cite{zhang2013ase} investigates 8 sampling strategies on top of operator based mutant selection.
+They find that sampling strategies based on programming elements (method based) performed best.
+% Baseline : x\% from selected set
+% MOP : x\% from each mutagen
+% for these, it is sampled from operator based selected set.
+% PLEm : x\% from inside the same program element.
+% PLE + MOP: sample x\% from same mutagen from same element.
 
@@
 
-$ \mu_\{M_{all} | M_{sdl}\} = 0 + \Sexpr{sdl.est} \times M_{sdl} \text{ with } R^2 = \Sexpr{sdl.r} $
+<<>>=
+c <- cor(subset(m, select=c(mut.avg.sdl, mut.avg)) , method="kendall", use="pairwise")['mut.avg.sdl', 'mut.avg']
+d <- cor(subset(m, select=c(mut.avg.rnd, mut.avg)) , method="kendall", use="pairwise")['mut.avg.rnd', 'mut.avg']
+@
+
+$ \mu_\{M_{all} | M_{sdl}\} = \Sexpr{sdl.est} \times M_{sdl} \text{ : } R^2 = \Sexpr{sdl.r} \text{,} \tau_{\beta} = \Sexpr{c}$
 
@@
 
-$ \mu_\{M_{all} | M_{rnd}\} = 0 + \Sexpr{rnd.est} \times M_{rnd}  \text{ with } R^2 = \Sexpr{rnd.r} $
+$ \mu_\{M_{all} | M_{rnd}\} = \Sexpr{rnd.est} \times M_{rnd} \text{ : } R^2 = \Sexpr{rnd.r} \text{,} \tau_{\beta} = \Sexpr{d}$
 
@@
 
-TODO: We should check if the distribution significantly different too.
-TODO: Use sampling
-TODO: Check on randoop samples too
-TODO: Implement bomb (athrow) and see its mutation score, and see how close it comes.
+\begin{enumerate}
+\item [TODO] We should check if the distribution significantly different too.
+\item [TODO] Use sampling
+\item [TODO] Check on randoop samples too
+\item [TODO] Implement bomb (athrow) and see its mutation score, and see how close it comes.
+\item [TODO] Compare random selection with class, method, and mutagen sampling.
+\item [TODO] Report time for each, as cost.
+\item [TODO] Find the mutant count to LOC multiplier, and use it to get the probability of choosing for each project.
+\end{enumerate}

### 2014-02-01 src/paper.Rnw
udate names

@@
 attach(m)
-sdl_f <- mut.avg~mut.avg.sdl + 0
-rnd_f <- mut.avg~mut.avg.rnd + 0
+sdl_f <- mut.avg~sdl.mut.avg + 0
+rnd_f <- mut.avg~lrnd.mut.avg + 0
 
@@
 
-sdl.est <- sdl_s$coefficients['mut.avg.sdl','Estimate']
-rnd.est <- rnd_s$coefficients['mut.avg.rnd','Estimate']
+sdl.est <- sdl_s$coefficients['sdl.mut.avg','Estimate']
+rnd.est <- rnd_s$coefficients['lrnd.mut.avg','Estimate']
 
@@
 <<mutnum, fig.width=5, fig.height=5, out.width='.45\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-hist(log(10,m$pit.mutation.total.sdl), breaks=50, col=rgb(0,0,1,1/4), main='histogram of log(sdl) mutation score')
-hist(log(10,m$pit.mutation.num.sdl), breaks=50, add=T, col=rgb(1,0,0,1/4))
+hist(log(10,m$sdl.pit.mutation.total), breaks=50, col=rgb(0,0,1,1/4), main='histogram of log(sdl) mutation score')
+hist(log(10,m$sdl.pit.mutation.num), breaks=50, add=T, col=rgb(1,0,0,1/4))
 
-hist(log(10,m$pit.mutation.total.rnd), breaks=50, col=rgb(0,0,1,1/4), main='histogram of log(rnd) mutation score')
-hist(log(10,m$pit.mutation.num.rnd), breaks=50, add=T, col=rgb(1,0,0,1/4))
+hist(log(10,m$lrnd.pit.mutation.total), breaks=50, col=rgb(0,0,1,1/4), main='histogram of log(rnd) mutation score')
+hist(log(10,m$lrnd.pit.mutation.num), breaks=50, add=T, col=rgb(1,0,0,1/4))
 
@@
 
-\subsubsection{mut.avg.sdl and mut.avg}
+\subsubsection{sdl.mut.avg and mut.avg}
 
 <<>>=
-c <- cor(subset(m, select=c(mut.avg.sdl, mut.avg)) , method="kendall", use="pairwise")['mut.avg.sdl', 'mut.avg']
-d <- cor(subset(m, select=c(mut.avg.rnd, mut.avg)) , method="kendall", use="pairwise")['mut.avg.rnd', 'mut.avg']
+c <- cor(subset(m, select=c(sdl.mut.avg, mut.avg)) , method="kendall", use="pairwise")['sdl.mut.avg', 'mut.avg']
+d <- cor(subset(m, select=c(lrnd.mut.avg, mut.avg)) , method="kendall", use="pairwise")['lrnd.mut.avg', 'mut.avg']
 @
@@
 
-\subsubsection{mut.avg.rnd and mut.avg}
+\subsubsection{lrnd.mut.avg and mut.avg}
 
@@
 <<>>=
-s <- t.test(mut.avg.rnd, mut.avg.sdl, paired=T)
+s <- t.test(lrnd.mut.avg, sdl.mut.avg, paired=T)
 @
@@
 $ \mu_\{M_{all} | M_{sdl}, M_{rnd}\} = 0 + \beta_1 {sdl} + \beta_2 M_{rnd} + \beta_3 M_{sdl} M_{rnd}  $
+\begin{small}
 <<results='asis'>>=
-s <- subset(m, select=c(mut.avg,mut.avg.sdl))
+s <- subset(m, select=c(mut.avg,sdl.mut.avg))
 s$type <- 'sdl'
 colnames(s) <- c('mut', 'sample', 'type')
-r <- subset(m, select=c(mut.avg,mut.avg.rnd))
+r <- subset(m, select=c(mut.avg,lrnd.mut.avg))
 r$type <- 'rnd'
@@
 sm <- anova(fm)
-xtable(sm)
+print(xtable(sm,caption="My caption"), size="\\small")
 @
+\end{small}
 
@@
 The number of mutators in RND is
- \Sexpr{sum(m$pit.mutation.total.rnd) / sum(m$pit.mutation.total.sdl)} times SDL.
+ \Sexpr{sum(m$lrnd.pit.mutation.total) / sum(m$sdl.pit.mutation.total)} times SDL.
 
-The total mutants for all is \Sexpr{sum(m$pit.mutation.total)}, for rnd is \Sexpr{sum(m$pit.mutation.total.rnd)} and for sdl is \Sexpr{sum(m$pit.mutation.total.sdl)}
+The total mutants for all is \Sexpr{sum(m$pit.mutation.total)}, for rnd is \Sexpr{sum(m$lrnd.pit.mutation.total)} and for sdl is \Sexpr{sum(m$sdl.pit.mutation.total)}
 

### 2014-02-02 src/paper.Rnw
update

@@
 @
-\caption{Plots}
+\caption{Plots of total mutation number, and those killed.}
 \label{fig:caddrm}
@@
 all <- rbind(s, r)
-detach(m)
 fm <- with(all, lm(mut ~ sample + type + sample:type))
@@
 Hence, the techniques random sampling and statement deletion operator do not have any difference.
+
+\begin{figure*}[t]
+<<tplots, fig.width=5, fig.height=5, out.width='.45\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+t_f <- sdl.time~lrnd.time
+plot(t_f, main='SDL ~ RND',pch='*')
+abline(lm(t_f), col='red')
+detach(m)
+@
+\caption{Time}
+\label{fig:caddrm}
+\end{figure*}
 

### 2014-02-18 etc/abstract.tex
shift to do-fewer

--- 2014-01-14 etc/abstract.tex
@@
-Explain why Random
+% 1.Statetheproblem
+Mutation analysis is a metric for measuring the quality of test suites.
+However, its exorbitant computational requirements makes it hard to use in practice.
+Choosing a smaller subset of mutations to run is a simple approach that can alleviate this problem.
+
+%2.Saywhyit’saninterestingproblem
+However, how best to choose among multiple selection criterias is an open problem, especially for real-world programs and test-suites.
+
+%3.Saywhatyoursolutionachieves
+Our research compare a number of selection criteria along different dimensions including prediction of original mutation score, mutant reduction ratio, and time for completion.
+
+%4.Saywhatfollowsfromyoursolution
 

### 2014-02-26 src/paper.Rnw
update

@@
 % PLE + MOP: sample x\% from same mutagen from same element.
+
+% On Mutation and Dataflow : W.E Eong
+Wong et al~\cite{wong1994on} suggests random sampling of mutants from the complete population.
+
+Wong and Mathur suggests constrained mutation~\cite{} which chooses specific mutation operators only.
+
+% Empirical Evaluation of the Statement Deletion Mutation Operator : Offutt
+Deng et al~\cite{deng2013empirical} considers the effect of using a single mutation operator -- the statement deletion operator. They define deletion for different language elements,
 

### 2014-02-27 src/paper.Rnw
remove R for now

@@
 
-<<a,message=F, echo=F>>=
-require(xtable)
-require(data.table)
-load('data/mu.rda')
-@
+% <<a,message=F, echo=F>>=
+% require(xtable)
+% require(data.table)
+% load('data/mu.rda')
+% @
 
@@
 
-<<prepare,echo=F>>=
-attach(m)
-sdl_f <- mut.avg~sdl.mut.avg + 0
-rnd_f <- mut.avg~lrnd.mut.avg + 0
-
-sdl_all <- lm(sdl_f)
-rnd_all <- lm(rnd_f)
-
-sdl_s <- summary(sdl_all)
-rnd_s <- summary(rnd_all)
-
-sdl.est <- sdl_s$coefficients['sdl.mut.avg','Estimate']
-rnd.est <- rnd_s$coefficients['lrnd.mut.avg','Estimate']
-
-sdl.r <- sdl_s$r.squared
-rnd.r <- rnd_s$r.squared
-
-@
+% <<prepare,echo=F>>=
+% attach(m)
+% sdl_f <- mut.avg~sdl.mut.avg + 0
+% rnd_f <- mut.avg~lrnd.mut.avg + 0
+% 
+% sdl_all <- lm(sdl_f)
+% rnd_all <- lm(rnd_f)
+% 
+% sdl_s <- summary(sdl_all)
+% rnd_s <- summary(rnd_all)
+% 
+% sdl.est <- sdl_s$coefficients['sdl.mut.avg','Estimate']
+% rnd.est <- rnd_s$coefficients['lrnd.mut.avg','Estimate']
+% 
+% sdl.r <- sdl_s$r.squared
+% rnd.r <- rnd_s$r.squared
+% 
+% @
 
 \begin{figure*}[t]
-<<plots, fig.width=5, fig.height=5, out.width='.45\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-plot(sdl_f, main='SDL ~ ALL',pch='*')
-abline(sdl_all, col='red')
-plot(rnd_f, main='RND ~ ALL',pch='*')
-abline(rnd_all, col='blue')
-abline(sdl_all, col='red', lty=2)
-@
+% <<plots, fig.width=5, fig.height=5, out.width='.45\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+% plot(sdl_f, main='SDL ~ ALL',pch='*')
+% abline(sdl_all, col='red')
+% plot(rnd_f, main='RND ~ ALL',pch='*')
+% abline(rnd_all, col='blue')
+% abline(sdl_all, col='red', lty=2)
+% @
 \caption{Plots}
@@
 \begin{figure*}[t]
-<<mutnum, fig.width=5, fig.height=5, out.width='.45\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-hist(log(10,m$sdl.pit.mutation.total), breaks=50, col=rgb(0,0,1,1/4), main='histogram of log(sdl) mutation score')
-hist(log(10,m$sdl.pit.mutation.num), breaks=50, add=T, col=rgb(1,0,0,1/4))
-
-hist(log(10,m$lrnd.pit.mutation.total), breaks=50, col=rgb(0,0,1,1/4), main='histogram of log(rnd) mutation score')
-hist(log(10,m$lrnd.pit.mutation.num), breaks=50, add=T, col=rgb(1,0,0,1/4))
-
-hist(log(10,m$pit.mutation.total), breaks=50, col=rgb(0,0,1,1/4), main='histogram of log(total) mutation score')
-hist(log(10,m$pit.mutation.num), breaks=50, add=T, col=rgb(1,0,0,1/4))
-@
+% <<mutnum, fig.width=5, fig.height=5, out.width='.45\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+% hist(log(10,m$sdl.pit.mutation.total), breaks=50, col=rgb(0,0,1,1/4), main='histogram of log(sdl) mutation score')
+% hist(log(10,m$sdl.pit.mutation.num), breaks=50, add=T, col=rgb(1,0,0,1/4))
+% 
+% hist(log(10,m$lrnd.pit.mutation.total), breaks=50, col=rgb(0,0,1,1/4), main='histogram of log(rnd) mutation score')
+% hist(log(10,m$lrnd.pit.mutation.num), breaks=50, add=T, col=rgb(1,0,0,1/4))
+% 
+% hist(log(10,m$pit.mutation.total), breaks=50, col=rgb(0,0,1,1/4), main='histogram of log(total) mutation score')
+% hist(log(10,m$pit.mutation.num), breaks=50, add=T, col=rgb(1,0,0,1/4))
+% @
 \caption{Plots of total mutation number, and those killed.}
@@
 
-<<>>=
-c <- cor(subset(m, select=c(sdl.mut.avg, mut.avg)) , method="kendall", use="pairwise")['sdl.mut.avg', 'mut.avg']
-d <- cor(subset(m, select=c(lrnd.mut.avg, mut.avg)) , method="kendall", use="pairwise")['lrnd.mut.avg', 'mut.avg']
-@
+% <<>>=
+% c <- cor(subset(m, select=c(sdl.mut.avg, mut.avg)) , method="kendall", use="pairwise")['sdl.mut.avg', 'mut.avg']
+% d <- cor(subset(m, select=c(lrnd.mut.avg, mut.avg)) , method="kendall", use="pairwise")['lrnd.mut.avg', 'mut.avg']
+% @
 
-$ \mu_\{M_{all} | M_{sdl}\} = \Sexpr{sdl.est} \times M_{sdl} \text{ : } R^2 = \Sexpr{sdl.r} \text{,} \tau_{\beta} = \Sexpr{c}$
+$ \mu_\{M_{all} | M_{sdl}\} = Sexpr{sdl.est} \times M_{sdl} \text{ : } R^2 = Sexpr{sdl.r} \text{,} \tau_{\beta} = Sexpr{c}$
 
@@
 
-$ \mu_\{M_{all} | M_{rnd}\} = \Sexpr{rnd.est} \times M_{rnd} \text{ : } R^2 = \Sexpr{rnd.r} \text{,} \tau_{\beta} = \Sexpr{d}$
+$ \mu_\{M_{all} | M_{rnd}\} = Sexpr{rnd.est} \times M_{rnd} \text{ : } R^2 = Sexpr{rnd.r} \text{,} \tau_{\beta} = Sexpr{d}$
 
@@
 
-The paired t-test failed to sufficient difference between the two distributions with a two-sided p-value of \Sexpr{s$p.value}.
+The paired t-test failed to sufficient difference between the two distributions with a two-sided p-value of Sexpr{s.p.value}.
 That is, we do not have sufficient evidence to conclude that the two distributions are different.
@@
 \begin{small}
-<<results='asis'>>=
-s <- subset(m, select=c(mut.avg,sdl.mut.avg))
-s$type <- 'sdl'
-colnames(s) <- c('mut', 'sample', 'type')
-r <- subset(m, select=c(mut.avg,lrnd.mut.avg))
-r$type <- 'rnd'
-colnames(r) <- c('mut', 'sample', 'type')
-all <- rbind(s, r)
-fm <- with(all, lm(mut ~ sample + type + sample:type))
-sm <- anova(fm)
-print(xtable(sm,caption="My caption"), size="\\small")
-@
+% <<results='asis'>>=
+% s <- subset(m, select=c(mut.avg,sdl.mut.avg))
+% s$type <- 'sdl'
+% colnames(s) <- c('mut', 'sample', 'type')
+% r <- subset(m, select=c(mut.avg,lrnd.mut.avg))
+% r$type <- 'rnd'
+% colnames(r) <- c('mut', 'sample', 'type')
+% all <- rbind(s, r)
+% fm <- with(all, lm(mut ~ sample + type + sample:type))
+% sm <- anova(fm)
+% print(xtable(sm,caption="My caption"), size="\\small")
+% @
 \end{small}
@@
 \begin{figure*}[t]
-<<tplots, fig.width=5, fig.height=5, out.width='.45\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-t_f <- sdl.time~lrnd.time
-plot(t_f, main='SDL ~ RND',pch='*')
-abline(lm(t_f), col='red')
-detach(m)
-@
+% <<tplots, fig.width=5, fig.height=5, out.width='.45\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+% t_f <- sdl.time~lrnd.time
+% plot(t_f, main='SDL ~ RND',pch='*')
+% abline(lm(t_f), col='red')
+% detach(m)
+% @
 \caption{Time}

### 2014-02-28 src/paper.Rnw
update

@@
 \begin{enumerate}
+\item [x] For op-selection to work, the distributions of mutations across different projects has to be similar enough. This can be checked by t-test.
 \item [TODO] We should check if the distribution significantly different too.
-\item [TODO] Use sampling
-\item [TODO] Check on randoop samples too
-\item [TODO] Implement bomb (athrow) and see its mutation score, and see how close it comes.
-\item [TODO] Compare random selection with class, method, and mutagen sampling.
+\item [DONE] Use sampling
+\item [DONE] Check on randoop samples too
+\item [NO] Implement bomb (athrow) and see its mutation score, and see how close it comes.
+\item [DONE] Compare random selection with class, method, and mutagen sampling.
 \item [TODO] Report time for each, as cost.
-\item [TODO] Find the mutant count to LOC multiplier, and use it to get the probability of choosing for each project.
+\item [DONTKNOWHOWTO] Find the mutant count to LOC multiplier, and use it to get the probability of choosing for each project.
 \end{enumerate}

### 2014-03-01 src/paper.Rnw
Adding operator fertility graph

@@
 <<setup, include=FALSE, cache=FALSE, message=FALSE, echo=FALSE>>=
+clean <- function(x)sub('CONSTRUCTOR','CONSTR',sub('RETURN','R',sub('INCREMENTS','INC',sub('VOID','V',sub('CONDITIONAL','COND',sub('NON','N',sub('VARIABLE','VAR',sub('MEMBER','MEM',sub('DELETE_','D_',sub('REMOVE_','R_',sub('NEGATE_','N_',sub('_CALLS','',sub('EXPERIMENTAL_','E_',x)))))))))))))
 #options(warn=-1)
@@
 logit<-function(x) log(x/(1-x))
+require(reshape2)
+require(xtable)
 @
@@
 \section{Introduction}
+<<>>=
+load('data/opdist.rda')
+@
 % 1. Describe the problem
@@
 
+\subsection{Operators}
+
+\subsection{Occurrence of Operators}
+\begin{figure*}[t]
+<<op,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+par(las=1,mfrow = c(1, 2),mar=c(2,8,1,1))
+o.all <- cbind(projects = rownames(o.pit.all), stack(o.pit.all))
+o.all$ind <- clean(o.all$ind)
+with(o.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='*',main='Original'))
+o.det <- cbind(projects = rownames(o.pit.det), stack(o.pit.det))
+o.det$ind <- clean(o.det$ind)
+with(o.det,boxplot(values~ind,horizontal=T,border=c('darkgray'), add=T,pch='+'))
+
+r.all <- cbind(projects = rownames(r.pit.all), stack(r.pit.all))
+r.all$ind <- clean(r.all$ind)
+with(r.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='*',main='Randoop'))
+r.det <- cbind(projects = rownames(r.pit.det), stack(r.pit.det))
+r.det$ind <- clean(r.det$ind)
+with(r.det,boxplot(values~ind,horizontal=T,border=c('darkgray'), add=T,pch='+'))
+@
+\caption{Relative fertility of mutation operators}
+\label{fig:mfert}
+
+\end{figure*}
+
 % <<prepare,echo=F>>=
@@
 
-<<>>=
-s <- t.test(lrnd.mut.avg, sdl.mut.avg, paired=T)
-@
+%<<>>=
+%s <- t.test(lrnd.mut.avg, sdl.mut.avg, paired=T)
+%@
 
@@
 The number of mutators in RND is
- \Sexpr{sum(m$lrnd.pit.mutation.total) / sum(m$sdl.pit.mutation.total)} times SDL.
+ Sexpr{sum(m.lrnd.pit.mutation.total) / sum(m.sdl.pit.mutation.total)} times SDL.
 
-The total mutants for all is \Sexpr{sum(m$pit.mutation.total)}, for rnd is \Sexpr{sum(m$lrnd.pit.mutation.total)} and for sdl is \Sexpr{sum(m$sdl.pit.mutation.total)}
+The total mutants for all is Sexpr{sum(m.pit.mutation.total)}, for rnd is Sexpr{sum(m.lrnd.pit.mutation.total)} and for sdl is Sexpr{sum(m.sdl.pit.mutation.total)}
 

### 2014-03-01 src/paper.Rnw
update

@@
 require(xtable)
+require(Mutsel)
 @
@@
 <<>>=
-load('data/opdist.rda')
+data(o.pit.all)
+data(o.pit.det)
+data(r.pit.all)
+data(r.pit.det)
 @
@@
 @
-\caption{Relative fertility of mutation operators}
+\caption{Relative fertility of mutation operators. The gray boxes represent detected mutants, while black represents total mutants.}
 \label{fig:mfert}
@@
 % @
-
-\begin{figure*}[t]
-% <<plots, fig.width=5, fig.height=5, out.width='.45\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-% plot(sdl_f, main='SDL ~ ALL',pch='*')
-% abline(sdl_all, col='red')
-% plot(rnd_f, main='RND ~ ALL',pch='*')
-% abline(rnd_all, col='blue')
-% abline(sdl_all, col='red', lty=2)
-% @
-\caption{Plots}
-\label{fig:caddrm}
-\end{figure*}
-
-\begin{figure*}[t]
-% <<mutnum, fig.width=5, fig.height=5, out.width='.45\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-% hist(log(10,m$sdl.pit.mutation.total), breaks=50, col=rgb(0,0,1,1/4), main='histogram of log(sdl) mutation score')
-% hist(log(10,m$sdl.pit.mutation.num), breaks=50, add=T, col=rgb(1,0,0,1/4))
-% 
-% hist(log(10,m$lrnd.pit.mutation.total), breaks=50, col=rgb(0,0,1,1/4), main='histogram of log(rnd) mutation score')
-% hist(log(10,m$lrnd.pit.mutation.num), breaks=50, add=T, col=rgb(1,0,0,1/4))
-% 
-% hist(log(10,m$pit.mutation.total), breaks=50, col=rgb(0,0,1,1/4), main='histogram of log(total) mutation score')
-% hist(log(10,m$pit.mutation.num), breaks=50, add=T, col=rgb(1,0,0,1/4))
-% @
-\caption{Plots of total mutation number, and those killed.}
-\label{fig:caddrm}
-\end{figure*}
 

### 2014-03-01 src/paper.Rnw
update

@@
 o.all$ind <- clean(o.all$ind)
-with(o.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='*',main='Original'))
+bcol <- '#2171B5'
+#bcol <- 'darkgray'
+icol <- '#9ECAE0'
+#icol <- 'lightgray'
+with(o.all,boxplot(values~ind,horizontal=T,border=c(bcol), col=icol, pch='.',main='Original'))
 o.det <- cbind(projects = rownames(o.pit.det), stack(o.pit.det))
 o.det$ind <- clean(o.det$ind)
-with(o.det,boxplot(values~ind,horizontal=T,border=c('darkgray'), add=T,pch='+'))
+with(o.det,boxplot(values~ind,horizontal=T,border=c('black'), add=T,pch='.',  yaxt="n"))
 
@@
 r.all$ind <- clean(r.all$ind)
-with(r.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='*',main='Randoop'))
+with(r.all,boxplot(values~ind,horizontal=T,border=c(bcol),col=icol, pch='.',main='Randoop'))
 r.det <- cbind(projects = rownames(r.pit.det), stack(r.pit.det))
 r.det$ind <- clean(r.det$ind)
-with(r.det,boxplot(values~ind,horizontal=T,border=c('darkgray'), add=T,pch='+'))
+with(r.det,boxplot(values~ind,horizontal=T,border=c('black'), add=T,pch='.', yaxt='n'))
 @

### 2014-03-01 src/paper.Rnw
update

--- 2014-03-01 src/paper.Rnw
@@
 o.all$ind <- clean(o.all$ind)
-with(o.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='*',main='Original'))
+bcol <- '#2171B5'
+#bcol <- 'darkgray'
+icol <- '#9ECAE0'
+#icol <- 'lightgray'
+with(o.all,boxplot(values~ind,horizontal=T,border=c(bcol), col=icol, pch='.',main='Original', cex.axis=0.8, ylim=c(0,1.0)))
 o.det <- cbind(projects = rownames(o.pit.det), stack(o.pit.det))
 o.det$ind <- clean(o.det$ind)
-with(o.det,boxplot(values~ind,horizontal=T,border=c('darkgray'), add=T,pch='+'))
+with(o.det,boxplot(values~ind,horizontal=T,border=c('black'), add=T,pch='.', axes=F, ylim=c(0,1.0)))
 
@@
 r.all$ind <- clean(r.all$ind)
-with(r.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='*',main='Randoop'))
+with(r.all,boxplot(values~ind,horizontal=T,border=c(bcol),col=icol, pch='.',main='Randoop', cex.axis=0.8,ylim=c(0,1.0)))
 r.det <- cbind(projects = rownames(r.pit.det), stack(r.pit.det))
 r.det$ind <- clean(r.det$ind)
-with(r.det,boxplot(values~ind,horizontal=T,border=c('darkgray'), add=T,pch='+'))
+with(r.det,boxplot(values~ind,horizontal=T,border=c('black'), add=T,pch='.', axes=F,ylim=c(0,1.0)))
 @

### 2014-03-01 src/paper.Rnw
update

--- 2014-03-01 src/paper.Rnw
@@
 o.all$ind <- clean(o.all$ind)
-with(o.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='*',main='Original'))
+bcol <- '#2171B5'
+#bcol <- 'darkgray'
+icol <- '#9ECAE0'
+#icol <- 'lightgray'
+with(o.all,boxplot(values~ind,horizontal=T,border=c(bcol), col=icol, pch='.',main='Original', cex.axis=0.8, ylim=c(0,0.5)))
 o.det <- cbind(projects = rownames(o.pit.det), stack(o.pit.det))
 o.det$ind <- clean(o.det$ind)
-with(o.det,boxplot(values~ind,horizontal=T,border=c('darkgray'), add=T,pch='+'))
+with(o.det,boxplot(values~ind,horizontal=T,border=c('black'), add=T,pch='.', axes=F, ylim=c(0,0.5)))
 
@@
 r.all$ind <- clean(r.all$ind)
-with(r.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='*',main='Randoop'))
+with(r.all,boxplot(values~ind,horizontal=T,border=c(bcol),col=icol, pch='.',main='Randoop', cex.axis=0.8,ylim=c(0,0.5)))
 r.det <- cbind(projects = rownames(r.pit.det), stack(r.pit.det))
 r.det$ind <- clean(r.det$ind)
-with(r.det,boxplot(values~ind,horizontal=T,border=c('darkgray'), add=T,pch='+'))
+with(r.det,boxplot(values~ind,horizontal=T,border=c('black'), add=T,pch='.', axes=F,ylim=c(0,0.5)))
 @

### 2014-03-01 src/paper.Rnw
update

--- 2014-03-01 src/paper.Rnw
@@
 #icol <- 'lightgray'
-with(o.all,boxplot(values~ind,horizontal=T,border=c(bcol), col=icol, pch='.',main='Original'))
+with(o.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Original', cex.axis=0.8, ylim=c(0,0.5)))
 o.det <- cbind(projects = rownames(o.pit.det), stack(o.pit.det))
 o.det$ind <- clean(o.det$ind)
-with(o.det,boxplot(values~ind,horizontal=T,border=c('black'), add=T,pch='.',  yaxt="n"))
+with(o.det,boxplot(values~ind,horizontal=T,border=c(bcol), col=icol, add=T,pch='.', axes=F, ylim=c(0,0.5)))
 
@@
 r.all$ind <- clean(r.all$ind)
-with(r.all,boxplot(values~ind,horizontal=T,border=c(bcol),col=icol, pch='.',main='Randoop'))
+with(r.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Randoop', cex.axis=0.8,ylim=c(0,0.5)))
 r.det <- cbind(projects = rownames(r.pit.det), stack(r.pit.det))
 r.det$ind <- clean(r.det$ind)
-with(r.det,boxplot(values~ind,horizontal=T,border=c('black'), add=T,pch='.', yaxt='n'))
+with(r.det,boxplot(values~ind,horizontal=T,border=c(bcol), col=icol, add=T,pch='.', axes=F,ylim=c(0,0.5)))
 @
@@
 \item [TODO] Report time for each, as cost.
-\item [DONTKNOWHOWTO] Find the mutant count to LOC multiplier, and use it to get the probability of choosing for each project.
+\item [TODOX] Find the mutant count to LOC multiplier, and use it to get the probability of choosing for each project.
 \end{enumerate}

### 2014-03-01 src/paper.Rnw
update

@@
 #icol <- 'lightgray'
-with(o.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Original', cex.axis=0.8, ylim=c(0,0.5)))
 o.det <- cbind(projects = rownames(o.pit.det), stack(o.pit.det))
 o.det$ind <- clean(o.det$ind)
-with(o.det,boxplot(values~ind,horizontal=T,border=c(bcol), col=icol, add=T,pch='.', axes=F, ylim=c(0,0.5)))
+with(o.det,boxplot(values~ind,horizontal=T,border=c(bcol), col=icol, pch='.', axes=F, ylim=c(0,0.5)))
+with(o.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Original', cex.axis=0.8, ylim=c(0,0.5),add=T))
 
@@
 r.all$ind <- clean(r.all$ind)
-with(r.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Randoop', cex.axis=0.8,ylim=c(0,0.5)))
 r.det <- cbind(projects = rownames(r.pit.det), stack(r.pit.det))
 r.det$ind <- clean(r.det$ind)
-with(r.det,boxplot(values~ind,horizontal=T,border=c(bcol), col=icol, add=T,pch='.', axes=F,ylim=c(0,0.5)))
+with(r.det,boxplot(values~ind,horizontal=T,border=c(bcol), col=icol, pch='.', axes=F,ylim=c(0,0.5)))
+with(r.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Randoop', cex.axis=0.8,ylim=c(0,0.5),add=T))
 @

### 2014-03-01 src/paper.Rnw
update

@@
 o.det$ind <- clean(o.det$ind)
-with(o.det,boxplot(values~ind,horizontal=T,border=c(bcol), col=icol, pch='.', axes=F, ylim=c(0,0.5)))
-with(o.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Original', cex.axis=0.8, ylim=c(0,0.5),add=T))
+with(o.det,boxplot(values~ind,horizontal=T,border=c(bcol), col=icol, pch='.', axes=F, ylim=c(0,0.6)))
+with(o.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Original', cex.axis=0.8, ylim=c(0,0.6),add=T))
 
@@
 r.det$ind <- clean(r.det$ind)
-with(r.det,boxplot(values~ind,horizontal=T,border=c(bcol), col=icol, pch='.', axes=F,ylim=c(0,0.5)))
-with(r.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Randoop', cex.axis=0.8,ylim=c(0,0.5),add=T))
+with(r.det,boxplot(values~ind,horizontal=T,border=c(bcol), col=icol, pch='.', axes=F,ylim=c(0,0.6)))
+with(r.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Randoop', cex.axis=0.8,ylim=c(0,0.6),add=T))
 @

### 2014-03-01 src/paper.Rnw
udpate

@@
 <<setup>>
+v=data(package='Mutsel')
+data(list = v$results[,3])
 @
@@
 <<>>=
-data(o.pit.all)
-data(o.pit.det)
-data(r.pit.all)
-data(r.pit.det)
+data(o.dist.all)
+data(o.dist.det)
+data(r.dist.all)
+data(r.dist.det)
 @
@@
 par(las=1,mfrow = c(1, 2),mar=c(2,8,1,1))
-o.all <- cbind(projects = rownames(o.pit.all), stack(o.pit.all))
+o.all <- cbind(projects = rownames(o.dist.all), stack(o.dist.all))
 o.all$ind <- clean(o.all$ind)
@@
 #icol <- 'lightgray'
-o.det <- cbind(projects = rownames(o.pit.det), stack(o.pit.det))
+o.det <- cbind(projects = rownames(o.dist.det), stack(o.dist.det))
 o.det$ind <- clean(o.det$ind)
@@
 
-r.all <- cbind(projects = rownames(r.pit.all), stack(r.pit.all))
+r.all <- cbind(projects = rownames(r.dist.all), stack(r.dist.all))
 r.all$ind <- clean(r.all$ind)
-r.det <- cbind(projects = rownames(r.pit.det), stack(r.pit.det))
+r.det <- cbind(projects = rownames(r.dist.det), stack(r.dist.det))
 r.det$ind <- clean(r.det$ind)
@@
 @
-\caption{Relative fertility of mutation operators. The gray boxes represent detected mutants, while black represents total mutants.}
-\label{fig:mfert}
-
+\caption{Relative fertility of mutation operators. The blue shade represent detected mutants, while black represents total mutants.}
+\label{fig:op}
 \end{figure*}
 
-% <<prepare,echo=F>>=
-% attach(m)
-% sdl_f <- mut.avg~sdl.mut.avg + 0
-% rnd_f <- mut.avg~lrnd.mut.avg + 0
-% 
-% sdl_all <- lm(sdl_f)
-% rnd_all <- lm(rnd_f)
-% 
-% sdl_s <- summary(sdl_all)
-% rnd_s <- summary(rnd_all)
-% 
-% sdl.est <- sdl_s$coefficients['sdl.mut.avg','Estimate']
-% rnd.est <- rnd_s$coefficients['lrnd.mut.avg','Estimate']
-% 
-% sdl.r <- sdl_s$r.squared
-% rnd.r <- rnd_s$r.squared
-% 
-% @
+\subsection{SDL vs Random selection}
+\begin{figure*}[t]
+<<sdl.1,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+par(mfrow=c(2,2))
+with(o.pit.all, plot(all.cov~TSDL.cov, pch='+', main='Original SDL'))
+with(o.pit.all, plot(all.cov~x1_per_line.cov, pch='+', main='Original 1 per line'))
+with(r.pit.all, plot(all.cov~TSDL.cov, pch='+', main='Randoop SDl'))
+with(r.pit.all, plot(all.cov~x1_per_line.cov, pch='+', main='Original 1 per line'))
+@
+\label{fig:sdl1}
+\caption{Statement Deletion vs One per line.}
+\end{figure*}
 

### 2014-03-01 src/paper.Rnw
update

@@
 with(r.pit.all, plot(all.cov~TSDL.cov, pch='+', main='Randoop SDl'))
-with(r.pit.all, plot(all.cov~x1_per_line.cov, pch='+', main='Original 1 per line'))
+with(r.pit.all, plot(all.cov~x1_per_line.cov, pch='+', main='Randoop 1 per line'))
 @

### 2014-03-02 src/paper.Rnw
update

@@
 
+<<results='asis'>>=
+o <- subset(stats.df[with(stats.df, order(-mutant.reduction, -r.square)),], mutant.reduction != Inf & kind == 'original')
+o.x <- subset(o, select=c('operator', 'r.square', 'mutant.reduction', 'score.multiplier'))
+colnames(o.x) <- c('operator', 'r^2', 'm.reduction', 'mcov.mult')
+print(xtable(o.x, caption='Original', label='table:try1'), include.rownames=FALSE)
+# , sanitize.text.function = function(x){x}, include.rownames=FALSE)
+@
+<<results='asis'>>=
+r <- subset(stats.df[with(stats.df, order(-mutant.reduction, -r.square)),], mutant.reduction != Inf & kind == 'randoop')
+r.x <- subset(o, select=c('operator','r.square', 'mutant.reduction', 'score.multiplier'))
+colnames(r.x) <- c('operator', 'r^2', 'm.reduction', 'mcov.mult')
+print(xtable(r.x, caption='Randoop', label='table:try1'), include.rownames=FALSE)
+@
+
 \subsection{Correlation Analysis}

### 2014-03-02 src/paper.Rnw
update

--- 2014-03-01 src/paper.Rnw
@@
 
+<<results='asis'>>=
+o <- subset(stats.df[with(stats.df, order(-r.square, -mutant.reduction)),], mutant.reduction != Inf & kind == 'original')
+o.x <- subset(o, select=c('operator', 'r.square', 'mutant.reduction', 'score.multiplier'))
+colnames(o.x) <- c('operator', 'r^2', 'm.reduction', 'mcov.mult')
+print(xtable(o.x, caption='Original', label='table:try1'), include.rownames=FALSE)
+# , sanitize.text.function = function(x){x}, include.rownames=FALSE)
+@
+<<results='asis'>>=
+r <- subset(stats.df[with(stats.df, order(-r.square, -mutant.reduction)),], mutant.reduction != Inf & kind == 'randoop')
+r.x <- subset(o, select=c('operator','r.square', 'mutant.reduction', 'score.multiplier'))
+colnames(r.x) <- c('operator', 'r^2', 'm.reduction', 'mcov.mult')
+print(xtable(r.x, caption='Randoop', label='table:try1'), include.rownames=FALSE)
+@
+
 \subsection{Correlation Analysis}

### 2014-03-03 src/paper.Rnw
udpate

--- 2014-03-01 src/paper.Rnw
@@
 
+<<results='asis'>>=
+o <- subset(stats.df, kind == 'original')
+o.x <- subset(o, select=c('operator', 'r.square', 'mutant.reduction', 'score.multiplier'))
+colnames(o.x) <- c('operator', 'r^2', 'm.reduction', 'mcov.mult')
+print(xtable(o.x, caption='Original', label='table:try1'), include.rownames=FALSE)
+# , sanitize.text.function = function(x){x}, include.rownames=FALSE)
+@
+<<results='asis'>>=
+r <- subset(stats.df, kind == 'randoop')
+r.x <- subset(o, select=c('operator','r.square', 'mutant.reduction', 'score.multiplier'))
+colnames(r.x) <- c('operator', 'r^2', 'm.reduction', 'mcov.mult')
+print(xtable(r.x, caption='Randoop', label='table:try1'), include.rownames=FALSE)
+@
+
 \subsection{Correlation Analysis}

### 2014-03-05 src/methodology.tex
decomposing the tex files, updating Makefile

--- 2014-03-03 src/paper.Rnw
@@
-\newcommand*\per{\scalebox{.5}{\%}}
-\newcommand\Mua{Mutation analysis~}
-\newcommand\mua{mutation analysis~}
-\begin{comment}
-<<setup, include=FALSE, cache=FALSE, message=FALSE, echo=FALSE>>=
-clean <- function(x)sub('CONSTRUCTOR','CONSTR',sub('RETURN','R',sub('INCREMENTS','INC',sub('VOID','V',sub('CONDITIONAL','COND',sub('NON','N',sub('VARIABLE','VAR',sub('MEMBER','MEM',sub('DELETE_','D_',sub('REMOVE_','R_',sub('NEGATE_','N_',sub('_CALLS','',sub('EXPERIMENTAL_','E_',x)))))))))))))
-#options(warn=-1)
-options(digits=3)
-opts_chunk$set(fig.path='figure/twocolumn-', fig.align='center', fig.show='hold', echo=FALSE)
-render_listings()
-logit<-function(x) log(x/(1-x))
-require(reshape2)
-require(xtable)
-require(Mutsel)
-@
-<<chunk-hook, echo=2>>=
-<<setup>>
-v=data(package='Mutsel')
-data(list = v$results[,3])
-@
-\end{comment}
-
-% <<a,message=F, echo=F>>=
-% require(xtable)
-% require(data.table)
-% load('data/mu.rda')
-% @
-
-% 10 pages for the main text + 1 for references.
-\section{Introduction}
-<<>>=
-data(o.dist.all)
-data(o.dist.det)
-data(r.dist.all)
-data(r.dist.det)
-@
-% 1. Describe the problem
-% 2. State your contributions
-
-Mutation analysis originally proposed by Lipton\cite{lipton1971fault} involves systematic transformation of program through introduction of first order syntactical changes\cite{ammann2008introduction}.
-Researchers have shown that the mutations thus introduced behave similarly to the real faults\cite{andrews2005mutation}, and hence can be used as a stand-in for real faults when determining the efficacy of a test suite against faults.
-
-While mutation analysis provides a useful metric, its use has been held back due to its high computational requirements\cite{jia2011analysis}.
-This has led researchers to search for ways of reducing the resource requirements of the analysis.
-The methods in this direction can be classified into ``Do faster'', ``Do fewer'', and ``Do smarter''\cite{offutt2001mutation}.
-The ``Do fewer'' approach has come in for special study, and various researchers have investigated different ways to reduce the number of mutants thus produced.
-
-One of the main approaches is selective mutation, proposed by Mathur\cite{mathur1991performance}, and further refined by Offutt et al.\cite{offutt1993anexperimental}.
-This approach relies on the fact that some of the mutagens generate a large number of variants, and hence produce highly redundant test cases.
-Previous research suggested that elimination of mutagens with high fertility results in the reduction of total number of mutations produced, and hence reduces the computational requirements.
-
-% TODO check the survey again on selective mutation.
-
-It was recently questioned whether this approach indeed resulted in a tangible improvement over random selection of mutants\cite{zhang2010operator}, which did not find operator based selection to be better than random selection.
-It was later found that using operator based selection and random sampling was better than using each strategy separately\cite{zhang2013ase}.
-
-Another research, initially by Unch\cite{untch2009onreduced} and recently by Deng et al.\cite{deng2013empirical} suggests using software deletion operator since it produces the least number of mutants (smallest neighborhood).
-The researchers were able to obtain a close approximation of original mutant score with significant savings with this approach.
-
-However, our previous research suggests that mutation coverage is closely predicted by statement coverage, this suggests that any criteria that forces accounting of the impact of each statement should provide a close approximation to the full mutation score.
-Hence, our research suggests that SDL works because it forces accounting of each line, and a random sampling criteria that provides the same criteria should result in similar results.
-
-In our analysis, we find that a random sampling approach that randomly chose a single mutant per line was found to have a better correlation with the full mutation score than that obtained by SDL.
-Further it was also found that the mutation score produced by random sampling was closer to the full mutation score than that produced by SDL.
-
-\section{Related Work}
-Mathur\cite{mathur1991performance, wong1993mutation, wong1995reducing} first mentioned the idea of constrained mutation in a one-pager.
-This was taken up by Offut et al.\cite{offutt1993experimental}.
-(Offutt states in his 1993 paper\cite{offutt1993experimental} that Mathur has in 1991\cite{mathur1991performance} suggested the constrined/selective mutation.
-However, that paper does not propose it at all.
-It says we are experimenting with an idea, and that is it.
-It is in 1995\cite{wong1995reducing} that the idea is actually proposed, notably after Offutt has written about its effectiveness.
-$\ddot\smile$ - time travel?).
-The idea is that normal mutation has quadratic complexity on variable references while eliminatng the most fecund mutagens (SVR and ASR) achieves linear complexity on program size, while still approximating the full mutation score closely.
-They propose N-selective mutation which avoids N most fertile mutagens.
-Wong \cite{wong1995reducing} compares the effect of x\% mutation selection, and abs/ror constrained mutation.
-According to Wong, this is different from selective mutation in that only the most fecund operators are included rather than excluded.
-He finds that there is no evidence to suggest one over the other.
-Offutt\cite{offutt1993experimental} does not compare the effectivenss of selective mutation with x\% mutation.
-He also defines the concept of {\it operator strength} for an operator, which is defined as the total number of mutants that are killed by test data that is generated to kill only the mutants generated by that operator.
-He further posits that the mutagens with greatest strength may be the most useful ones.
-%(test data generated to eliminate variants of one operator may remove the mutants of other kinds too.)
-This is taken up later by Mresa\cite{mresa1999efficiency} et al.
-who used the cost of detection of mutants as a means of selection, and uses it to define another set of operators (san, aor, sdl, ror, uoi).
-They also find that if very high mutation score close to 100\% is required, x\% selective mutation is better than operator selection, and conversely for less stringent scores, operator selection would be better if const of mutant is considered.
-
-Barbosa et. al.\cite{barbosa2001toward} provides a set of guidelines for selecting mutagens.
-
-Namin et al.\cite{namin2006finding,siami2008sufficient} treats the operator selection as a variable reduction problem, and applying statistical approaches, finds 28 operators from a total of 108 operators that are sufficient for an adequate test suite.
-
-Offutt\cite{offutt1996anexperimental} following the previous paper\cite{offutt1993experimental} compares the effectiveness of selecting different operators.
-He divides the total operators into operand, operation, and statement categories, with es-selective avoiding operands, rs-selective avoiding operations, and re-selective avoiding statements, and e-selective only operations.
-He finds that using only operation based mutation operators (numbering 5) is sufficient for close approximation of full mutation score.
-He suggests that the reason they are effective is that most statements contain operators.
-He further posits that another reason is the amount of semantic change accomplished by an operator, and perhaps the most interesting ones are those that produce the smallest semantic difference.
-% Replacement of Operand , Statement modification, Expression Modification: modify operators, ES-selective : not using operand, RS-Selective: not using expression, RE-Selective: not uinsg statement, E-selective : only expression..
-
-Unch\cite{untch2009onreduced} suggested using a single mutagen statement deletion.
-He compares the statement deletion with other selective mutagen sets, and finds statement deletion operator to provide the best prediction of original mutation score ($R^2 = 0.97$)
-This was carried forward by Deng et al\cite{deng2013empirical}, (according to whom, random sampling was weak when it was made low enough for appreciable mutant savings).
-They realize a mean mutation score of 92\% for adequate test suites with SDL alone, and generating a saving of 81\% in the number of mutants, and 41\% fewer equivalent mutants.
-
-Zhang et al.\cite{zhang2010operator}, compares operator based mutant selection to random mutant selection.
-They compare three diffrent operator based selection techniques from Offutt et al., Barbosa et al., and Namin et al.
-against random mutant selection, with equal mutant probability, and equal mutagen probaiblity.
-They find that none of these selection techniques are superior to random selection, with same number of mutants.
-They also find that equal mutation sampling is more effective for larger subjects compared to equal mutagen sampling and the reverse is true for smaller subjects.
-A second paper by Zhang et al.\cite{zhang2013ase} investigates 8 sampling strategies on top of operator based mutant selection.
-They find that sampling strategies based on programming elements (method based) performed best.
-% Baseline : x\% from selected set
-% MOP : x\% from each mutagen
-% for these, it is sampled from operator based selected set.
-% PLEm : x\% from inside the same program element.
-% PLE + MOP: sample x\% from same mutagen from same element.
-
-% On Mutation and Dataflow : W.E Eong
-Wong et al~\cite{wong1994on} suggests random sampling of mutants from the complete population.
-
-Wong and Mathur suggests constrained mutation~\cite{} which chooses specific mutation operators only.
-
-% Empirical Evaluation of the Statement Deletion Mutation Operator : Offutt
-Deng et al~\cite{deng2013empirical} considers the effect of using a single mutation operator -- the statement deletion operator. They define deletion for different language elements,
-
 \section{Methodology}
+\ref{sec:methodology}
 We collected a random sample of Java programs from Github\cite{github} that utilized the Maven\cite{maven} system for building.
@@
 This was done to ensure that the results from the random sampling and statement deletion could be compared.
-
-\section{Analysis}
-
-\subsection{Operators}
-
-\subsection{Occurrence of Operators}
-\begin{figure*}[t]
-<<op,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-par(las=1,mfrow = c(1, 2),mar=c(2,8,1,1))
-o.all <- cbind(projects = rownames(o.dist.all), stack(o.dist.all))
-o.all$ind <- clean(o.all$ind)
-bcol <- '#2171B5'
-#bcol <- 'darkgray'
-icol <- '#9ECAE0'
-#icol <- 'lightgray'
-o.det <- cbind(projects = rownames(o.dist.det), stack(o.dist.det))
-o.det$ind <- clean(o.det$ind)
-with(o.det,boxplot(values~ind,horizontal=T,border=c(bcol), col=icol, pch='.', axes=F, ylim=c(0,0.6)))
-with(o.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Original', cex.axis=0.8, ylim=c(0,0.6),add=T))
-
-r.all <- cbind(projects = rownames(r.dist.all), stack(r.dist.all))
-r.all$ind <- clean(r.all$ind)
-r.det <- cbind(projects = rownames(r.dist.det), stack(r.dist.det))
-r.det$ind <- clean(r.det$ind)
-with(r.det,boxplot(values~ind,horizontal=T,border=c(bcol), col=icol, pch='.', axes=F,ylim=c(0,0.6)))
-with(r.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Randoop', cex.axis=0.8,ylim=c(0,0.6),add=T))
-@
-\caption{Relative fertility of mutation operators. The blue shade represent detected mutants, while black represents total mutants.}
-\label{fig:op}
-\end{figure*}
-
-\subsection{SDL vs Random selection}
-\begin{figure*}[t]
-<<sdl.1,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-par(mfrow=c(2,2))
-with(o.pit.all, plot(all.cov~TSDL.cov, pch='+', main='Original SDL'))
-with(o.pit.all, plot(all.cov~x1_per_line.cov, pch='+', main='Original 1 per line'))
-with(r.pit.all, plot(all.cov~TSDL.cov, pch='+', main='Randoop SDl'))
-with(r.pit.all, plot(all.cov~x1_per_line.cov, pch='+', main='Randoop 1 per line'))
-@
-\label{fig:sdl1}
-\caption{Statement Deletion vs One per line.}
-\end{figure*}
-
-<<results='asis'>>=
-o <- subset(stats.df, kind == 'original')
-o.x <- subset(o, select=c('operator', 'r.square', 'mutant.reduction', 'score.multiplier'))
-colnames(o.x) <- c('operator', 'r^2', 'm.reduction', 'mcov.mult')
-print(xtable(o.x, caption='Original', label='table:try1'), include.rownames=FALSE)
-# , sanitize.text.function = function(x){x}, include.rownames=FALSE)
-@
-<<results='asis'>>=
-r <- subset(stats.df, kind == 'randoop')
-r.x <- subset(o, select=c('operator','r.square', 'mutant.reduction', 'score.multiplier'))
-colnames(r.x) <- c('operator', 'r^2', 'm.reduction', 'mcov.mult')
-print(xtable(r.x, caption='Randoop', label='table:try1'), include.rownames=FALSE)
-@
-
-\subsection{Correlation Analysis}
-
-$ \mu\{ M_{all}| M_{sample} \} = 0 + \beta_1 \times M{sample}  $
-
-The interesting part is (1) the $\beta_1$ coefficient which tells how much we must multiply the  sampled/selected score to get original score, and $R^2$ which tells us how close the score is.
-
-\subsubsection{sdl.mut.avg and mut.avg}
-
-% <<>>=
-% c <- cor(subset(m, select=c(sdl.mut.avg, mut.avg)) , method="kendall", use="pairwise")['sdl.mut.avg', 'mut.avg']
-% d <- cor(subset(m, select=c(lrnd.mut.avg, mut.avg)) , method="kendall", use="pairwise")['lrnd.mut.avg', 'mut.avg']
-% @
-
-$ \mu_\{M_{all} | M_{sdl}\} = Sexpr{sdl.est} \times M_{sdl} \text{ : } R^2 = Sexpr{sdl.r} \text{,} \tau_{\beta} = Sexpr{c}$
-
-\subsubsection{lrnd.mut.avg and mut.avg}
-
-$ \mu_\{M_{all} | M_{rnd}\} = Sexpr{rnd.est} \times M_{rnd} \text{ : } R^2 = Sexpr{rnd.r} \text{,} \tau_{\beta} = Sexpr{d}$
-
-\subsection{Regression Analysis}
-The next question we will tackle is if there exist a difference at all between SDL mutagen and the random sampling.
-We can perform two statistical tests to answer this question.
-For the first, we run a simple paired t-test.
-
-%<<>>=
-%s <- t.test(lrnd.mut.avg, sdl.mut.avg, paired=T)
-%@
-
-The paired t-test failed to sufficient difference between the two distributions with a two-sided p-value of Sexpr{s.p.value}.
-That is, we do not have sufficient evidence to conclude that the two distributions are different.
-
-The second approch is convoluted (I am a little unclear here.). We try to predict the original mutation score using the mutation score from both sdl and random sampling.
-Our full model is
-
-$ \mu_\{M_{all} | M_{sdl}, M_{rnd}\} = 0 + \beta_1 {sdl} + \beta_2 M_{rnd} + \beta_3 M_{sdl} M_{rnd}  $
-\begin{small}
-% <<results='asis'>>=
-% s <- subset(m, select=c(mut.avg,sdl.mut.avg))
-% s$type <- 'sdl'
-% colnames(s) <- c('mut', 'sample', 'type')
-% r <- subset(m, select=c(mut.avg,lrnd.mut.avg))
-% r$type <- 'rnd'
-% colnames(r) <- c('mut', 'sample', 'type')
-% all <- rbind(s, r)
-% fm <- with(all, lm(mut ~ sample + type + sample:type))
-% sm <- anova(fm)
-% print(xtable(sm,caption="My caption"), size="\\small")
-% @
-\end{small}
-
-We see that both type and sample:type are non-significant for predicting the final model, and sequentially removing them does not change the effectiveness.
-Hence, the techniques random sampling and statement deletion operator do not have any difference.
-
-\begin{figure*}[t]
-% <<tplots, fig.width=5, fig.height=5, out.width='.45\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-% t_f <- sdl.time~lrnd.time
-% plot(t_f, main='SDL ~ RND',pch='*')
-% abline(lm(t_f), col='red')
-% detach(m)
-% @
-\caption{Time}
-\label{fig:caddrm}
-\end{figure*}
-
-\section{Results}
-
-We see from the data that random sampling has a higher $R^2$, and also approximates the all  mutations score better.
-However, caveat emptor. There is a difference between the number of mutators for SDL and RAND. If our approximation was right, we should have gotten nearly same number of mutators. However
-The number of mutators in RND is
- Sexpr{sum(m.lrnd.pit.mutation.total) / sum(m.sdl.pit.mutation.total)} times SDL.
-
-The total mutants for all is Sexpr{sum(m.pit.mutation.total)}, for rnd is Sexpr{sum(m.lrnd.pit.mutation.total)} and for sdl is Sexpr{sum(m.sdl.pit.mutation.total)}
-
-\begin{enumerate}
-\item [x] For op-selection to work, the distributions of mutations across different projects has to be similar enough. This can be checked by t-test.
-\item [TODO] We should check if the distribution significantly different too.
-\item [DONE] Use sampling
-\item [DONE] Check on randoop samples too
-\item [NO] Implement bomb (athrow) and see its mutation score, and see how close it comes.
-\item [DONE] Compare random selection with class, method, and mutagen sampling.
-\item [TODO] Report time for each, as cost.
-\item [TODOX] Find the mutant count to LOC multiplier, and use it to get the probability of choosing for each project.
-\end{enumerate}

### 2014-03-05 src/x1x32_perline_example.tex
decomposing the tex files, updating Makefile

killed:
./AntiCheat/src/main/java/net/h31ix/anticheat/xray/XRayTracker.java

        return calculate(player, stats.getDiamond(), total) || calculate(player, stats.getGold(), total) || calculate(player, stats.getIron(), total) || calculate(player, stats.getLapis(), total) || calculate(player, stats.getRedstone(), total);

live:
./AntiCheat/src/main/java/net/h31ix/anticheat/util/PastebinReport.java
 out.write(("api_option=paste" + "&api_dev_key=" + URLEncoder.encode("c0616def494dcb5b7632304f8c52c0f1", "utf-8") + "&api_paste_code=" + URLEncoder.encode(report.toString(), "utf-8") + "&api_paste_private=" + URLEncoder.encode("1", "utf-8") + "&api_paste_name=" + URLEncoder.encode("", "utf-8") + "&api_paste_expire_date=" + URLEncoder.encode("1M", "utf-8") + "&api_paste_format=" + URLEncoder.encode("text", "utf-8") + "&api_user_key=" + URLEncoder.encode("", "utf-8")).getBytes());

### 2014-03-05 src/paper.Rnw

@@
 
+\subsection{Probes}
+% half_per_line half_per_method :  + halfrand-project
+%   For each (line|method|class), get the number of mutants produced. Then sample exactly half the mutants produced per unit
+
 \section{Analysis}
@@
 o <- subset(stats.df, kind == 'original')
-o.x <- subset(o, select=c('operator', 'r.square', 'mutant.reduction', 'score.multiplier'))
-colnames(o.x) <- c('operator', 'r^2', 'm.reduction', 'mcov.mult')
+o.x <- subset(o, select=c('operator', 'r.square', 'mutant.reduction', 'sample', 'score.multiplier'))
+colnames(o.x) <- c('operator', 'r^2', 'm.red', 'sample', 'mcov.mult')
 print(xtable(o.x, caption='Original', label='table:try1'), include.rownames=FALSE)
@@
 r <- subset(stats.df, kind == 'randoop')
-r.x <- subset(o, select=c('operator','r.square', 'mutant.reduction', 'score.multiplier'))
-colnames(r.x) <- c('operator', 'r^2', 'm.reduction', 'mcov.mult')
+r.x <- subset(r, select=c('operator','r.square', 'mutant.reduction', 'sample', 'score.multiplier'))
+colnames(r.x) <- c('operator', 'r^2', 'm.red', 'sample', 'mcov.mult')
 print(xtable(r.x, caption='Randoop', label='table:try1'), include.rownames=FALSE)

### 2014-03-05 src/methodology.tex
More seperation of concerns

@@
 \section{Methodology}
-\ref{sec:methodology}
+\label{sec:methodology}
 We collected a random sample of Java programs from Github\cite{github} that utilized the Maven\cite{maven} system for building.
@@
 This was done to ensure that the results from the random sampling and statement deletion could be compared.
+
+\subsection{Probes}
+% half_per_line half_per_method :  + halfrand-project
+%   For each (line|method|class), get the number of mutants produced. Then sample exactly half the mutants produced per unit

### 2014-03-05 src/paper.Rnw
More seperation of concerns

@@
 % 10 pages for the main text + 1 for references.
-\section{Introduction}
 <<>>=
@@
 @
-% 1. Describe the problem
-% 2. State your contributions
+\input{intro}
 
-Mutation analysis originally proposed by Lipton\cite{lipton1971fault} involves systematic transformation of program through introduction of first order syntactical changes\cite{ammann2008introduction}.
-Researchers have shown that the mutations thus introduced behave similarly to the real faults\cite{andrews2005mutation}, and hence can be used as a stand-in for real faults when determining the efficacy of a test suite against faults.
-
-While mutation analysis provides a useful metric, its use has been held back due to its high computational requirements\cite{jia2011analysis}.
-This has led researchers to search for ways of reducing the resource requirements of the analysis.
-The methods in this direction can be classified into ``Do faster'', ``Do fewer'', and ``Do smarter''\cite{offutt2001mutation}.
-The ``Do fewer'' approach has come in for special study, and various researchers have investigated different ways to reduce the number of mutants thus produced.
-
-One of the main approaches is selective mutation, proposed by Mathur\cite{mathur1991performance}, and further refined by Offutt et al.\cite{offutt1993anexperimental}.
-This approach relies on the fact that some of the mutagens generate a large number of variants, and hence produce highly redundant test cases.
-Previous research suggested that elimination of mutagens with high fertility results in the reduction of total number of mutations produced, and hence reduces the computational requirements.
-
-% TODO check the survey again on selective mutation.
-
-It was recently questioned whether this approach indeed resulted in a tangible improvement over random selection of mutants\cite{zhang2010operator}, which did not find operator based selection to be better than random selection.
-It was later found that using operator based selection and random sampling was better than using each strategy separately\cite{zhang2013ase}.
-
-Another research, initially by Unch\cite{untch2009onreduced} and recently by Deng et al.\cite{deng2013empirical} suggests using software deletion operator since it produces the least number of mutants (smallest neighborhood).
-The researchers were able to obtain a close approximation of original mutant score with significant savings with this approach.
-
-However, our previous research suggests that mutation coverage is closely predicted by statement coverage, this suggests that any criteria that forces accounting of the impact of each statement should provide a close approximation to the full mutation score.
-Hence, our research suggests that SDL works because it forces accounting of each line, and a random sampling criteria that provides the same criteria should result in similar results.
-
-In our analysis, we find that a random sampling approach that randomly chose a single mutant per line was found to have a better correlation with the full mutation score than that obtained by SDL.
-Further it was also found that the mutation score produced by random sampling was closer to the full mutation score than that produced by SDL.
-
-\section{Related Work}
-Mathur\cite{mathur1991performance, wong1993mutation, wong1995reducing} first mentioned the idea of constrained mutation in a one-pager.
-This was taken up by Offut et al.\cite{offutt1993experimental}.
-(Offutt states in his 1993 paper\cite{offutt1993experimental} that Mathur has in 1991\cite{mathur1991performance} suggested the constrined/selective mutation.
-However, that paper does not propose it at all.
-It says we are experimenting with an idea, and that is it.
-It is in 1995\cite{wong1995reducing} that the idea is actually proposed, notably after Offutt has written about its effectiveness.
-$\ddot\smile$ - time travel?).
-The idea is that normal mutation has quadratic complexity on variable references while eliminatng the most fecund mutagens (SVR and ASR) achieves linear complexity on program size, while still approximating the full mutation score closely.
-They propose N-selective mutation which avoids N most fertile mutagens.
-Wong \cite{wong1995reducing} compares the effect of x\% mutation selection, and abs/ror constrained mutation.
-According to Wong, this is different from selective mutation in that only the most fecund operators are included rather than excluded.
-He finds that there is no evidence to suggest one over the other.
-Offutt\cite{offutt1993experimental} does not compare the effectivenss of selective mutation with x\% mutation.
-He also defines the concept of {\it operator strength} for an operator, which is defined as the total number of mutants that are killed by test data that is generated to kill only the mutants generated by that operator.
-He further posits that the mutagens with greatest strength may be the most useful ones.
-%(test data generated to eliminate variants of one operator may remove the mutants of other kinds too.)
-This is taken up later by Mresa\cite{mresa1999efficiency} et al.
-who used the cost of detection of mutants as a means of selection, and uses it to define another set of operators (san, aor, sdl, ror, uoi).
-They also find that if very high mutation score close to 100\% is required, x\% selective mutation is better than operator selection, and conversely for less stringent scores, operator selection would be better if const of mutant is considered.
-
-Barbosa et. al.\cite{barbosa2001toward} provides a set of guidelines for selecting mutagens.
-
-Namin et al.\cite{namin2006finding,siami2008sufficient} treats the operator selection as a variable reduction problem, and applying statistical approaches, finds 28 operators from a total of 108 operators that are sufficient for an adequate test suite.
-
-Offutt\cite{offutt1996anexperimental} following the previous paper\cite{offutt1993experimental} compares the effectiveness of selecting different operators.
-He divides the total operators into operand, operation, and statement categories, with es-selective avoiding operands, rs-selective avoiding operations, and re-selective avoiding statements, and e-selective only operations.
-He finds that using only operation based mutation operators (numbering 5) is sufficient for close approximation of full mutation score.
-He suggests that the reason they are effective is that most statements contain operators.
-He further posits that another reason is the amount of semantic change accomplished by an operator, and perhaps the most interesting ones are those that produce the smallest semantic difference.
-% Replacement of Operand , Statement modification, Expression Modification: modify operators, ES-selective : not using operand, RS-Selective: not using expression, RE-Selective: not uinsg statement, E-selective : only expression..
-
-Unch\cite{untch2009onreduced} suggested using a single mutagen statement deletion.
-He compares the statement deletion with other selective mutagen sets, and finds statement deletion operator to provide the best prediction of original mutation score ($R^2 = 0.97$)
-This was carried forward by Deng et al\cite{deng2013empirical}, (according to whom, random sampling was weak when it was made low enough for appreciable mutant savings).
-They realize a mean mutation score of 92\% for adequate test suites with SDL alone, and generating a saving of 81\% in the number of mutants, and 41\% fewer equivalent mutants.
-
-Zhang et al.\cite{zhang2010operator}, compares operator based mutant selection to random mutant selection.
-They compare three diffrent operator based selection techniques from Offutt et al., Barbosa et al., and Namin et al.
-against random mutant selection, with equal mutant probability, and equal mutagen probaiblity.
-They find that none of these selection techniques are superior to random selection, with same number of mutants.
-They also find that equal mutation sampling is more effective for larger subjects compared to equal mutagen sampling and the reverse is true for smaller subjects.
-A second paper by Zhang et al.\cite{zhang2013ase} investigates 8 sampling strategies on top of operator based mutant selection.
-They find that sampling strategies based on programming elements (method based) performed best.
-% Baseline : x\% from selected set
-% MOP : x\% from each mutagen
-% for these, it is sampled from operator based selected set.
-% PLEm : x\% from inside the same program element.
-% PLE + MOP: sample x\% from same mutagen from same element.
-
-% On Mutation and Dataflow : W.E Eong
-Wong et al~\cite{wong1994on} suggests random sampling of mutants from the complete population.
-
-Wong and Mathur suggests constrained mutation~\cite{} which chooses specific mutation operators only.
-
-% Empirical Evaluation of the Statement Deletion Mutation Operator : Offutt
-Deng et al~\cite{deng2013empirical} considers the effect of using a single mutation operator -- the statement deletion operator. They define deletion for different language elements,
-
-\section{Methodology}
-We collected a random sample of Java programs from Github\cite{github} that utilized the Maven\cite{maven} system for building.
-Next, we selected those programs from this set that passed all the unit test cases within them.
-We ran mutation analysis on this set of projects using PIT\cite{pitest}, with the mutators selected set to {\it all}.
-Because of the limitations of using a bytecode mutation engine, we could not implement statement deletion directly.
-Instead, we made use of the following mutation operators, that closely approximated statement deletion operator -- remove void method calls, remove non void method calls, remove conditionals, remove member variable assignments, remove increments and decrements.
-Finally, we modified the mutation engine to only choose one random mutation per line out of the set of applicable mutants for that line.
-For the second phase, we looked at the ratio between the number of mutants produced by the set of operators corresponding to statement deletion, and that of the random line mutants, and used this as a probability to add the mutants for the random line set.
-This was done to ensure that the results from the random sampling and statement deletion could be compared.
-
-\subsection{Probes}
-% half_per_line half_per_method :  + halfrand-project
-%   For each (line|method|class), get the number of mutants produced. Then sample exactly half the mutants produced per unit
-
-\section{Analysis}
+\input{related}
+\input{methodology}
+\input{analysis}
 

### 2014-03-05 src/paper.Rnw
udpate

@@
 o <- subset(stats.df, kind == 'original')
-o.x <- subset(o, select=c('operator', 'r.square', 'mutant.reduction', 'sample', 'score.multiplier'))
-colnames(o.x) <- c('operator', 'r^2', 'm.red', 'sample', 'mcov.mult')
+o.x <- subset(o, select=c('operator', 'r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier'))
+colnames(o.x) <- c('operator', 'r^2', 'm.red', 'm.sd', 'num', 'B*')
 print(xtable(o.x, caption='Original', label='table:try1'), include.rownames=FALSE)
@@
 r <- subset(stats.df, kind == 'randoop')
-r.x <- subset(r, select=c('operator','r.square', 'mutant.reduction', 'sample', 'score.multiplier'))
-colnames(r.x) <- c('operator', 'r^2', 'm.red', 'sample', 'mcov.mult')
+r.x <- subset(r, select=c('operator','r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier'))
+colnames(r.x) <- c('operator', 'r^2', 'm.red','m.sd', 'num', 'B*')
 print(xtable(r.x, caption='Randoop', label='table:try1'), include.rownames=FALSE)

### 2014-03-05 src/intro.Rnw
update

\section{Introduction}

% 1. Describe the problem
% 2. State your contributions

TODO: Mutation analysis is a transformation of programs that generates several mutants 
Mutation analysis originally proposed by Lipton\cite{lipton1971fault} involves systematic transformation of program through introduction of first order syntactical changes\cite{ammann2008introduction}. Researchers have shown that the mutations thus introduced behave similarly to the real faults\cite{andrews2005mutation}, and hence can be used as a stand-in for real faults when determining the efficacy of a test suite against faults.

Programs can be modified in many different ways to generate mutants, thus, the set of 
possible mutants of programs can be very large introducing a high computational cost.
The computational cost has hindered wider use of mutation analysis.

Several studies has tried to devise techniques to reduce the cost of mutational analysis.
\begin{comment}
  Offut \cite{offutt2001mutation} classifies these techniques into the following three categories:
  \begin{enumerata}
  \item \emph{Do fewer}: techniques that try to reduce the number of mutants.
  \item \emph{Do faser}: techniques that 
  \item \emph{Do smarter}: techniques that 
  \end{enumerate}
\end{comment}
One of the main approaches is selective mutation which reduces the set of mutagens\footnote{We use the terms mutagens 
and mutation operators interchangably hereafter.}.
Mathur \cite{} reduced the number of mutagens in Mothra \cite{Mothra} by omitting two operators. 
Offutt et al.\cite{offutt1993anexperimental} further omitted upto six oprators from the 
mutagens and observed negligible loss of effectiveness in mutation analysis. 
Unch\cite{untch2009onreduced} and more recently Deng et al.\cite{deng2013empirical} suggest
that using only statement deletion operator gives a close approximation of original mutation score.

While some studies try to 
find the \emph{sufficient} subset of mutagens, like\cite{siami2008sufficient}, others 
have suggested that \emph{random} selection of mutants works as fine, e.g. \cite{zhang2010operator}.
Some approaches combine the selective mutation selection and random selection, e.g. \cite{zhang2013ase}.

\begin{comment}
  These approach relies on the fact that some of the mutagens generate a large number of variants, and hence produce highly redundant test cases. Previous research suggested that elimination of mutagens with high fertility results in the reduction of total number of mutations produced, and hence reduces the computational requirements.

  % TODO check the survey again on selective mutation.

  It was recently questioned whether this approach indeed resulted in a tangible improvement over random selection of mutants\cite{zhang2010operator}, which did not find operator based selection to be better than random selection.

  Another research, initially by Unch\cite{untch2009onreduced} and recently by Deng et al.\cite{deng2013empirical} suggests using software deletion operator since it produces the least number of mutants (smallest neighborhood). The researchers were able to obtain a close approximation of original mutant score with significant savings with this approach.

  However, our previous research suggests that mutation coverage is closely predicted by statement coverage, this suggests that any criteria that forces accounting of the impact of each statement should provide a close approximation to the full mutation score. Hence, our research suggests that SDL works because it forces accounting of each line, and a random sampling criteria that provides the same criteria should result in similar results.

  In our analysis, we find that a random sampling approach that randomly chose a single mutant per line was found to have a better correlation with the full mutation score than that obtained by SDL. Further it was also found that the mutation score produced by random sampling was closer to the full mutation score than that produced by SDL.
\end{comment}

In this paper, we study the effects of different mutation selection and sampling on the effictiveness of 
mutation analysis and the computational costs. We have used more than 107 real world projects for our
experiments.

This paper follows in this order: Section \ref{sec:methodology} describes the methodology.
Section \ref{sec:implementation} explain our experiment setting and implemetation.
Results of experiments are summarized in Section{sec:results}. Section \ref{sec:anaysis}
provides analysis of the results. Section \ref{sec:related} provides the related work. 
Finally, Section \ref{sec:conclusion} concludes the paper.

### 2014-03-05 src/related.Rnw
update

\section{Related Work}
\label{sec:related}
Mathur\cite{mathur1991performance, wong1993mutation, wong1995reducing} first mentioned the idea of constrained mutation in a one-pager. This was taken up by Offut et al.\cite{offutt1993experimental}. (Offutt states in his 1993 paper\cite{offutt1993experimental} that Mathur has in 1991\cite{mathur1991performance} suggested the constrined/selective mutation. However, that paper does not propose it at all. It says we are experimenting with an idea, and that is it. It is in 1995\cite{wong1995reducing} that the idea is actually proposed, notably after Offutt has written about its effectiveness. $\ddot\smile$ - time travel?). The idea is that normal mutation has quadratic complexity on variable references while eliminatng the most fecund mutagens (SVR and ASR) achieves linear complexity on program size, while still approximating the full mutation score closely. They propose N-selective mutation which avoids N most fertile mutagens. Wong \cite{wong1995reducing} compares the effect of x\% mutation selection, and abs/ror constrained mutation. According to Wong, this is different from selective mutation in that only the most fecund operators are included rather than excluded. He finds that there is no evidence to suggest one over the other. Offutt\cite{offutt1993experimental} does not compare the effectivenss of selective mutation with x\% mutation. He also defines the concept of {\it operator strength} for an operator, which is defined as the total number of mutants that are killed by test data that is generated to kill only the mutants generated by that operator. He further posits that the mutagens with greatest strength may be the most useful ones. %(test data generated to eliminate variants of one operator may remove the mutants of other kinds too.)
This is taken up later by Mresa\cite{mresa1999efficiency} et al. who used the cost of detection of mutants as a means of selection, and uses it to define another set of operators (san, aor, sdl, ror, uoi). They also find that if very high mutation score close to 100\% is required, x\% selective mutation is better than operator selection, and conversely for less stringent scores, operator selection would be better if const of mutant is considered.

Barbosa et. al.\cite{barbosa2001toward} provides a set of guidelines for selecting mutagens.

Namin et al.\cite{namin2006finding,siami2008sufficient} treats the operator selection as a variable reduction problem, and applying statistical approaches, finds 28 operators from a total of 108 operators that are sufficient for an adequate test suite.

Offutt\cite{offutt1996anexperimental} following the previous paper\cite{offutt1993experimental} compares the effectiveness of selecting different operators. He divides the total operators into operand, operation, and statement categories, with es-selective avoiding operands, rs-selective avoiding operations, and re-selective avoiding statements, and e-selective only operations. He finds that using only operation based mutation operators (numbering 5) is sufficient for close approximation of full mutation score. He suggests that the reason they are effective is that most statements contain operators. He further posits that another reason is the amount of semantic change accomplished by an operator, and perhaps the most interesting ones are those that produce the smallest semantic difference.
% Replacement of Operand , Statement modification, Expression Modification: modify operators, ES-selective : not using operand, RS-Selective: not using expression, RE-Selective: not uinsg statement, E-selective : only expression..

Unch\cite{untch2009onreduced} suggested using a single mutagen statement deletion. He compares the statement deletion with other selective mutagen sets, and finds statement deletion operator to provide the best prediction of original mutation score ($R^2 = 0.97$)
This was carried forward by Deng et al\cite{deng2013empirical}, (according to whom, random sampling was weak when it was made low enough for appreciable mutant savings). They realize a mean mutation score of 92\% for adequate test suites with SDL alone, and generating a saving of 81\% in the number of mutants, and 41\% fewer equivalent mutants.

Zhang et al.\cite{zhang2010operator}, compares operator based mutant selection to random mutant selection. They compare three diffrent operator based selection techniques from Offutt et al., Barbosa et al., and Namin et al. against random mutant selection, with equal mutant probability, and equal mutagen probaiblity. They find that none of these selection techniques are superior to random selection, with same number of mutants. They also find that equal mutation sampling is more effective for larger subjects compared to equal mutagen sampling and the reverse is true for smaller subjects.
A second paper by Zhang et al.\cite{zhang2013ase} investigates 8 sampling strategies on top of operator based mutant selection. They find that sampling strategies based on programming elements (method based) performed best.
% Baseline : x\% from selected set
% MOP : x\% from each mutagen
% for these, it is sampled from operator based selected set.
% PLEm : x\% from inside the same program element.
% PLE + MOP: sample x\% from same mutagen from same element.

% On Mutation and Dataflow : W.E Eong
Wong et al~\cite{wong1994on} suggests random sampling of mutants from the complete population.

Wong and Mathur suggests constrained mutation~\cite{} which chooses specific mutation operators only.

% Empirical Evaluation of the Statement Deletion Mutation Operator : Offutt
Deng et al~\cite{deng2013empirical} considers the effect of using a single mutation operator -- the statement deletion operator. They define deletion for different language elements,

### 2014-03-05 src/results.Rnw
update

--- 2014-03-05 src/paper.Rnw
@@
-\newcommand*\per{\scalebox{.5}{\%}}
-\newcommand\Mua{Mutation analysis~}
-\newcommand\mua{mutation analysis~}
-\begin{comment}
-<<setup, include=FALSE, cache=FALSE, message=FALSE, echo=FALSE>>=
-clean <- function(x)sub('CONSTRUCTOR','CONSTR',sub('RETURN','R',sub('INCREMENTS','INC',sub('VOID','V',sub('CONDITIONAL','COND',sub('NON','N',sub('VARIABLE','VAR',sub('MEMBER','MEM',sub('DELETE_','D_',sub('REMOVE_','R_',sub('NEGATE_','N_',sub('_CALLS','',sub('EXPERIMENTAL_','E_',x)))))))))))))
-#options(warn=-1)
-options(digits=3)
-opts_chunk$set(fig.path='figure/twocolumn-', fig.align='center', fig.show='hold', echo=FALSE)
-render_listings()
-logit<-function(x) log(x/(1-x))
-require(reshape2)
-require(xtable)
-require(Mutsel)
-@
-<<chunk-hook, echo=2>>=
-<<setup>>
-v=data(package='Mutsel')
-data(list = v$results[,3])
-@
-\end{comment}
-
-% <<a,message=F, echo=F>>=
-% require(xtable)
-% require(data.table)
-% load('data/mu.rda')
-% @
-
-% 10 pages for the main text + 1 for references.
-<<>>=
-data(o.dist.all)
-data(o.dist.det)
-data(r.dist.all)
-data(r.dist.det)
-@
-\input{intro}
-
-\input{related}
-\input{methodology}
-\input{analysis}
-
-\subsection{Operators}
-
-\subsection{Occurrence of Operators}
-\begin{figure*}[t]
-<<op,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-par(las=1,mfrow = c(1, 2),mar=c(2,8,1,1))
-o.all <- cbind(projects = rownames(o.dist.all), stack(o.dist.all))
-o.all$ind <- clean(o.all$ind)
-bcol <- '#2171B5'
-#bcol <- 'darkgray'
-icol <- '#9ECAE0'
-#icol <- 'lightgray'
-o.det <- cbind(projects = rownames(o.dist.det), stack(o.dist.det))
-o.det$ind <- clean(o.det$ind)
-with(o.det,boxplot(values~ind,horizontal=T,border=c(bcol), col=icol, pch='.', axes=F, ylim=c(0,0.6)))
-with(o.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Original', cex.axis=0.8, ylim=c(0,0.6),add=T))
-
-r.all <- cbind(projects = rownames(r.dist.all), stack(r.dist.all))
-r.all$ind <- clean(r.all$ind)
-r.det <- cbind(projects = rownames(r.dist.det), stack(r.dist.det))
-r.det$ind <- clean(r.det$ind)
-with(r.det,boxplot(values~ind,horizontal=T,border=c(bcol), col=icol, pch='.', axes=F,ylim=c(0,0.6)))
-with(r.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Randoop', cex.axis=0.8,ylim=c(0,0.6),add=T))
-@
-\caption{Relative fertility of mutation operators. The blue shade represent detected mutants, while black represents total mutants.}
-\label{fig:op}
-\end{figure*}
-
-\subsection{SDL vs Random selection}
-\begin{figure*}[t]
-<<sdl.1,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-par(mfrow=c(2,2))
-with(o.pit.all, plot(all.cov~TSDL.cov, pch='+', main='Original SDL'))
-with(o.pit.all, plot(all.cov~x1_per_line.cov, pch='+', main='Original 1 per line'))
-with(r.pit.all, plot(all.cov~TSDL.cov, pch='+', main='Randoop SDl'))
-with(r.pit.all, plot(all.cov~x1_per_line.cov, pch='+', main='Randoop 1 per line'))
-@
-\label{fig:sdl1}
-\caption{Statement Deletion vs One per line.}
-\end{figure*}
-
-<<results='asis'>>=
-o <- subset(stats.df, kind == 'original')
-o.x <- subset(o, select=c('operator', 'r.square', 'mutant.reduction', 'sample', 'score.multiplier'))
-colnames(o.x) <- c('operator', 'r^2', 'm.red', 'sample', 'mcov.mult')
-print(xtable(o.x, caption='Original', label='table:try1'), include.rownames=FALSE)
-# , sanitize.text.function = function(x){x}, include.rownames=FALSE)
-@
-<<results='asis'>>=
-r <- subset(stats.df, kind == 'randoop')
-r.x <- subset(r, select=c('operator','r.square', 'mutant.reduction', 'sample', 'score.multiplier'))
-colnames(r.x) <- c('operator', 'r^2', 'm.red', 'sample', 'mcov.mult')
-print(xtable(r.x, caption='Randoop', label='table:try1'), include.rownames=FALSE)
-@
-
-\subsection{Correlation Analysis}
-
-$ \mu\{ M_{all}| M_{sample} \} = 0 + \beta_1 \times M{sample}  $
-
-The interesting part is (1) the $\beta_1$ coefficient which tells how much we must multiply the  sampled/selected score to get original score, and $R^2$ which tells us how close the score is.
-
-\subsubsection{sdl.mut.avg and mut.avg}
-
-% <<>>=
-% c <- cor(subset(m, select=c(sdl.mut.avg, mut.avg)) , method="kendall", use="pairwise")['sdl.mut.avg', 'mut.avg']
-% d <- cor(subset(m, select=c(lrnd.mut.avg, mut.avg)) , method="kendall", use="pairwise")['lrnd.mut.avg', 'mut.avg']
-% @
-
-$ \mu_\{M_{all} | M_{sdl}\} = Sexpr{sdl.est} \times M_{sdl} \text{ : } R^2 = Sexpr{sdl.r} \text{,} \tau_{\beta} = Sexpr{c}$
-
-\subsubsection{lrnd.mut.avg and mut.avg}
-
-$ \mu_\{M_{all} | M_{rnd}\} = Sexpr{rnd.est} \times M_{rnd} \text{ : } R^2 = Sexpr{rnd.r} \text{,} \tau_{\beta} = Sexpr{d}$
-
-\subsection{Regression Analysis}
-The next question we will tackle is if there exist a difference at all between SDL mutagen and the random sampling.
-We can perform two statistical tests to answer this question.
-For the first, we run a simple paired t-test.
-
-%<<>>=
-%s <- t.test(lrnd.mut.avg, sdl.mut.avg, paired=T)
-%@
-
-The paired t-test failed to sufficient difference between the two distributions with a two-sided p-value of Sexpr{s.p.value}.
-That is, we do not have sufficient evidence to conclude that the two distributions are different.
-
-The second approch is convoluted (I am a little unclear here.). We try to predict the original mutation score using the mutation score from both sdl and random sampling.
-Our full model is
-
-$ \mu_\{M_{all} | M_{sdl}, M_{rnd}\} = 0 + \beta_1 {sdl} + \beta_2 M_{rnd} + \beta_3 M_{sdl} M_{rnd}  $
-\begin{small}
-% <<results='asis'>>=
-% s <- subset(m, select=c(mut.avg,sdl.mut.avg))
-% s$type <- 'sdl'
-% colnames(s) <- c('mut', 'sample', 'type')
-% r <- subset(m, select=c(mut.avg,lrnd.mut.avg))
-% r$type <- 'rnd'
-% colnames(r) <- c('mut', 'sample', 'type')
-% all <- rbind(s, r)
-% fm <- with(all, lm(mut ~ sample + type + sample:type))
-% sm <- anova(fm)
-% print(xtable(sm,caption="My caption"), size="\\small")
-% @
-\end{small}
-
-We see that both type and sample:type are non-significant for predicting the final model, and sequentially removing them does not change the effectiveness.
-Hence, the techniques random sampling and statement deletion operator do not have any difference.
-
-\begin{figure*}[t]
-% <<tplots, fig.width=5, fig.height=5, out.width='.45\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-% t_f <- sdl.time~lrnd.time
-% plot(t_f, main='SDL ~ RND',pch='*')
-% abline(lm(t_f), col='red')
-% detach(m)
-% @
-\caption{Time}
-\label{fig:caddrm}
-\end{figure*}
-
 \section{Results}
-
+\label{sec:results}
 We see from the data that random sampling has a higher $R^2$, and also approximates the all  mutations score better.

### 2014-03-05 src/methodology.Rnw
update

\section{Methodology}
\label{sec:methodology}
%We collected a random sample of Java programs from Github\cite{github} that utilized the Maven\cite{maven} system for building. Next, we selected those programs from this set that passed all the unit test cases within them. We ran mutation analysis on this set of projects using PIT\cite{pitest}, with the mutators selected set to {\it all}. Because of the limitations of using a bytecode mutation engine, we could not implement statement deletion directly. Instead, we made use of the following mutation operators, that closely approximated statement deletion operator -- remove void method calls, remove non void method calls, remove conditionals, remove member variable assignments, remove increments and decrements. Finally, we modified the mutation engine to only choose one random mutation per line out of the set of applicable mutants for that line. For the second phase, we looked at the ratio between the number of mutants produced by the set of operators corresponding to statement deletion, and that of the random line mutants, and used this as a probability to add the mutants for the random line set. This was done to ensure that the results from the random sampling and statement deletion could be compared.

Our selection of programs was driven by a few overriding concerns --- primarily
our results had to be as widely applicable as possible for real-world programs.
Secondly, we strived for a statistically significant result, reducing the amount
of variables present in the experiments. For this reason we chose a random sample
of Java projects from Github\cite{github} that uses the popular maven\cite{maven}
build system, that has been used elsewhere\cite{gopinath2014code}. This set of
projects comes in two flavors of test-suites. The original test-suites present in
a limited number of projects, and automatically generatd test-suites using randoop.
Due to the constraints in resources, we had to further reduce the programs and
test-suites to those that could finish the mutation run in 10 minutes. From this
set of test-suites, we sampled 110 suites each for both original and randoop
generated test-suiets. This gave us 81 unique projects for both original and randoop,
and remaining projects having both flavors of test suites.

We ran mutation analysis on this set of projects using PIT\cite{pitest}. However,
since the operators provided by PIT are limited, we extended PIT to provide newer
operators that are similar to operators provided by other mutation systems.

<<opstable,results='asis'>>=
op=c(
'INVERT-NEGS',
'RETURN-VALS',
'MATH',
'VOID-M-CALLS',
'NEGATE-COND',
'COND-BOUNDARY',
'INCREMENTS',
'NV-M-CALLS',
'CONSTR-CALLS',
'INLINE-CONSTS',
'REMOVE-INCR',
'E-MEMBER-VAR',
'E-SWITCH',
'RM-SWITCH',
'REMOVE-COND',
'DELETE-COND')
expl=c(
'Invert negatives',
'Change return values',
'Modify arithmetic operators',
'Remove void method calls',
'Negate conditional statements',
'Modify boundary conditions',
'Modify increment/decrement',
'Replace non-void method calls',
'Replace constructor calls',
'Replace inline constants',
'Remove increment/decrement',
'Replace member variable assignments',
'Modify switch statements',
'Remove switch elements*',
'Make conditionas true',
'Make conditionas false*')
op.df <- data.frame(Operator=op, Explanation=expl)
print(xtable(op.df,caption='PIT Mutation Opeators (* indicates new opeators)', label='table:pitop'), sanitize.text.function  = function(x){x}, include.colnames=FALSE, include.rownames=F)
@
\subsection{Probes}
% half_per_line half_per_method :  + halfrand-project
%   For each (line|method|class), get the number of mutants produced. Then sample exactly half the mutants produced per unit

### 2014-03-05 src/methodology.Rnw
update

@@
 since the operators provided by PIT are limited, we extended PIT to provide newer
-operators that are similar to operators provided by other mutation systems.
+operators that are similar to operators provided by other mutation systems. The set
+of operators provided by PIT are provided in Table~\ref{tbl:pitop}.
+
+Further, we also modified PIT to provide random selection of mutants according to
+various criterias.
 
@@
 'INCREMENTS',
-'NV-M-CALLS',
+'NVOID-M-CALLS',
 'CONSTR-CALLS',
 'INLINE-CONSTS',
-'REMOVE-INCR',
+'RM-INCR',
 'E-MEMBER-VAR',
@@
 'RM-SWITCH',
-'REMOVE-COND',
+'RM-COND',
 'DELETE-COND')
@@
 @
+
+One of our research questions was to compare the utility of operator
+selection --- especially statement deletion --- with random sampling of mutants,
+Since we use PIT, which is a bytecode oriented mutation engine, implementing statement deletion
+directly is very hard. However, we can approximate statement deletion by combining different
+bytecode operators, as given below.
+
+The basic statement deletion was mdeled on the work by Deng et al.~\cite{deng2013empirical}. The operations
+on single statements was modeled using \textit{VOID-M-CALLS,NONV-M-CALLS,CONSTR-CALLS,E-MEMBER-VAR,RM-INCR} for simple statements, and using \textit{RM-COND} for control structures, which replaced the boolean condition with false, resulting in removal of the block of statements.
+The operator for return values was modeled using \textit{RETURN-VALS}, which is similar.
+The operators for \textit{while,for}, and \textit{if} statements were modeled using \textit{DELETE-COND}, which replaced the boolean condition with true, which removed the effect of conditional.
+The \textit{switch} statement deletion was modeled using \textit{RM-SWITCH} which replaced the first 100 labels with default label, resulting in the switch element getting deleted.
+(Due to the constraints of the architecture of PIT only the first 100 labels were replaced).
 \subsection{Probes}
-% half_per_line half_per_method :  + halfrand-project
-%   For each (line|method|class), get the number of mutants produced. Then sample exactly half the mutants produced per unit

### 2014-03-05 src/methodology.Rnw
update

@@
 (Due to the constraints of the architecture of PIT only the first 100 labels were replaced).
+The \textit{try catch} was not necessary at bytecode level.
+Finally, to get an accurate estimation of the effect of true statement deletion, we grouped the mutants by line, and considered a single virtual mutant (That is, the total number of mutants is equal to the total number of lines).
+Further, killing any mutant from a line resulted in marking the virtual mutant for that line as killed.
+This gave us the mutation score for the virtual statement deletion operator.
+We note that the approximation of simple statement deletion, especially when arithmetic operators are involved is not complete.
+However, as seen in Figure~\ref{fig:op}, the number of mutants produced by \textit{MATH} operator is very small.
+We also note that our approximation does not account for the increase in ease of detection when multiple mutations are combined together (ref: coupling effect).
+This also means that not all the lines may be mutated since there may be no applicable operators.
+However, given the constraints of a bytecode based mutation system, we believe that our procedure is reasonable.
+
 \subsection{Probes}

### 2014-03-05 src/methodology.Rnw
pdate

@@
 
-\subsection{Probes}
+\subsection{Sampling Criterias}
+
+We used several different sampling criterias.
+The simplest one consisted of using x\% selection as suggested by Wong et al.~\cite{wong1995reducing}.
+Next, we looked at choosing x\% per program elements such as blocks, lines, method, and classes.
+Then in the interests of comparison to statement deletion operator, we chose the number of lines per program elements as the sampling criteria.
+We next extended this criteria by sampling the mutants thus produced again by half, quarter etc.
+Next, we looked at the impact of simply selecting a single mutant per program element, and extended it by reducing that even further by half quarter etc.
+Finally, as with statement deletion, we approximated other statement selection operators discussed in the literature (Wong, Offutt96, Javalanche, Namin08) as the operator selection criteria.

### 2014-03-05 src/methodology.Rnw
update

@@
 op.df <- data.frame(Operator=op, Explanation=expl)
-print(xtable(op.df,caption='PIT Mutation Opeators (* indicates new opeators)', label='table:pitop'), sanitize.text.function  = function(x){x}, include.colnames=FALSE, include.rownames=F)
+print(xtable(op.df,caption='PIT Mutation Opeators (* indicates new opeators)', label='tbl:pitop'), sanitize.text.function  = function(x){x}, include.colnames=FALSE, include.rownames=F)
 @

### 2014-03-05 src/paper.Rnw
update

--- 2014-03-05 src/paper.Rnw
@@
 @
-\input{intro}
-
-\input{related}
-\input{methodology}
-\input{analysis}
-
-\subsection{Operators}
+<<test, child='intro.Rnw'>>=
+@
+<<test, child='related.Rnw'>>=
+@
+<<test, child='methodology.Rnw'>>=
+@
+<<test, child='analysis.Rnw'>>=
+@
 
@@
 \end{figure*}
-
 <<results='asis'>>=
 o <- subset(stats.df, kind == 'original')
-o.x <- subset(o, select=c('operator', 'r.square', 'mutant.reduction', 'sample', 'score.multiplier'))
-colnames(o.x) <- c('operator', 'r^2', 'm.red', 'sample', 'mcov.mult')
+o.x <- subset(o, select=c('operator', 'r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier'))
+colnames(o.x) <- c('operator', 'r^2', 'm.red', 'm.sd', 'num', 'B*')
 print(xtable(o.x, caption='Original', label='table:try1'), include.rownames=FALSE)
@@
 
+\begin{figure*}[t]
+\includegraphics[totalheight=6cm]{fig/original.pdf}
+\caption{Subsumption Original}
+\label{fig:subsumptiono}
+\end{figure*}[t]
+
+\begin{figure*}[t]
+\includegraphics[totalheight=6cm]{fig/randoop.pdf}
+\caption{Subsumption Randoop}
+\label{fig:subsumptionr}
+\end{figure*}[t]
+
 \section{Results}

### 2014-03-05 src/paper.Rnw
update

@@
 @
-<<test, child='intro.Rnw'>>=
+<<intro, child='intro.Rnw'>>=
 @
-<<test, child='related.Rnw'>>=
+<<related, child='related.Rnw'>>=
 @
-<<test, child='methodology.Rnw'>>=
+<<methodology, child='methodology.Rnw'>>=
 @
-<<test, child='analysis.Rnw'>>=
+<<analysis, child='analysis.Rnw'>>=
 @
@@
 
+<<results, child='results.Rnw'>>=
+@
+
+\begin{enumerate}
+\item [x] For op-selection to work, the distributions of mutations across different projects has to be similar enough. This can be checked by t-test.
+\item [TODO] We should check if the distribution significantly different too.
+\item [DONE] Use sampling
+\item [DONE] Check on randoop samples too
+\item [NO] Implement bomb (athrow) and see its mutation score, and see how close it comes.
+\item [DONE] Compare random selection with class, method, and mutagen sampling.
+\item [TODO] Report time for each, as cost.
+\item [TODOX] Find the mutant count to LOC multiplier, and use it to get the probability of choosing for each project.
+\end{enumerate}
 \section{Results}

### 2014-03-05 src/results.Rnw
update

@@
 The total mutants for all is Sexpr{sum(m.pit.mutation.total)}, for rnd is Sexpr{sum(m.lrnd.pit.mutation.total)} and for sdl is Sexpr{sum(m.sdl.pit.mutation.total)}
-
-\begin{enumerate}
-\item [x] For op-selection to work, the distributions of mutations across different projects has to be similar enough. This can be checked by t-test.
-\item [TODO] We should check if the distribution significantly different too.
-\item [DONE] Use sampling
-\item [DONE] Check on randoop samples too
-\item [NO] Implement bomb (athrow) and see its mutation score, and see how close it comes.
-\item [DONE] Compare random selection with class, method, and mutagen sampling.
-\item [TODO] Report time for each, as cost.
-\item [TODOX] Find the mutant count to LOC multiplier, and use it to get the probability of choosing for each project.
-\end{enumerate}

### 2014-03-05 src/paper.Rnw
update

@@
 <<results='asis'>>=
-o <- subset(stats.df, kind == 'original')
+oprand <- subset(stats.df,!grepl('^..op', rownames(stats.df)))
+
+o <- subset(oprand, kind == 'original')
 o.x <- subset(o, select=c('operator', 'r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier'))
 colnames(o.x) <- c('operator', 'r^2', 'm.red', 'm.sd', 'num', 'B*')
-print(xtable(o.x, caption='Original', label='table:try1'), include.rownames=FALSE)
+print(xtable(o.x, caption='Original', label='table:rando'), include.rownames=FALSE)
 # , sanitize.text.function = function(x){x}, include.rownames=FALSE)
@@
 <<results='asis'>>=
-r <- subset(stats.df, kind == 'randoop')
+r <- subset(oprand, kind == 'randoop')
 r.x <- subset(r, select=c('operator','r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier'))
 colnames(r.x) <- c('operator', 'r^2', 'm.red','m.sd', 'num', 'B*')
-print(xtable(r.x, caption='Randoop', label='table:try1'), include.rownames=FALSE)
+print(xtable(r.x, caption='Randoop', label='table:randr'), include.rownames=FALSE)
+@
+
+<<results='asis'>>=
+opsel <- subset(stats.df,grepl('^..op', rownames(stats.df)))
+
+o <- subset(opsel, kind == 'original')
+o.x <- subset(o, select=c('operator', 'r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier'))
+colnames(o.x) <- c('operator', 'r^2', 'm.red', 'm.sd', 'num', 'B*')
+print(xtable(o.x, caption='Original', label='table:selo'), include.rownames=FALSE)
+# , sanitize.text.function = function(x){x}, include.rownames=FALSE)
+@
+<<results='asis'>>=
+r <- subset(opsel, kind == 'randoop')
+r.x <- subset(r, select=c('operator','r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier'))
+colnames(r.x) <- c('operator', 'r^2', 'm.red','m.sd', 'num', 'B*')
+print(xtable(r.x, caption='Randoop', label='table:selr'), include.rownames=FALSE)
 @

### 2014-03-07 etc/abstract.tex
update

@@
 Choosing a smaller subset of mutations to run is a simple approach that can alleviate this problem.
+There exist multiple ways to reduce the set of mutations to run.
+Operator selection has recently been in the focus.
+However recently researchers have found that sampling can achive accuracy and mutant reduction similar to operator selection.
 
 %2.Saywhyit’saninterestingproblem
-However, how best to choose among multiple selection criterias is an open problem, especially for real-world programs and test-suites.
+However, which sampling technique is best, is an open problem, especially for real-world programs and test-suites.
 
 %3.Saywhatyoursolutionachieves
-Our research compare a number of selection criteria along different dimensions including prediction of original mutation score, mutant reduction ratio, and time for completion.
+Our research compares a number of sampling criteria, and operator selection criteria based on their ability to approximate the full mutation score, and also the consistency of results.
 
 %4.Saywhatfollowsfromyoursolution
+Our experiments rank sampling criterias that can be used by testers according how much mutant reduction is achieved, their ability to predict the final mutation score, the relative effect of unit increase in sampled mutation score on the final score, and also the time required for the run.
 

### 2014-03-07 src/conclusion.Rnw
udpate

--- 2014-03-05 src/paper.Rnw
@@
-\newcommand*\per{\scalebox{.5}{\%}}
-\newcommand\Mua{Mutation analysis~}
-\newcommand\mua{mutation analysis~}
-\begin{comment}
-<<setup, include=FALSE, cache=FALSE, message=FALSE, echo=FALSE>>=
-clean <- function(x)sub('CONSTRUCTOR','CONSTR',sub('RETURN','R',sub('INCREMENTS','INC',sub('VOID','V',sub('CONDITIONAL','COND',sub('NON','N',sub('VARIABLE','VAR',sub('MEMBER','MEM',sub('DELETE_','D_',sub('REMOVE_','R_',sub('NEGATE_','N_',sub('_CALLS','',sub('EXPERIMENTAL_','E_',x)))))))))))))
-#options(warn=-1)
-options(digits=3)
-opts_chunk$set(fig.path='figure/twocolumn-', fig.align='center', fig.show='hold', echo=FALSE)
-render_listings()
-logit<-function(x) log(x/(1-x))
-require(reshape2)
-require(xtable)
-require(Mutsel)
-@
-<<chunk-hook, echo=2>>=
-<<setup>>
-v=data(package='Mutsel')
-data(list = v$results[,3])
-@
-\end{comment}
-
-% <<a,message=F, echo=F>>=
-% require(xtable)
-% require(data.table)
-% load('data/mu.rda')
-% @
-
-% 10 pages for the main text + 1 for references.
-<<>>=
-data(o.dist.all)
-data(o.dist.det)
-data(r.dist.all)
-data(r.dist.det)
-@
-<<test, child='intro.Rnw'>>=
-@
-<<test, child='related.Rnw'>>=
-@
-<<test, child='methodology.Rnw'>>=
-@
-<<test, child='analysis.Rnw'>>=
-@
-
-\subsection{Occurrence of Operators}
-\begin{figure*}[t]
-<<op,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-par(las=1,mfrow = c(1, 2),mar=c(2,8,1,1))
-o.all <- cbind(projects = rownames(o.dist.all), stack(o.dist.all))
-o.all$ind <- clean(o.all$ind)
-bcol <- '#2171B5'
-#bcol <- 'darkgray'
-icol <- '#9ECAE0'
-#icol <- 'lightgray'
-o.det <- cbind(projects = rownames(o.dist.det), stack(o.dist.det))
-o.det$ind <- clean(o.det$ind)
-with(o.det,boxplot(values~ind,horizontal=T,border=c(bcol), col=icol, pch='.', axes=F, ylim=c(0,0.6)))
-with(o.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Original', cex.axis=0.8, ylim=c(0,0.6),add=T))
-
-r.all <- cbind(projects = rownames(r.dist.all), stack(r.dist.all))
-r.all$ind <- clean(r.all$ind)
-r.det <- cbind(projects = rownames(r.dist.det), stack(r.dist.det))
-r.det$ind <- clean(r.det$ind)
-with(r.det,boxplot(values~ind,horizontal=T,border=c(bcol), col=icol, pch='.', axes=F,ylim=c(0,0.6)))
-with(r.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Randoop', cex.axis=0.8,ylim=c(0,0.6),add=T))
-@
-\caption{Relative fertility of mutation operators. The blue shade represent detected mutants, while black represents total mutants.}
-\label{fig:op}
-\end{figure*}
-
-\subsection{SDL vs Random selection}
-\begin{figure*}[t]
-<<sdl.1,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-par(mfrow=c(2,2))
-with(o.pit.all, plot(all.cov~TSDL.cov, pch='+', main='Original SDL'))
-with(o.pit.all, plot(all.cov~x1_per_line.cov, pch='+', main='Original 1 per line'))
-with(r.pit.all, plot(all.cov~TSDL.cov, pch='+', main='Randoop SDl'))
-with(r.pit.all, plot(all.cov~x1_per_line.cov, pch='+', main='Randoop 1 per line'))
-@
-\label{fig:sdl1}
-\caption{Statement Deletion vs One per line.}
-\end{figure*}
-<<results='asis'>>=
-o <- subset(stats.df, kind == 'original')
-o.x <- subset(o, select=c('operator', 'r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier'))
-colnames(o.x) <- c('operator', 'r^2', 'm.red', 'm.sd', 'num', 'B*')
-print(xtable(o.x, caption='Original', label='table:try1'), include.rownames=FALSE)
-# , sanitize.text.function = function(x){x}, include.rownames=FALSE)
-@
-<<results='asis'>>=
-r <- subset(stats.df, kind == 'randoop')
-r.x <- subset(r, select=c('operator','r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier'))
-colnames(r.x) <- c('operator', 'r^2', 'm.red','m.sd', 'num', 'B*')
-print(xtable(r.x, caption='Randoop', label='table:try1'), include.rownames=FALSE)
-@
-
-\subsection{Correlation Analysis}
-
-$ \mu\{ M_{all}| M_{sample} \} = 0 + \beta_1 \times M{sample}  $
-
-The interesting part is (1) the $\beta_1$ coefficient which tells how much we must multiply the  sampled/selected score to get original score, and $R^2$ which tells us how close the score is.
-
-\subsubsection{sdl.mut.avg and mut.avg}
-
-% <<>>=
-% c <- cor(subset(m, select=c(sdl.mut.avg, mut.avg)) , method="kendall", use="pairwise")['sdl.mut.avg', 'mut.avg']
-% d <- cor(subset(m, select=c(lrnd.mut.avg, mut.avg)) , method="kendall", use="pairwise")['lrnd.mut.avg', 'mut.avg']
-% @
-
-$ \mu_\{M_{all} | M_{sdl}\} = Sexpr{sdl.est} \times M_{sdl} \text{ : } R^2 = Sexpr{sdl.r} \text{,} \tau_{\beta} = Sexpr{c}$
-
-\subsubsection{lrnd.mut.avg and mut.avg}
-
-$ \mu_\{M_{all} | M_{rnd}\} = Sexpr{rnd.est} \times M_{rnd} \text{ : } R^2 = Sexpr{rnd.r} \text{,} \tau_{\beta} = Sexpr{d}$
-
-\subsection{Regression Analysis}
-The next question we will tackle is if there exist a difference at all between SDL mutagen and the random sampling.
-We can perform two statistical tests to answer this question.
-For the first, we run a simple paired t-test.
-
-%<<>>=
-%s <- t.test(lrnd.mut.avg, sdl.mut.avg, paired=T)
-%@
-
-The paired t-test failed to sufficient difference between the two distributions with a two-sided p-value of Sexpr{s.p.value}.
-That is, we do not have sufficient evidence to conclude that the two distributions are different.
-
-The second approch is convoluted (I am a little unclear here.). We try to predict the original mutation score using the mutation score from both sdl and random sampling.
-Our full model is
-
-$ \mu_\{M_{all} | M_{sdl}, M_{rnd}\} = 0 + \beta_1 {sdl} + \beta_2 M_{rnd} + \beta_3 M_{sdl} M_{rnd}  $
-\begin{small}
-% <<results='asis'>>=
-% s <- subset(m, select=c(mut.avg,sdl.mut.avg))
-% s$type <- 'sdl'
-% colnames(s) <- c('mut', 'sample', 'type')
-% r <- subset(m, select=c(mut.avg,lrnd.mut.avg))
-% r$type <- 'rnd'
-% colnames(r) <- c('mut', 'sample', 'type')
-% all <- rbind(s, r)
-% fm <- with(all, lm(mut ~ sample + type + sample:type))
-% sm <- anova(fm)
-% print(xtable(sm,caption="My caption"), size="\\small")
-% @
-\end{small}
-
-We see that both type and sample:type are non-significant for predicting the final model, and sequentially removing them does not change the effectiveness.
-Hence, the techniques random sampling and statement deletion operator do not have any difference.
-
-\begin{figure*}[t]
-% <<tplots, fig.width=5, fig.height=5, out.width='.45\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-% t_f <- sdl.time~lrnd.time
-% plot(t_f, main='SDL ~ RND',pch='*')
-% abline(lm(t_f), col='red')
-% detach(m)
-% @
-\caption{Time}
-\label{fig:caddrm}
-\end{figure*}
-
-\begin{figure*}[t]
-\includegraphics[totalheight=6cm]{fig/original.pdf}
-\caption{Subsumption Original}
-\label{fig:subsumptiono}
-\end{figure*}[t]
-
-\begin{figure*}[t]
-\includegraphics[totalheight=6cm]{fig/randoop.pdf}
-\caption{Subsumption Randoop}
-\label{fig:subsumptionr}
-\end{figure*}[t]
-
-\section{Results}
-
-We see from the data that random sampling has a higher $R^2$, and also approximates the all  mutations score better.
-However, caveat emptor. There is a difference between the number of mutators for SDL and RAND. If our approximation was right, we should have gotten nearly same number of mutators. However
-The number of mutators in RND is
- Sexpr{sum(m.lrnd.pit.mutation.total) / sum(m.sdl.pit.mutation.total)} times SDL.
-
-The total mutants for all is Sexpr{sum(m.pit.mutation.total)}, for rnd is Sexpr{sum(m.lrnd.pit.mutation.total)} and for sdl is Sexpr{sum(m.sdl.pit.mutation.total)}
+\section{Conclusion}
+\label{sec:conclusion}
 

### 2014-03-07 src/intro.Rnw
udpate

@@
 % 2. State your contributions
+Mutation analysis is a method of evaluation of quality of test-suites. It involves generation
+of first (and higher) order mutants, and evaluating the effectiveness of test-suites against
+the generated mutants~\cite{lipton1971fault, ammann2008introduction}.
+Previous research~\cite{andrews2005mutation} has shown that mutations thus introduced behave
+similar to the real-faults.
 
-TODO: Mutation analysis is a transformation of programs that generates several mutants 
-Mutation analysis originally proposed by Lipton\cite{lipton1971fault} involves systematic transformation of program through introduction of first order syntactical changes\cite{ammann2008introduction}.
-Researchers have shown that the mutations thus introduced behave similarly to the real faults\cite{andrews2005mutation}, and hence can be used as a stand-in for real faults when determining the efficacy of a test suite against faults.
+A major impediment on the path to wide adoption of mutation analysis is its high cost of
+execution. A full mutation analysis requires running the test-suite against all the first
+order syntactical variants, and is prohibitive for even moderately large programs.
 
-Programs can be modified in many different ways to generate mutants, thus, the set of 
-possible mutants of programs can be very large introducing a high computational cost.
-The computational cost has hindered wider use of mutation analysis.
+A major strain of research into cost-reduction of mutation analysis is to choose a smaller
+representative set of mutants~\cite{offutt2001mutation,jia2011analysis}, often called the
+``do fewer'' approach. A major variant of this approach is the selective mutation strategy
+which advocates selecting a representative subset of operators based on heuristics and
+statistical analysis, and using them instead of the whole gamut of mutation
+operators~\cite{offutt1993anexperimental,untch2009onreduced}.
 
-Several studies has tried to devise techniques to reduce the cost of mutational analysis.
-\begin{comment}
-  Offut \cite{offutt2001mutation} classifies these techniques into the following three categories:
-  \begin{enumerata}
-  \item \emph{Do fewer}: techniques that try to reduce the number of mutants.
-  \item \emph{Do faser}: techniques that 
-  \item \emph{Do smarter}: techniques that 
-  \end{enumerate}
-\end{comment}
-One of the main approaches is selective mutation which reduces the set of mutagens\footnote{We use the terms mutagens 
-and mutation operators interchangably hereafter.}.
-Mathur \cite{} reduced the number of mutagens in Mothra \cite{Mothra} by omitting two operators. 
-Offutt et al.\cite{offutt1993anexperimental} further omitted upto six oprators from the 
-mutagens and observed negligible loss of effectiveness in mutation analysis. 
-Unch\cite{untch2009onreduced} and more recently Deng et al.\cite{deng2013empirical} suggest
-that using only statement deletion operator gives a close approximation of original mutation score.
+Another fertile area of research has been sampling strategies, where, a smaller representative
+sample is used in lieu.
+This was investigated first by Acreed~\cite{acree1980mutation} and Budd~\cite{budd1980mutation},
+who proposed using only $x$\% of the mutants produced. The studies by Wong and
+Mathur, found that random sampling with ratio as low as 10\% could provide
+accurate results~\cite{jia2011analysis}.
 
-While some studies try to 
-find the \emph{sufficient} subset of mutagens, like\cite{siami2008sufficient}, others 
-have suggested that \emph{random} selection of mutants works as fine, e.g. \cite{zhang2010operator}.
-Some approaches combine the selective mutation selection and random selection, e.g. \cite{zhang2013ase}.
+%Mathur \cite{} reduced the number of mutagens in Mothra \cite{Mothra} by omitting two operators.
+%Offutt et al.\cite{offutt1993anexperimental} further omitted upto six oprators from the
+%mutagens and observed negligible loss of effectiveness in mutation analysis.
+%Unch\cite{untch2009onreduced} and more recently Deng et al.\cite{deng2013empirical} suggest
+%that using only statement deletion operator gives a close approximation of original mutation score.
 
-\begin{comment}
-  These approach relies on the fact that some of the mutagens generate a large number of variants, and hence produce highly redundant test cases.
+%While some studies try to
+%find the \emph{sufficient} subset of mutagens, like\cite{siami2008sufficient}, others
+%have suggested that \emph{random} selection of mutants works as fine, e.g. \cite{zhang2010operator}.
+%Some approaches combine the selective mutation selection and random selection, e.g. \cite{zhang2013ase}.
+
+Finally, clustering of mutants~\cite{hussain08mutation} based on similar test cases has also
+been used successfully for mutant reduction. These are explained more in depth in Section~\ref{sec:related}
+
+While all these areas of research has been relatively successful in reducing the number of mutants
+produced, there has been comparitively few studies that compares the approaches taken. The studies
+that has been attempted so far, has been limited by the comparitively small number of sampled projects.
+
+Our contributions in this paper are the following. First, as described in Section~\ref{sec:methodology},
+we seek to improve the statistical confidence in our results by utilizing a much larger sample of projects
+(188 projects) from the open source repository at Github~\cite{github}, using both original and automatically
+generated test-suites using Randoop~\cite{randoop}. Second, as detailed in Section~\ref{sec:analysis}, we
+compare the reduction effectiveness of a large number of random sampling criterias (some of which are novel,
+and some that has been proposed by other researchers), and a some of the common operator selection
+criterias proposed in literature using statistical analysis. This provides us with insight for choosing
+mutation reduction techniqus according to the trade-offs in accuracy, and reduction ratios that a tester
+is willing to make for their specific requirements. This is detailed in Section~\ref{sec:results}.
+
+Our conclusion and recommendation for practicing testers are provided in Section~\ref{sec:conclusion}.
+
+% \begin{comment}
+%   These approach relies on the fact that some of the mutagens generate a large number of variants, and hence produce highly redundant test cases.
 Previous research suggested that elimination of mutagens with high fertility results in the reduction of total number of mutations produced, and hence reduces the computational requirements.
-
-  % TODO check the survey again on selective mutation.
-
-  It was recently questioned whether this approach indeed resulted in a tangible improvement over random selection of mutants\cite{zhang2010operator}, which did not find operator based selection to be better than random selection.
-
-  Another research, initially by Unch\cite{untch2009onreduced} and recently by Deng et al.\cite{deng2013empirical} suggests using software deletion operator since it produces the least number of mutants (smallest neighborhood).
+%
+%   % TODO check the survey again on selective mutation.
+%
+%   It was recently questioned whether this approach indeed resulted in a tangible improvement over random selection of mutants\cite{zhang2010operator}, which did not find operator based selection to be better than random selection.
+%
+%
+%   Another research, initially by Unch\cite{untch2009onreduced} and recently by Deng et al.\cite{deng2013empirical} suggests using software deletion operator since it produces the least number of mutants (smallest neighborhood).
 The researchers were able to obtain a close approximation of original mutant score with significant savings with this approach.
-
-  However, our previous research suggests that mutation coverage is closely predicted by statement coverage, this suggests that any criteria that forces accounting of the impact of each statement should provide a close approximation to the full mutation score.
+%
+%   However, our previous research suggests that mutation coverage is closely predicted by statement coverage, this suggests that any criteria that forces accounting of the impact of each statement should provide a close approximation to the full mutation score.
 Hence, our research suggests that SDL works because it forces accounting of each line, and a random sampling criteria that provides the same criteria should result in similar results.
-
-  In our analysis, we find that a random sampling approach that randomly chose a single mutant per line was found to have a better correlation with the full mutation score than that obtained by SDL.
+%
+%   In our analysis, we find that a random sampling approach that randomly chose a single mutant per line was found to have a better correlation with the full mutation score than that obtained by SDL.
 Further it was also found that the mutation score produced by random sampling was closer to the full mutation score than that produced by SDL.
-\end{comment}
-
-In this paper, we study the effects of different mutation selection and sampling on the effictiveness of 
-mutation analysis and the computational costs. We have used more than 107 real world projects for our
-experiments.
-
-This paper follows in this order: Section \ref{sec:methodology} describes the methodology.
-Section \ref{sec:implementation} explain our experiment setting and implemetation.
-Results of experiments are summarized in Section{sec:results}. Section \ref{sec:anaysis}
-provides analysis of the results. Section \ref{sec:related} provides the related work. 
-Finally, Section \ref{sec:conclusion} concludes the paper.
+%
+% Order of most fertile operators for N-selective operator selection.
+% NON_VOID_METHOD_CALLS
+% NEGATE_CONDITIONALS
+% REMOVE_CONDITIONALS
+% DELETE_CONDITIONALS
+% RETURN_VALS
+% INLINE_CONSTS
+% CONSTRUCTOR_CALLS
+% EXPERIMENTAL_MEMBER_VARIABLE
+% VOID_METHOD_CALLS
+% MATH
+% CONDITIONALS_BOUNDARY
+% INCREMENTS
+% REMOVE_INCREMENTS
+% RMSWITCH
+% EXPERIMENTAL_SWITCH
+% INVERT_NEGS
+%
+% \end{comment}
+%
+%

### 2014-03-07 src/paper.Rnw
udpate

@@
 @
-
-\begin{enumerate}
-\item [x] For op-selection to work, the distributions of mutations across different projects has to be similar enough. This can be checked by t-test.
-\item [TODO] We should check if the distribution significantly different too.
-\item [DONE] Use sampling
-\item [DONE] Check on randoop samples too
-\item [NO] Implement bomb (athrow) and see its mutation score, and see how close it comes.
-\item [DONE] Compare random selection with class, method, and mutagen sampling.
-\item [TODO] Report time for each, as cost.
-\item [TODOX] Find the mutant count to LOC multiplier, and use it to get the probability of choosing for each project.
-\end{enumerate}
-\section{Results}
-
-We see from the data that random sampling has a higher $R^2$, and also approximates the all  mutations score better.
-However, caveat emptor. There is a difference between the number of mutators for SDL and RAND. If our approximation was right, we should have gotten nearly same number of mutators. However
-The number of mutators in RND is
- Sexpr{sum(m.lrnd.pit.mutation.total) / sum(m.sdl.pit.mutation.total)} times SDL.
-
-The total mutants for all is Sexpr{sum(m.pit.mutation.total)}, for rnd is Sexpr{sum(m.lrnd.pit.mutation.total)} and for sdl is Sexpr{sum(m.sdl.pit.mutation.total)}
-
-\begin{enumerate}
-\item [x] For op-selection to work, the distributions of mutations across different projects has to be similar enough. This can be checked by t-test.
-\item [TODO] We should check if the distribution significantly different too.
-\item [DONE] Use sampling
-\item [DONE] Check on randoop samples too
-\item [NO] Implement bomb (athrow) and see its mutation score, and see how close it comes.
-\item [DONE] Compare random selection with class, method, and mutagen sampling.
-\item [TODO] Report time for each, as cost.
-\item [TODOX] Find the mutant count to LOC multiplier, and use it to get the probability of choosing for each project.
-\end{enumerate}
+<<results, child='conclusion.Rnw'>>=
+@

### 2014-03-07 src/methodology.Rnw
update

@@
 \label{sec:methodology}
-%We collected a random sample of Java programs from Github\cite{github} that utilized the Maven\cite{maven} system for building.
-Next, we selected those programs from this set that passed all the unit test cases within them.
-We ran mutation analysis on this set of projects using PIT\cite{pitest}, with the mutators selected set to {\it all}.
-Because of the limitations of using a bytecode mutation engine, we could not implement statement deletion directly.
-Instead, we made use of the following mutation operators, that closely approximated statement deletion operator -- remove void method calls, remove non void method calls, remove conditionals, remove member variable assignments, remove increments and decrements.
-Finally, we modified the mutation engine to only choose one random mutation per line out of the set of applicable mutants for that line.
-For the second phase, we looked at the ratio between the number of mutants produced by the set of operators corresponding to statement deletion, and that of the random line mutants, and used this as a probability to add the mutants for the random line set.
-This was done to ensure that the results from the random sampling and statement deletion could be compared.
+Our selection of programs was driven by a few overriding concerns. Our primary
+requirement was that, our results had to be as widely applicable as possible
+for real-world programs. Secondly, we strived for a statistically significant
+result, reducing the amount of variables present in the experiments. For this
+reason we chose a random sample of Java projects from Github\cite{github}
+that uses the popular maven\cite{maven} build system, that has been used
+elsewhere\cite{gopinath2014code}. This set of projects comes in two flavors
+of test-suites. The original test-suites present in a limited number of
+projects, and automatically generatd test-suites using randoop.  Due to the
+constraints in resources, we had to further reduce the programs and test-suites
+to those that could finish the mutation run in 10 minutes. From this set
+of test-suites, we sampled 110 suites each for both original and randoop
+generated test-suiets. This gave us 81 unique projects for both original
+and randoop, and remaining projects having both flavors of test suites.
 
-Our selection of programs was driven by a few overriding concerns --- primarily
-our results had to be as widely applicable as possible for real-world programs.
-Secondly, we strived for a statistically significant result, reducing the amount
-of variables present in the experiments. For this reason we chose a random sample
-of Java projects from Github\cite{github} that uses the popular maven\cite{maven}
-build system, that has been used elsewhere\cite{gopinath2014code}. This set of
-projects comes in two flavors of test-suites. The original test-suites present in
-a limited number of projects, and automatically generatd test-suites using randoop.
-Due to the constraints in resources, we had to further reduce the programs and
-test-suites to those that could finish the mutation run in 10 minutes. From this
-set of test-suites, we sampled 110 suites each for both original and randoop
-generated test-suiets. This gave us 81 unique projects for both original and randoop,
-and remaining projects having both flavors of test suites.
+We ran mutation analysis on this set of projects using
+PIT\cite{pitest}. However, since the operators provided by PIT are limited,
+we extended PIT to provide newer operators that are similar to operators
+provided by other mutation systems. The set of operators provided by PIT
+are provided in Table~\ref{tbl:pitop}.
 
-We ran mutation analysis on this set of projects using PIT\cite{pitest}. However,
-since the operators provided by PIT are limited, we extended PIT to provide newer
-operators that are similar to operators provided by other mutation systems. The set
-of operators provided by PIT are provided in Table~\ref{tbl:pitop}.
-
-Further, we also modified PIT to provide random selection of mutants according to
-various criterias.
+Further, we also modified PIT to provide random selection of mutants according
+to various criterias.
 
@@
 However, as seen in Figure~\ref{fig:op}, the number of mutants produced by \textit{MATH} operator is very small.
-We also note that our approximation does not account for the increase in ease of detection when multiple mutations are combined together (ref: coupling effect).
+We also note that our approximation does not account for the increase in ease of detection when multiple mutations are combined together due to coupling effect.
 This also means that not all the lines may be mutated since there may be no applicable operators.
@@
 We used several different sampling criterias.
+
+\subsubsection{x\% selection}
 The simplest one consisted of using x\% selection as suggested by Wong et al.~\cite{wong1995reducing}.
+In this criteria, we choose a specific fraction of the complete mutants.
+Following the suggestion of Zhang et al.~\cite{zhang2013ase}, we extend this criteria to sample mutants from within different program elements.
+We sampled x\% selection in the increasing order of scope, --- \textit{line}, \textit{method}, \textit{class}, and \textit{project} --- and decreasing fraction of total mutants -- \textit{1, 1/2, 1/4, 1/8, 1/16, 1/64}.
+
+While the sampling criteria is simple, it is not immediately clear when we are faced with program elements that produced too few mutants for a particular fraction to yield at-least one mutant.
+For example, for a line that produced 15 mutants, the number of mutants that can be chosen in \textit{(line, 1/64)} is less than 1.
+Our choices at this point are 1) to round the resulting number to the nearest integer, and choose that value as sampling (in effect, ignoring elements that are less complex), 2) to apply \textit{ceil} function to the resulting value, ensuring that there is atleast one mutant per program element, and 3) to perform the sampling in such a way that it chooses a mutant with with the fractional probability (this is the method followed by Zhang et al.~\cite{zhang2013ase}).
+
+\subsubsection{others}
 Next, we looked at choosing x\% per program elements such as blocks, lines, method, and classes.

### 2014-03-07 src/methodology.Rnw
update

@@
 For example, for a line that produced 15 mutants, the number of mutants that can be chosen in \textit{(line, 1/64)} is less than 1.
-Our choices at this point are 1) to round the resulting number to the nearest integer, and choose that value as sampling (in effect, ignoring elements that are less complex), 2) to apply \textit{ceil} function to the resulting value, ensuring that there is atleast one mutant per program element, and 3) to perform the sampling in such a way that it chooses a mutant with with the fractional probability (this is the method followed by Zhang et al.~\cite{zhang2013ase}).
+We analyzed the results of the following criterias: 1) to round the resulting number to the nearest integer, and choose that value as sampling (in effect, ignoring elements that are less complex), 2) to apply \textit{ceil} function to the resulting value, ensuring that there is atleast one mutant per program element, and 3) to perform the sampling in such a way that it chooses a mutant with with the fractional probability (this is the method followed by Zhang et al.~\cite{zhang2013ase}).
+
+\subsubsection{Lines per element}
+Our previous research~\cite{gopinath2014code} found that statement coverage was highly correlated with mutation coverage for a project.
+This immediately suggests that perhaps choosing one mutant per line may be sufficient to achieve a close approximation of the final mutation score.
+Further, statement deletion has been researched previously~\cite{untch2009onreduced,deng2013empirical} and has been found to reduce the number of mutants well, without an appreciable decrease in accuracy.
+This also provides a nice comparison with similar number of mutants between operator selection and random sampling of mutants.
 

### 2014-03-07 src/methodology.Rnw
update

@@
 
-\subsubsection{others}
-Next, we looked at choosing x\% per program elements such as blocks, lines, method, and classes.
-Then in the interests of comparison to statement deletion operator, we chose the number of lines per program elements as the sampling criteria.
-We next extended this criteria by sampling the mutants thus produced again by half, quarter etc.
-Next, we looked at the impact of simply selecting a single mutant per program element, and extended it by reducing that even further by half quarter etc.
-Finally, as with statement deletion, we approximated other statement selection operators discussed in the literature (Wong, Offutt96, Javalanche, Namin08) as the operator selection criteria.
+A simple extension of this approach is to extend this strategy as previously, by choosing as many number of mutants as there are number of lines in a program element, and we can extend it as before to sample \textit{1/2,1/4,1/8,1/16,1/32,1/64} of the mutants thus chosen.
+We chose the rounding strategy for fractional samples for simplicity.
+
+\subsubsection{One per element}
+An extremely simple strategy of sampling is to just choose one mutant per program element, which as before, we extended to include all the fractions \textit{1/2,1/4,1/8,1/16,1/32,1/64}.

### 2014-03-07 src/methodology.Rnw
update

@@
 While the sampling criteria is simple, it is not immediately clear when we are faced with program elements that produced too few mutants for a particular fraction to yield at-least one mutant.
-For example, for a line that produced 15 mutants, the number of mutants that can be chosen in \textit{(line, 1/64)} is less than 1.
+For example, for a line that produced 15 mutants, the number of mutants that can be chosen in \textit{(x\%, line, 1/64)} is less than 1.
 We analyzed the results of the following criterias: 1) to round the resulting number to the nearest integer, and choose that value as sampling (in effect, ignoring elements that are less complex), 2) to apply \textit{ceil} function to the resulting value, ensuring that there is atleast one mutant per program element, and 3) to perform the sampling in such a way that it chooses a mutant with with the fractional probability (this is the method followed by Zhang et al.~\cite{zhang2013ase}).
@@
 We chose the rounding strategy for fractional samples for simplicity.
+% TODO: Actually do the other rounding choices.
+
+Here too, we have a few choices when sampling mutants.
+We could either choose the fraction of mutants within the program element, or we could apply the sampling externally.
+For example, using $\lambda_E$ as number of lines in an element, for \textit{(lpe, $1/2$, method)}, we first get $1/2 \times \lambda_{Method}$ number of mutants from each method.
+The second alternative is to get $\lambda_{Method}$ number of mutants for all methods, then from this larger set, choose only half of the mutants.
 

### 2014-03-07 src/methodology.Rnw
update

@@
 An extremely simple strategy of sampling is to just choose one mutant per program element, which as before, we extended to include all the fractions \textit{1/2,1/4,1/8,1/16,1/32,1/64}.
+
+\subsection{Operator Reduction}
+% TODO expand as required
+
+For operator reduction, we utilized the constrained mutation operators suggested by Wong et al.~\cite{wong1995reducing}, Offutt et al.~\cite{offutt1996anexperimental,deng2013empirical}, % TODO Barbosa
+ and, Namin et al~\cite{siami2008sufficient}. Since Javalanche~\cite{javalanche} utilized operator selection mechanisms, we also compared the Javalanche operators for operator selection.
+
+\subsubsection{Constrained Mutation}
+For this criteria, we used the two operators \textit{COND\_BOUNDARY, and NEGATE\_COND} which are similar to those given by Wong.
+\subsubsection{Operator Selection}
+We used the operators given by Offutt et al.
+\textit{INVERT\_NEGS, MATH, COND\_BOUNDARY,} \textit{NEGATE\_COND}, those given by Javalanche \textit{NEGATE\_COND, VOID\_METHOD\_CALLS, NON\_VOID\_METHOD\_CALLS, MATH, INLINE\_CONSTS, E\_MEMBER\_VARIABLE},  and by Namin et al.\textit{INVERT\_NEGS, MATH, INCREMENTS, NEGATE\_COND}.
+We also  compare N-Selective mutation as suggested by Offutt et al.
+
+\subsection{Mutant Clustering}
+For mutant clustering, we were unable to directly apply clustering based on distinct mutants as suggested by Hussain~\cite{hussain2008mutation}.
+However, we were able to apply clustering techniques on mutation operators, thus turning it to a set of selected operators.

### 2014-03-07 src/methodology.Rnw
update

@@
 directly is very hard. However, we can approximate statement deletion by combining different
-bytecode operators, as given below.
-
-The basic statement deletion was mdeled on the work by Deng et al.~\cite{deng2013empirical}. The operations
-on single statements was modeled using \textit{VOID-M-CALLS,NONV-M-CALLS,CONSTR-CALLS,E-MEMBER-VAR,RM-INCR} for simple statements, and using \textit{RM-COND} for control structures, which replaced the boolean condition with false, resulting in removal of the block of statements.
-The operator for return values was modeled using \textit{RETURN-VALS}, which is similar.
-The operators for \textit{while,for}, and \textit{if} statements were modeled using \textit{DELETE-COND}, which replaced the boolean condition with true, which removed the effect of conditional.
-The \textit{switch} statement deletion was modeled using \textit{RM-SWITCH} which replaced the first 100 labels with default label, resulting in the switch element getting deleted.
-(Due to the constraints of the architecture of PIT only the first 100 labels were replaced).
-The \textit{try catch} was not necessary at bytecode level.
-Finally, to get an accurate estimation of the effect of true statement deletion, we grouped the mutants by line, and considered a single virtual mutant (That is, the total number of mutants is equal to the total number of lines).
-Further, killing any mutant from a line resulted in marking the virtual mutant for that line as killed.
-This gave us the mutation score for the virtual statement deletion operator.
-We note that the approximation of simple statement deletion, especially when arithmetic operators are involved is not complete.
-However, as seen in Figure~\ref{fig:op}, the number of mutants produced by \textit{MATH} operator is very small.
-We also note that our approximation does not account for the increase in ease of detection when multiple mutations are combined together due to coupling effect.
-This also means that not all the lines may be mutated since there may be no applicable operators.
-However, given the constraints of a bytecode based mutation system, we believe that our procedure is reasonable.
+bytecode operators, as explained later.
 
@@
 We analyzed the results of the following criterias: 1) to round the resulting number to the nearest integer, and choose that value as sampling (in effect, ignoring elements that are less complex), 2) to apply \textit{ceil} function to the resulting value, ensuring that there is atleast one mutant per program element, and 3) to perform the sampling in such a way that it chooses a mutant with with the fractional probability (this is the method followed by Zhang et al.~\cite{zhang2013ase}).
+% TODO: If the criterias ceil and round does not make sense, we might remove them to gain space.
 
@@
 
+\textit{Statement Deletion:}
+The basic statement deletion was modeled on the work by Deng et
+al.~\cite{deng2013empirical}. The operations on single statements was modeled
+using \textit{VOID-M-CALLS,NONV-M-CALLS,CONSTR-CALLS,E-MEMBER-VAR,RM-INCR}
+for simple statements, and using \textit{RM-COND} for control structures,
+which replaced the boolean condition with false, resulting in removal of
+the block of statements. The operator for return values was modeled using
+\textit{RETURN-VALS}, which is similar.  The operators for \textit{while,for},
+and \textit{if} statements were modeled using \textit{DELETE-COND},
+which replaced the boolean condition with true, which removed the effect
+of conditional. The \textit{switch} statement deletion was modeled using
+\textit{RM-SWITCH} which replaced the first 100 labels with default label,
+resulting in the switch element getting deleted. (Due to the constraints
+of the architecture of PIT only the first 100 labels were replaced). The
+\textit{try catch} was not necessary at bytecode level.  Finally, to get an
+accurate estimation of the effect of true statement deletion, we grouped
+the mutants by line, and considered a single virtual mutant (That is, the
+total number of mutants is equal to the total number of lines). Further,
+killing any mutant from a line resulted in marking the virtual mutant
+for that line as killed. This gave us the mutation score for the virtual
+statement deletion operator.  We note that the approximation of simple
+statement deletion, especially when arithmetic operators are involved is not
+complete. However, as seen in Figure~\ref{fig:op}, the number of mutants
+produced by \textit{MATH} operator is very small. We also note that our
+approximation does not account for the increase in ease of detection when
+multiple mutations are combined together due to coupling effect. This also
+means that not all the lines may be mutated since there may be no applicable
+operators. However, given the constraints of a bytecode based mutation system,
+we believe that our procedure is reasonable.
+
 \subsection{Mutant Clustering}

### 2014-03-07 src/paper.Rnw
update

@@
 
-o <- subset(oprand, kind == 'original')
+oprand.x <- subset(oprand,grepl('^.1x[0-9]+_per_', operator))
+oprand.l <- subset(oprand,!grepl('^.1x[0-9]+_per_', operator))
+@
+
+<<results='asis'>>=
+o <- subset(oprand.x, kind == 'original')
 o.x <- subset(o, select=c('operator', 'r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier'))
@@
 <<results='asis'>>=
-r <- subset(oprand, kind == 'randoop')
+r <- subset(oprand.x, kind == 'randoop')
+r.x <- subset(r, select=c('operator','r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier'))
+colnames(r.x) <- c('operator', 'r^2', 'm.red','m.sd', 'num', 'B*')
+print(xtable(r.x, caption='Randoop', label='table:randr'), include.rownames=FALSE)
+@
+
+<<results='asis'>>=
+o <- subset(oprand.l, kind == 'original')
+o.x <- subset(o, select=c('operator', 'r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier'))
+colnames(o.x) <- c('operator', 'r^2', 'm.red', 'm.sd', 'num', 'B*')
+print(xtable(o.x, caption='Original', label='table:rando'), include.rownames=FALSE)
+# , sanitize.text.function = function(x){x}, include.rownames=FALSE)
+@
+<<results='asis'>>=
+r <- subset(oprand.l, kind == 'randoop')
 r.x <- subset(r, select=c('operator','r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier'))

### 2014-03-07 src/paper.Rnw
update

@@
 with(o.pit.all, plot(all.cov~TSDL.cov, pch='+', main='Original SDL'))
-with(o.pit.all, plot(all.cov~x1_per_line.cov, pch='+', main='Original 1 per line'))
+with(o.pit.all, plot(all.cov~x1x1nl_per_line.cov, pch='+', main='Original 1 per line'))
 with(r.pit.all, plot(all.cov~TSDL.cov, pch='+', main='Randoop SDl'))
-with(r.pit.all, plot(all.cov~x1_per_line.cov, pch='+', main='Randoop 1 per line'))
+with(r.pit.all, plot(all.cov~x1x1nl_per_line.cov, pch='+', main='Randoop 1 per line'))
 @

### 2014-03-07 src/methodology.Rnw
udpate

@@
 
-\subsection{Operator Reduction}
+\subsection{Operator Selection}
 % TODO expand as required
@@
 
-\subsubsection{Constrained Mutation}
+\subsubsection{Criteria I}
 For this criteria, we used the two operators \textit{COND\_BOUNDARY, and NEGATE\_COND} which are similar to those given by Wong.
-\subsubsection{Operator Selection}
-We used the operators given by Offutt et al.
-\textit{INVERT\_NEGS, MATH, COND\_BOUNDARY,} \textit{NEGATE\_COND}, those given by Javalanche \textit{NEGATE\_COND, VOID\_METHOD\_CALLS, NON\_VOID\_METHOD\_CALLS, MATH, INLINE\_CONSTS, E\_MEMBER\_VARIABLE},  and by Namin et al.\textit{INVERT\_NEGS, MATH, INCREMENTS, NEGATE\_COND}.
+\subsubsection{Criteria II}
+We used the operators given by Offutt et al. \textit{INVERT\_NEGS, MATH, COND\_BOUNDARY,} \textit{NEGATE\_COND},
+\subsubsection{Criteria III}
+Those given by Javalanche \textit{NEGATE\_COND, VOID\_METHOD\_CALLS, NON\_VOID\_METHOD\_CALLS, MATH, INLINE\_CONSTS, E\_MEMBER\_VARIABLE}
+\subsubsection{Criteria IV}
+those given by Javalanche \textit{NEGATE\_COND, VOID\_METHOD\_CALLS, NON\_VOID\_METHOD\_CALLS, MATH, INLINE\_CONSTS, E\_MEMBER\_VARIABLE}
+\subsubsection{Criteria V}
+By Namin et al.\textit{INVERT\_NEGS, MATH, INCREMENTS, NEGATE\_COND}.
 We also  compare N-Selective mutation as suggested by Offutt et al.
-
-\textit{Statement Deletion:}
+\subsubsection{Criteria VI}
+By Namin et al.\textit{INVERT\_NEGS, MATH, INCREMENTS, NEGATE\_COND}.
+\subsubsection{Statement Deletion:}
 The basic statement deletion was modeled on the work by Deng et

### 2014-03-07 src/analysis.Rnw
update

--- 2014-03-07 src/paper.Rnw
@@
-\newcommand*\per{\scalebox{.5}{\%}}
-\newcommand\Mua{Mutation analysis~}
-\newcommand\mua{mutation analysis~}
-\begin{comment}
-<<setup, include=FALSE, cache=FALSE, message=FALSE, echo=FALSE>>=
-clean <- function(x)sub('CONSTRUCTOR','CONSTR',sub('RETURN','R',sub('INCREMENTS','INC',sub('VOID','V',sub('CONDITIONAL','COND',sub('NON','N',sub('VARIABLE','VAR',sub('MEMBER','MEM',sub('DELETE_','D_',sub('REMOVE_','R_',sub('NEGATE_','N_',sub('_CALLS','',sub('EXPERIMENTAL_','E_',x)))))))))))))
-#options(warn=-1)
-options(digits=3)
-opts_chunk$set(fig.path='figure/twocolumn-', fig.align='center', fig.show='hold', echo=FALSE)
-render_listings()
-logit<-function(x) log(x/(1-x))
-require(reshape2)
-require(xtable)
-require(Mutsel)
-@
-<<chunk-hook, echo=2>>=
-<<setup>>
-v=data(package='Mutsel')
-data(list = v$results[,3])
-@
-\end{comment}
-
-% <<a,message=F, echo=F>>=
-% require(xtable)
-% require(data.table)
-% load('data/mu.rda')
-% @
-
-% 10 pages for the main text + 1 for references.
-<<>>=
-data(o.dist.all)
-data(o.dist.det)
-data(r.dist.all)
-data(r.dist.det)
-@
-<<intro, child='intro.Rnw'>>=
-@
-<<related, child='related.Rnw'>>=
-@
-<<methodology, child='methodology.Rnw'>>=
-@
-<<analysis, child='analysis.Rnw'>>=
-@
-
+\section{Analysis}
+\label{sec:analysis}
 \subsection{Occurrence of Operators}
@@
 \end{figure*}[t]
-
-<<results, child='results.Rnw'>>=
-@
-<<results, child='conclusion.Rnw'>>=
-@

### 2014-03-07 src/paper.Rnw
update

--- 2014-03-07 src/paper.Rnw
@@
 @
-
-\subsection{Occurrence of Operators}
-\begin{figure*}[t]
-<<op,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-par(las=1,mfrow = c(1, 2),mar=c(2,8,1,1))
-o.all <- cbind(projects = rownames(o.dist.all), stack(o.dist.all))
-o.all$ind <- clean(o.all$ind)
-bcol <- '#2171B5'
-#bcol <- 'darkgray'
-icol <- '#9ECAE0'
-#icol <- 'lightgray'
-o.det <- cbind(projects = rownames(o.dist.det), stack(o.dist.det))
-o.det$ind <- clean(o.det$ind)
-with(o.det,boxplot(values~ind,horizontal=T,border=c(bcol), col=icol, pch='.', axes=F, ylim=c(0,0.6)))
-with(o.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Original', cex.axis=0.8, ylim=c(0,0.6),add=T))
-
-r.all <- cbind(projects = rownames(r.dist.all), stack(r.dist.all))
-r.all$ind <- clean(r.all$ind)
-r.det <- cbind(projects = rownames(r.dist.det), stack(r.dist.det))
-r.det$ind <- clean(r.det$ind)
-with(r.det,boxplot(values~ind,horizontal=T,border=c(bcol), col=icol, pch='.', axes=F,ylim=c(0,0.6)))
-with(r.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Randoop', cex.axis=0.8,ylim=c(0,0.6),add=T))
-@
-\caption{Relative fertility of mutation operators. The blue shade represent detected mutants, while black represents total mutants.}
-\label{fig:op}
-\end{figure*}
-
-\subsection{SDL vs Random selection}
-\begin{figure*}[t]
-<<sdl.1,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-par(mfrow=c(2,2))
-with(o.pit.all, plot(all.cov~TSDL.cov, pch='+', main='Original SDL'))
-with(o.pit.all, plot(all.cov~x1_per_line.cov, pch='+', main='Original 1 per line'))
-with(r.pit.all, plot(all.cov~TSDL.cov, pch='+', main='Randoop SDl'))
-with(r.pit.all, plot(all.cov~x1_per_line.cov, pch='+', main='Randoop 1 per line'))
-@
-\label{fig:sdl1}
-\caption{Statement Deletion vs One per line.}
-\end{figure*}
-<<results='asis'>>=
-oprand <- subset(stats.df,!grepl('^..op', rownames(stats.df)))
-
-o <- subset(oprand, kind == 'original')
-o.x <- subset(o, select=c('operator', 'r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier'))
-colnames(o.x) <- c('operator', 'r^2', 'm.red', 'm.sd', 'num', 'B*')
-print(xtable(o.x, caption='Original', label='table:rando'), include.rownames=FALSE)
-# , sanitize.text.function = function(x){x}, include.rownames=FALSE)
-@
-<<results='asis'>>=
-r <- subset(oprand, kind == 'randoop')
-r.x <- subset(r, select=c('operator','r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier'))
-colnames(r.x) <- c('operator', 'r^2', 'm.red','m.sd', 'num', 'B*')
-print(xtable(r.x, caption='Randoop', label='table:randr'), include.rownames=FALSE)
-@
-
-<<results='asis'>>=
-opsel <- subset(stats.df,grepl('^..op', rownames(stats.df)))
-
-o <- subset(opsel, kind == 'original')
-o.x <- subset(o, select=c('operator', 'r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier'))
-colnames(o.x) <- c('operator', 'r^2', 'm.red', 'm.sd', 'num', 'B*')
-print(xtable(o.x, caption='Original', label='table:selo'), include.rownames=FALSE)
-# , sanitize.text.function = function(x){x}, include.rownames=FALSE)
-@
-<<results='asis'>>=
-r <- subset(opsel, kind == 'randoop')
-r.x <- subset(r, select=c('operator','r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier'))
-colnames(r.x) <- c('operator', 'r^2', 'm.red','m.sd', 'num', 'B*')
-print(xtable(r.x, caption='Randoop', label='table:selr'), include.rownames=FALSE)
-@
-
-\subsection{Correlation Analysis}
-
-$ \mu\{ M_{all}| M_{sample} \} = 0 + \beta_1 \times M{sample}  $
-
-The interesting part is (1) the $\beta_1$ coefficient which tells how much we must multiply the  sampled/selected score to get original score, and $R^2$ which tells us how close the score is.
-
-\subsubsection{sdl.mut.avg and mut.avg}
-
-% <<>>=
-% c <- cor(subset(m, select=c(sdl.mut.avg, mut.avg)) , method="kendall", use="pairwise")['sdl.mut.avg', 'mut.avg']
-% d <- cor(subset(m, select=c(lrnd.mut.avg, mut.avg)) , method="kendall", use="pairwise")['lrnd.mut.avg', 'mut.avg']
-% @
-
-$ \mu_\{M_{all} | M_{sdl}\} = Sexpr{sdl.est} \times M_{sdl} \text{ : } R^2 = Sexpr{sdl.r} \text{,} \tau_{\beta} = Sexpr{c}$
-
-\subsubsection{lrnd.mut.avg and mut.avg}
-
-$ \mu_\{M_{all} | M_{rnd}\} = Sexpr{rnd.est} \times M_{rnd} \text{ : } R^2 = Sexpr{rnd.r} \text{,} \tau_{\beta} = Sexpr{d}$
-
-\subsection{Regression Analysis}
-The next question we will tackle is if there exist a difference at all between SDL mutagen and the random sampling.
-We can perform two statistical tests to answer this question.
-For the first, we run a simple paired t-test.
-
-%<<>>=
-%s <- t.test(lrnd.mut.avg, sdl.mut.avg, paired=T)
-%@
-
-The paired t-test failed to sufficient difference between the two distributions with a two-sided p-value of Sexpr{s.p.value}.
-That is, we do not have sufficient evidence to conclude that the two distributions are different.
-
-The second approch is convoluted (I am a little unclear here.). We try to predict the original mutation score using the mutation score from both sdl and random sampling.
-Our full model is
-
-$ \mu_\{M_{all} | M_{sdl}, M_{rnd}\} = 0 + \beta_1 {sdl} + \beta_2 M_{rnd} + \beta_3 M_{sdl} M_{rnd}  $
-\begin{small}
-% <<results='asis'>>=
-% s <- subset(m, select=c(mut.avg,sdl.mut.avg))
-% s$type <- 'sdl'
-% colnames(s) <- c('mut', 'sample', 'type')
-% r <- subset(m, select=c(mut.avg,lrnd.mut.avg))
-% r$type <- 'rnd'
-% colnames(r) <- c('mut', 'sample', 'type')
-% all <- rbind(s, r)
-% fm <- with(all, lm(mut ~ sample + type + sample:type))
-% sm <- anova(fm)
-% print(xtable(sm,caption="My caption"), size="\\small")
-% @
-\end{small}
-
-We see that both type and sample:type are non-significant for predicting the final model, and sequentially removing them does not change the effectiveness.
-Hence, the techniques random sampling and statement deletion operator do not have any difference.
-
-\begin{figure*}[t]
-% <<tplots, fig.width=5, fig.height=5, out.width='.45\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-% t_f <- sdl.time~lrnd.time
-% plot(t_f, main='SDL ~ RND',pch='*')
-% abline(lm(t_f), col='red')
-% detach(m)
-% @
-\caption{Time}
-\label{fig:caddrm}
-\end{figure*}
-
-\begin{figure*}[t]
-\includegraphics[totalheight=6cm]{fig/original.pdf}
-\caption{Subsumption Original}
-\label{fig:subsumptiono}
-\end{figure*}[t]
-
-\begin{figure*}[t]
-\includegraphics[totalheight=6cm]{fig/randoop.pdf}
-\caption{Subsumption Randoop}
-\label{fig:subsumptionr}
-\end{figure*}[t]
-
 <<results, child='results.Rnw'>>=

### 2014-03-07 src/paper.Rnw
update

@@
 \newcommand\mua{mutation analysis~}
+
 \begin{comment}
@@
 \end{comment}
-
-% <<a,message=F, echo=F>>=
-% require(xtable)
-% require(data.table)
-% load('data/mu.rda')
-% @
-
 % 10 pages for the main text + 1 for references.
-<<>>=
-data(o.dist.all)
-data(o.dist.det)
-data(r.dist.all)
-data(r.dist.det)
-@
 <<intro, child='intro.Rnw'>>=

### 2014-03-07 src/methodology.Rnw
update

@@
 
+Finally, to ensure accuracy of our observations, each criteria described has been run four times, and the results are averaged to produce the final result.
+
 One of our research questions was to compare the utility of operator
@@
 \subsubsection{Criteria I}
-For this criteria, we used the two operators \textit{COND\_BOUNDARY, and NEGATE\_COND} which are similar to those given by Wong.
+For this criteria, we used the two operators \pitcb, and \pitnc which are similar to those given by Wong.
 \subsubsection{Criteria II}
-We used the operators given by Offutt et al. \textit{INVERT\_NEGS, MATH, COND\_BOUNDARY,} \textit{NEGATE\_COND},
+We used the operators given by Offutt et al. \pitin, \pitm, \pitcb, \pitnc.
 \subsubsection{Criteria III}
-Those given by Javalanche \textit{NEGATE\_COND, VOID\_METHOD\_CALLS, NON\_VOID\_METHOD\_CALLS, MATH, INLINE\_CONSTS, E\_MEMBER\_VARIABLE}
+Those given by Javalanche \pitnc, \pitvmc, \pitnvmc, \pitm, \pitic, \pitemv
 \subsubsection{Criteria IV}
-those given by Javalanche \textit{NEGATE\_COND, VOID\_METHOD\_CALLS, NON\_VOID\_METHOD\_CALLS, MATH, INLINE\_CONSTS, E\_MEMBER\_VARIABLE}
+those given by Javalanche \pitnc, \pitvmc, \pitnvmc, \pitm, \pitic, \pitemv
 \subsubsection{Criteria V}
-By Namin et al.\textit{INVERT\_NEGS, MATH, INCREMENTS, NEGATE\_COND}.
+By Namin et al. \pitin, \pitm, \piti, \pitnc.
+\subsubsection{Criteria VI}
 We also  compare N-Selective mutation as suggested by Offutt et al.
-\subsubsection{Criteria VI}
-By Namin et al.\textit{INVERT\_NEGS, MATH, INCREMENTS, NEGATE\_COND}.
 \subsubsection{Statement Deletion:}

### 2014-03-07 src/methodology.Rnw
update

@@
 al.~\cite{deng2013empirical}. The operations on single statements was modeled
-using \textit{VOID-M-CALLS,NONV-M-CALLS,CONSTR-CALLS,E-MEMBER-VAR,RM-INCR}
-for simple statements, and using \textit{RM-COND} for control structures,
+using \pitvmc, \pitnvmc, \pitcc, \pitemv, \pitri
+for simple statements, and using \pitrc for control structures,
 which replaced the boolean condition with false, resulting in removal of
 the block of statements. The operator for return values was modeled using
-\textit{RETURN-VALS}, which is similar.  The operators for \textit{while,for},
-and \textit{if} statements were modeled using \textit{DELETE-COND},
+\pitrv, which is similar.  The operators for \textit{while,for},
+and \textit{if} statements were modeled using \pitdc,
 which replaced the boolean condition with true, which removed the effect
 of conditional. The \textit{switch} statement deletion was modeled using
-\textit{RM-SWITCH} which replaced the first 100 labels with default label,
+\pitrs which replaced the first 100 labels with default label,
 resulting in the switch element getting deleted. (Due to the constraints
@@
 complete. However, as seen in Figure~\ref{fig:op}, the number of mutants
-produced by \textit{MATH} operator is very small. We also note that our
+produced by \pitm operator is very small. We also note that our
 approximation does not account for the increase in ease of detection when

### 2014-03-07 src/analysis.Rnw
update

@@
 \label{sec:analysis}
+
 \subsection{Occurrence of Operators}
@@
 
+\begin{table*}
+\begin{minipage}[h]{0.49\linewidth}
 <<results='asis'>>=
@@
 colnames(o.x) <- c('operator', 'r^2', 'm.red', 'm.sd', 'num', 'B*')
-print(xtable(o.x, caption='Original', label='table:rando'), include.rownames=FALSE)
-# , sanitize.text.function = function(x){x}, include.rownames=FALSE)
+print(xtable(o.x, caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
 @
+\end{minipage}
+\hspace{0.5cm}
+\begin{minipage}[h]{0.49\linewidth}
 <<results='asis'>>=
@@
 colnames(r.x) <- c('operator', 'r^2', 'm.red','m.sd', 'num', 'B*')
-print(xtable(r.x, caption='Randoop', label='table:randr'), include.rownames=FALSE)
+print(xtable(r.x, caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
 @
+\end{minipage}
+\end{table*}
 
+\begin{table*}
+\begin{minipage}[h]{0.49\linewidth}
 <<results='asis'>>=
@@
 colnames(o.x) <- c('operator', 'r^2', 'm.red', 'm.sd', 'num', 'B*')
-print(xtable(o.x, caption='Original', label='table:rando'), include.rownames=FALSE)
+print(xtable(o.x, caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE,size='\\small')
 # , sanitize.text.function = function(x){x}, include.rownames=FALSE)
 @
+\end{minipage}
+\hspace{0.5cm}
+\begin{minipage}[h]{0.49\linewidth}
 <<results='asis'>>=
@@
 colnames(r.x) <- c('operator', 'r^2', 'm.red','m.sd', 'num', 'B*')
-print(xtable(r.x, caption='Randoop', label='table:randr'), include.rownames=FALSE)
+print(xtable(r.x, caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
 @
+\end{minipage}
+\end{table*}
+
+\begin{table*}
+\begin{minipage}[h]{0.49\linewidth}
 
@@
 colnames(o.x) <- c('operator', 'r^2', 'm.red', 'm.sd', 'num', 'B*')
-print(xtable(o.x, caption='Original', label='table:selo'), include.rownames=FALSE)
+print(xtable(o.x, caption='Original', label='table:selo'), include.rownames=FALSE, floating=FALSE,size='\\small')
 # , sanitize.text.function = function(x){x}, include.rownames=FALSE)
 @
+\end{minipage}
+\hspace{0.5cm}
+\begin{minipage}[h]{0.49\linewidth}
+
 <<results='asis'>>=
@@
 colnames(r.x) <- c('operator', 'r^2', 'm.red','m.sd', 'num', 'B*')
-print(xtable(r.x, caption='Randoop', label='table:selr'), include.rownames=FALSE)
+print(xtable(r.x, caption='Randoop', label='table:selr'), include.rownames=FALSE, floating=FALSE,size='\\small')
 @
+\end{minipage}
+\end{table*}
 
@@
 % @
-
 $ \mu_\{M_{all} | M_{sdl}\} = Sexpr{sdl.est} \times M_{sdl} \text{ : } R^2 = Sexpr{sdl.r} \text{,} \tau_{\beta} = Sexpr{c}$

### 2014-03-07 src/analysis.Rnw
update

@@
 \label{sec:analysis}
-
-\subsection{Occurrence of Operators}
-\begin{figure*}[t]
+\begin{figure*}[!htb]
 <<op,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
@@
 \end{figure*}
+
+First, we ran the the mutation analysis to identify the general distribution of mutants within our set of projects.
+This provided us with the relative number of each mutation operators, that are produced, and also the general number of
+mutants generated by each operator that was detected. This is given in Figure~\ref{fig:op}.
 

### 2014-03-07 src/methodology.Rnw
selective mutation

@@
 
-For operator reduction, we utilized the constrained mutation operators suggested by Wong et al.~\cite{wong1995reducing}, Offutt et al.~\cite{offutt1996anexperimental,deng2013empirical}, % TODO Barbosa
- and, Namin et al~\cite{siami2008sufficient}. Since Javalanche~\cite{javalanche} utilized operator selection mechanisms, we also compared the Javalanche operators for operator selection.
+For selective methods, we tried mutation operators suggested by Wong et al.~\cite{wong1995reducing}, Offutt et al.~\cite{offutt1996anexperimental,deng2013empirical}, % TODO Barbosa
+ and, Namin et al~\cite{siami2008sufficient}.
+Since Javalanche~\cite{javalanche} utilized operator selection mechanisms, we also compared the Javalanche operators for operator selection.
+Note that all of these techniques except
+Javalanche have targeted C programs, thus some of these operators
+are sensible in C but in Java programs. For example C compilers tolerate
+removing a return statement but, in Java, it causes a compilation error.
+Moreover, there were some operators that are not supported by PIT framework
+like ABS (absolute mutation operators), however, we tried to realize as many
+as possible operators using PIT's bytecode level mutation. We also extended 
+the PIT framework to support the  statement deletion operator (SDL).
+
+{\bf Amin: The rest of this section is for Alex and Carlos info and would be omitted later.}
 

### 2014-03-07 src/analysis.Rnw
udpate

@@
 @
-\caption{Relative fertility of mutation operators. The blue shade represent detected mutants, while black represents total mutants.}
+\caption{The relative contribution of mutation operators in terms of fraction of mutants generated and detected. The blue shade represent detected mutants, while black represents total mutants.}
 \label{fig:op}
@@
 This provided us with the relative number of each mutation operators, that are produced, and also the general number of
-mutants generated by each operator that was detected. This is given in Figure~\ref{fig:op}.
+mutants generated by each operator that was detected. This is given in Figure~\ref{fig:op}. This suggests that the operators
+are distributed in the following order: \pitnvmc, \pitnc, \pitrc, \pitdc, \pitrv, \pitic, \pitcc, \pitemv, \pitvmc, \pitm,
+\pitcb, \piti, \pitri, \pitrs, \pites, \pitin. We use this information later for n-selective mutation.
+
+For comparing between different techniques, we ran correlation analysis between the full mutation score,
+and that produced by the reduction criteria. Further, we also collected the mean reduction, and the standard
+deviation of the reduction across all the projects for both randoop and original. These statistics are provided below.
+\subsection{Analysis of Sampling Criteria}
+% We have power, element, kind(O/R), and MuRed, MuRedSD, R^2
+<<>>=
+odata <- subset(stats.df, s.element=='project' & strategy=='xpercentperunit' & kind=='original')
+rdata <- subset(stats.df, s.element=='project' & strategy=='xpercentperunit' & kind=='randoop')
+@
+\subsubsection{x\% selection}
+\begin{figure*}[t]
+<<x.per.sel,fig.width=5, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+names=odata$s.power
+x = (1:nrow(odata))
+o.CI.up = as.numeric(odata$mutant.reduction)+as.numeric(odata$sd.reduction)
+o.CI.dn = as.numeric(odata$mutant.reduction)-as.numeric(odata$sd.reduction)
+r.CI.up = as.numeric(rdata$mutant.reduction)+as.numeric(rdata$sd.reduction)
+r.CI.dn = as.numeric(rdata$mutant.reduction)-as.numeric(rdata$sd.reduction)
+plot(odata$mutant.reduction~odata$s.power,xaxt='n', cex=1.5,ylim=c(0,100), xlab='Power',ylab='Reduction', main='Mutant Reduction vs Power',col='blue',pch=16)
+axis(1, at=x, labels=names)
+arrows(x,o.CI.dn,x,o.CI.up,code=3,length=0.2,angle=90,col='blue')
+points(rdata$mutant.reduction~rdata$s.power,xaxt='n', cex=1.5,ylim=c(0,100), xlab='Power',ylab='Reduction', main='Mutant Reduction vs Power',col='red',pch=16)
+arrows(x,r.CI.dn,x,r.CI.up,code=3,length=0.2,angle=90,col='green')
+#legend("bottomleft",paste(names,": S.E=",data$se),ncol=6,text.width=5)
+@
+\label{fig:sel}
+\end{figure*}[t]
 

### 2014-03-07 src/analysis.Rnw
temp update

@@
 r.CI.dn = as.numeric(rdata$mutant.reduction)-as.numeric(rdata$sd.reduction)
-plot(odata$mutant.reduction~odata$s.power,xaxt='n', cex=1.5,ylim=c(0,100), xlab='Power',ylab='Reduction', main='Mutant Reduction vs Power',col='blue',pch=16)
+plot(odata$mutant.reduction~odata$s.power,xaxt='n', cex=1.5,ylim=c(0,100), xlab='Power',ylab='Reduction', main='Project: Mutant Reduction vs Power',col='blue',pch=16)
 axis(1, at=x, labels=names)
 arrows(x,o.CI.dn,x,o.CI.up,code=3,length=0.2,angle=90,col='blue')
-points(rdata$mutant.reduction~rdata$s.power,xaxt='n', cex=1.5,ylim=c(0,100), xlab='Power',ylab='Reduction', main='Mutant Reduction vs Power',col='red',pch=16)
-arrows(x,r.CI.dn,x,r.CI.up,code=3,length=0.2,angle=90,col='green')
+points(rdata$mutant.reduction~rdata$s.power,xaxt='n', cex=1.5,ylim=c(0,100), xlab='Power',ylab='Reduction', main='Project: Mutant Reduction vs Power',col='red',pch=16)
+arrows(x,r.CI.dn,x,r.CI.up,code=3,length=0.2,angle=90,col='red')
+#legend("bottomleft",paste(names,": S.E=",data$se),ncol=6,text.width=5)
+@
+\label{fig:sel}
+\end{figure*}[t]
+
+<<>>=
+odata <- subset(stats.df, s.element=='class' & strategy=='xpercentperunit' & kind=='original')
+rdata <- subset(stats.df, s.element=='class' & strategy=='xpercentperunit' & kind=='randoop')
+odata$s.power
+odata$mutant.reduction
+@
+\subsubsection{x\% selection}
+\begin{figure*}[t]
+<<x.per.sel.class,fig.width=5, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+names=odata$s.power
+x = (1:nrow(odata))
+o.CI.up = as.numeric(odata$mutant.reduction)+as.numeric(odata$sd.reduction)
+o.CI.dn = as.numeric(odata$mutant.reduction)-as.numeric(odata$sd.reduction)
+r.CI.up = as.numeric(rdata$mutant.reduction)+as.numeric(rdata$sd.reduction)
+r.CI.dn = as.numeric(rdata$mutant.reduction)-as.numeric(rdata$sd.reduction)
+plot(odata$mutant.reduction~odata$s.power,xaxt='n', cex=1.5,ylim=c(0,100), xlab='Power',ylab='Reduction', main='Class: Mutant Reduction vs Power',col='blue',pch=16)
+axis(1, at=x, labels=names)
+arrows(x,o.CI.dn,x,o.CI.up,code=3,length=0.2,angle=90,col='blue')
+points(rdata$mutant.reduction~rdata$s.power,xaxt='n', cex=1.5,ylim=c(0,100), xlab='Power',ylab='Reduction', main='Class: Mutant Reduction vs Power',col='red',pch=16)
+arrows(x,r.CI.dn,x,r.CI.up,code=3,length=0.2,angle=90,col='red')
+#legend("bottomleft",paste(names,": S.E=",data$se),ncol=6,text.width=5)
+@
+\label{fig:sel}
+\end{figure*}[t]
+
+<<>>=
+odata <- subset(stats.df, s.element=='method' & strategy=='xpercentperunit' & kind=='original')
+rdata <- subset(stats.df, s.element=='method' & strategy=='xpercentperunit' & kind=='randoop')
+odata$s.power
+odata$mutant.reduction
+@
+\subsubsection{x\% selection}
+\begin{figure*}[t]
+<<x.per.sel.method,fig.width=5, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+names=odata$s.power
+x = (1:nrow(odata))
+o.CI.up = as.numeric(odata$mutant.reduction)+as.numeric(odata$sd.reduction)
+o.CI.dn = as.numeric(odata$mutant.reduction)-as.numeric(odata$sd.reduction)
+r.CI.up = as.numeric(rdata$mutant.reduction)+as.numeric(rdata$sd.reduction)
+r.CI.dn = as.numeric(rdata$mutant.reduction)-as.numeric(rdata$sd.reduction)
+plot(odata$mutant.reduction~odata$s.power,xaxt='n', cex=1.5,ylim=c(0,400), xlab='Power',ylab='Reduction', main='Method: Mutant Reduction vs Power',col='blue',pch=16)
+axis(1, at=x, labels=names)
+arrows(x,o.CI.dn,x,o.CI.up,code=3,length=0.2,angle=90,col='blue')
+points(rdata$mutant.reduction~rdata$s.power,xaxt='n', cex=1.5,ylim=c(0,400), xlab='Power',ylab='Reduction', main='Method: Mutant Reduction vs Power',col='red',pch=16)
+arrows(x,r.CI.dn,x,r.CI.up,code=3,length=0.2,angle=90,col='red')
+#legend("bottomleft",paste(names,": S.E=",data$se),ncol=6,text.width=5)
+@
+\label{fig:sel}
+\end{figure*}[t]
+
+<<>>=
+odata <- subset(stats.df, s.element=='line' & strategy=='xpercentperunit' & kind=='original')
+rdata <- subset(stats.df, s.element=='line' & strategy=='xpercentperunit' & kind=='randoop')
+odata$s.power
+odata$mutant.reduction
+@
+\subsubsection{x\% selection}
+\begin{figure*}[t]
+<<x.per.sel.line,fig.width=5, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+names=odata$s.power
+x = (1:nrow(odata))
+o.CI.up = as.numeric(odata$mutant.reduction)+as.numeric(odata$sd.reduction)
+o.CI.dn = as.numeric(odata$mutant.reduction)-as.numeric(odata$sd.reduction)
+r.CI.up = as.numeric(rdata$mutant.reduction)+as.numeric(rdata$sd.reduction)
+r.CI.dn = as.numeric(rdata$mutant.reduction)-as.numeric(rdata$sd.reduction)
+plot(odata$mutant.reduction~odata$s.power,xaxt='n', cex=1.5,ylim=c(0,20000), xlab='Power',ylab='Reduction', main='Line: Mutant Reduction vs Power',col='blue',pch=16)
+axis(1, at=x, labels=names)
+arrows(x,o.CI.dn,x,o.CI.up,code=3,length=0.2,angle=90,col='blue')
+points(rdata$mutant.reduction~rdata$s.power,xaxt='n', cex=1.5,ylim=c(0,20000), xlab='Power',ylab='Reduction', main='Line: Mutant Reduction vs Power',col='red',pch=16)
+arrows(x,r.CI.dn,x,r.CI.up,code=3,length=0.2,angle=90,col='red')
+#legend("bottomleft",paste(names,": S.E=",data$se),ncol=6,text.width=5)
+@
+\label{fig:sel}
+\end{figure*}[t]
+
+<<>>=
+odata <- subset(stats.df, s.element=='line' & strategy=='xpercentperunit' & kind=='original')
+rdata <- subset(stats.df, s.element=='line' & strategy=='xpercentperunit' & kind=='randoop')
+odata$s.power
+odata$mutant.reduction
+@
+\subsubsection{x\% selection}
+\begin{figure*}[t]
+<<x.per.sel.line.2,fig.width=5, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+names=odata$s.power
+x = (1:nrow(odata))
+o.CI.up = as.numeric(odata$mutant.reduction)+as.numeric(odata$sd.reduction)
+o.CI.dn = as.numeric(odata$mutant.reduction)-as.numeric(odata$sd.reduction)
+r.CI.up = as.numeric(rdata$mutant.reduction)+as.numeric(rdata$sd.reduction)
+r.CI.dn = as.numeric(rdata$mutant.reduction)-as.numeric(rdata$sd.reduction)
+plot(odata$mutant.reduction~odata$s.power,xaxt='n', cex=1.5,ylim=c(0,100), xlab='Power',ylab='Reduction', main='Line: Mutant Reduction vs Power',col='blue',pch=16)
+axis(1, at=x, labels=names)
+arrows(x,o.CI.dn,x,o.CI.up,code=3,length=0.2,angle=90,col='blue')
+points(rdata$mutant.reduction~rdata$s.power,xaxt='n', cex=1.5,ylim=c(0,100), xlab='Power',ylab='Reduction', main='Line: Mutant Reduction vs Power',col='red',pch=16)
+arrows(x,r.CI.dn,x,r.CI.up,code=3,length=0.2,angle=90,col='red')
+#legend("bottomleft",paste(names,": S.E=",data$se),ncol=6,text.width=5)
+@
+\label{fig:sel}
+\end{figure*}[t]
+
+<<>>=
+odata <- subset(stats.df, s.element=='class' & strategy=='xceilperunit' & kind=='original')
+rdata <- subset(stats.df, s.element=='class' & strategy=='xceilperunit' & kind=='randoop')
+@
+\subsubsection{x\% selection}
+\begin{figure*}[t]
+<<x.per.sel.class.3,fig.width=5, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+names=odata$s.power
+x = (1:nrow(odata))
+o.CI.up = as.numeric(odata$mutant.reduction)+as.numeric(odata$sd.reduction)
+o.CI.dn = as.numeric(odata$mutant.reduction)-as.numeric(odata$sd.reduction)
+r.CI.up = as.numeric(rdata$mutant.reduction)+as.numeric(rdata$sd.reduction)
+r.CI.dn = as.numeric(rdata$mutant.reduction)-as.numeric(rdata$sd.reduction)
+plot(odata$mutant.reduction~odata$s.power,xaxt='n', cex=1.5,ylim=c(0,10), xlab='Power',ylab='Reduction', main='Ceil:Class: Mutant Reduction vs Power',col='blue',pch=16)
+axis(1, at=x, labels=names)
+arrows(x,o.CI.dn,x,o.CI.up,code=3,length=0.2,angle=90,col='blue')
+points(rdata$mutant.reduction~rdata$s.power,xaxt='n', cex=1.5,ylim=c(0,10), xlab='Power',ylab='Reduction', main='Ceil:Class: Mutant Reduction vs Power',col='red',pch=16)
+arrows(x,r.CI.dn,x,r.CI.up,code=3,length=0.2,angle=90,col='red')
+#legend("bottomleft",paste(names,": S.E=",data$se),ncol=6,text.width=5)
+@
+\label{fig:sel}
+\end{figure*}[t]
+
+<<>>=
+odata <- subset(stats.df, s.element=='line' & strategy=='xceilperunit' & kind=='original')
+rdata <- subset(stats.df, s.element=='line' & strategy=='xceilperunit' & kind=='randoop')
+@
+\subsubsection{x\% selection}
+\begin{figure*}[t]
+<<x.per.sel.line.3,fig.width=5, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+names=odata$s.power
+x = (1:nrow(odata))
+o.CI.up = as.numeric(odata$mutant.reduction)+as.numeric(odata$sd.reduction)
+o.CI.dn = as.numeric(odata$mutant.reduction)-as.numeric(odata$sd.reduction)
+r.CI.up = as.numeric(rdata$mutant.reduction)+as.numeric(rdata$sd.reduction)
+r.CI.dn = as.numeric(rdata$mutant.reduction)-as.numeric(rdata$sd.reduction)
+plot(odata$mutant.reduction~odata$s.power,xaxt='n', cex=1.5,ylim=c(0,10), xlab='Power',ylab='Reduction', main='Ceil:Line: Mutant Reduction vs Power',col='blue',pch=16)
+axis(1, at=x, labels=names)
+arrows(x,o.CI.dn,x,o.CI.up,code=3,length=0.2,angle=90,col='blue')
+points(rdata$mutant.reduction~rdata$s.power,xaxt='n', cex=1.5,ylim=c(0,10), xlab='Power',ylab='Reduction', main='Ceil:Line: Mutant Reduction vs Power',col='red',pch=16)
+arrows(x,r.CI.dn,x,r.CI.up,code=3,length=0.2,angle=90,col='red')
+#legend("bottomleft",paste(names,": S.E=",data$se),ncol=6,text.width=5)
+@
+\label{fig:sel}
+\end{figure*}[t]
+
+<<>>=
+odata <- subset(stats.df, s.element=='project' & strategy=='xprobperunit' & kind=='original')
+rdata <- subset(stats.df, s.element=='project' & strategy=='xprobperunit' & kind=='randoop')
+@
+\subsubsection{x\% selection}
+\begin{figure*}[t]
+<<x.per.sel.line.4,fig.width=5, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+names=odata$s.power
+x = c(2,3,5,6)
+o.CI.up = as.numeric(odata$mutant.reduction)+as.numeric(odata$sd.reduction)
+o.CI.dn = as.numeric(odata$mutant.reduction)-as.numeric(odata$sd.reduction)
+r.CI.up = as.numeric(rdata$mutant.reduction)+as.numeric(rdata$sd.reduction)
+r.CI.dn = as.numeric(rdata$mutant.reduction)-as.numeric(rdata$sd.reduction)
+plot(odata$mutant.reduction~odata$s.power,xaxt='n', cex=1.5,ylim=c(0,10), xlab='Power',ylab='Reduction', main='Prob:Project: Mutant Reduction vs Power',col='blue',pch=16)
+axis(1, at=x, labels=names)
+arrows(x,o.CI.dn,x,o.CI.up,code=3,length=0.2,angle=90,col='blue')
+points(rdata$mutant.reduction~rdata$s.power,xaxt='n', cex=1.5,ylim=c(0,10), xlab='Power',ylab='Reduction', main='Prob:Project: Mutant Reduction vs Power',col='red',pch=16)
+arrows(x,r.CI.dn,x,r.CI.up,code=3,length=0.2,angle=90,col='red')
 #legend("bottomleft",paste(names,": S.E=",data$se),ncol=6,text.width=5)

### 2014-03-07 src/methodology.Rnw
clarification about mutants

@@
 \subsubsection{Criteria I}
-For this criteria, we used the two operators \pitcb, and \pitnc which are similar to those given by Wong.
+For this criteria, we used the two operators \pitcb, and \pitnc which are similar to those given by Wong. We did not have ABS operator available in PIT.
 \subsubsection{Criteria II}
-We used the operators given by Offutt et al. \pitin, \pitm, \pitcb, \pitnc.
+We used the operators given by Offutt et al. \pitin, \pitm, \pitcb, \pitnc. We did not have LCR available in PIT.
 \subsubsection{Criteria III}
-Those given by Javalanche \pitnc, \pitvmc, \pitnvmc, \pitm, \pitic, \pitemv
+Those given by Javalanche \pitnc, \pitvmc, \pitnvmc, \pitm, \pitic, \pitemv. 
 \subsubsection{Criteria IV}
-those given by Javalanche \pitnc, \pitvmc, \pitnvmc, \pitm, \pitic, \pitemv
-\subsubsection{Criteria V}
-By Namin et al. \pitin, \pitm, \piti, \pitnc.
-\subsubsection{Criteria VI}
-We also  compare N-Selective mutation as suggested by Offutt et al.
+By Namin et al. \pitin, \pitm, \piti, \pitnc. Many of operators were not applicable in Java and some were not available in PIT like IndVarBitNeg.
+
 \subsubsection{Statement Deletion:}

### 2014-03-07 src/analysis.Rnw
update

@@
 names=odata$s.power
-x = c(2,3,5,6)
+x = c(2:6)
 o.CI.up = as.numeric(odata$mutant.reduction)+as.numeric(odata$sd.reduction)
@@
 r.CI.dn = as.numeric(rdata$mutant.reduction)-as.numeric(rdata$sd.reduction)
-plot(odata$mutant.reduction~odata$s.power,xaxt='n', cex=1.5,ylim=c(0,10), xlab='Power',ylab='Reduction', main='Prob:Project: Mutant Reduction vs Power',col='blue',pch=16)
+plot(odata$mutant.reduction~odata$s.power,xaxt='n', cex=1.5,ylim=c(0,100), xlab='Power',ylab='Reduction', main='Prob:Project: Mutant Reduction vs Power',col='blue',pch=16)
 axis(1, at=x, labels=names)
 arrows(x,o.CI.dn,x,o.CI.up,code=3,length=0.2,angle=90,col='blue')
-points(rdata$mutant.reduction~rdata$s.power,xaxt='n', cex=1.5,ylim=c(0,10), xlab='Power',ylab='Reduction', main='Prob:Project: Mutant Reduction vs Power',col='red',pch=16)
+points(rdata$mutant.reduction~rdata$s.power,xaxt='n', cex=1.5,ylim=c(0,100), xlab='Power',ylab='Reduction', main='Prob:Project: Mutant Reduction vs Power',col='red',pch=16)
 arrows(x,r.CI.dn,x,r.CI.up,code=3,length=0.2,angle=90,col='red')

### 2014-03-07 src/intro.Rnw
update
intro

@@
 Mutation analysis is a method of evaluation of quality of test-suites. It involves generation
-of first (and higher) order mutants, and evaluating the effectiveness of test-suites against
-the generated mutants~\cite{lipton1971fault, ammann2008introduction}.
-Previous research~\cite{andrews2005mutation} has shown that mutations thus introduced behave
-similar to the real-faults.
+of  mutants by making syntactic changes to the program. First (higher) order mutants
+have one (more) syntactic distance to the origianl program.
+Mutants are used to evaluate the effectiveness of test-suites 
+~\cite{lipton1971fault, ammann2008introduction}.
+Studies like ~\cite{andrews2005mutation} have shown that mutation score 
+are predictors of the real fault detection of a test suits.
 
-A major impediment on the path to wide adoption of mutation analysis is its high cost of
-execution. A full mutation analysis requires running the test-suite against all the first
-order syntactical variants, and is prohibitive for even moderately large programs.
+A major impediment to wider adoption of mutation analysis is its high computational cost.
+Set of first oder mutants of a moderate size program can be very large, 
+which renders mutation analysis of a test-suite against all the first
+order mutants prohibitively time-consuming.
 
 A major strain of research into cost-reduction of mutation analysis is to choose a smaller
-representative set of mutants~\cite{offutt2001mutation,jia2011analysis}, often called the
-``do fewer'' approach. A major variant of this approach is the selective mutation strategy
-which advocates selecting a representative subset of operators based on heuristics and
-statistical analysis, and using them instead of the whole gamut of mutation
-operators~\cite{offutt1993anexperimental,untch2009onreduced}.
+representative set of mutants~\cite{offutt2001mutation,jia2011analysis}-- often called the
+``do fewer'' approach. This approach can be generally divided into 
+selective strategies and sampling strategies.
 
-Another fertile area of research has been sampling strategies, where, a smaller representative
-sample is used in lieu.
+Selective mutation strategies attempt to select a representative subset of operators based 
+on heuristics and statistical analysis. They suggest applying these subsets instead of the 
+applying the whole gamut of mutation operators~\cite{offutt1993anexperimental,untch2009onreduced}.
+
+Sampling strategies seek to randomly select smaller representative mutants.
 This was investigated first by Acreed~\cite{acree1980mutation} and Budd~\cite{budd1980mutation},
@@
 
-Finally, clustering of mutants~\cite{hussain08mutation} based on similar test cases has also
-been used successfully for mutant reduction. These are explained more in depth in Section~\ref{sec:related}
+% {Amin: I am not a fan of this ~\cite{hussain08mutation} }
+%Finally, clustering of mutants~\cite{hussain08mutation} based on similar test cases has also
+%been used successfully for mutant reduction. These are explained more in depth in Section~\ref{sec:related}
 
@@
 
-Our contributions in this paper are the following. First, as described in Section~\ref{sec:methodology},
-we seek to improve the statistical confidence in our results by utilizing a much larger sample of projects
+\noindent\textbf{Contribution.} Contributions of this paper are he following.
+\begin{itemize}
+\item It compares a large number of various mutation sampling and selection strategies (Section~\ref{sec:analysis}).
+\item It seek sto improve the statistical confidence in our results by utilizing a much larger sample of projects
       (188 projects) from the open source repository at Github~\cite{github}, using both original and automatically
-generated test-suites using Randoop~\cite{randoop}. Second, as detailed in Section~\ref{sec:analysis}, we
-compare the reduction effectiveness of a large number of random sampling criterias (some of which are novel,
-and some that has been proposed by other researchers), and a some of the common operator selection
-criterias proposed in literature using statistical analysis. This provides us with insight for choosing
-mutation reduction techniqus according to the trade-offs in accuracy, and reduction ratios that a tester
-is willing to make for their specific requirements. This is detailed in Section~\ref{sec:results}.
+      generated test-suites using Randoop~\cite{randoop} (Section~\ref{sec:methodology}). 
+\item It analyses the results and suggest strategies (Section~\ref{sec:results}).
+\end{itemize}
 
-Our conclusion and recommendation for practicing testers are provided in Section~\ref{sec:conclusion}.
+%Our contributions in this paper are the following. First, as described in Section~\ref{sec:methodo%logy},
+%we seek to improve the statistical confidence in our results by utilizing a much larger sample of projects
+%(188 projects) from the open source repository at Github~\cite{github}, using both original and automatically
+%generated test-suites using Randoop~\cite{randoop}. Second, as detailed in Section~\ref{sec:analysis}, we
+%compare the reduction effectiveness of a large number of random sampling criterias (some of which are novel,
+%and some that has been proposed by other researchers), and a some of the common operator selection
+%criterias proposed in literature using statistical analysis. This provides us with insight for choosing
+%mutation reduction techniqus according to the trade-offs in accuracy, and reduction ratios that a tester
+%is willing to make for their specific requirements. This is detailed in Section~\ref{sec:results}.
+
+%Our conclusion and recommendation for practicing testers are provided in Section~\ref{sec:conclusion}.
 
@@
 %
+% NON_VOID_METHOD_CALLS VOID_METHOD_CALLS CONSTRUCTOR_CALLS
+% NEGATE_CONDITIONALS REMOVE_CONDITIONALS DELETE_CONDITIONALS CONDITIONALS_BOUNDARY
+% RETURN_VALS INLINE_CONSTS EXPERIMENTAL_MEMBER_VARIABLE
+% MATH INCREMENTS REMOVE_INCREMENTS INVERT_NEGS
+% RMSWITCH EXPERIMENTAL_SWITCH

### 2014-03-08 src/analysis.Rnw
update

@@
 with(o.pit.all, plot(all.cov~TSDL.cov, pch='+', main='Original SDL'))
-with(o.pit.all, plot(all.cov~x1x1nl_per_line.cov, pch='+', main='Original 1 per line'))
+with(o.pit.all, plot(all.cov~l.1x1_per_line.cov, pch='+', main='Original 1 per line'))
 with(r.pit.all, plot(all.cov~TSDL.cov, pch='+', main='Randoop SDl'))
-with(r.pit.all, plot(all.cov~x1x1nl_per_line.cov, pch='+', main='Randoop 1 per line'))
+with(r.pit.all, plot(all.cov~l.1x1_per_line.cov, pch='+', main='Randoop 1 per line'))
 @

### 2014-03-08 src/methodology.Rnw
update

@@
 
-<<opstable,results='asis'>>=
-op=c(
-'INVERT-NEGS',
-'RETURN-VALS',
-'MATH',
-'VOID-M-CALLS',
-'NEGATE-COND',
-'COND-BOUNDARY',
-'INCREMENTS',
-'NVOID-M-CALLS',
-'CONSTR-CALLS',
-'INLINE-CONSTS',
-'RM-INCR',
-'E-MEMBER-VAR',
-'E-SWITCH',
-'RM-SWITCH',
-'RM-COND',
-'DELETE-COND')
-expl=c(
-'Invert negatives',
-'Change return values',
-'Modify arithmetic operators',
-'Remove void method calls',
-'Negate conditional statements',
-'Modify boundary conditions',
-'Modify increment/decrement',
-'Replace non-void method calls',
-'Replace constructor calls',
-'Replace inline constants',
-'Remove increment/decrement',
-'Replace member variable assignments',
-'Modify switch statements',
-'Remove switch elements*',
-'Make conditionas true',
-'Make conditionas false*')
-op.df <- data.frame(Operator=op, Explanation=expl)
-print(xtable(op.df,caption='PIT Mutation Opeators (* indicates new opeators)', label='tbl:pitop'), sanitize.text.function  = function(x){x}, include.colnames=FALSE, include.rownames=F)
-@
+\begin{table}[h]\footnotesize
+\begin{tabular}{ll}
+\pitic & Invert negatives \\
+\pitrv & Change return values \\
+\pitm & Modify arithmetic operators\\
+\pitvmc & Remove void method calls \\
+\pitnc & Negate conditional statements \\
+\pitcb & Modify boundary conditions \\
+\piti & Modify increment/decrement \\
+\pitnvmc & Replace non-void method calls \\
+\pitcc & Replace constructor calls \\
+\pitic & Replace inline constants \\
+\piti & Remove increment/decrement \\
+\pitemv & Replace member variable assignments \\
+\pites & Modify switch statements \\
+\pitrs & Remove switch elements* \\
+\pitrc & Make conditionals true \\
+\pitnc & Make conditionas false*
+\end{tabular}
+\caption{PIT Mutation Opeators}
+\label{tbl:pitop}
+\end{table}
 

### 2014-03-08 src/analysis.Rnw
update

@@
 @
-\caption{The relative contribution of mutation operators in terms of fraction of mutants generated and detected. The blue shade represent detected mutants, while black represents total mutants.}
+\caption{The relative contribution of mutation operators in terms of fraction of mutants generated and detected. \\
+The blue shade represent detected mutants, while black represents total mutants.}
 \label{fig:op}
@@
 % We have power, element, kind(O/R), and MuRed, MuRedSD, R^2
-<<>>=
-odata <- subset(stats.df, s.element=='project' & strategy=='xpercentperunit' & kind=='original')
-rdata <- subset(stats.df, s.element=='project' & strategy=='xpercentperunit' & kind=='randoop')
+\subsubsection{x\% selection}
+<<xpercentunit>>=
+sel.colnames <- c('operator', 'r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier')
+new.colnames <- c('operator', 'r^2',      'm.red',            'm.sd',         'num',    'B*')
+stats.xp <- subset(stats.df, grepl('^(r|rr|rc)[.]', operator))
+
+o.stats.sel.xp <- subset(o.f(stats.xp), select=sel.colnames)
+r.stats.sel.xp <- subset(r.f(stats.xp), select=sel.colnames)
+stats.rest <- subset(stats.df, !grepl('^(r|rr)[.]', operator)) # We are ignoring ceil here. add rc if needed.
+colnames(o.stats.sel.xp) <- new.colnames
+colnames(r.stats.sel.xp) <- new.colnames
+
+#odata <- subset(o.f(stats.xp), s.element=='project')
+#rdata <- subset(r.f(stats.xp), s.element=='project')
 @
-\subsubsection{x\% selection}
+
+\begin{table*}
+\begin{minipage}[h]{0.49\linewidth}
+<<results='asis'>>=
+print(xtable(o.stats.sel.xp, caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
+@
+\end{minipage}
+\hspace{0.5cm}
+\begin{minipage}[h]{0.49\linewidth}
+<<results='asis'>>=
+print(xtable(r.stats.sel.xp, caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
+@
+\end{minipage}
+\bigskip
+\caption {The x\% random selection criteria results.}
+\end{table*}
+
 \begin{figure*}[t]
-<<x.per.sel,fig.width=5, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+<<x.per.sel,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+o.xp <- subset(o.processed, grepl('^r[.].*.m[.]red',ind))
+ggplot(subset(o.xp, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
+  stat_boxplot(geom ='errorbar')+
+  geom_boxplot() + facet_wrap(~type)
+@
+\label{fig:sel}
+\end{figure*}[t]
+
+% ----------------------------------------------------------------------
+<<count>>=
+stats.loc <- subset(stats.rest, grepl('^(l|wl)[.]', operator))
+
+o.stats.sel.loc <- subset(o.f(stats.loc), select=sel.colnames)
+r.stats.sel.loc <- subset(r.f(stats.loc), select=sel.colnames)
+stats.rest <- subset(stats.rest, !grepl('^(l|wl)[.]', operator))
+colnames(o.stats.sel.loc) <- new.colnames
+colnames(r.stats.sel.loc) <- new.colnames
+@
+\begin{table*}
+\begin{minipage}[h]{0.49\linewidth}
+<<results='asis'>>=
+print(xtable(o.stats.sel.loc, caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
+@
+\end{minipage}
+\hspace{0.5cm}
+\begin{minipage}[h]{0.49\linewidth}
+<<results='asis'>>=
+print(xtable(r.stats.sel.loc, caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
+@
+\end{minipage}
+\bigskip
+\caption {The loc count selection criteria results.}
+\end{table*}
+
+% ----------------------------------------------------------------------
+<<one>>=
+stats.one <- subset(stats.rest, grepl('^o[.]', operator))
+
+o.stats.sel.one <- subset(o.f(stats.one), select=sel.colnames)
+r.stats.sel.one <- subset(r.f(stats.one), select=sel.colnames)
+stats.rest <- subset(stats.rest, !grepl('^o[.]', operator))
+colnames(o.stats.sel.one) <- new.colnames
+colnames(r.stats.sel.one) <- new.colnames
+@
+\begin{table*}
+\begin{minipage}[h]{0.49\linewidth}
+<<results='asis'>>=
+print(xtable(o.stats.sel.one, caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
+@
+\end{minipage}
+\hspace{0.5cm}
+\begin{minipage}[h]{0.49\linewidth}
+<<results='asis'>>=
+print(xtable(r.stats.sel.one, caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
+@
+\end{minipage}
+\bigskip
+\caption {The one per element selection criteria results.}
+\end{table*}
+
+% ----------------------------------------------------------------------
+
+\if 0
+% START HERE
+\begin{figure*}[t]
+<<xx.per.sel,fig.width=5, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
 names=odata$s.power
@@
 \end{figure*}[t]
+%% END HERE
+\fi

### 2014-03-08 src/paper.Rnw
update
udpate

@@
 \newcommand\mua{mutation analysis~}
+%\newcommand{\pitnvmc}{~NON\_\allowbreak{}VOID\_\allowbreak{}METHOD\_\allowbreak{}CALLS~}
+%\newcommand{\pitnc}{~NEGATE\_\allowbreak{}CONDITIONALS~}
+%\newcommand{\pitrc}{~REMOVE\_\allowbreak{}CONDITIONALS~}
+%\newcommand{\pitdc}{~DELETE\_\allowbreak{}CONDITIONALS~}
+%\newcommand{\pitrv}{~RETURN\_\allowbreak{}VALUES~}
+%\newcommand{\pitic}{~INLINE\_\allowbreak{}CONSTANTS~}
+%\newcommand{\pitcc}{~CONSTRUCTOR\_\allowbreak{}CALLS~}
+%\newcommand{\pitemv}{~E\_\allowbreak{}MEMBER\_\allowbreak{}VARIABLE~}
+%\newcommand{\pitvmc}{~VOID\_\allowbreak{}METHOD\_\allowbreak{}CALLS~}
+%\newcommand{\pitm}{~MATH~}
+%\newcommand{\pitcb}{~CONDITIONALS\_\allowbreak{}BOUNDARY~}
+%\newcommand{\piti}{~INCREMENTS~}
+%\newcommand{\pitri}{~REMOVE\_\allowbreak{}INCREMENTS~}
+%\newcommand{\pitrs}{~RM\_\allowbreak{}SWITCH~}
+%\newcommand{\pites}{~E\_\allowbreak{}SWITCH~}
+%\newcommand{\pitin}{~INVERT\_\allowbreak{}NEGATIVES~}
+%
+\newcommand{\pitnvmc}{NVMC~}
+\newcommand{\pitnc}{NC~}
+\newcommand{\pitrc}{RC~}
+\newcommand{\pitdc}{DC~}
+\newcommand{\pitrv}{RV~}
+\newcommand{\pitic}{IC~}
+\newcommand{\pitcc}{CC~}
+\newcommand{\pitemv}{EMV~}
+\newcommand{\pitvmc}{VMC~}
+\newcommand{\pitm}{M~}
+\newcommand{\pitcb}{CB~}
+\newcommand{\piti}{I~}
+\newcommand{\pitri}{RI~}
+\newcommand{\pitrs}{RS~}
+\newcommand{\pites}{ES~}
+\newcommand{\pitin}{IN~}
+% No space variants.
+\newcommand{\Pitnvmc}{NVMC}
+\newcommand{\Pitnc}{NC}
+\newcommand{\Pitrc}{RC}
+\newcommand{\Pitdc}{DC}
+\newcommand{\Pitrv}{RV}
+\newcommand{\Pitic}{IC}
+\newcommand{\Pitcc}{CC}
+\newcommand{\Pitemv}{EMV}
+\newcommand{\Pitvmc}{VMC}
+\newcommand{\Pitm}{M}
+\newcommand{\Pitcb}{CB}
+\newcommand{\Piti}{I}
+\newcommand{\Pitri}{RI}
+\newcommand{\Pitrs}{RS}
+\newcommand{\Pites}{ES}
+\newcommand{\Pitin}{IN}
 
@@
 require(xtable)
+require(ggplot2)
 require(Mutsel)
@@
 data(list = v$results[,3])
+original.stats.df <- stats.df # save it
+o.f <- function(x) subset(x, kind == 'original')
+r.f <- function(x) subset(x, kind == 'randoop')
+o.stats.df <- o.f(stats.df)
+r.stats.df <- r.f(stats.df)
 @

### 2014-03-08 src/analysis.Rnw
udpate

@@
 new.colnames <- c('operator', 'r^2',      'm.red',            'm.sd',         'num',    'B*')
-stats.xp <- subset(stats.df, grepl('^(r|rr|rc)[.]', operator))
+stats.xp <- subset(stats.df, grepl('^(r|rr)[.]', operator)) # We are ignoring ceil here. add rc if needed.
 
@@
 r.stats.sel.xp <- subset(r.f(stats.xp), select=sel.colnames)
-stats.rest <- subset(stats.df, !grepl('^(r|rr)[.]', operator)) # We are ignoring ceil here. add rc if needed.
+stats.rest <- subset(stats.df, !grepl('^(r|rr|rc)[.]', operator))
 colnames(o.stats.sel.xp) <- new.colnames

### 2014-03-08 src/analysis.Rnw
update

@@
 \begin{figure*}[t]
-<<x.per.sel,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+<<x.per.sel.round,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
 o.xp <- subset(o.processed, grepl('^r[.].*.m[.]red',ind))
@@
 \label{fig:sel}
+\caption{The effect of round(x) reduction, Except for line sampling of power $5$ and $6$ all others are above 0.90 $R^2$.}
+\end{figure*}[t]
+
+\begin{figure*}[t]
+<<x.per.sel.sample,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+o.xp <- subset(o.processed, grepl('^rr[.].*.m[.]red',ind))
+ggplot(subset(o.xp, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
+  stat_boxplot(geom ='errorbar')+
+  geom_boxplot() + facet_wrap(~type)
+@
+\label{fig:sel}
+\caption{The effect of sample(x) reduction. All are above 0.90 $R^2$.}
 \end{figure*}[t]

### 2014-03-08 src/analysis.Rnw
update

@@
 deviation of the reduction across all the projects for both randoop and original. These statistics are provided below.
-\subsection{Analysis of Sampling Criteria}
+\subsection{Sampling Criteria}
 % We have power, element, kind(O/R), and MuRed, MuRedSD, R^2
@@
 colnames(r.stats.sel.xp) <- new.colnames
-
-#odata <- subset(o.f(stats.xp), s.element=='project')
-#rdata <- subset(r.f(stats.xp), s.element=='project')
 @
@@
 \caption {The x\% random selection criteria results.}
+\label{tbl:xsel}
 \end{table*}
@@
 @
-\label{fig:sel}
 \caption{The effect of round(x) reduction, Except for line sampling of power $5$ and $6$ all others are above 0.90 $R^2$.}
-\end{figure*}[t]
+\label{fig:xroundsel}
+\end{figure*}
 
@@
 @
-\label{fig:sel}
+\label{fig:xsamplesel}
 \caption{The effect of sample(x) reduction. All are above 0.90 $R^2$.}
-\end{figure*}[t]
+\end{figure*}
+%TODO : See if the following paragraph is needed, or shall we just sink the ceil(x) discussion completely?
+Our experiments found that while $round(x)$ and $sample(x)$ produced relatively reasonable reduction of mutants, the $ceil(x)$ criteria failed to produce a reasonable reduction of mutants except for higher power where the reduction was some what close to that produced by $round(x)$ and $sample(x)$ (which was expected).
+The $R^2$ values of $ceil(x)$ were almost always lower than that produced by $round(x)$ and $sample(x)$ for similar reduction of mutants.
+For this reason, we do not consider this function again.
+
+The reduction in mutants for x\% selection using $round(x)$ is graphed in Figure~\ref{fig:xroundsel}. The values for the same are given in Table~\ref{tbl:xsel}
 

### 2014-03-08 src/methodology.Rnw
update

@@
 \pitrc & Make conditionals true \\
-\pitnc & Make conditionas false*
+\pitnc & Make conditionas false* \\
+\hline
 \end{tabular}
@@
 For example, for a line that produced 15 mutants, the number of mutants that can be chosen in \textit{(x\%, line, 1/64)} is less than 1.
-We analyzed the results of the following criterias: 1) to round the resulting number to the nearest integer, and choose that value as sampling (in effect, ignoring elements that are less complex), 2) to apply \textit{ceil} function to the resulting value, ensuring that there is atleast one mutant per program element, and 3) to perform the sampling in such a way that it chooses a mutant with with the fractional probability (this is the method followed by Zhang et al.~\cite{zhang2013ase}).
+We analyzed the results of the following criterias: 1) to apply \textit{round} function to the resulting number and covert to the nearest integer, and choose that value as the number of mutants (in effect, ignoring elements that are less complex), 2) to apply \textit{ceil} function to the resulting value, ensuring that there is atleast one mutant per program element, and 3) to apply \textit{sample} criteria suggested by Zhang et al.~\cite{zhang2013ase}, which chooses a mutant with given fracton as probability.
 % TODO: If the criterias ceil and round does not make sense, we might remove them to gain space.
@@
 
-{\bf Amin: The rest of this section is for Alex and Carlos info and would be omitted later.}
+{\bf Amin: The rest of this section is for Alex and Carlos info and should be verified if we should include this or wave our hands about approximation instead.}
 

### 2014-03-08 src/analysis.Rnw
update

@@
 @
+\caption{The effect of sample(x) reduction. All are above 0.90 $R^2$.}
 \label{fig:xsamplesel}
-\caption{The effect of sample(x) reduction. All are above 0.90 $R^2$.}
 \end{figure*}
@@
 For this reason, we do not consider this function again.
+However, interested parties can refer to our published data.
 
-The reduction in mutants for x\% selection using $round(x)$ is graphed in Figure~\ref{fig:xroundsel}. The values for the same are given in Table~\ref{tbl:xsel}
+The reduction in mutants for x\% selection using $round(x)$ is graphed in Figure~\ref{fig:xroundsel}. The values for the same are given in Table~\ref{tbl:xsel}.
+Similarly reduction in mutants for x\% selection using $sample(x)$ is graphed in Figure~\ref{fig:xsamplesel}. The values for the same are given in Table~\ref{tbl:xsel}.
+% ----------------------------------------------------------------------
 
-% ----------------------------------------------------------------------
+\subsubsection{Lines per element}
+The aim of this criteria is similar in some sense to selective mutation.
+While n-selective mutation ignores the most numerous mutant species, this criteria seeks to deprioritize the most complex program elements.
+
 <<count>>=
 stats.loc <- subset(stats.rest, grepl('^(l|wl)[.]', operator))
-
 o.stats.sel.loc <- subset(o.f(stats.loc), select=sel.colnames)
@@
 \end{minipage}
-\bigskip
-\caption {The loc count selection criteria results.}
+\caption {The line count selection criteria results.}
+\label{tbl:locsel}
 \end{table*}
+
+\begin{figure*}[t]
+<<loc.per.sel.sample,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+o.loc <- subset(o.processed, grepl('^l[.].*.m[.]red',ind))
+ggplot(subset(o.loc, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
+  stat_boxplot(geom ='errorbar')+
+  geom_boxplot() + facet_wrap(~type)
+@
+\caption{The effect of loc (external) reduction. All are above 0.98 $R^2$.}
+\label{fig:locsel}
+\end{figure*}
+
+\begin{figure*}[t]
+<<wloc.per.sel.sample,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+o.loc <- subset(o.processed, grepl('^wl[.].*.m[.]red',ind))
+ggplot(subset(o.loc, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
+  stat_boxplot(geom ='errorbar')+
+  geom_boxplot() + facet_wrap(~type)
+@
+\caption{The effect of loc (internal) reduction. All are above 0.90 $R^2$.}
+\label{fig:wlocsel}
+\end{figure*}
+
+The results of this selection criteria are provided in Table~\ref{tbl:locsel}.
+The effect of random selection within the program elements are visualized in Figure~\ref{fig:wlocsel}, and when it is made external to the program elements is visualized in Figure~\ref{fig:wlocsel}.
 

### 2014-03-08 src/analysis.Rnw
update

@@
 % ----------------------------------------------------------------------
+\subsubsection{One per element}
+The aim of this criteria is is to take the previous idea to the extreme. We choose only a single mutant per program element.
+
 <<one>>=
@@
 \caption {The one per element selection criteria results.}
+\label{tbl:onesel}
 \end{table*}
 
+\begin{figure*}[t]
+<<one.per.sel.sample,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+o.one <- subset(o.processed, grepl('^o[.].*.m[.]red',ind))
+ggplot(subset(o.one, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
+  stat_boxplot(geom ='errorbar')+
+  geom_boxplot() + facet_wrap(~type)
+@
+\caption{The effect of loc (external) reduction. All are above 0.98 $R^2$.}
+\label{fig:onesel}
+\end{figure*}
+
+The values are given in Table~\ref{tbl:onesel}, and its visaulization is in Figure~\ref{fig:onesel}.
 % ----------------------------------------------------------------------
 
+% IGNORED FROM HERE.
 \if 0
-% START HERE
-\begin{figure*}[t]
-<<xx.per.sel,fig.width=5, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-names=odata$s.power
-x = (1:nrow(odata))
-o.CI.up = as.numeric(odata$mutant.reduction)+as.numeric(odata$sd.reduction)
-o.CI.dn = as.numeric(odata$mutant.reduction)-as.numeric(odata$sd.reduction)
-r.CI.up = as.numeric(rdata$mutant.reduction)+as.numeric(rdata$sd.reduction)
-r.CI.dn = as.numeric(rdata$mutant.reduction)-as.numeric(rdata$sd.reduction)
-plot(odata$mutant.reduction~odata$s.power,xaxt='n', cex=1.5,ylim=c(0,100), xlab='Power',ylab='Reduction', main='Project: Mutant Reduction vs Power',col='blue',pch=16)
-axis(1, at=x, labels=names)
-arrows(x,o.CI.dn,x,o.CI.up,code=3,length=0.2,angle=90,col='blue')
-points(rdata$mutant.reduction~rdata$s.power,xaxt='n', cex=1.5,ylim=c(0,100), xlab='Power',ylab='Reduction', main='Project: Mutant Reduction vs Power',col='red',pch=16)
-arrows(x,r.CI.dn,x,r.CI.up,code=3,length=0.2,angle=90,col='red')
-#legend("bottomleft",paste(names,": S.E=",data$se),ncol=6,text.width=5)
-@
-\label{fig:sel}
-\end{figure*}[t]
-
-<<>>=
-odata <- subset(stats.df, s.element=='class' & strategy=='xpercentperunit' & kind=='original')
-rdata <- subset(stats.df, s.element=='class' & strategy=='xpercentperunit' & kind=='randoop')
-odata$s.power
-odata$mutant.reduction
-@
-\subsubsection{x\% selection}
-\begin{figure*}[t]
-<<x.per.sel.class,fig.width=5, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-names=odata$s.power
-x = (1:nrow(odata))
-o.CI.up = as.numeric(odata$mutant.reduction)+as.numeric(odata$sd.reduction)
-o.CI.dn = as.numeric(odata$mutant.reduction)-as.numeric(odata$sd.reduction)
-r.CI.up = as.numeric(rdata$mutant.reduction)+as.numeric(rdata$sd.reduction)
-r.CI.dn = as.numeric(rdata$mutant.reduction)-as.numeric(rdata$sd.reduction)
-plot(odata$mutant.reduction~odata$s.power,xaxt='n', cex=1.5,ylim=c(0,100), xlab='Power',ylab='Reduction', main='Class: Mutant Reduction vs Power',col='blue',pch=16)
-axis(1, at=x, labels=names)
-arrows(x,o.CI.dn,x,o.CI.up,code=3,length=0.2,angle=90,col='blue')
-points(rdata$mutant.reduction~rdata$s.power,xaxt='n', cex=1.5,ylim=c(0,100), xlab='Power',ylab='Reduction', main='Class: Mutant Reduction vs Power',col='red',pch=16)
-arrows(x,r.CI.dn,x,r.CI.up,code=3,length=0.2,angle=90,col='red')
-#legend("bottomleft",paste(names,": S.E=",data$se),ncol=6,text.width=5)
-@
-\label{fig:sel}
-\end{figure*}[t]
-
-<<>>=
-odata <- subset(stats.df, s.element=='method' & strategy=='xpercentperunit' & kind=='original')
-rdata <- subset(stats.df, s.element=='method' & strategy=='xpercentperunit' & kind=='randoop')
-odata$s.power
-odata$mutant.reduction
-@
-\subsubsection{x\% selection}
-\begin{figure*}[t]
-<<x.per.sel.method,fig.width=5, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-names=odata$s.power
-x = (1:nrow(odata))
-o.CI.up = as.numeric(odata$mutant.reduction)+as.numeric(odata$sd.reduction)
-o.CI.dn = as.numeric(odata$mutant.reduction)-as.numeric(odata$sd.reduction)
-r.CI.up = as.numeric(rdata$mutant.reduction)+as.numeric(rdata$sd.reduction)
-r.CI.dn = as.numeric(rdata$mutant.reduction)-as.numeric(rdata$sd.reduction)
-plot(odata$mutant.reduction~odata$s.power,xaxt='n', cex=1.5,ylim=c(0,400), xlab='Power',ylab='Reduction', main='Method: Mutant Reduction vs Power',col='blue',pch=16)
-axis(1, at=x, labels=names)
-arrows(x,o.CI.dn,x,o.CI.up,code=3,length=0.2,angle=90,col='blue')
-points(rdata$mutant.reduction~rdata$s.power,xaxt='n', cex=1.5,ylim=c(0,400), xlab='Power',ylab='Reduction', main='Method: Mutant Reduction vs Power',col='red',pch=16)
-arrows(x,r.CI.dn,x,r.CI.up,code=3,length=0.2,angle=90,col='red')
-#legend("bottomleft",paste(names,": S.E=",data$se),ncol=6,text.width=5)
-@
-\label{fig:sel}
-\end{figure*}[t]
-
-<<>>=
-odata <- subset(stats.df, s.element=='line' & strategy=='xpercentperunit' & kind=='original')
-rdata <- subset(stats.df, s.element=='line' & strategy=='xpercentperunit' & kind=='randoop')
-odata$s.power
-odata$mutant.reduction
-@
-\subsubsection{x\% selection}
-\begin{figure*}[t]
-<<x.per.sel.line,fig.width=5, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-names=odata$s.power
-x = (1:nrow(odata))
-o.CI.up = as.numeric(odata$mutant.reduction)+as.numeric(odata$sd.reduction)
-o.CI.dn = as.numeric(odata$mutant.reduction)-as.numeric(odata$sd.reduction)
-r.CI.up = as.numeric(rdata$mutant.reduction)+as.numeric(rdata$sd.reduction)
-r.CI.dn = as.numeric(rdata$mutant.reduction)-as.numeric(rdata$sd.reduction)
-plot(odata$mutant.reduction~odata$s.power,xaxt='n', cex=1.5,ylim=c(0,20000), xlab='Power',ylab='Reduction', main='Line: Mutant Reduction vs Power',col='blue',pch=16)
-axis(1, at=x, labels=names)
-arrows(x,o.CI.dn,x,o.CI.up,code=3,length=0.2,angle=90,col='blue')
-points(rdata$mutant.reduction~rdata$s.power,xaxt='n', cex=1.5,ylim=c(0,20000), xlab='Power',ylab='Reduction', main='Line: Mutant Reduction vs Power',col='red',pch=16)
-arrows(x,r.CI.dn,x,r.CI.up,code=3,length=0.2,angle=90,col='red')
-#legend("bottomleft",paste(names,": S.E=",data$se),ncol=6,text.width=5)
-@
-\label{fig:sel}
-\end{figure*}[t]
-
-<<>>=
-odata <- subset(stats.df, s.element=='line' & strategy=='xpercentperunit' & kind=='original')
-rdata <- subset(stats.df, s.element=='line' & strategy=='xpercentperunit' & kind=='randoop')
-odata$s.power
-odata$mutant.reduction
-@
-\subsubsection{x\% selection}
-\begin{figure*}[t]
-<<x.per.sel.line.2,fig.width=5, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-names=odata$s.power
-x = (1:nrow(odata))
-o.CI.up = as.numeric(odata$mutant.reduction)+as.numeric(odata$sd.reduction)
-o.CI.dn = as.numeric(odata$mutant.reduction)-as.numeric(odata$sd.reduction)
-r.CI.up = as.numeric(rdata$mutant.reduction)+as.numeric(rdata$sd.reduction)
-r.CI.dn = as.numeric(rdata$mutant.reduction)-as.numeric(rdata$sd.reduction)
-plot(odata$mutant.reduction~odata$s.power,xaxt='n', cex=1.5,ylim=c(0,100), xlab='Power',ylab='Reduction', main='Line: Mutant Reduction vs Power',col='blue',pch=16)
-axis(1, at=x, labels=names)
-arrows(x,o.CI.dn,x,o.CI.up,code=3,length=0.2,angle=90,col='blue')
-points(rdata$mutant.reduction~rdata$s.power,xaxt='n', cex=1.5,ylim=c(0,100), xlab='Power',ylab='Reduction', main='Line: Mutant Reduction vs Power',col='red',pch=16)
-arrows(x,r.CI.dn,x,r.CI.up,code=3,length=0.2,angle=90,col='red')
-#legend("bottomleft",paste(names,": S.E=",data$se),ncol=6,text.width=5)
-@
-\label{fig:sel}
-\end{figure*}[t]
-
-<<>>=
-odata <- subset(stats.df, s.element=='class' & strategy=='xceilperunit' & kind=='original')
-rdata <- subset(stats.df, s.element=='class' & strategy=='xceilperunit' & kind=='randoop')
-@
-\subsubsection{x\% selection}
-\begin{figure*}[t]
-<<x.per.sel.class.3,fig.width=5, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-names=odata$s.power
-x = (1:nrow(odata))
-o.CI.up = as.numeric(odata$mutant.reduction)+as.numeric(odata$sd.reduction)
-o.CI.dn = as.numeric(odata$mutant.reduction)-as.numeric(odata$sd.reduction)
-r.CI.up = as.numeric(rdata$mutant.reduction)+as.numeric(rdata$sd.reduction)
-r.CI.dn = as.numeric(rdata$mutant.reduction)-as.numeric(rdata$sd.reduction)
-plot(odata$mutant.reduction~odata$s.power,xaxt='n', cex=1.5,ylim=c(0,10), xlab='Power',ylab='Reduction', main='Ceil:Class: Mutant Reduction vs Power',col='blue',pch=16)
-axis(1, at=x, labels=names)
-arrows(x,o.CI.dn,x,o.CI.up,code=3,length=0.2,angle=90,col='blue')
-points(rdata$mutant.reduction~rdata$s.power,xaxt='n', cex=1.5,ylim=c(0,10), xlab='Power',ylab='Reduction', main='Ceil:Class: Mutant Reduction vs Power',col='red',pch=16)
-arrows(x,r.CI.dn,x,r.CI.up,code=3,length=0.2,angle=90,col='red')
-#legend("bottomleft",paste(names,": S.E=",data$se),ncol=6,text.width=5)
-@
-\label{fig:sel}
-\end{figure*}[t]
-
-<<>>=
-odata <- subset(stats.df, s.element=='line' & strategy=='xceilperunit' & kind=='original')
-rdata <- subset(stats.df, s.element=='line' & strategy=='xceilperunit' & kind=='randoop')
-@
-\subsubsection{x\% selection}
-\begin{figure*}[t]
-<<x.per.sel.line.3,fig.width=5, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-names=odata$s.power
-x = (1:nrow(odata))
-o.CI.up = as.numeric(odata$mutant.reduction)+as.numeric(odata$sd.reduction)
-o.CI.dn = as.numeric(odata$mutant.reduction)-as.numeric(odata$sd.reduction)
-r.CI.up = as.numeric(rdata$mutant.reduction)+as.numeric(rdata$sd.reduction)
-r.CI.dn = as.numeric(rdata$mutant.reduction)-as.numeric(rdata$sd.reduction)
-plot(odata$mutant.reduction~odata$s.power,xaxt='n', cex=1.5,ylim=c(0,10), xlab='Power',ylab='Reduction', main='Ceil:Line: Mutant Reduction vs Power',col='blue',pch=16)
-axis(1, at=x, labels=names)
-arrows(x,o.CI.dn,x,o.CI.up,code=3,length=0.2,angle=90,col='blue')
-points(rdata$mutant.reduction~rdata$s.power,xaxt='n', cex=1.5,ylim=c(0,10), xlab='Power',ylab='Reduction', main='Ceil:Line: Mutant Reduction vs Power',col='red',pch=16)
-arrows(x,r.CI.dn,x,r.CI.up,code=3,length=0.2,angle=90,col='red')
-#legend("bottomleft",paste(names,": S.E=",data$se),ncol=6,text.width=5)
-@
-\label{fig:sel}
-\end{figure*}[t]
-
-<<>>=
-odata <- subset(stats.df, s.element=='project' & strategy=='xprobperunit' & kind=='original')
-rdata <- subset(stats.df, s.element=='project' & strategy=='xprobperunit' & kind=='randoop')
-@
-\subsubsection{x\% selection}
-\begin{figure*}[t]
-<<x.per.sel.line.4,fig.width=5, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-names=odata$s.power
-x = c(2:6)
-o.CI.up = as.numeric(odata$mutant.reduction)+as.numeric(odata$sd.reduction)
-o.CI.dn = as.numeric(odata$mutant.reduction)-as.numeric(odata$sd.reduction)
-r.CI.up = as.numeric(rdata$mutant.reduction)+as.numeric(rdata$sd.reduction)
-r.CI.dn = as.numeric(rdata$mutant.reduction)-as.numeric(rdata$sd.reduction)
-plot(odata$mutant.reduction~odata$s.power,xaxt='n', cex=1.5,ylim=c(0,100), xlab='Power',ylab='Reduction', main='Prob:Project: Mutant Reduction vs Power',col='blue',pch=16)
-axis(1, at=x, labels=names)
-arrows(x,o.CI.dn,x,o.CI.up,code=3,length=0.2,angle=90,col='blue')
-points(rdata$mutant.reduction~rdata$s.power,xaxt='n', cex=1.5,ylim=c(0,100), xlab='Power',ylab='Reduction', main='Prob:Project: Mutant Reduction vs Power',col='red',pch=16)
-arrows(x,r.CI.dn,x,r.CI.up,code=3,length=0.2,angle=90,col='red')
-#legend("bottomleft",paste(names,": S.E=",data$se),ncol=6,text.width=5)
-@
-\label{fig:sel}
-\end{figure*}[t]
-
 \subsection{SDL vs Random selection}
@@
 @
-
-\begin{table*}
-\begin{minipage}[h]{0.49\linewidth}
-<<results='asis'>>=
-o <- subset(oprand.x, kind == 'original')
-o.x <- subset(o, select=c('operator', 'r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier'))
-colnames(o.x) <- c('operator', 'r^2', 'm.red', 'm.sd', 'num', 'B*')
-print(xtable(o.x, caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
-@
-\end{minipage}
-\hspace{0.5cm}
-\begin{minipage}[h]{0.49\linewidth}
-<<results='asis'>>=
-r <- subset(oprand.x, kind == 'randoop')
-r.x <- subset(r, select=c('operator','r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier'))
-colnames(r.x) <- c('operator', 'r^2', 'm.red','m.sd', 'num', 'B*')
-print(xtable(r.x, caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
-@
-\end{minipage}
-\end{table*}
-
-\begin{table*}
-\begin{minipage}[h]{0.49\linewidth}
-<<results='asis'>>=
-o <- subset(oprand.l, kind == 'original')
-o.x <- subset(o, select=c('operator', 'r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier'))
-colnames(o.x) <- c('operator', 'r^2', 'm.red', 'm.sd', 'num', 'B*')
-print(xtable(o.x, caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE,size='\\small')
-# , sanitize.text.function = function(x){x}, include.rownames=FALSE)
-@
-\end{minipage}
-\hspace{0.5cm}
-\begin{minipage}[h]{0.49\linewidth}
-<<results='asis'>>=
-r <- subset(oprand.l, kind == 'randoop')
-r.x <- subset(r, select=c('operator','r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier'))
-colnames(r.x) <- c('operator', 'r^2', 'm.red','m.sd', 'num', 'B*')
-print(xtable(r.x, caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
-@
-\end{minipage}
-\end{table*}
-
-\begin{table*}
-\begin{minipage}[h]{0.49\linewidth}
-
-<<results='asis'>>=
-opsel <- subset(stats.df,grepl('^..op', rownames(stats.df)))
-
-o <- subset(opsel, kind == 'original')
-o.x <- subset(o, select=c('operator', 'r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier'))
-colnames(o.x) <- c('operator', 'r^2', 'm.red', 'm.sd', 'num', 'B*')
-print(xtable(o.x, caption='Original', label='table:selo'), include.rownames=FALSE, floating=FALSE,size='\\small')
-# , sanitize.text.function = function(x){x}, include.rownames=FALSE)
-@
-\end{minipage}
-\hspace{0.5cm}
-\begin{minipage}[h]{0.49\linewidth}
-
-<<results='asis'>>=
-r <- subset(opsel, kind == 'randoop')
-r.x <- subset(r, select=c('operator','r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier'))
-colnames(r.x) <- c('operator', 'r^2', 'm.red','m.sd', 'num', 'B*')
-print(xtable(r.x, caption='Randoop', label='table:selr'), include.rownames=FALSE, floating=FALSE,size='\\small')
-@
-\end{minipage}
-\end{table*}
 

### 2014-03-08 src/analysis.Rnw
update

@@
 @
-\caption{The effect of loc (external) reduction. All are above 0.98 $R^2$.}
+\caption{The effect of one element selection, All are above 0.98 $R^2$.}
 \label{fig:onesel}
@@
 The values are given in Table~\ref{tbl:onesel}, and its visaulization is in Figure~\ref{fig:onesel}.
+% ----------------------------------------------------------------------
+<<oth>>=
+stats.o <- stats.rest
+o.stats.sel.o <- subset(o.f(stats.o), select=sel.colnames)
+r.stats.sel.o <- subset(r.f(stats.o), select=sel.colnames)
+stats.rest <- subset(stats.rest, !grepl('^o[.]', operator))
+colnames(o.stats.sel.o) <- new.colnames
+colnames(r.stats.sel.o) <- new.colnames
+
+@
+
+\begin{table*}
+\begin{minipage}[h]{0.49\linewidth}
+<<results='asis'>>=
+print(xtable(o.stats.sel.o, caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
+@
+\end{minipage}
+\hspace{0.5cm}
+\begin{minipage}[h]{0.49\linewidth}
+<<results='asis'>>=
+print(xtable(r.stats.sel.o, caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
+@
+\end{minipage}
+\bigskip
+\caption {Others}
+\label{tbl:osel}
+\end{table*}
+
 % ----------------------------------------------------------------------

### 2014-03-08 src/analysis.Rnw
update

--- 2014-03-08 src/analysis.Rnw
@@
 % ----------------------------------------------------------------------
+% <<oth>>=
+% stats.o <- subset(stats.rest, !grepl('^op', operator))
+% o.stats.sel.o <- subset(o.f(stats.o), select=sel.colnames)
+% r.stats.sel.o <- subset(r.f(stats.o), select=sel.colnames)
+% stats.rest <- subset(stats.rest, grepl('^op', operator))
+% colnames(o.stats.sel.o) <- new.colnames
+% colnames(r.stats.sel.o) <- new.colnames
+% @
+% 
+% \begin{table*}
+% \begin{minipage}[h]{0.49\linewidth}
+% <<results='asis'>>=
+% print(xtable(o.stats.sel.o, caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
+% @
+% \end{minipage}
+% \hspace{0.5cm}
+% \begin{minipage}[h]{0.49\linewidth}
+% <<results='asis'>>=
+% print(xtable(r.stats.sel.o, caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
+% @
+% \end{minipage}
+% \bigskip
+% \caption {Others}
+% \label{tbl:osel}
+% \end{table*}
+% 
+% ----------------------------------------------------------------------
+
+\subsection{Operator Selection}
+<<opsel>>=
+stats.op <- subset(stats.rest, grepl('^(op|TSDL)', operator))
+o.stats.sel.op <- subset(o.f(stats.op), select=sel.colnames)
+r.stats.sel.op <- subset(r.f(stats.op), select=sel.colnames)
+stats.rest <- subset(stats.rest, !grepl('^(op|TSDL)', operator))
+colnames(o.stats.sel.op) <- new.colnames
+colnames(r.stats.sel.op) <- new.colnames
+@
+
+\begin{table*}
+\begin{minipage}[h]{0.49\linewidth}
+<<results='asis'>>=
+print(xtable(o.stats.sel.op, caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
+@
+\end{minipage}
+\hspace{0.5cm}
+\begin{minipage}[h]{0.49\linewidth}
+<<results='asis'>>=
+print(xtable(r.stats.sel.op, caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
+@
+\end{minipage}
+\bigskip
+\caption {Operator Selection}
+\label{tbl:opsel}
+\end{table*}
+
+For operator selection, we approximated the operators as far as possible from the research works into the operators exposed by PIT. The results of this are provided in Table~\ref{tbl:opsel}.
 

### 2014-03-08 src/results.Rnw
update

@@
 \label{sec:results}
-We see from the data that random sampling has a higher $R^2$, and also approximates the all  mutations score better.
-However, caveat emptor. There is a difference between the number of mutators for SDL and RAND. If our approximation was right, we should have gotten nearly same number of mutators. However
-The number of mutators in RND is
- Sexpr{sum(m.lrnd.pit.mutation.total) / sum(m.sdl.pit.mutation.total)} times SDL.
-
-The total mutants for all is Sexpr{sum(m.pit.mutation.total)}, for rnd is Sexpr{sum(m.lrnd.pit.mutation.total)} and for sdl is Sexpr{sum(m.sdl.pit.mutation.total)}
+Our analysis of results suggests that different kinds of operator selection criterias can actually provide better reduction in mutants while not reducing the approximatin accuracy below acceptable limits.

### 2014-03-08 src/conclusion.Rnw
update

@@
 
-\begin{enumerate}
-\item [x] For op-selection to work, the distributions of mutations across different projects has to be similar enough. This can be checked by t-test.
-\item [TODO] We should check if the distribution significantly different too.
-\item [DONE] Use sampling
-\item [DONE] Check on randoop samples too
-\item [NO] Implement bomb (athrow) and see its mutation score, and see how close it comes.
-\item [DONE] Compare random selection with class, method, and mutagen sampling.
-\item [TODO] Report time for each, as cost.
-\item [TODOX] Find the mutant count to LOC multiplier, and use it to get the probability of choosing for each project.
-\end{enumerate}
+% For op-selection to work, the distributions of mutations across different projects has to be similar enough. This can be checked by t-test.
+% For mutant clustering
+%TODO Report time for each, as cost.
+
+Our analysis suggests that random sampling of mutants can help reduce the computational requirements to an extremely large extant while still staying within acceptable accuracy limits.
+An interesting finding is that statement deletion did produce as good accuracy in predicting final mutation score as random sampling techniques that offered comparable mutation reduction.

### 2014-03-08 src/analysis.Rnw
update

@@
 <<x.per.sel.round,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+#myopts <- theme(panel.background = element_blank())
+#myopts <-   theme_bw() +
+#  opts(axis.line = theme_segment(colour = "black"),
+#    panel.grid.major = theme_blank(),
+#    panel.grid.minor = theme_blank(),
+#    panel.border = theme_blank(),
+#    panel.background = theme_blank()) 
+  #theme with white background
+myopts <- theme_bw() +
+  #eliminates background, gridlines, and chart border
+  theme(
+    plot.background = element_blank()
+   ,panel.grid.major = element_blank()
+   ,panel.grid.minor = element_blank()
+   ,panel.border = element_blank()
+  ) + 
+  #draws x and y axis line
+  theme(axis.line = element_line(color = 'black'))
+myopts <-  theme_classic() 
+#+ opts(strip.background = theme_rect(colour = 'NA', fill = 'NA')) + opts(strip.text.y = theme_text(colour = 'white')) + theme(axis.line = element_line(color = 'black'))
+
 o.xp <- subset(o.processed, grepl('^r[.].*.m[.]red',ind))
@@
   stat_boxplot(geom ='errorbar')+
-  geom_boxplot() + facet_wrap(~type)
+  geom_boxplot() + facet_wrap(~type)+ myopts
 @
@@
   stat_boxplot(geom ='errorbar')+
-  geom_boxplot() + facet_wrap(~type)
+  geom_boxplot() + facet_wrap(~type) + myopts
 @
@@
 
-For operator selection, we approximated the operators as far as possible from the research works into the operators exposed by PIT. The results of this are provided in Table~\ref{tbl:opsel}.
+For operator selection, we approximated the operators as far as possible from the research works into the operators exposed by PIT.
+The results of this are provided in Table~\ref{tbl:opsel}.
+The subsumption graphs are provided in Figure~\ref{fig:subsumptiono}
+% TODO : Check if this makes sense.
+\begin{figure*}[t]
+\includegraphics[totalheight=6cm]{fig/original.pdf}
+\caption{Subsumption Original}
+\label{fig:subsumptiono}
+\end{figure*}
 
+%\begin{figure*}[t]
+%\includegraphics[totalheight=6cm]{fig/randoop.pdf}
+%\caption{Subsumption Randoop}
+%\label{fig:subsumptionr}
+%\end{figure*}[t]
+
+% ----------------------------------------------------------------------
+\subsection{Mutant Clustering}
+To be added later.
 % IGNORED FROM HERE.

### 2014-03-08 src/analysis.Rnw
update

@@
 <<x.per.sel.round,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+theme_set(theme_bw(24))
 #myopts <- theme(panel.background = element_blank())
@@
   theme(axis.line = element_line(color = 'black'))
-myopts <-  theme_classic() 
+myopts <-  opts() #theme_classic() 
 #+ opts(strip.background = theme_rect(colour = 'NA', fill = 'NA')) + opts(strip.text.y = theme_text(colour = 'white')) + theme(axis.line = element_line(color = 'black'))

### 2014-03-08 src/paper.Rnw
update

@@
 @
-<<results, child='conclusion.Rnw'>>=
+<<conclusion, child='conclusion.Rnw'>>=
 @

### 2014-03-09 etc/abstract.tex
update
udpate

@@
 Mutation analysis is a metric for measuring the quality of test suites.
-However, its exorbitant computational requirements makes it hard to use in practice.
+However, it is computationally intensive compared to other measures which it hard to use in practice.
 Choosing a smaller subset of mutations to run is a simple approach that can alleviate this problem.
@@
 Our experiments rank sampling criterias that can be used by testers according how much mutant reduction is achieved, their ability to predict the final mutation score, the relative effect of unit increase in sampled mutation score on the final score, and also the time required for the run.
+We also find that sampling techniques work better than operator selection methods including statement deletion in both mutation reduction and accuracy of approximation to the full mutation score.
 

### 2014-03-09 src/analysis.Rnw
udpate

--- 2014-03-08 src/analysis.Rnw
@@
 @
-
 \begin{table*}
@@
 <<results='asis'>>=
-print(xtable(o.stats.sel.xp, caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
+print(xtable(subset(o.stats.sel.xp, grepl('^r[.]', operator)), caption='Original', label='table:rando', main='Original'), include.rownames=FALSE, floating=FALSE, size='\\small')
 @
@@
 <<results='asis'>>=
-print(xtable(r.stats.sel.xp, caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
+print(xtable(subset(r.stats.sel.xp, grepl('^r[.]', operator)), caption='Randoop', label='table:randr', main='Randoop'), include.rownames=FALSE, floating=FALSE,size='\\small')
 @
@@
 \bigskip
-\caption {The x\% random selection criteria results.}
+\caption {The round(x)\% random selection criteria results.}
 \label{tbl:xsel}
+\end{table*}
+
+\begin{table*}
+\begin{minipage}[h]{0.49\linewidth}
+<<results='asis'>>=
+print(xtable(subset(o.stats.sel.xp, grepl('^rr[.]', operator)), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
+@
+\end{minipage}
+\hspace{0.5cm}
+\begin{minipage}[h]{0.49\linewidth}
+<<results='asis'>>=
+print(xtable(subset(r.stats.sel.xp, grepl('^rr[.]', operator)), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
+@
+\end{minipage}
+\bigskip
+\caption {The sample(x)\% random selection criteria results.}
+\label{tbl:xsel2}
 \end{table*}
@@
 <<x.per.sel.round,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-#myopts <- theme(panel.background = element_blank())
+theme_set(theme_bw(12))
+myopts <- theme(panel.background = element_blank())
 #myopts <-   theme_bw() +
@@
   #theme with white background
-myopts <- theme_bw() +
+#myopts <- theme_bw() +
   #eliminates background, gridlines, and chart border
-  theme(
-    plot.background = element_blank()
-   ,panel.grid.major = element_blank()
-   ,panel.grid.minor = element_blank()
-   ,panel.border = element_blank()
-  ) + 
+#  theme(
+#    plot.background = element_blank()
+#   ,panel.grid.major = element_blank()
+#   ,panel.grid.minor = element_blank()
+#   ,panel.border = element_blank()
+#  ) +
   #draws x and y axis line
-  theme(axis.line = element_line(color = 'black'))
-myopts <-  theme_classic() 
+#  theme(axis.line = element_line(color = 'black'))
+#myopts <-  opts() #theme_classic()
 #+ opts(strip.background = theme_rect(colour = 'NA', fill = 'NA')) + opts(strip.text.y = theme_text(colour = 'white')) + theme(axis.line = element_line(color = 'black'))
 
-o.xp <- subset(o.processed, grepl('^r[.].*.m[.]red',ind))
+# TODO - replace by o.processed.
+o.xp <- subset(r.processed, grepl('^r[.].*.m[.]red',ind))
 ggplot(subset(o.xp, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
@@
 <<x.per.sel.sample,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-o.xp <- subset(o.processed, grepl('^rr[.].*.m[.]red',ind))
+o.xp <- subset(r.processed, grepl('^rr[.].*.m[.]red',ind))
 ggplot(subset(o.xp, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
@@
 @
-\caption{The effect of sample(x) reduction. All are above 0.90 $R^2$.}
+\caption{The effect of sample(x) reduction(randoop). All are above 0.90 $R^2$.}
 \label{fig:xsamplesel}
@@
 \subsection{Operator Selection}
+\begin{figure*}[t]
+<<op.all,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+#with(subset(stats.df,r.square > 0.9),plot(mutant.reduction, (1-r.square)*100, pch='*', col=as.factor(strategy)))
+# "kind" "operator" "s.power" "s.element" "strategy" "mutant.reduction" "sd.reduction"
+#  "sample" "r.square" "score.multiplier" "p.value"
+
+df <-  subset(stats.df, r.square>=0.9 & (sd.reduction * 2) < mutant.reduction)
+df$sqr <- 1 - df$r.square
+df$type <- with(df, as.factor(
+      ifelse(grepl('line',operator), 'line',
+        ifelse(grepl('block',operator), 'block',
+        ifelse(grepl('method',operator), 'method',
+          ifelse(grepl('class',operator), 'class',
+            ifelse(grepl('project',operator), 'project',
+              NA)))))))
+df$strat <- with(df,
+    ifelse(grepl('perunit', strategy), 'xpercent',
+      ifelse(grepl('op',strategy), 'opsel',
+        ifelse(grepl('one',strategy), 'oneperelm',
+          ifelse(grepl('elem',strategy), 'loc', 'other'
+            )))))
+ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(size=sqr, color=type))
+@
+\end{figure*}
+\begin{figure*}[t]
+<<op.all.2,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(shape=strat, color=type))
+@
+\end{figure*}
+\begin{figure*}[t]
+<<op.all.3,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+dfd <- subset(df, !(strategy %in% c('op','opsel')) )
+ggplot(dfd, aes(sd.reduction, mutant.reduction)) + geom_point(aes(shape=type, color=sqr)) + facet_wrap(~strategy) + theme(axis.text.x = element_text(angle = 90, hjust = 1))
+@
+\end{figure*}
 <<opsel>>=

### 2014-03-09 src/related.Rnw
update
related -- partial

@@
 \label{sec:related}
-Mathur\cite{mathur1991performance, wong1993mutation, wong1995reducing} first mentioned the idea of constrained mutation in a one-pager.
-This was taken up by Offut et al.\cite{offutt1993experimental}.
-(Offutt states in his 1993 paper\cite{offutt1993experimental} that Mathur has in 1991\cite{mathur1991performance} suggested the constrined/selective mutation.
-However, that paper does not propose it at all.
-It says we are experimenting with an idea, and that is it.
-It is in 1995\cite{wong1995reducing} that the idea is actually proposed, notably after Offutt has written about its effectiveness.
-$\ddot\smile$ - time travel?).
+In this section we summarize the related work. There have been
+different approaches to reduce the cost of mutation analysis.
+Offutt \cite{} categorize them in three categories: Do Fewer, 
+Do Smarter, Do Faster approaches.
+
+\subsection{Do Fewer}
+The idea of using a subset of mutants instead of all of them started
+by Mathur\cite{mathur1991performance} and 
+further have developed by Wong et al.\cite{wong1993mutation, wong1995reducing}
+ and Offut et al. \cite{offutt1993experimental}.
+Each of them targeted the mutation operators of Mothra \cite{Mothra}.
+Mathur \cite{mathur1991performance} suggested removal of two mutation operators
+has little effect on the effectiveness of mutation testing.
+Offut et al. \cite{offutt1993experimental} experiment removal of 
+upto six mutation operators. They observe that the reduction has
+little effect on the mutation score.
+Wong and Mathur \cite{wong1995reducing} suggested two operators in Mothra system
+that could approximate mutation score. They also proposed \%x sampling.
+
 The idea is that normal mutation has quadratic complexity on variable references while eliminatng the most fecund mutagens (SVR and ASR) achieves linear complexity on program size, while still approximating the full mutation score closely.
@@
 
-% On Mutation and Dataflow : W.E Eong
-Wong et al~\cite{wong1994on} suggests random sampling of mutants from the complete population.
-
-Wong and Mathur suggests constrained mutation~\cite{} which chooses specific mutation operators only.
-
 % Empirical Evaluation of the Statement Deletion Mutation Operator : Offutt

### 2014-03-09 src/intro.Rnw
update

@@
 % 2. State your contributions
-Mutation analysis is a method of evaluation of quality of test-suites. It involves generation
-of  mutants by making syntactic changes to the program. First (higher) order mutants
-have one (more) syntactic distance to the origianl program.
-Mutants are used to evaluate the effectiveness of test-suites 
-~\cite{lipton1971fault, ammann2008introduction}.
-Studies like ~\cite{andrews2005mutation} have shown that mutation score 
-are predictors of the real fault detection of a test suits.
+Mutation analysis is a method of evaluation of quality of test-suites. It involves producing
+a family of mutants with simple differences from the original program, and evaluating the
+effectiveness of test-suites against the these mutants~\cite{lipton1971fault, ammann2008introduction}.
+Previous research~\cite{andrews2005mutation} suggests that mutations thus introduced behave
+in a fashion similar to the real-faults with respect to the difficulty of detection.
 
-A major impediment to wider adoption of mutation analysis is its high computational cost.
-Set of first oder mutants of a moderate size program can be very large, 
-which renders mutation analysis of a test-suite against all the first
-order mutants prohibitively time-consuming.
+One of the impediments to wider adoption of mutation analysis is its high computational cost.
+The set of simple mutants of a moderate sized program can be very large, and renders
+mutation analysis prohibitively time-consuming.
 
@@
 representative set of mutants~\cite{offutt2001mutation,jia2011analysis}-- often called the
-``do fewer'' approach. This approach can be generally divided into 
-selective strategies and sampling strategies.
+``do fewer'' approach. This approach can be generally divided into selective strategies
+and sampling strategies.
 
 Selective mutation strategies attempt to select a representative subset of operators based
-on heuristics and statistical analysis. They suggest applying these subsets instead of the 
-applying the whole gamut of mutation operators~\cite{offutt1993anexperimental,untch2009onreduced}.
+on heuristics and statistical analysis, and applying this subset of operators to generate mutants
+instead of applying the whole gamut of mutation operators~\cite{offutt1993anexperimental,untch2009onreduced}.
 
 Sampling strategies seek to randomly select smaller representative mutants.
-This was investigated first by Acreed~\cite{acree1980mutation} and Budd~\cite{budd1980mutation},
+This was investigated first by Acree~\cite{acree1980mutation} and Budd~\cite{budd1980mutation},
 who proposed using only $x$\% of the mutants produced. The studies by Wong and
-Mathur, found that random sampling with ratio as low as 10\% could provide
+Mathur found that random sampling with ratio as low as 10\% could provide
 accurate results~\cite{jia2011analysis}.
@@
 
-While all these areas of research has been relatively successful in reducing the number of mutants
-produced, there has been comparitively few studies that compares the approaches taken. The studies
-that has been attempted so far, has been limited by the comparitively small number of sampled projects.
+A few recent works~\cite{zhang2010icse,zhang2013ase} have investigated the relative merits of
+random sampling strategies and operator selection. It was found that while random sampling can
+generally perform equal to or better than operator selection, a strategy that combined random
+sampling with program elements paid superior dividends.
 
-\noindent\textbf{Contribution.} Contributions of this paper are he following.
+However, as pointed out by Zhang et al.~\cite{zhang2013ase}, the field has a serious lacuna in
+large scale research, both in the size of the programs studied, and in the number and diversity
+of programs, which reduces our confidence in the espoused results. This is true both for
+selective mutation, sampling strategies, and also for comparatively newer studies that attempt
+to join them together.  This is particularly worrisome if mutation analysis is to gain wider
+acceptance among testing professionals. Further quite a few of the influential studies has been
+conducted on older programming languages such as Fortran with operators specific to it, which
+may not carry over to the newer and popular languages such as Java. Finally, with the modern
+research into the ``do-smarter'' approach which allows byte code based mutation -- thus eliminating
+the compilation step -- operators based on source code modification is no longer be applicable, and
+their equivalents in the bytecode needs to be found and compared with other approaches. A detailed
+discussion of these issues can be found in Section~\ref{sec:relatedwork}.
+
+% RAHUL>AMIN: I find the non-bulleted contributions better flowing as I can work the references
+% to other sections into it. Let me know if you have a better idea (As it stands neither my
+% previous wording, nor your bulleted list reads good)
+We have attempted to rectify this situation with a large scale study of industrial programs.
+As detailed in Section~\ref{sec:methodology}, we sample 188 real world Java programs from Github, with
+size ranging from 50loc to 100kloc, which makes our inferences relatively strong, and widely applicable.
+We provide the results from running both original human generated test-suites, and also programmatically
+generated test-suites, increasing the applicability of our findings to both researchers who seek to
+compare test-suites quickly, and to industrial software testers who might be looking for a way to reduce
+the time of their build cycle when using mutation coverage. The Section~\ref{sec:methodology} discusses
+the sampling strategies attempted, and the operator selection strategies in detail, and the results of
+our experiment are given in Section~\ref{sec:results}, followed by detailed discussion of what it implies
+in section ~\ref{sec:discussion}. The research concludes in Section~\ref{sec:conclusion}.
+
+Our specific contributions in this paper are listed as follows:
+
 \begin{itemize}
-\item It compares a large number of various mutation sampling and selection strategies (Section~\ref{sec:analysis}).
-\item It seek sto improve the statistical confidence in our results by utilizing a much larger sample of projects
-      (188 projects) from the open source repository at Github~\cite{github}, using both original and automatically
-      generated test-suites using Randoop~\cite{randoop} (Section~\ref{sec:methodology}). 
-\item It analyses the results and suggest strategies (Section~\ref{sec:results}).
+\item Our study is the largest so far in terms of both the size of programs involved, and the number of
+  programs analyzed for ``do-fewer'' strategies, which makes our inferences stronger and widely applicable.
+\item We compare a large number of ``do-fewer'' strategies, especially with respect to their predictive
+  power over the final mutation score.
+\item Our sampling strategies include some that were suggested by other researchers, and also a few novel
+  strategies that has not been published elsewhere.
+\item Our recommendations are valid for both testing researchers who might be comparing programmatically
+  generated test-suites, and software testing professionals working on real test-suites.
 \end{itemize}
+%We make the following contributions:
+%\begin{itemize}
+%\item We compare a large number of mutation sampling and selection strategies (Section~\ref{sec:analysis}).
+%\item It seek sto improve the statistical confidence in our results by utilizing a much larger sample of projects
+%      (188 projects) from the open source repository at Github~\cite{github}, using both original and automatically
+%      generated test-suites using Randoop~\cite{randoop} (Section~\ref{sec:methodology}). 
+%\item It analyses the results and suggest strategies (Section~\ref{sec:results}).
+%\end{itemize}
 
@@
 % \begin{comment}
-%   These approach relies on the fact that some of the mutagens generate a large number of variants, and hence produce highly redundant test cases.
-Previous research suggested that elimination of mutagens with high fertility results in the reduction of total number of mutations produced, and hence reduces the computational requirements.
-%
-%   % TODO check the survey again on selective mutation.
-%
-%   It was recently questioned whether this approach indeed resulted in a tangible improvement over random selection of mutants\cite{zhang2010operator}, which did not find operator based selection to be better than random selection.
-%
-%
-%   Another research, initially by Unch\cite{untch2009onreduced} and recently by Deng et al.\cite{deng2013empirical} suggests using software deletion operator since it produces the least number of mutants (smallest neighborhood).
-The researchers were able to obtain a close approximation of original mutant score with significant savings with this approach.
-%
-%   However, our previous research suggests that mutation coverage is closely predicted by statement coverage, this suggests that any criteria that forces accounting of the impact of each statement should provide a close approximation to the full mutation score.
-Hence, our research suggests that SDL works because it forces accounting of each line, and a random sampling criteria that provides the same criteria should result in similar results.
-%
-%   In our analysis, we find that a random sampling approach that randomly chose a single mutant per line was found to have a better correlation with the full mutation score than that obtained by SDL.
-Further it was also found that the mutation score produced by random sampling was closer to the full mutation score than that produced by SDL.
-%
 % Order of most fertile operators for N-selective operator selection.
@@
 %
-%
 % NON_VOID_METHOD_CALLS VOID_METHOD_CALLS CONSTRUCTOR_CALLS

### 2014-03-09 src/paper.Rnw
update

--- 2014-03-08 src/paper.Rnw
@@
 @
-<<results, child='conclusion.Rnw'>>=
+<<results, child='discussion.Rnw'>>=
 @
+<<conclusion, child='conclusion.Rnw'>>=
+@

### 2014-03-09 src/results.Rnw
update

@@
 Our analysis of results suggests that different kinds of operator selection criterias can actually provide better reduction in mutants while not reducing the approximatin accuracy below acceptable limits.
+
+\subsection{SDL vs Random selection}
+\begin{figure*}[t]
+<<sdl.x,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+par(mfrow=c(2,2))
+with(o.pit.all, plot(all.cov~TSDL.cov, pch='+', main='Original SDL'))
+with(o.pit.all, plot(all.cov~l.1x1_per_line.cov, pch='+', main='Original 1 per line'))
+with(r.pit.all, plot(all.cov~TSDL.cov, pch='+', main='Randoop SDl'))
+with(r.pit.all, plot(all.cov~l.1x1_per_line.cov, pch='+', main='Randoop 1 per line'))
+@
+\label{fig:sdl1}
+\caption{Statement Deletion vs One per line.}
+\end{figure*}
+<<results='asis'>>=
+oprand <- subset(stats.df,!grepl('^..op', rownames(stats.df)))
+
+oprand.x <- subset(oprand,grepl('^.1x[0-9]+_per_', operator))
+oprand.l <- subset(oprand,!grepl('^.1x[0-9]+_per_', operator))
+@

### 2014-03-09 src/analysis.Rnw
update

@@
 df$sqr <- 1 - df$r.square
+df$mult <- 1 - df$score.multiplier
 df$type <- with(df, as.factor(
@@
 @
+\caption{The mean reduction of mutants vs its standard deviation.
+The sqr represents (1-$R^2$), i.e smaller is good.
+Only those observations with $R^2 > 0.9$ and $2\times $ standard deviation > mean reduction is shown here.
+}
+\label{fig:fullimgsize}
 \end{figure*}
@@
 @
+\caption{The mean reduction of mutants vs its standard deviation. Only those observations with $R^2 > 0.9$ and $2\times $ standard deviation > mean reduction is shown here. }
 \end{figure*}
+
+\begin{figure*}[t]
+<<op.all.4,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(shape=strat, color=mult))
+@
+\caption{The mean reduction of mutants vs its standard deviation.
+Only those observations with $R^2 > 0.9$ and $2\times $ standard deviation > mean reduction is shown here.
+The color represents the (1-multiplier) to the sampled mutation score to get final score }
+\end{figure*}
+
 \begin{figure*}[t]
@@
 @
+\label{fig:fullimgshape}
 \end{figure*}
@@
 To be added later.
-% IGNORED FROM HERE.
-\if 0
-\subsection{SDL vs Random selection}
-\begin{figure*}[t]
-<<sdl.1,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-par(mfrow=c(2,2))
-with(o.pit.all, plot(all.cov~TSDL.cov, pch='+', main='Original SDL'))
-with(o.pit.all, plot(all.cov~l.1x1_per_line.cov, pch='+', main='Original 1 per line'))
-with(r.pit.all, plot(all.cov~TSDL.cov, pch='+', main='Randoop SDl'))
-with(r.pit.all, plot(all.cov~l.1x1_per_line.cov, pch='+', main='Randoop 1 per line'))
-@
-\label{fig:sdl1}
-\caption{Statement Deletion vs One per line.}
-\end{figure*}
-<<results='asis'>>=
-oprand <- subset(stats.df,!grepl('^..op', rownames(stats.df)))
-
-oprand.x <- subset(oprand,grepl('^.1x[0-9]+_per_', operator))
-oprand.l <- subset(oprand,!grepl('^.1x[0-9]+_per_', operator))
-@
-
-\subsection{Correlation Analysis}
-
-$ \mu\{ M_{all}| M_{sample} \} = 0 + \beta_1 \times M{sample}  $
-
-The interesting part is (1) the $\beta_1$ coefficient which tells how much we must multiply the  sampled/selected score to get original score, and $R^2$ which tells us how close the score is.
-
-\subsubsection{sdl.mut.avg and mut.avg}
-
-% <<>>=
-% c <- cor(subset(m, select=c(sdl.mut.avg, mut.avg)) , method="kendall", use="pairwise")['sdl.mut.avg', 'mut.avg']
-% d <- cor(subset(m, select=c(lrnd.mut.avg, mut.avg)) , method="kendall", use="pairwise")['lrnd.mut.avg', 'mut.avg']
-% @
-$ \mu_\{M_{all} | M_{sdl}\} = Sexpr{sdl.est} \times M_{sdl} \text{ : } R^2 = Sexpr{sdl.r} \text{,} \tau_{\beta} = Sexpr{c}$
-
-\subsubsection{lrnd.mut.avg and mut.avg}
-
-$ \mu_\{M_{all} | M_{rnd}\} = Sexpr{rnd.est} \times M_{rnd} \text{ : } R^2 = Sexpr{rnd.r} \text{,} \tau_{\beta} = Sexpr{d}$
-
-\subsection{Regression Analysis}
-The next question we will tackle is if there exist a difference at all between SDL mutagen and the random sampling.
-We can perform two statistical tests to answer this question.
-For the first, we run a simple paired t-test.
-
-%<<>>=
-%s <- t.test(lrnd.mut.avg, sdl.mut.avg, paired=T)
-%@
-
-The paired t-test failed to sufficient difference between the two distributions with a two-sided p-value of Sexpr{s.p.value}.
-That is, we do not have sufficient evidence to conclude that the two distributions are different.
-
-The second approch is convoluted (I am a little unclear here.). We try to predict the original mutation score using the mutation score from both sdl and random sampling.
-Our full model is
-
-$ \mu_\{M_{all} | M_{sdl}, M_{rnd}\} = 0 + \beta_1 {sdl} + \beta_2 M_{rnd} + \beta_3 M_{sdl} M_{rnd}  $
-\begin{small}
-% <<results='asis'>>=
-% s <- subset(m, select=c(mut.avg,sdl.mut.avg))
-% s$type <- 'sdl'
-% colnames(s) <- c('mut', 'sample', 'type')
-% r <- subset(m, select=c(mut.avg,lrnd.mut.avg))
-% r$type <- 'rnd'
-% colnames(r) <- c('mut', 'sample', 'type')
-% all <- rbind(s, r)
-% fm <- with(all, lm(mut ~ sample + type + sample:type))
-% sm <- anova(fm)
-% print(xtable(sm,caption="My caption"), size="\\small")
-% @
-\end{small}
-
-We see that both type and sample:type are non-significant for predicting the final model, and sequentially removing them does not change the effectiveness.
-Hence, the techniques random sampling and statement deletion operator do not have any difference.
-
-\begin{figure*}[t]
-% <<tplots, fig.width=5, fig.height=5, out.width='.45\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-% t_f <- sdl.time~lrnd.time
-% plot(t_f, main='SDL ~ RND',pch='*')
-% abline(lm(t_f), col='red')
-% detach(m)
-% @
-\caption{Time}
-\label{fig:caddrm}
-\end{figure*}
-
-\begin{figure*}[t]
-\includegraphics[totalheight=6cm]{fig/original.pdf}
-\caption{Subsumption Original}
-\label{fig:subsumptiono}
-\end{figure*}[t]
-
-\begin{figure*}[t]
-\includegraphics[totalheight=6cm]{fig/randoop.pdf}
-\caption{Subsumption Randoop}
-\label{fig:subsumptionr}
-\end{figure*}[t]
-%% END HERE
-\fi

### 2014-03-09 src/results.Rnw
update

@@
 \label{sec:results}
+The first observation from our different kinds of random sampling is that the standard deviation tends to increase with the increase in mutation reduction.
+While this in itself is not unexpected, what is unexpected is the difference in the increase in standard deviation between different kinds of sampling techniques.
+Our observations suggests that random sampling based on the entire project has a much lower growth of standard deviation (and hence higher stability of results) than sampling in lower scopes.
+Further, we also observe that the rate of increase in standard deviation actually increases as we go into more finer scopes such as class, method and line, with line having the largest increase in standard deviation.
+
+Further, looking at the reduction of mutants in Figure~\ref{fig:fullimgshape} and Figure~\ref{fig:fullimgsize}, we see that the x\% selection strategy is generally the best strategy, and it is generally best to stick with random selection from the entire project.
+This too is perhaps not unexpected, since sampling from the entire population rather than its elements should provide a better correlation with the final score.
+
 Our analysis of results suggests that different kinds of operator selection criterias can actually provide better reduction in mutants while not reducing the approximatin accuracy below acceptable limits.

### 2014-03-09 src/analysis.Rnw
update

@@
 # TODO - replace by o.processed.
-o.xp <- subset(r.processed, grepl('^r[.].*.m[.]red',ind))
+o.xp <- subset(o.processed, grepl('^r[.].*.m[.]red',ind))
 ggplot(subset(o.xp, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
@@
 <<x.per.sel.sample,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-o.xp <- subset(r.processed, grepl('^rr[.].*.m[.]red',ind))
+o.xp <- subset(o.processed, grepl('^rr[.].*.m[.]red',ind))
 ggplot(subset(o.xp, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
@@
 @
-\caption{The effect of sample(x) reduction(randoop). All are above 0.90 $R^2$.}
+\caption{The effect of sample(x) reduction. All are above 0.90 $R^2$.}
 \label{fig:xsamplesel}

### 2014-03-09 src/analysis.Rnw
update

@@
 new.colnames <- c('operator', 'r^2',      'm.red',            'm.sd',         'num',    'B*')
-stats.xp <- subset(stats.df, grepl('^(r|rr)[.]', operator)) # We are ignoring ceil here. add rc if needed.
+stats.xp <- subset(stats.df, grepl('^(r|rr|rc)[.]', operator)) # We are ignoring ceil here. add rc if needed.
 
@@
 \caption {The sample(x)\% random selection criteria results.}
+\label{tbl:xsel2}
+\end{table*}
+
+\begin{table*}
+\begin{minipage}[h]{0.49\linewidth}
+<<results='asis'>>=
+print(xtable(subset(o.stats.sel.xp, grepl('^rc[.]', operator)), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
+@
+\end{minipage}
+\hspace{0.5cm}
+\begin{minipage}[h]{0.49\linewidth}
+<<results='asis'>>=
+print(xtable(subset(r.stats.sel.xp, grepl('^rc[.]', operator)), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
+@
+\end{minipage}
+\bigskip
+\caption {The ceil(x)\% random selection criteria results.}
 \label{tbl:xsel2}

### 2014-03-10 src/related.Rnw
related work

@@
 different approaches to reduce the cost of mutation analysis.
-Offutt \cite{} categorize them in three categories: Do Fewer, 
-Do Smarter, Do Faster approaches.
+Jia and Harman \cite{jia2011analysis} have categorized them into two
+broad categories: Mutation Reduction and Execution Reduction.
 
-\subsection{Do Fewer}
+\subsection{Mutant Reduction}
 The idea of using a subset of mutants instead of all of them started
@@
 Wong and Mathur \cite{wong1995reducing} suggested two operators in Mothra system
-that could approximate mutation score. They also proposed \%x sampling.
+that could approximate mutation score.
 
-The idea is that normal mutation has quadratic complexity on variable references while eliminatng the most fecund mutagens (SVR and ASR) achieves linear complexity on program size, while still approximating the full mutation score closely.
-They propose N-selective mutation which avoids N most fertile mutagens.
-Wong \cite{wong1995reducing} compares the effect of x\% mutation selection, and abs/ror constrained mutation.
-According to Wong, this is different from selective mutation in that only the most fecund operators are included rather than excluded.
-He finds that there is no evidence to suggest one over the other.
-Offutt\cite{offutt1993experimental} does not compare the effectivenss of selective mutation with x\% mutation.
-He also defines the concept of {\it operator strength} for an operator, which is defined as the total number of mutants that are killed by test data that is generated to kill only the mutants generated by that operator.
-He further posits that the mutagens with greatest strength may be the most useful ones.
-%(test data generated to eliminate variants of one operator may remove the mutants of other kinds too.)
-This is taken up later by Mresa\cite{mresa1999efficiency} et al.
-who used the cost of detection of mutants as a means of selection, and uses it to define another set of operators (san, aor, sdl, ror, uoi).
-They also find that if very high mutation score close to 100\% is required, x\% selective mutation is better than operator selection, and conversely for less stringent scores, operator selection would be better if const of mutant is considered.
+Some studies have tried to find set of \emph{sufficient mutation operators} --minimal set
+of operators that while reducing the cost of mutations, its mutation score maintains
+a good correlation with mutaion score of the original set of operators.
+Barbosa et. al.\cite{barbosa2001toward} provides a set of guidelines for selecting 
+such mutation operators. Namin et al.\cite{namin2006finding,siami2008sufficient} 
+formulate this problem as a variable reduction problem, and apply statistical 
+approaches. They found a subset of 28 operators out of 108 opertors as the sufificient operators.
+Recently, Deng et al~\cite{deng2013empirical} considers the effect of using a single mutation operator 
+-- the statement deletion operator. They define deletion for different language elements,
 
-Barbosa et. al.\cite{barbosa2001toward} provides a set of guidelines for selecting mutagens.
+Wong and Mathur \cite{wong1995reducing}, Acree\cite{Acree1980}, and Budd\cite{Budd1980}  suggest \%x sampling of all mutants.
+They observed that random sampling of mutatnts can greatelly reduces the cost of mutation analysis while
+it can closely approximate the mutation score. Recently, Zhang et al. \cite{zhang2013ase} has shown that sampling
+as small as five percent is a good preditor of mutation score.
 
-Namin et al.\cite{namin2006finding,siami2008sufficient} treats the operator selection as a variable reduction problem, and applying statistical approaches, finds 28 operators from a total of 108 operators that are sufficient for an adequate test suite.
+%The idea is that normal mutation has quadratic complexity on variable references while eliminatng the most 
+%fecund mutagens (SVR and ASR) achieves linear complexity on program size, while still approximating the full
+% mutation score closely. They propose N-selective mutation which avoids N most fertile mutagens. 
+%Wong \cite{wong1995reducing} compares the effect of x\% mutation selection, and abs/ror constrained mutation. 
+%According to Wong, this is different from selective mutation in that only the most fecund operators 
+%are included rather than excluded. He finds that there is no evidence to suggest one over the other.
+% Offutt\cite{offutt1993experimental} does not compare the effectivenss of selective mutation with x\% mutation.
+% He also defines the concept of {\it operator strength} for an operator, which is defined as the total number 
+% of mutants that are killed by test data that is generated to kill only the mutants generated by that operator. 
+% He further posits that the mutagens with greatest strength may be the most useful ones. %(test data generated 
+% to eliminate variants of one operator may remove the mutants of other kinds too.)
+%This is taken up later by Mresa\cite{mresa1999efficiency} et al. who used the cost of detection of mutants as 
+%a means of selection, and uses it to define another set of operators (san, aor, sdl, ror, uoi). They %also find 
+%that if very high mutation score close to 100\% is required, x\% selective mutation is better than operator selection, 
+%and conversely for less stringent scores, operator selection would be better if %const of mutant is considered.
 
-Offutt\cite{offutt1996anexperimental} following the previous paper\cite{offutt1993experimental} compares the effectiveness of selecting different operators.
-He divides the total operators into operand, operation, and statement categories, with es-selective avoiding operands, rs-selective avoiding operations, and re-selective avoiding statements, and e-selective only operations.
-He finds that using only operation based mutation operators (numbering 5) is sufficient for close approximation of full mutation score.
-He suggests that the reason they are effective is that most statements contain operators.
-He further posits that another reason is the amount of semantic change accomplished by an operator, and perhaps the most interesting ones are those that produce the smallest semantic difference.
-% Replacement of Operand , Statement modification, Expression Modification: modify operators, ES-selective : not using operand, RS-Selective: not using expression, RE-Selective: not uinsg statement, E-selective : only expression..
+%Offutt\cite{offutt1996anexperimental} following the previous paper\cite{offutt1993experimental} compares the
+% effectiveness of selecting different operators. He divides the total operators into operand, operation, and 
+% statement categories, with es-selective avoiding operands, rs-selective avoiding operations, and re-selective 
+% avoiding statements, and e-selective only operations. He finds that using only operation based mutation operators
+%  (numbering 5) is sufficient for close approximation of full mutation score. He suggests that the reason they are
+%   effective is that most statements contain operators. He further posits that another reason is the amount of semantic
+%change accomplished by an operator, and perhaps the most interesting ones are those that produce the smallest semantic difference.
+% Replacement of Operand , Statement modification, Expression Modification: modify operators, ES-selective : not using
+% operand, RS-Selective: not using expression, RE-Selective: not uinsg statement, E-selective : only expression..
 
-Unch\cite{untch2009onreduced} suggested using a single mutagen statement deletion.
-He compares the statement deletion with other selective mutagen sets, and finds statement deletion operator to provide the best prediction of original mutation score ($R^2 = 0.97$)
-This was carried forward by Deng et al\cite{deng2013empirical}, (according to whom, random sampling was weak when it was made low enough for appreciable mutant savings).
-They realize a mean mutation score of 92\% for adequate test suites with SDL alone, and generating a saving of 81\% in the number of mutants, and 41\% fewer equivalent mutants.
+%Unch\cite{untch2009onreduced} suggested using a single mutagen statement deletion. He compares the statement deletion
+% with other selective mutagen sets, and finds statement deletion operator to provide the best prediction of original mutation score ($R^2 = 0.97$)
+%This was carried forward by Deng et al\cite{deng2013empirical}, (according to whom, random sampling was weak when it was 
+%made low enough for appreciable mutant savings). They realize a mean mutation score of 92\% for adequate test suites with
+% SDL alone, and generating a saving of 81\% in the number of mutants, and 41\% fewer equivalent mutants.
 
-Zhang et al.\cite{zhang2010operator}, compares operator based mutant selection to random mutant selection.
-They compare three diffrent operator based selection techniques from Offutt et al., Barbosa et al., and Namin et al.
-against random mutant selection, with equal mutant probability, and equal mutagen probaiblity.
-They find that none of these selection techniques are superior to random selection, with same number of mutants.
-They also find that equal mutation sampling is more effective for larger subjects compared to equal mutagen sampling and the reverse is true for smaller subjects.
-A second paper by Zhang et al.\cite{zhang2013ase} investigates 8 sampling strategies on top of operator based mutant selection.
-They find that sampling strategies based on programming elements (method based) performed best.
+Zhang et al.\cite{zhang2010operator} compare operator based mutant selection in 
+\cite{barbosa2001toward,siami2008sufficient,offutt1996anexperimental} to random mutant selection. 
+%They compare three diffrent operator based selection techniques from Offutt et al., Barbosa et al., and Namin 
+%et al. against random mutant selection, with equal mutant probability, and equal mutagen probaiblity. 
+They find that none of these selection techniques are superior to random selection, with same number of 
+mutants. They also find that equal mutation sampling is more effective for larger subjects compared to 
+equal mutagen sampling and the reverse is true for smaller subjects.
+Zhang et al.\cite{zhang2013ase} investigates 8 sampling strategies on top of operator
+based mutant selection. They find that sampling strategies based on program componenets.
+(based on methods) performed best.
+
+This work is closely related to Zhang et al.\cite{zhang2013ase}. We extend the scope of 
+their study with much wider range of mutation selection and we experimented them on much more
+real-world projects.
+
 % Baseline : x\% from selected set
@@
 % Empirical Evaluation of the Statement Deletion Mutation Operator : Offutt
-Deng et al~\cite{deng2013empirical} considers the effect of using a single mutation operator -- the statement deletion operator. They define deletion for different language elements,
+
+\subsection{Execution Reduction}
+
+Weak mutation, devised by Howden \cite{howden1982weak}, considers a mutant as detected, if 
+the states of program after the mutated statement in mutant and the original
+program differ. Several oher studies have refined the idea theoretically \cite{horgan1990weak}and
+observed its effectiveness emperically\cite{offutt1994empirical,Offutt:1991:SWM:120807.120826}.
+
+Some studies have utlized parallel computation to enhance the execution time of 
+the mutation testing \cite{}. Others have used custom built compilers and interpretors \cite{}
+to reduce the overall compile time in mutation testing \cite{}.

### 2014-03-11 src/discussion.Rnw
update

\section{Discussion}
\label{sec:discussion}

\begin{figure}[t]
\includegraphics[totalheight=4cm]{fig/opstrat.eps}
\caption{Example Mutants}
\label{fig:egmutants}
\end{figure}

### 2014-03-11 src/discussion.Rnw
.

@@
 \begin{figure}[t]
-\includegraphics[totalheight=4cm]{fig/opstrat.eps}
+\includegraphics[totalheight=5cm]{fig/opstrat1.eps}
 \caption{Example Mutants}
@@
 \end{figure}
+
+%Our data from Figure~\ref{fig:op} suggests that while there are small differences, the average rate of detection of mutants of each type is similar to the average number of mutants produced for each type.
+This suggests that mutants produced by each operator is similar in terms of difficulty of detection.
+
+We see three clear patterns in our results. The first is that sampling strategy
+can predict the final score with very minimal loss in accuracy up to a fraction
+of $\frac{1}{64}$ of the total number of mutants (Our experiments suggest up
+to $70$ times reduction, with a low standard deviation of $6.72$). We did nto
+cut off with the 99\% rule as mentioned by Zhang et al.~\cite{zhang2013ase}
+(Originally proposed by Offutt et al.~\cite{offutt1996experimental} for a
+different measurement), and instead chose to observe that we obtained
+$R^2 > 0.96$ which provides a high confidence in the accuracy of prediction.
+
+The second pattern is that fractional sampling based on projects appears to be
+better than that based on classes, which inturn is better than methods and
+lines, with regard to the stability of the result (i.e low sd), and correlation.
+This seems not very visible at lower levels (where the reduction fraction is less
+than 32), but becomes more pronounced as the mutant reduction fraction increases.
+There seem to exist a hierarchy of sampling, where by as you go more fine grained,
+the stability and correlation decreases. This is infact opposite to what Zhang
+et al.~\cite{zhang2013ase} observed, where they found that $S_{meth}$ ourperforms
+$S_{base}$.
+
+The third pattern is that the simplest sampling scheme --- simple random sampling ---
+performs best compared to sampling schems that tried to provide higher weightage
+to specific elements based on specific criterias. More importantly, operator selection
+seems to be generally worse off in predicting the final score than any of the random
+selection schemes.

### 2014-03-11 src/conclusion.Rnw
udpate

@@
 
-% For op-selection to work, the distributions of mutations across different projects has to be similar enough. This can be checked by t-test.
-% For mutant clustering
-%TODO Report time for each, as cost.
+Our analysis suggests that simple random sampling, that is, at the project level works best when compared to more sophesticated schemes of sampling.
+Further, we also note that random sampling performs better in predicting final mutation score when compared against operator selection.
 
-Our analysis suggests that random sampling of mutants can help reduce the computational requirements to an extremely large extant while still staying within acceptable accuracy limits.
-An interesting finding is that statement deletion did produce as good accuracy in predicting final mutation score as random sampling techniques that offered comparable mutation reduction.
+This suggests that the best way to reduce the computational requirements while trying to build a representative set is to randomly sample on the whole set of mutants directly.

### 2014-03-11 src/discussion.Rnw
udpate

@@
 \begin{figure}[t]
-\includegraphics[totalheight=5cm]{fig/opstrat1.eps}
-\caption{Example Mutants}
+\includegraphics[totalheight=4.5cm]{fig/opstrat1.eps}
+\caption{Mutant distribution in a sample project along operators and program elements}
 \label{fig:egmutants}
@@
 selection schemes.
+
+There may infact be a simple reason for this observation. Consider the Figure~\ref{fig:egmutants}.
+It is a representation of the distribution of mutants along two orthogonal axes --- the
+mutation operators, and program elements such as classes. For the purposes of this
+explanation, assume that each classes contain about five lines, and each mutant
+produced per line by each of the mutation operators are marked by a small solid circle.
+The two solid vertical lines in blue and red represents two classes, one with a relatively
+small number of mutants and other with large number of mutants. Further, let use use
+$N_{red}$ as the number of mutants in red class, and $N_{blue}$ as the number of mutants
+in blue classs, and $N_{blue} > N_{red}$ as shown in figure, and let $N$ be the total
+number of mutants, and $C$ the number of classes.
+
+To consider a concrete example, consider two classes with 4 and 2 mutants respectively.
+Then -- \textbf{solve} --
+
+What this is saying in effect is that irrespective of the sophestication of sampling used,
+the simplest sampling technique --- that of project based sampling --- is the best form of
+sampling, for a representative set.
+
+This also applies immediately to operator selection as it is another kind of sampling on
+a smaller set. Hence it is no surprise that for larger samples, random sampling is able
+to trump operator selection on predicting the final result.

### 2014-03-11 src/related.Rnw
udpate

@@
 that could approximate mutation score.
+
+% RAHUL ( I want to emphasise two points here, First is, Budd in 1980 showed
+% that 10\% selection lead to less than 1\% accuracy loss, which is confirmed
+% by Wong. Further, Wong says that operator selection with 2 operators are
+% virtually indistinguishable from x\% selection with 5\%.
+% Also, I want to note that their sampling was on top of the operator and not
+% directly on project. Finally we should also note that MUA was done on 5 small
+% programs.
+
+% Operator Selection also assumes that fault detection ability of some operators
+% are higher than others, and hence some operators should have higher weight
+% than others. ~\cite{wong1997comparison}
+
+A number of studies in the past have looked at the relative merits of operator
+selection and random sampling criteria, starting with Wong and Mathur in
+1995~\cite{wong1995reducing}.  They observed that x\% selection up to 10\%
+and constrained mutation had similar accuracy, and that constrained mutation
+provided similar reduction (80\%) compared to sampling. It is to be noted
+that the x\% selection was applied on top of each operator, and not directly
+on the whole set of mutants. They used 5 small programs in C and Fortran.
+
+% RAHUL )
 

### 2014-03-11 src/methodology.Rnw
update
udpate

@@
 \begin{tabular}{ll}
+\hline \hline \\
 \pitic & Invert negatives \\
@@
 \end{tabular}
-\caption{PIT Mutation Opeators}
+\caption{PIT Mutation Opeators (We have used abbreviations instead of operator names.)}
 \label{tbl:pitop}
@@
 we believe that our procedure is reasonable.
-
-\subsection{Mutant Clustering}
-For mutant clustering, we were unable to directly apply clustering based on distinct mutants as suggested by Hussain~\cite{hussain2008mutation}.
-However, we were able to apply clustering techniques on mutation operators, thus turning it to a set of selected operators.

### 2014-03-11 src/discussion.Rnw
update

@@
 mutation operators, and program elements such as classes. For the purposes of this
-explanation, assume that each classes contain about five lines, and each mutant
+explanation, assume that each classes contain equal number of lines, and each mutant
 produced per line by each of the mutation operators are marked by a small solid circle.
 The two solid vertical lines in blue and red represents two classes, one with a relatively
-small number of mutants and other with large number of mutants. Further, let use use
-$N_{red}$ as the number of mutants in red class, and $N_{blue}$ as the number of mutants
-in blue classs, and $N_{blue} > N_{red}$ as shown in figure, and let $N$ be the total
-number of mutants, and $C$ the number of classes.
-
-To consider a concrete example, consider two classes with 4 and 2 mutants respectively.
-Then -- \textbf{solve} --
+small number of mutants and other with large number of mutants. Consider that we are sampling
+by class, and we are choosing all mutants for simplicity. Let $c$ be the number of classes.
+Here, a mutant in red class contributes to $1/n_{red}$ to the mean of the score of the
+red class, and the red class contributes $1/c$ to the total mean.  So the contribution of a
+mutant in red class to the complete is $1/(c * n_{red})$. Similarly for blue class.
+However, if the sampling is done on a complete project basis, then the contribution of any
+mutant is $\frac{1}{\sum_{i=1}^{c} n_{i}}$, which depending on the size of the class might
+be different from what it would contribute if sampling is used. To put it another way,
+for any kind of sampling used based on sub elements, the units in the sample gets equal
+weightage in contribution irrespective of the size of elements themselves, while if the sampling
+is done on a project basis, the contribution of sub elements depends on the number of mutants
+each elements produced.
 

### 2014-03-11 src/results.Rnw
update

@@
 \label{sec:results}
+\subsection{Standard deviation of mutant reduction}
+We observe multiple patterns in our results.
+First, for all sampling criterias used, standard deviation of reduction of mutants is roughly proportional to their mean value.
+This can be seen in Figure~\ref{fig:roundsel}.
+Secondly, we also observe that standard deviation based on project sampling is lower than standard deviation of class based sampling for corresponding mean mutant reduction, and the standard deviation of class based sampling is lower than that based on methods, and similarly for lines.
+
 The first observation from our different kinds of random sampling is that the standard deviation tends to increase with the increase in mutation reduction.

### 2014-03-11 src/analysis.Rnw
udpate

@@
 \label{sec:analysis}
-\begin{figure*}[!htb]
-<<op,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-par(las=1,mfrow = c(1, 2),mar=c(2,8,1,1))
-o.all <- cbind(projects = rownames(o.dist.all), stack(o.dist.all))
-o.all$ind <- clean(o.all$ind)
-bcol <- '#2171B5'
-#bcol <- 'darkgray'
-icol <- '#9ECAE0'
-#icol <- 'lightgray'
-o.det <- cbind(projects = rownames(o.dist.det), stack(o.dist.det))
-o.det$ind <- clean(o.det$ind)
-with(o.det,boxplot(values~ind,horizontal=T,border=c(bcol), col=icol, pch='.', axes=F, ylim=c(0,0.6)))
-with(o.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Original', cex.axis=0.8, ylim=c(0,0.6),add=T))
-
-r.all <- cbind(projects = rownames(r.dist.all), stack(r.dist.all))
-r.all$ind <- clean(r.all$ind)
-r.det <- cbind(projects = rownames(r.dist.det), stack(r.dist.det))
-r.det$ind <- clean(r.det$ind)
-with(r.det,boxplot(values~ind,horizontal=T,border=c(bcol), col=icol, pch='.', axes=F,ylim=c(0,0.6)))
-with(r.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Randoop', cex.axis=0.8,ylim=c(0,0.6),add=T))
-@
-\caption{The relative contribution of mutation operators in terms of fraction of mutants generated and detected. \\
-The blue shade represent detected mutants, while black represents total mutants.}
-\label{fig:op}
-\end{figure*}
 
@@
 % ----------------------------------------------------------------------
-\subsection{Mutant Clustering}
-To be added later.

### 2014-03-11 src/paper.Rnw
udpate

--- 2014-03-08 src/paper.Rnw
@@
 @
+\begin{figure*}[ht]
+<<op,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+par(las=1,mfrow = c(1, 2),mar=c(2,8,1,1))
+o.all <- cbind(projects = rownames(o.dist.all), stack(o.dist.all))
+o.all$ind <- clean(o.all$ind)
+bcol <- '#2171B5'
+#bcol <- 'darkgray'
+icol <- '#9ECAE0'
+#icol <- 'lightgray'
+o.det <- cbind(projects = rownames(o.dist.det), stack(o.dist.det))
+o.det$ind <- clean(o.det$ind)
+with(o.det,boxplot(values~ind,horizontal=T,border=c(bcol), col=icol, pch='.', axes=F, ylim=c(0,0.6)))
+with(o.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Original', cex.axis=0.8, ylim=c(0,0.6),add=T))
+
+r.all <- cbind(projects = rownames(r.dist.all), stack(r.dist.all))
+r.all$ind <- clean(r.all$ind)
+r.det <- cbind(projects = rownames(r.dist.det), stack(r.dist.det))
+r.det$ind <- clean(r.det$ind)
+with(r.det,boxplot(values~ind,horizontal=T,border=c(bcol), col=icol, pch='.', axes=F,ylim=c(0,0.6)))
+with(r.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Randoop', cex.axis=0.8,ylim=c(0,0.6),add=T))
+@
+\caption{The relative contribution of mutation operators in terms of fraction of mutants generated and detected. \\
+The blue shade represent detected mutants, while black represents total mutants.}
+\label{fig:op}
+\end{figure*}
+
 <<methodology, child='methodology.Rnw'>>=
 @
+
 <<analysis, child='analysis.Rnw'>>=

### 2014-03-11 etc/abstract.tex
Updated paper to use cached knitr, and updated abstract to say what we achieved.

--- 2014-02-18 etc/abstract.tex
@@
 Mutation analysis is a metric for measuring the quality of test suites.
-However, its exorbitant computational requirements makes it hard to use in practice.
+However, it is computationally intensive compared to other measures which it hard to use in practice.
 Choosing a smaller subset of mutations to run is a simple approach that can alleviate this problem.
+There exist multiple ways to reduce the set of mutations to run.
+Operator selection is an area that has been heavily researched.
+Recently, researchers have found that sampling can achive accuracy and mutant reduction similar to operator selection.
 
 %2.Saywhyit’saninterestingproblem
-However, how best to choose among multiple selection criterias is an open problem, especially for real-world programs and test-suites.
+However, the statistical inference that can be drawn from these research has been limited due to the small number of subject programs.
+Further, which sampling technique is best is still an open problem that needs to be tackled on a much larger range of test subjects.
 
 %3.Saywhatyoursolutionachieves
-Our research compare a number of selection criteria along different dimensions including prediction of original mutation score, mutant reduction ratio, and time for completion.
+Our research compares a number of sampling criteria, and operator selection criteria based on their ability to approximate the full mutation score, and also the consistency of mutation reduction ratios achieved.
+Our results provide a ranking that can be used to choose an appropriate mutation reduction technique according to the mutation reduction ratio desired, and how much reduction in accuracy is acceptable.
+%4.Saywhatfollowsfromyoursolution
 
-%4.Saywhatfollowsfromyoursolution
+We find that all sampling criterias perform better than operator selection methods when considering their ability to predict the full mutation score, and also the consistency of mutation reduction ratios achieved.
+We find that simplest sampling criteria --- sampling based on projects works best on all the factors examined, We provide an explanation for this result, and why this is important for future research.
 

### 2014-03-11 src/paper.Rnw
Rename introduction

@@
 \begin{comment}
-<<setup, include=FALSE, cache=FALSE, message=FALSE, echo=FALSE>>=
+<<setup, include=FALSE, message=FALSE, echo=FALSE>>=
 clean <- function(x)sub('CONSTRUCTOR','CONSTR',sub('RETURN','R',sub('INCREMENTS','INC',sub('VOID','V',sub('CONDITIONAL','COND',sub('NON','N',sub('VARIABLE','VAR',sub('MEMBER','MEM',sub('DELETE_','D_',sub('REMOVE_','R_',sub('NEGATE_','N_',sub('_CALLS','',sub('EXPERIMENTAL_','E_',x)))))))))))))
@@
 opts_chunk$set(fig.path='figure/twocolumn-', fig.align='center', fig.show='hold', echo=FALSE)
+opts_chunk$set(cache=TRUE)
 render_listings()
@@
 % 10 pages for the main text + 1 for references.
-<<intro, child='intro.Rnw'>>=
+<<introduction, child='introduction.Rnw'>>=
 @

### 2014-03-12 src/paper.Rnw
update

@@
 \begin{figure*}[ht]
-<<op,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-par(las=1,mfrow = c(1, 2),mar=c(2,8,1,1))
-o.all <- cbind(projects = rownames(o.dist.all), stack(o.dist.all))
-o.all$ind <- clean(o.all$ind)
-bcol <- '#2171B5'
-#bcol <- 'darkgray'
-icol <- '#9ECAE0'
-#icol <- 'lightgray'
-o.det <- cbind(projects = rownames(o.dist.det), stack(o.dist.det))
-o.det$ind <- clean(o.det$ind)
-with(o.det,boxplot(values~ind,horizontal=T,border=c(bcol), col=icol, pch='.', axes=F, ylim=c(0,0.6)))
-with(o.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Original', cex.axis=0.8, ylim=c(0,0.6),add=T))
-
-r.all <- cbind(projects = rownames(r.dist.all), stack(r.dist.all))
-r.all$ind <- clean(r.all$ind)
-r.det <- cbind(projects = rownames(r.dist.det), stack(r.dist.det))
-r.det$ind <- clean(r.det$ind)
-with(r.det,boxplot(values~ind,horizontal=T,border=c(bcol), col=icol, pch='.', axes=F,ylim=c(0,0.6)))
-with(r.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Randoop', cex.axis=0.8,ylim=c(0,0.6),add=T))
-@
+% <<op,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+% par(las=1,mfrow = c(1, 2),mar=c(2,8,1,1))
+% o.all <- cbind(projects = rownames(o.dist.all), stack(o.dist.all))
+% o.all$ind <- clean(o.all$ind)
+% bcol <- '#2171B5'
+% #bcol <- 'darkgray'
+% icol <- '#9ECAE0'
+% #icol <- 'lightgray'
+% o.det <- cbind(projects = rownames(o.dist.det), stack(o.dist.det))
+% o.det$ind <- clean(o.det$ind)
+% with(o.det,boxplot(values~ind,horizontal=T,border=c(bcol), col=icol, pch='.', axes=F, ylim=c(0,0.6)))
+% with(o.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Original', cex.axis=0.8, ylim=c(0,0.6),add=T))
+% 
+% r.all <- cbind(projects = rownames(r.dist.all), stack(r.dist.all))
+% r.all$ind <- clean(r.all$ind)
+% r.det <- cbind(projects = rownames(r.dist.det), stack(r.dist.det))
+% r.det$ind <- clean(r.det$ind)
+% with(r.det,boxplot(values~ind,horizontal=T,border=c(bcol), col=icol, pch='.', axes=F,ylim=c(0,0.6)))
+% with(r.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Randoop', cex.axis=0.8,ylim=c(0,0.6),add=T))
+% @
+\includegraphics[width=1\textwidth]{fig/twocolumn-op.pdf}
 \caption{The relative contribution of mutation operators in terms of fraction of mutants generated and detected. \\

### 2014-03-12 src/paper.Rnw
.
update

--- 2014-03-11 src/paper.Rnw
@@
 <<setup, include=FALSE, message=FALSE, echo=FALSE>>=
+is.installed <- function(mypkg) is.element(mypkg, installed.packages()[,1])
+if (!is.installed("xtable")) install.packages("xtable")
+if (!is.installed("ggplot2")) install.packages("ggplot2")
+if (!is.installed("reshape2")) install.packages("reshape2")
+
 clean <- function(x)sub('CONSTRUCTOR','CONSTR',sub('RETURN','R',sub('INCREMENTS','INC',sub('VOID','V',sub('CONDITIONAL','COND',sub('NON','N',sub('VARIABLE','VAR',sub('MEMBER','MEM',sub('DELETE_','D_',sub('REMOVE_','R_',sub('NEGATE_','N_',sub('_CALLS','',sub('EXPERIMENTAL_','E_',x)))))))))))))
@@
 @
-\caption{The relative contribution of mutation operators in terms of fraction of mutants generated and detected. \\
+\caption{The relative contribution of mutation operators in terms of fraction of mutants generated and detected.
 The blue shade represent detected mutants, while black represents total mutants.}

### 2014-03-12 src/introduction.Rnw
update

--- 2014-03-09 src/intro.Rnw
@@
 % 2. State your contributions
-Mutation analysis is a method of evaluation of quality of test-suites. It involves producing
-a family of mutants with simple differences from the original program, and evaluating the
-effectiveness of test-suites against the these mutants~\cite{lipton1971fault, ammann2008introduction}.
-Previous research~\cite{andrews2005mutation} suggests that mutations thus introduced behave
-in a fashion similar to the real-faults with respect to the difficulty of detection.
+Mutation analysis is a method of evaluation of quality of test-suites. It
+involves producing a family of mutants with simple differences from the
+original program, and evaluating the effectiveness of test-suites against
+these mutants~\cite{lipton1971fault, ammann2008introduction}.  Previous
+research~\cite{andrews2005mutation} suggests that mutations thus introduced
+behave in a fashion similar to the real-faults with respect to the difficulty
+of detection.
 
-One of the impediments to wider adoption of mutation analysis is its high computational cost.
-The set of simple mutants of a moderate sized program can be very large, and renders
-mutation analysis prohibitively time-consuming.
+One of the impediments to wider adoption of mutation analysis is its high
+computational cost.  The set of simple mutants of a moderate sized program
+can be very large, and renders mutation analysis prohibitively time-consuming.
 
-A major strain of research into cost-reduction of mutation analysis is to choose a smaller
-representative set of mutants~\cite{offutt2001mutation,jia2011analysis}-- often called the
-``do fewer'' approach. This approach can be generally divided into selective strategies
-and sampling strategies.
+A major strain of research into cost-reduction of mutation
+analysis is to choose a smaller representative set of
+mutants~\cite{offutt2001mutation,jia2011analysis}-- often called the ``do
+fewer'' approach. This approach can be generally divided into selective
+strategies and sampling strategies.
 
-Selective mutation strategies attempt to select a representative subset of operators based
-on heuristics and statistical analysis, and applying this subset of operators to generate mutants
-instead of applying the whole gamut of mutation operators~\cite{offutt1993anexperimental,untch2009onreduced}.
+Selective mutation strategies attempt to select a representative subset of
+operators based on heuristics and statistical analysis, and applying this
+subset of operators to generate mutants instead of applying the whole gamut
+of mutation operators~\cite{offutt1993anexperimental,untch2009onreduced}.
 
-Sampling strategies seek to randomly select smaller representative mutants.
-This was investigated first by Acree~\cite{acree1980mutation} and Budd~\cite{budd1980mutation},
-who proposed using only $x$\% of the mutants produced. The studies by Wong and
-Mathur found that random sampling with ratio as low as 10\% could provide
-accurate results~\cite{jia2011analysis}.
+Sampling strategies seek to randomly select smaller representative
+mutants.  This was investigated first by Acree~\cite{acree1980mutation} and
+Budd~\cite{budd1980mutation}, who proposed using only $x$\% of the mutants
+produced. The studies by Wong and Mathur found that random sampling with
+ratio as low as 10\% could provide accurate results~\cite{jia2011analysis}.
 
@@
 
-A few recent works~\cite{zhang2010icse,zhang2013ase} have investigated the relative merits of
-random sampling strategies and operator selection. It was found that while random sampling can
-generally perform equal to or better than operator selection, a strategy that combined random
-sampling with program elements paid superior dividends.
+A few recent works~\cite{zhang2010icse,zhang2013ase} have investigated the
+relative merits of random sampling strategies and operator selection. It
+was found that while random sampling can generally perform equal to or
+better than operator selection, a strategy that combined random sampling
+with program elements paid superior dividends.
 
-However, as pointed out by Zhang et al.~\cite{zhang2013ase}, the field has a serious lacuna in
-large scale research, both in the size of the programs studied, and in the number and diversity
-of programs, which reduces our confidence in the espoused results. This is true both for
-selective mutation, sampling strategies, and also for comparatively newer studies that attempt
-to join them together.  This is particularly worrisome if mutation analysis is to gain wider
-acceptance among testing professionals. Further quite a few of the influential studies has been
-conducted on older programming languages such as Fortran with operators specific to it, which
-may not carry over to the newer and popular languages such as Java. Finally, with the modern
-research into the ``do-smarter'' approach which allows byte code based mutation -- thus eliminating
-the compilation step -- operators based on source code modification is no longer be applicable, and
-their equivalents in the bytecode needs to be found and compared with other approaches. A detailed
-discussion of these issues can be found in Section~\ref{sec:relatedwork}.
+However, as pointed out by Zhang et al.~\cite{zhang2013ase}, the
+field has a serious lacuna in large scale research, both in the
+size of the programs studied, and in the number and diversity of
+programs, which reduces our confidence in their results. This is
+true for selective mutation studies, studies in sampling, and also
+for comparatively newer studies that attempt to combine them. This is
+particularly worrisome if mutation analysis is to gain wider acceptance
+among testing professionals. Further, quite a few of the influential
+studies~\cite{offutt1993experimental,offutt1996anexperimental,wong1995reducing}
+has been conducted on older programming languages such as Fortran with
+operators specific to it, and are not directly applicable to newer languages
+such as Java, with significant differences. Finally, with the modern research
+into the ``do-smarter'' approach using byte code based mutation -- eliminating
+the compilation step -- operators based on source code modification is no
+longer be applicable, and their equivalents in the bytecode needs to be
+found and compared with other approaches. A detailed discussion of these
+issues can be found in Section~\ref{sec:related}.
 
@@
 % previous wording, nor your bulleted list reads good)
-We have attempted to rectify this situation with a large scale study of industrial programs.
-As detailed in Section~\ref{sec:methodology}, we sample 188 real world Java programs from Github, with
-size ranging from 50loc to 100kloc, which makes our inferences relatively strong, and widely applicable.
-We provide the results from running both original human generated test-suites, and also programmatically
-generated test-suites, increasing the applicability of our findings to both researchers who seek to
-compare test-suites quickly, and to industrial software testers who might be looking for a way to reduce
-the time of their build cycle when using mutation coverage. The Section~\ref{sec:methodology} discusses
-the sampling strategies attempted, and the operator selection strategies in detail, and the results of
-our experiment are given in Section~\ref{sec:results}, followed by detailed discussion of what it implies
-in section ~\ref{sec:discussion}. The research concludes in Section~\ref{sec:conclusion}.
+We have attempted to rectify this situation with a large scale study
+of industrial programs.  As detailed in Section~\ref{sec:methodology},
+we sample 188 real world Java programs from Github, with size ranging
+from 50loc to 100kloc, which allows us to make widely applicable
+statistical inferences. We provide the results from running both original human
+generated test-suites, and also programmatically generated test-suites,
+increasing the applicability of our findings to both researchers who seek to
+compare test-suites quickly, and to industrial software testers who might be
+looking for a way to reduce the time of their build cycle when using mutation
+coverage. The Section~\ref{sec:methodology} discusses the sampling strategies
+attempted, and the operator selection strategies in detail, and the results of
+our experiment are given in Section~\ref{sec:results}, followed by detailed
+discussion of what it implies in section ~\ref{sec:discussion}. The research
+concludes in Section~\ref{sec:conclusion}.
 
@@
 \begin{itemize}
-\item Our study is the largest so far in terms of both the size of programs involved, and the number of
-  programs analyzed for ``do-fewer'' strategies, which makes our inferences stronger and widely applicable.
-\item We compare a large number of ``do-fewer'' strategies, especially with respect to their predictive
-  power over the final mutation score.
-\item Our sampling strategies include some that were suggested by other researchers, and also a few novel
-  strategies that has not been published elsewhere.
-\item Our recommendations are valid for both testing researchers who might be comparing programmatically
-  generated test-suites, and software testing professionals working on real test-suites.
+\item Our study is the largest so far in terms of both the size of programs
+involved (50loc to 100kloc), and the number of programs analyzed
+(188 unique open source projects) for mutant reduction strategies. This allows
+for stronger and widely applicable statistical inferences to be drawn.
+\item We compare a much large number of mutant reduction strategies, especially
+with respect to their predictive power over the final mutation score, the
+expected mutant reduction, and the stability of the amount of mutant reduction
+expected. Our sampling strategies include some that were suggested by other
+researchers, and also a few novel strategies that has not been published elsewhere.
+\item Our recommendations are valid for both testing researchers who might be
+comparing programmatically generated test-suites, and software testing
+professionals working on real test-suites.
+\item Most importanly, we find that the simplest strategy of mutation reduction,
+that of x\% sampling is better than more sophesticated strategies in predicting
+the final mutation score. This is true not only for those strategies that we
+analyzed but also for any other strategies that seek to predict the full mutation
+score by looking at only a subset of mutants, irrespective of the kind of
+reduction used (operator selection, sampling or clustering, or any other).
+\end{itemize}
+
+\begin{itemize}
+\item simpler schemes work better. %Don't try sophisticated schemes. against Zhang's impression future work.
+\item Sampling at coarsest level (i.e. project level) gives the best result. % against Zhang's findings
+\item Single line sampling gives better results than statement deletion. % comparing random selection and operator selection.
+ % SDL has been recommended by Offutt.
+
 \end{itemize}

### 2014-03-12 src/analysis.Rnw
update

@@
 
-df <-  subset(stats.df, r.square>=0.9 & (sd.reduction * 2) < mutant.reduction)
+df <-  subset(stats.df, r.square>=0.9 & (sd.reduction * 2) < mutant.reduction) # & mutant.reduction < 20)
 df$sqr <- 1 - df$r.square
@@
             ifelse(grepl('project',operator), 'project',
-              NA)))))))
+              'selection')))))))
 df$strat <- with(df,

### 2014-03-12 src/methodology.Rnw
update

@@
 that uses the popular maven\cite{maven} build system, that has been used
-elsewhere\cite{gopinath2014code}. This set of projects comes in two flavors
+elsewhere\cite{gopinath2014code}. We utilize two flavors of
 of test-suites. The original test-suites present in a limited number of
-projects, and automatically generatd test-suites using randoop.  Due to the
-constraints in resources, we had to further reduce the programs and test-suites
+projects, and automatically generatd test-suites using randoop.  Due
+limited resources, we had to further reduce the programs and test-suites
 to those that could finish the mutation run in 10 minutes. From this set
@@
 we extended PIT to provide newer operators that are similar to operators
-provided by other mutation systems. The set of operators provided by PIT
-are provided in Table~\ref{tbl:pitop}.
+provided by other mutation systems. The set of operators that we used
+are provided in Table~\ref{tbl:pitop}. For a detailed description of each,
+please see~\cite{pitmut}
 
@@
 
-\begin{table}[h]\footnotesize
+\begin{table}[h]
+\small{
 \begin{tabular}{ll}
 \hline \hline \\
-\pitic & Invert negatives \\
-\pitrv & Change return values \\
-\pitm & Modify arithmetic operators\\
-\pitvmc & Remove void method calls \\
-\pitnc & Negate conditional statements \\
-\pitcb & Modify boundary conditions \\
-\piti & Modify increment/decrement \\
-\pitnvmc & Replace non-void method calls \\
-\pitcc & Replace constructor calls \\
-\pitic & Replace inline constants \\
-\piti & Remove increment/decrement \\
-\pitemv & Replace member variable assignments \\
+\pitin & Remove negative sign from numbers\\
+\pitrv & Mutate return values\\
+\pitm & Mutate arithmetic operators\\
+\pitvmc & Remove void method calls\\
+\pitnc & Negate conditional statements\\
+\pitcb & Modify boundaries in logical conditions\\
+\piti & Modify increment and decrement statements\\
+\pitnvmc & Remove non-void method calls, returning default value \\
+\pitcc & Replace constructor calls, returning null \\
+\pitic & Replace inline constants with default value \\
+\pitri & Remove increment and decrement statements \\
+\pitemv & Replace member variable assignments with default value \\
 \pites & Modify switch statements \\
-\pitrs & Remove switch elements* \\
-\pitrc & Make conditionals true \\
-\pitnc & Make conditionas false* \\
+\pitrs & Replace switch labels with default (thus removing them) \\
+\pitrc & Replace boolean conditions with true\\
+\pitnc & Replace boolean conditions with false\\
 \hline
 \end{tabular}
+}
 \caption{PIT Mutation Opeators (We have used abbreviations instead of operator names.)}

### 2014-03-12 src/methodology.Rnw
update
udpate

@@
 
-Finally, to ensure accuracy of our observations, each criteria described has been run four times, and the results are averaged to produce the final result.
+Finally, to remove random noice, each criteria described has been run four times, and the results are averaged to produce the final result.
 
-One of our research questions was to compare the utility of operator
-selection --- especially statement deletion --- with random sampling of mutants,
-Since we use PIT, which is a bytecode oriented mutation engine, implementing statement deletion
-directly is very hard. However, we can approximate statement deletion by combining different
-bytecode operators, as explained later.
+One of the criterias we sampled was \textit{statement deletion}.
+Since we use PIT, which is a bytecode based mutation engine, implementing direct equivalent of
+source code statement deletion is very hard. We were able to approximate statement deletion
+by combining different bytecode operators, which is explained in Subsection~\ref{subsec:stmtdel}.
 
@@
 
-We used several different sampling criterias.
+We used several different sampling criterias, based on different strategies of sampling, and what happens when the number of mutants selected falls below a threshold.
 
@@
 \subsubsection{Statement Deletion:}
+\label{subsec:stmtdel}
 The basic statement deletion was modeled on the work by Deng et

### 2014-03-12 src/methodology.Rnw
Fix floating ratios

@@
+\begin{figure*}
+<<op,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+par(las=1,mfrow = c(1, 2),mar=c(2,8,1,1))
+o.all <- cbind(projects = rownames(o.dist.all), stack(o.dist.all))
+o.all$ind <- clean(o.all$ind)
+bcol <- '#2171B5'
+#bcol <- 'darkgray'
+icol <- '#9ECAE0'
+#icol <- 'lightgray'
+o.det <- cbind(projects = rownames(o.dist.det), stack(o.dist.det))
+o.det$ind <- clean(o.det$ind)
+with(o.det,boxplot(values~ind,horizontal=T,border=c(bcol), col=icol, pch='.', axes=F, ylim=c(0,0.6)))
+with(o.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Original', cex.axis=0.8, ylim=c(0,0.6),add=T))
+
+r.all <- cbind(projects = rownames(r.dist.all), stack(r.dist.all))
+r.all$ind <- clean(r.all$ind)
+r.det <- cbind(projects = rownames(r.dist.det), stack(r.dist.det))
+r.det$ind <- clean(r.det$ind)
+with(r.det,boxplot(values~ind,horizontal=T,border=c(bcol), col=icol, pch='.', axes=F,ylim=c(0,0.6)))
+with(r.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Randoop', cex.axis=0.8,ylim=c(0,0.6),add=T))
+@
+\caption{The relative contribution of mutation operators in terms of fraction of mutants generated and detected.
+The blue shade represent detected mutants, while black represents total mutants.}
+\label{fig:op}
+\end{figure*}
+
 \section{Methodology}
@@
 provided by other mutation systems. The set of operators that we used
-are provided in Table~\ref{tbl:pitop}. For a detailed description of each,
-please see~\cite{pitmut}
+are provided in Table~\ref{tbl:pitop}. A distribution of these operators
+in our projects are provided in Figure~\ref{fig:op}, which shows both the
+distribution of complete mutants and the relative detection rates of each
+mutation operators. For a detailed description of each, please see~\cite{pitmut}
 
@@
 
-\begin{table}[h]
+\begin{table}
 \small{

### 2014-03-12 src/paper.Rnw
update
Fix floating ratios

@@
 %
-\newcommand{\pitnvmc}{NVMC~}
+\newcommand{\pitnvmc}{NMC~}
 \newcommand{\pitnc}{NC~}
@@
 % No space variants.
-\newcommand{\Pitnvmc}{NVMC}
+\newcommand{\Pitnvmc}{NMC}
 \newcommand{\Pitnc}{NC}
@@
 @
-\begin{figure*}[ht]
-<<op,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-par(las=1,mfrow = c(1, 2),mar=c(2,8,1,1))
-o.all <- cbind(projects = rownames(o.dist.all), stack(o.dist.all))
-o.all$ind <- clean(o.all$ind)
-bcol <- '#2171B5'
-#bcol <- 'darkgray'
-icol <- '#9ECAE0'
-#icol <- 'lightgray'
-o.det <- cbind(projects = rownames(o.dist.det), stack(o.dist.det))
-o.det$ind <- clean(o.det$ind)
-with(o.det,boxplot(values~ind,horizontal=T,border=c(bcol), col=icol, pch='.', axes=F, ylim=c(0,0.6)))
-with(o.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Original', cex.axis=0.8, ylim=c(0,0.6),add=T))
-
-r.all <- cbind(projects = rownames(r.dist.all), stack(r.dist.all))
-r.all$ind <- clean(r.all$ind)
-r.det <- cbind(projects = rownames(r.dist.det), stack(r.dist.det))
-r.det$ind <- clean(r.det$ind)
-with(r.det,boxplot(values~ind,horizontal=T,border=c(bcol), col=icol, pch='.', axes=F,ylim=c(0,0.6)))
-with(r.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Randoop', cex.axis=0.8,ylim=c(0,0.6),add=T))
-@
-\caption{The relative contribution of mutation operators in terms of fraction of mutants generated and detected.
-The blue shade represent detected mutants, while black represents total mutants.}
-\label{fig:op}
-\end{figure*}
 

### 2014-03-12 src/methodology.Rnw
update

@@
 distribution of complete mutants and the relative detection rates of each
-mutation operators. For a detailed description of each, please see~\cite{pitmut}
+mutation operators. In the figure, there are two box-plots corresponding
+to each mutation operator on the Y-axis. The black box represents the
+relative frequency of the particular mutation operator in the total mutants
+\textit{generated}. For example for projects in the randoop set, the
+operator \pitnvmc contributed about 23\% of the total number of mutants
+produced while \pitrv contributed about 15\%. Similarly, the blue shaded
+box-plot represents the relative frequency of particular mutation operator
+in the total mutants \textit{detected}. For example, \pitnvmc contribution
+in the detected mutants was 34\% while that of \pitrv was 7\%.
 
-Further, we also modified PIT to provide random selection of mutants according
-to various criterias.
+For a detailed description of each mutants, please see~\cite{pitmut}.
+PIT was also modifed to provide random selection of mutants according
+to various criterias. Finally, to remove random noice, each criteria
+described has been run four times, and the results are averaged to produce
+the final result.
 
@@
 \end{table}
-
-Finally, to remove random noice, each criteria described has been run four times, and the results are averaged to produce the final result.
 

### 2014-03-12 src/methodology.Rnw
update

@@
 
-We used several different sampling criterias, based on different strategies of sampling, and what happens when the number of mutants selected falls below a threshold.
+We used several different sampling criteria. We varied the criterias based on the granularity and
+scope of sampling, and strategy chosen when the number of mutants to be sampled falls below one.
 

### 2014-03-12 src/methodology.Rnw
update

--- 2014-03-12 src/methodology.Rnw
@@
 o.det$ind <- clean(o.det$ind)
-with(o.det,boxplot(values~ind,horizontal=T,border=c(bcol), col=icol, pch='.', axes=F, ylim=c(0,0.6)))
-with(o.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Original', cex.axis=0.8, ylim=c(0,0.6),add=T))
+with(o.all,boxplot(values~ind,horizontal=T,border=c(bcol), pch='.', axes=F, ylim=c(0,0.6), col=icol ))
+with(o.det,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Original', cex.axis=0.8, ylim=c(0,0.6),add=T))
 
@@
 r.det$ind <- clean(r.det$ind)
-with(r.det,boxplot(values~ind,horizontal=T,border=c(bcol), col=icol, pch='.', axes=F,ylim=c(0,0.6)))
-with(r.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Randoop', cex.axis=0.8,ylim=c(0,0.6),add=T))
+with(r.all,boxplot(values~ind,horizontal=T,border=c(bcol), pch='.', axes=F,ylim=c(0,0.6),  col=icol))
+with(r.det,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Randoop', cex.axis=0.8,ylim=c(0,0.6),add=T))
 @
@@
 \textit{generated}. For example for projects in the randoop set, the
-operator \pitnvmc contributed about 23\% of the total number of mutants
-produced while \pitrv contributed about 15\%. Similarly, the blue shaded
+operator \pitnvmc contributed about 34\% of the total number of mutants
+produced while \pitrv contributed about 7\%. Similarly, the blue shaded
 box-plot represents the relative frequency of particular mutation operator
 in the total mutants \textit{detected}. For example, \pitnvmc contribution
-in the detected mutants was 34\% while that of \pitrv was 7\%.
+in the detected mutants was 23\% while that of \pitrv was 15\%.
 
@@
 
-We used several different sampling criterias, based on different strategies of sampling, and what happens when the number of mutants selected falls below a threshold.
+We used several different sampling criteria, some of which has been suggested in the literature before,
+and some which are variants of previously suggested criterias, and some that have not been used before.
 

### 2014-03-12 src/methodology.Rnw
udpate
update

@@
 
-We used several different sampling criteria, some of which has been suggested in the literature before,
-and some which are variants of previously suggested criterias, and some that have not been used before.
+We used several different sampling criteria, some of which has been suggested
+in the literature before, and some which are variants of previously suggested
+criteria, and some that have not been used before.  For each sampling
+criteria, we sampled mutants on a decreasing power scale sampling
+\textit{1, 1/2, 1/4, 1/8, 1/16, 1/64} of the total mutants.
 
 \subsubsection{x\% selection}
-The simplest one consisted of using x\% selection as suggested by Wong et al.~\cite{wong1995reducing}.
-In this criteria, we choose a specific fraction of the complete mutants.
-Following the suggestion of Zhang et al.~\cite{zhang2013ase}, we extend this criteria to sample mutants from within different program elements.
-We sampled x\% selection in the increasing order of scope, --- \textit{line}, \textit{method}, \textit{class}, and \textit{project} --- and decreasing fraction of total mutants -- \textit{1, 1/2, 1/4, 1/8, 1/16, 1/64}.
+The simplest one consisted of using x\% selection as suggested by
+Budd~\cite{budd1980mutation}. In this criteria, we choose a specific
+fraction of the complete set of mutants. This criteria also serves as a
+control for the verifying the effectiveness of other criteria.
 
-While the sampling criteria is simple, it is not immediately clear when we are faced with program elements that produced too few mutants for a particular fraction to yield at-least one mutant.
-For example, for a line that produced 15 mutants, the number of mutants that can be chosen in \textit{(x\%, line, 1/64)} is less than 1.
-We analyzed the results of the following criterias: 1) to apply \textit{round} function to the resulting number and covert to the nearest integer, and choose that value as the number of mutants (in effect, ignoring elements that are less complex), 2) to apply \textit{ceil} function to the resulting value, ensuring that there is atleast one mutant per program element, and 3) to apply \textit{sample} criteria suggested by Zhang et al.~\cite{zhang2013ase}, which chooses a mutant with given fracton as probability.
+\subsubsection{x\% selection over program elements}
+Following the suggestion of Zhang et al.~\cite{zhang2013ase}, we
+extended x\% selection to sample from within different program elements.
+We sampled in the increasing order of scope, --- \textit{line},
+\textit{method} and \textit{class} (\textit{project} scope was
+analyzed as part of x\% selection).
+
+While the criteria is simple, it is not immediately clear when we
+are faced with program elements that produced too few mutants for a particular
+fraction to yield at-least one mutant. For example, for a line that produced
+15 mutants, the number of mutants that can be chosen in \textit{(x\%, line,
+1/64)} is less than 1. We analyzed the results of the following criterias:
+1) to apply \textit{round} function to the resulting number and covert to
+the nearest integer, and choose that value as the number of mutants (in
+effect, ignoring elements that are less complex), 2) to apply \textit{ceil}
+function to the resulting value, ensuring that there is atleast one mutant
+per program element, and 3) to apply \textit{sample} criteria suggested by
+Zhang et al.~\cite{zhang2013ase}, which chooses a mutant with given fracton
+as probability.
 % TODO: If the criterias ceil and round does not make sense, we might remove them to gain space.

### 2014-03-12 src/methodology.Rnw
update

@@
 
-\subsubsection{x\% selection over program elements}
+\subsubsection{x\% selection over program elements (and variations)}
 Following the suggestion of Zhang et al.~\cite{zhang2013ase}, we
-extended x\% selection to sample from within different program elements.
-We sampled in the increasing order of scope, --- \textit{line},
-\textit{method} and \textit{class} (\textit{project} scope was
-analyzed as part of x\% selection).
+extended x\% selection criteria to sample from within different program
+elements.  We sampled in the increasing order of scope,
+--- \textit{line}, \textit{method} and \textit{class} (\textit{project}
+scope was analyzed as part of x\% selection).
 
-While the criteria is simple, it is not immediately clear when we
-are faced with program elements that produced too few mutants for a particular
-fraction to yield at-least one mutant. For example, for a line that produced
-15 mutants, the number of mutants that can be chosen in \textit{(x\%, line,
-1/64)} is less than 1. We analyzed the results of the following criterias:
-1) to apply \textit{round} function to the resulting number and covert to
-the nearest integer, and choose that value as the number of mutants (in
-effect, ignoring elements that are less complex), 2) to apply \textit{ceil}
-function to the resulting value, ensuring that there is atleast one mutant
-per program element, and 3) to apply \textit{sample} criteria suggested by
-Zhang et al.~\cite{zhang2013ase}, which chooses a mutant with given fracton
-as probability.
-% TODO: If the criterias ceil and round does not make sense, we might remove them to gain space.
+When the number of mutants to be chosen was not a whole number, we used
+the formula suggested by Zhang et a.~\cite{zhang2013ase}, and used the
+decimal part to select a mutant with that probability.
 
-\subsubsection{Lines per element}
-Our previous research~\cite{gopinath2014code} found that statement coverage was highly correlated with mutation coverage for a project.
-This immediately suggests that perhaps choosing one mutant per line may be sufficient to achieve a close approximation of the final mutation score.
-Further, statement deletion has been researched previously~\cite{untch2009onreduced,deng2013empirical} and has been found to reduce the number of mutants well, without an appreciable decrease in accuracy.
-This also provides a nice comparison with similar number of mutants between operator selection and random sampling of mutants.
+Next, we modified this criteria slightly, and instead of choosing a mutant
+with probability of decimal part, applied \texit{round(sample)} to round
+it to the nearest whole number. We used this as the number of samples to
+be chosen from the population. Our aim was to remove elements that was
+too simple. That is, if the number of mutants dropped below a threshold
+determined by the mutant reduction ratio, that program element did not
+contribute any thing to the final result.
 
-A simple extension of this approach is to extend this strategy as previously, by choosing as many number of mutants as there are number of lines in a program element, and we can extend it as before to sample \textit{1/2,1/4,1/8,1/16,1/32,1/64} of the mutants thus chosen.
-We chose the rounding strategy for fractional samples for simplicity.
-% TODO: Actually do the other rounding choices.
+Next, we explored in the other direction, by forcing the program elements
+to return atleast one element by using the \textit{ceil(sample)}. That is,
+irrespective of the fraction being sampled, the simplest elements always
+contributed atleast one mutant to the total sample.
 
-Here too, we have a few choices when sampling mutants.
-We could either choose the fraction of mutants within the program element, or we could apply the sampling externally.
-For example, using $\lambda_E$ as number of lines in an element, for \textit{(lpe, $1/2$, method)}, we first get $1/2 \times \lambda_{Method}$ number of mutants from each method.
-The second alternative is to get $\lambda_{Method}$ number of mutants for all methods, then from this larger set, choose only half of the mutants.
+\subsubsection{Lines per element and variants}
+Our previous research~\cite{gopinath2014code} found that statement coverage
+was highly correlated with mutation coverage for a project. This immediately
+suggests that perhaps choosing one mutant per line may be sufficient to achieve
+a close approximation of the final mutation score. Further, statement deletion
+has been researched previously~\cite{untch2009onreduced,deng2013empirical} and
+has been found to reduce the number of mutants well, without an appreciable
+decrease in accuracy. This also provides a nice comparison with similar
+number of mutants between operator selection and random sampling of mutants.
+
+We next extended it to sample from each method instead, but using the number
+of lines in the method as the number of mutants to be sampled. This provided
+a test of hypothesis of how important the coverage was. This was extended
+to class and project scope also.
 
 \subsubsection{One per element}
-An extremely simple strategy of sampling is to just choose one mutant per program element, which as before, we extended to include all the fractions \textit{1/2,1/4,1/8,1/16,1/32,1/64}.
+Another simple strategy of sampling we experimented with is to just choose
+one mutant per program element, in the order \textit{line},\textit{method},
+\textit{class}.
 
 \subsection{Operator Selection}
-% TODO expand as required
 

### 2014-03-12 src/methodology.Rnw
udpate

@@
 Next, we modified this criteria slightly, and instead of choosing a mutant
-with probability of decimal part, applied \texit{round(sample)} to round
+with probability of decimal part, applied \textit{round(sample)} to round
 it to the nearest whole number. We used this as the number of samples to

### 2014-03-12 src/methodology.Rnw
udpate

@@
 
-\subsubsection{x\% selection over program elements (and variations)}
+\subsubsection{Sampling over program elements (and variations)}
 Following the suggestion of Zhang et al.~\cite{zhang2013ase}, we

### 2014-03-12 src/analysis.Rnw
Remove subsum graphs
update

@@
+<<xpercentunit>>=
+sel.colnames <- c('operator', 'r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier')
+new.colnames <- c('operator', 'r^2',      'm.red',            'm.sd',         'num',    'B*')
+stats.xp <- subset(stats.df, grepl('^(r|rr|rc)[.]', operator)) # We are ignoring ceil here. add rc if needed.
+
+o.stats.sel.xp <- subset(o.f(stats.xp), select=sel.colnames)
+r.stats.sel.xp <- subset(r.f(stats.xp), select=sel.colnames)
+stats.rest <- subset(stats.df, !grepl('^(r|rr|rc)[.]', operator))
+colnames(o.stats.sel.xp) <- new.colnames
+colnames(r.stats.sel.xp) <- new.colnames
+
+o.stats.sel.xp.sample <- subset(o.stats.sel.xp, grepl('^rr[.]', operator))
+r.stats.sel.xp.sample <- subset(r.stats.sel.xp, grepl('^rr[.]', operator))
+o.stats.sel.xp.sample$operator <- gsub('rr[.]1x','1/', subset(o.stats.sel.xp, grepl('^rr[.]', operator))$operator)
+r.stats.sel.xp.sample$operator  <- gsub('rr[.]1x','1/', subset(r.stats.sel.xp, grepl('^rr[.]', operator))$operator)
+
+o.stats.sel.xp.round <- subset(o.stats.sel.xp, grepl('^r[.]', operator))
+r.stats.sel.xp.round <- subset(r.stats.sel.xp, grepl('^r[.]', operator))
+o.stats.sel.xp.round$operator  <- gsub('r[.]1x','1/', subset(o.stats.sel.xp, grepl('^r[.]', operator))$operator)
+r.stats.sel.xp.round$operator  <- gsub('r[.]1x','1/', subset(r.stats.sel.xp, grepl('^r[.]', operator))$operator)
+
+o.stats.sel.xp.ceil <- subset(o.stats.sel.xp, grepl('^rc[.]', operator))
+r.stats.sel.xp.ceil <- subset(r.stats.sel.xp, grepl('^rc[.]', operator))
+o.stats.sel.xp.ceil$operator  <- gsub('rc[.]1x','1/', subset(o.stats.sel.xp, grepl('^rc[.]', operator))$operator)
+r.stats.sel.xp.ceil$operator  <- gsub('rc[.]1x','1/', subset(r.stats.sel.xp, grepl('^rc[.]', operator))$operator)
+
+@
+\subsubsection{x\% selection}
+\begin{table*}
+\begin{minipage}[h]{0.49\linewidth}
+<<results='asis'>>=
+print(xtable(o.stats.sel.xp.sample, caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
+@
+\end{minipage}
+\hspace{0.5cm}
+\begin{minipage}[h]{0.49\linewidth}
+<<results='asis'>>=
+print(xtable(r.stats.sel.xp.sample, caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
+@
+\end{minipage}
+\bigskip
+\caption {The sample(x)\% random selection criteria results.}
+\label{tbl:xselsample}
+\end{table*}
+
+\begin{table*}
+\begin{minipage}[h]{0.49\linewidth}
+<<results='asis'>>=
+print(xtable(o.stats.sel.xp.round, caption='Original', label='table:rando', main='Original'), include.rownames=FALSE, floating=FALSE, size='\\small')
+@
+\end{minipage}
+\hspace{0.5cm}
+\begin{minipage}[h]{0.49\linewidth}
+<<results='asis'>>=
+print(xtable(r.stats.sel.xp.round, caption='Randoop', label='table:randr', main='Randoop'), include.rownames=FALSE, floating=FALSE,size='\\small')
+@
+\end{minipage}
+\bigskip
+\caption {The round(x)\% random selection criteria results.}
+\label{tbl:xselround}
+\end{table*}
+
+\begin{table*}
+\begin{minipage}[h]{0.49\linewidth}
+<<results='asis'>>=
+print(xtable(o.stats.sel.xp.ceil, caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
+@
+\end{minipage}
+\hspace{0.5cm}
+\begin{minipage}[h]{0.49\linewidth}
+<<results='asis'>>=
+print(xtable(r.stats.sel.xp.ceil, caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
+@
+\end{minipage}
+\bigskip
+\caption {The ceil(x)\% random selection criteria results.}
+\label{tbl:xselceil}
+\end{table*}
+
 \section{Analysis}
 \label{sec:analysis}
+
+Our results for x\% sampling over program elements are given in Table~\ref{tbl:xselsample}. The result of
+its variation, using \textit{round(sample)} is given in Table~\ref{tbl:xselround}. The result of using \textit{ceil(sample)}
+is given in Table~\ref{tbl:xselceil}.
 
@@
 \subsection{Sampling Criteria}
-% We have power, element, kind(O/R), and MuRed, MuRedSD, R^2
-\subsubsection{x\% selection}
-<<xpercentunit>>=
-sel.colnames <- c('operator', 'r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier')
-new.colnames <- c('operator', 'r^2',      'm.red',            'm.sd',         'num',    'B*')
-stats.xp <- subset(stats.df, grepl('^(r|rr|rc)[.]', operator)) # We are ignoring ceil here. add rc if needed.
-
-o.stats.sel.xp <- subset(o.f(stats.xp), select=sel.colnames)
-r.stats.sel.xp <- subset(r.f(stats.xp), select=sel.colnames)
-stats.rest <- subset(stats.df, !grepl('^(r|rr|rc)[.]', operator))
-colnames(o.stats.sel.xp) <- new.colnames
-colnames(r.stats.sel.xp) <- new.colnames
-@
-\begin{table*}
-\begin{minipage}[h]{0.49\linewidth}
-<<results='asis'>>=
-print(xtable(subset(o.stats.sel.xp, grepl('^r[.]', operator)), caption='Original', label='table:rando', main='Original'), include.rownames=FALSE, floating=FALSE, size='\\small')
-@
-\end{minipage}
-\hspace{0.5cm}
-\begin{minipage}[h]{0.49\linewidth}
-<<results='asis'>>=
-print(xtable(subset(r.stats.sel.xp, grepl('^r[.]', operator)), caption='Randoop', label='table:randr', main='Randoop'), include.rownames=FALSE, floating=FALSE,size='\\small')
-@
-\end{minipage}
-\bigskip
-\caption {The round(x)\% random selection criteria results.}
-\label{tbl:xsel}
-\end{table*}
-
-\begin{table*}
-\begin{minipage}[h]{0.49\linewidth}
-<<results='asis'>>=
-print(xtable(subset(o.stats.sel.xp, grepl('^rr[.]', operator)), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
-@
-\end{minipage}
-\hspace{0.5cm}
-\begin{minipage}[h]{0.49\linewidth}
-<<results='asis'>>=
-print(xtable(subset(r.stats.sel.xp, grepl('^rr[.]', operator)), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
-@
-\end{minipage}
-\bigskip
-\caption {The sample(x)\% random selection criteria results.}
-\label{tbl:xsel2}
-\end{table*}
-
-\begin{table*}
-\begin{minipage}[h]{0.49\linewidth}
-<<results='asis'>>=
-print(xtable(subset(o.stats.sel.xp, grepl('^rc[.]', operator)), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
-@
-\end{minipage}
-\hspace{0.5cm}
-\begin{minipage}[h]{0.49\linewidth}
-<<results='asis'>>=
-print(xtable(subset(r.stats.sel.xp, grepl('^rc[.]', operator)), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
-@
-\end{minipage}
-\bigskip
-\caption {The ceil(x)\% random selection criteria results.}
-\label{tbl:xsel2}
-\end{table*}
 
@@
 
-For operator selection, we approximated the operators as far as possible from the research works into the operators exposed by PIT.
-The results of this are provided in Table~\ref{tbl:opsel}.
-The subsumption graphs are provided in Figure~\ref{fig:subsumptiono}
+For operator selection, we approximated the operators as far as possible from the research works into the operators exposed by PIT. The results of this are provided in Table~\ref{tbl:opsel}.
+% The subsumption graphs are provided in Figure~\ref{fig:subsumptiono}
 % TODO : Check if this makes sense.
-\begin{figure*}[t]
-\includegraphics[totalheight=6cm]{fig/original.pdf}
-\caption{Subsumption Original}
-\label{fig:subsumptiono}
-\end{figure*}
+%\begin{figure*}[t]
+%\includegraphics[totalheight=6cm]{fig/original.pdf}
+%\caption{Subsumption Original}
+%\label{fig:subsumptiono}
+%\end{figure*}
 

### 2014-03-12 src/analysis.Rnw
update

@@
 colnames(r.stats.sel.xp) <- new.colnames
+o.stats.sel.xp$scope <- NA
+r.stats.sel.xp$scope <- NA
+o.stats.sel.xp$sampling <- NA
+r.stats.sel.xp$sampling <- NA
+
+f <- function(x) {
+  x <- x[,c(7,8,2,3,4,5,6)]
+  return(x)
+}
 
@@
 r.stats.sel.xp.sample <- subset(r.stats.sel.xp, grepl('^rr[.]', operator))
-o.stats.sel.xp.sample$operator <- gsub('rr[.]1x','1/', subset(o.stats.sel.xp, grepl('^rr[.]', operator))$operator)
-r.stats.sel.xp.sample$operator  <- gsub('rr[.]1x','1/', subset(r.stats.sel.xp, grepl('^rr[.]', operator))$operator)
+
+o.stats.sel.xp.sample$operator <- gsub('rr[.]1x','1/', o.stats.sel.xp.sample$operator)
+o.stats.sel.xp.sample$scope <- gsub('.*_','', o.stats.sel.xp.sample$operator)
+o.stats.sel.xp.sample$sampling <- gsub('_.*','', o.stats.sel.xp.sample$operator)
+r.stats.sel.xp.sample$operator  <- gsub('rr[.]1x','1/', r.stats.sel.xp.sample$operator)
+r.stats.sel.xp.sample$scope <- gsub('.*_','', r.stats.sel.xp.sample$operator)
+r.stats.sel.xp.sample$sampling <- gsub('_.*','', r.stats.sel.xp.sample$operator)
 
@@
 r.stats.sel.xp.round <- subset(r.stats.sel.xp, grepl('^r[.]', operator))
-o.stats.sel.xp.round$operator  <- gsub('r[.]1x','1/', subset(o.stats.sel.xp, grepl('^r[.]', operator))$operator)
-r.stats.sel.xp.round$operator  <- gsub('r[.]1x','1/', subset(r.stats.sel.xp, grepl('^r[.]', operator))$operator)
+
+o.stats.sel.xp.round$operator  <- gsub('r[.]1x','1/', o.stats.sel.xp.round$operator)
+o.stats.sel.xp.round$scope  <- gsub('.*_','', o.stats.sel.xp.round$operator)
+o.stats.sel.xp.round$sampling  <- gsub('_.*','', o.stats.sel.xp.round$operator)
+r.stats.sel.xp.round$operator  <- gsub('r[.]1x','1/', r.stats.sel.xp.round$operator)
+r.stats.sel.xp.round$scope  <- gsub('.*_','', r.stats.sel.xp.round$operator)
+r.stats.sel.xp.round$sampling  <- gsub('_.*','', r.stats.sel.xp.round$operator)
 
@@
 r.stats.sel.xp.ceil <- subset(r.stats.sel.xp, grepl('^rc[.]', operator))
-o.stats.sel.xp.ceil$operator  <- gsub('rc[.]1x','1/', subset(o.stats.sel.xp, grepl('^rc[.]', operator))$operator)
-r.stats.sel.xp.ceil$operator  <- gsub('rc[.]1x','1/', subset(r.stats.sel.xp, grepl('^rc[.]', operator))$operator)
+
+o.stats.sel.xp.ceil$operator  <- gsub('rc[.]1x','1/', o.stats.sel.xp.ceil$operator)
+o.stats.sel.xp.ceil$scope  <- gsub('.*_','', o.stats.sel.xp.ceil$operator)
+o.stats.sel.xp.ceil$sampling  <- gsub('_.*','', o.stats.sel.xp.ceil$operator)
+r.stats.sel.xp.ceil$operator  <- gsub('rc[.]1x','1/', r.stats.sel.xp.ceil$operator)
+r.stats.sel.xp.ceil$scope  <- gsub('.*_','', r.stats.sel.xp.ceil$operator)
+r.stats.sel.xp.ceil$sampling  <- gsub('_.*','', r.stats.sel.xp.ceil$operator)
 
@@
 <<results='asis'>>=
-print(xtable(o.stats.sel.xp.sample, caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
+print(xtable(f(o.stats.sel.xp.sample), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
 @
@@
 <<results='asis'>>=
-print(xtable(r.stats.sel.xp.sample, caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
+print(xtable(f(r.stats.sel.xp.sample), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
 @
@@
 <<results='asis'>>=
-print(xtable(o.stats.sel.xp.round, caption='Original', label='table:rando', main='Original'), include.rownames=FALSE, floating=FALSE, size='\\small')
+print(xtable(f(o.stats.sel.xp.round), caption='Original', label='table:rando', main='Original'), include.rownames=FALSE, floating=FALSE, size='\\small')
 @
@@
 <<results='asis'>>=
-print(xtable(r.stats.sel.xp.round, caption='Randoop', label='table:randr', main='Randoop'), include.rownames=FALSE, floating=FALSE,size='\\small')
+print(xtable(f(r.stats.sel.xp.round), caption='Randoop', label='table:randr', main='Randoop'), include.rownames=FALSE, floating=FALSE,size='\\small')
 @
@@
 <<results='asis'>>=
-print(xtable(o.stats.sel.xp.ceil, caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
+print(xtable(f(o.stats.sel.xp.ceil), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
 @
@@
 <<results='asis'>>=
-print(xtable(r.stats.sel.xp.ceil, caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
+print(xtable(f(r.stats.sel.xp.ceil), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
 @
@@
 \label{sec:analysis}
+Our results for x\% sampling over program elements are given
+in Table~\ref{tbl:xselsample}. The result of its variation, using
+\textit{round(sample)} is given in Table~\ref{tbl:xselround}. The result
+of using \textit{ceil(sample)} is given in Table~\ref{tbl:xselceil}.
+The first column in each table provides the scope of sampling i.e if it was
+done per class, per method, per line etc. The second column provides the
+fraction involved.  Third column contains the $R^2$ value obtained between
+the mutation score of the sampling criteria used and the full mutation score.
+The fourth column contains the mutant reduction factor. This is the average of
+total mutants produced divided by the number of mutants sampled by the criteria.
+Fifth column contains the standard deviation of the same. A few of the projects
+did not return any value for certain sampling criterias for particular mutation
+reduction fractions. The sixth column contains the number of projects that
+actually had valid values for the criteria being considered. The seventh column
+is the average multiplier between the sampled mutation score and the full mutation
+score.
 
-Our results for x\% sampling over program elements are given in Table~\ref{tbl:xselsample}. The result of
-its variation, using \textit{round(sample)} is given in Table~\ref{tbl:xselround}. The result of using \textit{ceil(sample)}
-is given in Table~\ref{tbl:xselceil}.
-
-First, we ran the the mutation analysis to identify the general distribution of mutants within our set of projects.
-This provided us with the relative number of each mutation operators, that are produced, and also the general number of
-mutants generated by each operator that was detected. This is given in Figure~\ref{fig:op}. This suggests that the operators
-are distributed in the following order: \pitnvmc, \pitnc, \pitrc, \pitdc, \pitrv, \pitic, \pitcc, \pitemv, \pitvmc, \pitm,
-\pitcb, \piti, \pitri, \pitrs, \pites, \pitin. We use this information later for n-selective mutation.
-
-For comparing between different techniques, we ran correlation analysis between the full mutation score,
-and that produced by the reduction criteria. Further, we also collected the mean reduction, and the standard
-deviation of the reduction across all the projects for both randoop and original. These statistics are provided below.
 \subsection{Sampling Criteria}

### 2014-03-12 src/analysis.Rnw
update

@@
 o.one <- subset(o.processed, grepl('^o[.].*.m[.]red',ind))
-ggplot(subset(o.one, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
+ggplot(subset(o.one, values < 100 & (type=='line' | type=='method')), aes(power, values, fill=interaction(type,power), dodge=type)) +
   stat_boxplot(geom ='errorbar')+

### 2014-03-12 src/analysis.Rnw
update

@@
 \label{sec:analysis}
-Our results for x\% sampling over program elements are given
-in Table~\ref{tbl:xselsample}. The result of its variation, using
-\textit{round(sample)} is given in Table~\ref{tbl:xselround}. The result
-of using \textit{ceil(sample)} is given in Table~\ref{tbl:xselceil}.
-The first column in each table provides the scope of sampling i.e if it was
-done per class, per method, per line etc. The second column provides the
-fraction involved.  Third column contains the $R^2$ value obtained between
-the mutation score of the sampling criteria used and the full mutation score.
-The fourth column contains the mutant reduction factor. This is the average of
-total mutants produced divided by the number of mutants sampled by the criteria.
-Fifth column contains the standard deviation of the same. A few of the projects
-did not return any value for certain sampling criterias for particular mutation
-reduction fractions. The sixth column contains the number of projects that
-actually had valid values for the criteria being considered. The seventh column
-is the average multiplier between the sampled mutation score and the full mutation
-score.
+For the purposes of comparing between the criterias, we computed the
+correlation between sampled mutation score and full mutation score.
+Since for most of the sampling criteria, if there are no mutants to
+sample, it probably means there are no mutants generated on the whole,
+we used $lm(M_{all}~0+M_{sample})$ as the regression formula, and report
+the correlation from this linear regression. We also report the expected
+multiplier factor for the sampled mutation score. This factor determines
+the ease of satisfying the sampling criteria. That is, if the multiplier
+factor is small, then it is easier to satisfy compared to a larger multiplier
+factor.
+Next, for each criteria, we computed the reduction of mutants given by the
+ratio between total number of mutants and sampled mutants.
+We also compute standard deviation of the mutant reduction, which determines
+the consistency of results. (A large amount of standard deviation suggests
+that the mutant reduction ratio achieved is very much dependent on the
+project. So as a heuristic, we suggest looking at only those projects which
+has a mean reduction ratio atleast twice the standard deviation.)
+
+For some of the smaller projects, some of the sampling criteria did not
+return any results. This is also collected in our tables.
 
@@
 However, interested parties can refer to our published data.
-
-The reduction in mutants for x\% selection using $round(x)$ is graphed in Figure~\ref{fig:xroundsel}. The values for the same are given in Table~\ref{tbl:xsel}.
-Similarly reduction in mutants for x\% selection using $sample(x)$ is graphed in Figure~\ref{fig:xsamplesel}. The values for the same are given in Table~\ref{tbl:xsel}.
 % ----------------------------------------------------------------------

### 2014-03-12 src/results.Rnw
update

@@
 \label{sec:results}
+
+Our results for x\% sampling over program elements are given
+in Table~\ref{tbl:xselsample}. The result of its variation, using
+\textit{round(sample)} is given in Table~\ref{tbl:xselround}. The result
+of using \textit{ceil(sample)} is given in Table~\ref{tbl:xselceil}.
+The first column in each table provides the scope of sampling i.e if it was
+done per class, per method, per line etc. The second column provides the
+fraction involved.  Third column contains the $R^2$ value obtained between
+the mutation score of the sampling criteria used and the full mutation score.
+The fourth column contains the mutant reduction factor. This is the average of
+total mutants produced divided by the number of mutants sampled by the criteria.
+Fifth column contains the standard deviation of the same. A few of the projects
+did not return any value for certain sampling criterias for particular mutation
+reduction fractions. The sixth column contains the number of projects that
+actually had valid values for the criteria being considered. The seventh column
+is the average multiplier between the sampled mutation score and the full mutation
+score.
+
 \subsection{Standard deviation of mutant reduction}

### 2014-03-12 src/paper.Rnw
udpate

@@
 @
+<<threats, child='threats.Rnw'>>=
+@
 <<conclusion, child='conclusion.Rnw'>>=

### 2014-03-12 src/analysis.Rnw
update

@@
 
-\subsection{Sampling Criteria}
+%\subsection{Sampling Criteria}
 
@@
 myopts <- theme(panel.background = element_blank())
-#myopts <-   theme_bw() +
-#  opts(axis.line = theme_segment(colour = "black"),
-#    panel.grid.major = theme_blank(),
-#    panel.grid.minor = theme_blank(),
-#    panel.border = theme_blank(),
-#    panel.background = theme_blank())
-  #theme with white background
-#myopts <- theme_bw() +
-  #eliminates background, gridlines, and chart border
-#  theme(
-#    plot.background = element_blank()
-#   ,panel.grid.major = element_blank()
-#   ,panel.grid.minor = element_blank()
-#   ,panel.border = element_blank()
-#  ) +
-  #draws x and y axis line
-#  theme(axis.line = element_line(color = 'black'))
-#myopts <-  opts() #theme_classic()
-#+ opts(strip.background = theme_rect(colour = 'NA', fill = 'NA')) + opts(strip.text.y = theme_text(colour = 'white')) + theme(axis.line = element_line(color = 'black'))
-
-# TODO - replace by o.processed.
 o.xp <- subset(o.processed, grepl('^r[.].*.m[.]red',ind))
@@
 \end{figure*}
-%TODO : See if the following paragraph is needed, or shall we just sink the ceil(x) discussion completely?
-Our experiments found that while $round(x)$ and $sample(x)$ produced relatively reasonable reduction of mutants, the $ceil(x)$ criteria failed to produce a reasonable reduction of mutants except for higher power where the reduction was some what close to that produced by $round(x)$ and $sample(x)$ (which was expected).
+%Our experiments found that while $round(x)$ and $sample(x)$ produced relatively reasonable reduction of mutants, the $ceil(x)$ criteria failed to produce a reasonable reduction of mutants except for higher power where the reduction was some what close to that produced by $round(x)$ and $sample(x)$ (which was expected).
 The $R^2$ values of $ceil(x)$ were almost always lower than that produced by $round(x)$ and $sample(x)$ for similar reduction of mutants.
@@
 
-\subsubsection{Lines per element}
-The aim of this criteria is similar in some sense to selective mutation.
+%\subsubsection{Lines per element}
+%The aim of this criteria is similar in some sense to selective mutation.
 While n-selective mutation ignores the most numerous mutant species, this criteria seeks to deprioritize the most complex program elements.
@@
 
-The results of this selection criteria are provided in Table~\ref{tbl:locsel}.
+%The results of this selection criteria are provided in Table~\ref{tbl:locsel}.
 The effect of random selection within the program elements are visualized in Figure~\ref{fig:wlocsel}, and when it is made external to the program elements is visualized in Figure~\ref{fig:wlocsel}.
@@
 % ----------------------------------------------------------------------
-\subsubsection{One per element}
-The aim of this criteria is is to take the previous idea to the extreme. We choose only a single mutant per program element.
+%\subsubsection{One per element}
+%The aim of this criteria is is to take the previous idea to the extreme. We choose only a single mutant per program element.
 
@@
 
-The values are given in Table~\ref{tbl:onesel}, and its visaulization is in Figure~\ref{fig:onesel}.
+%The values are given in Table~\ref{tbl:onesel}, and its visaulization is in Figure~\ref{fig:onesel}.
 % ----------------------------------------------------------------------
@@
 
-\subsection{Operator Selection}
+%\subsection{Operator Selection}
 \begin{figure*}[t]
@@
 
-For operator selection, we approximated the operators as far as possible from the research works into the operators exposed by PIT. The results of this are provided in Table~\ref{tbl:opsel}.
+%For operator selection, we approximated the operators as far as possible from the research works into the operators exposed by PIT. The results of this are provided in Table~\ref{tbl:opsel}.
 % The subsumption graphs are provided in Figure~\ref{fig:subsumptiono}

### 2014-03-12 src/analysis.Rnw
update

@@
 <<count>>=
-stats.loc <- subset(stats.rest, grepl('^(l|wl)[.]', operator))
+stats.loc <- subset(stats.rest, grepl('^l[.]', operator))
 o.stats.sel.loc <- subset(o.f(stats.loc), select=sel.colnames)
 r.stats.sel.loc <- subset(r.f(stats.loc), select=sel.colnames)
-stats.rest <- subset(stats.rest, !grepl('^(l|wl)[.]', operator))
+stats.rest <- subset(stats.rest, !grepl('^l[.]', operator))
 colnames(o.stats.sel.loc) <- new.colnames
 colnames(r.stats.sel.loc) <- new.colnames
+
+o.stats.sel.loc$operator  <- gsub('l[.]1x','1/', o.stats.sel.loc$operator)
+o.stats.sel.loc$scope  <- gsub('.*_','', o.stats.sel.loc$operator)
+o.stats.sel.loc$sampling  <- gsub('_.*','', o.stats.sel.loc$operator)
+r.stats.sel.loc$operator  <- gsub('l[.]1x','1/', r.stats.sel.loc$operator)
+r.stats.sel.loc$scope  <- gsub('.*_','', r.stats.sel.loc$operator)
+r.stats.sel.loc$sampling  <- gsub('_.*','', r.stats.sel.loc$operator)
+
+stats.loc.w <- subset(stats.rest, grepl('^wl[.]', operator))
+o.stats.sel.loc.w <- subset(o.f(stats.loc.w), select=sel.colnames)
+r.stats.sel.loc.w <- subset(r.f(stats.loc.w), select=sel.colnames)
+stats.rest <- subset(stats.rest, !grepl('^wl[.]', operator))
+colnames(o.stats.sel.loc.w) <- new.colnames
+colnames(r.stats.sel.loc.w) <- new.colnames
+
+o.stats.sel.loc.w$operator  <- gsub('wl[.]1x','1/', o.stats.sel.loc.w$operator)
+o.stats.sel.loc.w$scope  <- gsub('.*_','', o.stats.sel.loc.w$operator)
+o.stats.sel.loc.w$sampling  <- gsub('_.*','', o.stats.sel.loc.w$operator)
+r.stats.sel.loc.w$operator  <- gsub('wl[.]1x','1/', r.stats.sel.loc.w$operator)
+r.stats.sel.loc.w$scope  <- gsub('.*_','', r.stats.sel.loc.w$operator)
+r.stats.sel.loc.w$sampling  <- gsub('_.*','', r.stats.sel.loc.w$operator)
+
 @
@@
 <<results='asis'>>=
-print(xtable(o.stats.sel.loc, caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
+print(xtable(f(o.stats.sel.loc), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
 @
@@
 <<results='asis'>>=
-print(xtable(r.stats.sel.loc, caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
+print(xtable(f(r.stats.sel.loc), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
 @
@@
 \caption {The line count selection criteria results.}
+\label{tbl:locsel}
+\end{table*}
+
+\begin{table*}
+\begin{minipage}[h]{0.49\linewidth}
+<<results='asis'>>=
+print(xtable(f(o.stats.sel.loc.w), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
+@
+\end{minipage}
+\hspace{0.5cm}
+\begin{minipage}[h]{0.49\linewidth}
+<<results='asis'>>=
+print(xtable(f(r.stats.sel.loc.w), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
+@
+\end{minipage}
+\caption {The line count selection criteria results (within).}
 \label{tbl:locsel}

### 2014-03-12 src/results.Rnw
update

@@
 
-\subsection{Standard deviation of mutant reduction}
-We observe multiple patterns in our results.
-First, for all sampling criterias used, standard deviation of reduction of mutants is roughly proportional to their mean value.
-This can be seen in Figure~\ref{fig:roundsel}.
-Secondly, we also observe that standard deviation based on project sampling is lower than standard deviation of class based sampling for corresponding mean mutant reduction, and the standard deviation of class based sampling is lower than that based on methods, and similarly for lines.
-
-The first observation from our different kinds of random sampling is that the standard deviation tends to increase with the increase in mutation reduction.
-While this in itself is not unexpected, what is unexpected is the difference in the increase in standard deviation between different kinds of sampling techniques.
-Our observations suggests that random sampling based on the entire project has a much lower growth of standard deviation (and hence higher stability of results) than sampling in lower scopes.
-Further, we also observe that the rate of increase in standard deviation actually increases as we go into more finer scopes such as class, method and line, with line having the largest increase in standard deviation.
-
-Further, looking at the reduction of mutants in Figure~\ref{fig:fullimgshape} and Figure~\ref{fig:fullimgsize}, we see that the x\% selection strategy is generally the best strategy, and it is generally best to stick with random selection from the entire project.
-This too is perhaps not unexpected, since sampling from the entire population rather than its elements should provide a better correlation with the final score.
-
-Our analysis of results suggests that different kinds of operator selection criterias can actually provide better reduction in mutants while not reducing the approximatin accuracy below acceptable limits.
+The Table~\ref{tbl:lcountl} provides the results for line count criteria.
 

### 2014-03-12 src/analysis.Rnw
update

@@
 colnames(r.stats.sel.one) <- new.colnames
+
+o.stats.sel.one$operator  <- gsub('o[.]1x','1/', o.stats.sel.one$operator)
+o.stats.sel.one$scope  <- gsub('.*_','', o.stats.sel.one$operator)
+o.stats.sel.one$sampling  <- gsub('_.*','', o.stats.sel.one$operator)
+
+r.stats.sel.one$operator  <- gsub('o[.]1x','1/', r.stats.sel.one$operator)
+r.stats.sel.one$scope  <- gsub('.*_','', r.stats.sel.one$operator)
+r.stats.sel.one$sampling  <- gsub('_.*','', r.stats.sel.one$operator)
+
 @
@@
 <<results='asis'>>=
-print(xtable(o.stats.sel.one, caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
+print(xtable(f(o.stats.sel.one), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
 @
@@
 <<results='asis'>>=
-print(xtable(r.stats.sel.one, caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
+print(xtable(f(r.stats.sel.one), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
 @
@@
 
-%The values are given in Table~\ref{tbl:onesel}, and its visaulization is in Figure~\ref{fig:onesel}.
-% ----------------------------------------------------------------------
-% <<oth>>=
-% stats.o <- subset(stats.rest, !grepl('^op', operator))
-% o.stats.sel.o <- subset(o.f(stats.o), select=sel.colnames)
-% r.stats.sel.o <- subset(r.f(stats.o), select=sel.colnames)
-% stats.rest <- subset(stats.rest, grepl('^op', operator))
-% colnames(o.stats.sel.o) <- new.colnames
-% colnames(r.stats.sel.o) <- new.colnames
-% @
-% 
-% \begin{table*}
-% \begin{minipage}[h]{0.49\linewidth}
-% <<results='asis'>>=
-% print(xtable(o.stats.sel.o, caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
-% @
-% \end{minipage}
-% \hspace{0.5cm}
-% \begin{minipage}[h]{0.49\linewidth}
-% <<results='asis'>>=
-% print(xtable(r.stats.sel.o, caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
-% @
-% \end{minipage}
-% \bigskip
-% \caption {Others}
-% \label{tbl:osel}
-% \end{table*}
-% 
 % ----------------------------------------------------------------------
@@
 colnames(r.stats.sel.op) <- new.colnames
+
 @

### 2014-03-12 src/methodology.Rnw
update

@@
 
+For the first variant, we applied the x\% sampling to the result of the first
+sampling based on line counts. That is, in the case of methods, we first
+selected $#linecount$ mutants each from each method, and applied the x\%
+selection to the result of this selection. For the second variant, we did
+the sampling in one go, where we chose $#linecount/x$ number of mutants from
+each program element.
+
 \subsubsection{One per element}

### 2014-03-12 src/methodology.Rnw
update

--- 2014-03-12 src/methodology.Rnw
@@
 
+For the first variant, we applied the x\% sampling to the result of the first
+sampling based on line counts. That is, in the case of methods, we first
+selected \textit{linecount} mutants each from each method, and applied the x\%
+selection to the result of this selection. For the second variant, we did
+the sampling in one go, where we chose \textit{linecount/x} number of mutants from
+each program element.
+
 \subsubsection{One per element}

### 2014-03-12 src/results.Rnw
update

@@
 
-The Table~\ref{tbl:lcountl} provides the results for line count criteria.
+The Table~\ref{tbl:lcountl} provides the results for line count criteria where the
+sampling was conducted outside program element, and Table~\ref{tbl:lcountw} contains
+the results for line count criteria where the sampling was conducted inside the
+program element.
 

### 2014-03-12 src/methodology.Rnw
update

@@
 operators. However, given the constraints of a bytecode based mutation system,
-we believe that our procedure is reasonable.
+we believe that our procedure is reasonable. An interesting point is that
+by this procedure statement deletion is nolonger a simple mutation and qualifies
+as a higher order mutation operator. Infact, the procedure we outlined can
+be used in general to judge the effectiveness of a higher order operator from
+the results of first order mutatin operators that makeup the higher order
+mutant in question.

### 2014-03-12 src/results.Rnw
update

@@
 the results for line count criteria where the sampling was conducted inside the
-program element.
+program element. Similaryl the Table~\ref{tbl:onesel} contains the results for
+the criteria of one mutant per program element.
 
-\subsection{SDL vs Random selection}
-\begin{figure*}[t]
-<<sdl.x,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-par(mfrow=c(2,2))
-with(o.pit.all, plot(all.cov~TSDL.cov, pch='+', main='Original SDL'))
-with(o.pit.all, plot(all.cov~l.1x1_per_line.cov, pch='+', main='Original 1 per line'))
-with(r.pit.all, plot(all.cov~TSDL.cov, pch='+', main='Randoop SDl'))
-with(r.pit.all, plot(all.cov~l.1x1_per_line.cov, pch='+', main='Randoop 1 per line'))
-@
-\label{fig:sdl1}
-\caption{Statement Deletion vs One per line.}
-\end{figure*}
-<<results='asis'>>=
-oprand <- subset(stats.df,!grepl('^..op', rownames(stats.df)))
+Finally Table~\ref{tbl:opsel} contains the results for operator selectionl. Unlike
+the other tables, the first column here contains the kind of operator selection
+applied. We have tabulated the results of applying particular kinds of operator
+selection. The TSDL row is the result of applying only the higher order mutant
+equivalent to \textit{statement deletion}. The rows that have prefixes \textit{op:}
+are the result of applying only a single mutation operator on the program. The rows
+with \textit{opsel:} contains the results of various operator selection mechansisms.
+All the \textit{opsel:N-sel} are the results of N-selective operator selection
+strategies~\cite{offutt1993anexperimental}. We used the order of operators
+determined from Figure~\ref{fig:op} for this purpose.
 
-oprand.x <- subset(oprand,grepl('^.1x[0-9]+_per_', operator))
-oprand.l <- subset(oprand,!grepl('^.1x[0-9]+_per_', operator))
-@
+% \subsection{SDL vs Random selection}
+% \begin{figure*}[t]
+% <<sdl.x,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+% par(mfrow=c(2,2))
+% with(o.pit.all, plot(all.cov~TSDL.cov, pch='+', main='Original SDL'))
+% with(o.pit.all, plot(all.cov~l.1x1_per_line.cov, pch='+', main='Original 1 per line'))
+% with(r.pit.all, plot(all.cov~TSDL.cov, pch='+', main='Randoop SDl'))
+% with(r.pit.all, plot(all.cov~l.1x1_per_line.cov, pch='+', main='Randoop 1 per line'))
+% @
+% \label{fig:sdl1}
+% \caption{Statement Deletion vs One per line.}
+% \end{figure*}
+% <<results='asis'>>=
+% oprand <- subset(stats.df,!grepl('^..op', rownames(stats.df)))
+% 
+% oprand.x <- subset(oprand,grepl('^.1x[0-9]+_per_', operator))
+% oprand.l <- subset(oprand,!grepl('^.1x[0-9]+_per_', operator))
+% @

### 2014-03-12 src/introduction.Rnw
update
udpate

@@
 among testing professionals. Further, quite a few of the influential
-studies~\cite{offutt1993experimental,offutt1996anexperimental,wong1995reducing}
+studies~\cite{offutt1993experimental,offutt1996anexperimental,wong1995reducing,mresa1999efficiency}
 has been conducted on older programming languages such as Fortran with
@@
 
-\begin{itemize}
-\item simpler schemes work better. %Don't try sophisticated schemes. against Zhang's impression future work.
-\item Sampling at coarsest level (i.e. project level) gives the best result. % against Zhang's findings
-\item Single line sampling gives better results than statement deletion. % comparing random selection and operator selection.
- % SDL has been recommended by Offutt.
-
-\end{itemize}
 %We make the following contributions:

### 2014-03-12 src/threats.Rnw
udpate

\section{Threats to Validity}
While we have taken every care to ensure that our results are valid, and to eliminate the
effects pf random noice in experiments, our results are subject to the following threats
to validity.

Our results were observed on open source Java programs from Github repository, using the
maven build system. Further, only those projects that successfully completed mutation
testing within a designated amount of time were chosen. This implies that if there is a
confounding factor in play that affects the relation between the full mutation score and
sampling mutation score, and any of the noted factors, it might cause our results to be
either wrong or less applicable.

Secondly, we had to rely on the PIT mutation testing tool, and had to extend its capabilities
to some extent for our purposes. Software bugs are a fact of life. While every care has been
taken to avoid them, there is still some probability of some bugs having escaped us.

### 2014-03-13 src/paper.Rnw
update

@@
 is.installed <- function(mypkg) is.element(mypkg, installed.packages()[,1])
+options(CRAN = "http://cran.stat.ucla.edu")
 if (!is.installed("xtable")) install.packages("xtable")

### 2014-03-13 etc/abstract.tex
update

@@
 % 1.Statetheproblem
-Mutation analysis is a metric for measuring the quality of test suites.
-However, it is computationally intensive compared to other measures which it hard to use in practice.
-Choosing a smaller subset of mutations to run is a simple approach that can alleviate this problem.
-There exist multiple ways to reduce the set of mutations to run.
-Operator selection is an area that has been heavily researched.
-Recently, researchers have found that sampling can achive accuracy and mutant reduction similar to operator selection.
+Mutation analysis is a metric for measuring the quality of test
+suites. However, it is computationally intensive compared to other measures
+which makes it hard to use in practice. Choosing a smaller subset of mutations
+to run is a simple approach that can alleviate this problem.
+Operator selection is an area that has been heavily researched. Recently,
+researchers have found that sampling can achive accuracy and mutant
+reduction similar to operator selection.
 
 %2.Saywhyit’saninterestingproblem
-However, the statistical inference that can be drawn from these research has been limited due to the small number of subject programs.
-Further, which sampling technique is best is still an open problem that needs to be tackled on a much larger range of test subjects.
+However, the statistical inference that can be drawn from the previous
+research has been limited due to the small number of subject programs. Further,
+which sampling technique is best is still an open problem that needs to be
+tackled on a much larger range of test subjects.
 
 %3.Saywhatyoursolutionachieves
-Our research compares a number of sampling criteria, and operator selection criteria based on their ability to approximate the full mutation score, and also the consistency of mutation reduction ratios achieved.
-Our results provide a ranking that can be used to choose an appropriate mutation reduction technique according to the mutation reduction ratio desired, and how much reduction in accuracy is acceptable.
+Our research compares a number of sampling and operator selection criteria
+based on their ability to approximate the full mutation score, and also
+the consistency of mutation reduction ratios achieved. Our results provide
+a ranking that can be used to choose an appropriate mutation reduction
+technique according to the mutation reduction ratio desired, and how much
+reduction in accuracy is acceptable.
+
 %4.Saywhatfollowsfromyoursolution
-
-We find that all sampling criterias perform better than operator selection methods when considering their ability to predict the full mutation score, and also the consistency of mutation reduction ratios achieved.
-We find that simplest sampling criteria --- sampling based on projects works best on all the factors examined, We provide an explanation for this result, and why this is important for future research.
+We find that all sampling criterias perform better than operator selection
+methods when considering their ability to predict the full mutation score,
+and also the consistency of mutation reduction ratios achieved.  Specifically,
+we find that random selection of a mutant performs better than statement
+deletion operator selection criteria.
 

### 2014-03-13 src/introduction.Rnw
udpate

@@
 % 2. State your contributions
-Mutation analysis is a method of evaluation of quality of test-suites. It
+Mutation analysis is a method of evaluating the quality of test-suites. It
 involves producing a family of mutants with simple differences from the
@@
 analysis is to choose a smaller representative set of
-mutants~\cite{offutt2001mutation,jia2011analysis}-- often called the ``do
-fewer'' approach. This approach can be generally divided into selective
+mutants~\cite{offutt2001mutation,jia2011analysis}-- often called the \textit{do
+fewer} approach. This approach can be generally divided into selective
 strategies and sampling strategies.
@@
 true for selective mutation studies, studies in sampling, and also
-for comparatively newer studies that attempt to combine them. This is
-particularly worrisome if mutation analysis is to gain wider acceptance
-among testing professionals. Further, quite a few of the influential
+for comparatively newer studies that attempt to combine them. This
+is particularly worrisome if mutation analysis is to gain wider
+acceptance among testing professionals. Further, quite a few of the influential
 studies~\cite{offutt1993experimental,offutt1996anexperimental,wong1995reducing,mresa1999efficiency}
 has been conducted on older programming languages such as Fortran with
-operators specific to it, and are not directly applicable to newer languages
-such as Java, with significant differences. Finally, with the modern research
-into the ``do-smarter'' approach using byte code based mutation -- eliminating
-the compilation step -- operators based on source code modification is no
-longer be applicable, and their equivalents in the bytecode needs to be
-found and compared with other approaches. A detailed discussion of these
-issues can be found in Section~\ref{sec:related}.
+operators specific to it, and are not directly applicable to newer
+languages such as Java, with significant differences. Finally, with the
+modern research into the byte code based mutation (a \textit{do smarter}
+approach for eliminating the compilation step, and gaining execution speed)
+operators based on source code modification is no longer be applicable,
+and their equivalents in the bytecode needs to be found and compared with
+other approaches. A detailed discussion of these issues can be found in
+Section~\ref{sec:related}.
 
-% RAHUL>AMIN: I find the non-bulleted contributions better flowing as I can work the references
-% to other sections into it. Let me know if you have a better idea (As it stands neither my
-% previous wording, nor your bulleted list reads good)
-We have attempted to rectify this situation with a large scale study
-of industrial programs.  As detailed in Section~\ref{sec:methodology},
-we sample 188 real world Java programs from Github, with size ranging
-from 50loc to 100kloc, which allows us to make widely applicable
-statistical inferences. We provide the results from running both original human
-generated test-suites, and also programmatically generated test-suites,
-increasing the applicability of our findings to both researchers who seek to
-compare test-suites quickly, and to industrial software testers who might be
-looking for a way to reduce the time of their build cycle when using mutation
-coverage. The Section~\ref{sec:methodology} discusses the sampling strategies
-attempted, and the operator selection strategies in detail, and the results of
-our experiment are given in Section~\ref{sec:results}, followed by detailed
+We have attempted to rectify this situation with a large scale study of
+industrial programs.  As detailed in Section~\ref{sec:methodology}, we sample
+188 real world Java programs from Github, with size ranging from 50loc to
+100kloc, which allows widely applicable statistical inferences to be made. We
+provide the results from running both original human generated test-suites, and
+also programmatically generated test-suites, increasing the applicability of
+our findings to both researchers who seek to compare test-suites quickly,
+and to industrial software testers who might be looking for a way to
+reduce the time of their build cycle when using mutation coverage. The
+Section~\ref{sec:methodology} discusses the sampling strategies attempted,
+and the operator selection strategies in detail, and the results of our
+experiment are given in Section~\ref{sec:results}, followed by detailed
 discussion of what it implies in section ~\ref{sec:discussion}. The research
@@
 \begin{itemize}
+
 \item Our study is the largest so far in terms of both the size of programs
-involved (50loc to 100kloc), and the number of programs analyzed
-(188 unique open source projects) for mutant reduction strategies. This allows
+involved (50loc to 100kloc), and the number of programs analyzed (188
+unique open source projects) for mutant reduction strategies. This allows
 for stronger and widely applicable statistical inferences to be drawn.
-\item We compare a much large number of mutant reduction strategies, especially
-with respect to their predictive power over the final mutation score, the
-expected mutant reduction, and the stability of the amount of mutant reduction
-expected. Our sampling strategies include some that were suggested by other
-researchers, and also a few novel strategies that has not been published elsewhere.
-\item Our recommendations are valid for both testing researchers who might be
-comparing programmatically generated test-suites, and software testing
+
+\item We compare a much large number of mutant reduction strategies,
+especially with respect to their predictive power over the final mutation
+score, the expected mutant reduction, and the stability of the amount of
+mutant reduction expected. Our sampling strategies include some that were
+suggested by other researchers, and also a few novel strategies that has
+not been published elsewhere.
+
+\item Our recommendations are valid for both testing researchers who might
+be comparing programmatically generated test-suites, and software testing
 professionals working on real test-suites.
-\item Most importanly, we find that the simplest strategy of mutation reduction,
-that of x\% sampling is better than more sophesticated strategies in predicting
-the final mutation score. This is true not only for those strategies that we
-analyzed but also for any other strategies that seek to predict the full mutation
-score by looking at only a subset of mutants, irrespective of the kind of
-reduction used (operator selection, sampling or clustering, or any other).
+
+\item Most importantly, we find that random sampling strategies perform
+better than operator selection strategies consistently in predicting the
+final mutation score.
+
 \end{itemize}

### 2014-03-13 src/related.Rnw
.
udpate

--- 2014-03-10 src/related.Rnw
@@
 different approaches to reduce the cost of mutation analysis.
-Jia and Harman \cite{jia2011analysis} have categorized them into two
-broad categories: Mutation Reduction and Execution Reduction.
+These were categorized by Offutt and Untch~\cite{offutt2001mutation}
+into three approaches: Do \textit{fewer}, \textit{smarter}, \textit{faster}.
+The fewer approaches includes selective mutation and mutant sampling while
+weak mutation, parallelization of mutation analysis, space time trade offs
+are grouped under the umbrella of \textit{do smarter}. Finally
+\textit{do faster} approaches include byte code based mutation analysis
+systems like PIT, and similar binary patching methods.
 
-\subsection{Mutant Reduction}
-The idea of using a subset of mutants instead of all of them started
-by Mathur\cite{mathur1991performance} and 
-further have developed by Wong et al.\cite{wong1993mutation, wong1995reducing}
- and Offut et al. \cite{offutt1993experimental}.
-Each of them targeted the mutation operators of Mothra \cite{Mothra}.
-Mathur \cite{mathur1991performance} suggested removal of two mutation operators
-has little effect on the effectiveness of mutation testing.
-Offut et al. \cite{offutt1993experimental} experiment removal of 
-upto six mutation operators. They observe that the reduction has
-little effect on the mutation score.
-Wong and Mathur \cite{wong1995reducing} suggested two operators in Mothra system
-that could approximate mutation score.
+The idea of using a subset of mutants was born along with the mutation analysis
+itself. Budd~\cite{budd1980mutation} and Acree~\cite{Acree1980} showed that
+even 10\% sampling can achieve 99\% accuracy for the final score.
 
-Some studies have tried to find set of \emph{sufficient mutation operators} --minimal set
-of operators that while reducing the cost of mutations, its mutation score maintains
-a good correlation with mutaion score of the original set of operators.
+It was further investigated by Mathur~\cite{mathur1991performance},
+Wong et al.~\cite{wong1993mutation,wong1995reducing}, and
+Offutt et al.~\cite{offutt1993experimental} using the Mothra~\cite{Mothra}
+mutation operators for Fortran. Mathur~\cite{mathur1991performance,wong1995reducing}
+suggested constrained mutation where in only two mutation operators were used which
+were felt to be better than using the entire set.
+
+% Operator Selection also assumes that fault detection ability of some operators
+% are higher than others, and hence some operators should have higher weight
+% than others. ~\cite{wong1997comparison}
+
+A number of studies in the past have looked at the relative merits of operator
+selection and random sampling criteria, starting with Wong and Mathur in
+1995~\cite{wong1995reducing}. They compared x\% selection of each mutant type
+with operator selection of just two mutation operators, and finds that both
+achieved similar accuracy and reduction (80\%). This study was conducted on
+five small programs in C and Fortran.
+
+Some studies have tried to find set of \emph{sufficient mutation operators} that
+while reducing the cost of mutations, maintains the correlation with the full
+mutation score. Offutt~\cite{offutt1993experimental} suggested n-selective
+approach which advocates step by step removal of mutation operators that produced
+the largest number of mutants.
+
+Mresa et al.\cite{mresa1999efficiency} used the cost of detection of mutants as
+a means of selection, and uses it to define a set of operators. They find
+that if very high mutation score close to 100\% is required, x\% selective
+mutation is better than operator selection, and conversely for less stringent
+scores, operator selection would be better if cost of mutant is considered.
+
 Barbosa et. al.\cite{barbosa2001toward} provides a set of guidelines for selecting
@@
 formulate this problem as a variable reduction problem, and apply statistical
-approaches. They found a subset of 28 operators out of 108 opertors as the sufificient operators.
-Recently, Deng et al~\cite{deng2013empirical} considers the effect of using a single mutation operator 
--- the statement deletion operator. They define deletion for different language elements,
+approaches. They found a subset of 28 operators out of 108 operators as the sufficient
+operators.
 
-Wong and Mathur \cite{wong1995reducing}, Acree\cite{Acree1980}, and Budd\cite{Budd1980}  suggest \%x sampling of all mutants.
-They observed that random sampling of mutatnts can greatelly reduces the cost of mutation analysis while
-it can closely approximate the mutation score. Recently, Zhang et al. \cite{zhang2013ase} has shown that sampling
-as small as five percent is a good preditor of mutation score.
+Using only the statement deletion operator was first suggested by
+Untch~\cite{untch2009onreduced}, who found that it correlated ($R^2 = 0.97$) with the
+full mutation score better than other operator selection methods, while generating the
+least number of mutants.  This was further reinforced by Deng et al.~\cite{deng2013empirical}
+who defined deletion for different language elements, and found that an accuracy of 92\% is
+achieved while reducing the mutants by 80\%.
+
+Zhang et al.~\cite{zhang2010operator} compares operators based mutant selection in
+~\cite{barbosa2001toward,siami2008sufficient,offutt1996anexperimental} to random mutant selection.
+They find that none of these selection techniques are superior to random selection, with same number of
+mutants. They also find that equal mutation sampling is more effective for larger subjects compared to
+equal mutagen sampling and the reverse is true for smaller subjects.
+
+Recently, Zhang et al.~\cite{zhang2013ase} confirmed that sampling as few as 5\% mutants
+was sufficient for a very correlation (99\%) with the full mutation score, while sampling even
+fewer mutants has good potential for retaining high accuracy. They investigate 8 sampling
+strategies on top of operator based mutant selection and find that sampling strategies
+based on program components (based on methods) performed best.
 
@@
 
-Zhang et al.\cite{zhang2010operator} compare operator based mutant selection in 
-\cite{barbosa2001toward,siami2008sufficient,offutt1996anexperimental} to random mutant selection. 
-%They compare three diffrent operator based selection techniques from Offutt et al., Barbosa et al., and Namin 
-%et al. against random mutant selection, with equal mutant probability, and equal mutagen probaiblity. 
-They find that none of these selection techniques are superior to random selection, with same number of 
-mutants. They also find that equal mutation sampling is more effective for larger subjects compared to 
-equal mutagen sampling and the reverse is true for smaller subjects.
-Zhang et al.\cite{zhang2013ase} investigates 8 sampling strategies on top of operator
-based mutant selection. They find that sampling strategies based on program componenets.
-(based on methods) performed best.
-
-This work is closely related to Zhang et al.\cite{zhang2013ase}. We extend the scope of 
+This work is closely related to Zhang et al.~\cite{zhang2013ase}. We extend the scope of
 their study with much wider range of mutation selection and we experimented them on much more
@@
 
-\subsection{Execution Reduction}
+%\subsection{Execution Reduction}
 
-Weak mutation, devised by Howden \cite{howden1982weak}, considers a mutant as detected, if 
-the states of program after the mutated statement in mutant and the original
-program differ. Several oher studies have refined the idea theoretically \cite{horgan1990weak}and
-observed its effectiveness emperically\cite{offutt1994empirical,Offutt:1991:SWM:120807.120826}.
+%Weak mutation, devised by Howden \cite{howden1982weak}, considers a mutant as detected, if
+%the states of program after the mutated statement in mutant and the original
+%program differ. Several oher studies have refined the idea theoretically \cite{horgan1990weak}and
+%observed its effectiveness emperically\cite{offutt1994empirical,Offutt:1991:SWM:120807.120826}.
 
-Some studies have utlized parallel computation to enhance the execution time of 
-the mutation testing \cite{}. Others have used custom built compilers and interpretors \cite{}
-to reduce the overall compile time in mutation testing \cite{}.
+%Some studies have utlized parallel computation to enhance the execution time of
+%the mutation testing \cite{}. Others have used custom built compilers and interpretors \cite{}
+%to reduce the overall compile time in mutation testing \cite{}.

### 2014-03-13 src/methodology.Rnw
udpate

--- 2014-03-12 src/methodology.Rnw
@@
 of test-suites. The original test-suites present in a limited number of
-projects, and automatically generatd test-suites using randoop.  Due
+projects, and automatically generated test-suites using randoop.  Due
 limited resources, we had to further reduce the programs and test-suites
@@
 of test-suites, we sampled 110 suites each for both original and randoop
-generated test-suiets. This gave us 81 unique projects for both original
+generated test-suits. This gave us 81 unique projects for both original
 and randoop, and remaining projects having both flavors of test suites.
@@
 For a detailed description of each mutants, please see~\cite{pitmut}.
-PIT was also modifed to provide random selection of mutants according
-to various criterias. Finally, to remove random noice, each criteria
+PIT was also modified to provide random selection of mutants according
+to various criteria. Finally, to remove random noise, each criteria
 described has been run four times, and the results are averaged to produce
@@
 }
-\caption{PIT Mutation Opeators (We have used abbreviations instead of operator names.)}
+\caption{PIT Mutation Operators (We have used abbreviations instead of operator names.)}
 \label{tbl:pitop}
@@
 
-One of the criterias we sampled was \textit{statement deletion}.
+One of the criteria we sampled was \textit{statement deletion}.
 Since we use PIT, which is a bytecode based mutation engine, implementing direct equivalent of
@@
 
-\subsection{Sampling Criterias}
+\subsection{Sampling Criteria}
 
@@
 Next, we explored in the other direction, by forcing the program elements
-to return atleast one element by using the \textit{ceil(sample)}. That is,
+to return at least one element by using the \textit{ceil(sample)}. That is,
 irrespective of the fraction being sampled, the simplest elements always
-contributed atleast one mutant to the total sample.
+contributed at least one mutant to the total sample.
 
@@
 operators. However, given the constraints of a bytecode based mutation system,
-we believe that our procedure is reasonable.
+we believe that our procedure is reasonable. An interesting point is that
+by this procedure statement deletion is no longer a simple mutation and qualifies
+as a higher order mutation operator. In fact, the procedure we outlined can
+be used in general to judge the effectiveness of a higher order operator from
+the results of first order mutation operators that makeup the higher order
+mutant in question.

### 2014-03-13 src/analysis.Rnw
udpate
update

@@
 @
-\subsubsection{x\% selection}
 \begin{table*}
@@
 \label{sec:analysis}
-For the purposes of comparing between the criterias, we computed the
+For the purposes of comparing between the criteria, we computed the
 correlation between sampled mutation score and full mutation score.
@@
 project. So as a heuristic, we suggest looking at only those projects which
-has a mean reduction ratio atleast twice the standard deviation.)
+has a mean reduction ratio at least twice the standard deviation.)
 
@@
 \caption {The line count selection criteria results.}
-\label{tbl:locsel}
+\label{tbl:lcountl}
 \end{table*}
@@
 \caption {The line count selection criteria results (within).}
-\label{tbl:locsel}
+\label{tbl:lcountw}
 \end{table*}

### 2014-03-13 src/analysis.Rnw
update

@@
 
+o.stats.sel.op$kind  <- ifelse(grepl('opsel:', o.stats.sel.op$operator), 'selection', 'operator')
+r.stats.sel.op$kind  <- ifelse(grepl('opsel:', o.stats.sel.op$operator), 'selection', 'operator')
+
+o.stats.sel.op$operator  <- gsub('_','',gsub('op.*:','', o.stats.sel.op$operator))
+r.stats.sel.op$operator  <- gsub('_','',gsub('op.*:','', r.stats.sel.op$operator))
+
+o.stats.sel.op <- o.stats.sel.op[,c(1,7,2,3,4,5,6)]
+r.stats.sel.op <- r.stats.sel.op[,c(1,7,2,3,4,5,6)]
+
+#o.stats.sel.one$sampling  <- gsub('_.*','', o.stats.sel.one$operator)
+
 @

### 2014-03-14 src/analysis.Rnw
update

@@
 <<opsel>>=
-stats.op <- subset(stats.rest, grepl('^(op|TSDL)', operator))
+stats.op <- subset(stats.rest, grepl('^(op:|TSDL)', operator))
 o.stats.sel.op <- subset(o.f(stats.op), select=sel.colnames)
 r.stats.sel.op <- subset(r.f(stats.op), select=sel.colnames)
-stats.rest <- subset(stats.rest, !grepl('^(op|TSDL)', operator))
+stats.rest <- subset(stats.rest, !grepl('^(op:|TSDL)', operator))
 colnames(o.stats.sel.op) <- new.colnames
@@
 
-o.stats.sel.op$kind  <- ifelse(grepl('opsel:', o.stats.sel.op$operator), 'selection', 'operator')
-r.stats.sel.op$kind  <- ifelse(grepl('opsel:', o.stats.sel.op$operator), 'selection', 'operator')
+#o.stats.sel.op$kind  <- ifelse(grepl('opsel:', o.stats.sel.op$operator), 'selection', 'operator')
+#r.stats.sel.op$kind  <- ifelse(grepl('opsel:', o.stats.sel.op$operator), 'selection', 'operator')
 
@@
 #o.stats.sel.one$sampling  <- gsub('_.*','', o.stats.sel.one$operator)
+@
 
+<<opselx>>=
+stats.opsel <- subset(stats.rest, grepl('^opsel', operator))
+o.stats.sel.opsel <- subset(o.f(stats.opsel), select=sel.colnames)
+r.stats.sel.opsel <- subset(r.f(stats.opsel), select=sel.colnames)
+stats.rest <- subset(stats.rest, !grepl('^opsel', operator))
+colnames(o.stats.sel.opsel) <- new.colnames
+colnames(r.stats.sel.opsel) <- new.colnames
+
+#o.stats.sel.op$kind  <- ifelse(grepl('opsel:', o.stats.sel.op$operator), 'selection', 'operator')
+#r.stats.sel.op$kind  <- ifelse(grepl('opsel:', o.stats.sel.op$operator), 'selection', 'operator')
+
+o.stats.sel.opsel$operator  <- gsub('_','',gsub('op.*:','', o.stats.sel.opsel$operator))
+r.stats.sel.opsel$operator  <- gsub('_','',gsub('op.*:','', r.stats.sel.opsel$operator))
+
+o.stats.sel.opsel <- o.stats.sel.opsel[,c(1,7,2,3,4,5,6)]
+r.stats.sel.opsel <- r.stats.sel.opsel[,c(1,7,2,3,4,5,6)]
+
+#o.stats.sel.one$sampling  <- gsub('_.*','', o.stats.sel.one$operator)
 @
@@
 print(xtable(r.stats.sel.op, caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
+@
+\end{minipage}
+\bigskip
+\caption {Operators}
+\label{tbl:operators}
+\end{table*}
+
+\begin{table*}
+\begin{minipage}[h]{0.49\linewidth}
+<<results='asis'>>=
+print(xtable(o.stats.sel.opsel, caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
+@
+\end{minipage}
+\hspace{0.5cm}
+\begin{minipage}[h]{0.49\linewidth}
+<<results='asis'>>=
+print(xtable(r.stats.sel.opsel, caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
 @

### 2014-03-14 src/analysis.Rnw
.

@@
 
-o.stats.sel.op <- o.stats.sel.op[,c(1,7,2,3,4,5,6)]
-r.stats.sel.op <- r.stats.sel.op[,c(1,7,2,3,4,5,6)]
+o.stats.sel.op <- o.stats.sel.op[,c(0,6,1,2,3,4,5)]
+r.stats.sel.op <- r.stats.sel.op[,c(0,6,1,2,3,4,5)]
 
@@
 
-o.stats.sel.opsel <- o.stats.sel.opsel[,c(1,7,2,3,4,5,6)]
-r.stats.sel.opsel <- r.stats.sel.opsel[,c(1,7,2,3,4,5,6)]
+o.stats.sel.opsel <- o.stats.sel.opsel[,c(0,6,1,2,3,4,5)]
+r.stats.sel.opsel <- r.stats.sel.opsel[,c(0,6,1,2,3,4,5)]
 

### 2014-03-14 src/analysis.Rnw
update

--- 2014-03-13 src/analysis.Rnw
@@
 <<xpercentunit>>=
-sel.colnames <- c('operator', 'r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier')
-new.colnames <- c('operator', 'r^2',      'm.red',            'm.sd',         'num',    'B*')
-stats.xp <- subset(stats.df, grepl('^(r|rr|rc)[.]', operator)) # We are ignoring ceil here. add rc if needed.
-
-o.stats.sel.xp <- subset(o.f(stats.xp), select=sel.colnames)
-r.stats.sel.xp <- subset(r.f(stats.xp), select=sel.colnames)
-stats.rest <- subset(stats.df, !grepl('^(r|rr|rc)[.]', operator))
-colnames(o.stats.sel.xp) <- new.colnames
-colnames(r.stats.sel.xp) <- new.colnames
-o.stats.sel.xp$scope <- NA
-r.stats.sel.xp$scope <- NA
-o.stats.sel.xp$sampling <- NA
-r.stats.sel.xp$sampling <- NA
-
-f <- function(x) {
-  x <- x[,c(7,8,2,3,4,5,6)]
-  return(x)
-}
-
-o.stats.sel.xp.sample <- subset(o.stats.sel.xp, grepl('^rr[.]', operator))
-r.stats.sel.xp.sample <- subset(r.stats.sel.xp, grepl('^rr[.]', operator))
-
-o.stats.sel.xp.sample$operator <- gsub('rr[.]1x','1/', o.stats.sel.xp.sample$operator)
-o.stats.sel.xp.sample$scope <- gsub('.*_','', o.stats.sel.xp.sample$operator)
-o.stats.sel.xp.sample$sampling <- gsub('_.*','', o.stats.sel.xp.sample$operator)
-r.stats.sel.xp.sample$operator  <- gsub('rr[.]1x','1/', r.stats.sel.xp.sample$operator)
-r.stats.sel.xp.sample$scope <- gsub('.*_','', r.stats.sel.xp.sample$operator)
-r.stats.sel.xp.sample$sampling <- gsub('_.*','', r.stats.sel.xp.sample$operator)
-
-o.stats.sel.xp.round <- subset(o.stats.sel.xp, grepl('^r[.]', operator))
-r.stats.sel.xp.round <- subset(r.stats.sel.xp, grepl('^r[.]', operator))
-
-o.stats.sel.xp.round$operator  <- gsub('r[.]1x','1/', o.stats.sel.xp.round$operator)
-o.stats.sel.xp.round$scope  <- gsub('.*_','', o.stats.sel.xp.round$operator)
-o.stats.sel.xp.round$sampling  <- gsub('_.*','', o.stats.sel.xp.round$operator)
-r.stats.sel.xp.round$operator  <- gsub('r[.]1x','1/', r.stats.sel.xp.round$operator)
-r.stats.sel.xp.round$scope  <- gsub('.*_','', r.stats.sel.xp.round$operator)
-r.stats.sel.xp.round$sampling  <- gsub('_.*','', r.stats.sel.xp.round$operator)
-
-o.stats.sel.xp.ceil <- subset(o.stats.sel.xp, grepl('^rc[.]', operator))
-r.stats.sel.xp.ceil <- subset(r.stats.sel.xp, grepl('^rc[.]', operator))
-
-o.stats.sel.xp.ceil$operator  <- gsub('rc[.]1x','1/', o.stats.sel.xp.ceil$operator)
-o.stats.sel.xp.ceil$scope  <- gsub('.*_','', o.stats.sel.xp.ceil$operator)
-o.stats.sel.xp.ceil$sampling  <- gsub('_.*','', o.stats.sel.xp.ceil$operator)
-r.stats.sel.xp.ceil$operator  <- gsub('rc[.]1x','1/', r.stats.sel.xp.ceil$operator)
-r.stats.sel.xp.ceil$scope  <- gsub('.*_','', r.stats.sel.xp.ceil$operator)
-r.stats.sel.xp.ceil$sampling  <- gsub('_.*','', r.stats.sel.xp.ceil$operator)
-
+#1
 @
@@
 \begin{figure*}[t]
+<<x.per.sel.sample,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+o.xp.sample <- subset(o.processed, grepl('^rr[.].*.m[.]red',ind))
+ggplot(subset(o.xp.sample, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
+  stat_boxplot(geom ='errorbar')+
+  geom_boxplot() + facet_wrap(~type) + myopts
+@
+\caption{The effect of sample(x) reduction. All are above 0.90 $R^2$.}
+\label{fig:xsamplesel}
+\end{figure*}
+
+\begin{figure*}[t]
 <<x.per.sel.round,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-theme_set(theme_bw(12))
-myopts <- theme(panel.background = element_blank())
-o.xp <- subset(o.processed, grepl('^r[.].*.m[.]red',ind))
-ggplot(subset(o.xp, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
+o.xp.round <- subset(o.processed, grepl('^r[.].*.m[.]red',ind))
+ggplot(subset(o.xp.round, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
   stat_boxplot(geom ='errorbar')+
@@
 \label{fig:xroundsel}
-\end{figure*}
-
-\begin{figure*}[t]
-<<x.per.sel.sample,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-o.xp <- subset(o.processed, grepl('^rr[.].*.m[.]red',ind))
-ggplot(subset(o.xp, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
-  stat_boxplot(geom ='errorbar')+
-  geom_boxplot() + facet_wrap(~type) + myopts
-@
-\caption{The effect of sample(x) reduction. All are above 0.90 $R^2$.}
-\label{fig:xsamplesel}
 \end{figure*}
@@
 <<count>>=
-stats.loc <- subset(stats.rest, grepl('^l[.]', operator))
-o.stats.sel.loc <- subset(o.f(stats.loc), select=sel.colnames)
-r.stats.sel.loc <- subset(r.f(stats.loc), select=sel.colnames)
-stats.rest <- subset(stats.rest, !grepl('^l[.]', operator))
-colnames(o.stats.sel.loc) <- new.colnames
-colnames(r.stats.sel.loc) <- new.colnames
-
-o.stats.sel.loc$operator  <- gsub('l[.]1x','1/', o.stats.sel.loc$operator)
-o.stats.sel.loc$scope  <- gsub('.*_','', o.stats.sel.loc$operator)
-o.stats.sel.loc$sampling  <- gsub('_.*','', o.stats.sel.loc$operator)
-r.stats.sel.loc$operator  <- gsub('l[.]1x','1/', r.stats.sel.loc$operator)
-r.stats.sel.loc$scope  <- gsub('.*_','', r.stats.sel.loc$operator)
-r.stats.sel.loc$sampling  <- gsub('_.*','', r.stats.sel.loc$operator)
-
-stats.loc.w <- subset(stats.rest, grepl('^wl[.]', operator))
-o.stats.sel.loc.w <- subset(o.f(stats.loc.w), select=sel.colnames)
-r.stats.sel.loc.w <- subset(r.f(stats.loc.w), select=sel.colnames)
-stats.rest <- subset(stats.rest, !grepl('^wl[.]', operator))
-colnames(o.stats.sel.loc.w) <- new.colnames
-colnames(r.stats.sel.loc.w) <- new.colnames
-
-o.stats.sel.loc.w$operator  <- gsub('wl[.]1x','1/', o.stats.sel.loc.w$operator)
-o.stats.sel.loc.w$scope  <- gsub('.*_','', o.stats.sel.loc.w$operator)
-o.stats.sel.loc.w$sampling  <- gsub('_.*','', o.stats.sel.loc.w$operator)
-r.stats.sel.loc.w$operator  <- gsub('wl[.]1x','1/', r.stats.sel.loc.w$operator)
-r.stats.sel.loc.w$scope  <- gsub('.*_','', r.stats.sel.loc.w$operator)
-r.stats.sel.loc.w$sampling  <- gsub('_.*','', r.stats.sel.loc.w$operator)
-
+#2
 @
@@
 <<loc.per.sel.sample,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-o.loc <- subset(o.processed, grepl('^l[.].*.m[.]red',ind))
-ggplot(subset(o.loc, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
+o.loc.ext <- subset(o.processed, grepl('^l[.].*.m[.]red',ind))
+ggplot(subset(o.loc.ext, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
   stat_boxplot(geom ='errorbar')+
@@
 <<wloc.per.sel.sample,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-o.loc <- subset(o.processed, grepl('^wl[.].*.m[.]red',ind))
-ggplot(subset(o.loc, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
+o.loc.int <- subset(o.processed, grepl('^wl[.].*.m[.]red',ind))
+ggplot(subset(o.loc.int, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
   stat_boxplot(geom ='errorbar')+
@@
 <<one>>=
-stats.one <- subset(stats.rest, grepl('^o[.]', operator))
-
-o.stats.sel.one <- subset(o.f(stats.one), select=sel.colnames)
-r.stats.sel.one <- subset(r.f(stats.one), select=sel.colnames)
-stats.rest <- subset(stats.rest, !grepl('^o[.]', operator))
-colnames(o.stats.sel.one) <- new.colnames
-colnames(r.stats.sel.one) <- new.colnames
-
-o.stats.sel.one$operator  <- gsub('o[.]1x','1/', o.stats.sel.one$operator)
-o.stats.sel.one$scope  <- gsub('.*_','', o.stats.sel.one$operator)
-o.stats.sel.one$sampling  <- gsub('_.*','', o.stats.sel.one$operator)
-
-r.stats.sel.one$operator  <- gsub('o[.]1x','1/', r.stats.sel.one$operator)
-r.stats.sel.one$scope  <- gsub('.*_','', r.stats.sel.one$operator)
-r.stats.sel.one$sampling  <- gsub('_.*','', r.stats.sel.one$operator)
-
+#3
 @
@@
 <<opsel>>=
-stats.op <- subset(stats.rest, grepl('^(op|TSDL)', operator))
-o.stats.sel.op <- subset(o.f(stats.op), select=sel.colnames)
-r.stats.sel.op <- subset(r.f(stats.op), select=sel.colnames)
-stats.rest <- subset(stats.rest, !grepl('^(op|TSDL)', operator))
-colnames(o.stats.sel.op) <- new.colnames
-colnames(r.stats.sel.op) <- new.colnames
-
-o.stats.sel.op$kind  <- ifelse(grepl('opsel:', o.stats.sel.op$operator), 'selection', 'operator')
-r.stats.sel.op$kind  <- ifelse(grepl('opsel:', o.stats.sel.op$operator), 'selection', 'operator')
-
-o.stats.sel.op$operator  <- gsub('_','',gsub('op.*:','', o.stats.sel.op$operator))
-r.stats.sel.op$operator  <- gsub('_','',gsub('op.*:','', r.stats.sel.op$operator))
-
-o.stats.sel.op <- o.stats.sel.op[,c(1,7,2,3,4,5,6)]
-r.stats.sel.op <- r.stats.sel.op[,c(1,7,2,3,4,5,6)]
-
-#o.stats.sel.one$sampling  <- gsub('_.*','', o.stats.sel.one$operator)
-
+#4
 @

### 2014-03-14 src/paper.Rnw
update

@@
 \end{comment}
+<<>>=
+theme_set(theme_bw(12))
+myopts <- theme(panel.background = element_blank())
+
+sel.colnames <- c('operator', 'r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier')
+new.colnames <- c('operator', 'r^2',      'm.red',            'm.sd',         'num',    'B*')
+stats.xp <- subset(stats.df, grepl('^(r|rr|rc)[.]', operator)) # We are ignoring ceil here. add rc if needed.
+
+o.stats.sel.xp <- subset(o.f(stats.xp), select=sel.colnames)
+r.stats.sel.xp <- subset(r.f(stats.xp), select=sel.colnames)
+stats.rest <- subset(stats.df, !grepl('^(r|rr|rc)[.]', operator))
+colnames(o.stats.sel.xp) <- new.colnames
+colnames(r.stats.sel.xp) <- new.colnames
+o.stats.sel.xp$scope <- NA
+r.stats.sel.xp$scope <- NA
+o.stats.sel.xp$sampling <- NA
+r.stats.sel.xp$sampling <- NA
+
+f <- function(x) {
+  x <- x[,c(7,8,2,3,4,5,6)]
+  return(x)
+}
+
+o.stats.sel.xp.sample <- subset(o.stats.sel.xp, grepl('^rr[.]', operator))
+r.stats.sel.xp.sample <- subset(r.stats.sel.xp, grepl('^rr[.]', operator))
+
+o.stats.sel.xp.sample$operator <- gsub('rr[.]1x','1/', o.stats.sel.xp.sample$operator)
+o.stats.sel.xp.sample$scope <- gsub('.*_','', o.stats.sel.xp.sample$operator)
+o.stats.sel.xp.sample$sampling <- gsub('_.*','', o.stats.sel.xp.sample$operator)
+r.stats.sel.xp.sample$operator  <- gsub('rr[.]1x','1/', r.stats.sel.xp.sample$operator)
+r.stats.sel.xp.sample$scope <- gsub('.*_','', r.stats.sel.xp.sample$operator)
+r.stats.sel.xp.sample$sampling <- gsub('_.*','', r.stats.sel.xp.sample$operator)
+
+o.stats.sel.xp.round <- subset(o.stats.sel.xp, grepl('^r[.]', operator))
+r.stats.sel.xp.round <- subset(r.stats.sel.xp, grepl('^r[.]', operator))
+
+o.stats.sel.xp.round$operator  <- gsub('r[.]1x','1/', o.stats.sel.xp.round$operator)
+o.stats.sel.xp.round$scope  <- gsub('.*_','', o.stats.sel.xp.round$operator)
+o.stats.sel.xp.round$sampling  <- gsub('_.*','', o.stats.sel.xp.round$operator)
+r.stats.sel.xp.round$operator  <- gsub('r[.]1x','1/', r.stats.sel.xp.round$operator)
+r.stats.sel.xp.round$scope  <- gsub('.*_','', r.stats.sel.xp.round$operator)
+r.stats.sel.xp.round$sampling  <- gsub('_.*','', r.stats.sel.xp.round$operator)
+
+o.stats.sel.xp.ceil <- subset(o.stats.sel.xp, grepl('^rc[.]', operator))
+r.stats.sel.xp.ceil <- subset(r.stats.sel.xp, grepl('^rc[.]', operator))
+
+o.stats.sel.xp.ceil$operator  <- gsub('rc[.]1x','1/', o.stats.sel.xp.ceil$operator)
+o.stats.sel.xp.ceil$scope  <- gsub('.*_','', o.stats.sel.xp.ceil$operator)
+o.stats.sel.xp.ceil$sampling  <- gsub('_.*','', o.stats.sel.xp.ceil$operator)
+r.stats.sel.xp.ceil$operator  <- gsub('rc[.]1x','1/', r.stats.sel.xp.ceil$operator)
+r.stats.sel.xp.ceil$scope  <- gsub('.*_','', r.stats.sel.xp.ceil$operator)
+r.stats.sel.xp.ceil$sampling  <- gsub('_.*','', r.stats.sel.xp.ceil$operator)
+# 1 done
+stats.loc <- subset(stats.rest, grepl('^l[.]', operator))
+o.stats.sel.loc <- subset(o.f(stats.loc), select=sel.colnames)
+r.stats.sel.loc <- subset(r.f(stats.loc), select=sel.colnames)
+stats.rest <- subset(stats.rest, !grepl('^l[.]', operator))
+colnames(o.stats.sel.loc) <- new.colnames
+colnames(r.stats.sel.loc) <- new.colnames
+
+o.stats.sel.loc$operator  <- gsub('l[.]1x','1/', o.stats.sel.loc$operator)
+o.stats.sel.loc$scope  <- gsub('.*_','', o.stats.sel.loc$operator)
+o.stats.sel.loc$sampling  <- gsub('_.*','', o.stats.sel.loc$operator)
+r.stats.sel.loc$operator  <- gsub('l[.]1x','1/', r.stats.sel.loc$operator)
+r.stats.sel.loc$scope  <- gsub('.*_','', r.stats.sel.loc$operator)
+r.stats.sel.loc$sampling  <- gsub('_.*','', r.stats.sel.loc$operator)
+
+stats.loc.w <- subset(stats.rest, grepl('^wl[.]', operator))
+o.stats.sel.loc.w <- subset(o.f(stats.loc.w), select=sel.colnames)
+r.stats.sel.loc.w <- subset(r.f(stats.loc.w), select=sel.colnames)
+stats.rest <- subset(stats.rest, !grepl('^wl[.]', operator))
+colnames(o.stats.sel.loc.w) <- new.colnames
+colnames(r.stats.sel.loc.w) <- new.colnames
+
+o.stats.sel.loc.w$operator  <- gsub('wl[.]1x','1/', o.stats.sel.loc.w$operator)
+o.stats.sel.loc.w$scope  <- gsub('.*_','', o.stats.sel.loc.w$operator)
+o.stats.sel.loc.w$sampling  <- gsub('_.*','', o.stats.sel.loc.w$operator)
+r.stats.sel.loc.w$operator  <- gsub('wl[.]1x','1/', r.stats.sel.loc.w$operator)
+r.stats.sel.loc.w$scope  <- gsub('.*_','', r.stats.sel.loc.w$operator)
+r.stats.sel.loc.w$sampling  <- gsub('_.*','', r.stats.sel.loc.w$operator)
+# 2 done
+
+stats.one <- subset(stats.rest, grepl('^o[.]', operator))
+
+o.stats.sel.one <- subset(o.f(stats.one), select=sel.colnames)
+r.stats.sel.one <- subset(r.f(stats.one), select=sel.colnames)
+stats.rest <- subset(stats.rest, !grepl('^o[.]', operator))
+colnames(o.stats.sel.one) <- new.colnames
+colnames(r.stats.sel.one) <- new.colnames
+
+o.stats.sel.one$operator  <- gsub('o[.]1x','1/', o.stats.sel.one$operator)
+o.stats.sel.one$scope  <- gsub('.*_','', o.stats.sel.one$operator)
+o.stats.sel.one$sampling  <- gsub('_.*','', o.stats.sel.one$operator)
+
+r.stats.sel.one$operator  <- gsub('o[.]1x','1/', r.stats.sel.one$operator)
+r.stats.sel.one$scope  <- gsub('.*_','', r.stats.sel.one$operator)
+r.stats.sel.one$sampling  <- gsub('_.*','', r.stats.sel.one$operator)
+# 3 done
+
+stats.op <- subset(stats.rest, grepl('^(op:|TSDL)', operator))
+o.stats.sel.op <- subset(o.f(stats.op), select=sel.colnames)
+r.stats.sel.op <- subset(r.f(stats.op), select=sel.colnames)
+stats.rest <- subset(stats.rest, !grepl('^(op:|TSDL)', operator))
+colnames(o.stats.sel.op) <- new.colnames
+colnames(r.stats.sel.op) <- new.colnames
+
+#o.stats.sel.op$kind  <- ifelse(grepl('opsel:', o.stats.sel.op$operator), 'selection', 'operator')
+#r.stats.sel.op$kind  <- ifelse(grepl('opsel:', o.stats.sel.op$operator), 'selection', 'operator')
+
+o.stats.sel.op$operator  <- gsub('NVMC','NMC', gsub('_','',gsub('op.*:','', o.stats.sel.op$operator)))
+r.stats.sel.op$operator  <- gsub('NVMC','NMC', gsub('_','',gsub('op.*:','', r.stats.sel.op$operator)))
+
+o.stats.sel.op <- o.stats.sel.op[,c(0,6,1,2,3,4,5)]
+r.stats.sel.op <- r.stats.sel.op[,c(0,6,1,2,3,4,5)]
+
+stats.opsel <- subset(stats.rest, grepl('^opsel', operator))
+o.stats.sel.opsel <- subset(o.f(stats.opsel), select=sel.colnames)
+r.stats.sel.opsel <- subset(r.f(stats.opsel), select=sel.colnames)
+stats.rest <- subset(stats.rest, !grepl('^opsel', operator))
+colnames(o.stats.sel.opsel) <- new.colnames
+colnames(r.stats.sel.opsel) <- new.colnames
+
+#o.stats.sel.op$kind  <- ifelse(grepl('opsel:', o.stats.sel.op$operator), 'selection', 'operator')
+#r.stats.sel.op$kind  <- ifelse(grepl('opsel:', o.stats.sel.op$operator), 'selection', 'operator')
+
+o.stats.sel.opsel$operator  <- gsub('_','',gsub('op.*:','', o.stats.sel.opsel$operator))
+r.stats.sel.opsel$operator  <- gsub('_','',gsub('op.*:','', r.stats.sel.opsel$operator))
+
+o.stats.sel.opsel <- o.stats.sel.opsel[,c(0,6,1,2,3,4,5)]
+r.stats.sel.opsel <- r.stats.sel.opsel[,c(0,6,1,2,3,4,5)]
+# 4 done
+
+@
 % 10 pages for the main text + 1 for references.

### 2014-03-14 src/analysis.Rnw
update

@@
 sample, it probably means there are no mutants generated on the whole,
-we used $lm(M_{all}~0+M_{sample})$ as the regression formula, and report
+we used
+\[\mu_\{M_{all}|M_{reduced}\} = 0 + \beta_1 \times M_{reduced}\]
+as the regression formula, and report
 the correlation from this linear regression. We also report the expected
-multiplier factor for the sampled mutation score. This factor determines
-the ease of satisfying the sampling criteria. That is, if the multiplier
-factor is small, then it is easier to satisfy compared to a larger multiplier
-factor.
+multiplier factor $\beta_1$ for the sampled mutation score. This factor
+determines the ease of satisfying the sampling criteria. That is, if the
+multiplier factor is small, then it is easier to satisfy compared to a
+larger multiplier factor.
+
 Next, for each criteria, we computed the reduction of mutants given by the
@@
 
-For some of the smaller projects, some of the sampling criteria did not
-return any results. This is also collected in our tables.
+A few projects did not return any results for some large reduction factors.
+This number of valid results from projects are also collected in the result
+tables.
 

### 2014-03-14 src/results.Rnw
.

@@
 Fifth column contains the standard deviation of the same. A few of the projects
-did not return any value for certain sampling criterias for particular mutation
+did not return any value for certain sampling criteria for particular mutation
 reduction fractions. The sixth column contains the number of projects that
@@
 the results for line count criteria where the sampling was conducted inside the
-program element. Similaryl the Table~\ref{tbl:onesel} contains the results for
+program element. Similarly the Table~\ref{tbl:onesel} contains the results for
 the criteria of one mutant per program element.
 
-Finally Table~\ref{tbl:opsel} contains the results for operator selectionl. Unlike
-the other tables, the first column here contains the kind of operator selection
-applied. We have tabulated the results of applying particular kinds of operator
-selection. The TSDL row is the result of applying only the higher order mutant
-equivalent to \textit{statement deletion}. The rows that have prefixes \textit{op:}
-are the result of applying only a single mutation operator on the program. The rows
-with \textit{opsel:} contains the results of various operator selection mechansisms.
-All the \textit{opsel:N-sel} are the results of N-selective operator selection
+Finally Table~\ref{tbl:operators} contains the results when only a single operator
+is used, and Table~\ref{tbl:opsel} contains the results for specific operator
+selection criteria. The first column in these two tables contain the particular
+operator or operator selection applied. Second column contains the
+correlation coefficient $R^2$ with the final mutation score. Third column contains
+the mean mutant reduction ratio, and fourth contains the standard deviation of the
+mutant reduction ratio achieved. The fifth column contains the number of projects
+that returned valid values for that operator selection mechanism, and the final
+column gives the multiplier factor.
+The TSDL row is the result of applying only the higher order mutant
+equivalent to \textit{statement deletion}.
+All the \textit{N-sel} rows are the results of N-selective operator selection
 strategies~\cite{offutt1993anexperimental}. We used the order of operators

### 2014-03-14 src/analysis.Rnw
update

@@
 \begin{figure*}[t]
-<<x.per.sel.sample,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+<<x.per.sel.sample,fig.width=10, fig.height=3, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
 o.xp.sample <- subset(o.processed, grepl('^rr[.].*.m[.]red',ind))
@@
   stat_boxplot(geom ='errorbar')+
-  geom_boxplot() + facet_wrap(~type) + myopts
+  geom_boxplot() + facet_wrap(~type) + myopts + theme(legend.position="none")
 @
@@
 \begin{figure*}[t]
-<<x.per.sel.round,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+<<x.per.sel.round,fig.width=10, fig.height=3, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
 o.xp.round <- subset(o.processed, grepl('^r[.].*.m[.]red',ind))
@@
   stat_boxplot(geom ='errorbar')+
-  geom_boxplot() + facet_wrap(~type)+ myopts
+  geom_boxplot() + facet_wrap(~type)+ myopts+ theme(legend.position="none")
 @
@@
 
-\begin{figure*}[t]
-<<loc.per.sel.sample,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-o.loc.ext <- subset(o.processed, grepl('^l[.].*.m[.]red',ind))
-ggplot(subset(o.loc.ext, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
-  stat_boxplot(geom ='errorbar')+
-  geom_boxplot() + facet_wrap(~type) + myopts
-@
-\caption{The effect of loc (external) reduction. All are above 0.98 $R^2$.}
-\label{fig:locsel}
-\end{figure*}
-
-\begin{figure*}[t]
-<<wloc.per.sel.sample,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-o.loc.int <- subset(o.processed, grepl('^wl[.].*.m[.]red',ind))
-ggplot(subset(o.loc.int, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
-  stat_boxplot(geom ='errorbar')+
-  geom_boxplot() + facet_wrap(~type) + myopts
-@
-\caption{The effect of loc (internal) reduction. All are above 0.90 $R^2$.}
-\label{fig:wlocsel}
-\end{figure*}
-
-%The results of this selection criteria are provided in Table~\ref{tbl:locsel}.
-The effect of random selection within the program elements are visualized in Figure~\ref{fig:wlocsel}, and when it is made external to the program elements is visualized in Figure~\ref{fig:wlocsel}.
-
-% ----------------------------------------------------------------------
-%\subsubsection{One per element}
-%The aim of this criteria is is to take the previous idea to the extreme. We choose only a single mutant per program element.
-
-<<one>>=
-#3
-@
-\begin{table*}
-\begin{minipage}[h]{0.49\linewidth}
-<<results='asis'>>=
-print(xtable(f(o.stats.sel.one), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
-@
-\end{minipage}
-\hspace{0.5cm}
-\begin{minipage}[h]{0.49\linewidth}
-<<results='asis'>>=
-print(xtable(f(r.stats.sel.one), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
-@
-\end{minipage}
-\bigskip
-\caption {The one per element selection criteria results.}
-\label{tbl:onesel}
-\end{table*}
-
-\begin{figure*}[t]
-<<one.per.sel.sample,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-o.one <- subset(o.processed, grepl('^o[.].*.m[.]red',ind))
-ggplot(subset(o.one, values < 100 & (type=='line' | type=='method')), aes(power, values, fill=interaction(type,power), dodge=type)) +
-  stat_boxplot(geom ='errorbar')+
-  geom_boxplot() + facet_wrap(~type) + myopts
-@
-\caption{The effect of one element selection, All are above 0.98 $R^2$.}
-\label{fig:onesel}
-\end{figure*}
-
-% ----------------------------------------------------------------------
-
-%\subsection{Operator Selection}
-\begin{figure*}[t]
-<<op.all,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-#with(subset(stats.df,r.square > 0.9),plot(mutant.reduction, (1-r.square)*100, pch='*', col=as.factor(strategy)))
-# "kind" "operator" "s.power" "s.element" "strategy" "mutant.reduction" "sd.reduction"
-#  "sample" "r.square" "score.multiplier" "p.value"
-
-df <-  subset(stats.df, r.square>=0.9 & (sd.reduction * 2) < mutant.reduction) # & mutant.reduction < 20)
-df$sqr <- 1 - df$r.square
-df$mult <- 1 - df$score.multiplier
-df$type <- with(df, as.factor(
-      ifelse(grepl('line',operator), 'line',
-        ifelse(grepl('block',operator), 'block',
-        ifelse(grepl('method',operator), 'method',
-          ifelse(grepl('class',operator), 'class',
-            ifelse(grepl('project',operator), 'project',
-              'selection')))))))
-df$strat <- with(df,
-    ifelse(grepl('perunit', strategy), 'xpercent',
-      ifelse(grepl('op',strategy), 'opsel',
-        ifelse(grepl('one',strategy), 'oneperelm',
-          ifelse(grepl('elem',strategy), 'loc', 'other'
-            )))))
-ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(size=sqr, color=type))
-@
-\caption{The mean reduction of mutants vs its standard deviation.
-The sqr represents (1-$R^2$), i.e smaller is good.
-Only those observations with $R^2 > 0.9$ and $2\times $ standard deviation > mean reduction is shown here.
-}
-\label{fig:fullimgsize}
-\end{figure*}
-\begin{figure*}[t]
-<<op.all.2,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(shape=strat, color=type))
-@
-\caption{The mean reduction of mutants vs its standard deviation. Only those observations with $R^2 > 0.9$ and $2\times $ standard deviation > mean reduction is shown here. }
-\end{figure*}
-
-\begin{figure*}[t]
-<<op.all.4,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(shape=strat, color=mult))
-@
-\caption{The mean reduction of mutants vs its standard deviation.
-Only those observations with $R^2 > 0.9$ and $2\times $ standard deviation > mean reduction is shown here.
-The color represents the (1-multiplier) to the sampled mutation score to get final score }
-\end{figure*}
-
-\begin{figure*}[t]
-<<op.all.3,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-dfd <- subset(df, !(strategy %in% c('op','opsel')) )
-ggplot(dfd, aes(sd.reduction, mutant.reduction)) + geom_point(aes(shape=type, color=sqr)) + facet_wrap(~strategy) + theme(axis.text.x = element_text(angle = 90, hjust = 1))
-@
-\label{fig:fullimgshape}
-\end{figure*}
-<<opsel>>=
-#4
-@
-
 \begin{table*}
@@
 
+\begin{figure*}[t]
+<<loc.per.sel.sample,fig.width=10, fig.height=3, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+o.loc.ext <- subset(o.processed, grepl('^l[.].*.m[.]red',ind))
+ggplot(subset(o.loc.ext, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
+  stat_boxplot(geom ='errorbar')+
+  geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none")
+@
+\caption{The effect of loc (external) reduction. All are above 0.98 $R^2$.}
+\label{fig:locsel}
+\end{figure*}
+
+\begin{figure*}[t]
+<<wloc.per.sel.sample,fig.width=10, fig.height=2, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+o.loc.int <- subset(o.processed, grepl('^wl[.].*.m[.]red',ind))
+ggplot(subset(o.loc.int, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
+  stat_boxplot(geom ='errorbar')+
+  geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none")
+@
+\caption{The effect of loc (internal) reduction. All are above 0.90 $R^2$.}
+\label{fig:wlocsel}
+\end{figure*}
+
+%The results of this selection criteria are provided in Table~\ref{tbl:locsel}.
+The effect of random selection within the program elements are visualized in Figure~\ref{fig:wlocsel}, and when it is made external to the program elements is visualized in Figure~\ref{fig:wlocsel}.
+
+% ----------------------------------------------------------------------
+%\subsubsection{One per element}
+%The aim of this criteria is is to take the previous idea to the extreme. We choose only a single mutant per program element.
+
+<<one>>=
+#3
+@
+\begin{table*}
+\begin{minipage}[h]{0.49\linewidth}
+<<results='asis'>>=
+print(xtable(f(o.stats.sel.one), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
+@
+\end{minipage}
+\hspace{0.5cm}
+\begin{minipage}[h]{0.49\linewidth}
+<<results='asis'>>=
+print(xtable(f(r.stats.sel.one), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
+@
+\end{minipage}
+\bigskip
+\caption {The one per element selection criteria results.}
+\label{tbl:onesel}
+\end{table*}
+
+\begin{figure*}[t]
+<<one.per.sel.sample,fig.width=10, fig.height=2, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+o.one <- subset(o.processed, grepl('^o[.].*.m[.]red',ind))
+ggplot(subset(o.one, values < 100 & (type=='line' | type=='method')), aes(power, values, fill=interaction(type,power), dodge=type)) +
+  stat_boxplot(geom ='errorbar')+
+  geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none")
+@
+\caption{The effect of one element selection, All are above 0.98 $R^2$.}
+\label{fig:onesel}
+\end{figure*}
+
+% ----------------------------------------------------------------------
+
+%\subsection{Operator Selection}
+\begin{figure*}[t]
+<<op.all,fig.width=10, fig.height=3, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+#with(subset(stats.df,r.square > 0.9),plot(mutant.reduction, (1-r.square)*100, pch='*', col=as.factor(strategy)))
+# "kind" "operator" "s.power" "s.element" "strategy" "mutant.reduction" "sd.reduction"
+#  "sample" "r.square" "score.multiplier" "p.value"
+
+df <-  subset(stats.df, r.square>=0.9 & (sd.reduction * 2) < mutant.reduction) # & mutant.reduction < 20)
+df$sqr <- 1 - df$r.square
+df$mult <- 1 - df$score.multiplier
+df$type <- with(df, as.factor(
+      ifelse(grepl('line',operator), 'line',
+        ifelse(grepl('block',operator), 'block',
+        ifelse(grepl('method',operator), 'method',
+          ifelse(grepl('class',operator), 'class',
+            ifelse(grepl('project',operator), 'project',
+              'selection')))))))
+df$strat <- with(df,
+    ifelse(grepl('perunit', strategy), 'xpercent',
+      ifelse(grepl('op',strategy), 'opsel',
+        ifelse(grepl('one',strategy), 'oneperelm',
+          ifelse(grepl('elem',strategy), 'loc', 'other'
+            )))))
+ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(size=sqr, color=type))
+@
+\caption{The mean reduction of mutants vs its standard deviation.
+The sqr represents (1-$R^2$), i.e smaller is good.
+Only those observations with $R^2 > 0.9$ and $2\times $ standard deviation > mean reduction is shown here.
+}
+\label{fig:fullimgsize}
+\end{figure*}
+\begin{figure*}[t]
+<<op.all.2,fig.width=10, fig.height=3, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(shape=strat, color=type))
+@
+\caption{The mean reduction of mutants vs its standard deviation. Only those observations with $R^2 > 0.9$ and $2\times $ standard deviation > mean reduction is shown here. }
+\end{figure*}
+
+% \begin{figure*}[t]
+% <<op.all.4,fig.width=10, fig.height=3, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+% ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(shape=strat, color=mult))
+% @
+% \caption{The mean reduction of mutants vs its standard deviation.
+Only those observations with $R^2 > 0.9$ and $2\times $ standard deviation > mean reduction is shown here.
+The color represents the (1-multiplier) to the sampled mutation score to get final score }
+% \end{figure*}
+%
+
+% \begin{figure*}[t]
+% <<op.all.3,fig.width=10, fig.height=3, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+% dfd <- subset(df, !(strategy %in% c('op','opsel')) )
+% ggplot(dfd, aes(sd.reduction, mutant.reduction)) + geom_point(aes(shape=type, color=sqr)) + facet_wrap(~strategy) + theme(axis.text.x = element_text(angle = 90, hjust = 1))
+% @
+% \label{fig:fullimgshape}
+% \end{figure*}
+<<opsel>>=
+#4
+@
+
 %For operator selection, we approximated the operators as far as possible from the research works into the operators exposed by PIT. The results of this are provided in Table~\ref{tbl:opsel}.

### 2014-03-14 src/related.Rnw
update

@@
 Recently, Zhang et al.~\cite{zhang2013ase} confirmed that sampling as few as 5\% mutants
-was sufficient for a very correlation (99\%) with the full mutation score, while sampling even
+was sufficient for a very high correlation (99\%) with the full mutation score, while sampling even
 fewer mutants has good potential for retaining high accuracy. They investigate 8 sampling

### 2014-03-14 src/discussion.Rnw
udpate
update

--- 2014-03-11 src/discussion.Rnw
@@
 
-\begin{figure}[t]
-\includegraphics[totalheight=5cm]{fig/opstrat1.eps}
-\caption{Example Mutants}
-\label{fig:egmutants}
-\end{figure}
+%\begin{figure}[t]
+%\includegraphics[totalheight=4.5cm]{fig/opstrat1.pdf}
+%\caption{Mutant distribution in a sample project along operators and program elements}
+%\label{fig:egmutants}
+%\end{figure}
 
@@
 
-We see three clear patterns in our results. The first is that sampling strategy
+We see a few patterns in our results. The first is that sampling strategy
 can predict the final score with very minimal loss in accuracy up to a fraction
 of $\frac{1}{64}$ of the total number of mutants (Our experiments suggest up
-to $70$ times reduction, with a low standard deviation of $6.72$). We did nto
+to $70$ times reduction, with a low standard deviation of $6.72$). We did not
 cut off with the 99\% rule as mentioned by Zhang et al.~\cite{zhang2013ase}
@@
 The second pattern is that fractional sampling based on projects appears to be
-better than that based on classes, which inturn is better than methods and
-lines, with regard to the stability of the result (i.e low sd), and correlation.
+better than that based on classes, which in turn is better than methods and
+lines, with regard to the stability of the result (i.e low sd).
 This seems not very visible at lower levels (where the reduction fraction is less
@@
 There seem to exist a hierarchy of sampling, where by as you go more fine grained,
-the stability and correlation decreases. This is infact opposite to what Zhang
-et al.~\cite{zhang2013ase} observed, where they found that $S_{meth}$ ourperforms
-$S_{base}$.
+the stability decreases.
+We did not see the pattern found by Zhang et al.~\cite{zhang2013ase} where by
+the method based sampling had the highest accuracy. In fact, in our measurements,
+the opposite may be true, with project based sampling getting the highest correlation
+with the final score a majority of the time.
 
 The third pattern is that the simplest sampling scheme --- simple random sampling ---
-performs best compared to sampling schems that tried to provide higher weightage
-to specific elements based on specific criterias. More importantly, operator selection
+performs best compared to sampling schemes that tried to provide higher weight
+to specific elements based on specific criteria. More importantly, operator selection
 seems to be generally worse off in predicting the final score than any of the random
 selection schemes.
+
+% There may in fact be a simple reason for this observation. Consider the Figure~\ref{fig:egmutants}.
+% It is a representation of the distribution of mutants along two orthogonal axes --- the
+% mutation operators, and program elements such as classes. For the purposes of this
+% explanation, assume that each classes contain equal number of lines, and each mutant
+% produced per line by each of the mutation operators are marked by a small solid circle.
+% The two solid vertical lines in blue and red represents two classes, one with a relatively
+% small number of mutants and other with large number of mutants. Consider that we are sampling
+% by class, and we are choosing all mutants for simplicity. Let $c$ be the number of classes.
+% Here, a mutant in red class contributes to $1/n_{red}$ to the mean of the score of the
+% red class, and the red class contributes $1/c$ to the total mean.  So the contribution of a
+% mutant in red class to the complete is $1/(c * n_{red})$. Similarly for blue class.
+% However, if the sampling is done on a complete project basis, then the contribution of any
+% mutant is $\frac{1}{\sum_{i=1}^{c} n_{i}}$, which depending on the size of the class might
+% be different from what it would contribute if sampling is used. To put it another way,
+% for any kind of sampling used based on sub elements, the units in the sample gets equal
+% weightage in contribution irrespective of the size of elements themselves, while if the sampling
+% is done on a project basis, the contribution of sub elements depends on the number of mutants
+% each elements produced.
+% 
+% What this is saying in effect is that irrespective of the sophestication of sampling used,
+% the simplest sampling technique --- that of project based sampling --- is the best form of
+% sampling, for a representative set.
+% 
+% This also applies immediately to operator selection as it is another kind of sampling on
+% a smaller set. Hence it is no surprise that for larger samples, random sampling is able
+% to trump operator selection on predicting the final result.
+%

### 2014-03-14 src/analysis.Rnw
update

@@
 
-\begin{figure*}[t]
-<<x.per.sel.sample,fig.width=10, fig.height=3, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-o.xp.sample <- subset(o.processed, grepl('^rr[.].*.m[.]red',ind))
-ggplot(subset(o.xp.sample, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
-  stat_boxplot(geom ='errorbar')+
-  geom_boxplot() + facet_wrap(~type) + myopts + theme(legend.position="none")
-@
-\caption{The effect of sample(x) reduction. All are above 0.90 $R^2$.}
-\label{fig:xsamplesel}
-\end{figure*}
-
-\begin{figure*}[t]
-<<x.per.sel.round,fig.width=10, fig.height=3, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-o.xp.round <- subset(o.processed, grepl('^r[.].*.m[.]red',ind))
-ggplot(subset(o.xp.round, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
-  stat_boxplot(geom ='errorbar')+
-  geom_boxplot() + facet_wrap(~type)+ myopts+ theme(legend.position="none")
-@
-\caption{The effect of round(x) reduction, Except for line sampling of power $5$ and $6$ all others are above 0.90 $R^2$.}
-\label{fig:xroundsel}
-\end{figure*}
+% \begin{figure*}[t]
+% <<x.per.sel.sample,fig.width=10, fig.height=3, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+% o.xp.sample <- subset(o.processed, grepl('^rr[.].*.m[.]red',ind))
+% ggplot(subset(o.xp.sample, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
+%   stat_boxplot(geom ='errorbar')+
+%   geom_boxplot() + facet_wrap(~type) + myopts + theme(legend.position="none")
+% @
+% \caption{The effect of sample(x) reduction. All are above 0.90 $R^2$.}
+% \label{fig:xsamplesel}
+% \end{figure*}
+% 
+% \begin{figure*}[t]
+% <<x.per.sel.round,fig.width=10, fig.height=3, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+% o.xp.round <- subset(o.processed, grepl('^r[.].*.m[.]red',ind))
+% ggplot(subset(o.xp.round, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
+%   stat_boxplot(geom ='errorbar')+
+%   geom_boxplot() + facet_wrap(~type)+ myopts+ theme(legend.position="none")
+% @
+% \caption{The effect of round(x) reduction, Except for line sampling of power $5$ and $6$ all others are above 0.90 $R^2$.}
+% \label{fig:xroundsel}
+% \end{figure*}
 %Our experiments found that while $round(x)$ and $sample(x)$ produced relatively reasonable reduction of mutants, the $ceil(x)$ criteria failed to produce a reasonable reduction of mutants except for higher power where the reduction was some what close to that produced by $round(x)$ and $sample(x)$ (which was expected).
@@
 
-\begin{figure*}[t]
-<<loc.per.sel.sample,fig.width=10, fig.height=3, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-o.loc.ext <- subset(o.processed, grepl('^l[.].*.m[.]red',ind))
-ggplot(subset(o.loc.ext, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
-  stat_boxplot(geom ='errorbar')+
-  geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none")
-@
-\caption{The effect of loc (external) reduction. All are above 0.98 $R^2$.}
-\label{fig:locsel}
-\end{figure*}
-
-\begin{figure*}[t]
-<<wloc.per.sel.sample,fig.width=10, fig.height=2, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-o.loc.int <- subset(o.processed, grepl('^wl[.].*.m[.]red',ind))
-ggplot(subset(o.loc.int, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
-  stat_boxplot(geom ='errorbar')+
-  geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none")
-@
-\caption{The effect of loc (internal) reduction. All are above 0.90 $R^2$.}
-\label{fig:wlocsel}
-\end{figure*}
-
-%The results of this selection criteria are provided in Table~\ref{tbl:locsel}.
-The effect of random selection within the program elements are visualized in Figure~\ref{fig:wlocsel}, and when it is made external to the program elements is visualized in Figure~\ref{fig:wlocsel}.
-
-% ----------------------------------------------------------------------
-%\subsubsection{One per element}
-%The aim of this criteria is is to take the previous idea to the extreme. We choose only a single mutant per program element.
-
-<<one>>=
-#3
-@
 \begin{table*}
@@
 \begin{figure*}[t]
-<<one.per.sel.sample,fig.width=10, fig.height=2, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+<<x.per.sel.sample,fig.width=10, fig.height=3, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+o.xp.sample <- subset(o.processed, grepl('^rr[.].*.m[.]red',ind))
+ggplot(subset(o.xp.sample, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
+  stat_boxplot(geom ='errorbar')+
+  geom_boxplot() + facet_wrap(~type) + myopts + theme(legend.position="none") + opts(title="sample(x)")
+# @
+# \caption{The effect of sample(x) reduction. All are above 0.90 $R^2$.}
+# \label{fig:xsamplesel}
+# \end{figure*}
+# 
+# \begin{figure*}[t]
+# <<x.per.sel.round,fig.width=10, fig.height=3, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+o.xp.round <- subset(o.processed, grepl('^r[.].*.m[.]red',ind))
+ggplot(subset(o.xp.round, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
+  stat_boxplot(geom ='errorbar')+
+  geom_boxplot() + facet_wrap(~type)+ myopts+ theme(legend.position="none")+ opts(title="sample(x)")
+
+o.loc.ext <- subset(o.processed, grepl('^l[.].*.m[.]red',ind))
+ggplot(subset(o.loc.ext, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
+  stat_boxplot(geom ='errorbar')+
+  geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none") + opts(title="loc(external)")
+
+o.loc.int <- subset(o.processed, grepl('^wl[.].*.m[.]red',ind))
+ggplot(subset(o.loc.int, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
+  stat_boxplot(geom ='errorbar')+
+  geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none") + opts(title="loc(internal)")
+
 o.one <- subset(o.processed, grepl('^o[.].*.m[.]red',ind))
@@
   stat_boxplot(geom ='errorbar')+
-  geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none")
+  geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none") + opts(title="One per element")
 @
-\caption{The effect of one element selection, All are above 0.98 $R^2$.}
-\label{fig:onesel}
+\caption{The effect of sampling reductions, Except for line sampling of power $5$ and $6$ all others are above 0.90 $R^2$.}
+\label{fig:xroundsel}
 \end{figure*}
 
+% \begin{figure*}[t]
+% <<loc.per.sel.sample,fig.width=10, fig.height=3, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+% o.loc.ext <- subset(o.processed, grepl('^l[.].*.m[.]red',ind))
+% ggplot(subset(o.loc.ext, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
+%   stat_boxplot(geom ='errorbar')+
+%   geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none")
+% @
+% \caption{The effect of loc (external) reduction. All are above 0.98 $R^2$.}
+% \label{fig:locsel}
+% \end{figure*}
+% 
+%\begin{figure*}[t]
+%<<wloc.per.sel.sample,fig.width=10, fig.height=2, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+%o.loc.int <- subset(o.processed, grepl('^wl[.].*.m[.]red',ind))
+%ggplot(subset(o.loc.int, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
+%  stat_boxplot(geom ='errorbar')+
+%  geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none")
+%@
+%\caption{The effect of loc (internal) reduction. All are above 0.90 $R^2$.}
+%\label{fig:wlocsel}
+%\end{figure*}
+%
+%
+%The results of this selection criteria are provided in Table~\ref{tbl:locsel}.
+The effect of random selection within the program elements are visualized in Figure~\ref{fig:wlocsel}, and when it is made external to the program elements is visualized in Figure~\ref{fig:wlocsel}.
+
+% ----------------------------------------------------------------------
+%\subsubsection{One per element}
+%The aim of this criteria is is to take the previous idea to the extreme. We choose only a single mutant per program element.
+
+<<one>>=
+#3
+@
+%\begin{figure*}[t]
+%<<one.per.sel.sample,fig.width=10, fig.height=2, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+%o.one <- subset(o.processed, grepl('^o[.].*.m[.]red',ind))
+%ggplot(subset(o.one, values < 100 & (type=='line' | type=='method')), aes(power, values, fill=interaction(type,power), dodge=type)) +
+%  stat_boxplot(geom ='errorbar')+
+%  geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none")
+%@
+%\caption{The effect of one element selection, All are above 0.98 $R^2$.}
+%\label{fig:onesel}
+%\end{figure*}
+%
 % ----------------------------------------------------------------------
@@
 ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(size=sqr, color=type))
+ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(shape=strat, color=type))
 @
@@
 \end{figure*}
-\begin{figure*}[t]
-<<op.all.2,fig.width=10, fig.height=3, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(shape=strat, color=type))
-@
-\caption{The mean reduction of mutants vs its standard deviation. Only those observations with $R^2 > 0.9$ and $2\times $ standard deviation > mean reduction is shown here. }
-\end{figure*}
-
+% \begin{figure*}[t]
+% <<op.all.2,fig.width=10, fig.height=3, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+% @
+% \caption{The mean reduction of mutants vs its standard deviation. Only those observations with $R^2 > 0.9$ and $2\times $ standard deviation > mean reduction is shown here. }
+% \end{figure*}
+% 
 % \begin{figure*}[t]

### 2014-03-14 src/analysis.Rnw
update

@@
 \begin{figure*}[t]
-<<op.all,fig.width=10, fig.height=3, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+<<op.all,fig.width=10, fig.height=7, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
 #with(subset(stats.df,r.square > 0.9),plot(mutant.reduction, (1-r.square)*100, pch='*', col=as.factor(strategy)))

### 2014-03-14 src/analysis.Rnw
update

@@
 <<results='asis'>>=
+print(xtable(f(o.stats.sel.one), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
+@
+\end{minipage}
+\hspace{0.5cm}
+\begin{minipage}[h]{0.49\linewidth}
+<<results='asis'>>=
+print(xtable(f(r.stats.sel.one), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
+@
+\end{minipage}
+\bigskip
+\caption {The one per element selection criteria results.}
+\label{tbl:onesel}
+\end{table*}
+
+\begin{table*}
+\begin{minipage}[h]{0.49\linewidth}
+<<results='asis'>>=
 print(xtable(o.stats.sel.op, caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
@@
 \label{tbl:opsel}
-\end{table*}
-
-\begin{table*}
-\begin{minipage}[h]{0.49\linewidth}
-<<results='asis'>>=
-print(xtable(f(o.stats.sel.one), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
-@
-\end{minipage}
-\hspace{0.5cm}
-\begin{minipage}[h]{0.49\linewidth}
-<<results='asis'>>=
-print(xtable(f(r.stats.sel.one), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
-@
-\end{minipage}
-\bigskip
-\caption {The one per element selection criteria results.}
-\label{tbl:onesel}
 \end{table*}
@@
 
-df <-  subset(stats.df, r.square>=0.9 & (sd.reduction * 2) < mutant.reduction) # & mutant.reduction < 20)
+df <-  subset(stats.df, r.square>=0.9 & (sd.reduction * 2) < mutant.reduction)
 df$sqr <- 1 - df$r.square
@@
               'selection')))))))
-df$strat <- with(df,
-    ifelse(grepl('perunit', strategy), 'xpercent',
-      ifelse(grepl('op',strategy), 'opsel',
-        ifelse(grepl('one',strategy), 'oneperelm',
-          ifelse(grepl('elem',strategy), 'loc', 'other'
-            )))))
+df$sampling <- with(df,
+      ifelse(grepl('op',strategy), 'operator(x)',
+          ifelse(grepl('onelement',strategy), 'one(x)',
+            ifelse(grepl('locelement',strategy), 'lines(x)',
+              ifelse(grepl('withinelement',strategy), 'one(x)',
+                ifelse(grepl('xceilperunit',strategy), 'ceil(x)',
+                  ifelse(grepl('xpercentperunit',strategy), 'round(x)',
+                    ifelse(grepl('xprobperunit',strategy), 'sample(x)',
+strategy))))))))
 ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(size=sqr, color=type))
-ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(shape=strat, color=type))
+ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(shape=sampling, color=type))
 @
@@
 \end{figure*}
+
+\begin{figure*}[t]
+<<op.all.2,fig.width=10, fig.height=7, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+#with(subset(stats.df,r.square > 0.9),plot(mutant.reduction, (1-r.square)*100, pch='*', col=as.factor(strategy)))
+# "kind" "operator" "s.power" "s.element" "strategy" "mutant.reduction" "sd.reduction"
+#  "sample" "r.square" "score.multiplier" "p.value"
+
+df <-  subset(df, r.square>=0.9 & (sd.reduction * 2) < mutant.reduction & mutant.reduction <= 20)
+ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(size=sqr, color=type))
+ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(shape=sampling, color=type))
+@
+\caption{The mean reduction of mutants vs its standard deviation. The sqr represents (1-$R^2$), i.e smaller is good. Only mean reduction <= 20 (5\%)}
+\label{fig:fullimgsize2}
+\end{figure*}
+
+\begin{figure*}[t]
+<<op.all.3,fig.width=10, fig.height=7, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+#with(subset(stats.df,r.square > 0.9),plot(mutant.reduction, (1-r.square)*100, pch='*', col=as.factor(strategy)))
+# "kind" "operator" "s.power" "s.element" "strategy" "mutant.reduction" "sd.reduction"
+#  "sample" "r.square" "score.multiplier" "p.value"
+
+df <-  subset(df, r.square>=0.9 & (sd.reduction * 2) < mutant.reduction & mutant.reduction <= 10)
+ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(size=sqr, color=type))
+ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(shape=sampling, color=type))
+@
+\caption{The mean reduction of mutants vs its standard deviation. The sqr represents (1-$R^2$), i.e smaller is good. Only mean reduction <= 10 (10\%)}
+\label{fig:fullimgsize3}
+\end{figure*}
+
+\begin{figure*}[t]
+<<op.all.4,fig.width=10, fig.height=7, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+#with(subset(stats.df,r.square > 0.9),plot(mutant.reduction, (1-r.square)*100, pch='*', col=as.factor(strategy)))
+# "kind" "operator" "s.power" "s.element" "strategy" "mutant.reduction" "sd.reduction"
+#  "sample" "r.square" "score.multiplier" "p.value"
+
+df <-  subset(df, r.square>=0.9 & (sd.reduction * 2) < mutant.reduction & mutant.reduction <= 5)
+ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(size=sqr, color=type))
+ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(shape=sampling, color=type))
+@
+\caption{The mean reduction of mutants vs its standard deviation. The sqr represents (1-$R^2$), i.e smaller is good. Only mean reduction <= 5 (20\%)}
+\label{fig:fullimgsize4}
+\end{figure*}
+
 % \begin{figure*}[t]

### 2014-03-14 src/methodology.Rnw
update

@@
 o.all <- cbind(projects = rownames(o.dist.all), stack(o.dist.all))
-o.all$ind <- clean(o.all$ind)
+#o.all$ind <- clean(o.all$ind)
 bcol <- '#2171B5'
@@
 o.det <- cbind(projects = rownames(o.dist.det), stack(o.dist.det))
-o.det$ind <- clean(o.det$ind)
+#o.det$ind <- clean(o.det$ind)
 with(o.all,boxplot(values~ind,horizontal=T,border=c(bcol), pch='.', axes=F, ylim=c(0,0.6), col=icol ))
@@
 r.all <- cbind(projects = rownames(r.dist.all), stack(r.dist.all))
-r.all$ind <- clean(r.all$ind)
+#r.all$ind <- clean(r.all$ind)
 r.det <- cbind(projects = rownames(r.dist.det), stack(r.dist.det))
-r.det$ind <- clean(r.det$ind)
+#r.det$ind <- clean(r.det$ind)
 with(r.all,boxplot(values~ind,horizontal=T,border=c(bcol), pch='.', axes=F,ylim=c(0,0.6),  col=icol))

### 2014-03-14 src/paper.Rnw
.
update
udate

@@
+% MAX LIMIT: 10 pages for all figurs and text + any number of references.
 \newcommand*\per{\scalebox{.5}{\%}}
@@
 
-clean <- function(x)sub('CONSTRUCTOR','CONSTR',sub('RETURN','R',sub('INCREMENTS','INC',sub('VOID','V',sub('CONDITIONAL','COND',sub('NON','N',sub('VARIABLE','VAR',sub('MEMBER','MEM',sub('DELETE_','D_',sub('REMOVE_','R_',sub('NEGATE_','N_',sub('_CALLS','',sub('EXPERIMENTAL_','E_',x)))))))))))))
 #options(warn=-1)
@@
 
-o.stats.sel.op <- o.stats.sel.op[,c(0,6,1,2,3,4,5)]
-r.stats.sel.op <- r.stats.sel.op[,c(0,6,1,2,3,4,5)]
-
 stats.opsel <- subset(stats.rest, grepl('^opsel', operator))
@@
 
-o.stats.sel.opsel <- o.stats.sel.opsel[,c(0,6,1,2,3,4,5)]
-r.stats.sel.opsel <- r.stats.sel.opsel[,c(0,6,1,2,3,4,5)]
 # 4 done
@@
 @
+\FloatBarrier

### 2014-03-14 src/analysis.Rnw
update

@@
 % o.xp.sample <- subset(o.processed, grepl('^rr[.].*.m[.]red',ind))
-% ggplot(subset(o.xp.sample, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
+% ggplot(subset(o.xp.sample, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
 %   stat_boxplot(geom ='errorbar')+
@@
 % o.xp.round <- subset(o.processed, grepl('^r[.].*.m[.]red',ind))
-% ggplot(subset(o.xp.round, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
+% ggplot(subset(o.xp.round, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
 %   stat_boxplot(geom ='errorbar')+
@@
 o.xp.sample <- subset(o.processed, grepl('^rr[.].*.m[.]red',ind))
-ggplot(subset(o.xp.sample, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
+ggplot(subset(o.xp.sample, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
   stat_boxplot(geom ='errorbar')+
@@
 o.xp.round <- subset(o.processed, grepl('^r[.].*.m[.]red',ind))
-ggplot(subset(o.xp.round, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
+ggplot(subset(o.xp.round, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
   stat_boxplot(geom ='errorbar')+
@@
 o.loc.ext <- subset(o.processed, grepl('^l[.].*.m[.]red',ind))
-ggplot(subset(o.loc.ext, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
+ggplot(subset(o.loc.ext, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
   stat_boxplot(geom ='errorbar')+
@@
 o.loc.int <- subset(o.processed, grepl('^wl[.].*.m[.]red',ind))
-ggplot(subset(o.loc.int, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
+ggplot(subset(o.loc.int, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
   stat_boxplot(geom ='errorbar')+
@@
 o.one <- subset(o.processed, grepl('^o[.].*.m[.]red',ind))
-ggplot(subset(o.one, values < 100 & (type=='line' | type=='method')), aes(power, values, fill=interaction(type,power), dodge=type)) +
+ggplot(subset(o.one, reduction < 100 & (type=='line' | type=='method')), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
   stat_boxplot(geom ='errorbar')+
@@
 
+\begin{figure*}[t]
+<<op.sample,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+o.xp.opsel <- o.op.processed
+o.xp.opsel <- colnames(o.xp.opsel)[]
+colnames(o.xp.opsel)[colnames(o.xp.opsel)=="power"] <- "num.operators"
+
+ggplot(subset(o.xp.opsel, reduction < 1000), aes(num.operators, reduction, fill=interaction(type,num.operators), dodge=type)) +
+  stat_boxplot(geom ='errorbar')+
+  geom_boxplot() + facet_wrap(~type) + myopts + theme(legend.position="none") + opts(title="opsel(x)")
+@
+\caption{Operator selection}
+\label{fig:xroundsel}
+\end{figure*}
+
 % \begin{figure*}[t]
@@
 % o.loc.ext <- subset(o.processed, grepl('^l[.].*.m[.]red',ind))
-% ggplot(subset(o.loc.ext, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
+% ggplot(subset(o.loc.ext, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
 %   stat_boxplot(geom ='errorbar')+
@@
 %o.loc.int <- subset(o.processed, grepl('^wl[.].*.m[.]red',ind))
-%ggplot(subset(o.loc.int, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
+%ggplot(subset(o.loc.int, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
 %  stat_boxplot(geom ='errorbar')+
@@
 %o.one <- subset(o.processed, grepl('^o[.].*.m[.]red',ind))
-%ggplot(subset(o.one, values < 100 & (type=='line' | type=='method')), aes(power, values, fill=interaction(type,power), dodge=type)) +
+%ggplot(subset(o.one, reduction < 100 & (type=='line' | type=='method')), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
 %  stat_boxplot(geom ='errorbar')+

### 2014-03-14 src/methodology.Rnw
update

--- 2014-03-13 src/methodology.Rnw
@@
 o.det <- cbind(projects = rownames(o.dist.det), stack(o.dist.det))
-o.det$ind <- clean(o.det$ind)
-with(o.all,boxplot(values~ind,horizontal=T,border=c(bcol), pch='.', axes=F, ylim=c(0,0.6), col=icol ))
-with(o.det,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Original', cex.axis=0.8, ylim=c(0,0.6),add=T))
+#o.det$ind <- clean(o.det$ind)
+with(o.all,boxplot(reduction~ind,horizontal=T,border=c(bcol), pch='.', axes=F, ylim=c(0,0.6), col=icol ))
+with(o.det,boxplot(reduction~ind,horizontal=T,border=c('black'), pch='.',main='Original', cex.axis=0.8, ylim=c(0,0.6),add=T))
 
 r.all <- cbind(projects = rownames(r.dist.all), stack(r.dist.all))
-r.all$ind <- clean(r.all$ind)
+#r.all$ind <- clean(r.all$ind)
 r.det <- cbind(projects = rownames(r.dist.det), stack(r.dist.det))
-r.det$ind <- clean(r.det$ind)
-with(r.all,boxplot(values~ind,horizontal=T,border=c(bcol), pch='.', axes=F,ylim=c(0,0.6),  col=icol))
-with(r.det,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Randoop', cex.axis=0.8,ylim=c(0,0.6),add=T))
+#r.det$ind <- clean(r.det$ind)
+with(r.all,boxplot(reduction~ind,horizontal=T,border=c(bcol), pch='.', axes=F,ylim=c(0,0.6),  col=icol))
+with(r.det,boxplot(reduction~ind,horizontal=T,border=c('black'), pch='.',main='Randoop', cex.axis=0.8,ylim=c(0,0.6),add=T))
 @

### 2014-03-14 src/results.Rnw
update

@@
 
-Our results for x\% sampling over program elements are given
-in Table~\ref{tbl:xselsample}. The result of its variation, using
-\textit{round(sample)} is given in Table~\ref{tbl:xselround}. The result
-of using \textit{ceil(sample)} is given in Table~\ref{tbl:xselceil}.
-The first column in each table provides the scope of sampling i.e if it was
+Our results for random sampling over program elements using $sample(x)$
+are given in Table~\ref{tbl:xselsample}. The result of its variation, using
+$round(x)$ is given in Table~\ref{tbl:xselround}, and that using
+$ceil(x)$ is given in Table~\ref{tbl:xselceil}.
+The first column in each table provides the scope of sampling i.e. if it was
 done per class, per method, per line etc. The second column provides the
@@
 the criteria of one mutant per program element.
+
+The same (only for original test suite) is visualized in Figure~\ref{fig:xroundsel}.
 

### 2014-03-14 src/methodology.Rnw
fix

--- 2014-03-13 src/methodology.Rnw
@@
 <<op,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+clean <- function(x) {
+  sub('CONSTRUCTOR_CALLS','CC',
+      sub('INCREMENTS','I',
+        sub('RETURN_VALS','RV',
+          sub('VOID_METHOD_CALLS','VMC',
+            sub('NON_VOID_METHOD_CALLS','NMC',
+              sub('RMSWITCH','RS',
+                sub('REMOVE_CONDITIONALS','RC',
+                  sub('REMOVE_INCREMENTS','RI',
+                    sub('NEGATE_CONDITIONALS','NC',
+                      sub('MATH','M',
+                        sub('INVERT_NEGS','IN',
+                          sub('INLINE_CONSTS','IC',
+                            sub('EXPERIMENTAL_SWITCH','ES',
+                              sub('EXPERIMENTAL_MEMBER_VARIABLE','EMV',
+                                sub('DELETE_CONDITIONALS','DC',
+                                  sub('CONDITIONALS_BOUNDARY','CB',x))))))))))))))))
+}
 par(las=1,mfrow = c(1, 2),mar=c(2,8,1,1))

### 2014-03-14 src/analysis.Rnw
udpate

@@
 o.xp.opsel <- o.op.processed
-o.xp.opsel <- colnames(o.xp.opsel)[]
 colnames(o.xp.opsel)[colnames(o.xp.opsel)=="power"] <- "num.operators"

### 2014-03-14 src/paper.Rnw
update

@@
 is.installed <- function(mypkg) is.element(mypkg, installed.packages()[,1])
-options(CRAN = "http://cran.stat.ucla.edu")
-if (!is.installed("xtable")) install.packages("xtable")
-if (!is.installed("ggplot2")) install.packages("ggplot2")
-if (!is.installed("reshape2")) install.packages("reshape2")
+#options(CRAN = "http://cran.stat.ucla.edu")
+#if (!is.installed("xtable")) install.packages("xtable")
+#if (!is.installed("ggplot2")) install.packages("ggplot2")
+#if (!is.installed("reshape2")) install.packages("reshape2")
 

### 2014-03-14 src/analysis.Rnw
udpate

@@
 o.xp.opsel <- o.op.processed
-colnames(o.xp.opsel)[colnames(o.xp.opsel)=="power"] <- "num.operators"
+o.xp.opsel$operators <- 16 - o.xp.opsel$operators
+colnames(o.xp.opsel)[colnames(o.xp.opsel)=="operators"] <- "rm.operators"
 
-ggplot(subset(o.xp.opsel, reduction < 1000), aes(num.operators, reduction, fill=interaction(type,num.operators), dodge=type)) +
-  stat_boxplot(geom ='errorbar')+
-  geom_boxplot() + facet_wrap(~type) + myopts + theme(legend.position="none") + opts(title="opsel(x)")
+df <- subset(o.xp.opsel, rm.operators <= 20 & reduction != Inf & type != 'operator' & (type != 'n-selection' | rm.operators < 9))
+#ggplot(df, aes(rm.operators, reduction, fill=interaction(type,rm.operators), dodge=type)) +
+#  stat_boxplot(geom ='errorbar')+
+#  geom_boxplot() + facet_wrap(~type) + myopts +
+#  #theme(legend.position="none") +
+#  opts(title="opsel(x)")
+qplot(rm.operators, reduction, fill=interaction(type,rm.operators), data=df, geom="boxplot", position="dodge") + theme_bw()
 @
-\caption{Operator selection}
+\caption{Operator selection comparison between n-selection and other selection methods in mutation reduction.  We show only up to 8-selection}
 \label{fig:xroundsel}

### 2014-03-14 etc/abstract.tex
update
Alex edits

--- 2014-03-09 etc/abstract.tex
@@
 % 1.Statetheproblem
-Mutation analysis is a metric for measuring the quality of test suites.
-However, it is computationally intensive compared to other measures which it hard to use in practice.
-Choosing a smaller subset of mutations to run is a simple approach that can alleviate this problem.
-There exist multiple ways to reduce the set of mutations to run.
-Operator selection has recently been in the focus.
-However recently researchers have found that sampling can achive accuracy and mutant reduction similar to operator selection.
+Mutation analysis is a well-known method for measuring the quality of
+test suites. However, it is computationally intensive compared to
+other measures, which makes it hard to use in practice. Choosing a
+smaller subset of mutations to run is a simple approach that can
+alleviate this problem.  Mutation operator selection has been heavily
+researched. Recently, researchers have found that sampling mutants can
+achieve accuracy and mutant reduction similar to operator selection.
 
 %2.Saywhyit’saninterestingproblem
-However, which sampling technique is best, is an open problem, especially for real-world programs and test-suites.
+However, the statistical support for these conclusions has been limited, due to the small number of subject programs investigated.  The best sampling technique is also an open problem.
+% that can be drawn from the previous
+%research has been limited due to the small number of subject programs. Further,
+%which sampling technique is best is still an open problem that needs to be
+%tackled on a much larger range of test subjects.
 
 %3.Saywhatyoursolutionachieves
-Our research compares a number of sampling criteria, and operator selection criteria based on their ability to approximate the full mutation score, and also the consistency of results.
+
+Our research compares a large number of sampling and operator
+selection criteria based on their ability to predict the full mutation
+score as well as the consistency of mutation reduction ratios
+achieved. Our results provide a ranking that can be used to choose an
+appropriate mutation reduction technique by the reduction and level of fidelity to full mutation results required.
+
+%according to the mutation reduction ratio desired, and
+%how much reduction in accuracy is acceptable.
 
 %4.Saywhatfollowsfromyoursolution
-Our experiments rank sampling criterias that can be used by testers according how much mutant reduction is achieved, their ability to predict the final mutation score, the relative effect of unit increase in sampled mutation score on the final score, and also the time required for the run.
-We also find that sampling techniques work better than operator selection methods including statement deletion in both mutation reduction and accuracy of approximation to the full mutation score.
+
+We find that all sampling approaches perform better than operator
+selection methods, when considering ability to predict the full
+mutation score as well as the consistency of mutation reduction ratios
+achieved.
+
+%and also the consistency of mutation reduction ratios achieved.  Specifically,
+%we find that random selection of a mutant performs better than statement
+%deletion operator selection criteria.
 

### 2014-03-14 src/introduction.Rnw
update
Alex edits

@@
 
-% 1. Describe the problem
-% 2. State your contributions
-Mutation analysis is a method of evaluating the quality of test-suites. It
-involves producing a family of mutants with simple differences from the
-original program, and evaluating the effectiveness of test-suites against
-these mutants~\cite{lipton1971fault, ammann2008introduction}.  Previous
-research~\cite{andrews2005mutation} suggests that mutations thus introduced
-behave in a fashion similar to the real-faults with respect to the difficulty
-of detection.
+% 1. Describe the problem % 2. State your contributions Mutation
+analysis is a method for evaluating the quality of test-suites. It
+involves producing a family of \emph{mutants}, programs with small
+differences from the original program, and evaluating the
+effectiveness of test suites against these
+mutants~\cite{lipton1971fault, ammann2008introduction}.  Previous
+research~\cite{andrews2005mutation} suggests that mutations thus
+introduced behave in a fashion similar to real faults, with respect to
+the difficulty of detection.
 
-One of the impediments to wider adoption of mutation analysis is its high
-computational cost.  The set of simple mutants of a moderate sized program
-can be very large, and renders mutation analysis prohibitively time-consuming.
+One of the impediments to wider adoption of mutation analysis is its
+high computational cost.  The set of simple mutants for even a
+moderate sized program can be very large, which renders mutation
+analysis prohibitively time consuming.
 
-A major strain of research into cost-reduction of mutation
-analysis is to choose a smaller representative set of
-mutants~\cite{offutt2001mutation,jia2011analysis}-- often called the \textit{do
-fewer} approach. This approach can be generally divided into selective
-strategies and sampling strategies.
+A major strain of research into cost-reduction of mutation analysis is
+to choose a smaller, representative, set of
+mutants~\cite{offutt2001mutation,jia2011analysis} --- often called the
+\textit{do fewer} approach. This approach can be generally divided
+into selective strategies and sampling strategies.
 
-Selective mutation strategies attempt to select a representative subset of
-operators based on heuristics and statistical analysis, and applying this
-subset of operators to generate mutants instead of applying the whole gamut
-of mutation operators~\cite{offutt1993anexperimental,untch2009onreduced}.
+Selective mutation strategies attempt to select a representative
+subset of mutation \emph{operators} based on heuristics and
+statistical analysis, and apply this subset of operators to generate
+mutants instead of applying the whole set of mutation
+operators~\cite{offutt1993anexperimental,untch2009onreduced}.  As an
+example, recent work suggests that using statement deletion only can
+provide effective mutation analysis~\cite{untch2009onreduced}.
 
-Sampling strategies seek to randomly select smaller representative
-mutants.  This was investigated first by Acree~\cite{acree1980mutation} and
-Budd~\cite{budd1980mutation}, who proposed using only $x$\% of the mutants
-produced. The studies by Wong and Mathur found that random sampling with
-ratio as low as 10\% could provide accurate results~\cite{jia2011analysis}.
+Sampling strategies seek to randomly select a set of representative
+mutants.  This was investigated first by
+Acree~\cite{acree1980mutation} and Budd~\cite{budd1980mutation}, who
+proposed using only $x$\% of all mutants produced. Wong and Mathur
+found that random sampling with ratio as low as 10\% could provide
+accurate results~\cite{jia2011analysis}.
 
@@
 
-A few recent works~\cite{zhang2010icse,zhang2013ase} have investigated the
-relative merits of random sampling strategies and operator selection. It
-was found that while random sampling can generally perform equal to or
-better than operator selection, a strategy that combined random sampling
-with program elements paid superior dividends.
+Recent work~\cite{zhang2010icse,zhang2013ase} has investigated the
+relative merits of random sampling strategies and operator selection.
+Random sampling can perform as well as or better than operator
+selection, in these studies; a strategy combining random sampling with
+program element-based sampling was best.  {\bf ADG: did it combing
+random with pelem or pelem with operator???}
 
-However, as pointed out by Zhang et al.~\cite{zhang2013ase}, the
-field has a serious lacuna in large scale research, both in the
-size of the programs studied, and in the number and diversity of
-programs, which reduces our confidence in their results. This is
-true for selective mutation studies, studies in sampling, and also
-for comparatively newer studies that attempt to combine them. This
-is particularly worrisome if mutation analysis is to gain wider
-acceptance among testing professionals. Further, quite a few of the influential
+However, as pointed out by Zhang et al.~\cite{zhang2013ase}, the field
+has a serious lacuna in large scale research, both in the size of the
+programs studied, and in the number and diversity of programs, which
+reduces our confidence in all results. This is true for selective
+mutation studies, studies in sampling, and also for comparatively
+newer studies that attempt to combine methods. This is particularly
+worrisome if mutation analysis is to gain wider acceptance among
+testing professionals. Further, quite a few of the influential
 studies~\cite{offutt1993experimental,offutt1996anexperimental,wong1995reducing,mresa1999efficiency}
-has been conducted on older programming languages such as Fortran with
-operators specific to it, and are not directly applicable to newer
-languages such as Java, with significant differences. Finally, with the
-modern research into the byte code based mutation (a \textit{do smarter}
-approach for eliminating the compilation step, and gaining execution speed)
-operators based on source code modification is no longer be applicable,
-and their equivalents in the bytecode needs to be found and compared with
-other approaches. A detailed discussion of these issues can be found in
+were conducted on older programming languages such as Fortran, with
+operators specific to the language, and are not directly applicable to
+newer languages such as Java. Finally, modern research into the byte
+code based mutation (a \textit{do smarter} approach for eliminating
+the compilation step to gain execution speed) operators based on
+source code modification are no longer applicable, and their
+equivalents in bytecode need to be identified and compared with other
+approaches. A detailed discussion of these issues can be found in
 Section~\ref{sec:related}.
 
-We have attempted to rectify this situation with a large scale study of
-industrial programs.  As detailed in Section~\ref{sec:methodology}, we sample
-188 real world Java programs from Github, with size ranging from 50loc to
-100kloc, which allows widely applicable statistical inferences to be made. We
-provide the results from running both original human generated test-suites, and
-also programmatically generated test-suites, increasing the applicability of
-our findings to both researchers who seek to compare test-suites quickly,
-and to industrial software testers who might be looking for a way to
-reduce the time of their build cycle when using mutation coverage. The
-Section~\ref{sec:methodology} discusses the sampling strategies attempted,
-and the operator selection strategies in detail, and the results of our
-experiment are given in Section~\ref{sec:results}, followed by detailed
-discussion of what it implies in section ~\ref{sec:discussion}. The research
-concludes in Section~\ref{sec:conclusion}.
+We have attempted to rectify this situation with a large scale study
+of real world programs.  As detailed in Section~\ref{sec:methodology},
+we sample 188 Java programs from Github, with size ranging from 50 LOC
+to 100 KLOC, which allows widely applicable statistical inferences to
+be made. We provide the results from running both original project
+human generated test-suites and also automatically generated
+test suites using random testing, increasing the applicability of our
+findings to both testers in traditional development who are interested in applying mutation analysis to suite evaluation and to researchers who seek to compare test suites quickly.
 
-Our specific contributions in this paper are listed as follows:
+Section~\ref{sec:methodology} discusses the sampling and operator
+selection strategies we study in detail, and the results of our
+experiment are given in Section~\ref{sec:results}, followed by
+detailed discussion of what these results imply in Section
+~\ref{sec:discussion}. The specific contributions of this paper are:
+
+%The research concludes in Section~\ref{sec:conclusion}.
 
@@
 \item Our study is the largest so far in terms of both the size of programs
-involved (50loc to 100kloc), and the number of programs analyzed (188
+involved (50 LOC to 100 KLOC), and the number of programs analyzed (188
 unique open source projects) for mutant reduction strategies. This allows
-for stronger and widely applicable statistical inferences to be drawn.
+for stronger and more widely applicable conclusions about effectiveness.
 
-\item We compare a much large number of mutant reduction strategies,
-especially with respect to their predictive power over the final mutation
-score, the expected mutant reduction, and the stability of the amount of
-mutant reduction expected. Our sampling strategies include some that were
-suggested by other researchers, and also a few novel strategies that has
-not been published elsewhere.
+\item We compare a much large number of mutant reduction strategies
+than previous studies. We compare with respect to the predictive power
+(correlation) with the full mutation score, expected mutant reduction,
+and the stability of the amount of mutant reduction expected. Our
+sampling strategies include some that were suggested by other
+researchers, as well as a few novel strategies that have not been
+previously considered.
 
-\item Our recommendations are valid for both testing researchers who might
-be comparing programmatically generated test-suites, and software testing
-professionals working on real test-suites.
+\item Our recommendations are valid for both testing researchers who
+might be comparing automatically generated test-suites, and software
+testers in real world development working to produce and evaluate manual test suites.
 
@@
 \end{itemize}
+
+Our data is available for replication~\cite{data}\footnote{Available on publication}.
 

### 2014-03-14 src/introduction.Rnw
Fixing the pointed out issues: do/faster/fewer/smarter
Fix unintented %'s

@@
 
-% 1. Describe the problem % 2. State your contributions Mutation
-analysis is a method for evaluating the quality of test-suites. It
+% 1. Describe the problem % 2. State your contributions
+Mutation analysis is a method for evaluating the quality of test-suites. It
 involves producing a family of \emph{mutants}, programs with small
@@
 Random sampling can perform as well as or better than operator
-selection, in these studies; a strategy combining random sampling with
-program element-based sampling was best.  {\bf ADG: did it combing
-random with pelem or pelem with operator???}
+selection, in these studies; a strategy of either program elements
+based sample or one combining both program element-based sampling
+and operator selection was best.
+%{\bf ADG: did it combing random with pelem or pelem with operator???}
 
@@
 newer languages such as Java. Finally, modern research into the byte
-code based mutation (a \textit{do smarter} approach for eliminating
+code based mutation (a \textit{do faster} approach for eliminating
 the compilation step to gain execution speed) operators based on

### 2014-03-14 src/related.Rnw
Fixing the pointed out issues: do/faster/fewer/smarter
Fix unintented %'s
fix conflict

--- 2014-03-13 src/related.Rnw
@@
 \label{sec:related}
-In this section we summarize the related work. There have been
-different approaches to reduce the cost of mutation analysis.
+There are several approaches to reducing the cost of mutation analysis.
 These were categorized by Offutt and Untch~\cite{offutt2001mutation}
-into three approaches: Do \textit{fewer}, \textit{smarter}, \textit{faster}.
-The fewer approaches includes selective mutation and mutant sampling while
-weak mutation, parallelization of mutation analysis, space time trade offs
+into three approaches: do \textit{fewer}, \textit{smarter}, or \textit{faster}.
+The fewer approaches includes selective mutation and mutant sampling;
+weak mutation, parallelization of mutation analysis, and space/time trade-offs
 are grouped under the umbrella of \textit{do smarter}. Finally
-\textit{do faster} approaches include byte code based mutation analysis
-systems like PIT, and similar binary patching methods.
+\textit{do faster} approaches include mutant schema generation methods,
+code patching techniques, and byte code based mutation analysis systems like PIT.
 
-The idea of using a subset of mutants was born along with the mutation analysis
-itself. Budd~\cite{budd1980mutation} and Acree~\cite{Acree1980} showed that
-even 10\% sampling can achieve 99\% accuracy for the final score.
-
-It was further investigated by Mathur~\cite{mathur1991performance},
-Wong et al.~\cite{wong1993mutation,wong1995reducing}, and
-Offutt et al.~\cite{offutt1993experimental} using the Mothra~\cite{Mothra}
-mutation operators for Fortran. Mathur~\cite{mathur1991performance,wong1995reducing}
-suggested constrained mutation where in only two mutation operators were used which
-were felt to be better than using the entire set.
+The idea of using a subset of mutants was conceived along with
+mutation analysis itself. Budd~\cite{budd1980mutation} and
+Acree~\cite{Acree1980} showed that even 10\% sampling can achieve 99\%
+accuracy for the final score.  The idea was further investigated by
+Mathur~\cite{mathur1991performance}, Wong et
+al.~\cite{wong1993mutation,wong1995reducing}, and Offutt et
+al.~\cite{offutt1993experimental} using the Mothra~\cite{Mothra}
+mutation operators for
+Fortran. Mathur~\cite{mathur1991performance,wong1995reducing}
+suggested constrained mutation where only two mutation operators
+were used.%, which were felt to be better than using the entire set.
 
@@
 1995~\cite{wong1995reducing}. They compared x\% selection of each mutant type
-with operator selection of just two mutation operators, and finds that both
+with operator selection using just two mutation operators, and found that both
 achieved similar accuracy and reduction (80\%). This study was conducted on
@@
 
-Some studies have tried to find set of \emph{sufficient mutation operators} that
-while reducing the cost of mutations, maintains the correlation with the full
-mutation score. Offutt~\cite{offutt1993experimental} suggested n-selective
-approach which advocates step by step removal of mutation operators that produced
-the largest number of mutants.
+Some studies have tried to find set of \emph{sufficient mutation
+operators} that reduce the cost of mutation but maintain correlation
+with the full mutation score. Offutt~\cite{offutt1993experimental}
+suggested an $n$-selective approach with step-by-step removal of
+mutation operators that produced the largest number of mutants.
 
-Mresa et al.\cite{mresa1999efficiency} used the cost of detection of mutants as
-a means of selection, and uses it to define a set of operators. They find
-that if very high mutation score close to 100\% is required, x\% selective
-mutation is better than operator selection, and conversely for less stringent
-scores, operator selection would be better if cost of mutant is considered.
+Mresa et al.\cite{mresa1999efficiency} used the cost of detection of
+mutants as a means of selection to define a set of operators. They
+found that if very high mutation score (close to 100\%) is required,
+x\% selective mutation is better than operator selection, and,
+conversely, for lower scores, operator selection would be better if
+the cost of mutants is considered.
 
-Barbosa et. al.\cite{barbosa2001toward} provides a set of guidelines for selecting
-such mutation operators. Namin et al.\cite{namin2006finding,siami2008sufficient}
-formulate this problem as a variable reduction problem, and apply statistical
-approaches. They found a subset of 28 operators out of 108 operators as the sufficient
-operators.
+Barbosa et. al.\cite{barbosa2001toward} provide a set of guidelines
+for selecting such mutation operators. Namin et
+al.\cite{namin2006finding,siami2008sufficient} formulate the problem
+as a variable reduction problem, and apply statistical
+approaches. They found a subset of 28 operators out of 108 operators that are
+sufficient.
 
 Using only the statement deletion operator was first suggested by
-Untch~\cite{untch2009onreduced}, who found that it correlated ($R^2 = 0.97$) with the
-full mutation score better than other operator selection methods, while generating the
-least number of mutants.  This was further reinforced by Deng et al.~\cite{deng2013empirical}
-who defined deletion for different language elements, and found that an accuracy of 92\% is
-achieved while reducing the mutants by 80\%.
+Untch~\cite{untch2009onreduced}, who found that it correlated ($R^2 =
+0.97$) with the full mutation score better than other operator
+selection methods, while generating the smallest number of mutants.
+This was further reinforced by Deng et al.~\cite{deng2013empirical}
+who defined deletion for different language elements, and found that
+an accuracy of 92\% is achieved while reducing the number of mutants
+by 80\%.
 
-Zhang et al.~\cite{zhang2010operator} compares operators based mutant selection in
-~\cite{barbosa2001toward,siami2008sufficient,offutt1996anexperimental} to random mutant selection.
-They find that none of these selection techniques are superior to random selection, with same number of
-mutants. They also find that equal mutation sampling is more effective for larger subjects compared to
-equal mutagen sampling and the reverse is true for smaller subjects.
+Zhang et al.~\cite{zhang2010operator} compares operators based mutant
+selection techniques proposed in a set of
+papers~\cite{barbosa2001toward,siami2008sufficient,offutt1996anexperimental}
+to random mutant sampling.  They find that none of the selection
+techniques are superior to random sampling, with the same number of
+mutants. They also find that equal mutation sampling is more effective
+for larger subjects compared to equal mutagen sampling and the reverse
+is true for smaller subjects.
+{\bf ADG:  not having defined mutagen/mtuation sampling this is not easy for most readers to understand.
+also we switch between "sampling" and "random selection" a lot, I tried to make consistent.}
 
-Recently, Zhang et al.~\cite{zhang2013ase} confirmed that sampling as few as 5\% mutants
-was sufficient for a very correlation (99\%) with the full mutation score, while sampling even
-fewer mutants has good potential for retaining high accuracy. They investigate 8 sampling
-strategies on top of operator based mutant selection and find that sampling strategies
-based on program components (based on methods) performed best.
+Recently, Zhang et al.~\cite{zhang2013ase} confirmed that sampling as
+few as 5\% of mutants was sufficient for a very high correlation
+(99\%) with full mutation score, while sampling even fewer mutants has
+good potential for retaining high accuracy. They investigated 8
+sampling strategies on top of operator-based mutant selection and
+found that sampling strategies based on program components (methods in
+particular) performed best.
 
@@
 
-This work is closely related to Zhang et al.~\cite{zhang2013ase}. We extend the scope of
-their study with much wider range of mutation selection and we experimented them on much more
-real-world projects.
+Our work is most closely related to that of Zhang et
+al.~\cite{zhang2013ase}. We extend the scope of their study with a
+much wider range of mutation approches and base our results on a large
+set of real-world projects.
 

### 2014-03-14 src/methodology.Rnw
methodology alex

@@
 
-\section{Methodology}
-\label{sec:methodology}
-Our selection of programs was driven by a few overriding concerns. Our primary
-requirement was that, our results had to be as widely applicable as possible
-for real-world programs. Secondly, we strived for a statistically significant
-result, reducing the amount of variables present in the experiments. For this
-reason we chose a random sample of Java projects from Github\cite{github}
-that uses the popular maven\cite{maven} build system, that has been used
-elsewhere\cite{gopinath2014code}. We utilize two flavors of
-of test-suites. The original test-suites present in a limited number of
-projects, and automatically generated test-suites using randoop.  Due
-limited resources, we had to further reduce the programs and test-suites
-to those that could finish the mutation run in 10 minutes. From this set
-of test-suites, we sampled 110 suites each for both original and randoop
-generated test-suits. This gave us 81 unique projects for both original
-and randoop, and remaining projects having both flavors of test suites.
+\section{Methodology} \label{sec:methodology} Our selection of
+programs was driven by a few overriding concerns. Our primary
+requirement was that our results had to be as widely applicable as
+possible for real-world programs. Secondly, we strived for a
+statistically significant result, reducing the number of variables
+present in the experiments. For this reason we chose a random sample
+of Java projects from Github\cite{github} that use the popular
+maven\cite{maven} build system, following the methodology used by some
+of the authors in an ICSE 2014 paper~\cite{gopinath2014code}. As in
+that work, we utilize two kinds of of test suites: the original test
+suites present in a limited number of projects, and automatically
+generated test suites from Randoop~\cite{randoop}.  Due to limited resources, we had to
+further reduce the programs and test suites to those that could finish
+mutation analysis in 10 minutes. From this set of test suites, we
+sampled 110 suites each for both original and randoop generated
+test suites. This gave us 81 unique projects for both original and
+Randoop suites, and remaining projects having both flavors of test suites. {\bf ADG I have no idea what that last sentence means, really.}
 
@@
 provided by other mutation systems. The set of operators that we used
-are provided in Table~\ref{tbl:pitop}. A distribution of these operators
-in our projects are provided in Figure~\ref{fig:op}, which shows both the
-distribution of complete mutants and the relative detection rates of each
-mutation operators. In the figure, there are two box-plots corresponding
+is provided in Table~\ref{tbl:pitop}. Figure~\ref{fig:op} which shows both the
+distribution of mutants and the relative detection rates of each
+mutation operator for our projects. In the figure, there are two box-plots corresponding
 to each mutation operator on the Y-axis. The black box represents the
 relative frequency of the particular mutation operator in the total mutants
-\textit{generated}. For example for projects in the randoop set, the
+\textit{generated}. For example for projects in the Randoop set, the
 operator \pitnvmc contributed about 34\% of the total number of mutants
@@
 
-For a detailed description of each mutants, please see~\cite{pitmut}.
+For a detailed description of each mutant type, please see~\cite{pitmut}.
 PIT was also modified to provide random selection of mutants according
 to various criteria. Finally, to remove random noise, each criteria
-described has been run four times, and the results are averaged to produce
+described was run four times, and the results averaged to produce
 the final result.
@@
 source code statement deletion is very hard. We were able to approximate statement deletion
-by combining different bytecode operators, which is explained in Subsection~\ref{subsec:stmtdel}.
+by combining different bytecode operators, as explained in Subsection~\ref{subsec:stmtdel}.
 
@@
 We used several different sampling criteria, some of which has been suggested
-in the literature before, and some which are variants of previously suggested
-criteria, and some that have not been used before.  For each sampling
-criteria, we sampled mutants on a decreasing power scale sampling
+in the literature before, some of which are variants of previously suggested
+criteria, and some of which have not been used before.  For each sampling
+criteria, we sampled mutants on a decreasing power scale, sampling
 \textit{1, 1/2, 1/4, 1/8, 1/16, 1/64} of the total mutants.
@@
 \subsubsection{x\% selection}
-The simplest one consisted of using x\% selection as suggested by
+The simplest sampling approach consisted of using x\% selection as suggested by
 Budd~\cite{budd1980mutation}. In this criteria, we choose a specific
 fraction of the complete set of mutants. This criteria also serves as a
-control for the verifying the effectiveness of other criteria.
+control for verifying the effectiveness of other criteria.
 
@@
 extended x\% selection criteria to sample from within different program
-elements.  We sampled in the increasing order of scope,
+elements.  We sampled in increasing order of scope,
 --- \textit{line}, \textit{method} and \textit{class} (\textit{project}
-scope was analyzed as part of x\% selection).
+scope is just x\% selection).
 
@@
 
-Next, we modified this criteria slightly, and instead of choosing a mutant
-with probability of decimal part, applied \textit{round(sample)} to round
-it to the nearest whole number. We used this as the number of samples to
-be chosen from the population. Our aim was to remove elements that was
-too simple. That is, if the number of mutants dropped below a threshold
-determined by the mutant reduction ratio, that program element did not
-contribute any thing to the final result.
+Next, we modified this criteria slightly, and instead of choosing a
+mutant with probability equal to the decimal part, we applied
+\textit{round(sample)} to round it to the nearest whole number. We
+used this as the number of samples to be chosen from the
+population. Our aim was to \emph{remove} elements that were too simple. That
+is, if the number of mutants dropped below a threshold determined by
+the mutant reduction ratio, that program element did not contribute
+any mutants to the final result.
+Conceptually the idea is that mutants of more complex code have more discriminatory power (and may correspond better to real faults though we do not evaluate this concept).
 
 Next, we explored in the other direction, by forcing the program elements
-to return at least one element by using the \textit{ceil(sample)}. That is,
+to return at least one element by using \textit{ceil(sample)}. That is,
 irrespective of the fraction being sampled, the simplest elements always
@@
 decrease in accuracy. This also provides a nice comparison with similar
-number of mutants between operator selection and random sampling of mutants.
+numbers of mutants between operator selection and random sampling of mutants.
 
-We next extended it to sample from each method instead, but using the number
-of lines in the method as the number of mutants to be sampled. This provided
-a test of hypothesis of how important the coverage was. This was extended
-to class and project scope also.
+We next extended this approach to sample from each method instead, but
+used the number of lines in the method as the number of mutants to be
+sampled from it. This provided a test of the hypothesis of how
+important a mutation samplings relationship to simple code coverage
+was. This was extended to class and project scope also.
 
@@
 the sampling in one go, where we chose \textit{linecount/x} number of mutants from
-each program element.
+each program element. {\bf ADG:  Could maybe make this clearer?}
 
@@
 Javalanche have targeted C programs, thus some of these operators
-are sensible in C but in Java programs. For example C compilers tolerate
-removing a return statement but, in Java, it causes a compilation error.
-Moreover, there were some operators that are not supported by PIT framework
-like ABS (absolute mutation operators), however, we tried to realize as many
-as possible operators using PIT's bytecode level mutation. We also extended 
+are sensible in C but not in Java programs. For example C compilers tolerate
+removing a return statement --- in Java this causes a compilation error.
+Moreover, there were some operators that are not supported by the PIT framework
+like ABS (absolute mutation operators). We tried to realize as many
+as possible of the operators using PIT's bytecode level mutation. We also extended 
 the PIT framework to support the  statement deletion operator (SDL).

### 2014-03-14 src/methodology.Rnw
updates: methodology related
For related: got the message, for methodology, fixed
the problems pointed out.

@@
 suites present in a limited number of projects, and automatically
-generated test suites from Randoop~\cite{randoop}.  Due to limited resources, we had to
-further reduce the programs and test suites to those that could finish
-mutation analysis in 10 minutes. From this set of test suites, we
-sampled 110 suites each for both original and randoop generated
-test suites. This gave us 81 unique projects for both original and
-Randoop suites, and remaining projects having both flavors of test suites. {\bf ADG I have no idea what that last sentence means, really.}
+generated test suites from Randoop~\cite{randoop}.  Due to limited
+resources, we had to further reduce the programs and test suites to those
+that could finish mutation analysis in 10 minutes. From this set of test
+suites, we sampled 110 suites each for both original and Randoop generated
+test suites. Since there was some overlap between projects with original
+test suites, and those with Randoop test suites, we had 81 unique projects
+each in both sets. The remaining projects had both flavors of test suites.
+% {\bf ADG I have no idea what that last sentence means, really.
+% RG: Fixed}
 
@@
 sampled from it. This provided a test of the hypothesis of how
-important a mutation samplings relationship to simple code coverage
+important a mutation sampling's relationship to simple code coverage
 was. This was extended to class and project scope also.
@@
 selected \textit{linecount} mutants each from each method, and applied the x\%
-selection to the result of this selection. For the second variant, we did
-the sampling in one go, where we chose \textit{linecount/x} number of mutants from
-each program element. {\bf ADG:  Could maybe make this clearer?}
+selection to the result of this selection. For e.g for $1/2$ sampling on methods
+if a method had $10$ lines and another had $10$ lines, we sampled $10$ mutants
+from the first, and $20$ mutants from the second, and from the combined $30$
+mutants, we sampled $15$.  For the second variant, we did the sampling in one go,
+where we chose \textit{linecount/x} number of mutants from each program element.
+That is, in the previous example, only $5$ mutants from the first and $10$ mutants
+from the second method would be chosen.
+
+%{\bf ADG:  Could maybe make this clearer?}
+% RG: Fixed with an example.
 

### 2014-03-14 src/analysis.Rnw
Alex changes

@@
 \[\mu_\{M_{all}|M_{reduced}\} = 0 + \beta_1 \times M_{reduced}\]
-as the regression formula, and report
-the correlation from this linear regression. We also report the expected
+as the regression formula, and reported
+the correlation for this linear regression. We also report the expected
 multiplier factor $\beta_1$ for the sampled mutation score. This factor
@@
 We also compute standard deviation of the mutant reduction, which determines
-the consistency of results. (A large amount of standard deviation suggests
+the consistency of results. A large amount of standard deviation suggests
 that the mutant reduction ratio achieved is very much dependent on the
-project. So as a heuristic, we suggest looking at only those projects which
-has a mean reduction ratio at least twice the standard deviation.)
+project. So as a heuristic, we suggest looking at only those methods which
+have a mean reduction ratio at least twice the standard deviation.
 
 A few projects did not return any results for some large reduction factors.
-This number of valid results from projects are also collected in the result
+Thus number of valid results from projects is also collected in the result
 tables.

### 2014-03-14 src/conclusion.Rnw
udpate
Alex changes

@@
 
-Our analysis suggests that simple random sampling, that is, at the project level works best when compared to more sophesticated schemes of sampling.
-Further, we also note that random sampling performs better in predicting final mutation score when compared against operator selection.
+Our analysis suggests that simple random sampling --- that is, at the
+project level --- works best when compared to more sophesticated schemes of
+sampling. Further, we also note that random sampling performs better in
+predicting final mutation score than operator selection.
 
-This suggests that the best way to reduce the computational requirements while trying to build a representative set is to randomly sample on the whole set of mutants directly.
+This suggests that the best way to reduce the computational
+requirements of mutation analysis is fortunately easy to apply in
+almost any setting, given a tool that produces a good starting set of
+mutants.  Namely, randomly sampling the total mutant population, even
+with very small sample sizes, can effectively predict the results of
+running all mutants, but at only a fraction of the computational cost.
+Not only is this method simple and effective, but it is also quite
+stable comapred to some alternatives, with a low standard deviation in
+effectiveness across projects, for both original and random test suites.
+
+There is a second possible point of interest here: as with coverage
+metrics used to predict mutation scores~\cite{gopinath2014code}, using
+a large body of actual open source code to perform experiments seems
+to favor simple and easily-implemented approaches much more strongly
+than limited experiments on more academic subjects.  We speculate that
+the inadequacies in real world test suites, or even in randomly
+generated tests for real world programs, may frequently be more simply
+predicted and evaluated than for typical research subjects, which may
+be smaller or involve less easily distinguished test suites.

### 2014-03-14 src/discussion.Rnw
Alex changes

@@
 better than that based on classes, which in turn is better than methods and
-lines, with regard to the stability of the result (i.e low sd).
+lines, with regard to the stability of the result (i.e. low standard deviation).
 This seems not very visible at lower levels (where the reduction fraction is less
 than 32), but becomes more pronounced as the mutant reduction fraction increases.
-There seem to exist a hierarchy of sampling, where by as you go more fine grained,
-the stability decreases.
-We did not see the pattern found by Zhang et al.~\cite{zhang2013ase} where by
-the method based sampling had the highest accuracy. In fact, in our measurements,
+There seem to exist a hierarchy of sampling, where by as sampling becomes more fine grained stability decreases.
+We did not see the pattern found by Zhang et al.~\cite{zhang2013ase} where method-based sampling had the highest accuracy. In fact, in our measurements,
 the opposite may be true, with project based sampling getting the highest correlation

### 2014-03-14 src/results.Rnw
Alex changes

@@
 Our results for random sampling over program elements using $sample(x)$
-are given in Table~\ref{tbl:xselsample}. The result of its variation, using
-$round(x)$ is given in Table~\ref{tbl:xselround}, and that using
+are given in Table~\ref{tbl:xselsample}. The result of the variation using
+$round(x)$ is given in Table~\ref{tbl:xselround} and that using
 $ceil(x)$ is given in Table~\ref{tbl:xselceil}.
@@
 done per class, per method, per line etc. The second column provides the
-fraction involved.  Third column contains the $R^2$ value obtained between
+fraction involved.  The third column contains the $R^2$ value obtained between
 the mutation score of the sampling criteria used and the full mutation score.
@@
 total mutants produced divided by the number of mutants sampled by the criteria.
-Fifth column contains the standard deviation of the same. A few of the projects
+The fifth column contains the standard deviation of the same. A few of the projects
 did not return any value for certain sampling criteria for particular mutation
@@
 
-The Table~\ref{tbl:lcountl} provides the results for line count criteria where the
+Table~\ref{tbl:lcountl} provides the results for line count criteria where the
 sampling was conducted outside program element, and Table~\ref{tbl:lcountw} contains
 the results for line count criteria where the sampling was conducted inside the
-program element. Similarly the Table~\ref{tbl:onesel} contains the results for
+program element. Similarly Table~\ref{tbl:onesel} contains the results for
 the criteria of one mutant per program element.
 
-The same (only for original test suite) is visualized in Figure~\ref{fig:xroundsel}.
+The same data (only for original test suite) is visualized in Figure~\ref{fig:xroundsel}.
 

### 2014-03-14 src/threats.Rnw
Alex changes

@@
 While we have taken every care to ensure that our results are valid, and to eliminate the
-effects pf random noice in experiments, our results are subject to the following threats
+effects of random noise in experiments, our results are subject to the following threats
 to validity.
 
-Our results were observed on open source Java programs from Github repository, using the
+Our results were observed on open source Java programs from the Github repository, using the
 maven build system. Further, only those projects that successfully completed mutation
@@
 to some extent for our purposes. Software bugs are a fact of life. While every care has been
-taken to avoid them, there is still some probability of some bugs having escaped us.
+taken to avoid them, there is still some possibility of some bugs having escaped us.

### 2014-03-15 src/analysis.Rnw
remove redundant lines

@@
 tables.
-
-%\subsection{Sampling Criteria}
-
-% \begin{figure*}[t]
-% <<x.per.sel.sample,fig.width=10, fig.height=3, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-% o.xp.sample <- subset(o.processed, grepl('^rr[.].*.m[.]red',ind))
-% ggplot(subset(o.xp.sample, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
-%   stat_boxplot(geom ='errorbar')+
-%   geom_boxplot() + facet_wrap(~type) + myopts + theme(legend.position="none")
-% @
-% \caption{The effect of sample(x) reduction. All are above 0.90 $R^2$.}
-% \label{fig:xsamplesel}
-% \end{figure*}
-% 
-% \begin{figure*}[t]
-% <<x.per.sel.round,fig.width=10, fig.height=3, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-% o.xp.round <- subset(o.processed, grepl('^r[.].*.m[.]red',ind))
-% ggplot(subset(o.xp.round, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
-%   stat_boxplot(geom ='errorbar')+
-%   geom_boxplot() + facet_wrap(~type)+ myopts+ theme(legend.position="none")
-% @
-% \caption{The effect of round(x) reduction, Except for line sampling of power $5$ and $6$ all others are above 0.90 $R^2$.}
-% \label{fig:xroundsel}
-% \end{figure*}
-%Our experiments found that while $round(x)$ and $sample(x)$ produced relatively reasonable reduction of mutants, the $ceil(x)$ criteria failed to produce a reasonable reduction of mutants except for higher power where the reduction was some what close to that produced by $round(x)$ and $sample(x)$ (which was expected).
-The $R^2$ values of $ceil(x)$ were almost always lower than that produced by $round(x)$ and $sample(x)$ for similar reduction of mutants.
-For this reason, we do not consider this function again.
-However, interested parties can refer to our published data.
-% ----------------------------------------------------------------------
-
-%\subsubsection{Lines per element}
-%The aim of this criteria is similar in some sense to selective mutation.
-While n-selective mutation ignores the most numerous mutant species, this criteria seeks to deprioritize the most complex program elements.
 
@@
   geom_boxplot() + facet_wrap(~type) + myopts + theme(legend.position="none") + opts(title="sample(x)")
-# @
-# \caption{The effect of sample(x) reduction. All are above 0.90 $R^2$.}
-# \label{fig:xsamplesel}
-# \end{figure*}
-# 
-# \begin{figure*}[t]
-# <<x.per.sel.round,fig.width=10, fig.height=3, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
 o.xp.round <- subset(o.processed, grepl('^r[.].*.m[.]red',ind))
@@
 df <- subset(o.xp.opsel, rm.operators <= 20 & reduction != Inf & type != 'operator' & (type != 'n-selection' | rm.operators < 9))
-#ggplot(df, aes(rm.operators, reduction, fill=interaction(type,rm.operators), dodge=type)) +
-#  stat_boxplot(geom ='errorbar')+
-#  geom_boxplot() + facet_wrap(~type) + myopts +
-#  #theme(legend.position="none") +
-#  opts(title="opsel(x)")
 qplot(rm.operators, reduction, fill=interaction(type,rm.operators), data=df, geom="boxplot", position="dodge") + theme_bw()
@@
 
-% \begin{figure*}[t]
-% <<loc.per.sel.sample,fig.width=10, fig.height=3, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-% o.loc.ext <- subset(o.processed, grepl('^l[.].*.m[.]red',ind))
-% ggplot(subset(o.loc.ext, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
-%   stat_boxplot(geom ='errorbar')+
-%   geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none")
-% @
-% \caption{The effect of loc (external) reduction. All are above 0.98 $R^2$.}
-% \label{fig:locsel}
-% \end{figure*}
-% 
-%\begin{figure*}[t]
-%<<wloc.per.sel.sample,fig.width=10, fig.height=2, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-%o.loc.int <- subset(o.processed, grepl('^wl[.].*.m[.]red',ind))
-%ggplot(subset(o.loc.int, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
-%  stat_boxplot(geom ='errorbar')+
-%  geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none")
-%@
-%\caption{The effect of loc (internal) reduction. All are above 0.90 $R^2$.}
-%\label{fig:wlocsel}
-%\end{figure*}
-%
-%
-%The results of this selection criteria are provided in Table~\ref{tbl:locsel}.
-The effect of random selection within the program elements are visualized in Figure~\ref{fig:wlocsel}, and when it is made external to the program elements is visualized in Figure~\ref{fig:wlocsel}.
-
-% ----------------------------------------------------------------------
-%\subsubsection{One per element}
-%The aim of this criteria is is to take the previous idea to the extreme. We choose only a single mutant per program element.
-
-<<one>>=
-#3
-@
-%\begin{figure*}[t]
-%<<one.per.sel.sample,fig.width=10, fig.height=2, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-%o.one <- subset(o.processed, grepl('^o[.].*.m[.]red',ind))
-%ggplot(subset(o.one, reduction < 100 & (type=='line' | type=='method')), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
-%  stat_boxplot(geom ='errorbar')+
-%  geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none")
-%@
-%\caption{The effect of one element selection, All are above 0.98 $R^2$.}
-%\label{fig:onesel}
-%\end{figure*}
-%
-% ----------------------------------------------------------------------
-
-%\subsection{Operator Selection}
 \begin{figure*}[t]
 <<op.all,fig.width=10, fig.height=7, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-#with(subset(stats.df,r.square > 0.9),plot(mutant.reduction, (1-r.square)*100, pch='*', col=as.factor(strategy)))
-# "kind" "operator" "s.power" "s.element" "strategy" "mutant.reduction" "sd.reduction"
-#  "sample" "r.square" "score.multiplier" "p.value"
 
@@
 <<op.all.2,fig.width=10, fig.height=7, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-#with(subset(stats.df,r.square > 0.9),plot(mutant.reduction, (1-r.square)*100, pch='*', col=as.factor(strategy)))
-# "kind" "operator" "s.power" "s.element" "strategy" "mutant.reduction" "sd.reduction"
-#  "sample" "r.square" "score.multiplier" "p.value"
-
 df <-  subset(df, r.square>=0.9 & (sd.reduction * 2) < mutant.reduction & mutant.reduction <= 20)
@@
 <<op.all.3,fig.width=10, fig.height=7, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-#with(subset(stats.df,r.square > 0.9),plot(mutant.reduction, (1-r.square)*100, pch='*', col=as.factor(strategy)))
-# "kind" "operator" "s.power" "s.element" "strategy" "mutant.reduction" "sd.reduction"
-#  "sample" "r.square" "score.multiplier" "p.value"
 
@@
 <<op.all.4,fig.width=10, fig.height=7, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-#with(subset(stats.df,r.square > 0.9),plot(mutant.reduction, (1-r.square)*100, pch='*', col=as.factor(strategy)))
-# "kind" "operator" "s.power" "s.element" "strategy" "mutant.reduction" "sd.reduction"
-#  "sample" "r.square" "score.multiplier" "p.value"
 
@@
 \end{figure*}
-
-% \begin{figure*}[t]
-% <<op.all.2,fig.width=10, fig.height=3, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-% @
-% \caption{The mean reduction of mutants vs its standard deviation. Only those observations with $R^2 > 0.9$ and $2\times $ standard deviation > mean reduction is shown here. }
-% \end{figure*}
-% 
-% \begin{figure*}[t]
-% <<op.all.4,fig.width=10, fig.height=3, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-% ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(shape=strat, color=mult))
-% @
-% \caption{The mean reduction of mutants vs its standard deviation.
-Only those observations with $R^2 > 0.9$ and $2\times $ standard deviation > mean reduction is shown here.
-The color represents the (1-multiplier) to the sampled mutation score to get final score }
-% \end{figure*}
-%
-
-% \begin{figure*}[t]
-% <<op.all.3,fig.width=10, fig.height=3, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-% dfd <- subset(df, !(strategy %in% c('op','opsel')) )
-% ggplot(dfd, aes(sd.reduction, mutant.reduction)) + geom_point(aes(shape=type, color=sqr)) + facet_wrap(~strategy) + theme(axis.text.x = element_text(angle = 90, hjust = 1))
-% @
-% \label{fig:fullimgshape}
-% \end{figure*}
-<<opsel>>=
-#4
-@
-
-%For operator selection, we approximated the operators as far as possible from the research works into the operators exposed by PIT. The results of this are provided in Table~\ref{tbl:opsel}.
-% The subsumption graphs are provided in Figure~\ref{fig:subsumptiono}
-% TODO : Check if this makes sense.
-%\begin{figure*}[t]
-%\includegraphics[totalheight=6cm]{fig/original.pdf}
-%\caption{Subsumption Original}
-%\label{fig:subsumptiono}
-%\end{figure*}
-
-%\begin{figure*}[t]
-%\includegraphics[totalheight=6cm]{fig/randoop.pdf}
-%\caption{Subsumption Randoop}
-%\label{fig:subsumptionr}
-%\end{figure*}[t]
-
-% ----------------------------------------------------------------------

### 2014-03-15 src/analysis.Rnw
Fix column names to use correct letters

@@
 <<results='asis'>>=
-print(xtable(f(o.stats.sel.xp.sample), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
+print(xtable(f(o.stats.sel.xp.sample), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small',sanitize.text.function=function(x){x})
 @
@@
 <<results='asis'>>=
-print(xtable(f(r.stats.sel.xp.sample), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
+print(xtable(f(r.stats.sel.xp.sample), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small',sanitize.text.function=function(x){x})
 @
@@
 <<results='asis'>>=
-print(xtable(f(o.stats.sel.xp.round), caption='Original', label='table:rando', main='Original'), include.rownames=FALSE, floating=FALSE, size='\\small')
+print(xtable(f(o.stats.sel.xp.round), caption='Original', label='table:rando', main='Original'), include.rownames=FALSE, floating=FALSE, size='\\small',sanitize.text.function=function(x){x})
 @
@@
 <<results='asis'>>=
-print(xtable(f(r.stats.sel.xp.round), caption='Randoop', label='table:randr', main='Randoop'), include.rownames=FALSE, floating=FALSE,size='\\small')
+print(xtable(f(r.stats.sel.xp.round), caption='Randoop', label='table:randr', main='Randoop'), include.rownames=FALSE, floating=FALSE,size='\\small',sanitize.text.function=function(x){x})
 @
@@
 <<results='asis'>>=
-print(xtable(f(o.stats.sel.xp.ceil), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
+print(xtable(f(o.stats.sel.xp.ceil), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small',sanitize.text.function=function(x){x})
 @
@@
 <<results='asis'>>=
-print(xtable(f(r.stats.sel.xp.ceil), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
+print(xtable(f(r.stats.sel.xp.ceil), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small',sanitize.text.function=function(x){x})
 @
@@
 <<results='asis'>>=
-print(xtable(f(o.stats.sel.loc), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
+print(xtable(f(o.stats.sel.loc), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small',sanitize.text.function=function(x){x})
 @
@@
 <<results='asis'>>=
-print(xtable(f(r.stats.sel.loc), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
+print(xtable(f(r.stats.sel.loc), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small',sanitize.text.function=function(x){x})
 @
@@
 <<results='asis'>>=
-print(xtable(f(o.stats.sel.loc.w), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
+print(xtable(f(o.stats.sel.loc.w), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small',sanitize.text.function=function(x){x})
 @
@@
 <<results='asis'>>=
-print(xtable(f(r.stats.sel.loc.w), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
+print(xtable(f(r.stats.sel.loc.w), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small',sanitize.text.function=function(x){x})
 @
@@
 <<results='asis'>>=
-print(xtable(f(o.stats.sel.one), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
+print(xtable(f(o.stats.sel.one), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small',sanitize.text.function=function(x){x})
 @
@@
 <<results='asis'>>=
-print(xtable(f(r.stats.sel.one), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
+print(xtable(f(r.stats.sel.one), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small',sanitize.text.function=function(x){x})
 @
@@
 <<results='asis'>>=
-print(xtable(o.stats.sel.op, caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
+print(xtable(o.stats.sel.op, caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small',sanitize.text.function=function(x){x})
 @
@@
 <<results='asis'>>=
-print(xtable(r.stats.sel.op, caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
+print(xtable(r.stats.sel.op, caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small',sanitize.text.function=function(x){x})
 @
@@
 <<results='asis'>>=
-print(xtable(o.stats.sel.opsel, caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
+print(xtable(o.stats.sel.opsel, caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small',sanitize.text.function=function(x){x})
 @
@@
 <<results='asis'>>=
-print(xtable(r.stats.sel.opsel, caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
+print(xtable(r.stats.sel.opsel, caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small',sanitize.text.function=function(x){x})
 @

### 2014-03-15 src/paper.Rnw
Fix column names to use correct letters

@@
 sel.colnames <- c('operator', 'r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier')
-new.colnames <- c('operator', 'r^2',      'm.red',            'm.sd',         'num',    'B*')
+new.colnames <- c('operator', '$R^2$',      '$\\mu_{red}$',            '$\\sigma_{red}$',         'num',    '$\\beta_1$')
 stats.xp <- subset(stats.df, grepl('^(r|rr|rc)[.]', operator)) # We are ignoring ceil here. add rc if needed.

### 2014-03-15 src/paper.Rnw
Fix column names to use correct letters

--- 2014-03-14 src/paper.Rnw
@@
 sel.colnames <- c('operator', 'r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier')
-new.colnames <- c('operator', 'r^2',      'm.red',            'm.sd',         'num',    'B*')
+new.colnames <- c('operator', '$R^2$',      '$\\mu_{red}$',            '$\\sigma_{red}$',         'valid',    '$\\beta_1$')
 stats.xp <- subset(stats.df, grepl('^(r|rr|rc)[.]', operator)) # We are ignoring ceil here. add rc if needed.

### 2014-03-15 src/discussion.Rnw
Fix up the discussion a little bit

@@
 
-%\begin{figure}[t]
-%\includegraphics[totalheight=4.5cm]{fig/opstrat1.pdf}
-%\caption{Mutant distribution in a sample project along operators and program elements}
-%\label{fig:egmutants}
-%\end{figure}
+From our data, we see that for original and generated test suites, the
+mutant reduction ratio and standard deviation was similar for stable strategies
+(where the standard deviation of the reduction achieved was less than half
+of the reduction achieved). This suggests that our analysis is equally
+applicable for both generated test suites and original test suites.
 
-%Our data from Figure~\ref{fig:op} suggests that while there are small differences, the average rate of detection of mutants of each type is similar to the average number of mutants produced for each type.
-This suggests that mutants produced by each operator is similar in terms of difficulty of detection.
+Analysing the scores achieved further, we note that the accuracy of prediction
+($R^2$) achieved by sampling is generally lower for generated test
+suites. Especially, as the fraction of sampling becomes larger the accuracy
+reduces drastically for generated test suites while the accuracy still
+holds good for original test suites
+Secondly, we also observe that the multiplier factor $\beta_1$ 
+is smaller for generated test suites than original test suites. This
+observation holds good for all sampling and operator selection strategies
+examined.  Both these factors together suggest that generated
+test suites have a higher variability in their sampled mutation scores than
+original test suites. We note that since $\beta_1$ was generally smaller
+for generated test suites than original test suites, the full mutation score
+corresponding to a sampled mutation score for generated test suites would
+be lower than what would be expected from original test suite.
+Secondly, the amount of reduction that can be gained by sampling satisfying
+a given accuracy is lower for generated test suites in comparison with original
+test suites.
 
-We see a few patterns in our results. The first is that sampling strategy
-can predict the final score with very minimal loss in accuracy up to a fraction
-of $\frac{1}{64}$ of the total number of mutants (Our experiments suggest up
-to $70$ times reduction, with a low standard deviation of $6.72$). We did not
-cut off with the 99\% rule as mentioned by Zhang et al.~\cite{zhang2013ase}
-(Originally proposed by Offutt et al.~\cite{offutt1996experimental} for a
-different measurement), and instead chose to observe that we obtained
-$R^2 > 0.96$ which provides a high confidence in the accuracy of prediction.
+Considering different sampling strategies, we see a few general patterns. The
+first is that sampling strategy can predict the final score with very
+minimal loss in accuracy up to a fraction of $\frac{1}{64}$ of the total
+number of mutants (Our experiments suggest up to $70$ times reduction,
+with a low standard deviation of $6.72$). We did not cut off with the 99\%
+rule as mentioned by Zhang et al.~\cite{zhang2013ase} (Originally proposed
+by Offutt et al.~\cite{offutt1996experimental} for a different measurement),
+and instead chose to observe that we obtained $R^2 > 0.96$ which provides
+a high confidence in the accuracy of prediction.
 
-The second pattern is that fractional sampling based on projects appears to be
-better than that based on classes, which in turn is better than methods and
-lines, with regard to the stability of the result (i.e. low standard deviation).
-This seems not very visible at lower levels (where the reduction fraction is less
-than 32), but becomes more pronounced as the mutant reduction fraction increases.
-There seem to exist a hierarchy of sampling, where by as sampling becomes more fine grained stability decreases.
-We did not see the pattern found by Zhang et al.~\cite{zhang2013ase} where method-based sampling had the highest accuracy. In fact, in our measurements,
-the opposite may be true, with project based sampling getting the highest correlation
-with the final score a majority of the time.
+The second pattern is that fractional sampling based on projects appears
+to be better than that based on classes, which in turn is better than
+methods and lines, with regard to the stability of the result (i.e. low
+standard deviation).  This seems not very visible at lower levels (where
+the reduction fraction is less than 32), but becomes more pronounced as the
+mutant reduction fraction increases.  There seem to exist a hierarchy of
+sampling, where by as sampling becomes more fine grained stability decreases.
+We did not see the pattern found by Zhang et al.~\cite{zhang2013ase} where
+method-based sampling had the highest accuracy. In fact, in our measurements,
+the opposite may be true, with project based sampling getting the highest
+correlation with the final score a majority of the time.
 
@@
 selection schemes.
-
-% There may in fact be a simple reason for this observation. Consider the Figure~\ref{fig:egmutants}.
-% It is a representation of the distribution of mutants along two orthogonal axes --- the
-% mutation operators, and program elements such as classes. For the purposes of this
-% explanation, assume that each classes contain equal number of lines, and each mutant
-% produced per line by each of the mutation operators are marked by a small solid circle.
-% The two solid vertical lines in blue and red represents two classes, one with a relatively
-% small number of mutants and other with large number of mutants. Consider that we are sampling
-% by class, and we are choosing all mutants for simplicity. Let $c$ be the number of classes.
-% Here, a mutant in red class contributes to $1/n_{red}$ to the mean of the score of the
-% red class, and the red class contributes $1/c$ to the total mean.  So the contribution of a
-% mutant in red class to the complete is $1/(c * n_{red})$. Similarly for blue class.
-% However, if the sampling is done on a complete project basis, then the contribution of any
-% mutant is $\frac{1}{\sum_{i=1}^{c} n_{i}}$, which depending on the size of the class might
-% be different from what it would contribute if sampling is used. To put it another way,
-% for any kind of sampling used based on sub elements, the units in the sample gets equal
-% weightage in contribution irrespective of the size of elements themselves, while if the sampling
-% is done on a project basis, the contribution of sub elements depends on the number of mutants
-% each elements produced.
-% 
-% What this is saying in effect is that irrespective of the sophestication of sampling used,
-% the simplest sampling technique --- that of project based sampling --- is the best form of
-% sampling, for a representative set.
-% 
-% This also applies immediately to operator selection as it is another kind of sampling on
-% a smaller set. Hence it is no surprise that for larger samples, random sampling is able
-% to trump operator selection on predicting the final result.
-%

### 2014-03-15 src/discussion.Rnw
Add more meat to discussion

@@
 
+% About Randoop and Original
 From our data, we see that for original and generated test suites, the
@@
 
+% About Randoop and Original
 Analysing the scores achieved further, we note that the accuracy of prediction
@@
 test suites.
+
+% Different sampling strategies
+Considering different sampling strategies, based on their stability and mutation
+reduction achieved, we note that using simple sampling (\textit{sample(x)})
+produced the most stable results. For both generated and original test suites,
+this strategy produced valid results for all different scopes and sampling
+ratios. It also was able to achieve the highest mutation reduction of $72.63$,
+that is only $1.37\%$ of the original mutants is needed to produce a highly
+accurate ($R^2 = 0.97$) mutation score, with minimal deviation
+($\sigma = 6.36$) for original test suites. While the accuracy suffers for
+generated test suites it is still high at $R^2 = 0.90$
+
+Considering \textit{round(x)}, the strategy of ignoring low complexity elements
+did not pay off, with the scope line having a tendency to become unstable and
+inaccurate at high sampling ratios. At very high sampling ratio $1/64$, the
+strategy with method scope also becomes unstable and inaccurate. On the whole
+\textit{round(x)} did not perform as well as \textit{sample(x)}
+
+The strategy of \textit{ceil(x)} did not perform well either. While the
+results were generally stable, the reduction ratios achieved was lower than
+\textit{sample(x)}, with similar accuracy.
+
+For line count strategies, only the external sampling produced consistent
+results, which was again not as good as \textit{round(x)} for similar mutation
+reduction ratios. Secondly, we had hypothesised that perhaps coverage was
+a significant contributor to the accuracy of sampled mutation score. However
+we could find no evidence in support of this hypothesis with line, method,
+class, and project showing similar accuracy and consistency at similar reduction
+ratios.
+
+The one per element strategy did not have stable results in general except
+for at the scope of line (at which point it was same as count per element
+strategy).
+
+Considering mutation operators, only three operators \textit{NC,RC,DC} had
+consistent results (and only for original test suites). On considering
+operator selection, n-selection strategy had high accuracy and consistency
+(though low reduction ratio) until 7-selection (removing seven most numerous
+operators) for both generated and original test suites. Javalanche did not
+have a high mutation reduction ratio, though it had high accuracy for both
+kinds of test suites. The other operator selection methods performed poorly
+on generated test suites, while they had high accuracy and reasonable
+stability on original test suites. However, for comparable mutation
+reduction, they performed worse than random sampling strategies.
 

### 2014-03-15 src/analysis.Rnw
Turn off graphs other than sample(x)

@@
 \begin{figure*}[t]
-<<x.per.sel.sample,fig.width=10, fig.height=3, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+<<x.per.sel.sample,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
 o.xp.sample <- subset(o.processed, grepl('^rr[.].*.m[.]red',ind))
@@
   geom_boxplot() + facet_wrap(~type) + myopts + theme(legend.position="none") + opts(title="sample(x)")
-o.xp.round <- subset(o.processed, grepl('^r[.].*.m[.]red',ind))
-ggplot(subset(o.xp.round, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
-  stat_boxplot(geom ='errorbar')+
-  geom_boxplot() + facet_wrap(~type)+ myopts+ theme(legend.position="none")+ opts(title="sample(x)")
-
-o.loc.ext <- subset(o.processed, grepl('^l[.].*.m[.]red',ind))
-ggplot(subset(o.loc.ext, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
-  stat_boxplot(geom ='errorbar')+
-  geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none") + opts(title="loc(external)")
-
-o.loc.int <- subset(o.processed, grepl('^wl[.].*.m[.]red',ind))
-ggplot(subset(o.loc.int, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
-  stat_boxplot(geom ='errorbar')+
-  geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none") + opts(title="loc(internal)")
-
-o.one <- subset(o.processed, grepl('^o[.].*.m[.]red',ind))
-ggplot(subset(o.one, reduction < 100 & (type=='line' | type=='method')), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
-  stat_boxplot(geom ='errorbar')+
-  geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none") + opts(title="One per element")
+# o.xp.round <- subset(o.processed, grepl('^r[.].*.m[.]red',ind))
+# ggplot(subset(o.xp.round, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
+#   stat_boxplot(geom ='errorbar')+
+#   geom_boxplot() + facet_wrap(~type)+ myopts+ theme(legend.position="none")+ opts(title="sample(x)")
+# 
+# o.loc.ext <- subset(o.processed, grepl('^l[.].*.m[.]red',ind))
+# ggplot(subset(o.loc.ext, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
+#   stat_boxplot(geom ='errorbar')+
+#   geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none") + opts(title="loc(external)")
+# 
+# o.loc.int <- subset(o.processed, grepl('^wl[.].*.m[.]red',ind))
+# ggplot(subset(o.loc.int, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
+#   stat_boxplot(geom ='errorbar')+
+#   geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none") + opts(title="loc(internal)")
+# 
+# o.one <- subset(o.processed, grepl('^o[.].*.m[.]red',ind))
+# ggplot(subset(o.one, reduction < 100 & (type=='line' | type=='method')), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
+#   stat_boxplot(geom ='errorbar')+
+#   geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none") + opts(title="One per element")
 @
@@
 \begin{figure*}[t]
-<<op.sample,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+<<op.sample,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
 o.xp.opsel <- o.op.processed

### 2014-03-15 src/methodology.Rnw
Switching off Amins comment
Adding n-selective criteria

@@
 
-{\bf Amin: The rest of this section is for Alex and Carlos info and should be verified if we should include this or wave our hands about approximation instead.}
+% {\bf Amin: The rest of this section is for Alex and Carlos info and should be verified if we should include this or wave our hands about approximation instead.}
 
@@
 By Namin et al. \pitin, \pitm, \piti, \pitnc. Many of operators were not applicable in Java and some were not available in PIT like IndVarBitNeg.
+\subsubsection{Criteria V}
+For this criteria, we utilized the approach suggested by
+Offutt et al.~\cite{offutt1993experimental} where by most numerous operators
+are discarded at each step.
 

### 2014-03-15 src/analysis.Rnw
Adding the x\% selection for operators

@@
 \caption {The one per element selection criteria results.}
+\label{tbl:onesel}
+\end{table*}
+
+\begin{table*}
+\begin{minipage}[h]{0.49\linewidth}
+<<results='asis'>>=
+print(xtable(f(o.stats.sel.xop), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small',sanitize.text.function=function(x){x})
+@
+\end{minipage}
+\hspace{0.5cm}
+\begin{minipage}[h]{0.49\linewidth}
+<<results='asis'>>=
+print(xtable(f(r.stats.sel.xop), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small',sanitize.text.function=function(x){x})
+@
+\end{minipage}
+\bigskip
+\caption {The x\% per operator criteria results.}
 \label{tbl:onesel}

### 2014-03-15 src/paper.Rnw
Fix up table columns
switch delta
.
Adding the x\% selection for operators

@@
   x <- x[,c(7,8,2,3,4,5,6)]
+  names(x)[names(x) == 'sampling'] <- '$\\div$'
   return(x)
@@
 
+stats.xop <- subset(stats.rest, grepl('^OP', operator))
+stats.rest <- subset(stats.rest, !grepl('^OP', operator))
+
+o.stats.sel.xop <- subset(o.f(stats.xop), select=sel.colnames)
+r.stats.sel.xop <- subset(r.f(stats.xop), select=sel.colnames)
+colnames(o.stats.sel.xop) <- new.colnames
+colnames(r.stats.sel.xop) <- new.colnames
+
+o.stats.sel.xop$scope  <- 'op'
+o.stats.sel.xop$sampling  <- gsub('_per_op','',gsub('OP[.]1x','1/', o.stats.sel.xop$operator))
+r.stats.sel.xop$scope  <- 'op'
+r.stats.sel.xop$sampling  <- gsub('_per_op','',gsub('OP[.]1x','1/', r.stats.sel.xop$operator))
+
+o.stats.sel.xop$operator  <- gsub('_per_op','',gsub('OP[.]1x','1/', o.stats.sel.xop$operator))
+r.stats.sel.xop$operator  <- gsub('_per_op','',gsub('OP[.]1x','1/', r.stats.sel.xop$operator))
+
 # 4 done

### 2014-03-15 src/discussion.Rnw
Add x\% selection for operators

@@
 
-Considering mutation operators, only three operators \textit{NC,RC,DC} had
-consistent results (and only for original test suites). On considering
-operator selection, n-selection strategy had high accuracy and consistency
-(though low reduction ratio) until 7-selection (removing seven most numerous
-operators) for both generated and original test suites. Javalanche did not
-have a high mutation reduction ratio, though it had high accuracy for both
-kinds of test suites. The other operator selection methods performed poorly
-on generated test suites, while they had high accuracy and reasonable
-stability on original test suites. However, for comparable mutation
-reduction, they performed worse than random sampling strategies.
+While the x\% per operator strategy produced consistent results, its
+consistency was lower than \textit{sample(x)} results, and was either on
+par or below \textit{sample(x)} for accuracy.
+
+Considering mutation operators, only three operators \textit{NC,RC},and
+\textit{DC} had consistent results (and only for original test suites).
+On considering operator selection, n-selection strategy had high accuracy
+and consistency (though low reduction ratio) until 7-selection (removing
+seven most numerous operators) for both generated and original test suites.
+Javalanche did not have a high mutation reduction ratio, though it had high
+accuracy for both kinds of test suites. The other operator selection methods
+performed poorly on generated test suites, while they had high accuracy
+and reasonable stability on original test suites. However, for comparable
+mutation reduction, they performed worse than random sampling strategies.
 

### 2014-03-15 src/analysis.Rnw
Turn off redundant graphs

@@
 
-\begin{figure*}[t]
-<<op.all.2,fig.width=10, fig.height=7, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-df <-  subset(df, r.square>=0.9 & (sd.reduction * 2) < mutant.reduction & mutant.reduction <= 20)
-ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(size=sqr, color=type))
-ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(shape=sampling, color=type))
-@
-\caption{The mean reduction of mutants vs its standard deviation. The sqr represents (1-$R^2$), i.e smaller is good. Only mean reduction <= 20 (5\%)}
-\label{fig:fullimgsize2}
-\end{figure*}
+% \begin{figure*}[t]
+% <<op.all.2,fig.width=10, fig.height=7, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+% df <-  subset(df, r.square>=0.9 & (sd.reduction * 2) < mutant.reduction & mutant.reduction <= 20)
+% ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(size=sqr, color=type))
+% ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(shape=sampling, color=type))
+% @
+% \caption{The mean reduction of mutants vs its standard deviation. The sqr represents (1-$R^2$), i.e smaller is good. Only mean reduction <= 20 (5\%)}
+% \label{fig:fullimgsize2}
+% \end{figure*}
+% 
+% \begin{figure*}[t]
+% <<op.all.3,fig.width=10, fig.height=7, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+% 
+% df <-  subset(df, r.square>=0.9 & (sd.reduction * 2) < mutant.reduction & mutant.reduction <= 10)
+% ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(size=sqr, color=type))
+% ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(shape=sampling, color=type))
+% @
+% \caption{The mean reduction of mutants vs its standard deviation. The sqr represents (1-$R^2$), i.e smaller is good. Only mean reduction <= 10 (10\%)}
+% \label{fig:fullimgsize3}
+% \end{figure*}
+%
 
-\begin{figure*}[t]
-<<op.all.3,fig.width=10, fig.height=7, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-
-df <-  subset(df, r.square>=0.9 & (sd.reduction * 2) < mutant.reduction & mutant.reduction <= 10)
-ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(size=sqr, color=type))
-ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(shape=sampling, color=type))
-@
-\caption{The mean reduction of mutants vs its standard deviation. The sqr represents (1-$R^2$), i.e smaller is good. Only mean reduction <= 10 (10\%)}
-\label{fig:fullimgsize3}
-\end{figure*}
-
-\begin{figure*}[t]
-<<op.all.4,fig.width=10, fig.height=7, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-
-df <-  subset(df, r.square>=0.9 & (sd.reduction * 2) < mutant.reduction & mutant.reduction <= 5)
-ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(size=sqr, color=type))
-ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(shape=sampling, color=type))
-@
-\caption{The mean reduction of mutants vs its standard deviation. The sqr represents (1-$R^2$), i.e smaller is good. Only mean reduction <= 5 (20\%)}
-\label{fig:fullimgsize4}
-\end{figure*}
+% \begin{figure*}[t]
+% <<op.all.4,fig.width=10, fig.height=7, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+% 
+% df <-  subset(df, r.square>=0.9 & (sd.reduction * 2) < mutant.reduction & mutant.reduction <= 5)
+% ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(size=sqr, color=type))
+% ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(shape=sampling, color=type))
+% @
+% \caption{The mean reduction of mutants vs its standard deviation. The sqr represents (1-$R^2$), i.e smaller is good. Only mean reduction <= 5 (20\%)}
+% \label{fig:fullimgsize4}
+% \end{figure*}
+%

### 2014-03-15 src/analysis.Rnw
Change Title, Fix spellos

@@
-<<xpercentunit>>=
-#1
-@
 \begin{table*}
@@
 
-<<count>>=
-#2
-@
 \begin{table*}
@@
 
-\begin{figure*}[t]
-<<x.per.sel.sample,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-o.xp.sample <- subset(o.processed, grepl('^rr[.].*.m[.]red',ind))
-ggplot(subset(o.xp.sample, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
-  stat_boxplot(geom ='errorbar')+
-  geom_boxplot() + facet_wrap(~type) + myopts + theme(legend.position="none") + opts(title="sample(x)")
-# o.xp.round <- subset(o.processed, grepl('^r[.].*.m[.]red',ind))
-# ggplot(subset(o.xp.round, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
-#   stat_boxplot(geom ='errorbar')+
-#   geom_boxplot() + facet_wrap(~type)+ myopts+ theme(legend.position="none")+ opts(title="sample(x)")
-# 
-# o.loc.ext <- subset(o.processed, grepl('^l[.].*.m[.]red',ind))
-# ggplot(subset(o.loc.ext, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
-#   stat_boxplot(geom ='errorbar')+
-#   geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none") + opts(title="loc(external)")
-# 
-# o.loc.int <- subset(o.processed, grepl('^wl[.].*.m[.]red',ind))
-# ggplot(subset(o.loc.int, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
-#   stat_boxplot(geom ='errorbar')+
-#   geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none") + opts(title="loc(internal)")
-# 
-# o.one <- subset(o.processed, grepl('^o[.].*.m[.]red',ind))
-# ggplot(subset(o.one, reduction < 100 & (type=='line' | type=='method')), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
-#   stat_boxplot(geom ='errorbar')+
-#   geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none") + opts(title="One per element")
-@
-\caption{The effect of sampling reductions, Except for line sampling of power $5$ and $6$ all others are above 0.90 $R^2$.}
-\label{fig:xroundsel}
-\end{figure*}
+% \begin{figure*}[t]
+% <<x.per.sel.sample,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+% o.xp.sample <- subset(o.processed, grepl('^rr[.].*.m[.]red',ind))
+% ggplot(subset(o.xp.sample, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
+%   stat_boxplot(geom ='errorbar')+
+%   geom_boxplot() + facet_wrap(~type) + myopts + theme(legend.position="none") + opts(title="sample(x)")
+% # o.xp.round <- subset(o.processed, grepl('^r[.].*.m[.]red',ind))
+% # ggplot(subset(o.xp.round, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
+% #   stat_boxplot(geom ='errorbar')+
+% #   geom_boxplot() + facet_wrap(~type)+ myopts+ theme(legend.position="none")+ opts(title="sample(x)")
+% # 
+% # o.loc.ext <- subset(o.processed, grepl('^l[.].*.m[.]red',ind))
+% # ggplot(subset(o.loc.ext, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
+% #   stat_boxplot(geom ='errorbar')+
+% #   geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none") + opts(title="loc(external)")
+% # 
+% # o.loc.int <- subset(o.processed, grepl('^wl[.].*.m[.]red',ind))
+% # ggplot(subset(o.loc.int, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
+% #   stat_boxplot(geom ='errorbar')+
+% #   geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none") + opts(title="loc(internal)")
+% # 
+% # o.one <- subset(o.processed, grepl('^o[.].*.m[.]red',ind))
+% # ggplot(subset(o.one, reduction < 100 & (type=='line' | type=='method')), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
+% #   stat_boxplot(geom ='errorbar')+
+% #   geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none") + opts(title="One per element")
+% @
+% \caption{The effect of sampling reductions, Except for line sampling of power $5$ and $6$ all others are above 0.90 $R^2$.}
+% \label{fig:xroundsel}
+% \end{figure*}
+%
 
-\begin{figure*}[t]
-<<op.sample,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-o.xp.opsel <- o.op.processed
-o.xp.opsel$operators <- 16 - o.xp.opsel$operators
-colnames(o.xp.opsel)[colnames(o.xp.opsel)=="operators"] <- "rm.operators"
-
-df <- subset(o.xp.opsel, rm.operators <= 20 & reduction != Inf & type != 'operator' & (type != 'n-selection' | rm.operators < 9))
-qplot(rm.operators, reduction, fill=interaction(type,rm.operators), data=df, geom="boxplot", position="dodge") + theme_bw()
-@
-\caption{Operator selection comparison between n-selection and other selection methods in mutation reduction.  We show only up to 8-selection}
-\label{fig:xroundsel}
-\end{figure*}
+% \begin{figure*}[t]
+% <<op.sample,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+% o.xp.opsel <- o.op.processed
+% o.xp.opsel$operators <- 16 - o.xp.opsel$operators
+% colnames(o.xp.opsel)[colnames(o.xp.opsel)=="operators"] <- "rm.operators"
+% 
+% df <- subset(o.xp.opsel, rm.operators <= 20 & reduction != Inf & type != 'operator' & (type != 'n-selection' | rm.operators < 9))
+% qplot(rm.operators, reduction, fill=interaction(type,rm.operators), data=df, geom="boxplot", position="dodge") + theme_bw()
+% @
+% \caption{Operator selection comparison between n-selection and other selection methods in mutation reduction.  We show only up to 8-selection}
+% \label{fig:xroundsel}
+% \end{figure*}
+%
 

### 2014-03-15 src/conclusion.Rnw
Change Title, Fix spellos

@@
 Our analysis suggests that simple random sampling --- that is, at the
-project level --- works best when compared to more sophesticated schemes of
+project level --- works best when compared to more sophisticated schemes of
 sampling. Further, we also note that random sampling performs better in
@@
 Not only is this method simple and effective, but it is also quite
-stable comapred to some alternatives, with a low standard deviation in
+stable compared to some alternatives, with a low standard deviation in
 effectiveness across projects, for both original and random test suites.

### 2014-03-15 src/introduction.Rnw
fix conflict
Change Title, Fix spellos

@@
 % 1. Describe the problem % 2. State your contributions
-Mutation analysis is a method for evaluating the quality of test-suites. It
+Mutation analysis is a method for evaluating the quality of test suites. It
 involves producing a family of \emph{mutants}, programs with small
@@
 and operator selection was best.
-%{\bf ADG: did it combing random with pelem or pelem with operator???}
 
@@
 be made. We provide the results from running both original project
-human generated test-suites and also automatically generated
+human generated test suites and also automatically generated
 test suites using random testing, increasing the applicability of our
@@
 \item Our recommendations are valid for both testing researchers who
-might be comparing automatically generated test-suites, and software
+might be comparing automatically generated test suites, and software
 testers in real world development working to produce and evaluate manual test suites.
@@
 %      (188 projects) from the open source repository at Github~\cite{github}, using both original and automatically
-%      generated test-suites using Randoop~\cite{randoop} (Section~\ref{sec:methodology}). 
+%      generated test suites using Randoop~\cite{randoop} (Section~\ref{sec:methodology}). 
 %\item It analyses the results and suggest strategies (Section~\ref{sec:results}).
@@
 %(188 projects) from the open source repository at Github~\cite{github}, using both original and automatically
-%generated test-suites using Randoop~\cite{randoop}. Second, as detailed in Section~\ref{sec:analysis}, we
+%generated test suites using Randoop~\cite{randoop}. Second, as detailed in Section~\ref{sec:analysis}, we
 %compare the reduction effectiveness of a large number of random sampling criterias (some of which are novel,

### 2014-03-15 etc/abstract.tex
Fixing the pointed out issues: do/faster/fewer/smarter
Fix unintented %'s
Change Title, Fix spellos
Since we dont provide ranking, remove that portion

@@
 achieve accuracy and mutant reduction similar to operator selection.
-
+%
 %2.Saywhyit’saninterestingproblem
-However, the statistical support for these conclusions has been limited, due to the small number of subject programs investigated.  The best sampling technique is also an open problem.
+However, the empirical support for these conclusions has been limited, due to the small number of subject programs investigated.  The best sampling technique is also an open problem.
 % that can be drawn from the previous
@@
 score as well as the consistency of mutation reduction ratios
-achieved. Our results provide a ranking that can be used to choose an
-appropriate mutation reduction technique by the reduction and level of fidelity to full mutation results required.
+achieved. Our results can be used to choose an appropriate mutation
+reduction technique by the reduction and level of fidelity to full
+mutation results required.
 

### 2014-03-15 src/analysis.Rnw
Fix space requirements

@@
 \begin{table*}
-\begin{minipage}[h]{0.49\linewidth}
+\begin{minipage}[htb]{0.49\linewidth}
 <<results='asis'>>=

### 2014-03-15 src/threats.Rnw
Fix space requirements

@@
 confounding factor in play that affects the relation between the full mutation score and
-sampling mutation score, and any of the noted factors, it might cause our results to be
-either wrong or less applicable.
+sampling mutation score, it might cause our results to be either wrong or less applicable.
 

### 2014-03-15 src/analysis.Rnw
All Alex edits

@@
 For the purposes of comparing between the criteria, we computed the
-correlation between sampled mutation score and full mutation score.
+linear correlation between sampled mutation score and full mutation score.
 Since for most of the sampling criteria, if there are no mutants to
-sample, it probably means there are no mutants generated on the whole,
+sample, it probably means there are no mutants generated,
 we used
@@
 We also compute standard deviation of the mutant reduction, which determines
-the consistency of results. A large amount of standard deviation suggests
+the consistency of results. A large standard deviation suggests
 that the mutant reduction ratio achieved is very much dependent on the
-project. So as a heuristic, we suggest looking at only those methods which
+project. Therefore, as a heuristic, we suggest looking at only those methods which
 have a mean reduction ratio at least twice the standard deviation.
@@
 A few projects did not return any results for some large reduction factors.
-Thus number of valid results from projects is also collected in the result
+Thus the number of valid results from projects is also collected in the result
 tables.

### 2014-03-15 src/discussion.Rnw
update
All Alex edits

--- 2014-03-15 src/discussion.Rnw
@@
 
+% About Randoop and Original
 From our data, we see that for original and generated test suites, the
-mutant reduction ratio and standard deviation was similar for stable strategies
+mutant reduction ratio and standard deviation were similar for stable strategies
 (where the standard deviation of the reduction achieved was less than half
 of the reduction achieved). This suggests that our analysis is equally
-applicable for both generated test suites and original test suites.
+applicable for both original test suites and generated ones.
 
-Analysing the scores achieved further, we note that the accuracy of prediction
+% About Randoop and Original
+Analysing the scores further, we note that the accuracy of prediction
 ($R^2$) achieved by sampling is generally lower for generated test
-suites. Especially, as the fraction of sampling becomes larger the accuracy
-reduces drastically for generated test suites while the accuracy still
-holds good for original test suites
+suites. As the sampling denominator increases, the accuracy
+reduces drastically for generated test suites while correlation remains strong
+for original test suites
 Secondly, we also observe that the multiplier factor $\beta_1$ 
@@
 corresponding to a sampled mutation score for generated test suites would
-be lower than what would be expected from original test suite.
-Secondly, the amount of reduction that can be gained by sampling satisfying
-a given accuracy is lower for generated test suites in comparison with original
-test suites.
+be lower than what would be expected from the original test suite.
+Secondly, the amount of reduction that can be gained by sampling that must reach a given correlation is lower for generated test suites.
+
+% Different sampling strategies
+Considering different sampling strategies, based on their stability and mutation
+reduction achieved, we note that using simple sampling (\textit{sample(x)})
+produced the most stable results. For both generated and original test suites,
+this strategy produced valid results for all different scopes and sampling
+ratios. It also was able to achieve the highest mutation reduction of $72.63$,
+that is only $1.37\%$ of the original mutants were needed to produce a highly
+correlated ($R^2 = 0.97$) mutation score, with minimal deviation
+($\sigma = 6.36$) for original test suites. While the correlation is weaker for
+generated test suites it is still quite strong, with $R^2 = 0.90$
+
+Our \textit{round(x)}, the strategy of ignoring low complexity elements,
+did not pay off, with line scope having a tendency to become unstable and
+inaccurate at high sampling ratios. At very low sampling ratio ($1/64$), the
+strategy with method scope also becomes unstable and inaccurate. On the whole
+\textit{round(x)} did not perform as well as \textit{sample(x)}
+
+The strategy of \textit{ceil(x)} also did not perform well. While the
+results were generally stable, the reduction ratios achieved were lower than
+\textit{sample(x)}, with similar correlations.
+
+For line count strategies, only the external sampling produced
+consistent results, which were again not as good as \textit{round(x)}
+for similar mutation reduction ratios. Secondly, we had hypothesised
+that perhaps coverage was a significant contributor to the accuracy of
+sampled mutation score. However we could find no evidence in support
+of this hypothesis with line, method, class, and project scope showing
+similar accuracy and consistency at similar reduction ratios.
+
+The one per element strategy did not have stable results in general except
+for at the scope of line (at which point it was same as the count-per-element
+strategy).
+
+While the x\% per operator strategy produced consistent results, its
+consistency was not as good as \textit{sample(x)}, and was either on
+par with or worse than \textit{sample(x)} in correlation.
+
+Considering mutation operators, only three operators \textit{NC},
+\textit{RC},and \textit{DC} had consistent results (and only for
+original test suites). The n-selection strategy had high accuracy and
+consistency (though low reduction ratio) until 7-selection (removing
+the seven most numerous operators) for both generated and original
+test suites.  Javalanche did not have a high mutation reduction ratio,
+though it had high correlation for both kinds of test suites. The other
+operator selection methods performed poorly on generated test suites,
+while they had high correlation and reasonable stability on original test
+suites. However, for comparable mutation reduction levels, they all performed
+worse than random sampling strategies.
 
@@
 first is that sampling strategy can predict the final score with very
-minimal loss in accuracy up to a fraction of $\frac{1}{64}$ of the total
-number of mutants (Our experiments suggest up to $70$ times reduction,
+minimal loss up to a fraction of $\frac{1}{64}$ of the total
+number of mutants (our experiments suggest up to $70$ times reduction,
 with a low standard deviation of $6.72$). We did not cut off with the 99\%
-rule as mentioned by Zhang et al.~\cite{zhang2013ase} (Originally proposed
+rule as mentioned by Zhang et al.~\cite{zhang2013ase} (originally proposed
 by Offutt et al.~\cite{offutt1996experimental} for a different measurement),
@@
 
-The second pattern is that fractional sampling based on projects appears
-to be better than that based on classes, which in turn is better than
-methods and lines, with regard to the stability of the result (i.e. low
-standard deviation).  This seems not very visible at lower levels (where
-the reduction fraction is less than 32), but becomes more pronounced as the
-mutant reduction fraction increases.  There seem to exist a hierarchy of
-sampling, where by as sampling becomes more fine grained stability decreases.
-We did not see the pattern found by Zhang et al.~\cite{zhang2013ase} where
-method-based sampling had the highest accuracy. In fact, in our measurements,
-the opposite may be true, with project based sampling getting the highest
-correlation with the final score a majority of the time.
+The second pattern is that fractional sampling based on projects
+appears to be better than that based on classes, which in turn is
+better than methods and lines, with regard to the stability of the
+result (i.e. low standard deviation).  This is not clear at lower
+levels of reduction (more than 1/32), but becomes more pronounced as
+the denominator of the mutant reduction fraction increases.  There
+seems to exist a hierarchy of sampling, whereby as sampling becomes
+more fine grained stability decreases.  We did not observe the pattern
+found by Zhang et al.~\cite{zhang2013ase} where method-based sampling
+had the best correlations. In fact, in our measurements, the opposite
+may be true, with project based sampling having the highest
+correlation with the total mutation score a majority of the time.
 
-The third pattern is that the simplest sampling scheme --- simple random sampling ---
-performs best compared to sampling schemes that tried to provide higher weight
-to specific elements based on specific criteria. More importantly, operator selection
-seems to be generally worse off in predicting the final score than any of the random
-selection schemes.
+The third "pattern" is that the simplest sampling scheme --- simple
+random sampling --- performs best compared to sampling schemes that
+tried to provide higher weight to specific elements based on specific
+criteria. Additionally, operator selection seems to be generally worse
+off in predicting the final mutation score than any of the random selection
+schemes.  In principle, if we could devise sampling methods that
+somehow captured only the most discriminative mutants for programs,
+they might perform better than any of these; our results suggest that
+most schemes that (we assume) aim at this goal do not in fact achieve
+the goal over a large body of programs, and so tend to perform worse
+than simply randomly sampling the whole pool of mutants, which has
+attractive simplicity in the absence of a better strategy.

### 2014-03-15 src/introduction.Rnw
All Alex edits

@@
 Random sampling can perform as well as or better than operator
-selection, in these studies; a strategy of either program elements
-based sample or one combining both program element-based sampling
+selection, in these studies; a strategy of either sampling based on
+program elements or one combining both program element-based sampling
 and operator selection was best.
@@
 operators specific to the language, and are not directly applicable to
-newer languages such as Java. Finally, modern research into the byte
+newer languages such as Java. Finally, due to modern research into the byte
 code based mutation (a \textit{do faster} approach for eliminating
-the compilation step to gain execution speed) operators based on
+the compilation step to gain execution speed), operators based on
 source code modification are no longer applicable, and their
@@
 to 100 KLOC, which allows widely applicable statistical inferences to
-be made. We provide the results from running both original project
-human generated test suites and also automatically generated
-test suites using random testing, increasing the applicability of our
-findings to both testers in traditional development who are interested in applying mutation analysis to suite evaluation and to researchers who seek to compare test suites quickly.
+be made. We provide the results from running both the original
+project's (presumably human-generated) test suites and also
+automatically generated test suites using random testing, increasing
+the applicability of our findings to both testers in traditional
+development who are interested in applying mutation analysis to suite
+evaluation and to researchers who seek to compare test suites quickly to evaluate testing techniques.
+
+One note about our, and other researchers, evaluation criteria is in
+order.  We, like others, use the ability of a sample to correlate well
+to the score over all mutants as a measure of sampling quality.  The
+underlying reason for this is that, while many mutants have little
+ability to distinguish between good and bad test suites, some smaller
+set of mutants show subtle deficiencies in suites that are not clear
+from, say, code coverage.  The full set of mutants obviously contains
+these mutants, and correlating with (rather than exactly matching) the
+full mutation score is a strong indicator that many of these
+discriminatory mutants have been preserved in a sample.
 
@@
 
-\item Our recommendations are valid for both testing researchers who
+\item Our recommendations are useful for both testing researchers who
 might be comparing automatically generated test suites, and software
@@
 \item Most importantly, we find that random sampling strategies perform
-better than operator selection strategies consistently in predicting the
-final mutation score.
+better than operator selection strategies in consistently predicting the
+final mutation score while obtaining stable computational reduction.
 

### 2014-03-15 src/methodology.Rnw
Add x\% selection for operators
Fix citation for wong
Fix space requirements
All Alex edits

@@
 present in the experiments. For this reason we chose a random sample
-of Java projects from Github\cite{github} that use the popular
-maven\cite{maven} build system, following the methodology used by some
-of the authors in an ICSE 2014 paper~\cite{gopinath2014code}. As in
-that work, we utilize two kinds of of test suites: the original test
-suites present in a limited number of projects, and automatically
-generated test suites from Randoop~\cite{randoop}.  Due to limited
-resources, we had to further reduce the programs and test suites to those
-that could finish mutation analysis in 10 minutes. From this set of test
-suites, we sampled 110 suites each for both original and Randoop generated
-test suites. Since there was some overlap between projects with original
-test suites, and those with Randoop test suites, we had 81 unique projects
-each in both sets. The remaining projects had both flavors of test suites.
-% {\bf ADG I have no idea what that last sentence means, really.
-% RG: Fixed}
+of Java projects from Github~\cite{github} that use the popular
+maven~\cite{maven} build system, following the methodology we used
+previously in an ICSE 2014 paper~\cite{gopinath2014code}. As in that
+work, we utilize two kinds of of test suites: the original test suites
+present in a limited number of projects, and automatically generated
+test suites from Randoop~\cite{randoop}.  Due to limited resources, we
+had to further reduce the programs and test suites to those that could
+finish mutation analysis in 10 minutes. From this set of test suites,
+we sampled 110 suites each for both original and Randoop generated
+test suites. Since there was some overlap between projects with
+original test suites, and those with Randoop test suites, we had 81
+unique projects each in both sets. The remaining projects had both
+flavors of test suites.  % {\bf ADG I have no idea what that last
+sentence means, really.  % RG: Fixed}
 
@@
 Our previous research~\cite{gopinath2014code} found that statement coverage
-was highly correlated with mutation coverage for a project. This immediately
+was highly correlated with mutation score for a project. This immediately
 suggests that perhaps choosing one mutant per line may be sufficient to achieve
@@
 
-For the first variant, we applied the x\% sampling to the result of the first
-sampling based on line counts. That is, in the case of methods, we first
-selected \textit{linecount} mutants each from each method, and applied the x\%
-selection to the result of this selection. For e.g for $1/2$ sampling on methods
-if a method had $10$ lines and another had $10$ lines, we sampled $10$ mutants
-from the first, and $20$ mutants from the second, and from the combined $30$
-mutants, we sampled $15$.  For the second variant, we did the sampling in one go,
-where we chose \textit{linecount/x} number of mutants from each program element.
-That is, in the previous example, only $5$ mutants from the first and $10$ mutants
-from the second method would be chosen.
+For the first variant, we applied the x\% sampling to the result of
+the first sampling based on line counts. That is, in the case of
+methods, we first selected \textit{linecount} mutants each from each
+method, and applied the x\% selection to the result of this
+selection. For example, for $1/2$ sampling on methods if one method had
+$10$ lines and another had $20$ lines, we sampled $10$ mutants from
+the first, and $20$ mutants from the second, and from the combined
+$30$ mutants, we sampled $15$.  For the second variant, we did the
+sampling in one go, where we chose \textit{linecount/x} number of
+mutants from each program element.  That is, in the previous example,
+only $5$ mutants from the first and $10$ mutants from the second
+method would be chosen.
 
@@
 Another simple strategy of sampling we experimented with is to just choose
-one mutant per program element, in the order \textit{line},\textit{method},
-\textit{class}.
+one mutant per program element, in the order \textit{line}, \textit{method}, \textit{class}.
+
+\subsubsection{x\% selection per operator}
+This strategy, first suggested by Wong et al.~\cite{wong1995reducing} samples an equal percentage
+of mutants from each operator.
 
@@
 are sensible in C but not in Java programs. For example C compilers tolerate
-removing a return statement --- in Java this causes a compilation error.
+removing a return statement --- but in Java this causes a compilation error.
 Moreover, there were some operators that are not supported by the PIT framework
@@
 \subsubsection{Criteria I}
-For this criteria, we used the two operators \pitcb, and \pitnc which are similar to those given by Wong. We did not have ABS operator available in PIT.
+For this criteria, we used the two operators \pitcb and \pitnc which are similar to those given by Wong. We did not have ABS operator available in PIT.
 \subsubsection{Criteria II}
@@
 \subsubsection{Criteria IV}
-By Namin et al. \pitin, \pitm, \piti, \pitnc. Many of operators were not applicable in Java and some were not available in PIT like IndVarBitNeg.
+Namin et al. used \pitin, \pitm, \piti, \pitnc. Many of these operators were not applicable in Java, and some were not available in PIT (e.g. IndVarBitNeg).
 \subsubsection{Criteria V}
 For this criteria, we utilized the approach suggested by
-Offutt et al.~\cite{offutt1993experimental} where by most numerous operators
+Offutt et al.~\cite{offutt1993experimental} where the most numerous operators
 are discarded at each step.
 
-\subsubsection{Statement Deletion:}
-\label{subsec:stmtdel}
-The basic statement deletion was modeled on the work by Deng et
-al.~\cite{deng2013empirical}. The operations on single statements was modeled
-using \pitvmc, \pitnvmc, \pitcc, \pitemv, \pitri
-for simple statements, and using \pitrc for control structures,
-which replaced the boolean condition with false, resulting in removal of
-the block of statements. The operator for return values was modeled using
-\pitrv, which is similar.  The operators for \textit{while,for},
-and \textit{if} statements were modeled using \pitdc,
-which replaced the boolean condition with true, which removed the effect
-of conditional. The \textit{switch} statement deletion was modeled using
-\pitrs which replaced the first 100 labels with default label,
-resulting in the switch element getting deleted. (Due to the constraints
-of the architecture of PIT only the first 100 labels were replaced). The
-\textit{try catch} was not necessary at bytecode level.  Finally, to get an
-accurate estimation of the effect of true statement deletion, we grouped
-the mutants by line, and considered a single virtual mutant (That is, the
-total number of mutants is equal to the total number of lines). Further,
+\subsubsection{Statement Deletion:} \label{subsec:stmtdel} The basic
+statement deletion was modeled on the work by Deng et
+al.~\cite{deng2013empirical}. The operations on single statements were
+modeled using \pitvmc, \pitnvmc, \pitcc, \pitemv, and \pitri for
+simple statements, and using \pitrc for control structures, which
+replaced the boolean condition with false, resulting in removal of the
+block of statements. The operator for return values was modeled using
+\pitrv, which is similar.  The operators for \textit{while},
+\textit{for}, and \textit{if} statements were modeled using \pitdc,
+which replaced the boolean condition with true, which removed the
+effect of conditional. The \textit{switch} statement deletion was
+modeled using \pitrs which replaced the first 100 labels with a
+\textit{default} label, resulting in the switch element being
+deleted. Due to the constraints of the architecture of PIT only the
+first 100 labels were replaced. Deleting \textit{try/catch} was not
+necessary at bytecode level.  Finally, to get an accurate estimation
+of the effect of true statement deletion, we grouped the mutants by
+line, and considered a single virtual mutant (that is, the total
+number of mutants is equal to the total number of lines). Further,
 killing any mutant from a line resulted in marking the virtual mutant
-for that line as killed. This gave us the mutation score for the virtual
-statement deletion operator.  We note that the approximation of simple
-statement deletion, especially when arithmetic operators are involved is not
-complete. However, as seen in Figure~\ref{fig:op}, the number of mutants
-produced by \pitm operator is very small. We also note that our
-approximation does not account for the increase in ease of detection when
-multiple mutations are combined together due to coupling effect. This also
-means that not all the lines may be mutated since there may be no applicable
-operators. However, given the constraints of a bytecode based mutation system,
-we believe that our procedure is reasonable. An interesting point is that
-by this procedure statement deletion is no longer a simple mutation and qualifies
-as a higher order mutation operator. In fact, the procedure we outlined can
-be used in general to judge the effectiveness of a higher order operator from
-the results of first order mutation operators that makeup the higher order
-mutant in question.
+for that line as killed. This gave us the mutation score for the
+virtual statement deletion operator.  We note that the approximation
+of simple statement deletion, especially when arithmetic operators are
+involved, is not complete. However, as seen in Figure~\ref{fig:op},
+the number of mutants produced by \pitm operator is very small. We
+also note that our approximation does not account for the increase in
+ease of detection when multiple mutations are combined together due to
+the coupling effect. This also means that not all the lines may be
+mutated ,since there may be no applicable operators. However, given
+the constraints of a bytecode based mutation system, we believe that
+our procedure is reasonable. An interesting point is that using this
+procedure statement deletion is no longer a simple mutation and
+qualifies as a higher order mutation operator. In fact, the procedure
+we outlined can be used in general to judge the effectiveness of a
+higher order operator from the results of the first order mutation
+operators that together compose the higher order mutant.

### 2014-03-15 src/results.Rnw
Fix space requirements
All Alex edits

@@
 
-Our results for random sampling over program elements using $sample(x)$
-are given in Table~\ref{tbl:xselsample}. The result of the variation using
-$round(x)$ is given in Table~\ref{tbl:xselround} and that using
-$ceil(x)$ is given in Table~\ref{tbl:xselceil}.
-The first column in each table provides the scope of sampling i.e. if it was
-done per class, per method, per line etc. The second column provides the
-fraction involved.  The third column contains the $R^2$ value obtained between
-the mutation score of the sampling criteria used and the full mutation score.
-The fourth column contains the mutant reduction factor. This is the average of
-total mutants produced divided by the number of mutants sampled by the criteria.
-The fifth column contains the standard deviation of the same. A few of the projects
-did not return any value for certain sampling criteria for particular mutation
-reduction fractions. The sixth column contains the number of projects that
-actually had valid values for the criteria being considered. The seventh column
-is the average multiplier between the sampled mutation score and the full mutation
-score.
+Our results for random sampling over program elements using
+$sample(x)$ are given in Table~\ref{tbl:xselsample}. The result of the
+variation using $round(x)$ is given in Table~\ref{tbl:xselround} and
+that using $ceil(x)$ is given in Table~\ref{tbl:xselceil}.  The first
+column in each table provides the scope of sampling: per class, per
+method, or per line. The second column provides the fraction involved.
+The third column contains the $R^2$ value obtained between the
+mutation score of the sampling criteria used and the full mutation
+score.  The fourth column contains the mutant reduction factor. This
+is the average of total mutants produced divided by the number of
+mutants sampled by the criteria.  The fifth column contains the
+standard deviation of the same. A few of the projects did not return
+any value for certain sampling criteria for particular mutation
+reduction fractions. The sixth column contains the number of projects
+that actually had valid values for the criteria being considered. The
+seventh column is the average multiplier between the sampled mutation
+score and the full mutation score.
 
-Table~\ref{tbl:lcountl} provides the results for line count criteria where the
-sampling was conducted outside program element, and Table~\ref{tbl:lcountw} contains
-the results for line count criteria where the sampling was conducted inside the
-program element. Similarly Table~\ref{tbl:onesel} contains the results for
-the criteria of one mutant per program element.
+Table~\ref{tbl:lcountl} provides the results for line count criteria
+where the sampling was conducted after combining program elements, and
+Table~\ref{tbl:lcountw} contains the results for line count criteria
+where the sampling was conducted inside each program
+element. Similarly Table~\ref{tbl:onesel} contains the results for the
+criteria of one mutant per program element.
 
-The same data (only for original test suite) is visualized in Figure~\ref{fig:xroundsel}.
-
-Finally Table~\ref{tbl:operators} contains the results when only a single operator
+Finally, Table~\ref{tbl:operators} contains the results when only a single operator
 is used, and Table~\ref{tbl:opsel} contains the results for specific operator
-selection criteria. The first column in these two tables contain the particular
-operator or operator selection applied. Second column contains the
-correlation coefficient $R^2$ with the final mutation score. Third column contains
-the mean mutant reduction ratio, and fourth contains the standard deviation of the
+selection criteria. The first columns in these two tables contain the particular
+operator or operator selection applied. The second column contains the
+correlation coefficient $R^2$ with the final mutation score. The third column contains
+the mean mutant reduction ratio, and the fourth contains the standard deviation of the
 mutant reduction ratio achieved. The fifth column contains the number of projects
@@
 strategies~\cite{offutt1993anexperimental}. We used the order of operators
-determined from Figure~\ref{fig:op} for this purpose.
+determined from Figure~\ref{fig:op} for this purpose. The complete data
+(only for original test suites) is visualized in Figure~\ref{fig:fullimgsize}.
 

### 2014-03-15 src/paper.Rnw
Fix space requirements
update

@@
 
-o.stats.sel.xop$scope  <- 'op'
+o.stats.sel.xop$scope  <- 'operator'
 o.stats.sel.xop$sampling  <- gsub('_per_op','',gsub('OP[.]1x','1/', o.stats.sel.xop$operator))
-r.stats.sel.xop$scope  <- 'op'
+r.stats.sel.xop$scope  <- 'operator'
 r.stats.sel.xop$sampling  <- gsub('_per_op','',gsub('OP[.]1x','1/', r.stats.sel.xop$operator))
@@
 @
-\FloatBarrier
+%\FloatBarrier
+\clearpage

### 2014-03-15 src/methodology.Rnw
Fix the spaces after pit ops

@@
 \subsubsection{Criteria II}
-We used the operators given by Offutt et al. \pitin, \pitm, \pitcb, \pitnc. We did not have LCR available in PIT.
+We used the operators given by Offutt et al. \Pitin, \Pitm, \Pitcb, \Pitnc. We did not have LCR available in PIT.
 \subsubsection{Criteria III}
-Those given by Javalanche \pitnc, \pitvmc, \pitnvmc, \pitm, \pitic, \pitemv. 
+Those given by Javalanche \Pitnc, \Pitvmc, \Pitnvmc, \Pitm, \Pitic, \Pitemv. 
 \subsubsection{Criteria IV}
-Namin et al. used \pitin, \pitm, \piti, \pitnc. Many of these operators were not applicable in Java, and some were not available in PIT (e.g. IndVarBitNeg).
+Namin et al. used \Pitin, \Pitm, \Piti, \Pitnc. Many of these operators were not applicable in Java, and some were not available in PIT (e.g. IndVarBitNeg).
 \subsubsection{Criteria V}
@@
 al.~\cite{deng2013empirical}. The operations on single statements were
-modeled using \pitvmc, \pitnvmc, \pitcc, \pitemv, and \pitri for
+modeled using \Pitvmc, \Pitnvmc, \Pitcc, \Pitemv, and \Pitri for
 simple statements, and using \pitrc for control structures, which
@@
 block of statements. The operator for return values was modeled using
-\pitrv, which is similar.  The operators for \textit{while},
-\textit{for}, and \textit{if} statements were modeled using \pitdc,
+\Pitrv, which is similar.  The operators for \textit{while},
+\textit{for}, and \textit{if} statements were modeled using \Pitdc,
 which replaced the boolean condition with true, which removed the

### 2014-03-15 src/discussion.Rnw
Fix high/low

@@
 did not pay off, with line scope having a tendency to become unstable and
-inaccurate at high sampling ratios. At very low sampling ratio ($1/64$), the
+inaccurate at low sampling ratios. At very low sampling ratio ($1/64$), the
 strategy with method scope also becomes unstable and inaccurate. On the whole

### 2014-03-15 src/discussion.Rnw
Fixup accuracy/correlation

@@
 ($R^2$) achieved by sampling is generally lower for generated test
-suites. As the sampling denominator increases, the accuracy
+suites. As the sampling denominator increases, the correlation
 reduces drastically for generated test suites while correlation remains strong
@@
 for similar mutation reduction ratios. Secondly, we had hypothesised
-that perhaps coverage was a significant contributor to the accuracy of
-sampled mutation score. However we could find no evidence in support
-of this hypothesis with line, method, class, and project scope showing
-similar accuracy and consistency at similar reduction ratios.
+that perhaps coverage was a significant contributor to having a high
+correlation with the full mutation score. However we could find no
+evidence in support of this hypothesis with line, method, class, and
+project scope showing similar correlation and consistency at similar
+reduction ratios.
 
@@
 \textit{RC},and \textit{DC} had consistent results (and only for
-original test suites). The n-selection strategy had high accuracy and
+original test suites). The n-selection strategy had high correlation and
 consistency (though low reduction ratio) until 7-selection (removing

### 2014-03-15 src/discussion.Rnw
Obeying space requirements (10 pages without reference)

@@
 consistent results, which were again not as good as \textit{round(x)}
-for similar mutation reduction ratios. Secondly, we had hypothesised
-that perhaps coverage was a significant contributor to having a high
+for similar reduction ratios. Secondly, we had hypothesised
+that coverage was a significant contributor to having a high
 correlation with the full mutation score. However we could find no
@@
 consistency was not as good as \textit{sample(x)}, and was either on
-par with or worse than \textit{sample(x)} in correlation.
+par with or worse than \textit{sample(x)} in $R^2$.
 
@@
 test suites.  Javalanche did not have a high mutation reduction ratio,
-though it had high correlation for both kinds of test suites. The other
+though it had high $R^2$ for both kinds of test suites. The other
 operator selection methods performed poorly on generated test suites,
@@
 result (i.e. low standard deviation).  This is not clear at lower
-levels of reduction (more than 1/32), but becomes more pronounced as
-the denominator of the mutant reduction fraction increases.  There
-seems to exist a hierarchy of sampling, whereby as sampling becomes
+levels of reduction ($< 1/32$), but becomes more pronounced for lower
+ratios. There seems to exist a hierarchy of sampling, whereby as sampling becomes
 more fine grained stability decreases.  We did not observe the pattern
@@
 may be true, with project based sampling having the highest
-correlation with the total mutation score a majority of the time.
+$R^2$ a majority of the time.
 

### 2014-03-15 src/introduction.Rnw
Obeying space requirements (10 pages without reference)

@@
 high computational cost.  The set of simple mutants for even a
-moderate sized program can be very large, which renders mutation
-analysis prohibitively time consuming.
+moderate sized program can be very large, making mutation
+analysis prohibitivey time consuming.
 
@@
 mutants instead of applying the whole set of mutation
-operators~\cite{offutt1993anexperimental,untch2009onreduced}.  As an
-example, recent work suggests that using statement deletion only can
-provide effective mutation analysis~\cite{untch2009onreduced}.
+operators~\cite{offutt1993anexperimental,untch2009onreduced}.
+Recent work suggests that using statement deletion only can
+be effective~\cite{untch2009onreduced}.
 
@@
 from, say, code coverage.  The full set of mutants obviously contains
-these mutants, and correlating with (rather than exactly matching) the
+these mutants, and correlating with (rather than matching) the
 full mutation score is a strong indicator that many of these
@@
 sampling strategies include some that were suggested by other
-researchers, as well as a few novel strategies that have not been
-previously considered.
+researchers, as well as a few novel strategies not previously considered.
 
@@
 might be comparing automatically generated test suites, and software
-testers in real world development working to produce and evaluate manual test suites.
+testers in real world working to produce and evaluate manual test suites.
 
@@
 
-Our data is available for replication~\cite{data}\footnote{Available on publication}.
+Our data will be available for replication on publication~\cite{data}
+%\footnote{Available on publication}.
 

### 2014-03-15 src/methodology.Rnw
Obeying space requirements (10 pages without reference)

@@
 
-When the number of mutants to be chosen was not a whole number, we used
-the formula suggested by Zhang et a.~\cite{zhang2013ase}, and used the
+When the number of mutants sampled was not a whole number, we used
+the formula by Zhang et a.~\cite{zhang2013ase}, using the
 decimal part to select a mutant with that probability.
@@
 methods, we first selected \textit{linecount} mutants each from each
-method, and applied the x\% selection to the result of this
-selection. For example, for $1/2$ sampling on methods if one method had
-$10$ lines and another had $20$ lines, we sampled $10$ mutants from
-the first, and $20$ mutants from the second, and from the combined
+method, and applied the x\% selection to this result.
+For example, for $1/2$ sampling on methods if one method had
+$10$ lines and another had $20$, we sampled $10$ mutants from
+the first, and $20$ from the second, and from the combined
 $30$ mutants, we sampled $15$.  For the second variant, we did the
@@
 \subsubsection{Criteria IV}
-Namin et al. used \Pitin, \Pitm, \Piti, \Pitnc. Many of these operators were not applicable in Java, and some were not available in PIT (e.g. IndVarBitNeg).
+Namin et al. used \Pitin, \Pitm, \Piti, \Pitnc. Many of these operators were not applicable in Java, and some not in PIT.
 \subsubsection{Criteria V}

### 2014-03-15 src/related.Rnw
updates: methodology related
For related: got the message, for methodology, fixed
the problems pointed out.
Obeying space requirements (10 pages without reference)

@@
 \textit{do faster} approaches include mutant schema generation methods,
-code patching techniques, and byte code based mutation analysis systems like PIT.
+code patching etc.
 
@@
 Fortran. Mathur~\cite{mathur1991performance,wong1995reducing}
-suggested constrained mutation where only two mutation operators
+suggested constrained mutation where only two operators
 were used.%, which were felt to be better than using the entire set.
@@
 is true for smaller subjects.
-{\bf ADG:  not having defined mutagen/mtuation sampling this is not easy for most readers to understand.
-also we switch between "sampling" and "random selection" a lot, I tried to make consistent.}
+% {\bf ADG:  not having defined mutagen/mtuation sampling this is not easy
+% for most readers to understand.  also we switch between "sampling" and
+% "random selection" a lot, I tried to make consistent.  }
+% RG: Got it.
 

### 2014-03-15 src/results.Rnw
Obeying space requirements (10 pages without reference)

@@
 operator or operator selection applied. The second column contains the
-correlation coefficient $R^2$ with the final mutation score. The third column contains
+coefficient $R^2$ with the final mutation score. The third column contains
 the mean mutant reduction ratio, and the fourth contains the standard deviation of the
@@
 All the \textit{N-sel} rows are the results of N-selective operator selection
-strategies~\cite{offutt1993anexperimental}. We used the order of operators
-determined from Figure~\ref{fig:op} for this purpose. The complete data
+strategies~\cite{offutt1993anexperimental}, using the order of operators
+from Figure~\ref{fig:op}. The complete data
 (only for original test suites) is visualized in Figure~\ref{fig:fullimgsize}.

### 2014-03-15 src/threats.Rnw
Obeying space requirements (10 pages without reference)

@@
 While we have taken every care to ensure that our results are valid, and to eliminate the
-effects of random noise in experiments, our results are subject to the following threats
+effects of random noise, our results are subject to the following threats
 to validity.

### 2014-03-16 src/introduction.Rnw
Fix spellos

@@
 moderate sized program can be very large, making mutation
-analysis prohibitivey time consuming.
+analysis prohibitively time consuming.
 
@@
 operators~\cite{offutt1993anexperimental,untch2009onreduced}.
-Recent work suggests that using statement deletion only can
-be effective~\cite{untch2009onreduced}.
+Recent work suggests that using statement deletion alone can
+be an effective approach~\cite{untch2009onreduced}.
 
@@
 
-%Mathur \cite{} reduced the number of mutagens in Mothra \cite{Mothra} by omitting two operators.
-%Offutt et al.\cite{offutt1993anexperimental} further omitted upto six oprators from the
-%mutagens and observed negligible loss of effectiveness in mutation analysis.
-%Unch\cite{untch2009onreduced} and more recently Deng et al.\cite{deng2013empirical} suggest
-%that using only statement deletion operator gives a close approximation of original mutation score.
-
-%While some studies try to
-%find the \emph{sufficient} subset of mutagens, like\cite{siami2008sufficient}, others
-%have suggested that \emph{random} selection of mutants works as fine, e.g. \cite{zhang2010operator}.
-%Some approaches combine the selective mutation selection and random selection, e.g. \cite{zhang2013ase}.
-
-% {Amin: I am not a fan of this ~\cite{hussain08mutation} }
-%Finally, clustering of mutants~\cite{hussain08mutation} based on similar test cases has also
-%been used successfully for mutant reduction. These are explained more in depth in Section~\ref{sec:related}
-
 Recent work~\cite{zhang2010icse,zhang2013ase} has investigated the
@@
 Random sampling can perform as well as or better than operator
-selection, in these studies; a strategy of either sampling based on
+selection, in these studies; and a strategy of either sampling based on
 program elements or one combining both program element-based sampling
@@
 operators specific to the language, and are not directly applicable to
-newer languages such as Java. Finally, due to modern research into the byte
-code based mutation (a \textit{do faster} approach for eliminating
+newer languages such as Java. Finally, with bytecode based mutation
+engines like PIT~\cite{pitest} and Javalanche~\cite{javalanche}
+(a \textit{do faster} approach for eliminating
 the compilation step to gain execution speed), operators based on
@@
 
-%The research concludes in Section~\ref{sec:conclusion}.
-
 \begin{itemize}
@@
 than previous studies. We compare with respect to the predictive power
-(correlation) with the full mutation score, expected mutant reduction,
+(correlation with the full mutation score), expected mutant reduction,
 and the stability of the amount of mutant reduction expected. Our
@@
 %\footnote{Available on publication}.
-
-%We make the following contributions:
-%\begin{itemize}
-%\item We compare a large number of mutation sampling and selection strategies (Section~\ref{sec:analysis}).
-%\item It seek sto improve the statistical confidence in our results by utilizing a much larger sample of projects
-%      (188 projects) from the open source repository at Github~\cite{github}, using both original and automatically
-%      generated test suites using Randoop~\cite{randoop} (Section~\ref{sec:methodology}). 
-%\item It analyses the results and suggest strategies (Section~\ref{sec:results}).
-%\end{itemize}
-
-%Our contributions in this paper are the following. First, as described in Section~\ref{sec:methodo%logy},
-%we seek to improve the statistical confidence in our results by utilizing a much larger sample of projects
-%(188 projects) from the open source repository at Github~\cite{github}, using both original and automatically
-%generated test suites using Randoop~\cite{randoop}. Second, as detailed in Section~\ref{sec:analysis}, we
-%compare the reduction effectiveness of a large number of random sampling criterias (some of which are novel,
-%and some that has been proposed by other researchers), and a some of the common operator selection
-%criterias proposed in literature using statistical analysis. This provides us with insight for choosing
-%mutation reduction techniqus according to the trade-offs in accuracy, and reduction ratios that a tester
-%is willing to make for their specific requirements. This is detailed in Section~\ref{sec:results}.
-
-%Our conclusion and recommendation for practicing testers are provided in Section~\ref{sec:conclusion}.
-
-% \begin{comment}
-% Order of most fertile operators for N-selective operator selection.
-% NON_VOID_METHOD_CALLS
-% NEGATE_CONDITIONALS
-% REMOVE_CONDITIONALS
-% DELETE_CONDITIONALS
-% RETURN_VALS
-% INLINE_CONSTS
-% CONSTRUCTOR_CALLS
-% EXPERIMENTAL_MEMBER_VARIABLE
-% VOID_METHOD_CALLS
-% MATH
-% CONDITIONALS_BOUNDARY
-% INCREMENTS
-% REMOVE_INCREMENTS
-% RMSWITCH
-% EXPERIMENTAL_SWITCH
-% INVERT_NEGS
-%
-% \end{comment}
-%
-% NON_VOID_METHOD_CALLS VOID_METHOD_CALLS CONSTRUCTOR_CALLS
-% NEGATE_CONDITIONALS REMOVE_CONDITIONALS DELETE_CONDITIONALS CONDITIONALS_BOUNDARY
-% RETURN_VALS INLINE_CONSTS EXPERIMENTAL_MEMBER_VARIABLE
-% MATH INCREMENTS REMOVE_INCREMENTS INVERT_NEGS
-% RMSWITCH EXPERIMENTAL_SWITCH

### 2014-03-16 src/related.Rnw
Fix spellos

@@
 These were categorized by Offutt and Untch~\cite{offutt2001mutation}
-into three approaches: do \textit{fewer}, \textit{smarter}, or \textit{faster}.
-The fewer approaches includes selective mutation and mutant sampling;
-weak mutation, parallelization of mutation analysis, and space/time trade-offs
+into three approaches: do \textit{fewer}, \textit{smarter}, and \textit{faster}.
+The \textit{do fewer} approaches includes selective mutation and mutant sampling,
+while weak mutation, parallelization of mutation analysis, and space/time trade-offs
 are grouped under the umbrella of \textit{do smarter}. Finally
@@
 al.~\cite{offutt1993experimental} using the Mothra~\cite{Mothra}
-mutation operators for
-Fortran. Mathur~\cite{mathur1991performance,wong1995reducing}
+mutation operators for Fortran. Mathur~\cite{mathur1991performance,wong1995reducing}
 suggested constrained mutation where only two operators
 were used.%, which were felt to be better than using the entire set.
-
-% Operator Selection also assumes that fault detection ability of some operators
-% are higher than others, and hence some operators should have higher weight
-% than others. ~\cite{wong1997comparison}
 
@@
 with operator selection using just two mutation operators, and found that both
-achieved similar accuracy and reduction (80\%). This study was conducted on
-five small programs in C and Fortran.
-
-Some studies have tried to find set of \emph{sufficient mutation
-operators} that reduce the cost of mutation but maintain correlation
-with the full mutation score. Offutt~\cite{offutt1993experimental}
-suggested an $n$-selective approach with step-by-step removal of
-mutation operators that produced the largest number of mutants.
+achieved similar accuracy and reduction (80\%).
 
@@
 
-Barbosa et. al.\cite{barbosa2001toward} provide a set of guidelines
-for selecting such mutation operators. Namin et
-al.\cite{namin2006finding,siami2008sufficient} formulate the problem
-as a variable reduction problem, and apply statistical
-approaches. They found a subset of 28 operators out of 108 operators that are
-sufficient.
-
-Using only the statement deletion operator was first suggested by
-Untch~\cite{untch2009onreduced}, who found that it correlated ($R^2 =
-0.97$) with the full mutation score better than other operator
-selection methods, while generating the smallest number of mutants.
-This was further reinforced by Deng et al.~\cite{deng2013empirical}
-who defined deletion for different language elements, and found that
-an accuracy of 92\% is achieved while reducing the number of mutants
-by 80\%.
-
-Zhang et al.~\cite{zhang2010operator} compares operators based mutant
+Zhang et al.~\cite{zhang2010operator} compared operators based mutant
 selection techniques proposed in a set of
 papers~\cite{barbosa2001toward,siami2008sufficient,offutt1996anexperimental}
-to random mutant sampling.  They find that none of the selection
+to random mutant sampling. They found that none of the selection
 techniques are superior to random sampling, with the same number of
-mutants. They also find that equal mutation sampling is more effective
-for larger subjects compared to equal mutagen sampling and the reverse
-is true for smaller subjects.
-% {\bf ADG:  not having defined mutagen/mtuation sampling this is not easy
-% for most readers to understand.  also we switch between "sampling" and
-% "random selection" a lot, I tried to make consistent.  }
-% RG: Got it.
+mutants. They also found that uniform sampling of mutations is more effective
+for larger subjects compared to equal sampling of mutation operators
+and the reverse is true for smaller subjects.
 
@@
 (99\%) with full mutation score, while sampling even fewer mutants has
-good potential for retaining high accuracy. They investigated 8
-sampling strategies on top of operator-based mutant selection and
-found that sampling strategies based on program components (methods in
-particular) performed best.
+good potential for retaining a high accuracy of prediction.
+They investigated eight sampling strategies on top of operator-based mutant
+selection and found that sampling strategies based on program components
+(methods in particular) performed best.
 
-%The idea is that normal mutation has quadratic complexity on variable references while eliminatng the most
-%fecund mutagens (SVR and ASR) achieves linear complexity on program size, while still approximating the full
-% mutation score closely. They propose N-selective mutation which avoids N most fertile mutagens.
-%Wong \cite{wong1995reducing} compares the effect of x\% mutation selection, and abs/ror constrained mutation.
-%According to Wong, this is different from selective mutation in that only the most fecund operators
-%are included rather than excluded. He finds that there is no evidence to suggest one over the other.
-% Offutt\cite{offutt1993experimental} does not compare the effectivenss of selective mutation with x\% mutation.
-% He also defines the concept of {\it operator strength} for an operator, which is defined as the total number
-% of mutants that are killed by test data that is generated to kill only the mutants generated by that operator.
-% He further posits that the mutagens with greatest strength may be the most useful ones. %(test data generated
-% to eliminate variants of one operator may remove the mutants of other kinds too.)
-%This is taken up later by Mresa\cite{mresa1999efficiency} et al. who used the cost of detection of mutants as
-%a means of selection, and uses it to define another set of operators (san, aor, sdl, ror, uoi). They %also find
-%that if very high mutation score close to 100\% is required, x\% selective mutation is better than operator selection,
-%and conversely for less stringent scores, operator selection would be better if %const of mutant is considered.
+Some studies have tried to find the set of \emph{sufficient mutation
+operators} that reduce the cost of mutation but maintain correlation
+with the full mutation score. Offutt et al.~\cite{offutt1993experimental}
+suggested an $n$-selective approach with step-by-step removal of operators
+with most numerous mutations. Barbosa et al.\cite{barbosa2001toward}
+provided a set of guidelines for selecting such mutation operators.
+Namin et al.\cite{namin2006finding,siami2008sufficient} formulated
+the problem as a variable reduction problem in statistics, and
+found that just 28 out of 108 operators in Proteum were sufficient.
 
-%Offutt\cite{offutt1996anexperimental} following the previous paper\cite{offutt1993experimental} compares the
-% effectiveness of selecting different operators. He divides the total operators into operand, operation, and
-% statement categories, with es-selective avoiding operands, rs-selective avoiding operations, and re-selective
-% avoiding statements, and e-selective only operations. He finds that using only operation based mutation operators
-%  (numbering 5) is sufficient for close approximation of full mutation score. He suggests that the reason they are
-%   effective is that most statements contain operators. He further posits that another reason is the amount of semantic
-%change accomplished by an operator, and perhaps the most interesting ones are those that produce the smallest semantic difference.
-% Replacement of Operand , Statement modification, Expression Modification: modify operators, ES-selective : not using
-% operand, RS-Selective: not using expression, RE-Selective: not uinsg statement, E-selective : only expression..
-
-%Unch\cite{untch2009onreduced} suggested using a single mutagen statement deletion. He compares the statement deletion
-% with other selective mutagen sets, and finds statement deletion operator to provide the best prediction of original mutation score ($R^2 = 0.97$)
-%This was carried forward by Deng et al\cite{deng2013empirical}, (according to whom, random sampling was weak when it was
-%made low enough for appreciable mutant savings). They realize a mean mutation score of 92\% for adequate test suites with
-% SDL alone, and generating a saving of 81\% in the number of mutants, and 41\% fewer equivalent mutants.
+Using only the statement deletion operator was first suggested by
+Untch~\cite{untch2009onreduced}, who found that it had the highest
+correlation ($R^2 = 0.97$) with the full mutation score compared to
+other operator selection methods, while generating the smallest number of
+mutants.  This was further reinforced by Deng et al.~\cite{deng2013empirical}
+who defined deletion for different language elements, and found that an
+accuracy of 92\% is achieved while reducing the number of mutants by 80\%.
 
@@
 al.~\cite{zhang2013ase}. We extend the scope of their study with a
-much wider range of mutation approches and base our results on a large
+much wider range of mutation approaches and base our results on a much larger
 set of real-world projects.
-
-% Baseline : x\% from selected set
-% MOP : x\% from each mutagen
-% for these, it is sampled from operator based selected set.
-% PLEm : x\% from inside the same program element.
-% PLE + MOP: sample x\% from same mutagen from same element.
-
-% Empirical Evaluation of the Statement Deletion Mutation Operator : Offutt
-
-%\subsection{Execution Reduction}
-
-%Weak mutation, devised by Howden \cite{howden1982weak}, considers a mutant as detected, if
-%the states of program after the mutated statement in mutant and the original
-%program differ. Several oher studies have refined the idea theoretically \cite{horgan1990weak}and
-%observed its effectiveness emperically\cite{offutt1994empirical,Offutt:1991:SWM:120807.120826}.
-
-%Some studies have utlized parallel computation to enhance the execution time of
-%the mutation testing \cite{}. Others have used custom built compilers and interpretors \cite{}
-%to reduce the overall compile time in mutation testing \cite{}.

### 2014-03-16 src/discussion.Rnw
.

@@
-\section{Discussion}
+section{Discussion}
 \label{sec:discussion}
@@
 % About Randoop and Original
-Analysing the scores further, we note that the accuracy of prediction
+Analyzing the scores further, we note that the accuracy of prediction
 ($R^2$) achieved by sampling is generally lower for generated test
@@
 consistent results, which were again not as good as \textit{round(x)}
-for similar reduction ratios. Secondly, we had hypothesised
+for similar reduction ratios. Secondly, we had hypothesized
 that coverage was a significant contributor to having a high

### 2014-03-16 src/methodology.Rnw
update caption
Fix spellos and such

@@
 @
-\caption{The relative contribution of mutation operators in terms of fraction of mutants generated and detected.
-The blue shade represent detected mutants, while black represents total mutants.}
+\caption{The relative contribution of mutation operators in terms of fraction of mutants produced and detected.
+The produced mutants are shown with black outline while detected mutants have blue border and shade.}
 \label{fig:op}
@@
 finish mutation analysis in 10 minutes. From this set of test suites,
-we sampled 110 suites each for both original and Randoop generated
+we sampled 107 suites each for both original and Randoop generated
 test suites. Since there was some overlap between projects with
-original test suites, and those with Randoop test suites, we had 81
-unique projects each in both sets. The remaining projects had both
-flavors of test suites.  % {\bf ADG I have no idea what that last
-sentence means, really.  % RG: Fixed}
+original test suites, and those with generated test suites, we had 81
+unique projects each in both sets. The remaining 26 projects had both
+flavors of test suites.
 
 We ran mutation analysis on this set of projects using
-PIT\cite{pitest}. However, since the operators provided by PIT are limited,
-we extended PIT to provide newer operators that are similar to operators
-provided by other mutation systems. The set of operators that we used
-is provided in Table~\ref{tbl:pitop}. Figure~\ref{fig:op} which shows both the
-distribution of mutants and the relative detection rates of each
-mutation operator for our projects. In the figure, there are two box-plots corresponding
-to each mutation operator on the Y-axis. The black box represents the
-relative frequency of the particular mutation operator in the total mutants
-\textit{generated}. For example for projects in the Randoop set, the
-operator \pitnvmc contributed about 34\% of the total number of mutants
+PIT\cite{pitest}. However, since the operators provided by PIT are
+limited, we extended PIT to provide newer operators that are similar to
+operators provided by other mutation systems. The set of operators that
+we used is provided in Table~\ref{tbl:pitop}. Figure~\ref{fig:op} shows
+both the distribution of mutants and the relative detection rates of each
+mutation operator for our projects. In the figure, there are two box-plots
+corresponding to each mutation operator on the Y-axis. The black box represents
+the relative frequency of the particular mutation operator in the total
+mutants \textit{produced}. For example, for projects in the (Randoop) generated set,
+the operator \pitnvmc contributed about 34\% of the total number of mutants
 produced while \pitrv contributed about 7\%. Similarly, the blue shaded
@@
 
-For a detailed description of each mutant type, please see~\cite{pitmut}.
+For a detailed description of each mutant type, please refer to PIT documentation~\cite{pitmut}.
 PIT was also modified to provide random selection of mutants according
@@
 We used several different sampling criteria, some of which has been suggested
-in the literature before, some of which are variants of previously suggested
-criteria, and some of which have not been used before.  For each sampling
+in the literature before, some which are variants of previously suggested
+criteria, and a few novel ones.  For each sampling
 criteria, we sampled mutants on a decreasing power scale, sampling
-\textit{1, 1/2, 1/4, 1/8, 1/16, 1/64} of the total mutants.
+\textit{1/2, 1/4, 1/8, 1/16, 1/32, 1/64} of the total mutants.
 
@@
 
-\subsubsection{Sampling over program elements (and variations)}
+\subsubsection{Sampling over program elements and variants}
 Following the suggestion of Zhang et al.~\cite{zhang2013ase}, we
@@
 
-When the number of mutants sampled was not a whole number, we used
-the formula by Zhang et a.~\cite{zhang2013ase}, using the
-decimal part to select a mutant with that probability.
-
-Next, we modified this criteria slightly, and instead of choosing a
-mutant with probability equal to the decimal part, we applied
-\textit{round(sample)} to round it to the nearest whole number. We
-used this as the number of samples to be chosen from the
-population. Our aim was to \emph{remove} elements that were too simple. That
+We used the formula by Zhang et al.~\cite{zhang2013ase},
+\[sample(x) = floor (x + random(0..1))\]
+to correctly sample decimal numbers.
+Next, we modified this criteria slightly, and instead of
+\textit{sample()} which uses probability to manage the decimal numbers,
+we applied \textit{round()} to obtain the nearest whole number, which
+was used as the number of samples to be chosen from the population.
+Our aim was to \emph{remove} elements that were too simple. That
 is, if the number of mutants dropped below a threshold determined by
@@
 Next, we explored in the other direction, by forcing the program elements
-to return at least one element by using \textit{ceil(sample)}. That is,
+to return at least one element by using \textit{ceil()}. That is,
 irrespective of the fraction being sampled, the simplest elements always
-contributed at least one mutant to the total sample.
+contributed at least one mutant to the total sample, ensuring coverage but
+also giving priority to complex elements.
 
@@
 has been found to reduce the number of mutants well, without an appreciable
-decrease in accuracy. This also provides a nice comparison with similar
+decrease in effectiveness. This also provides a nice comparison with similar
 numbers of mutants between operator selection and random sampling of mutants.
@@
 For selective methods, we tried mutation operators suggested by Wong et al.~\cite{wong1995reducing}, Offutt et al.~\cite{offutt1996anexperimental,deng2013empirical}, % TODO Barbosa
- and, Namin et al~\cite{siami2008sufficient}.
+ and, Namin et al.~\cite{siami2008sufficient}.
 Since Javalanche~\cite{javalanche} utilized operator selection mechanisms, we also compared the Javalanche operators for operator selection.
 Note that all of these techniques except
-Javalanche have targeted C programs, thus some of these operators
-are sensible in C but not in Java programs. For example C compilers tolerate
-removing a return statement --- but in Java this causes a compilation error.
-Moreover, there were some operators that are not supported by the PIT framework
-like ABS (absolute mutation operators). We tried to realize as many
-as possible of the operators using PIT's bytecode level mutation. We also extended 
-the PIT framework to support the  statement deletion operator (SDL).
-
-% {\bf Amin: The rest of this section is for Alex and Carlos info and should be verified if we should include this or wave our hands about approximation instead.}
+Javalanche have targeted C programs. Thus some of these operators
+are sensible in C but not in Java programs. For example, deletion of return statement is tolerated in C, not in Java.
+Moreover, there were a few operators that were not supported by the PIT, and could not be implemented easily.
 
@@
 al.~\cite{deng2013empirical}. The operations on single statements were
-modeled using \Pitvmc, \Pitnvmc, \Pitcc, \Pitemv, and \Pitri for
-simple statements, and using \pitrc for control structures, which
-replaced the boolean condition with false, resulting in removal of the
-block of statements. The operator for return values was modeled using
+modeled using \Pitvmc, \Pitnvmc, \Pitcc, \Pitemv, and \Pitri~for
+simple statements, and using \pitrc for control structures. \pitrc
+replaces boolean conditions with \textit{false}, resulting in removal of the
+conditional block. The operator for return values was modeled using
 \Pitrv, which is similar.  The operators for \textit{while},
 \textit{for}, and \textit{if} statements were modeled using \Pitdc,
-which replaced the boolean condition with true, which removed the
+which replaced the boolean condition with \textit{true}, which removed the
 effect of conditional. The \textit{switch} statement deletion was
@@
 of the effect of true statement deletion, we grouped the mutants by
-line, and considered a single virtual mutant (that is, the total
+line, and considered each line a single virtual mutant (that is, the total
 number of mutants is equal to the total number of lines). Further,
@@
 the constraints of a bytecode based mutation system, we believe that
-our procedure is reasonable. An interesting point is that using this
-procedure statement deletion is no longer a simple mutation and
-qualifies as a higher order mutation operator. In fact, the procedure
-we outlined can be used in general to judge the effectiveness of a
-higher order operator from the results of the first order mutation
-operators that together compose the higher order mutant.
+our procedure is reasonable.
+% An interesting point is that using this
+%procedure statement, deletion is no longer a simple mutation and
+%qualifies as a higher order mutation operator. In fact, the procedure
+%we outlined can be used in general to judge the effectiveness of a
+%higher order operator from the results of the first order mutation
+%operators that together compose the higher order mutant.

### 2014-03-16 src/analysis.Rnw
update graph

@@
             ifelse(grepl('project',operator), 'project',
-              'selection')))))))
+              ifelse(grepl('per_op',operator), 'x% operator',
+              'operator selection'))))))))
 df$sampling <- with(df,
-      ifelse(grepl('op',strategy), 'operator(x)',
           ifelse(grepl('onelement',strategy), 'one(x)',
@@
                     ifelse(grepl('xprobperunit',strategy), 'sample(x)',
-strategy))))))))
+'other')))))))
 ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(size=sqr, color=type))

### 2014-03-16 src/analysis.Rnw
bw theme

--- 2014-03-15 src/analysis.Rnw
@@
                     ifelse(grepl('xprobperunit',strategy), 'sample(x)',
-strategy))))))))
-ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(size=sqr, color=type))
-ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(shape=sampling, color=type))
+'other')))))))
+ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(size=sqr, color=type)) + myopts
+ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(shape=sampling, color=type)) + myopts
 @

### 2014-03-16 src/analysis.Rnw
Fix explanation for regression

@@
 linear correlation between sampled mutation score and full mutation score.
-Since for most of the sampling criteria, if there are no mutants to
-sample, it probably means there are no mutants generated,
-we used
-\[\mu_\{M_{all}|M_{reduced}\} = 0 + \beta_1 \times M_{reduced}\]
-as the regression formula, and reported
-the correlation for this linear regression. We also report the expected
+Since for the control sampling criteria, no mutants sampled implies none generated,
+our model was
+\[\mu_\{M_{all}|M_{reduced}\} = \beta_1 \times M_{reduced}\]
+We reported the correlation for this linear regression. We also report the expected
 multiplier factor $\beta_1$ for the sampled mutation score. This factor

### 2014-03-16 src/analysis.Rnw
Fix up why beta 1 is important

@@
 multiplier factor $\beta_1$ for the sampled mutation score. This factor
-determines the ease of satisfying the sampling criteria. That is, if the
-multiplier factor is small, then it is easier to satisfy compared to a
-larger multiplier factor.
+determines the ease of detecting mutants in the sampling criteria. That is, if the
+multiplier factor is small, then the sample mutation score was larger than
+the full mutation score, and hence it was easier to detect mutants in the sample.
 

### 2014-03-16 src/analysis.Rnw
Add captions to indicate original and generated test cases

@@
 \bigskip
-\caption {The sample(x)\% random selection criteria results.}
+\caption {The sample(x)\% random selection criteria results. (left: Original, right: Generated)}
 \label{tbl:xselsample}
@@
 \bigskip
-\caption {The round(x)\% random selection criteria results.}
+\caption {The round(x)\% random selection criteria results. (left: Original, right: Generated)}
 \label{tbl:xselround}
@@
 \bigskip
-\caption {The ceil(x)\% random selection criteria results.}
+\caption {The ceil(x)\% random selection criteria results. (left: Original, right: Generated)}
 \label{tbl:xselceil}
@@
 \end{minipage}
-\caption {The line count selection criteria results.}
+\caption {The line count selection criteria results. (left: Original, right: Generated)}
 \label{tbl:lcountl}
@@
 \end{minipage}
-\caption {The line count selection criteria results (within).}
+\caption {The line count selection criteria results (within). (left: Original, right: Generated)}
 \label{tbl:lcountw}
@@
 \bigskip
-\caption {The one per element selection criteria results.}
+\caption {The one per element selection criteria results. (left: Original, right: Generated)}
 \label{tbl:onesel}
@@
 \bigskip
-\caption {The x\% per operator criteria results.}
+\caption {The x\% per operator criteria results. (left: Original, right: Generated)}
 \label{tbl:onesel}
@@
 \bigskip
-\caption {Operators}
+\caption {Operators (left: Original, right: Generated)}
 \label{tbl:operators}
@@
 \bigskip
-\caption {Operator Selection}
+\caption {Operator Selection (left: Original, right: Generated)}
 \label{tbl:opsel}

### 2014-03-16 src/results.Rnw
Shortening table description a little bit

@@
 
-Our results for random sampling over program elements using
-$sample(x)$ are given in Table~\ref{tbl:xselsample}. The result of the
-variation using $round(x)$ is given in Table~\ref{tbl:xselround} and
-that using $ceil(x)$ is given in Table~\ref{tbl:xselceil}.  The first
-column in each table provides the scope of sampling: per class, per
-method, or per line. The second column provides the fraction involved.
-The third column contains the $R^2$ value obtained between the
-mutation score of the sampling criteria used and the full mutation
-score.  The fourth column contains the mutant reduction factor. This
-is the average of total mutants produced divided by the number of
-mutants sampled by the criteria.  The fifth column contains the
-standard deviation of the same. A few of the projects did not return
-any value for certain sampling criteria for particular mutation
-reduction fractions. The sixth column contains the number of projects
-that actually had valid values for the criteria being considered. The
-seventh column is the average multiplier between the sampled mutation
-score and the full mutation score.
+Our results for random sampling over program elements using $sample(x)$
+are given in Table~\ref{tbl:xselsample}. The result of the variation using
+$round(x)$ is given in Table~\ref{tbl:xselround} and that using $ceil(x)$
+is given in Table~\ref{tbl:xselceil}. The left tables show results from the
+original set, while right tables show results from generated set.  The first
+column in each table provides the scope of sampling: per project, per class,
+per method, or per line. The second column ($\div$) provides the fraction
+involved. The third column contains the $R^2$ value obtained between the
+mutation score of the sampling criteria used and the full mutation score.
+The fourth column ($\mu_{red}$) contains the mutant reduction factor.
+This is the average of total mutants produced divided by the number of
+mutants sampled by the criteria. The fifth column ($\sigma_{red}$) contains
+the standard deviation of the same. A few of the projects did not return
+any value for certain sampling criteria for particular mutation reduction
+fractions. The sixth column contains the number of projects that actually
+had valid values for the criteria being considered. The seventh column
+($\beta_1$) is the average multiplier between the sampled mutation score
+and the full mutation score.
 
@@
 Table~\ref{tbl:lcountw} contains the results for line count criteria
-where the sampling was conducted inside each program
-element. Similarly Table~\ref{tbl:onesel} contains the results for the
-criteria of one mutant per program element.
+where the sampling was conducted inside each program element. Similarly
+Table~\ref{tbl:onesel} contains the results for the criteria of one mutant
+per program element.
 
-Finally, Table~\ref{tbl:operators} contains the results when only a single operator
-is used, and Table~\ref{tbl:opsel} contains the results for specific operator
-selection criteria. The first columns in these two tables contain the particular
-operator or operator selection applied. The second column contains the
-coefficient $R^2$ with the final mutation score. The third column contains
-the mean mutant reduction ratio, and the fourth contains the standard deviation of the
-mutant reduction ratio achieved. The fifth column contains the number of projects
-that returned valid values for that operator selection mechanism, and the final
-column gives the multiplier factor.
-The TSDL row is the result of applying only the higher order mutant
-equivalent to \textit{statement deletion}.
-All the \textit{N-sel} rows are the results of N-selective operator selection
-strategies~\cite{offutt1993anexperimental}, using the order of operators
-from Figure~\ref{fig:op}. The complete data
+Finally, Table~\ref{tbl:operators} contains the results when only a single
+operator is used, and Table~\ref{tbl:opsel} contains the results for specific
+operator selection criteria. The first columns in these two tables contain
+the particular operator or operator selection applied, and the fraction
+column ($\div$) is absent. The remaining columns are same as previous tables.
+The TSDL row is the result of applying only the higher order mutant equivalent
+to \textit{statement deletion}.  All the \textit{N-sel} rows are the results
+of N-selective operator selection strategies~\cite{offutt1993anexperimental},
+using the order of operators from Figure~\ref{fig:op}. The complete data
 (only for original test suites) is visualized in Figure~\ref{fig:fullimgsize}.

### 2014-03-16 src/discussion.Rnw
Fix mistake
Shortening table description a little bit
Fix up discussion

@@
-section{Discussion}
+\section{Discussion}
 \label{sec:discussion}
@@
 % About Randoop and Original
-Analyzing the scores further, we note that the accuracy of prediction
+Analyzing the scores further, we note that the correlation
 ($R^2$) achieved by sampling is generally lower for generated test
@@
 reduces drastically for generated test suites while correlation remains strong
-for original test suites
+for original test suites.
 Secondly, we also observe that the multiplier factor $\beta_1$
@@
 be lower than what would be expected from the original test suite.
-Secondly, the amount of reduction that can be gained by sampling that must reach a given correlation is lower for generated test suites.
+Further, the amount of mutant reduction possible such that the sampled
+mutation scores still has a high enough correlation with the total score
+is lower for generated test suites.
 
@@
 this strategy produced valid results for all different scopes and sampling
-ratios. It also was able to achieve the highest mutation reduction of $72.63$,
-that is only $1.37\%$ of the original mutants were needed to produce a highly
-correlated ($R^2 = 0.97$) mutation score, with minimal deviation
+ratios. It also was able to achieve a highest mutation reduction of $72.63$,
+with high stability. That is, only $1.37\%$ of the original mutants were needed
+to produce a highly correlated ($R^2 = 0.97$) mutation score, with minimal deviation
 ($\sigma = 6.36$) for original test suites. While the correlation is weaker for
@@
 did not pay off, with line scope having a tendency to become unstable and
-inaccurate at low sampling ratios. At very low sampling ratio ($1/64$), the
-strategy with method scope also becomes unstable and inaccurate. On the whole
+low correlated at low sampling ratios. At very low sampling ratio ($1/64$), the
+strategy with method scope also becomes unstable and low correlated. On the whole
 \textit{round(x)} did not perform as well as \textit{sample(x)}
 
-The strategy of \textit{ceil(x)} also did not perform well. While the
-results were generally stable, the reduction ratios achieved were lower than
-\textit{sample(x)}, with similar correlations.
+The strategy of ensuring coverage with \textit{ceil(x)} also did not perform
+well. While the results were generally stable, the reduction ratios achieved
+were lower than \textit{sample(x)}, with similar correlations.
 
@@
 minimal loss up to a fraction of $\frac{1}{64}$ of the total
-number of mutants (our experiments suggest up to $70$ times reduction,
-with a low standard deviation of $6.72$). We did not cut off with the 99\%
-rule as mentioned by Zhang et al.~\cite{zhang2013ase} (originally proposed
+number of mutants. We did not cut off with the 99\% rule as mentioned
+byZhang et al.~\cite{zhang2013ase} (originally proposed
 by Offutt et al.~\cite{offutt1996experimental} for a different measurement),
-and instead chose to observe that we obtained $R^2 > 0.96$ which provides
-a high confidence in the accuracy of prediction.
+and instead observe that we obtained $R^2 = 0.97$ which provides
+a high confidence in the accuracy of prediction of the full score.
 

### 2014-03-16 src/analysis.Rnw
Shortening table description a little bit
Correct the labels in graphs

@@
 Next, for each criteria, we computed the reduction of mutants given by the
-ratio between total number of mutants and sampled mutants.
+ratio between sampled mutants and total number of mutants.
 We also compute standard deviation of the mutant reduction, which determines
@@
 'other')))))))
-ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(size=sqr, color=type)) + myopts
-ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(shape=sampling, color=type)) + myopts
+
+df$type <- factor(df$type, levels=c('block','line','method','class','project','x% operator','operator selection'))
+
+ggplot(df, aes(mutant.reduction, sd.reduction)) +
+   labs(x=expression(mu[red]), y=expression(sigma[red]) ) +
+   geom_point(aes(size=sqr, color=type)) + myopts
+ggplot(df, aes(mutant.reduction, sd.reduction)) +
+   labs(x=expression(mu[red]), y=expression(sigma[red]) ) +
+   geom_point(aes(shape=sampling, color=type)) + myopts
 @

### 2014-03-16 src/introduction.Rnw
Fixes from Amin

@@
 reduces our confidence in all results. This is true for selective
-mutation studies, studies in sampling, and also for comparatively
+mutation studies, sampling studies, and also for comparatively
 newer studies that attempt to combine methods. This is particularly
@@
 
-We have attempted to rectify this situation with a large scale study
-of real world programs.  As detailed in Section~\ref{sec:methodology},
-we sample 188 Java programs from Github, with size ranging from 50 LOC
-to 100 KLOC, which allows widely applicable statistical inferences to
-be made. We provide the results from running both the original
-project's (presumably human-generated) test suites and also
-automatically generated test suites using random testing, increasing
-the applicability of our findings to both testers in traditional
-development who are interested in applying mutation analysis to suite
-evaluation and to researchers who seek to compare test suites quickly to evaluate testing techniques.
+We have attempted to rectify this situation with a large scale study of real
+world programs.  As detailed in Section~\ref{sec:methodology}, we sample
+188 Java programs from Github, with size ranging from 50 LOC to 100 KLOC,
+which should allow widely applicable statistical inferences to be made. We
+provide the results from running both the original project's (presumably
+human-generated) test suites and also automatically generated test suites
+using random testing, increasing the applicability of our findings to both
+testers in traditional development who are interested in applying mutation
+analysis to suite evaluation and to researchers who seek to compare test
+suites quickly to evaluate testing techniques.
 
@@
 
-\item We compare a much large number of mutant reduction strategies
+\item We compare a much larger number of mutant reduction strategies
 than previous studies. We compare with respect to the predictive power

### 2014-03-16 src/methodology.Rnw
Fixes from Amin

@@
 present in a limited number of projects, and automatically generated
-test suites from Randoop~\cite{randoop}.  Due to limited resources, we
-had to further reduce the programs and test suites to those that could
-finish mutation analysis in 10 minutes. From this set of test suites,
-we sampled 107 suites each for both original and Randoop generated
-test suites. Since there was some overlap between projects with
+test suites from Randoop~\cite{randoop}. From this set of test suites,
+After eliminating those that took too long to finish, we sampled 107
+suites each for both original and Randoop generated test suites,
+Since there was some overlap between projects with
 original test suites, and those with generated test suites, we had 81
@@
 we used is provided in Table~\ref{tbl:pitop}. Figure~\ref{fig:op} shows
-both the distribution of mutants and the relative detection rates of each
+the distribution of mutants and the relative detection rates of each
 mutation operator for our projects. In the figure, there are two box-plots
@@
 
-For a detailed description of each mutant type, please refer to PIT documentation~\cite{pitmut}.
+For a detailed description of each mutation operator, please refer to PIT documentation~\cite{pitmut}.
 PIT was also modified to provide random selection of mutants according
-to various criteria. Finally, to remove random noise, each criteria
+to various criteria.
+Finally, to remove random noise, each criteria
 described was run four times, and the results averaged to produce
@@
 \end{table}
-
-One of the criteria we sampled was \textit{statement deletion}.
-Since we use PIT, which is a bytecode based mutation engine, implementing direct equivalent of
-source code statement deletion is very hard. We were able to approximate statement deletion
-by combining different bytecode operators, as explained in Subsection~\ref{subsec:stmtdel}.
 

### 2014-03-16 src/related.Rnw
Fixes from Amin

@@
 into three approaches: do \textit{fewer}, \textit{smarter}, and \textit{faster}.
-The \textit{do fewer} approaches includes selective mutation and mutant sampling,
+The \textit{do fewer} approaches include selective mutation and mutant sampling,
 while weak mutation, parallelization of mutation analysis, and space/time trade-offs
@@
 A number of studies in the past have looked at the relative merits of operator
-selection and random sampling criteria, starting with Wong and Mathur in
-1995~\cite{wong1995reducing}. They compared x\% selection of each mutant type
+selection and random sampling criteria. Wong et al.~\cite{wong1995reducing}
+compared x\% selection of each mutant type
 with operator selection using just two mutation operators, and found that both
@@
 
-Zhang et al.~\cite{zhang2010operator} compared operators based mutant
-selection techniques proposed in a set of
-papers~\cite{barbosa2001toward,siami2008sufficient,offutt1996anexperimental}
-to random mutant sampling. They found that none of the selection
-techniques are superior to random sampling, with the same number of
-mutants. They also found that uniform sampling of mutations is more effective
-for larger subjects compared to equal sampling of mutation operators
-and the reverse is true for smaller subjects.
+Zhang et al.~\cite{zhang2010operator} compared operator based mutant
+selection techniques to random mutant sampling. They found that none of
+the selection techniques are superior to random sampling, with the same
+number of mutants. They also found that uniform sampling of mutations is
+more effective for larger subjects compared to equal sampling of mutation
+operators and the reverse is true for smaller subjects.
 
@@
 Namin et al.\cite{namin2006finding,siami2008sufficient} formulated
-the problem as a variable reduction problem in statistics, and
+the problem as a variable reduction problem, and
 found that just 28 out of 108 operators in Proteum were sufficient.

### 2014-03-16 src/analysis.Rnw
Fixes from Amin
Better graphs

@@
 
-% \begin{figure*}[t]
-% <<x.per.sel.sample,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-% o.xp.sample <- subset(o.processed, grepl('^rr[.].*.m[.]red',ind))
-% ggplot(subset(o.xp.sample, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
-%   stat_boxplot(geom ='errorbar')+
-%   geom_boxplot() + facet_wrap(~type) + myopts + theme(legend.position="none") + opts(title="sample(x)")
-% # o.xp.round <- subset(o.processed, grepl('^r[.].*.m[.]red',ind))
-% # ggplot(subset(o.xp.round, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
-% #   stat_boxplot(geom ='errorbar')+
-% #   geom_boxplot() + facet_wrap(~type)+ myopts+ theme(legend.position="none")+ opts(title="sample(x)")
-% # 
-% # o.loc.ext <- subset(o.processed, grepl('^l[.].*.m[.]red',ind))
-% # ggplot(subset(o.loc.ext, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
-% #   stat_boxplot(geom ='errorbar')+
-% #   geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none") + opts(title="loc(external)")
-% # 
-% # o.loc.int <- subset(o.processed, grepl('^wl[.].*.m[.]red',ind))
-% # ggplot(subset(o.loc.int, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
-% #   stat_boxplot(geom ='errorbar')+
-% #   geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none") + opts(title="loc(internal)")
-% # 
-% # o.one <- subset(o.processed, grepl('^o[.].*.m[.]red',ind))
-% # ggplot(subset(o.one, reduction < 100 & (type=='line' | type=='method')), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
-% #   stat_boxplot(geom ='errorbar')+
-% #   geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none") + opts(title="One per element")
-% @
-% \caption{The effect of sampling reductions, Except for line sampling of power $5$ and $6$ all others are above 0.90 $R^2$.}
-% \label{fig:xroundsel}
-% \end{figure*}
-%
+\begin{figure*}[t]
+<<x.per.sel.sample,fig.width=10, fig.height=7, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+o.xp.sample <- subset(o.processed, grepl('^rr[.].*.m[.]red',ind))
+o.xp.sample$type <- factor(o.xp.sample$type, levels=c('project','class','method','line'))
+ggplot(subset(o.xp.sample, reduction < 100), aes(factor(power), reduction, fill=type, dodge=type)) +
+  stat_boxplot(geom ='errorbar')+
+  geom_boxplot() + #facet_wrap(~type) +
+  myopts +
+  #xlab(label=expression(frac(all,sample))) +
+  xlab(label=expression(all%/%sample)) +
+  ylab('reduction') +
+  #theme(legend.position="none") +
+  opts(title="sample(x)")
+# o.xp.round <- subset(o.processed, grepl('^r[.].*.m[.]red',ind))
+# ggplot(subset(o.xp.round, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
+#   stat_boxplot(geom ='errorbar')+
+#   geom_boxplot() + facet_wrap(~type)+ myopts+ theme(legend.position="none")+ opts(title="sample(x)")
+# 
+# o.loc.ext <- subset(o.processed, grepl('^l[.].*.m[.]red',ind))
+# ggplot(subset(o.loc.ext, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
+#   stat_boxplot(geom ='errorbar')+
+#   geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none") + opts(title="loc(external)")
+# 
+# o.loc.int <- subset(o.processed, grepl('^wl[.].*.m[.]red',ind))
+# ggplot(subset(o.loc.int, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
+#   stat_boxplot(geom ='errorbar')+
+#   geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none") + opts(title="loc(internal)")
+# 
+# o.one <- subset(o.processed, grepl('^o[.].*.m[.]red',ind))
+# ggplot(subset(o.one, reduction < 100 & (type=='line' | type=='method')), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
+#   stat_boxplot(geom ='errorbar')+
+#   geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none") + opts(title="One per element")
+@
+\caption{The effect of sampling reductions, Original set $R^2 > 0.90$.}
+\label{fig:powerplot}
+\end{figure*}
 
@@
 
-ggplot(df, aes(mutant.reduction, sd.reduction)) +
-   labs(x=expression(mu[red]), y=expression(sigma[red]) ) +
-   geom_point(aes(size=sqr, color=type)) + myopts
+#ggplot(df, aes(mutant.reduction, sd.reduction)) +
+#   labs(x=expression(mu[red]), y=expression(sigma[red]) ) +
+#   geom_point(aes(size=sqr, color=type)) + myopts
 ggplot(df, aes(mutant.reduction, sd.reduction)) +
@@
 @
-\caption{The mean reduction of mutants vs its standard deviation.
+\caption{The mean reduction of mutants vs its standard deviation. Original set, only observations with $R^2 > 0.9$ and $2\times \sigma_{red} < \mu_{red}$ is shown here. }
+%\caption{The mean reduction of mutants vs its standard deviation.
 The sqr represents (1-$R^2$), i.e smaller is good.
-Only those observations with $R^2 > 0.9$ and $2\times $ standard deviation > mean reduction is shown here.
+Only those observations with $R^2 > 0.9$ and $2\times \sigma_{red} > \mu_{red}$ is shown here.
 }

### 2014-03-17 src/analysis.Rnw
Fix graphs so that it makes sense

@@
 @
-\caption{The effect of sampling reductions, Original set $R^2 > 0.90$.}
+\caption{The effect of sampling reductions, Original set $R^2 > 0.90$.
+Notice the hierarchy of spread within boxplot for similar sampling ratios ($\div$) project < class < method < line i.e project is better}
 \label{fig:powerplot}
@@
 df <-  subset(stats.df, r.square>=0.9 & (sd.reduction * 2) < mutant.reduction)
+
 df$sqr <- 1 - df$r.square
@@
 df$sampling <- with(df,
-          ifelse(grepl('onelement',strategy), 'one(x)',
-            ifelse(grepl('locelement',strategy), 'lines(x)',
-              ifelse(grepl('withinelement',strategy), 'one(x)',
+          ifelse(grepl('onelement',strategy), 'one.per.elem(x)',
+            ifelse(grepl('locelement',strategy), 'num.lines(x)',
+              ifelse(grepl('withinelement',strategy), 'within.one(x)',
                 ifelse(grepl('xceilperunit',strategy), 'ceil(x)',
@@
                     ifelse(grepl('xprobperunit',strategy), 'sample(x)',
-'other')))))))
+                      ifelse(grepl('xop',strategy), 'op.x%(x)',
+                        ifelse(grepl('opsel',strategy), 'opsel(x)',
+                          ifelse(grepl('^op$',strategy), 'op(x)',
+'other'))))))))))
 
-df$type <- factor(df$type, levels=c('block','line','method','class','project','x% operator','operator selection'))
+df <- subset(df, type!='block')
+df <- subset(df, sampling %in% c('sample(x)', 'num.lines(x)', 'one.per.elem(x)', 'op.x%(x)', 'opsel(x)'))
+df$sampling <- factor(df$sampling,levels=c('sample(x)', 'num.lines(x)', 'one.per.elem(x)', 'op.x%(x)', 'opsel(x)'))
+#df$type <- factor(df$type, levels=c('block','line','method','class','project','x% operator','operator selection'))
+df$type <- factor(df$type, levels=c('line','method','class','project','x% operator','operator selection'))
 
@@
    labs(x=expression(mu[red]), y=expression(sigma[red]) ) +
-   geom_point(aes(shape=sampling, color=type)) + myopts
+#   geom_point(aes(shape=sampling, color=type)) + myopts
+   geom_point(aes(shape=sampling, color=type),
+   #position=position_jitter(width=0.1, height=0.1),
+   size=3) +
+   myopts +
+   scale_color_manual(values = c('orange', 'purple', 'brown', 'red','blue', 'black'))
+   # block scale_color_manual(values = c('brown','orange', 'purple', 'green', 'red','blue', 'black'))
+   #theme(legend.position=c(0,1) ,legend.justification=c(0,1))
 @
-\caption{The mean reduction of mutants vs its standard deviation. Original set, only observations with $R^2 > 0.9$ and $2\times \sigma_{red} < \mu_{red}$ is shown here. }
+\caption{The mean reduction of mutants vs its standard deviation.
+Original set, main variations of sampling, only observations with $R^2 > 0.9$ and $2\times \sigma_{red} < \mu_{red}$ are shown here.
+Notice that operator selection is has high $\sigma$ for corresponding $\mu$, and project based sampling is better for high reduction}
 %\caption{The mean reduction of mutants vs its standard deviation.

### 2014-03-17 src/analysis.Rnw
Update spellings, fix space etc.

@@
 linear correlation between sampled mutation score and full mutation score.
-Since for the control sampling criteria, no mutants sampled implies none generated,
+Since for the baseline sampling criteria, no mutants sampled implies none generated,
 our model was
-\[\mu_\{M_{all}|M_{reduced}\} = \beta_1 \times M_{reduced}\]
+\[\mu\{M_{all}|M_{reduced}\} = \beta_1 \times M_{reduced}\]
+where $M_{all}$ is the mutation score of original mutation analysis and
+$M_{reduced}$ is the mutation score of the sample.
+
 We reported the correlation for this linear regression. We also report the expected
@@
 
-Next, for each criteria, we computed the reduction of mutants given by the
+Next, for each criterion, we computed the reduction of mutants given by the
 ratio between sampled mutants and total number of mutants.

### 2014-03-17 src/methodology.Rnw
Update spellings, fix space etc.

@@
 fraction of the complete set of mutants. This criteria also serves as a
-control for verifying the effectiveness of other criteria.
+baseline for verifying the effectiveness of other criteria.
 
@@
 We used the formula by Zhang et al.~\cite{zhang2013ase},
-\[sample(x) = floor (x + random(0..1))\]
+\[sample(x) = \lfloor x + random(0..1) \rfloor \]
 to correctly sample decimal numbers.
-Next, we modified this criteria slightly, and instead of
+Next, we slightly modified this criteria, and instead of
 \textit{sample()} which uses probability to manage the decimal numbers,
@@
 was used as the number of samples to be chosen from the population.
-Our aim was to \emph{remove} elements that were too simple. That
-is, if the number of mutants dropped below a threshold determined by
-the mutant reduction ratio, that program element did not contribute
-any mutants to the final result.
-Conceptually the idea is that mutants of more complex code have more discriminatory power (and may correspond better to real faults though we do not evaluate this concept).
+The new strategy ignores program elements with small number of mutants.
+This strategy can potentially guide mutation generation toward more
+complex program elements.
+That is, if the number of mutants dropped below a threshold determined by
+the mutant reduction ratio, that program element would not contribute any
+mutants to the final result.  Conceptually the idea is that mutants of more
+complex code have more discriminatory power (and may correspond better to
+real faults --- though we do not evaluate this concept).
 
@@
 has been researched previously~\cite{untch2009onreduced,deng2013empirical} and
-has been found to reduce the number of mutants well, without an appreciable
+has been found to reduce the number of mutants well, with negligible
 decrease in effectiveness. This also provides a nice comparison with similar
@@
 
-We next extended this approach to sample from each method instead, but
-used the number of lines in the method as the number of mutants to be
-sampled from it. This provided a test of the hypothesis of how
-important a mutation sampling's relationship to simple code coverage
-was. This was extended to class and project scope also.
+We extended sampling to levels coarser than methods, i.e. method, class, and
+project. We sampled $n$ mutants from a method (class or project), where $n$
+is the number of statements in the method (class or project).
+
+This provided a test of the hypothesis of how important a mutation sampling's
+relationship to simple code coverage is. This was extended to class and
+project scope also.
 
@@
 
-%{\bf ADG:  Could maybe make this clearer?}
-% RG: Fixed with an example.
-
 \subsubsection{One per element}
@@
 
-For selective methods, we tried mutation operators suggested by Wong et al.~\cite{wong1995reducing}, Offutt et al.~\cite{offutt1996anexperimental,deng2013empirical}, % TODO Barbosa
- and, Namin et al.~\cite{siami2008sufficient}.
-Since Javalanche~\cite{javalanche} utilized operator selection mechanisms, we also compared the Javalanche operators for operator selection.
-Note that all of these techniques except
-Javalanche have targeted C programs. Thus some of these operators
-are sensible in C but not in Java programs. For example, deletion of return statement is tolerated in C, not in Java.
-Moreover, there were a few operators that were not supported by the PIT, and could not be implemented easily.
+For selective methods, we tried mutation operators
+suggested by Wong et al.~\cite{wong1995reducing}, Offutt et
+al.~\cite{offutt1996anexperimental,deng2013empirical}, and, Namin et
+al.~\cite{siami2008sufficient}. Since Javalanche~\cite{javalanche} utilized
+operator selection mechanisms, we also compared the Javalanche operators for
+operator selection. Note that all of these techniques except Javalanche have
+targeted C programs. Thus, some of these operators are sensible in C but not
+in Java programs. For example, deletion of return statement is tolerated in C,
+not in Java.  Moreover, there were a few operators that were not supported
+by the PIT, and could not be implemented easily (as mentioned below).
 
-\subsubsection{Criteria I}
-For this criteria, we used the two operators \pitcb and \pitnc which are similar to those given by Wong. We did not have ABS operator available in PIT.
-\subsubsection{Criteria II}
-We used the operators given by Offutt et al. \Pitin, \Pitm, \Pitcb, \Pitnc. We did not have LCR available in PIT.
-\subsubsection{Criteria III}
-Those given by Javalanche \Pitnc, \Pitvmc, \Pitnvmc, \Pitm, \Pitic, \Pitemv. 
-\subsubsection{Criteria IV}
-Namin et al. used \Pitin, \Pitm, \Piti, \Pitnc. Many of these operators were not applicable in Java, and some not in PIT.
-\subsubsection{Criteria V}
-For this criteria, we utilized the approach suggested by
-Offutt et al.~\cite{offutt1993experimental} where the most numerous operators
-are discarded at each step.
+\subsubsection{Criteria I} For this criteria, we used the two operators
+\pitcb and \pitnc which are similar to those given by Wong. We did not have
+ABS operator available in PIT.
+
+\subsubsection{Criteria II} We used the operators given by Offutt et
+al. \Pitin, \Pitm, \Pitcb, \Pitnc. We did not have LCR available in PIT.
+
+\subsubsection{Criteria III} Those given by Javalanche : \Pitnc, \Pitvmc,
+\Pitnvmc, \Pitm, \Pitic, \Pitemv.
+
+\subsubsection{Criteria IV} Given by Namin et
+al~\cite{siami2008sufficient}. Many of these operators were not applicable
+in Java, and some not in PIT. The operators used by us were \Pitin, \Pitm,
+\Piti, \Pitnc.
+
+\subsubsection{Criteria V} In this criteria suggested by
+Offutt et al.~\cite{offutt1993experimental} the most numerous operators are
+discarded at each step. Our order was:
+\Pitnvmc, \Pitnc, \Pitrc, \Pitdc, \Pitrv, \Pitic, \Pitcc, \Pitemv, \Pitvmc,
+\Pitm, \Pitcb, \Piti, \Pitri, \Pitrs, \Pites, \Pitin.
 

### 2014-03-17 src/results.Rnw
move data to last
Update spellings, fix space etc.

@@
 mutation score of the sampling criteria used and the full mutation score.
-The fourth column ($\mu_{red}$) contains the mutant reduction factor.
-This is the average of total mutants produced divided by the number of
-mutants sampled by the criteria. The fifth column ($\sigma_{red}$) contains
-the standard deviation of the same. A few of the projects did not return
-any value for certain sampling criteria for particular mutation reduction
-fractions. The sixth column contains the number of projects that actually
-had valid values for the criteria being considered. The seventh column
-($\beta_1$) is the average multiplier between the sampled mutation score
-and the full mutation score.
+The fourth column ($\mu_{red}$) the mutant reduction factor,
+which is the average of total mutants divided by the number of
+mutants sampled. The fifth column ($\sigma_{red}$) is the standard deviation
+of the same. As we explained in the analysis, the sixth column contains
+the valid responses obtained.  The seventh column ($\beta_1$) is the
+multiplier factor (coefficient reported by the regression.)
 
@@
 % @
+
+Our data will be available for replication on publication~\cite{data}
+%\footnote{Available on publication}.

### 2014-03-17 src/analysis.Rnw
Updates from amin, fix for graph

@@
-\begin{table*}
-\begin{minipage}[htb]{0.49\linewidth}
+\begin{table*}[!ht]
+\begin{minipage}[h]{0.49\linewidth}
+\caption*{Original}
 <<results='asis'>>=
@@
 \begin{minipage}[h]{0.49\linewidth}
+\caption*{Generated}
 <<results='asis'>>=
@@
 \end{minipage}
-\bigskip
-\caption {The sample(x)\% random selection criteria results. (left: Original, right: Generated)}
+%\medskip
+\caption {The sample(x)\% random selection criteria results. }
 \label{tbl:xselsample}
@@
 
-\begin{table*}
+\begin{table*}[!ht]
 \begin{minipage}[h]{0.49\linewidth}
+\caption*{Original}
 <<results='asis'>>=
@@
 \end{minipage}
-\bigskip
-\caption {The round(x)\% random selection criteria results. (left: Original, right: Generated)}
+%\medskip
+\caption {The round(x)\% random selection criteria results. }
 \label{tbl:xselround}
@@
 \end{minipage}
-\bigskip
-\caption {The ceil(x)\% random selection criteria results. (left: Original, right: Generated)}
+%\medskip
+\caption {The ceil(x)\% random selection criteria results. }
 \label{tbl:xselceil}
@@
 \end{minipage}
-\caption {The line count selection criteria results. (left: Original, right: Generated)}
+%\medskip
+\caption {The line count selection criteria results. }
 \label{tbl:lcountl}
@@
 \end{minipage}
-\caption {The line count selection criteria results (within). (left: Original, right: Generated)}
+%\medskip
+\caption {The line count selection criteria results (within). }
 \label{tbl:lcountw}
@@
 \end{minipage}
-\bigskip
-\caption {The one per element selection criteria results. (left: Original, right: Generated)}
+%\medskip
+\caption {The one per element selection criteria results. }
 \label{tbl:onesel}
@@
 \end{minipage}
-\bigskip
-\caption {The x\% per operator criteria results. (left: Original, right: Generated)}
+%\medskip
+\caption {The x\% per operator criteria results. }
 \label{tbl:onesel}
@@
 \end{minipage}
-\bigskip
-\caption {Operators (left: Original, right: Generated)}
+%\medskip
+\caption {Operators}
 \label{tbl:operators}
@@
 \end{minipage}
-\bigskip
-\caption {Operator Selection (left: Original, right: Generated)}
+%\medskip
+\caption {Operator Selection}
 \label{tbl:opsel}
@@
 
-\begin{figure*}[t]
-<<x.per.sel.sample,fig.width=10, fig.height=7, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+\begin{figure*}[htb]
+<<x.per.sel.sample,fig.width=10, fig.height=8, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
 o.xp.sample <- subset(o.processed, grepl('^rr[.].*.m[.]red',ind))
@@
   #xlab(label=expression(frac(all,sample))) +
-  xlab(label=expression(all%/%sample)) +
+  xlab(label=expression(sample%/%all)) +
   ylab('reduction') +
   #theme(legend.position="none") +
-  opts(title="sample(x)")
+  opts(title="sample(x)") +
+  scale_x_discrete(breaks=c(1,2,3,4,5,6), labels=c("1/2", "1/4", "1/8",'1/16','1/32','1/64'))
 # o.xp.round <- subset(o.processed, grepl('^r[.].*.m[.]red',ind))
@@
 \caption{The effect of sampling reductions, Original set $R^2 > 0.90$.
-Notice the hierarchy of spread within boxplot for similar sampling ratios ($\div$) project < class < method < line i.e project is better}
+Notice the hierarchy of spread within boxplot for similar sampling ratios ($\div$) project < class < method < line i.e.
+project is better}
 \label{fig:powerplot}
@@
 
-\begin{figure*}[t]
-<<op.all,fig.width=10, fig.height=7, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+\begin{figure*}[htb]
+<<op.all,fig.width=10, fig.height=8, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
 

### 2014-03-17 src/methodology.Rnw
Updates from amin, fix for graph

@@
 \subsection{Operator Selection}
-
 For selective methods, we tried mutation operators
@@
 operator selection. Note that all of these techniques except Javalanche have
-targeted C programs. Thus, some of these operators are sensible in C but not
-in Java programs. For example, deletion of return statement is tolerated in C,
+targeted C programs. Thus, some of these operators may be sensible in C but not
+in Java. For example, deletion of return statement is tolerated in C,
 not in Java.  Moreover, there were a few operators that were not supported
@@
 
-\subsubsection{Criteria I} For this criteria, we used the two operators
-\pitcb and \pitnc which are similar to those given by Wong. We did not have
-ABS operator available in PIT.
+\subsubsection{Constrained Mutation}
+\noindent\textbf{Wong et al. ~\cite{wong1995reducing}.}
+They selected ROR  and ABS  from Mothra for
+mutation analysis. We used operators
+\pitcb and \pitnc to model ROR operator. There are no comparable operators to ABS in PIT.
 
-\subsubsection{Criteria II} We used the operators given by Offutt et
-al. \Pitin, \Pitm, \Pitcb, \Pitnc. We did not have LCR available in PIT.
+\subsubsection{E-Selective}
+\noindent\textbf{Offut et al. \cite{offutt1996anexperimental}.}
+They selected ABS, UOI, LCR, AOR, ROR from Mothra operators.
+We have used  \Pitin, \Pitm, \Pitcb, and \Pitnc. PIT does not have any operator
+comparable to LCR.
 
-\subsubsection{Criteria III} Those given by Javalanche : \Pitnc, \Pitvmc,
-\Pitnvmc, \Pitm, \Pitic, \Pitemv.
+\subsubsection{Javalanche}
+\noindent\textbf{Javalanche \cite{javalanche}.}
+Javalanche uses Negate Jump Condition, Omit Method
+ Call, Replace Arithmetic Operator, and Replace Numerical
+ Constant operators. We have used \Pitnc, \Pitvmc,
+\Pitnvmc, \Pitm, \Pitic and \Pitemv to model them.
 
-\subsubsection{Criteria IV} Given by Namin et
-al~\cite{siami2008sufficient}. Many of these operators were not applicable
-in Java, and some not in PIT. The operators used by us were \Pitin, \Pitm,
-\Piti, \Pitnc.
+\subsubsection{Variable Reduction}
+\noindent\textbf{Namin et al.~\cite{siami2008sufficient}.}
+They have tried to reduce the mutation operators of Proteum analysis
+tool which is for C programs. They suggest 28 operators which many of them
+are not applicable in Java, and some not in PIT.
+We  used by  \Pitin, \Pitm, \Piti and \Pitnc.
 
-\subsubsection{Criteria V} In this criteria suggested by
-Offutt et al.~\cite{offutt1993experimental} the most numerous operators are
-discarded at each step. Our order was:
+\subsubsection{N-selection}
+\noindent\textbf{Offut et al. ~\cite{offutt1993experimental}.} They suggested removal of
+$n$ most numerous operators. In our experiment, the order of operators was
 \Pitnvmc, \Pitnc, \Pitrc, \Pitdc, \Pitrv, \Pitic, \Pitcc, \Pitemv, \Pitvmc,
-\Pitm, \Pitcb, \Piti, \Pitri, \Pitrs, \Pites, \Pitin.
-
+\Pitm, \Pitcb, \Piti, \Pitri, \Pitrs, \Pites, and \Pitin. We discarded one at each
+step and evaluated the effectiveness at each $n$.
+%----------------------------------------
 \subsubsection{Statement Deletion:} \label{subsec:stmtdel} The basic

### 2014-03-17 src/paper.Rnw
Updates from amin, fix for graph

@@
 require(reshape2)
+require(scales)
 require(xtable)

### 2014-03-17 src/analysis.Rnw
latest

@@
    myopts +
-   scale_color_manual(values = c('orange', 'purple', 'brown', 'red','blue', 'black'))
+   scale_color_manual(values = c('orange', 'blue', 'green', 'red','purple', 'black'))
    # block scale_color_manual(values = c('brown','orange', 'purple', 'green', 'red','blue', 'black'))
@@
 Original set, main variations of sampling, only observations with $R^2 > 0.9$ and $2\times \sigma_{red} < \mu_{red}$ are shown here.
-Notice that operator selection is has high $\sigma$ for corresponding $\mu$, and project based sampling is better for high reduction}
+Notice that operator selection is has high $\sigma$ for corresponding $\mu$, and project based sampling is better for high reduction (note that x and y axis are in different scales)}
 %\caption{The mean reduction of mutants vs its standard deviation.

### 2014-03-17 src/methodology.Rnw
latest

@@
 %----------------------------------------
-\subsubsection{Statement Deletion:} \label{subsec:stmtdel} The basic
+\subsubsection{Statement Deletion} \label{subsec:stmtdel} The basic
 statement deletion was modeled on the work by Deng et

### 2014-03-17 src/paper.Rnw
colorize

@@
 <<>>=
+
+f <- function(x) {
+  x <- x[,c(7,8,2,3,4,5,6)]
+  names(x)[names(x) == 'sampling'] <- '$\\div$'
+  return(x)
+}
+
+colorize.rsqr <- function(x) {
+  ifelse(x >= 0.90,
+      paste("\\textcolor{blue}{", formatC(x, dig=2, format="f"), "}"),
+      paste("\\textcolor{black}{", formatC(x, dig=2, format="f"), "}"))
+}
+
+colorize.it <- function(x) {
+  x$sd.reduction <- ifelse(x$sd.reduction * 2 < x$mutant.reduction,
+      paste("\\textcolor{black}{", formatC(x$sd.reduction, dig=2, format="f"), "}"),
+      paste("\\textcolor{red}{", formatC(x$sd.reduction, dig=2, format="f"), "}"))
+  x$r.square <- colorize.rsqr(x$r.square)
+  return(x)
+}
+
 theme_set(theme_bw(12))
@@
 new.colnames <- c('operator', '$R^2$',      '$\\mu_{red}$',            '$\\sigma_{red}$',         'valid',    '$\\beta_1$')
-stats.xp <- subset(stats.df, grepl('^(r|rr|rc)[.]', operator)) # We are ignoring ceil here. add rc if needed.
+
+c.df <- colorize.it(stats.df)
+
+stats.xp <- subset(c.df, grepl('^(r|rr|rc)[.]', operator)) # We are ignoring ceil here. add rc if needed.
 
@@
 r.stats.sel.xp <- subset(r.f(stats.xp), select=sel.colnames)
-stats.rest <- subset(stats.df, !grepl('^(r|rr|rc)[.]', operator))
+stats.rest <- subset(c.df, !grepl('^(r|rr|rc)[.]', operator))
 colnames(o.stats.sel.xp) <- new.colnames
@@
 r.stats.sel.xp$sampling <- NA
-
-f <- function(x) {
-  x <- x[,c(7,8,2,3,4,5,6)]
-  names(x)[names(x) == 'sampling'] <- '$\\div$'
-  return(x)
-}
 

### 2014-12-12 src/introduction.Rnw
move data to last
discarding some tables

@@
 effectiveness of test suites against these
-mutants~\cite{lipton1971fault, ammann2008introduction}.  Previous
-research~\cite{andrews2005mutation} suggests that mutations thus
-introduced behave in a fashion similar to real faults, with respect to
-the difficulty of detection.
+mutants~\cite{lipton1971fault, ammann2008introduction}.  Andrews et. al 
+~\cite{andrews2005mutation} suggest mutations can simulate
+behavior of real faults.
+% thus
+% introduced behave in a fashion similar to real faults, with respect to
+% the difficulty of detection.
 
-One of the impediments to wider adoption of mutation analysis is its
+An impediments to wider adoption of mutation analysis is its
 high computational cost.  The set of simple mutants for even a
@@
 A major strain of research into cost-reduction of mutation analysis is
-to choose a smaller, representative, set of
+to choose a smaller, representative set of
 mutants~\cite{offutt2001mutation,jia2011analysis} --- often called the
@@
 \end{itemize}
-
-Our data will be available for replication on publication~\cite{data}
-%\footnote{Available on publication}.

### 2015-01-12 src/analysis.Rnw
discarding some tables
All tables and figures goes away

--- 2014-03-17 src/analysis.Rnw
@@
-\begin{table*}[!ht]
-\begin{minipage}[h]{0.49\linewidth}
-\caption*{Original}
-<<results='asis'>>=
-print(xtable(f(o.stats.sel.xp.sample), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small',sanitize.text.function=function(x){x})
-@
-\end{minipage}
-\hspace{0.5cm}
-\begin{minipage}[h]{0.49\linewidth}
-\caption*{Generated}
-<<results='asis'>>=
-print(xtable(f(r.stats.sel.xp.sample), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small',sanitize.text.function=function(x){x})
-@
-\end{minipage}
-%\medskip
-\caption {The sample(x)\% random selection criteria results. }
-\label{tbl:xselsample}
-\end{table*}
-
-\begin{table*}[!ht]
-\begin{minipage}[h]{0.49\linewidth}
-\caption*{Original}
-<<results='asis'>>=
-print(xtable(f(o.stats.sel.xp.round), caption='Original', label='table:rando', main='Original'), include.rownames=FALSE, floating=FALSE, size='\\small',sanitize.text.function=function(x){x})
-@
-\end{minipage}
-\hspace{0.5cm}
-\begin{minipage}[h]{0.49\linewidth}
-\caption*{Generated}
-<<results='asis'>>=
-print(xtable(f(r.stats.sel.xp.round), caption='Randoop', label='table:randr', main='Randoop'), include.rownames=FALSE, floating=FALSE,size='\\small',sanitize.text.function=function(x){x})
-@
-\end{minipage}
-%\medskip
-\caption {The round(x)\% random selection criteria results. }
-\label{tbl:xselround}
-\end{table*}
-
-\begin{table*}[!ht]
-\begin{minipage}[h]{0.49\linewidth}
-\caption*{Original}
-<<results='asis'>>=
-print(xtable(f(o.stats.sel.xp.ceil), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small',sanitize.text.function=function(x){x})
-@
-\end{minipage}
-\hspace{0.5cm}
-\begin{minipage}[h]{0.49\linewidth}
-\caption*{Generated}
-<<results='asis'>>=
-print(xtable(f(r.stats.sel.xp.ceil), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small',sanitize.text.function=function(x){x})
-@
-\end{minipage}
-%\medskip
-\caption {The ceil(x)\% random selection criteria results. }
-\label{tbl:xselceil}
-\end{table*}
-
 \section{Analysis}
@@
 tables.
-
-\begin{table*}[!ht]
-\begin{minipage}[h]{0.49\linewidth}
-\caption*{Original}
-<<results='asis'>>=
-print(xtable(f(o.stats.sel.loc), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small',sanitize.text.function=function(x){x})
-@
-\end{minipage}
-\hspace{0.5cm}
-\begin{minipage}[h]{0.49\linewidth}
-\caption*{Generated}
-<<results='asis'>>=
-print(xtable(f(r.stats.sel.loc), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small',sanitize.text.function=function(x){x})
-@
-\end{minipage}
-%\medskip
-\caption {The line count selection criteria results. }
-\label{tbl:lcountl}
-\end{table*}
-
-\begin{table*}[!ht]
-\begin{minipage}[h]{0.49\linewidth}
-\caption*{Original}
-<<results='asis'>>=
-print(xtable(f(o.stats.sel.loc.w), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small',sanitize.text.function=function(x){x})
-@
-\end{minipage}
-\hspace{0.5cm}
-\begin{minipage}[h]{0.49\linewidth}
-\caption*{Generated}
-<<results='asis'>>=
-print(xtable(f(r.stats.sel.loc.w), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small',sanitize.text.function=function(x){x})
-@
-\end{minipage}
-%\medskip
-\caption {The line count selection criteria results (within). }
-\label{tbl:lcountw}
-\end{table*}
-
-\begin{table*}[!ht]
-\begin{minipage}[h]{0.49\linewidth}
-\caption*{Original}
-<<results='asis'>>=
-print(xtable(f(o.stats.sel.one), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small',sanitize.text.function=function(x){x})
-@
-\end{minipage}
-\hspace{0.5cm}
-\begin{minipage}[h]{0.49\linewidth}
-\caption*{Generated}
-<<results='asis'>>=
-print(xtable(f(r.stats.sel.one), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small',sanitize.text.function=function(x){x})
-@
-\end{minipage}
-%\medskip
-\caption {The one per element selection criteria results. }
-\label{tbl:onesel}
-\end{table*}
-
-\begin{table*}[!ht]
-\begin{minipage}[h]{0.49\linewidth}
-\caption*{Original}
-<<results='asis'>>=
-print(xtable(f(o.stats.sel.xop), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small',sanitize.text.function=function(x){x})
-@
-\end{minipage}
-\hspace{0.5cm}
-\begin{minipage}[h]{0.49\linewidth}
-\caption*{Generated}
-<<results='asis'>>=
-print(xtable(f(r.stats.sel.xop), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small',sanitize.text.function=function(x){x})
-@
-\end{minipage}
-%\medskip
-\caption {The x\% per operator criteria results. }
-\label{tbl:onesel}
-\end{table*}
-
-\begin{table*}[!ht]
-\begin{minipage}[h]{0.49\linewidth}
-\caption*{Original}
-<<results='asis'>>=
-print(xtable(o.stats.sel.op, caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small',sanitize.text.function=function(x){x})
-@
-\end{minipage}
-\hspace{0.5cm}
-\begin{minipage}[h]{0.49\linewidth}
-\caption*{Generated}
-<<results='asis'>>=
-print(xtable(r.stats.sel.op, caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small',sanitize.text.function=function(x){x})
-@
-\end{minipage}
-%\medskip
-\caption {Operators}
-\label{tbl:operators}
-\end{table*}
-
-\begin{table*}[!ht]
-\begin{minipage}[h]{0.49\linewidth}
-\caption*{Original}
-<<results='asis'>>=
-print(xtable(o.stats.sel.opsel, caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small',sanitize.text.function=function(x){x})
-@
-\end{minipage}
-\hspace{0.5cm}
-\begin{minipage}[h]{0.49\linewidth}
-\caption*{Generated}
-<<results='asis'>>=
-print(xtable(r.stats.sel.opsel, caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small',sanitize.text.function=function(x){x})
-@
-\end{minipage}
-%\medskip
-\caption {Operator Selection}
-\label{tbl:opsel}
-\end{table*}
-
-\begin{figure*}[htb]
-<<x.per.sel.sample,fig.width=10, fig.height=8, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-o.xp.sample <- subset(o.processed, grepl('^rr[.].*.m[.]red',ind))
-o.xp.sample$type <- factor(o.xp.sample$type, levels=c('project','class','method','line'))
-ggplot(subset(o.xp.sample, reduction < 100), aes(factor(power), reduction, fill=type, dodge=type)) +
-  stat_boxplot(geom ='errorbar')+
-  geom_boxplot() + #facet_wrap(~type) +
-  myopts +
-  #xlab(label=expression(frac(all,sample))) +
-  xlab(label=expression(sample%/%all)) +
-  ylab('reduction') +
-  #theme(legend.position="none") +
-  opts(title="sample(x)") +
-  scale_x_discrete(breaks=c(1,2,3,4,5,6), labels=c("1/2", "1/4", "1/8",'1/16','1/32','1/64'))
-# o.xp.round <- subset(o.processed, grepl('^r[.].*.m[.]red',ind))
-# ggplot(subset(o.xp.round, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
-#   stat_boxplot(geom ='errorbar')+
-#   geom_boxplot() + facet_wrap(~type)+ myopts+ theme(legend.position="none")+ opts(title="sample(x)")
-# 
-# o.loc.ext <- subset(o.processed, grepl('^l[.].*.m[.]red',ind))
-# ggplot(subset(o.loc.ext, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
-#   stat_boxplot(geom ='errorbar')+
-#   geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none") + opts(title="loc(external)")
-# 
-# o.loc.int <- subset(o.processed, grepl('^wl[.].*.m[.]red',ind))
-# ggplot(subset(o.loc.int, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
-#   stat_boxplot(geom ='errorbar')+
-#   geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none") + opts(title="loc(internal)")
-# 
-# o.one <- subset(o.processed, grepl('^o[.].*.m[.]red',ind))
-# ggplot(subset(o.one, reduction < 100 & (type=='line' | type=='method')), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
-#   stat_boxplot(geom ='errorbar')+
-#   geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none") + opts(title="One per element")
-@
-\caption{The effect of sampling reductions, Original set $R^2 > 0.90$.
-Notice the hierarchy of spread within boxplot for similar sampling ratios ($\div$) project < class < method < line i.e.
-project is better}
-\label{fig:powerplot}
-\end{figure*}
-
-% \begin{figure*}[t]
-% <<op.sample,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-% o.xp.opsel <- o.op.processed
-% o.xp.opsel$operators <- 16 - o.xp.opsel$operators
-% colnames(o.xp.opsel)[colnames(o.xp.opsel)=="operators"] <- "rm.operators"
-% 
-% df <- subset(o.xp.opsel, rm.operators <= 20 & reduction != Inf & type != 'operator' & (type != 'n-selection' | rm.operators < 9))
-% qplot(rm.operators, reduction, fill=interaction(type,rm.operators), data=df, geom="boxplot", position="dodge") + theme_bw()
-% @
-% \caption{Operator selection comparison between n-selection and other selection methods in mutation reduction.  We show only up to 8-selection}
-% \label{fig:xroundsel}
-% \end{figure*}
-%
-
-\begin{figure*}[htb]
-<<op.all,fig.width=10, fig.height=8, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-
-df <-  subset(stats.df, r.square>=0.9 & (sd.reduction * 2) < mutant.reduction)
-
-df$sqr <- 1 - df$r.square
-df$mult <- 1 - df$score.multiplier
-df$type <- with(df, as.factor(
-      ifelse(grepl('line',operator), 'line',
-        ifelse(grepl('block',operator), 'block',
-        ifelse(grepl('method',operator), 'method',
-          ifelse(grepl('class',operator), 'class',
-            ifelse(grepl('project',operator), 'project',
-              ifelse(grepl('per_op',operator), 'x% operator',
-              'operator selection'))))))))
-df$sampling <- with(df,
-          ifelse(grepl('onelement',strategy), 'one.per.elem(x)',
-            ifelse(grepl('locelement',strategy), 'num.lines(x)',
-              ifelse(grepl('withinelement',strategy), 'within.one(x)',
-                ifelse(grepl('xceilperunit',strategy), 'ceil(x)',
-                  ifelse(grepl('xpercentperunit',strategy), 'round(x)',
-                    ifelse(grepl('xprobperunit',strategy), 'sample(x)',
-                      ifelse(grepl('xop',strategy), 'op.x%(x)',
-                        ifelse(grepl('opsel',strategy), 'opsel(x)',
-                          ifelse(grepl('^op$',strategy), 'op(x)',
-'other'))))))))))
-
-df <- subset(df, type!='block')
-df <- subset(df, sampling %in% c('sample(x)', 'num.lines(x)', 'one.per.elem(x)', 'op.x%(x)', 'opsel(x)'))
-df$sampling <- factor(df$sampling,levels=c('sample(x)', 'num.lines(x)', 'one.per.elem(x)', 'op.x%(x)', 'opsel(x)'))
-#df$type <- factor(df$type, levels=c('block','line','method','class','project','x% operator','operator selection'))
-df$type <- factor(df$type, levels=c('line','method','class','project','x% operator','operator selection'))
-
-#ggplot(df, aes(mutant.reduction, sd.reduction)) +
-#   labs(x=expression(mu[red]), y=expression(sigma[red]) ) +
-#   geom_point(aes(size=sqr, color=type)) + myopts
-ggplot(df, aes(mutant.reduction, sd.reduction)) +
-   labs(x=expression(mu[red]), y=expression(sigma[red]) ) +
-#   geom_point(aes(shape=sampling, color=type)) + myopts
-   geom_point(aes(shape=sampling, color=type),
-   #position=position_jitter(width=0.1, height=0.1),
-   size=3) +
-   myopts +
-   scale_color_manual(values = c('orange', 'purple', 'brown', 'red','blue', 'black'))
-   # block scale_color_manual(values = c('brown','orange', 'purple', 'green', 'red','blue', 'black'))
-   #theme(legend.position=c(0,1) ,legend.justification=c(0,1))
-@
-\caption{The mean reduction of mutants vs its standard deviation.
-Original set, main variations of sampling, only observations with $R^2 > 0.9$ and $2\times \sigma_{red} < \mu_{red}$ are shown here.
-Notice that operator selection is has high $\sigma$ for corresponding $\mu$, and project based sampling is better for high reduction}
-%\caption{The mean reduction of mutants vs its standard deviation.
-The sqr represents (1-$R^2$), i.e smaller is good.
-Only those observations with $R^2 > 0.9$ and $2\times \sigma_{red} > \mu_{red}$ is shown here.
-}
-\label{fig:fullimgsize}
-\end{figure*}
-
-% \begin{figure*}[t]
-% <<op.all.2,fig.width=10, fig.height=7, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-% df <-  subset(df, r.square>=0.9 & (sd.reduction * 2) < mutant.reduction & mutant.reduction <= 20)
-% ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(size=sqr, color=type))
-% ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(shape=sampling, color=type))
-% @
-% \caption{The mean reduction of mutants vs its standard deviation. The sqr represents (1-$R^2$), i.e smaller is good. Only mean reduction <= 20 (5\%)}
-% \label{fig:fullimgsize2}
-% \end{figure*}
-% 
-% \begin{figure*}[t]
-% <<op.all.3,fig.width=10, fig.height=7, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-% 
-% df <-  subset(df, r.square>=0.9 & (sd.reduction * 2) < mutant.reduction & mutant.reduction <= 10)
-% ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(size=sqr, color=type))
-% ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(shape=sampling, color=type))
-% @
-% \caption{The mean reduction of mutants vs its standard deviation. The sqr represents (1-$R^2$), i.e smaller is good. Only mean reduction <= 10 (10\%)}
-% \label{fig:fullimgsize3}
-% \end{figure*}
-%
-
-% \begin{figure*}[t]
-% <<op.all.4,fig.width=10, fig.height=7, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-% 
-% df <-  subset(df, r.square>=0.9 & (sd.reduction * 2) < mutant.reduction & mutant.reduction <= 5)
-% ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(size=sqr, color=type))
-% ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(shape=sampling, color=type))
-% @
-% \caption{The mean reduction of mutants vs its standard deviation. The sqr represents (1-$R^2$), i.e smaller is good. Only mean reduction <= 5 (20\%)}
-% \label{fig:fullimgsize4}
-% \end{figure*}
-%

### 2015-01-12 etc/abstract.tex
abstract

@@
 achieve accuracy and mutant reduction similar to operator selection.
+Newer research has also indicated that program element based sampling
+may be better than pure random sampling or traditional operator selection.
+
 %
 %2.Saywhyit’saninterestingproblem
-However, the empirical support for these conclusions has been limited, due to the small number of subject programs investigated.  The best sampling technique is also an open problem.
-% that can be drawn from the previous
-%research has been limited due to the small number of subject programs. Further,
-%which sampling technique is best is still an open problem that needs to be
-%tackled on a much larger range of test subjects.
-
+However, the empirical support for these conclusions has been limited,
+due to the small number of subject programs investigated. The best sampling
+technique is also an open problem. Further, current research has focused
+on evaluating mutation analysis techniques over adequate test suites. However,
+real world test suites are often far from test adequacy, and it is not clear
+if the results carry over to non-adequate test suites.
 %3.Saywhatyoursolutionachieves
 
-Our research compares a large number of sampling and operator
-selection criteria based on their ability to predict the full mutation
-score as well as the consistency of mutation reduction ratios
-achieved. Our results can be used to choose an appropriate mutation
-reduction technique by the reduction and level of fidelity to full
-mutation results required.
+We propose that a better mutation selection criteria should generate a larger
+number of defective behaviors than a worse mutation selection criteria, which
+we judge using the number of non-redundant tests able to kill the sampled
+mutants.
+
+We evaluate the performance of various selection criteria on 250 opensource
+projects from github, which shows that the popular operator selection and
+element based sampling are not much better than random selection, and often
+performs worse than random selection. This suggests a need for further research
+on better methods of operator selection and sampling.
+
+% Our results can be used to choose an appropriate mutation
+% reduction technique by the reduction and level of fidelity to full
+% mutation results required.
 
@@
 
-We find that all sampling approaches perform better than operator
-selection methods, when considering ability to predict the full
-mutation score as well as the consistency of mutation reduction ratios
-achieved.
+% We find that all sampling approaches perform better than operator
+% selection methods, when considering ability to predict the full
+% mutation score as well as the consistency of mutation reduction ratios
+% achieved.
 

### 2015-01-12 src/methodology.Rnw
remove fig

@@
-\begin{figure*}
-<<op,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-clean <- function(x) {
-  sub('CONSTRUCTOR_CALLS','CC',
-      sub('INCREMENTS','I',
-        sub('RETURN_VALS','RV',
-          sub('VOID_METHOD_CALLS','VMC',
-            sub('NON_VOID_METHOD_CALLS','NMC',
-              sub('RMSWITCH','RS',
-                sub('REMOVE_CONDITIONALS','RC',
-                  sub('REMOVE_INCREMENTS','RI',
-                    sub('NEGATE_CONDITIONALS','NC',
-                      sub('MATH','M',
-                        sub('INVERT_NEGS','IN',
-                          sub('INLINE_CONSTS','IC',
-                            sub('EXPERIMENTAL_SWITCH','ES',
-                              sub('EXPERIMENTAL_MEMBER_VARIABLE','EMV',
-                                sub('DELETE_CONDITIONALS','DC',
-                                  sub('CONDITIONALS_BOUNDARY','CB',x))))))))))))))))
-}
-par(las=1,mfrow = c(1, 2),mar=c(2,8,1,1))
-o.all <- cbind(projects = rownames(o.dist.all), stack(o.dist.all))
-o.all$ind <- clean(o.all$ind)
-bcol <- '#2171B5'
-#bcol <- 'darkgray'
-icol <- '#9ECAE0'
-#icol <- 'lightgray'
-o.det <- cbind(projects = rownames(o.dist.det), stack(o.dist.det))
-o.det$ind <- clean(o.det$ind)
-with(o.all,boxplot(values~ind,horizontal=T,border=c(bcol), pch='.', axes=F, ylim=c(0,0.6), col=icol ))
-with(o.det,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Original', cex.axis=0.8, ylim=c(0,0.6),add=T))
-
-r.all <- cbind(projects = rownames(r.dist.all), stack(r.dist.all))
-r.all$ind <- clean(r.all$ind)
-r.det <- cbind(projects = rownames(r.dist.det), stack(r.dist.det))
-r.det$ind <- clean(r.det$ind)
-with(r.all,boxplot(values~ind,horizontal=T,border=c(bcol), pch='.', axes=F,ylim=c(0,0.6),  col=icol))
-with(r.det,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Randoop', cex.axis=0.8,ylim=c(0,0.6),add=T))
-@
-\caption{The relative contribution of mutation operators in terms of fraction of mutants produced and detected.
-The produced mutants are shown with black outline while detected mutants have blue border and shade.}
-\label{fig:op}
-\end{figure*}
-
 \section{Methodology} \label{sec:methodology} Our selection of

### 2015-01-12 src/paper.Rnw
discarding some tables
update package name

@@
 require(ggplot2)
-require(Mutsel)
+require(MutSel)
 @
@@
 <<setup>>
-v=data(package='Mutsel')
+v=data(package='MutSel')
 data(list = v$results[,3])
-original.stats.df <- stats.df # save it
-o.f <- function(x) subset(x, kind == 'original')
-r.f <- function(x) subset(x, kind == 'randoop')
-o.stats.df <- o.f(stats.df)
-r.stats.df <- r.f(stats.df)
 @
@@
 
-sel.colnames <- c('operator', 'r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier')
-new.colnames <- c('operator', '$R^2$',      '$\\mu_{red}$',            '$\\sigma_{red}$',         'valid',    '$\\beta_1$')
-
-c.df <- colorize.it(stats.df)
-
-stats.xp <- subset(c.df, grepl('^(r|rr|rc)[.]', operator)) # We are ignoring ceil here. add rc if needed.
-
-o.stats.sel.xp <- subset(o.f(stats.xp), select=sel.colnames)
-r.stats.sel.xp <- subset(r.f(stats.xp), select=sel.colnames)
-stats.rest <- subset(c.df, !grepl('^(r|rr|rc)[.]', operator))
-colnames(o.stats.sel.xp) <- new.colnames
-colnames(r.stats.sel.xp) <- new.colnames
-o.stats.sel.xp$scope <- NA
-r.stats.sel.xp$scope <- NA
-o.stats.sel.xp$sampling <- NA
-r.stats.sel.xp$sampling <- NA
-
-o.stats.sel.xp.sample <- subset(o.stats.sel.xp, grepl('^rr[.]', operator))
-r.stats.sel.xp.sample <- subset(r.stats.sel.xp, grepl('^rr[.]', operator))
-
-o.stats.sel.xp.sample$operator <- gsub('rr[.]1x','1/', o.stats.sel.xp.sample$operator)
-o.stats.sel.xp.sample$scope <- gsub('.*_','', o.stats.sel.xp.sample$operator)
-o.stats.sel.xp.sample$sampling <- gsub('_.*','', o.stats.sel.xp.sample$operator)
-r.stats.sel.xp.sample$operator  <- gsub('rr[.]1x','1/', r.stats.sel.xp.sample$operator)
-r.stats.sel.xp.sample$scope <- gsub('.*_','', r.stats.sel.xp.sample$operator)
-r.stats.sel.xp.sample$sampling <- gsub('_.*','', r.stats.sel.xp.sample$operator)
-
-o.stats.sel.xp.round <- subset(o.stats.sel.xp, grepl('^r[.]', operator))
-r.stats.sel.xp.round <- subset(r.stats.sel.xp, grepl('^r[.]', operator))
-
-o.stats.sel.xp.round$operator  <- gsub('r[.]1x','1/', o.stats.sel.xp.round$operator)
-o.stats.sel.xp.round$scope  <- gsub('.*_','', o.stats.sel.xp.round$operator)
-o.stats.sel.xp.round$sampling  <- gsub('_.*','', o.stats.sel.xp.round$operator)
-r.stats.sel.xp.round$operator  <- gsub('r[.]1x','1/', r.stats.sel.xp.round$operator)
-r.stats.sel.xp.round$scope  <- gsub('.*_','', r.stats.sel.xp.round$operator)
-r.stats.sel.xp.round$sampling  <- gsub('_.*','', r.stats.sel.xp.round$operator)
-
-o.stats.sel.xp.ceil <- subset(o.stats.sel.xp, grepl('^rc[.]', operator))
-r.stats.sel.xp.ceil <- subset(r.stats.sel.xp, grepl('^rc[.]', operator))
-
-o.stats.sel.xp.ceil$operator  <- gsub('rc[.]1x','1/', o.stats.sel.xp.ceil$operator)
-o.stats.sel.xp.ceil$scope  <- gsub('.*_','', o.stats.sel.xp.ceil$operator)
-o.stats.sel.xp.ceil$sampling  <- gsub('_.*','', o.stats.sel.xp.ceil$operator)
-r.stats.sel.xp.ceil$operator  <- gsub('rc[.]1x','1/', r.stats.sel.xp.ceil$operator)
-r.stats.sel.xp.ceil$scope  <- gsub('.*_','', r.stats.sel.xp.ceil$operator)
-r.stats.sel.xp.ceil$sampling  <- gsub('_.*','', r.stats.sel.xp.ceil$operator)
-# 1 done
-stats.loc <- subset(stats.rest, grepl('^l[.]', operator))
-o.stats.sel.loc <- subset(o.f(stats.loc), select=sel.colnames)
-r.stats.sel.loc <- subset(r.f(stats.loc), select=sel.colnames)
-stats.rest <- subset(stats.rest, !grepl('^l[.]', operator))
-colnames(o.stats.sel.loc) <- new.colnames
-colnames(r.stats.sel.loc) <- new.colnames
-
-o.stats.sel.loc$operator  <- gsub('l[.]1x','1/', o.stats.sel.loc$operator)
-o.stats.sel.loc$scope  <- gsub('.*_','', o.stats.sel.loc$operator)
-o.stats.sel.loc$sampling  <- gsub('_.*','', o.stats.sel.loc$operator)
-r.stats.sel.loc$operator  <- gsub('l[.]1x','1/', r.stats.sel.loc$operator)
-r.stats.sel.loc$scope  <- gsub('.*_','', r.stats.sel.loc$operator)
-r.stats.sel.loc$sampling  <- gsub('_.*','', r.stats.sel.loc$operator)
-
-stats.loc.w <- subset(stats.rest, grepl('^wl[.]', operator))
-o.stats.sel.loc.w <- subset(o.f(stats.loc.w), select=sel.colnames)
-r.stats.sel.loc.w <- subset(r.f(stats.loc.w), select=sel.colnames)
-stats.rest <- subset(stats.rest, !grepl('^wl[.]', operator))
-colnames(o.stats.sel.loc.w) <- new.colnames
-colnames(r.stats.sel.loc.w) <- new.colnames
-
-o.stats.sel.loc.w$operator  <- gsub('wl[.]1x','1/', o.stats.sel.loc.w$operator)
-o.stats.sel.loc.w$scope  <- gsub('.*_','', o.stats.sel.loc.w$operator)
-o.stats.sel.loc.w$sampling  <- gsub('_.*','', o.stats.sel.loc.w$operator)
-r.stats.sel.loc.w$operator  <- gsub('wl[.]1x','1/', r.stats.sel.loc.w$operator)
-r.stats.sel.loc.w$scope  <- gsub('.*_','', r.stats.sel.loc.w$operator)
-r.stats.sel.loc.w$sampling  <- gsub('_.*','', r.stats.sel.loc.w$operator)
-# 2 done
-
-stats.one <- subset(stats.rest, grepl('^o[.]', operator))
-
-o.stats.sel.one <- subset(o.f(stats.one), select=sel.colnames)
-r.stats.sel.one <- subset(r.f(stats.one), select=sel.colnames)
-stats.rest <- subset(stats.rest, !grepl('^o[.]', operator))
-colnames(o.stats.sel.one) <- new.colnames
-colnames(r.stats.sel.one) <- new.colnames
-
-o.stats.sel.one$operator  <- gsub('o[.]1x','1/', o.stats.sel.one$operator)
-o.stats.sel.one$scope  <- gsub('.*_','', o.stats.sel.one$operator)
-o.stats.sel.one$sampling  <- gsub('_.*','', o.stats.sel.one$operator)
-
-r.stats.sel.one$operator  <- gsub('o[.]1x','1/', r.stats.sel.one$operator)
-r.stats.sel.one$scope  <- gsub('.*_','', r.stats.sel.one$operator)
-r.stats.sel.one$sampling  <- gsub('_.*','', r.stats.sel.one$operator)
-# 3 done
-
-stats.op <- subset(stats.rest, grepl('^(op:|TSDL)', operator))
-o.stats.sel.op <- subset(o.f(stats.op), select=sel.colnames)
-r.stats.sel.op <- subset(r.f(stats.op), select=sel.colnames)
-stats.rest <- subset(stats.rest, !grepl('^(op:|TSDL)', operator))
-colnames(o.stats.sel.op) <- new.colnames
-colnames(r.stats.sel.op) <- new.colnames
-
-#o.stats.sel.op$kind  <- ifelse(grepl('opsel:', o.stats.sel.op$operator), 'selection', 'operator')
-#r.stats.sel.op$kind  <- ifelse(grepl('opsel:', o.stats.sel.op$operator), 'selection', 'operator')
-
-o.stats.sel.op$operator  <- gsub('NVMC','NMC', gsub('_','',gsub('op.*:','', o.stats.sel.op$operator)))
-r.stats.sel.op$operator  <- gsub('NVMC','NMC', gsub('_','',gsub('op.*:','', r.stats.sel.op$operator)))
-
-stats.opsel <- subset(stats.rest, grepl('^opsel', operator))
-o.stats.sel.opsel <- subset(o.f(stats.opsel), select=sel.colnames)
-r.stats.sel.opsel <- subset(r.f(stats.opsel), select=sel.colnames)
-stats.rest <- subset(stats.rest, !grepl('^opsel', operator))
-colnames(o.stats.sel.opsel) <- new.colnames
-colnames(r.stats.sel.opsel) <- new.colnames
-
-#o.stats.sel.op$kind  <- ifelse(grepl('opsel:', o.stats.sel.op$operator), 'selection', 'operator')
-#r.stats.sel.op$kind  <- ifelse(grepl('opsel:', o.stats.sel.op$operator), 'selection', 'operator')
-
-o.stats.sel.opsel$operator  <- gsub('_','',gsub('op.*:','', o.stats.sel.opsel$operator))
-r.stats.sel.opsel$operator  <- gsub('_','',gsub('op.*:','', r.stats.sel.opsel$operator))
-
-stats.xop <- subset(stats.rest, grepl('^OP', operator))
-stats.rest <- subset(stats.rest, !grepl('^OP', operator))
-
-o.stats.sel.xop <- subset(o.f(stats.xop), select=sel.colnames)
-r.stats.sel.xop <- subset(r.f(stats.xop), select=sel.colnames)
-colnames(o.stats.sel.xop) <- new.colnames
-colnames(r.stats.sel.xop) <- new.colnames
-
-o.stats.sel.xop$scope  <- 'operator'
-o.stats.sel.xop$sampling  <- gsub('_per_op','',gsub('OP[.]1x','1/', o.stats.sel.xop$operator))
-r.stats.sel.xop$scope  <- 'operator'
-r.stats.sel.xop$sampling  <- gsub('_per_op','',gsub('OP[.]1x','1/', r.stats.sel.xop$operator))
-
-o.stats.sel.xop$operator  <- gsub('_per_op','',gsub('OP[.]1x','1/', o.stats.sel.xop$operator))
-r.stats.sel.xop$operator  <- gsub('_per_op','',gsub('OP[.]1x','1/', r.stats.sel.xop$operator))
-
-# 4 done
-
 @
@@
 %\FloatBarrier
-\clearpage
+%\clearpage

### 2015-01-12 src/discussion.Rnw
Better graphs
update without errors

@@
 
-The second pattern is that fractional sampling based on projects
-appears to be better than that based on classes, which in turn is
-better than methods and lines, with regard to the stability of the
-result (i.e. low standard deviation).  This is not clear at lower
-levels of reduction ($< 1/32$), but becomes more pronounced for lower
-ratios. There seems to exist a hierarchy of sampling, whereby as sampling becomes
-more fine grained stability decreases.  We did not observe the pattern
-found by Zhang et al.~\cite{zhang2013ase} where method-based sampling
-had the best correlations. In fact, in our measurements, the opposite
-may be true, with project based sampling having the highest
-$R^2$ a majority of the time.
-
 The third "pattern" is that the simplest sampling scheme --- simple

### 2015-01-12 src/methodology.Rnw
update without errors

@@
 operators provided by other mutation systems. The set of operators that
-we used is provided in Table~\ref{tbl:pitop}. Figure~\ref{fig:op} shows
-the distribution of mutants and the relative detection rates of each
-mutation operator for our projects. In the figure, there are two box-plots
-corresponding to each mutation operator on the Y-axis. The black box represents
-the relative frequency of the particular mutation operator in the total
-mutants \textit{produced}. For example, for projects in the (Randoop) generated set,
-the operator \pitnvmc contributed about 34\% of the total number of mutants
-produced while \pitrv contributed about 7\%. Similarly, the blue shaded
-box-plot represents the relative frequency of particular mutation operator
-in the total mutants \textit{detected}. For example, \pitnvmc contribution
-in the detected mutants was 23\% while that of \pitrv was 15\%.
+we used is provided in Table~\ref{tbl:pitop}.
+% Figure~\ref{fig:op} shows
+% the distribution of mutants and the relative detection rates of each
+% mutation operator for our projects. In the figure, there are two box-plots
+% corresponding to each mutation operator on the Y-axis. The black box represents
+% the relative frequency of the particular mutation operator in the total
+% mutants \textit{produced}. For example, for projects in the (Randoop) generated set,
+% the operator \pitnvmc contributed about 34\% of the total number of mutants
+% produced while \pitrv contributed about 7\%. Similarly, the blue shaded
+% box-plot represents the relative frequency of particular mutation operator
+% in the total mutants \textit{detected}. For example, \pitnvmc contribution
+% in the detected mutants was 23\% while that of \pitrv was 15\%.
 
@@
 of simple statement deletion, especially when arithmetic operators are
-involved, is not complete. However, as seen in Figure~\ref{fig:op},
+involved, is not complete. However,
 the number of mutants produced by \pitm operator is very small. We

### 2015-01-12 src/results.Rnw
Updates from amin, fix for graph
update without errors

@@
 \label{sec:results}
-
-Our results for random sampling over program elements using $sample(x)$
-are given in Table~\ref{tbl:xselsample}. The result of the variation using
-$round(x)$ is given in Table~\ref{tbl:xselround} and that using $ceil(x)$
-is given in Table~\ref{tbl:xselceil}. The left tables show results from the
-original set, while right tables show results from generated set.  The first
-column in each table provides the scope of sampling: per project, per class,
-per method, or per line. The second column ($\div$) provides the fraction
-involved. The third column contains the $R^2$ value obtained between the
-mutation score of the sampling criteria used and the full mutation score.
-The fourth column ($\mu_{red}$) the mutant reduction factor,
-which is the average of total mutants divided by the number of
-mutants sampled. The fifth column ($\sigma_{red}$) is the standard deviation
-of the same. As we explained in the analysis, the sixth column contains
-the valid responses obtained.  The seventh column ($\beta_1$) is the
-multiplier factor (coefficient reported by the regression.)
-
-Table~\ref{tbl:lcountl} provides the results for line count criteria
-where the sampling was conducted after combining program elements, and
-Table~\ref{tbl:lcountw} contains the results for line count criteria
-where the sampling was conducted inside each program element. Similarly
-Table~\ref{tbl:onesel} contains the results for the criteria of one mutant
-per program element.
-
-Finally, Table~\ref{tbl:operators} contains the results when only a single
-operator is used, and Table~\ref{tbl:opsel} contains the results for specific
-operator selection criteria. The first columns in these two tables contain
-the particular operator or operator selection applied, and the fraction
-column ($\div$) is absent. The remaining columns are same as previous tables.
-The TSDL row is the result of applying only the higher order mutant equivalent
-to \textit{statement deletion}.  All the \textit{N-sel} rows are the results
-of N-selective operator selection strategies~\cite{offutt1993anexperimental},
-using the order of operators from Figure~\ref{fig:op}. The complete data
-(only for original test suites) is visualized in Figure~\ref{fig:fullimgsize}.
 

### 2015-01-12 src/introduction.Rnw
update without errors
introduction update

@@
 
-An impediments to wider adoption of mutation analysis is its
+An impediment to the wider adoption of mutation analysis is its
 high computational cost.  The set of simple mutants for even a
@@
 operators specific to the language, and are not directly applicable to
-newer languages such as Java. Finally, with bytecode based mutation
+newer languages such as Java. Finally, with bytecode~\footnote{
+A \textit{do faster} approach for eliminating
+the compilation step to gain execution speed
+} based mutation
 engines like PIT~\cite{pitest} and Javalanche~\cite{javalanche}
-(a \textit{do faster} approach for eliminating
-the compilation step to gain execution speed), operators based on
+, operators based on
 source code modification are no longer applicable, and their
@@
 world programs. As detailed in Section~\ref{sec:methodology}, we sample
-188 Java programs from Github, with size ranging from 50 LOC to 100 KLOC,
-which should allow widely applicable statistical inferences to be made. We
-provide the results from running both the original project's (presumably
-human-generated) test suites and also automatically generated test suites
-using random testing, increasing the applicability of our findings to both
-testers in traditional development who are interested in applying mutation
-analysis to suite evaluation and to researchers who seek to compare test
-suites quickly to evaluate testing techniques.
-
-One note about our, and other researchers, evaluation criteria is in
-order.  We, like others, use the ability of a sample to correlate well
-to the score over all mutants as a measure of sampling quality.  The
-underlying reason for this is that, while many mutants have little
-ability to distinguish between good and bad test suites, some smaller
-set of mutants show subtle deficiencies in suites that are not clear
-from, say, code coverage.  The full set of mutants obviously contains
-these mutants, and correlating with (rather than matching) the
-full mutation score is a strong indicator that many of these
-discriminatory mutants have been preserved in a sample.
+250 Java programs from Github\footnote{Our dataset is 322 programs, but as of
+this writing the larger projects have not completed finished running
+full-mutation analysis.},
+with size ranging from 50 LOC to 100 KLOC, excluding tests,
+which should allow widely applicable statistical inferences to be made.
 
@@
 
-\item Our study is the largest so far in terms of both the size of programs
-involved (50 LOC to 100 KLOC), and the number of programs analyzed (188
-unique open source projects) for mutant reduction strategies. This allows
-for stronger and more widely applicable conclusions about effectiveness.
+\item Our study is the largest so far in terms of
+both the size of programs involved (50 LOC to 100 KLOC excluding tests),
+and the number of programs analyzed (250 unique open source projects) for
+mutant reduction strategies. This allows for stronger and more widely
+applicable conclusions about effectiveness.
 
-\item We compare a much larger number of mutant reduction strategies
-than previous studies. We compare with respect to the predictive power
-(correlation with the full mutation score), expected mutant reduction,
-and the stability of the amount of mutant reduction expected. Our
-sampling strategies include some that were suggested by other
-researchers, as well as a few novel strategies not previously considered.
+\item We compare a much larger
+number of mutant reduction strategies than previous studies. Our reduction
+strategies include all the common and influential strategies for
+random sampling, element scoped sampling, and operator selection, that
+have been proposed in previous studeies.
 
-\item Our recommendations are useful for both testing researchers who
-might be comparing automatically generated test suites, and software
-testers in real world working to produce and evaluate manual test suites.
+\item Our evaluation crtieria is applicable to non-adequate test suites
+which makes the results immediately relevant for real world programs with
+non-adequate test suites.
 
-\item Most importantly, we find that random sampling strategies perform
-better than operator selection strategies in consistently predicting the
-final mutation score while obtaining stable computational reduction.
+\item Most importantly, we find that current operator reduction strategies
+seldom perform better than random sampling of mutants, which suggests a need
+for further research in this area.
 

### 2015-01-12 src/analysis.Rnw
tables

@@
+\begin{table}[!ht]
+\caption*{Selective}
+<<results='asis'>>=
+print(xtable(r.selective.db, caption='Selective', label='table:selective'), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
+@
+\caption {The operator selection criteria results. }
+\label{tbl:lcountl}
+\end{table}
+
+\begin{table}[!ht]
+\caption*{Element Scoped}
+<<results='asis'>>=
+print(xtable(r.lmc.db, caption='Element Scoped', label='table:element'), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
+@
+\caption {The element based sampling criteria results. }
+\label{tbl:lcountl}
+\end{table}
+
+\begin{table}[!ht]
+\caption*{N-Selection}
+<<results='asis'>>=
+print(xtable(r.nselection.db, caption='N-Selection', label='table:nselection'), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
+@
+\caption {The n-selection criteria results}
+\label{tbl:lcountl}
+\end{table}
+
+\begin{table}[!ht]
+\caption*{Single Operators}
+<<results='asis'>>=
+print(xtable(r.singles.db, caption='Single Operators', label='table:singles'), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
+@
+\caption {The n-selection criteria results}
+\label{tbl:lcountl}
+\end{table}
+
 \section{Analysis}

### 2015-01-12 src/introduction.Rnw
tables

@@
 with size ranging from 50 LOC to 100 KLOC, excluding tests,
-which should allow widely applicable statistical inferences to be made.
+which allow widely applicable statistical inferences to be made.
+
+For a mutation selection strategy to be considered effective, especially during
+the development, it should be able to expose as many defect-like behaviors as
+possible.
 

### 2015-01-12 src/introduction.Rnw
update

--- 2015-01-12 src/introduction.Rnw
@@
 effectiveness of test suites against these
-mutants~\cite{lipton1971fault, ammann2008introduction}.  Andrews et. al 
-~\cite{andrews2005mutation} suggest mutations can simulate
-behavior of real faults.
+mutants~\cite{lipton1971fault, ammann2008introduction}. Research by
+Andrews et. al~\cite{andrews2005mutation} suggest that mutations can
+simulate behavior of real faults.
 % thus
@@
 
-Recent work~\cite{zhang2010icse,zhang2013ase} has investigated the
-relative merits of random sampling strategies and operator selection.
-Random sampling can perform as well as or better than operator
-selection, in these studies; and a strategy of either sampling based on
-program elements or one combining both program element-based sampling
-and operator selection was best.
+Recent work~\cite{zhang2010icse,zhang2013ase} investigating the
+relative merits of random sampling strategies and operator selection
+suggests that random sampling can perform as well as or better than operator
+selection, and a strategy of either sampling based on program elements or
+one combining both program element-based sampling and operator selection
+was the best approach.
 
@@
 programs studied, and in the number and diversity of programs, which
-reduces our confidence in all results. This is true for selective
-mutation studies, sampling studies, and also for comparatively
-newer studies that attempt to combine methods. This is particularly
-worrisome if mutation analysis is to gain wider acceptance among
-testing professionals. Further, quite a few of the influential
-studies~\cite{offutt1993experimental,offutt1996anexperimental,wong1995reducing,mresa1999efficiency}
+reduces our confidence. This is true for selective mutation studies,
+sampling studies, and also for comparatively newer studies that attempt
+to combine methods. This is particularly worrisome if mutation analysis
+is to gain wider acceptance among testing professionals.
+
+Further, quite a few of the influential studies~\cite{offutt1993experimental,offutt1996anexperimental,wong1995reducing,mresa1999efficiency}
 were conducted on older programming languages such as Fortran, with
 operators specific to the language, and are not directly applicable to
-newer languages such as Java. Finally, with bytecode~\footnote{
+newer languages such as Java.
+
+Finally, with bytecode~\footnote{
 A \textit{do faster} approach for eliminating
@@
 full-mutation analysis.},
-with size ranging from 50 LOC to 100 KLOC, excluding tests,
-which should allow widely applicable statistical inferences to be made.
+with size ranging from $50$ to $100,000$ lines (excluding tests), allowing
+us to draw more widely applicable statistical inferences.
+
+% For a mutation selection strategy to be considered effective, especially during
+% the development, it should be able to expose as many defect-like behaviors as
+% possible.
+Consider any test in a test suite. It is written with the intent of
+checking for the absence of some (faulty) behavior. If supposing, tests
+were equivalent in the number of behaviors that they test, then the best test
+suite would be one that included the largest number of non-redundant test
+cases~\footnote{We show later why this assumption is valid (Specifically,
+assertion distribution was $\mu=1.7$ and $\sigma=2$ )}. This suggests that
+we could evaluate different mutation reduction strategies on their ability
+to choose mutants such that they are killed by a larger number of
+non-redundant test cases. Further, such a technique is not limited by the
+adequacy of test suite under consideration.
 

### 2015-01-14 src/analysis.Rnw
update

--- 2015-01-12 src/analysis.Rnw
@@
+\begin{table*}[!ht]
+\caption*{Selective}
+<<results='asis'>>=
+print(xtable(s.selective.db, caption='Selective', label='table:selective'), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
+@
+\caption {The operator selection criteria results. }
+\label{tbl:lcountl}
+\end{table*}
+
+\begin{table*}[!ht]
+\caption*{Element Scoped}
+<<results='asis'>>=
+print(xtable(s.lmcp.db, caption='Element Scoped', label='table:element'), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
+@
+\caption {The element based sampling criteria results. }
+\label{tbl:lcountl}
+\end{table*}
+
+\begin{table*}[!ht]
+\caption*{N-Selection}
+<<results='asis'>>=
+print(xtable(s.nselection.db, caption='N-Selection', label='table:nselection'), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
+@
+\caption {The n-selection criteria results}
+\label{tbl:lcountl}
+\end{table*}
+
+\begin{table*}[!ht]
+\caption*{Single Operators}
+<<results='asis'>>=
+print(xtable(s.singles.db, caption='Single Operators', label='table:singles'), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
+@
+\caption {The n-selection criteria results}
+\label{tbl:lcountl}
+\end{table*}
+
 \section{Analysis}

### 2015-01-14 etc/abstract.tex
update abstract

@@
 test suites. However, it is computationally intensive compared to
-other measures, which makes it hard to use in practice. Choosing a
-smaller subset of mutations to run is a simple approach that can
-alleviate this problem.  Mutation operator selection has been heavily
-researched. Recently, researchers have found that sampling mutants can
-achieve accuracy and mutant reduction similar to operator selection.
-Newer research has also indicated that program element based sampling
-may be better than pure random sampling or traditional operator selection.
+other measures, which makes it hard to use in practice. Multiple
+strategies has been proposed to reduce the number of mutants produced,
+and hence reduce the computational requirements.
 
@@
 %2.Saywhyit’saninterestingproblem
-However, the empirical support for these conclusions has been limited,
-due to the small number of subject programs investigated. The best sampling
-technique is also an open problem. Further, current research has focused
-on evaluating mutation analysis techniques over adequate test suites. However,
-real world test suites are often far from test adequacy, and it is not clear
-if the results carry over to non-adequate test suites.
+However, current research on mutation reduction is beset with several
+problems. There is inconclusive evidence supporting many of the suggested
+reduction strategies due to the limited number and size of of subject
+programs investigated. The lack of a comprehensive study comparing
+at-least the major approaches is another problem. Finally the traditional
+evaluation criteria for mutation reduction approaches relies on
+mutation-adequate test suites which rarely occur in real world. There is
+little evidence that the strategies that perform well using the traditional
+evaluation crtiera leads to better mutation selection for non-adequate
+tests in the real world.
+
 %3.Saywhatyoursolutionachieves
 
-We propose that a better mutation selection criteria should generate a larger
-number of defective behaviors than a worse mutation selection criteria, which
-we judge using the number of non-redundant tests able to kill the sampled
-mutants.
+We extend the traditional reduction crtieria so that it is usable with
+non-mutation adequate test suites, and link it to the actual use of
+mutation analysis during development -- to produce tests that check for
+as many different bugs as possible.
 
-We evaluate the performance of various selection criteria on 250 opensource
-projects from github, which shows that the popular operator selection and
-element based sampling are not much better than random selection, and often
-performs worse than random selection. This suggests a need for further research
-on better methods of operator selection and sampling.
+We evaluate the performance of various selection criteria on 312 opensource
+projects from github, which shows that the popular reduction strategies:
+operator selection, operator based sampling, and element based sampling
+are hardly better than random selection, and often performs worse.
+This suggests a need for further research on better methods of mutation
+reduction strategies.
 

### 2015-01-14 src/introduction.Rnw
update

@@
 world programs. As detailed in Section~\ref{sec:methodology}, we sample
-250 Java programs from Github\footnote{Our dataset is 322 programs, but as of
-this writing the larger projects have not completed finished running
-full-mutation analysis.},
-with size ranging from $50$ to $100,000$ lines (excluding tests), allowing
-us to draw more widely applicable statistical inferences.
+312 Java programs from Github, with size ranging from $50$ to $100,000$
+lines (excluding tests), allowing us to draw more widely applicable
+statistical inferences.
 
@@
 Consider any test in a test suite. It is written with the intent of
-checking for the absence of some (faulty) behavior. If supposing, tests
-were equivalent in the number of behaviors that they test, then the best test
-suite would be one that included the largest number of non-redundant test
-cases~\footnote{We show later why this assumption is valid (Specifically,
-assertion distribution was $\mu=1.7$ and $\sigma=2$ )}. This suggests that
-we could evaluate different mutation reduction strategies on their ability
-to choose mutants such that they are killed by a larger number of
-non-redundant test cases. Further, such a technique is not limited by the
-adequacy of test suite under consideration.
+checking for the absence of some (faulty) behavior. From the perspective of a
+a tester, the best testsuite is one that checks for the absence
+of the largest number of faulty behaviors. If tests were equivalent in the
+amount of behaviors that they verify, then the best testsuite would be one that
+encouraged adding the largest number of non-redundant test cases. However,
+it is possible that different tests are not equivalent in the number of
+behaviors that they check. We can approximate this to some extent by
+including the number of assert statements within each test~\footnote{We
+approximate the effect of exception-only test cases by starting the assert
+count from $1$ rather than $0$}.
 
-Section~\ref{sec:methodology} discusses the sampling and operator
-selection strategies we study in detail, and the results of our
+Hence an easy way to evaluate a mutation reduction strategy would be to
+see if it promotes such test suites; that is, either test suites with a large
+number of non-redundant test cases, or those with a large number of asserts.
+
+If we assume that testers would prefer adding test cases that increases the
+mutation score, then a good strategy should reward the behavior of adding
+non-redundant test cases and test suites with larger number of asserts.
+Thus it should choose a set of mutants that are killed by a larger number
+of such non-redundant tests at-least in comparison with random selection
+of the same number of mutants as the chosen set. We could also ensure that
+a reduction strategy does not miss out on important tests by running the
+set of non-redundant tests against the full set of mutants to see how many
+of the mutants were detected in comparison with the original number of
+detected mutants. Since this evaluation crtieria does not depend on the
+mutation-adequacy of the test suite under consideration, we can run the
+evaluation using real world projects which almost always have non-adequate
+test suites.
+
+Section~\ref{sec:related} describes the research in mutation reduction 
+strategies. Section~\ref{sec:methodology} discusses the sampling and
+operator
+selection strategies we study in detail. The analysis is given in
+Section~\ref{sec:analysis}, and the results of our
 experiment are given in Section~\ref{sec:results}, followed by
@@
 \item Our study is the largest so far in terms of
-both the size of programs involved (50 LOC to 100 KLOC excluding tests),
-and the number of programs analyzed (250 unique open source projects) for
+both the size of programs involved ($50$ to $100,000$ lines excluding tests),
+and the number of programs analyzed ($312$ unique open source projects) for
 mutant reduction strategies. This allows for stronger and more widely
@@
 strategies include all the common and influential strategies for
-random sampling, element scoped sampling, and operator selection, that
-have been proposed in previous studeies.
+random sampling, element scoped sampling, operator based sampling,
+and operator selection, that have been proposed in previous studeies.
 

### 2015-01-14 src/methodology.Rnw
update abstract
update methodology

@@
 present in the experiments. For this reason we chose a random sample
-of Java projects from Github~\cite{github} that use the popular
+of Java projects from Github~\cite{github} and Apache Software
+Foundation~\cite{apache} that use the popular
 maven~\cite{maven} build system, following the methodology we used
-previously in an ICSE 2014 paper~\cite{gopinath2014code}. As in that
-work, we utilize two kinds of of test suites: the original test suites
-present in a limited number of projects, and automatically generated
-test suites from Randoop~\cite{randoop}. From this set of test suites,
-After eliminating those that took too long to finish, we sampled 107
-suites each for both original and Randoop generated test suites,
-Since there was some overlap between projects with
-original test suites, and those with generated test suites, we had 81
-unique projects each in both sets. The remaining 26 projects had both
-flavors of test suites.
+previously in an ICSE 2014 paper~\cite{gopinath2014code}.
 
@@
 For a detailed description of each mutation operator, please refer to PIT documentation~\cite{pitmut}.
-PIT was also modified to provide random selection of mutants according
-to various criteria.
-Finally, to remove random noise, each criteria
-described was run four times, and the results averaged to produce
-the final result.
+We modified PIT to report the entire test matrix of $tests \times failures$
+rather than just the first failure, and used this for our analysis. To remove
+the effects of random noice, results of each criteria was averaged out of ten
+runs.
 
@@
 
-We used several different sampling criteria, some of which has been suggested
-in the literature before, some which are variants of previously suggested
-criteria, and a few novel ones.  For each sampling
-criteria, we sampled mutants on a decreasing power scale, sampling
-\textit{1/2, 1/4, 1/8, 1/16, 1/32, 1/64} of the total mutants.
+We used several different sampling criteria that has been mentioned in the
+literature, For each sampling criteria, we sampled mutants on a decreasing
+power scale, sampling \textit{1/2, 1/4, 1/8, 1/16, 1/32, 1/64} of the total
+mutants.
 
@@
 
-\subsubsection{One per element}
-Another simple strategy of sampling we experimented with is to just choose
-one mutant per program element, in the order \textit{line}, \textit{method}, \textit{class}.
-
 \subsubsection{x\% selection per operator}
@@
 $n$ most numerous operators. In our experiment, the order of operators was
-\Pitnvmc, \Pitnc, \Pitrc, \Pitdc, \Pitrv, \Pitic, \Pitcc, \Pitemv, \Pitvmc,
-\Pitm, \Pitcb, \Piti, \Pitri, \Pitrs, \Pites, and \Pitin. We discarded one at each
+\Pitnvmc, \Pitrv, \Pitic, \Pitdc, \Pitnc, \Pitrc, \Pitvmc, \Pitcc, \Pitemv,
+\Pitm, \Pitcb, \Piti, \Pitri, \Pitrs, \Pites, and \Pitin
+We discarded one at each
 step and evaluated the effectiveness at each $n$.

### 2015-01-14 src/methodology.Rnw
update methodlogy

@@
 
-\subsubsection{Sampling over program elements and variants}
+\subsubsection{x\% selection per operator}
+This strategy, first suggested by Wong et al.~\cite{wong1995reducing} samples an equal percentage
+of mutants from each operator.
+
+\subsubsection{Sampling over program elements}
 Following the suggestion of Zhang et al.~\cite{zhang2013ase}, we
@@
 to correctly sample decimal numbers.
-Next, we slightly modified this criteria, and instead of
-\textit{sample()} which uses probability to manage the decimal numbers,
-we applied \textit{round()} to obtain the nearest whole number, which
-was used as the number of samples to be chosen from the population.
-The new strategy ignores program elements with small number of mutants.
-This strategy can potentially guide mutation generation toward more
-complex program elements.
-That is, if the number of mutants dropped below a threshold determined by
-the mutant reduction ratio, that program element would not contribute any
-mutants to the final result.  Conceptually the idea is that mutants of more
-complex code have more discriminatory power (and may correspond better to
-real faults --- though we do not evaluate this concept).
-
-Next, we explored in the other direction, by forcing the program elements
-to return at least one element by using \textit{ceil()}. That is,
-irrespective of the fraction being sampled, the simplest elements always
-contributed at least one mutant to the total sample, ensuring coverage but
-also giving priority to complex elements.
-
-\subsubsection{Lines per element and variants}
-Our previous research~\cite{gopinath2014code} found that statement coverage
-was highly correlated with mutation score for a project. This immediately
-suggests that perhaps choosing one mutant per line may be sufficient to achieve
-a close approximation of the final mutation score. Further, statement deletion
-has been researched previously~\cite{untch2009onreduced,deng2013empirical} and
-has been found to reduce the number of mutants well, with negligible
-decrease in effectiveness. This also provides a nice comparison with similar
-numbers of mutants between operator selection and random sampling of mutants.
-
-We extended sampling to levels coarser than methods, i.e. method, class, and
-project. We sampled $n$ mutants from a method (class or project), where $n$
-is the number of statements in the method (class or project).
-
-This provided a test of the hypothesis of how important a mutation sampling's
-relationship to simple code coverage is. This was extended to class and
-project scope also.
-
-For the first variant, we applied the x\% sampling to the result of
-the first sampling based on line counts. That is, in the case of
-methods, we first selected \textit{linecount} mutants each from each
-method, and applied the x\% selection to this result.
-For example, for $1/2$ sampling on methods if one method had
-$10$ lines and another had $20$, we sampled $10$ mutants from
-the first, and $20$ from the second, and from the combined
-$30$ mutants, we sampled $15$.  For the second variant, we did the
-sampling in one go, where we chose \textit{linecount/x} number of
-mutants from each program element.  That is, in the previous example,
-only $5$ mutants from the first and $10$ mutants from the second
-method would be chosen.
-
-\subsubsection{x\% selection per operator}
-This strategy, first suggested by Wong et al.~\cite{wong1995reducing} samples an equal percentage
-of mutants from each operator.
 

### 2015-01-15 src/analysis.Rnw
operator samples
update1

@@
 \caption {The operator selection criteria results. }
-\label{tbl:lcountl}
-\end{table*}
-
-\begin{table*}[!ht]
-\caption*{Element Scoped}
-<<results='asis'>>=
-print(xtable(s.lmcp.db, caption='Element Scoped', label='table:element'), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
-@
-\caption {The element based sampling criteria results. }
 \label{tbl:lcountl}
@@
 @
-\caption {The n-selection criteria results}
+\caption {The single operator selection results}
+\label{tbl:lcountl}
+\end{table*}
+
+\begin{table*}[!ht]
+\caption*{Operator Samples x\%}
+<<results='asis'>>=
+print(xtable(s.opsample.db, caption='Operator x samples', label='table:opsample'), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
+@
+\caption {The operator x\% sample criteria results}
+\label{tbl:lcountl}
+\end{table*}
+
+\begin{table*}[!ht]
+\caption*{Element Scoped}
+<<results='asis'>>=
+print(xtable(s.lmcp.db, caption='Element Scoped', label='table:element'), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
+@
+\caption {The element based sampling criteria results. }
 \label{tbl:lcountl}
@@
 \label{sec:analysis}
-For the purposes of comparing between the criteria, we computed the
-linear correlation between sampled mutation score and full mutation score.
-Since for the baseline sampling criteria, no mutants sampled implies none generated,
-our model was
-\[\mu\{M_{all}|M_{reduced}\} = \beta_1 \times M_{reduced}\]
-where $M_{all}$ is the mutation score of original mutation analysis and
-$M_{reduced}$ is the mutation score of the sample.
+For the purpose of comparing different mutation reduction strategies, we
+computed the average \textit{test utility}, and \textit{assert utility} of
+different strategies.
 
-We reported the correlation for this linear regression. We also report the expected
-multiplier factor $\beta_1$ for the sampled mutation score. This factor
-determines the ease of detecting mutants in the sampling criteria. That is, if the
-multiplier factor is small, then the sample mutation score was larger than
-the full mutation score, and hence it was easier to detect mutants in the sample.
+We use the mutant reduction strategy to select a subset
+of mutants from the original set. We then collect all test cases that were
+able to kill any of the selected set of mutants. Next we compute the
+non-redundant test cases by discarding any test case that can be removed
+without letting any of the mutants escape. This is repeated $10$ times,
+and the average number of non-redundant test cases are found.
 
-Next, for each criterion, we computed the reduction of mutants given by the
-ratio between sampled mutants and total number of mutants.
-We also compute standard deviation of the mutant reduction, which determines
-the consistency of results. A large standard deviation suggests
-that the mutant reduction ratio achieved is very much dependent on the
-project. Therefore, as a heuristic, we suggest looking at only those methods which
-have a mean reduction ratio at least twice the standard deviation.
+While computing the test cases, we also collect assertion number each
+test case has. We compute this as the number of asserts in the test case
+incremented by one to account for test cases without any asserts. Thus the
+compute both the assertions from non-redundant test cases for the mutant
+selection, and also the assertions for the full set of killing test cases
+for the mutant selection.
 
-A few projects did not return any results for some large reduction factors.
-Thus the number of valid results from projects is also collected in the result
-tables.
+The \textit{test utility} is computed as the difference between the number
+of non-redundant test cases the mutant selection achieved and the number of
+non-redundant test cases of a random sample of same number of mutants.
+The result is reported as a percentage of the non-redundant tests of the random
+sample (the baseline).
+
+Similarly \textit{assert utility} of a strategy is computed

### 2015-01-15 src/introduction.Rnw
update1

@@
 operators~\cite{offutt1993anexperimental,untch2009onreduced}.
-Recent work suggests that using statement deletion alone can
-be an effective approach~\cite{untch2009onreduced}.
+%Recent work suggests that using statement deletion alone can
+%be an effective approach~\cite{untch2009onreduced}.
 
@@
 Acree~\cite{acree1980mutation} and Budd~\cite{budd1980mutation}, who
-proposed using only $x$\% of all mutants produced. Wong and Mathur
-found that random sampling with ratio as low as 10\% could provide
-accurate results~\cite{jia2011analysis}.
+proposed using only a small fraction of randomly selected mutants.
+Wong and Mathur found that random sampling fraction as low as 10\%
+could provide accurate results~\cite{jia2011analysis}.
 
@@
 world programs. As detailed in Section~\ref{sec:methodology}, we sample
-312 Java programs from Github, with size ranging from $50$ to $100,000$
+$312$ Java programs from Github, with size ranging from $50$ to $100,000$
 lines (excluding tests), allowing us to draw more widely applicable
@@
 of the mutants were detected in comparison with the original number of
-detected mutants. Since this evaluation crtieria does not depend on the
-mutation-adequacy of the test suite under consideration, we can run the
-evaluation using real world projects which almost always have non-adequate
-test suites.
+detected mutants. This can again be compared to the test cases selected by
+a random sample of same number of mutants to see if the strategy performed
+better at-least with respect to random sampling. Since this evaluation crtieria
+does not depend on the mutation-adequacy of the test suite under consideration,
+we can run the evaluation using real world projects which almost always have
+non-adequate test suites.
 

### 2015-01-15 src/analysis.Rnw
analysis

@@
 
-While computing the test cases, we also collect assertion number each
+While computing the test cases, we also collect assertion information each
 test case has. We compute this as the number of asserts in the test case
-incremented by one to account for test cases without any asserts. Thus the
+incremented by one to account for test cases without any asserts. Thus we
 compute both the assertions from non-redundant test cases for the mutant
@@
 The result is reported as a percentage of the non-redundant tests of the random
-sample (the baseline).
+sample which is taken as the baseline.
 
-Similarly \textit{assert utility} of a strategy is computed
+Similarly \textit{assert utility} of a strategy is computed as the difference
+between the number of assertions of non-redundant test cases the mutatnt
+selection achieved and the number of assertions the test cases for random
+sample of same number of mutants. As before, it is reported as a percentage of
+the asserts of the non-redundant tests of the random sample which is taken
+as the baseline.
+
+\textit{Strategy effectiveness} is computed by collecting all the test cases
+that detected any of the mutants in the selected subset, and applying these
+test cases to the complete set of mutants. The mutation score thus obtained
+is then divided by the original number of detected mutants.
+
+Similarly \textit{baseline effectiveness} is computed by getting the number
+of mutants selected by the strategy, and selecting the same number of mutants
+randomly, collecting the test cases that kill any of these mutants, and
+applying the same test cases against the original set of mutants. The result
+is then divided by the original number of detected mutants.

### 2015-01-15 src/results.Rnw
update
results

@@
 
-% \subsection{SDL vs Random selection}
-% \begin{figure*}[t]
-% <<sdl.x,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-% par(mfrow=c(2,2))
-% with(o.pit.all, plot(all.cov~TSDL.cov, pch='+', main='Original SDL'))
-% with(o.pit.all, plot(all.cov~l.1x1_per_line.cov, pch='+', main='Original 1 per line'))
-% with(r.pit.all, plot(all.cov~TSDL.cov, pch='+', main='Randoop SDl'))
-% with(r.pit.all, plot(all.cov~l.1x1_per_line.cov, pch='+', main='Randoop 1 per line'))
-% @
-% \label{fig:sdl1}
-% \caption{Statement Deletion vs One per line.}
-% \end{figure*}
-% <<results='asis'>>=
-% oprand <- subset(stats.df,!grepl('^..op', rownames(stats.df)))
-% 
-% oprand.x <- subset(oprand,grepl('^.1x[0-9]+_per_', operator))
-% oprand.l <- subset(oprand,!grepl('^.1x[0-9]+_per_', operator))
-% @
+The results for operator selection criteria are given in Table~\ref{tbl:selective}.
+Those of N-Selection are given in Table~\ref{tbl:nselection}.
+The fractional sampling per operator is provided in Table~\ref{tbl:opsample}, and that of element scoped sampling is provided in Table~\ref{tbl:element}.
+Finally, operation selection using just single operators are given in Table~\ref{tbl:singles}.
 
-Our data will be available for replication on publication~\cite{data}
-%\footnote{Available on publication}.
+Our data is available for replication~\cite{ourdata}.

### 2015-01-15 src/analysis.Rnw
results
update

@@
 \begin{table*}[!ht]
-\caption*{Selective}
+%\caption*{Selective}
 <<results='asis'>>=
-print(xtable(s.selective.db, caption='Selective', label='table:selective'), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
+tbl.place <- function(xtb) {
+  align(xtb) <- "p{0.1\\textwidth}|p{0.15\\textwidth}|p{0.15\\textwidth}|p{0.15\\textwidth}|p{0.15\\textwidth}|p{0.15\\textwidth}"
+  return(xtb)
+}
+print(tbl.place(xtable(s.selective.db, caption='Selective Strategy', label='table:selective')),include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
 @
-\caption {The operator selection criteria results. }
-\label{tbl:lcountl}
+\caption {The operator selection strategy}
+\label{tbl:selective}
 \end{table*}
@@
 \begin{table*}[!ht]
-\caption*{N-Selection}
+%\caption*{N-Selection}
 <<results='asis'>>=
-print(xtable(s.nselection.db, caption='N-Selection', label='table:nselection'), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
+print(tbl.place(xtable(s.nselection.db, caption='N-Selection', label='table:nselection')), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
 @
-\caption {The n-selection criteria results}
-\label{tbl:lcountl}
+\caption {The N-selective strategy}
+\label{tbl:nselection}
 \end{table*}
@@
 \begin{table*}[!ht]
-\caption*{Single Operators}
+%\caption*{Operator Samples x\%}
 <<results='asis'>>=
-print(xtable(s.singles.db, caption='Single Operators', label='table:singles'), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
+print(tbl.place(xtable(s.opsample.db, caption='Operator x samples', label='table:opsample')), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
 @
-\caption {The single operator selection results}
-\label{tbl:lcountl}
+\caption {The operator based fractional sample strategy}
+\label{tbl:opsample}
 \end{table*}
@@
 \begin{table*}[!ht]
-\caption*{Operator Samples x\%}
+%\caption*{Element Scoped}
 <<results='asis'>>=
-print(xtable(s.opsample.db, caption='Operator x samples', label='table:opsample'), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
+print(tbl.place(xtable(s.lmcp.db, caption='Element Scoped', label='table:element')), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
 @
-\caption {The operator x\% sample criteria results}
-\label{tbl:lcountl}
+\caption {The element based fractional sample strategy}
+\label{tbl:element}
 \end{table*}
@@
 \begin{table*}[!ht]
-\caption*{Element Scoped}
+%\caption*{Single Operators}
 <<results='asis'>>=
-print(xtable(s.lmcp.db, caption='Element Scoped', label='table:element'), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
+print(tbl.place(xtable(s.singles.db, caption='Single Operators', label='table:singles')), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
 @
-\caption {The element based sampling criteria results. }
-\label{tbl:lcountl}
+\caption {The single operator selection strategy}
+\label{tbl:singles}
 \end{table*}

### 2015-01-15 src/analysis.Rnw
updates

@@
 <<results='asis'>>=
-print(tbl.place(xtable(s.singles.db, caption='Single Operators', label='table:singles')), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
+norder <- c('nmc','rv','ic','dc','nc','rc','vmc','cc','emv','m','cb','i','ri','rs','es','in')
+print(tbl.place(xtable(s.singles.db[norder,], caption='Single Operators', label='table:singles')), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
 @

### 2015-01-15 src/discussion.Rnw
nuke discussion

@@
 
-% About Randoop and Original
-From our data, we see that for original and generated test suites, the
-mutant reduction ratio and standard deviation were similar for stable strategies
-(where the standard deviation of the reduction achieved was less than half
-of the reduction achieved). This suggests that our analysis is equally
-applicable for both original test suites and generated ones.
-
-% About Randoop and Original
-Analyzing the scores further, we note that the correlation
-($R^2$) achieved by sampling is generally lower for generated test
-suites. As the sampling denominator increases, the correlation
-reduces drastically for generated test suites while correlation remains strong
-for original test suites.
-Secondly, we also observe that the multiplier factor $\beta_1$
-is smaller for generated test suites than original test suites. This
-observation holds good for all sampling and operator selection strategies
-examined.  Both these factors together suggest that generated
-test suites have a higher variability in their sampled mutation scores than
-original test suites. We note that since $\beta_1$ was generally smaller
-for generated test suites than original test suites, the full mutation score
-corresponding to a sampled mutation score for generated test suites would
-be lower than what would be expected from the original test suite.
-Further, the amount of mutant reduction possible such that the sampled
-mutation scores still has a high enough correlation with the total score
-is lower for generated test suites.
-
-% Different sampling strategies
-Considering different sampling strategies, based on their stability and mutation
-reduction achieved, we note that using simple sampling (\textit{sample(x)})
-produced the most stable results. For both generated and original test suites,
-this strategy produced valid results for all different scopes and sampling
-ratios. It also was able to achieve a highest mutation reduction of $72.63$,
-with high stability. That is, only $1.37\%$ of the original mutants were needed
-to produce a highly correlated ($R^2 = 0.97$) mutation score, with minimal deviation
-($\sigma = 6.36$) for original test suites. While the correlation is weaker for
-generated test suites it is still quite strong, with $R^2 = 0.90$
-
-Our \textit{round(x)}, the strategy of ignoring low complexity elements,
-did not pay off, with line scope having a tendency to become unstable and
-low correlated at low sampling ratios. At very low sampling ratio ($1/64$), the
-strategy with method scope also becomes unstable and low correlated. On the whole
-\textit{round(x)} did not perform as well as \textit{sample(x)}
-
-The strategy of ensuring coverage with \textit{ceil(x)} also did not perform
-well. While the results were generally stable, the reduction ratios achieved
-were lower than \textit{sample(x)}, with similar correlations.
-
-For line count strategies, only the external sampling produced
-consistent results, which were again not as good as \textit{round(x)}
-for similar reduction ratios. Secondly, we had hypothesized
-that coverage was a significant contributor to having a high
-correlation with the full mutation score. However we could find no
-evidence in support of this hypothesis with line, method, class, and
-project scope showing similar correlation and consistency at similar
-reduction ratios.
-
-The one per element strategy did not have stable results in general except
-for at the scope of line (at which point it was same as the count-per-element
-strategy).
-
-While the x\% per operator strategy produced consistent results, its
-consistency was not as good as \textit{sample(x)}, and was either on
-par with or worse than \textit{sample(x)} in $R^2$.
-
-Considering mutation operators, only three operators \textit{NC},
-\textit{RC},and \textit{DC} had consistent results (and only for
-original test suites). The n-selection strategy had high correlation and
-consistency (though low reduction ratio) until 7-selection (removing
-the seven most numerous operators) for both generated and original
-test suites.  Javalanche did not have a high mutation reduction ratio,
-though it had high $R^2$ for both kinds of test suites. The other
-operator selection methods performed poorly on generated test suites,
-while they had high correlation and reasonable stability on original test
-suites. However, for comparable mutation reduction levels, they all performed
-worse than random sampling strategies.
-
-Considering different sampling strategies, we see a few general patterns. The
-first is that sampling strategy can predict the final score with very
-minimal loss up to a fraction of $\frac{1}{64}$ of the total
-number of mutants. We did not cut off with the 99\% rule as mentioned
-byZhang et al.~\cite{zhang2013ase} (originally proposed
-by Offutt et al.~\cite{offutt1996experimental} for a different measurement),
-and instead observe that we obtained $R^2 = 0.97$ which provides
-a high confidence in the accuracy of prediction of the full score.
-
-The third "pattern" is that the simplest sampling scheme --- simple
-random sampling --- performs best compared to sampling schemes that
-tried to provide higher weight to specific elements based on specific
-criteria. Additionally, operator selection seems to be generally worse
-off in predicting the final mutation score than any of the random selection
-schemes.  In principle, if we could devise sampling methods that
-somehow captured only the most discriminative mutants for programs,
-they might perform better than any of these; our results suggest that
-most schemes that (we assume) aim at this goal do not in fact achieve
-the goal over a large body of programs, and so tend to perform worse
-than simply randomly sampling the whole pool of mutants, which has
-attractive simplicity in the absence of a better strategy.
+To be added.

### 2015-01-15 src/threats.Rnw
update

@@
 \section{Threats to Validity}
-While we have taken every care to ensure that our results are valid, and to eliminate the
-effects of random noise, our results are subject to the following threats
-to validity.
+While we have taken every care to ensure that our results are valid, and
+to eliminate the effects of random noise, our results are subject to the
+following threats to validity.
 
-Our results were observed on open source Java programs from the Github repository, using the
-maven build system. Further, only those projects that successfully completed mutation
-testing within a designated amount of time were chosen. This implies that if there is a
-confounding factor in play that affects the relation between the full mutation score and
-sampling mutation score, it might cause our results to be either wrong or less applicable.
+Our results were observed on open source Java programs from the Github
+repository, and Apache Commons Library, using the maven build system. Further,
+only those projects that successfully completed mutation testing within
+a designated amount of time were chosen.  This implies that if there is
+a confounding factor in play that affects the relation between the full
+mutation score and sampling mutation score, it might cause our results to
+be either wrong or less applicable.
 
-Secondly, we had to rely on the PIT mutation testing tool, and had to extend its capabilities
-to some extent for our purposes. Software bugs are a fact of life. While every care has been
-taken to avoid them, there is still some possibility of some bugs having escaped us.
+Secondly, we had to rely on the PIT mutation testing tool, and had to extend
+its capabilities to some extent for our purposes. Software bugs are a fact
+of life. While every care has been taken to avoid them, there is still some
+possibility of some bugs having escaped us.
+
+Finally, and most importanly, most of the previous research has been done on
+source level mutants. However, for a study of the size we have conducted,
+it is infeasible to rely on source level mutants (even using the bytecode
+based fast mutation evaluation provided by PIT, the mutation analysis took
+months to complete). This also means that we had to rely on translation of
+source level mutants to their bytecode equivalents, which was in most cases
+not a one to one process, and this could have introduced unintented errors.
+However, as we mentioned earlier, it is infeasible to run mutation analysis
+on source level for large programs using the tools we currently have. It is
+also important to evaluate different strategies on byte code based engines
+at least to provide guidance for testers trying to do the same.

### 2015-01-15 src/conclusion.Rnw
update

--- 2014-03-11 src/conclusion.Rnw
@@
 
-Our analysis suggests that simple random sampling, that is, at the project level works best when compared to more sophesticated schemes of sampling.
-Further, we also note that random sampling performs better in predicting final mutation score when compared against operator selection.
+Our analysis suggests that while some of the different strategies produce
+slightly advantageous mutation subsets, overall, the advantage thus gained
+is very little. None of the common operator selection strategies performed
+consistently well against random sampling while using either the utility or
+the mutation effectiveness criteria. While some of the individual operators
+such as \Pitrv, \Piti, \Pitri, and \Pites show promise in test utility,
+they do not stand out when we examine the mutation effectiveness in comparison
+to baseline.
 
-This suggests that the best way to reduce the computational requirements while trying to build a representative set is to randomly sample on the whole set of mutants directly.
+A similar result seems to be the case for operator based x\% selection
+strategy or even for the element based x\% strategy. They in general show a
+slight advantage in test utility which doesn't seem to translate to the
+strategy effectiveness in comparison with baseline.
+
+Thus we find that that none of the well known reduction strategies are actually
+able to consistenly select useful mutants, and the best path forward
+for a working tester is to rely on the simplest scheme of all -- the random
+selection of mutants.
+
+There is a second possible point of interest here: as with coverage
+metrics used to predict mutation scores~\cite{gopinath2014code}, using
+a large body of actual open source code to perform experiments seems
+to favor simple and easily-implemented approaches much more strongly
+than limited experiments on more academic subjects.  We speculate that
+the inadequacies in real world test suites may frequently be more simply
+predicted and evaluated than for typical research subjects, which may
+be smaller or involve less easily distinguished test suites.

### 2015-01-15 src/analysis.Rnw
updates
update

@@
 @
-\caption {The operator based fractional sample strategy}
+\caption {The operator based x\% sample strategy}
 \label{tbl:opsample}
@@
 @
-\caption {The element based fractional sample strategy}
+\caption {The element based x\% sample strategy}
 \label{tbl:element}
@@
 non-redundant test cases by discarding any test case that can be removed
-without letting any of the mutants escape. This is repeated $10$ times,
-and the average number of non-redundant test cases are found.
+without letting any of the mutants escape. This is repeated and averaged
+over multiple runs, and the average number of non-redundant test cases are
+found.
 

### 2015-01-16 src/analysis.Rnw
add Mutation details

@@
 is then divided by the original number of detected mutants.
+
+\begin{figure*}
+<<op,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+bcol <- '#2171B5'
+icol <- '#9ECAE0'
+m.db <- subset(allmutants.db, total > 0)
+d.db <- subset(allmutants.db, detected > 0)
+m.db$mutations <- m.db$mtotal * 100.0 / m.db$total
+d.db$detected <- d.db$mdetected * 100.0 / d.db$detected
+
+tmp1 <- subset(m.db, select=c("mutator","mutations"))
+tmp1$type <- "mutations"
+tmp2 <- subset(d.db, select=c("mutator","detected"))
+colnames(tmp2) <- c("mutator","mutations")
+tmp2$type <- "detected"
+tmp <- rbind(tmp1, tmp2)
+tmp$type <- factor(tmp$type, levels=c("mutations", "detected"))
+tmp$mutator <- factor(tmp$mutator, levels=c("nmc", "rv", "ic", "dc", "nc", "rc", "vmc", "cc", "emv", "m", "cb", "i", "ri", "rs", "es", "in"))
+options(warn=-1)
+ggplot(aes(y=mutations, x=mutator, fill=type),data=tmp) +
+  geom_boxplot(outlier.color=NA, outlier.shape=NA) +
+  scale_fill_manual(name = "Mutation Details", values = c(bcol, icol)
+                    , labels = c("mutations" = "Total mutations", "detected" = "Detected mutations")) +
+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
+ theme(axis.line = element_line(colour = "black"))
+ # coord_flip() +
+options(warn=0)
+# + stat_boxplot(geom ='errorbar') 
+#p1 <- ggplot(aes(y=mutations, x=mutator, fill=F),data=m.db) + geom_boxplot() + guides(fill=FALSE) + coord_flip()
+#p2 <- ggplot(aes(y=detected, x=mutator, fill=F),data=d.db) + geom_boxplot() + guides(fill=FALSE) + coord_flip()
+
+#grid.newpage()
+#pushViewport(viewport(layout = grid.layout(1, 2)))
+#print(p1, vp = vplayout(1, 1))
+#print(p2, vp = vplayout(1, 2))
+
+@
+\caption{The relative contribution of mutation operators in terms of fraction of mutants produced and detected.
+The produced mutants are shown with black outline while detected mutants have blue border and shade.}
+\end{figure*}

### 2015-01-16 src/paper.Rnw
update
add Mutation details

@@
 require(ggplot2)
+require(grid)
 require(MutSel)
+vplayout <- function(x, y) viewport(layout.pos.row = x, layout.pos.col = y)
+theme = theme_set(theme_minimal())
 @

### 2015-01-16 src/conclusion.Rnw
update

@@
 the mutation effectiveness criteria. While some of the individual operators
-such as \Pitrv, \Piti, \Pitri, and \Pites show promise in test utility,
+such as \Pitrv, \Piti, \Pitri, and \Pites~show promise in test utility,
 they do not stand out when we examine the mutation effectiveness in comparison

### 2015-01-16 src/analysis.Rnw
update

@@
 \begin{figure*}
-<<op,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+<<mutantdet,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
 bcol <- '#2171B5'
@@
 #print(p2, vp = vplayout(1, 2))
+@
+\caption{The relative contribution of mutation operators in terms of fraction of mutants produced and detected.}
+\end{figure*}
 
+\begin{figure*}
+<<mutanttest,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
+bcol <- '#2171B5'
+icol <- '#9ECAE0'
+m.db <- subset(allmutants.db, ncovering > 0)
+d.db <- subset(allmutants.db, nkilling > 0)
+m.db$covering <- m.db$tstcovering * 100.0 / m.db$ncovering
+d.db$killing <- d.db$tstkilling * 100.0 / d.db$nkilling
+
+tmp1 <- subset(m.db, select=c("mutator","covering"))
+colnames(tmp1) <- c("mutator","tests")
+tmp1$type <- "covering"
+
+tmp2 <- subset(d.db, select=c("mutator","killing"))
+colnames(tmp2) <- c("mutator","tests")
+tmp2$type <- "killing"
+
+tmp <- rbind(tmp1, tmp2)
+tmp$type <- factor(tmp$type, levels=c("covering", "killing"))
+tmp$mutator <- factor(tmp$mutator, levels=c("nmc", "rv", "ic", "dc", "nc", "rc", "vmc", "cc", "emv", "m", "cb", "i", "ri", "rs", "es", "in"))
+options(warn=-1)
+ggplot(aes(y=tests, x=mutator, fill=type),data=tmp) +
+  geom_boxplot(outlier.color=NA, outlier.shape=NA) +
+  scale_fill_manual(name = "Mutation Details", values = c(bcol, icol)
+                    , labels = c("covering" = "Total covering", "killing" = "Total killing")) +
+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
+ theme(axis.line = element_line(colour = "black"))
+options(warn=0)
 @
-\caption{The relative contribution of mutation operators in terms of fraction of mutants produced and detected.
-The produced mutants are shown with black outline while detected mutants have blue border and shade.}
+\caption{The relative contribution of mutation operators in terms of fraction of tests killed and covered.}
 \end{figure*}

### 2015-01-16 src/analysis.Rnw
update

@@
 d.db <- subset(allmutants.db, nkilling > 0)
-m.db$covering <- m.db$tstcovering * 100.0 / m.db$ncovering
-d.db$killing <- d.db$tstkilling * 100.0 / d.db$nkilling
+#m.db$covering <- m.db$tstcovering * 100.0 / m.db$ncovering
+m.db$covering <- m.db$tstcovering * 100.0 / m.db$ntests
+#d.db$killing <- d.db$tstkilling * 100.0 / d.db$nkilling
+d.db$killing <- d.db$tstkilling * 100.0 / d.db$ntests
 

### 2015-01-17 src/analysis.Rnw
update

@@
 <<results='asis'>>=
+eff <- function(v) {
+  v$strategy.effectiveness <- v$strategy.effectiveness - v$baseline.effectiveness
+  return(v)
+}
 tbl.place <- function(xtb) {
@@
 }
-print(tbl.place(xtable(s.selective.db, caption='Selective Strategy', label='table:selective')),include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
+print(tbl.place(xtable(eff(s.selective.db), caption='Selective Strategy', label='table:selective')),include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
 @
@@
 <<results='asis'>>=
-print(tbl.place(xtable(s.nselection.db, caption='N-Selection', label='table:nselection')), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
+print(tbl.place(xtable(eff(s.nselection.db), caption='N-Selection', label='table:nselection')), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
 @
@@
 <<results='asis'>>=
-print(tbl.place(xtable(s.opsample.db, caption='Operator x samples', label='table:opsample')), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
+print(tbl.place(xtable(eff(s.opsample.db), caption='Operator x samples', label='table:opsample')), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
 @
@@
 <<results='asis'>>=
-print(tbl.place(xtable(s.lmcp.db, caption='Element Scoped', label='table:element')), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
+print(tbl.place(xtable(eff(s.lmcp.db), caption='Element Scoped', label='table:element')), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
 @
@@
 norder <- c('nmc','rv','ic','dc','nc','rc','vmc','cc','emv','m','cb','i','ri','rs','es','in')
-print(tbl.place(xtable(s.singles.db[norder,], caption='Single Operators', label='table:singles')), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
+print(tbl.place(xtable(eff(s.singles.db[norder,]), caption='Single Operators', label='table:singles')), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
 @

### 2015-01-17 src/introduction.Rnw
added for alex

@@
 % possible.
-Consider any test in a test suite. It is written with the intent of
-checking for the absence of some (faulty) behavior. From the perspective of a
-a tester, the best testsuite is one that checks for the absence
-of the largest number of faulty behaviors. If tests were equivalent in the
-amount of behaviors that they verify, then the best testsuite would be one that
-encouraged adding the largest number of non-redundant test cases. However,
-it is possible that different tests are not equivalent in the number of
-behaviors that they check. We can approximate this to some extent by
-including the number of assert statements within each test~\footnote{We
-approximate the effect of exception-only test cases by starting the assert
-count from $1$ rather than $0$}.
+
+% Alex: added
+Given a set of mutants and a universe of test cases, we can approximate the
+minimal set of test cases required to kill those mutants.\footnote{We only
+approximate this, with greedy methods, due to the high cost of computing a
+perfect minimal set, as established in the test case selection literature
+\cite{YooHarman}.}  Ideally, we would like a set of mutants that require
+as many test cases as possible, if we assume that the original set of test
+cases is populated with useful, non-redundant test cases.  While the suites
+of many open source programs are far from adequate, they should satisfy that
+requirement:  each test was almost always added by considerable manual labor,
+and was at least believed to be useful.  Therefore, any tests omitted likely
+indicate a potential to miss faults.  A good mutation selection strategy,
+therefore, should 1) be as close to the original set of mutants as possible,
+in terms of the test cases it requires in a minimal suite and 2) require
+more test cases than a randomly selected set of mutants of the same size.
+
+All test cases are not created equal, of course -- we use assertion counts
+and execution time as other measures.
+
+% Alex: rm
+% Consider any test in a test suite. It is written with the intent of
+% checking for the absence of some (faulty) behavior. From the perspective of a
+% a tester, the best testsuite is one that checks for the absence
+% of the largest number of faulty behaviors. If tests were equivalent in the
+% amount of behaviors that they verify, then the best testsuite would be one that
+% encouraged adding the largest number of non-redundant test cases. However,
+% it is possible that different tests are not equivalent in the number of
+% behaviors that they check. We can approximate this to some extent by
+% including the number of assert statements within each test~\footnote{We
+% approximate the effect of exception-only test cases by starting the assert
+% count from $1$ rather than $0$}.
 

### 2015-01-17 src/analysis.Rnw
update analysis

@@
+<<results='asis'>>=
+mintc.t.test <- function(db) {
+  return(with(db, t.test(sel.mintc,sample.mintc, paired=T, alternative=c("greater"))))
+}
+mutant.t.test <- function(db) {
+  return(with(db, t.test(sel.all.killtcd_mutant,sample.all.killtcd_mutant, paired=T, alternative=c("greater"))))
+}
+db <- subset(common.db, kind == "nsel")
+nsel.t <- mintc.t.test(db)
+nsel.m <- mutant.t.test(db)
+#-- Insufficient evidence that sel.mintc is greater than random selection
+db <- subset(common.db, kind == "opsel")
+opsel.t <- mintc.t.test(db)
+opsel.m <- mutant.t.test(db)
+#-- Insufficient evidence that sel.mintc is greater than random selection
+db <- subset(common.db, kind == "single")
+single.t <- mintc.t.test(db)
+single.m <- mutant.t.test(db)
+#-- Insufficient evidence that sel.mintc is greater than random selection
+db <- subset(common.db, kind == "opx")
+opx.t <- mintc.t.test(db)
+opx.m <- mutant.t.test(db)
+#-- Insufficient evidence that sel.mintc is greater than random selection
+db <- subset(common.db, kind == "lmcp")
+lmcp.t <- mintc.t.test(db)
+lmcp.m <- mutant.t.test(db)
+# #---------------------------------------
+# # nmc     nc       rc       dc       rv       ic       cc
+# # emv      vmc      m       cb       i        ri       rs       es in
+# db <- subset(common.db, operator == "rm_nmc")
+# with(db, t.test(sel.mintc,sample.mintc, paired=T, alternative=c("greater")))
+# with(db, t.test(sel.all.killtcd_mutant,sample.all.killtcd_mutant, paired=T, alternative=c("greater")))
+# #---------------------------------------
+# db <- subset(common.db, operator == "cc")
+# with(db, t.test(sel.mintc,sample.mintc, paired=T, alternative=c("greater")))
+# with(db, t.test(sel.all.killtcd_mutant,sample.all.killtcd_mutant, paired=T, alternative=c("greater")))
+# #---------------------------------------
+# db <- subset(common.db, operator == "clazz")
+# with(db, t.test(sel.mintc,sample.mintc, paired=T)) #, alternative=c("greater")))
+# with(db, t.test(sel.all.killtcd_mutant,sample.all.killtcd_mutant, paired=T))#, alternative=c("greater")))
+@
 \begin{table*}[!ht]
@@
 
-\textit{Strategy effectiveness} is computed by collecting all the test cases
-that detected any of the mutants in the selected subset, and applying these
-test cases to the complete set of mutants. The mutation score thus obtained
-is then divided by the original number of detected mutants.
-
-Similarly \textit{baseline effectiveness} is computed by getting the number
+\textit{Baseline effectiveness} is computed by getting the number
 of mutants selected by the strategy, and selecting the same number of mutants
@@
 is then divided by the original number of detected mutants.
+
+\textit{Strategy effectiveness} is computed by collecting all the test cases
+that detected any of the mutants in the selected subset, and applying these
+test cases to the complete set of mutants. The mutation score thus obtained
+is then divided by the original number of detected mutants. This is reported
+as difference from the correspondign baseline effectiveness.
 

### 2015-01-17 src/analysis.Rnw
split into different files

--- 2015-01-16 src/analysis.Rnw
@@
-\begin{table*}[!ht]
-%\caption*{Selective}
-<<results='asis'>>=
-tbl.place <- function(xtb) {
-  align(xtb) <- "p{0.1\\textwidth}|p{0.15\\textwidth}|p{0.15\\textwidth}|p{0.15\\textwidth}|p{0.15\\textwidth}|p{0.15\\textwidth}"
-  return(xtb)
-}
-print(tbl.place(xtable(s.selective.db, caption='Selective Strategy', label='table:selective')),include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
+<<t.tests,child='ttests.Rnw'>>=
 @
-\caption {The operator selection strategy}
-\label{tbl:selective}
-\end{table*}
-
-\begin{table*}[!ht]
-%\caption*{N-Selection}
-<<results='asis'>>=
-print(tbl.place(xtable(s.nselection.db, caption='N-Selection', label='table:nselection')), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
+<<tblsingles, child='tables.Rnw'>>=
 @
-\caption {The N-selective strategy}
-\label{tbl:nselection}
-\end{table*}
-
-\begin{table*}[!ht]
-%\caption*{Operator Samples x\%}
-<<results='asis'>>=
-print(tbl.place(xtable(s.opsample.db, caption='Operator x samples', label='table:opsample')), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
-@
-\caption {The operator based x\% sample strategy}
-\label{tbl:opsample}
-\end{table*}
-
-\begin{table*}[!ht]
-%\caption*{Element Scoped}
-<<results='asis'>>=
-print(tbl.place(xtable(s.lmcp.db, caption='Element Scoped', label='table:element')), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
-@
-\caption {The element based x\% sample strategy}
-\label{tbl:element}
-\end{table*}
-
-\begin{table*}[!ht]
-%\caption*{Single Operators}
-<<results='asis'>>=
-norder <- c('nmc','rv','ic','dc','nc','rc','vmc','cc','emv','m','cb','i','ri','rs','es','in')
-print(tbl.place(xtable(s.singles.db[norder,], caption='Single Operators', label='table:singles')), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
-@
-\caption {The single operator selection strategy}
-\label{tbl:singles}
-\end{table*}
 
@@
 Similarly \textit{assert utility} of a strategy is computed as the difference
-between the number of assertions of non-redundant test cases the mutatnt
+between the number of assertions of non-redundant test cases the mutant
 selection achieved and the number of assertions the test cases for random
@@
 
+\textit{Strategy effectiveness} is computed by collecting all the test cases
+that detected any of the mutants in the selected subset, and applying these
+test cases to the complete set of mutants. The mutation score thus obtained
+is then divided by the original number of detected mutants. This is reported
+as difference from the corresponding baseline effectiveness.
+
 \begin{figure*}
-<<mutantdet,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-bcol <- '#2171B5'
-icol <- '#9ECAE0'
-m.db <- subset(allmutants.db, total > 0)
-d.db <- subset(allmutants.db, detected > 0)
-m.db$mutations <- m.db$mtotal * 100.0 / m.db$total
-d.db$detected <- d.db$mdetected * 100.0 / d.db$detected
-
-tmp1 <- subset(m.db, select=c("mutator","mutations"))
-tmp1$type <- "mutations"
-tmp2 <- subset(d.db, select=c("mutator","detected"))
-colnames(tmp2) <- c("mutator","mutations")
-tmp2$type <- "detected"
-tmp <- rbind(tmp1, tmp2)
-tmp$type <- factor(tmp$type, levels=c("mutations", "detected"))
-tmp$mutator <- factor(tmp$mutator, levels=c("nmc", "rv", "ic", "dc", "nc", "rc", "vmc", "cc", "emv", "m", "cb", "i", "ri", "rs", "es", "in"))
-options(warn=-1)
-ggplot(aes(y=mutations, x=mutator, fill=type),data=tmp) +
-  geom_boxplot(outlier.color=NA, outlier.shape=NA) +
-  scale_fill_manual(name = "Mutation Details", values = c(bcol, icol)
-                    , labels = c("mutations" = "Total mutations", "detected" = "Detected mutations")) +
- theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
- theme(axis.line = element_line(colour = "black"))
- # coord_flip() +
-options(warn=0)
-# + stat_boxplot(geom ='errorbar') 
-#p1 <- ggplot(aes(y=mutations, x=mutator, fill=F),data=m.db) + geom_boxplot() + guides(fill=FALSE) + coord_flip()
-#p2 <- ggplot(aes(y=detected, x=mutator, fill=F),data=d.db) + geom_boxplot() + guides(fill=FALSE) + coord_flip()
-
-#grid.newpage()
-#pushViewport(viewport(layout = grid.layout(1, 2)))
-#print(p1, vp = vplayout(1, 1))
-#print(p2, vp = vplayout(1, 2))
+<<mutantdet, child='fig.mutantdist.Rnw'>>=
 @
@@
 \begin{figure*}
-<<mutanttest,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
-bcol <- '#2171B5'
-icol <- '#9ECAE0'
-m.db <- subset(allmutants.db, ncovering > 0)
-d.db <- subset(allmutants.db, nkilling > 0)
-#m.db$covering <- m.db$tstcovering * 100.0 / m.db$ncovering
-m.db$covering <- m.db$tstcovering * 100.0 / m.db$ntests
-#d.db$killing <- d.db$tstkilling * 100.0 / d.db$nkilling
-d.db$killing <- d.db$tstkilling * 100.0 / d.db$ntests
-
-tmp1 <- subset(m.db, select=c("mutator","covering"))
-colnames(tmp1) <- c("mutator","tests")
-tmp1$type <- "covering"
-
-tmp2 <- subset(d.db, select=c("mutator","killing"))
-colnames(tmp2) <- c("mutator","tests")
-tmp2$type <- "killing"
-
-tmp <- rbind(tmp1, tmp2)
-tmp$type <- factor(tmp$type, levels=c("covering", "killing"))
-tmp$mutator <- factor(tmp$mutator, levels=c("nmc", "rv", "ic", "dc", "nc", "rc", "vmc", "cc", "emv", "m", "cb", "i", "ri", "rs", "es", "in"))
-options(warn=-1)
-ggplot(aes(y=tests, x=mutator, fill=type),data=tmp) +
-  geom_boxplot(outlier.color=NA, outlier.shape=NA) +
-  scale_fill_manual(name = "Mutation Details", values = c(bcol, icol)
-                    , labels = c("covering" = "Total covering", "killing" = "Total killing")) +
- theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
- theme(axis.line = element_line(colour = "black"))
-options(warn=0)
+<<testdet, child='fig.testdist.Rnw'>>=
 @

### 2015-01-17 src/fig.mutantdist.Rnw
split into different files

<<mutantdet,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
bcol <- '#2171B5'
icol <- '#9ECAE0'
m.db <- subset(allmutants.db, total > 0)
d.db <- subset(allmutants.db, detected > 0)
m.db$mutations <- m.db$mtotal * 100.0 / m.db$total
d.db$detected <- d.db$mdetected * 100.0 / d.db$detected

tmp1 <- subset(m.db, select=c("mutator","mutations"))
tmp1$type <- "mutations"
tmp2 <- subset(d.db, select=c("mutator","detected"))
colnames(tmp2) <- c("mutator","mutations")
tmp2$type <- "detected"
tmp <- rbind(tmp1, tmp2)
tmp$type <- factor(tmp$type, levels=c("mutations", "detected"))
tmp$mutator <- factor(tmp$mutator, levels=c("nmc", "rv", "ic", "dc", "nc", "rc", "vmc", "cc", "emv", "m", "cb", "i", "ri", "rs", "es", "in"))
options(warn=-1)
ggplot(aes(y=mutations, x=mutator, fill=type),data=tmp) +
  geom_boxplot(outlier.color=NA, outlier.shape=NA) +
  scale_fill_manual(name = "Mutation Details", values = c(bcol, icol)
                    , labels = c("mutations" = "Total mutations", "detected" = "Detected mutations")) +
 theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
 theme(axis.line = element_line(colour = "black"))
 # coord_flip() +
options(warn=0)
# + stat_boxplot(geom ='errorbar') 
#p1 <- ggplot(aes(y=mutations, x=mutator, fill=F),data=m.db) + geom_boxplot() + guides(fill=FALSE) + coord_flip()
#p2 <- ggplot(aes(y=detected, x=mutator, fill=F),data=d.db) + geom_boxplot() + guides(fill=FALSE) + coord_flip()

#grid.newpage()
#pushViewport(viewport(layout = grid.layout(1, 2)))
#print(p1, vp = vplayout(1, 1))
#print(p2, vp = vplayout(1, 2))
@

### 2015-01-17 src/fig.testdist.Rnw
split into different files

<<testdet,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
bcol <- '#2171B5'
icol <- '#9ECAE0'
m.db <- subset(allmutants.db, ncovering > 0)
d.db <- subset(allmutants.db, nkilling > 0)
#m.db$covering <- m.db$tstcovering * 100.0 / m.db$ncovering
m.db$covering <- m.db$tstcovering * 100.0 / m.db$ntests
#d.db$killing <- d.db$tstkilling * 100.0 / d.db$nkilling
d.db$killing <- d.db$tstkilling * 100.0 / d.db$ntests

tmp1 <- subset(m.db, select=c("mutator","covering"))
colnames(tmp1) <- c("mutator","tests")
tmp1$type <- "covering"

tmp2 <- subset(d.db, select=c("mutator","killing"))
colnames(tmp2) <- c("mutator","tests")
tmp2$type <- "killing"

tmp <- rbind(tmp1, tmp2)
tmp$type <- factor(tmp$type, levels=c("covering", "killing"))
tmp$mutator <- factor(tmp$mutator, levels=c("nmc", "rv", "ic", "dc", "nc", "rc", "vmc", "cc", "emv", "m", "cb", "i", "ri", "rs", "es", "in"))
options(warn=-1)
ggplot(aes(y=tests, x=mutator, fill=type),data=tmp) +
  geom_boxplot(outlier.color=NA, outlier.shape=NA) +
  scale_fill_manual(name = "Mutation Details", values = c(bcol, icol)
                    , labels = c("covering" = "Total covering", "killing" = "Total killing")) +
 theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
 theme(axis.line = element_line(colour = "black"))
options(warn=0)
@

### 2015-01-17 src/tables.Rnw
split into different files

\begin{table*}[!ht]
%\caption*{Selective}
<<results='asis'>>=
eff <- function(v) {
  v$strategy.effectiveness <- v$strategy.effectiveness - v$baseline.effectiveness
  return(v)
}
tbl.place <- function(xtb) {
  align(xtb) <- "p{0.1\\textwidth}|p{0.15\\textwidth}|p{0.15\\textwidth}|p{0.15\\textwidth}|p{0.15\\textwidth}|p{0.15\\textwidth}"
  return(xtb)
}
print(tbl.place(xtable(eff(s.selective.db), caption='Selective Strategy', label='table:selective')),include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
@
\caption {The operator selection strategy}
\label{tbl:selective}
\end{table*}

\begin{table*}[!ht]
%\caption*{N-Selection}
<<results='asis'>>=
print(tbl.place(xtable(eff(s.nselection.db), caption='N-Selection', label='table:nselection')), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
@
\caption {The N-selective strategy}
\label{tbl:nselection}
\end{table*}

\begin{table*}[!ht]
%\caption*{Operator Samples x\%}
<<results='asis'>>=
print(tbl.place(xtable(eff(s.opsample.db), caption='Operator x samples', label='table:opsample')), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
@
\caption {The operator based x\% sample strategy}
\label{tbl:opsample}
\end{table*}

\begin{table*}[!ht]
%\caption*{Element Scoped}
<<results='asis'>>=
print(tbl.place(xtable(eff(s.lmcp.db), caption='Element Scoped', label='table:element')), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
@
\caption {The element based x\% sample strategy}
\label{tbl:element}
\end{table*}

\begin{table*}[!ht]
<<tblsingles, child='tbl.singleop.Rnw'>>=
@
%\caption*{Single Operators}
\caption {The single operator selection strategy}
\label{tbl:singles}
\end{table*}

### 2015-01-17 src/ttests.Rnw
split into different files

<<tests,results='asis'>>=
mintc.t.test <- function(db) {
  return(with(db, t.test(sel.mintc,sample.mintc, paired=T, alternative=c("greater"))))
}
mutant.t.test <- function(db) {
  return(with(db, t.test(sel.all.killtcd_mutant,sample.all.killtcd_mutant, paired=T, alternative=c("greater"))))
}
db <- subset(common.db, kind == "nsel")
nsel.t <- mintc.t.test(db)
nsel.m <- mutant.t.test(db)
#-- Insufficient evidence that sel.mintc is greater than random selection
db <- subset(common.db, kind == "opsel")
opsel.t <- mintc.t.test(db)
opsel.m <- mutant.t.test(db)
#-- Insufficient evidence that sel.mintc is greater than random selection
db <- subset(common.db, kind == "single")
single.t <- mintc.t.test(db)
single.m <- mutant.t.test(db)
#-- Insufficient evidence that sel.mintc is greater than random selection
db <- subset(common.db, kind == "opx")
opx.t <- mintc.t.test(db)
opx.m <- mutant.t.test(db)
#-- Insufficient evidence that sel.mintc is greater than random selection
db <- subset(common.db, kind == "lmcp")
lmcp.t <- mintc.t.test(db)
lmcp.m <- mutant.t.test(db)
# #---------------------------------------
# # nmc     nc       rc       dc       rv       ic       cc
# # emv      vmc      m       cb       i        ri       rs       es in
# db <- subset(common.db, operator == "rm_nmc")
# with(db, t.test(sel.mintc,sample.mintc, paired=T, alternative=c("greater")))
# with(db, t.test(sel.all.killtcd_mutant,sample.all.killtcd_mutant, paired=T, alternative=c("greater")))
# #---------------------------------------
# db <- subset(common.db, operator == "cc")
# with(db, t.test(sel.mintc,sample.mintc, paired=T, alternative=c("greater")))
# with(db, t.test(sel.all.killtcd_mutant,sample.all.killtcd_mutant, paired=T, alternative=c("greater")))
# #---------------------------------------
# db <- subset(common.db, operator == "clazz")
# with(db, t.test(sel.mintc,sample.mintc, paired=T)) #, alternative=c("greater")))
# with(db, t.test(sel.all.killtcd_mutant,sample.all.killtcd_mutant, paired=T))#, alternative=c("greater")))
@

### 2015-01-17 src/analysis.Rnw
update the analysis part

@@
 
+Say the original set of mutants is given my $M$, then the reduced set of
+mutants is given by $M_{strategy}$. The strategy choses $|M_{strategy}|$
+mutants on its application. Test suite composed of test cases that
+are able to kill any of the mutants of $M_{strategy}$ is given by
+$T_{strategy}$. The total number of asserts on tests under $T_{strategy}$
+is given by $asserts(T_{strategy})$. We find a minimal test suite that
+is capable of killing all mutants under $M_{strategy}$ by a greedy strategy
+of iteratively choosing the test cases with the largest amount of kills
+for remaining mutants, and is given by $min(T_{strategy})$. Similarly,
+for baseline, we use a strategy of randomly choosing the mutants from the
+original set with number of mutants chosen same as the corresponding
+number of mutants that the strategy under consideration chose.
+That is, $|M_{strategy}| = |M_{random}|$. Given any set of tests $T$,
+the total number of mutants that can be killed by the test cases in $T$
+is given by $k(T)$, and those mutants that are covered by the test cases
+are given by $c(T)$.
+
 The \textit{test utility} is computed as the difference between the number
@@
 The result is reported as a percentage of the non-redundant tests of the random
-sample which is taken as the baseline.
+sample which is taken as the baseline. That is, test utility is given by
+$\left(\frac{|min(T_{strategy})|}{|min(T_{random})|}-1\right)\times 100.0$
 
@@
 the asserts of the non-redundant tests of the random sample which is taken
-as the baseline.
+as the baseline. It is given by
+$\left(\frac{|asserts(min(T_{strategy}))|}{|asserts(min(T_{random}))|}-1\right)\times 100.0$
 
@@
 applying the same test cases against the original set of mutants. The result
-is then divided by the original number of detected mutants.
+is then divided by the original number of detected mutants. It is given by
+$\frac{k(T_{random})}{k(M)}\times 100.0$.
 
@@
 test cases to the complete set of mutants. The mutation score thus obtained
-is then divided by the original number of detected mutants. This is reported
-as difference from the corresponding baseline effectiveness.
+is then divided by the original number of detected mutants, giving
+$\frac{k(T_{strategy})}{k(M)}$
+
+This is reported as difference from the corresponding baseline effectiveness,
+given by 
+$\frac{k(T_{strategy}) - k(T_{random})}{k(M)}\times100.0$.
 
@@
 \end{figure*}
+
+\subsection{Statistical tests}
+To compute the actual advantage gained by each of the different strategies, we
+calculated the paired t-test between the number of test cases reported by the
+strategy, and that of random selection of the same number of operators as
+baseline.
+
+We also calculated the paired t-test between the number of mutants from the
+full set which were killed by the test cases killing any of the mutants from
+the selected mutants by mutation reduction strategy.

### 2015-01-17 src/analysis.Rnw
update analysis

@@
 is then divided by the original number of detected mutants. It is given by
-$\frac{k(T_{random})}{k(M)}\times 100.0$.
+$\frac{|k(T_{random})|}{|k(M)|}\times 100.0$.
 
@@
 test cases to the complete set of mutants. The mutation score thus obtained
-is then divided by the original number of detected mutants, giving
-$\frac{k(T_{strategy})}{k(M)}$
-
+is then divided by the original number of detected mutants.
 This is reported as difference from the corresponding baseline effectiveness,
 given by 
-$\frac{k(T_{strategy}) - k(T_{random})}{k(M)}\times100.0$.
+$\frac{|k(T_{strategy})| - |k(T_{random})|}{|k(M)|}\times100.0$.
 

### 2015-01-17 src/analysis.Rnw
update

@@
 strategy, and that of random selection of the same number of operators as
-baseline.
+baseline, that is 
+\[T.test\left(T_{strategy}\sim{}T_{random}\right)\]
 
@@
 full set which were killed by the test cases killing any of the mutants from
-the selected mutants by mutation reduction strategy.
+the selected mutants by mutation reduction strategy. That is
+\[T.test\left(k(T_{strategy})\sim{}k(T_{random})\right)\]
+
+\begin{table*}[!ht]
+<<tblttest, child='tbl.ttests.Rnw'>>=
+@
+%\caption*{Single Operators}
+\caption {The t-test results}
+\label{tbl:ttests}
+\end{table*}

### 2015-01-17 src/ttests.Rnw
update

@@
 mintc.t.test <- function(db) {
-  return(with(db, t.test(sel.mintc,sample.mintc, paired=T, alternative=c("greater"))))
+  return(with(db, t.test(sel.mintc,sample.mintc, paired=T))) #, alternative=c("greater"))))
 }
 mutant.t.test <- function(db) {
-  return(with(db, t.test(sel.all.killtcd_mutant,sample.all.killtcd_mutant, paired=T, alternative=c("greater"))))
+  return(with(db, t.test(sel.all.killtcd_mutant,sample.all.killtcd_mutant, paired=T))) #, alternative=c("greater"))))
 }
@@
 # with(db, t.test(sel.all.killtcd_mutant,sample.all.killtcd_mutant, paired=T))#, alternative=c("greater")))
+db <- subset(common.db, operator=="constrained")
+constrained.t <- mintc.t.test(db)
+constrained.m <- mutant.t.test(db)
+
+db <- subset(common.db, operator=="eselective")
+eselective.t <- mintc.t.test(db)
+eselective.m <- mutant.t.test(db)
+
+db <- subset(common.db, operator=="javalanche")
+javalanche.t <- mintc.t.test(db)
+javalanche.m <- mutant.t.test(db)
+
+db <- subset(common.db, operator=="varreduction")
+variable.t <- mintc.t.test(db)
+variable.m <- mutant.t.test(db)
+
+db <- subset(common.db, operator=="sdl")
+sdl.t <- mintc.t.test(db)
+sdl.m <- mutant.t.test(db)
+
+db <- subset(common.db, operator=="line")
+line.t <- mintc.t.test(db)
+line.m <- mutant.t.test(db)
+
+db <- subset(common.db, operator=="method")
+method.t <- mintc.t.test(db)
+method.m <- mutant.t.test(db)
+
+db <- subset(common.db, operator=="clazz")
+clazz.t <- mintc.t.test(db)
+clazz.m <- mutant.t.test(db)
+
+# rm_none      rm_nmc       rm_nc        rm_rc        rm_dc        rm_rv
+# rm_ic        rm_cc       rm_emv       rm_vmc       rm_m         rm_cb
+# rm_i         rm_ri        rm_rs        rm_es       
+db <- subset(common.db, operator=="rm_nmc")
+rm.nmc.t <- mintc.t.test(db)
+rm.nmc.m <- mutant.t.test(db)
+
+db <- subset(common.db, operator=="rm_rv")
+rm.rv.t <- mintc.t.test(db)
+rm.rv.m <- mutant.t.test(db)
+
+db <- subset(common.db, operator=="rm_ic")
+rm.ic.t <- mintc.t.test(db)
+rm.ic.m <- mutant.t.test(db)
+
+db <- subset(common.db, operator=="rm_dc")
+rm.dc.t <- mintc.t.test(db)
+rm.dc.m <- mutant.t.test(db)
+
+db <- subset(common.db, operator=="rm_nc")
+rm.nc.t <- mintc.t.test(db)
+rm.nc.m <- mutant.t.test(db)
+
+db <- subset(common.db, operator=="rm_rc")
+rm.rc.t <- mintc.t.test(db)
+rm.rc.m <- mutant.t.test(db)
+
+db <- subset(common.db, operator=="rm_vmc")
+rm.vmc.t <- mintc.t.test(db)
+rm.vmc.m <- mutant.t.test(db)
+
+db <- subset(common.db, operator=="rm_cc")
+rm.cc.t <- mintc.t.test(db)
+rm.cc.m <- mutant.t.test(db)
+
+db <- subset(common.db, operator=="rm_emv")
+rm.emv.t <- mintc.t.test(db)
+rm.emv.m <- mutant.t.test(db)
+
+db <- subset(common.db, operator=="rm_m")
+rm.m.t <- mintc.t.test(db)
+rm.m.m <- mutant.t.test(db)
+
+db <- subset(common.db, operator=="rm_cb")
+rm.cb.t <- mintc.t.test(db)
+rm.cb.m <- mutant.t.test(db)
+
+db <- subset(common.db, operator=="rm_i")
+rm.i.t <- mintc.t.test(db)
+rm.i.m <- mutant.t.test(db)
+
+db <- subset(common.db, operator=="rm_ri")
+rm.ri.t <- mintc.t.test(db)
+rm.ri.m <- mutant.t.test(db)
+
+db <- subset(common.db, operator=="rm_rs")
+rm.rs.t <- mintc.t.test(db)
+rm.rs.m <- mutant.t.test(db)
+
+db <- subset(common.db, operator=="rm_es")
+rm.es.t <- mintc.t.test(db)
+rm.es.m <- mutant.t.test(db)
+
+db <- subset(common.db, operator=="rm_in")
+rm.in.t <- mintc.t.test(db)
+rm.in.m <- mutant.t.test(db)
+
 @

### 2015-01-17 src/tbl.ttests.Rnw
update

<<results='asis'>>=
t.test.table <- data.frame(u.mean=NA,u.CI.high=NA,u.CI.low=NA,u.p.value=NA, m.mean=NA,m.CI.high=NA,m.CI.low=NA,m.p.value=NA)[numeric(0),]

#t.test.table['N-Selection',]            <- c(nsel.t$estimate,nsel.t$conf.int[1],nsel.t$conf.int[2],nsel.t$p.value, nsel.m$estimate,nsel.m$conf.int[1],nsel.m$conf.int[2],nsel.m$p.value)

#t.test.table['Operator-Selection (all)',] <- c(opsel.t$estimate,opsel.t$conf.int[1],opsel.t$conf.int[2],opsel.t$p.value)
t.test.table['Constrained Selection',] <- c(constrained.t$estimate,constrained.t$conf.int[1],constrained.t$conf.int[2],constrained.t$p.value,constrained.m$estimate,constrained.m$conf.int[1],constrained.m$conf.int[2],constrained.m$p.value)
t.test.table['E-Selective',]           <- c(eselective.t$estimate,eselective.t$conf.int[1],eselective.t$conf.int[2],eselective.t$p.value, eselective.m$estimate,eselective.m$conf.int[1],eselective.m$conf.int[2],eselective.m$p.value)
t.test.table['Javalanche',]            <- c(javalanche.t$estimate,javalanche.t$conf.int[1],javalanche.t$conf.int[2],javalanche.t$p.value, javalanche.m$estimate,javalanche.m$conf.int[1],javalanche.m$conf.int[2],javalanche.m$p.value)
t.test.table['VariableReduction',]     <- c(variable.t$estimate,variable.t$conf.int[1],variable.t$conf.int[2],variable.t$p.value, variable.m$estimate,variable.m$conf.int[1],variable.m$conf.int[2],variable.m$p.value)
t.test.table['Statement Deletion',]    <- c(sdl.t$estimate,sdl.t$conf.int[1],sdl.t$conf.int[2],sdl.t$p.value, sdl.m$estimate,sdl.m$conf.int[1],sdl.m$conf.int[2],sdl.m$p.value)

t.test.table['SingleOp-Selection',]    <- c(single.t$estimate,single.t$conf.int[1],single.t$conf.int[2],single.t$p.value, single.m$estimate,single.m$conf.int[1],single.m$conf.int[2],single.m$p.value)

t.test.table['Operator x\\% Selection',]        <- c(opx.t$estimate,opx.t$conf.int[1],opx.t$conf.int[2],opx.t$p.value, opx.m$estimate,opx.m$conf.int[1],opx.m$conf.int[2],opx.m$p.value)
t.test.table['Line Scoped',]           <- c(line.t$estimate,line.t$conf.int[1],line.t$conf.int[2],line.t$p.value, line.m$estimate,line.m$conf.int[1],line.m$conf.int[2],line.m$p.value)
t.test.table['Method Scoped',]         <- c(method.t$estimate,method.t$conf.int[1],method.t$conf.int[2],method.t$p.value, method.m$estimate,method.m$conf.int[1],method.m$conf.int[2],method.m$p.value)
t.test.table['Class Scoped',]          <- c(clazz.t$estimate,clazz.t$conf.int[1],clazz.t$conf.int[2],clazz.t$p.value, clazz.m$estimate,clazz.m$conf.int[1],clazz.m$conf.int[2],clazz.m$p.value)

t.test.table['N-Selection -nmc',]            <- c(rm.nmc.t$estimate,rm.nmc.t$conf.int[1],rm.nmc.t$conf.int[2],rm.nmc.t$p.value, rm.nmc.m$estimate,rm.nmc.m$conf.int[1],rm.nmc.m$conf.int[2],rm.nmc.m$p.value)
t.test.table['N-Selection -rv',]            <- c(rm.rv.t$estimate,rm.rv.t$conf.int[1],rm.rv.t$conf.int[2],rm.rv.t$p.value, rm.rv.m$estimate,rm.rv.m$conf.int[1],rm.rv.m$conf.int[2],rm.rv.m$p.value)
t.test.table['N-Selection -ic',]            <- c(rm.ic.t$estimate,rm.ic.t$conf.int[1],rm.ic.t$conf.int[2],rm.ic.t$p.value, rm.ic.m$estimate,rm.ic.m$conf.int[1],rm.ic.m$conf.int[2],rm.ic.m$p.value)
t.test.table['N-Selection -dc',]            <- c(rm.dc.t$estimate,rm.dc.t$conf.int[1],rm.dc.t$conf.int[2],rm.dc.t$p.value, rm.dc.m$estimate,rm.dc.m$conf.int[1],rm.dc.m$conf.int[2],rm.dc.m$p.value)
t.test.table['N-Selection -nc',]            <- c(rm.nc.t$estimate,rm.nc.t$conf.int[1],rm.nc.t$conf.int[2],rm.nc.t$p.value, rm.nc.m$estimate,rm.nc.m$conf.int[1],rm.nc.m$conf.int[2],rm.nc.m$p.value)
t.test.table['N-Selection -rc',]            <- c(rm.rc.t$estimate,rm.rc.t$conf.int[1],rm.rc.t$conf.int[2],rm.rc.t$p.value, rm.rc.m$estimate,rm.rc.m$conf.int[1],rm.rc.m$conf.int[2],rm.rc.m$p.value)
t.test.table['N-Selection -vmc',]            <- c(rm.vmc.t$estimate,rm.vmc.t$conf.int[1],rm.vmc.t$conf.int[2],rm.vmc.t$p.value, rm.vmc.m$estimate,rm.vmc.m$conf.int[1],rm.vmc.m$conf.int[2],rm.vmc.m$p.value)
t.test.table['N-Selection -m',]            <- c(rm.m.t$estimate,rm.m.t$conf.int[1],rm.m.t$conf.int[2],rm.m.t$p.value, rm.m.m$estimate,rm.m.m$conf.int[1],rm.m.m$conf.int[2],rm.m.m$p.value)
t.test.table['N-Selection -cb',]            <- c(rm.cb.t$estimate,rm.cb.t$conf.int[1],rm.cb.t$conf.int[2],rm.cb.t$p.value, rm.cb.m$estimate,rm.cb.m$conf.int[1],rm.cb.m$conf.int[2],rm.cb.m$p.value)
t.test.table['N-Selection -i',]            <- c(rm.i.t$estimate,rm.i.t$conf.int[1],rm.i.t$conf.int[2],rm.i.t$p.value, rm.i.m$estimate,rm.i.m$conf.int[1],rm.i.m$conf.int[2],rm.i.m$p.value)
t.test.table['N-Selection -ri',]            <- c(rm.ri.t$estimate,rm.ri.t$conf.int[1],rm.ri.t$conf.int[2],rm.ri.t$p.value, rm.ri.m$estimate,rm.ri.m$conf.int[1],rm.ri.m$conf.int[2],rm.ri.m$p.value)
t.test.table['N-Selection -rs',]            <- c(rm.rs.t$estimate,rm.rs.t$conf.int[1],rm.rs.t$conf.int[2],rm.rs.t$p.value, rm.rs.m$estimate,rm.rs.m$conf.int[1],rm.rs.m$conf.int[2],rm.rs.m$p.value)
t.test.table['N-Selection -es',]            <- c(rm.es.t$estimate,rm.es.t$conf.int[1],rm.es.t$conf.int[2],rm.es.t$p.value, rm.es.m$estimate,rm.es.m$conf.int[1],rm.es.m$conf.int[2],rm.es.m$p.value)

print(xtable(t.test.table, caption='T-Tests', label='table:ttest'), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
@

### 2015-01-17 src/ttests.Rnw
update

@@
 lmcp.m <- mutant.t.test(db)
-# #---------------------------------------
-# # nmc     nc       rc       dc       rv       ic       cc
-# # emv      vmc      m       cb       i        ri       rs       es in
-# db <- subset(common.db, operator == "rm_nmc")
-# with(db, t.test(sel.mintc,sample.mintc, paired=T, alternative=c("greater")))
-# with(db, t.test(sel.all.killtcd_mutant,sample.all.killtcd_mutant, paired=T, alternative=c("greater")))
-# #---------------------------------------
-# db <- subset(common.db, operator == "cc")
-# with(db, t.test(sel.mintc,sample.mintc, paired=T, alternative=c("greater")))
-# with(db, t.test(sel.all.killtcd_mutant,sample.all.killtcd_mutant, paired=T, alternative=c("greater")))
-# #---------------------------------------
-# db <- subset(common.db, operator == "clazz")
-# with(db, t.test(sel.mintc,sample.mintc, paired=T)) #, alternative=c("greater")))
-# with(db, t.test(sel.all.killtcd_mutant,sample.all.killtcd_mutant, paired=T))#, alternative=c("greater")))
+
 db <- subset(common.db, operator=="constrained")
@@
 
-db <- subset(common.db, operator=="rm_in")
-rm.in.t <- mintc.t.test(db)
-rm.in.m <- mutant.t.test(db)
-
 @

### 2015-01-17 src/introduction.Rnw
add more references

@@
 Wong and Mathur found that random sampling fraction as low as 10\%
-could provide accurate results~\cite{jia2011analysis}.
+could provide accurate results~\cite{jia2011analysis}, and was recently
+found that it increases at a rate of $O(x^{\frac{1}{4}})$ when program
+size increases linearly~\cite{zhang2014empirical}.
 

### 2015-01-17 src/discussion.Rnw
add some discussion

@@
 
-To be added.
+We will analyze each of the different types of mutation reduction strategies in
+detail, and summarize the broad patterns we see at the end.
+
+\subsubsection{Operator Selection}
+From Table~\ref{tbl:selective}, we see that except for statement deletion, we
+have negative utility in comparison to baseline for both tests and asserts.
+Even for statement deleition, the utility is just 0.5 tests better than
+baseline. A similar result is present in the strategy effectiveness also,
+where the effectiveness over baseline is either negettive or extremely small.
+
+This is corroborated by statistical analysis where using paired t-test given in
+Table~\ref{tbl:ttests}, it was found that the test utiilty was lower than
+baseline for selective mutation strategies except statement deletion
+($p < 0.01$), and strategy effectiveness was found to be lower than baseline,
+but not significant.
+
+For statement deletion, while utility was found to be positive ($p < 0.05$),
+the magnitude was less than a single test.
+
+For N-selection, which is given in Table~\ref{tbl:nselection}, the situation
+is similar a few steps in operator removal seem to indicate a positive utility
+and a positive strategy effectiveness. However, as Table~\ref{tbl:ttests}
+shows, the mean utility is mostly negative, and for strategy effectiveness,
+the magnitude is very low~\footnote{The difference between
+Table~\ref{tbl:nselection} and Table~\ref{tbl:ttests} is due to test or mutant
+number being zero for baseline, and hence remvoed for computing percentage}.
+
+The strategy of selecting a single operator in Table~\ref{tbl:singles} also
+does not seem to do very well, with either negative or very small positive
+utility and strategy effectiveness when compared to baseline.
+
+\subsubsection{Sampling over program elements}
+For sampling over program elements in Table~\ref{tbl:element}, and t-tests
+in Table~\ref{tbl:ttests}, there appears to be a consistent advantage. However,
+even this advantage is extremely small with roughly 1 test utility or less
+than $6$ mutants advantage for strategy effectiveness.
+
+\subsubsection{Operator based x\% sampling}
+The operator based sampling given in Table~\ref{tbl:opsample} and t-tests in
+Table~\ref{tbl:ttests}, we see that there is a small positive test utility.
+However, as before, the magnitude is very low to be of practical significance.
+
+A general pattern that we can glean from this analysis is that none of the
+mutation reduction strategies appear to be practically better than the simplest
+strategy of all, the random selection strategy. This suggests that at least
+from the perspective of a software tester wishing to use mutation analysis
+as an evaluation criteria to judge when or which tests to add, random sampling
+is the easiest way to reduce the computational requirements of mutation
+analysis. This assumes even more importance when we consider that the adequate
+random sample of mutants increases at a rate less than $O(n^\frac{1}{4})$ when
+the program size increases linearly~\cite{zhang2014empirical}.

### 2015-01-17 src/tbl.ttests.Rnw
add some discussion

@@
 
+t.test.table['Op-Selection nmc',]            <- c(nmc.t$estimate,nmc.t$conf.int[1],nmc.t$conf.int[2],nmc.t$p.value, nmc.m$estimate,nmc.m$conf.int[1],nmc.m$conf.int[2],nmc.m$p.value)
+t.test.table['Op-Selection rv',]            <- c(rv.t$estimate,rv.t$conf.int[1],rv.t$conf.int[2],rv.t$p.value, rv.m$estimate,rv.m$conf.int[1],rv.m$conf.int[2],rv.m$p.value)
+t.test.table['Op-Selection ic',]            <- c(ic.t$estimate,ic.t$conf.int[1],ic.t$conf.int[2],ic.t$p.value, ic.m$estimate,ic.m$conf.int[1],ic.m$conf.int[2],ic.m$p.value)
+t.test.table['Op-Selection dc',]            <- c(dc.t$estimate,dc.t$conf.int[1],dc.t$conf.int[2],dc.t$p.value, dc.m$estimate,dc.m$conf.int[1],dc.m$conf.int[2],dc.m$p.value)
+t.test.table['Op-Selection nc',]            <- c(nc.t$estimate,nc.t$conf.int[1],nc.t$conf.int[2],nc.t$p.value, nc.m$estimate,nc.m$conf.int[1],nc.m$conf.int[2],nc.m$p.value)
+t.test.table['Op-Selection rc',]            <- c(rc.t$estimate,rc.t$conf.int[1],rc.t$conf.int[2],rc.t$p.value, rc.m$estimate,rc.m$conf.int[1],rc.m$conf.int[2],rc.m$p.value)
+t.test.table['Op-Selection vmc',]            <- c(vmc.t$estimate,vmc.t$conf.int[1],vmc.t$conf.int[2],vmc.t$p.value, vmc.m$estimate,vmc.m$conf.int[1],vmc.m$conf.int[2],vmc.m$p.value)
+t.test.table['Op-Selection m',]            <- c(m.t$estimate,m.t$conf.int[1],m.t$conf.int[2],m.t$p.value, m.m$estimate,m.m$conf.int[1],m.m$conf.int[2],m.m$p.value)
+t.test.table['Op-Selection cb',]            <- c(cb.t$estimate,cb.t$conf.int[1],cb.t$conf.int[2],cb.t$p.value, cb.m$estimate,cb.m$conf.int[1],cb.m$conf.int[2],cb.m$p.value)
+t.test.table['Op-Selection i',]            <- c(i.t$estimate,i.t$conf.int[1],i.t$conf.int[2],i.t$p.value, i.m$estimate,i.m$conf.int[1],i.m$conf.int[2],i.m$p.value)
+t.test.table['Op-Selection ri',]            <- c(ri.t$estimate,ri.t$conf.int[1],ri.t$conf.int[2],ri.t$p.value, ri.m$estimate,ri.m$conf.int[1],ri.m$conf.int[2],ri.m$p.value)
+t.test.table['Op-Selection rs',]            <- c(rs.t$estimate,rs.t$conf.int[1],rs.t$conf.int[2],rs.t$p.value, rs.m$estimate,rs.m$conf.int[1],rs.m$conf.int[2],rs.m$p.value)
+t.test.table['Op-Selection es',]            <- c(es.t$estimate,es.t$conf.int[1],es.t$conf.int[2],es.t$p.value, es.m$estimate,es.m$conf.int[1],es.m$conf.int[2],es.m$p.value)
+t.test.table['Op-Selection in',]            <- c(in.t$estimate,in.t$conf.int[1],in.t$conf.int[2],in.t$p.value, in.m$estimate,in.m$conf.int[1],in.m$conf.int[2],in.m$p.value)
+
 print(xtable(t.test.table, caption='T-Tests', label='table:ttest'), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})

### 2015-01-17 src/ttests.Rnw
add some discussion

@@
 
+db <- subset(common.db, operator=="nmc")
+nmc.t <- mintc.t.test(db)
+nmc.m <- mutant.t.test(db)
+
+db <- subset(common.db, operator=="rv")
+rv.t <- mintc.t.test(db)
+rv.m <- mutant.t.test(db)
+
+db <- subset(common.db, operator=="ic")
+ic.t <- mintc.t.test(db)
+ic.m <- mutant.t.test(db)
+
+db <- subset(common.db, operator=="dc")
+dc.t <- mintc.t.test(db)
+dc.m <- mutant.t.test(db)
+
+db <- subset(common.db, operator=="nc")
+nc.t <- mintc.t.test(db)
+nc.m <- mutant.t.test(db)
+
+db <- subset(common.db, operator=="rc")
+rc.t <- mintc.t.test(db)
+rc.m <- mutant.t.test(db)
+
+db <- subset(common.db, operator=="vmc")
+vmc.t <- mintc.t.test(db)
+vmc.m <- mutant.t.test(db)
+
+db <- subset(common.db, operator=="cc")
+cc.t <- mintc.t.test(db)
+cc.m <- mutant.t.test(db)
+
+db <- subset(common.db, operator=="emv")
+emv.t <- mintc.t.test(db)
+emv.m <- mutant.t.test(db)
+
+db <- subset(common.db, operator=="m")
+m.t <- mintc.t.test(db)
+m.m <- mutant.t.test(db)
+
+db <- subset(common.db, operator=="cb")
+cb.t <- mintc.t.test(db)
+cb.m <- mutant.t.test(db)
+
+db <- subset(common.db, operator=="i")
+i.t <- mintc.t.test(db)
+i.m <- mutant.t.test(db)
+
+db <- subset(common.db, operator=="ri")
+ri.t <- mintc.t.test(db)
+ri.m <- mutant.t.test(db)
+
+db <- subset(common.db, operator=="rs")
+rs.t <- mintc.t.test(db)
+rs.m <- mutant.t.test(db)
+
+db <- subset(common.db, operator=="es")
+es.t <- mintc.t.test(db)
+es.m <- mutant.t.test(db)
+
+db <- subset(common.db, operator=="in")
+in.t <- mintc.t.test(db)
+in.m <- mutant.t.test(db)
+
 @

### 2015-01-17 src/introduction.Rnw
yoo

@@
 perfect minimal set, as established in the test case selection literature
-\cite{YooHarman}.}  Ideally, we would like a set of mutants that require
+\cite{yoo2012regression}.}  Ideally, we would like a set of mutants that require
 as many test cases as possible, if we assume that the original set of test

### 2015-01-18 src/tbl.subsumption.Rnw
add sumsumption

\begin{table*}[!ht]
<<tblsubsumption,results='asis'>>=
library(ellipse)
subsumption <- read.csv('data/subsumption.csv')
print(xtable(1 - subsumption, caption='subsumption', label='table:subsumption'), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
@
\caption{The subsumption relationship.}
\end{table*}

% \begin{figure*}
% <<subsumption,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
% m <- as.matrix(subsumption)
% library(ellipse)
% #plotcorr(m, outline=F,col='white')
% colorfun <- colorRamp(c("#3366CC","white"), space="Lab")
% plotcorr(m, col=rgb(colorfun((m+1)/2), maxColorValue=255), outline=F)
% @
% \end{figure*}

### 2015-01-18 src/tbl.subsumption.Rnw
remove data dir

@@
 library(ellipse)
-subsumption <- read.csv('data/subsumption.csv')
-print(xtable(1 - subsumption, caption='subsumption', label='table:subsumption'), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
+print(xtable(1 - subsumption.db, caption='subsumption', label='table:subsumption'), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
 @

### 2015-01-18 src/tbl.subsumption.Rnw
remove ellipse

@@
 <<tblsubsumption,results='asis'>>=
-library(ellipse)
 print(xtable(1 - subsumption.db, caption='subsumption', label='table:subsumption'), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})

### 2015-01-18 src/conclusion.Rnw
update

@@
 the mutation effectiveness criteria. While some of the individual operators
-such as \Pitrv, \Piti, \Pitri, and \Pites~show promise in test utility,
-they do not stand out when we examine the mutation effectiveness in comparison
-to baseline.
+seemed to indicate a mean positive test utility or a mean strategy
+effectiveness, the effect itself is too small (of the order of one or two
+mutants or tests) to be of much help for a tester in the real world.
 
@@
 strategy or even for the element based x\% strategy. They in general show a
-slight advantage in test utility which doesn't seem to translate to the
-strategy effectiveness in comparison with baseline.
+slight advantage in test utility which while consistent, is not of much
+practical utility.
 
-Thus we find that that none of the well known reduction strategies are actually
-able to consistenly select useful mutants, and the best path forward
+This suggests that that none of the well known reduction strategies are
+actually able to consistenly select useful mutants, and the best path forward
 for a working tester is to rely on the simplest scheme of all -- the random

### 2015-01-18 src/related.Rnw
latest
update

@@
 mutation analysis itself. Budd~\cite{budd1980mutation} and
-Acree~\cite{Acree1980} showed that even 10\% sampling can achieve 99\%
+Acree~\cite{acree1980mutation} showed that even 10\% sampling can achieve 99\%
 accuracy for the final score.  The idea was further investigated by
@@
 
-Our work is most closely related to that of Zhang et
-al.~\cite{zhang2013ase}. We extend the scope of their study with a
-much wider range of mutation approaches and base our results on a much larger
-set of real-world projects.
+% Our work is most closely related to that of Zhang et
+% al.~\cite{zhang2013ase}. We extend the scope of their study with a
+% much wider range of mutation approaches and base our results on a much larger
+% set of real-world projects.

### 2015-01-18 src/methodology.Rnw
update

@@
 we used is provided in Table~\ref{tbl:pitop}.
+
+In order to ensure that the operators that we added were not redundant,
+we computed their operator subsumption matrix. This is given in
+Table~\ref{tbl:subsumption}, and a visualization of the subsumption is
+presented in Figure~\ref{fig:subsumption}. This shows that the operators
+we used were non-redundant, with a maximum subsumption of only $40\%$.
+
 % Figure~\ref{fig:op} shows
@@
 are not applicable in Java, and some not in PIT.
-We  used by  \Pitin, \Pitm, \Piti and \Pitnc.
+We  used by  \Pitin, \Pitm, \Piti, and \Pitnc.
 
@@
 \Pitnvmc, \Pitrv, \Pitic, \Pitdc, \Pitnc, \Pitrc, \Pitvmc, \Pitcc, \Pitemv,
-\Pitm, \Pitcb, \Piti, \Pitri, \Pitrs, \Pites, and \Pitin
+\Pitm, \Pitcb, \Piti, \Pitri, \Pitrs, \Pites, and \Pitin.
 We discarded one at each

### 2015-01-18 src/tbl.subsumption.Rnw
update

@@
 <<tblsubsumption,results='asis'>>=
-print(xtable(1 - subsumption.db, caption='subsumption', label='table:subsumption'), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
+print(xtable(1 - subsumption.db, caption='Subsumption of operators by others', label='tbl:subsumption'), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
 @
 \caption{The subsumption relationship.}
+\label{tbl:subsumption}
 \end{table*}

### 2015-01-18 src/introduction.Rnw
update intro

@@
 mutants~\cite{lipton1971fault, ammann2008introduction}. Research by
-Andrews et. al~\cite{andrews2005mutation} suggest that mutations can
-simulate behavior of real faults.
+Andrews et. al~\cite{andrews2005mutation,andrews2006using} suggest that
+mutations can simulate behavior of real faults. However, mutation analysis
+of test suites has not sufficiently permeated software engineering
+practice~\cite{daka2014asurvey} even though the need for a tool that is
+able to evaluate tests based on their fault finding quality is keenly
+felt~\cite{runeson2006asurvey}.
+
 % thus
@@
 Wong and Mathur found that random sampling fraction as low as 10\%
-could provide accurate results~\cite{jia2011analysis}, and was recently
-found that it increases at a rate of $O(x^{\frac{1}{4}})$ when program
-size increases linearly~\cite{zhang2014empirical}.
+could provide accurate results~\cite{jia2011analysis}. It was recently
+found that the fraction required to achieve adequacy on mutation sampling
+increases at a rate of $O(x^{\frac{1}{4}})$ when program size increases
+linearly~\cite{zhang2014empirical}.
 
@@
 
-Further, quite a few of the influential studies~\cite{offutt1993experimental,offutt1996anexperimental,wong1995reducing,mresa1999efficiency}
+We also note that quite a few of the influential
+studies~\cite{offutt1993experimental,offutt1996anexperimental,wong1995reducing,mresa1999efficiency}
 were conducted on older programming languages such as Fortran, with
-operators specific to the language, and are not directly applicable to
+operators specific to the language, and may not directly applicable to
 newer languages such as Java.
@@
 } based mutation
-engines like PIT~\cite{pitest} and Javalanche~\cite{javalanche}
-, operators based on
-source code modification are no longer applicable, and their
+engines like PIT~\cite{pitest} and Javalanche~\cite{javalanche},
+operators based on source code modification are no longer applicable, and their
 equivalents in bytecode need to be identified and compared with other
-approaches. A detailed discussion of these issues can be found in
-Section~\ref{sec:related}.
+approaches. A detailed discussion of our approach can be found in
+Section~\ref{sec:methodology}.
 
@@
 perfect minimal set, as established in the test case selection literature
-\cite{yoo2012regression}.}  Ideally, we would like a set of mutants that require
-as many test cases as possible, if we assume that the original set of test
-cases is populated with useful, non-redundant test cases.  While the suites
-of many open source programs are far from adequate, they should satisfy that
-requirement:  each test was almost always added by considerable manual labor,
-and was at least believed to be useful.  Therefore, any tests omitted likely
-indicate a potential to miss faults.  A good mutation selection strategy,
-therefore, should 1) be as close to the original set of mutants as possible,
-in terms of the test cases it requires in a minimal suite and 2) require
-more test cases than a randomly selected set of mutants of the same size.
+\cite{yoo2012regression}.}  Ideally, we would like a set of mutants that
+require as many test cases as possible, if we assume that the original set
+of test cases is populated with useful, non-redundant test cases.  While
+the suites of many open source programs are far from adequate, they should
+satisfy that requirement:  each test was almost always added by considerable
+manual labor, and was at least believed to be useful.  Therefore, any tests
+omitted likely indicate a potential to miss faults.  A good mutation selection
+strategy, therefore, should 1) be as close to the original set of mutants
+as possible, in terms of the test cases it requires in a minimal suite and
+2) require more test cases than a randomly selected set of mutants of the
+same size.
 
@@
 
-Hence an easy way to evaluate a mutation reduction strategy would be to
-see if it promotes such test suites; that is, either test suites with a large
-number of non-redundant test cases, or those with a large number of asserts.
+This suggests that an easy way to evaluate a mutation reduction strategy
+would be to see if it promotes such test suites; that is, either test suites
+with a large number of non-redundant test cases, or those with a large number
+of asserts.
 

### 2015-01-18 src/introduction.Rnw
updates from amin

@@
 
-Finally, with bytecode~\footnote{
-A \textit{do faster} approach for eliminating
-the compilation step to gain execution speed
-} based mutation
-engines like PIT~\cite{pitest} and Javalanche~\cite{javalanche},
-operators based on source code modification are no longer applicable, and their
-equivalents in bytecode need to be identified and compared with other
-approaches. A detailed discussion of our approach can be found in
-Section~\ref{sec:methodology}.
+Finally, with bytecode~\footnote{A \textit{do faster} approach for
+eliminating the compilation step to gain execution speed} based mutation
+engines such as PIT~\cite{pitest} and Javalanche~\cite{javalanche} becoming
+common in both development and research (e.g. \cite{zhang2013ase},
+\cite{gopinath2014code}, and \cite{inozemtseva2014coverage}),
+operators based on source code modification are no longer directly applicable,
+and their equivalents in bytecode need to be identified and compared with other
+approaches.
 
+This paper studies different mutant selection strategies on large number of
+Java programs using a popular bytecode-based mutation PIT.
+We sampled $312$ opensource Java project between $50$ to $100K$ non-comment
+lines of code (excluding test cases) from Github and Apache Foundation. This
+set of projects include many of popular Java projects that are regualry used in
+literature (such as Apache Common Lang, Common Math and Joda Time). For the
+mutation analysis of this study, we choose PIT, a fast and easy to use mutation
+analysis tool for Java, which has been used by researchers in the
+past~\cite{gopinath2014code,inozemtseva2014coverage} for its wide range of
+operators.
+% Amin: Total lines of code, total number of mutants
+
+For this study, we experimented four classic mutation selection techniques: Constrained \cite{wong1995reducing}, E-       Selective \cite{offutt1996anexperimental}, Javalanche \cite{javalanche} and N-Selection
+\cite{offutt1993experimental}, along with two sampling approaches: element based \cite{zhang2013ase} and operator based   sampling \cite{wong1995reducing}.
+We compare test effectiveness of each of techniques
+with pure random sampling.
+Our results show that in most cases there is no statistically significant benefit for mutation selection techniques.
+Moreover, in cases with statistically significant benefit, the gain is
+so low that is essentially negligible.
+
+\begin{comment}
 We have attempted to rectify this situation with a large scale study of real
@@
 statistical inferences.
+\end{comment}
 
@@
 
-Section~\ref{sec:related} describes the research in mutation reduction 
-strategies. Section~\ref{sec:methodology} discusses the sampling and
-operator
-selection strategies we study in detail. The analysis is given in
-Section~\ref{sec:analysis}, and the results of our
-experiment are given in Section~\ref{sec:results}, followed by
-detailed discussion of what these results imply in Section
-~\ref{sec:discussion}. The specific contributions of this paper are:
+The specific contributions of this paper are:
 
@@
 \end{itemize}
+
+\noindent\textbf{Organization.} Section~\ref{sec:related} describes the
+research in mutation reduction strategies. Section~\ref{sec:methodology}
+ discusses the sampling and operator
+selection strategies we study in detail. The analysis is given in
+Section~\ref{sec:analysis}, and the results of our
+experiment are given in Section~\ref{sec:results}, followed by
+detailed discussion of what these results imply in Section
+~\ref{sec:discussion}.

### 2015-01-18 src/related.Rnw
update intro
updates from amin
update related

@@
 \label{sec:related}
+
+The idea of mutation analysis was first proposed by Richard Lipton~\cite{mathur2012foundations},
+and formalized by DeMillo et al.~\cite{demillo1978hints} A practical implementation of
+mutation analysis was accomplished by Budd et al.~\cite{budd1980theoretical} in 1980.
+
+Mutation analysis was found to subsume different coverage measures~\cite{budd1980mutation,mathur1994empirical,offutt1996subsumption},
+and it was found that the faults produced by mutation analysis were similar to real
+faults in the errors it produced~\cite{daran1996software} and the ease of detection~\cite{andrews2005mutation,andrews2006using}.
+Just et al.~\cite{just2014mutants} investigated the relation between mutation score and test
+case effectiveness using 357 real bugs, and found that the mutation score increased
+with effectiveness for 75\% of the cases, which was better than the 46\% reported
+for structural coverage.
+
+The foundational assumptions of mutation analysis are the competent programmer
+hypothesis which states that programmers tend to make very simple mistakes, and
+coupling effect which states that a test case able to detect a fault in
+isolation will continue to detect it even in the presence of other
+faults~\cite{demillo1978hints}. This was confirmed using theoretical analysis by Wah~\cite{wah2000atheoretical,wah2003ananalysis}
+and using empirical studies by Offutt~\cite{offutt1989thecoupling,offutt1992investigations}
+
 There are several approaches to reducing the cost of mutation analysis.

### 2015-01-18 src/related.Rnw
update related

@@
 
+Operator and mutant subsumption is another active area of research
+for reduction of number of mutants where by operators or mutants
+that do not significantly differ from others are eliminated. Kurtz et
+al.~\cite{kurtz2014mutant} finds that savings up to 2400\% can be achieved
+using subsumption alone, even though the result is based on investigation
+of a single program \textit{cal}. Research into subsumption of mutants also
+includes Higher Order Mutants, where by multiple mutations are introduced
+into the same set of mutants, reducing the total number of individual mutants
+by subsuming the component mutants. These have investigated by
+Jia et al.~\cite{jia2009higher,jia2008constructing}, and finds that it can
+reduce the number of mutants by 50\%.
+
 % Our work is most closely related to that of Zhang et

### 2015-01-18 src/methodology.Rnw
update

@@
 %----------------------------------------
-\subsubsection{Statement Deletion} \label{subsec:stmtdel} The basic
-statement deletion was modeled on the work by Deng et
-al.~\cite{deng2013empirical}. The operations on single statements were
-modeled using \Pitvmc, \Pitnvmc, \Pitcc, \Pitemv, and \Pitri~for
-simple statements, and using \pitrc for control structures. \pitrc
+\subsubsection{Statement deletion emulation} \label{subsec:stmtdel}
+
+The statement deletion based operator selection was based on the work by
+Deng et al.~\cite{deng2013empirical}. The operations on single
+statements were modeled using \Pitvmc, \Pitnvmc, \Pitcc, \Pitemv, and
+\Pitri~for simple statements, and using \pitrc for control structures. \pitrc
 replaces boolean conditions with \textit{false}, resulting in removal of the
@@
 first 100 labels were replaced. Deleting \textit{try/catch} was not
-necessary at bytecode level.  Finally, to get an accurate estimation
-of the effect of true statement deletion, we grouped the mutants by
-line, and considered each line a single virtual mutant (that is, the total
-number of mutants is equal to the total number of lines). Further,
-killing any mutant from a line resulted in marking the virtual mutant
-for that line as killed. This gave us the mutation score for the
-virtual statement deletion operator.  We note that the approximation
-of simple statement deletion, especially when arithmetic operators are
-involved, is not complete. However,
-the number of mutants produced by \pitm operator is very small. We
-also note that our approximation does not account for the increase in
-ease of detection when multiple mutations are combined together due to
-the coupling effect. This also means that not all the lines may be
-mutated ,since there may be no applicable operators. However, given
-the constraints of a bytecode based mutation system, we believe that
-our procedure is reasonable.
+necessary at bytecode level.
+
+Note that we are not attempting to evaluate statement deletion mutation
+directly here. Rather, we have chosen a set of operators that could be
+involved in deletion of statements, and have used that as an operator
+selection criteria. This means that in order to translate the results
+from our experiment back to original statement deletion operator, we need
+to rely on some assumptions. They are, 1) Coupling effect: If a test is
+able to kill a mutant in this set, then it should kill it even when it
+is in combination with other mutants of this set (resulting in deletion
+of deletion of the statement in question). Note that there is a
+possibility for statement deletion to be less effective than our
+experiment, that is, for actual deleted statements to be detected more
+often than individual mutants are detected. However, this does not adversely
+affect our final conclusions.
+
+Finally, while the utility measures and the effectiveness for deletion based
+operators should hold when translating to true statement deletion, the mutation
+share reported is based on the independent mutants, and should not be taken
+as the mutation share of true statement deletion.
+
+% Finally, to get an accurate estimation
+% of the effect of true statement deletion, we grouped the mutants by
+% line, and considered each line a single virtual mutant (that is, the total
+% number of mutants is equal to the total number of lines). Further,
+% killing any mutant from a line resulted in marking the virtual mutant
+% for that line as killed. This gave us the mutation score for the
+% virtual statement deletion operator.  We note that the approximation
+% of simple statement deletion, especially when arithmetic operators are
+% involved, is not complete. However,
+% the number of mutants produced by \pitm operator is very small. We
+% also note that our approximation does not account for the increase in
+% ease of detection when multiple mutations are combined together due to
+% the coupling effect. This also means that not all the lines may be
+% mutated ,since there may be no applicable operators. However, given
+% the constraints of a bytecode based mutation system, we believe that
+% our procedure is reasonable.
 % An interesting point is that using this
+
 %procedure statement, deletion is no longer a simple mutation and

### 2015-01-18 src/tables.Rnw
update

@@
 }
+# s.selective.db['sdl','mutation.share'] <- -1 #paste(s.opsample.db['sdl','mutation.share'],'*')
 print(tbl.place(xtable(eff(s.selective.db), caption='Selective Strategy', label='table:selective')),include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})

### 2015-01-19 src/methodology.Rnw
cleanup with xspace

@@
 % box-plot represents the relative frequency of particular mutation operator
-% in the total mutants \textit{detected}. For example, \pitnvmc contribution
-% in the detected mutants was 23\% while that of \pitrv was 15\%.
+% in the total mutants \textit{detected}. For example, \Pitnvmc contribution
+% in the detected mutants was 23\% while that of \Pitrv was 15\%.
 
@@
 \hline \hline \\
-\pitin & Remove negative sign from numbers\\
-\pitrv & Mutate return values\\
-\pitm & Mutate arithmetic operators\\
-\pitvmc & Remove void method calls\\
-\pitnc & Negate conditional statements\\
-\pitcb & Modify boundaries in logical conditions\\
-\piti & Modify increment and decrement statements\\
-\pitnvmc & Remove non-void method calls, returning default value \\
-\pitcc & Replace constructor calls, returning null \\
-\pitic & Replace inline constants with default value \\
-\pitri & Remove increment and decrement statements \\
-\pitemv & Replace member variable assignments with default value \\
-\pites & Modify switch statements \\
-\pitrs & Replace switch labels with default (thus removing them) \\
-\pitrc & Replace boolean conditions with true\\
-\pitnc & Replace boolean conditions with false\\
+\Pitin & Remove negative sign from numbers\\
+\Pitrv & Mutate return values\\
+\Pitm & Mutate arithmetic operators\\
+\Pitvmc & Remove void method calls\\
+\Pitnc & Negate conditional statements\\
+\Pitcb & Modify boundaries in logical conditions\\
+\Piti & Modify increment and decrement statements\\
+\Pitnvmc & Remove non-void method calls, returning default value \\
+\Pitcc & Replace constructor calls, returning null \\
+\Pitic & Replace inline constants with default value \\
+\Pitri & Remove increment and decrement statements \\
+\Pitemv & Replace member variable assignments with default value \\
+\Pites & Modify switch statements \\
+\Pitrs & Replace switch labels with default (thus removing them) \\
+\Pitrc & Replace boolean conditions with true\\
+\Pitnc & Replace boolean conditions with false\\
 \hline
@@
 mutation analysis. We used operators
-\pitcb and \pitnc to model ROR operator. There are no comparable operators to ABS in PIT.
+\Pitcb and \Pitnc to model ROR operator. There are no comparable operators to ABS in PIT.
 
@@
 statements were modeled using \Pitvmc, \Pitnvmc, \Pitcc, \Pitemv, and
-\Pitri~for simple statements, and using \pitrc for control structures. \pitrc
+\Pitri~for simple statements, and using \Pitrc for control structures. \Pitrc
 replaces boolean conditions with \textit{false}, resulting in removal of the
@@
 effect of conditional. The \textit{switch} statement deletion was
-modeled using \pitrs which replaced the first 100 labels with a
+modeled using \Pitrs which replaced the first 100 labels with a
 \textit{default} label, resulting in the switch element being
@@
 % involved, is not complete. However,
-% the number of mutants produced by \pitm operator is very small. We
+% the number of mutants produced by \Pitm operator is very small. We
 % also note that our approximation does not account for the increase in

### 2015-01-19 src/paper.Rnw
cleanup with xspace

--- 2015-01-12 src/paper.Rnw
@@
 \newcommand*\per{\scalebox{.5}{\%}}
-\newcommand\Mua{Mutation analysis~}
-\newcommand\mua{mutation analysis~}
-%\newcommand{\pitnvmc}{~NON\_\allowbreak{}VOID\_\allowbreak{}METHOD\_\allowbreak{}CALLS~}
-%\newcommand{\pitnc}{~NEGATE\_\allowbreak{}CONDITIONALS~}
-%\newcommand{\pitrc}{~REMOVE\_\allowbreak{}CONDITIONALS~}
-%\newcommand{\pitdc}{~DELETE\_\allowbreak{}CONDITIONALS~}
-%\newcommand{\pitrv}{~RETURN\_\allowbreak{}VALUES~}
-%\newcommand{\pitic}{~INLINE\_\allowbreak{}CONSTANTS~}
-%\newcommand{\pitcc}{~CONSTRUCTOR\_\allowbreak{}CALLS~}
-%\newcommand{\pitemv}{~E\_\allowbreak{}MEMBER\_\allowbreak{}VARIABLE~}
-%\newcommand{\pitvmc}{~VOID\_\allowbreak{}METHOD\_\allowbreak{}CALLS~}
-%\newcommand{\pitm}{~MATH~}
-%\newcommand{\pitcb}{~CONDITIONALS\_\allowbreak{}BOUNDARY~}
-%\newcommand{\piti}{~INCREMENTS~}
-%\newcommand{\pitri}{~REMOVE\_\allowbreak{}INCREMENTS~}
-%\newcommand{\pitrs}{~RM\_\allowbreak{}SWITCH~}
-%\newcommand{\pites}{~E\_\allowbreak{}SWITCH~}
-%\newcommand{\pitin}{~INVERT\_\allowbreak{}NEGATIVES~}
-%
-\newcommand{\pitnvmc}{NMC~}
-\newcommand{\pitnc}{NC~}
-\newcommand{\pitrc}{RC~}
-\newcommand{\pitdc}{DC~}
-\newcommand{\pitrv}{RV~}
-\newcommand{\pitic}{IC~}
-\newcommand{\pitcc}{CC~}
-\newcommand{\pitemv}{EMV~}
-\newcommand{\pitvmc}{VMC~}
-\newcommand{\pitm}{M~}
-\newcommand{\pitcb}{CB~}
-\newcommand{\piti}{I~}
-\newcommand{\pitri}{RI~}
-\newcommand{\pitrs}{RS~}
-\newcommand{\pites}{ES~}
-\newcommand{\pitin}{IN~}
-% No space variants.
-\newcommand{\Pitnvmc}{NMC}
-\newcommand{\Pitnc}{NC}
-\newcommand{\Pitrc}{RC}
-\newcommand{\Pitdc}{DC}
-\newcommand{\Pitrv}{RV}
-\newcommand{\Pitic}{IC}
-\newcommand{\Pitcc}{CC}
-\newcommand{\Pitemv}{EMV}
-\newcommand{\Pitvmc}{VMC}
-\newcommand{\Pitm}{M}
-\newcommand{\Pitcb}{CB}
-\newcommand{\Piti}{I}
-\newcommand{\Pitri}{RI}
-\newcommand{\Pitrs}{RS}
-\newcommand{\Pites}{ES}
-\newcommand{\Pitin}{IN}
+\newcommand\Mua{Mutation analysis\xspace}
+\newcommand\mua{mutation analysis\xspace}
+\newcommand{\Pitnvmc}{NMC\xspace}
+\newcommand{\Pitnc}{NC\xspace}
+\newcommand{\Pitrc}{RC\xspace}
+\newcommand{\Pitdc}{DC\xspace}
+\newcommand{\Pitrv}{RV\xspace}
+\newcommand{\Pitic}{IC\xspace}
+\newcommand{\Pitcc}{CC\xspace}
+\newcommand{\Pitemv}{EMV\xspace}
+\newcommand{\Pitvmc}{VMC\xspace}
+\newcommand{\Pitm}{M\xspace}
+\newcommand{\Pitcb}{CB\xspace}
+\newcommand{\Piti}{I\xspace}
+\newcommand{\Pitri}{RI\xspace}
+\newcommand{\Pitrs}{RS\xspace}
+\newcommand{\Pites}{ES\xspace}
+\newcommand{\Pitin}{IN\xspace}
 
-\begin{comment}
-<<setup, include=FALSE, message=FALSE, echo=FALSE>>=
-is.installed <- function(mypkg) is.element(mypkg, installed.packages()[,1])
-#options(CRAN = "http://cran.stat.ucla.edu")
-#if (!is.installed("xtable")) install.packages("xtable")
-#if (!is.installed("ggplot2")) install.packages("ggplot2")
-#if (!is.installed("reshape2")) install.packages("reshape2")
-
-#options(warn=-1)
-options(digits=3)
-opts_chunk$set(fig.path='figure/twocolumn-', fig.align='center', fig.show='hold', echo=FALSE)
-opts_chunk$set(cache=TRUE)
-render_listings()
-logit<-function(x) log(x/(1-x))
-require(reshape2)
-require(scales)
-require(xtable)
-require(ggplot2)
-require(MutSel)
-@
-<<chunk-hook, echo=2>>=
-<<setup>>
-v=data(package='MutSel')
-data(list = v$results[,3])
-@
-\end{comment}
-<<>>=
-
-f <- function(x) {
-  x <- x[,c(7,8,2,3,4,5,6)]
-  names(x)[names(x) == 'sampling'] <- '$\\div$'
-  return(x)
-}
-
-colorize.rsqr <- function(x) {
-  ifelse(x >= 0.90,
-      paste("\\textcolor{blue}{", formatC(x, dig=2, format="f"), "}"),
-      paste("\\textcolor{black}{", formatC(x, dig=2, format="f"), "}"))
-}
-
-colorize.it <- function(x) {
-  x$sd.reduction <- ifelse(x$sd.reduction * 2 < x$mutant.reduction,
-      paste("\\textcolor{black}{", formatC(x$sd.reduction, dig=2, format="f"), "}"),
-      paste("\\textcolor{red}{", formatC(x$sd.reduction, dig=2, format="f"), "}"))
-  x$r.square <- colorize.rsqr(x$r.square)
-  return(x)
-}
-
-theme_set(theme_bw(12))
-myopts <- theme(panel.background = element_blank())
-
+<<rsetup, child='r.setup.Rnw'>>=
 @

### 2015-01-19 src/r.setup.Rnw
cleanup with xspace

\begin{comment}
<<setup, include=FALSE, message=FALSE, echo=FALSE>>=
is.installed <- function(mypkg) is.element(mypkg, installed.packages()[,1])
#options(CRAN = "http://cran.stat.ucla.edu")
#if (!is.installed("xtable")) install.packages("xtable")
#if (!is.installed("ggplot2")) install.packages("ggplot2")
#if (!is.installed("reshape2")) install.packages("reshape2")

#options(warn=-1)
options(digits=3)
opts_chunk$set(fig.path='figure/twocolumn-', fig.align='center', fig.show='hold', echo=FALSE)
opts_chunk$set(cache=TRUE)
render_listings()
logit<-function(x) log(x/(1-x))
require(reshape2)
require(scales)
require(xtable)
require(ggplot2)
require(grid)
require(MutSel)
vplayout <- function(x, y) viewport(layout.pos.row = x, layout.pos.col = y)
theme = theme_set(theme_minimal())
@
<<chunk-hook, echo=2>>=
<<setup>>
v=data(package='MutSel')
data(list = v$results[,3])
@
\end{comment}
<<>>=

f <- function(x) {
  x <- x[,c(7,8,2,3,4,5,6)]
  names(x)[names(x) == 'sampling'] <- '$\\div$'
  return(x)
}

colorize.rsqr <- function(x) {
  ifelse(x >= 0.90,
      paste("\\textcolor{blue}{", formatC(x, dig=2, format="f"), "}"),
      paste("\\textcolor{black}{", formatC(x, dig=2, format="f"), "}"))
}

colorize.it <- function(x) {
  x$sd.reduction <- ifelse(x$sd.reduction * 2 < x$mutant.reduction,
      paste("\\textcolor{black}{", formatC(x$sd.reduction, dig=2, format="f"), "}"),
      paste("\\textcolor{red}{", formatC(x$sd.reduction, dig=2, format="f"), "}"))
  x$r.square <- colorize.rsqr(x$r.square)
  return(x)
}

theme_set(theme_bw(12))
myopts <- theme(panel.background = element_blank())

@

### 2015-01-19 src/introduction.Rnw
update

@@
 Mutation analysis is a method for evaluating the quality of test suites. It
-involves producing a family of \emph{mutants}, programs with small
-differences from the original program, and evaluating the
-effectiveness of test suites against these
-mutants~\cite{lipton1971fault, ammann2008introduction}. Research by
-Andrews et. al~\cite{andrews2005mutation,andrews2006using} suggest that
-mutations can simulate behavior of real faults. However, mutation analysis
-of test suites has not sufficiently permeated software engineering
+involves producing a family of \emph{mutants}, programs with small differences
+from the original program, and evaluating the effectiveness of test suites
+against these mutants~\cite{lipton1971fault, ammann2008introduction}. Research
+by Andrews et. al~\cite{andrews2005mutation,andrews2006using} suggest
+that mutations can simulate behavior of real faults. However, mutation
+analysis of test suites has not sufficiently permeated software engineering
 practice~\cite{daka2014asurvey} even though the need for a tool that is
@@
 
-% thus
-% introduced behave in a fashion similar to real faults, with respect to
-% the difficulty of detection.
+An impediment to the wider adoption of mutation analysis is its high
+computational cost.  The set of simple mutants for even a moderate sized
+program can be very large, making mutation analysis prohibitively time
+consuming.
 
-An impediment to the wider adoption of mutation analysis is its
-high computational cost.  The set of simple mutants for even a
-moderate sized program can be very large, making mutation
-analysis prohibitively time consuming.
-
-A major strain of research into cost-reduction of mutation analysis is
-to choose a smaller, representative set of
+A major strain of research into cost-reduction of mutation
+analysis is to choose a smaller, representative set of
 mutants~\cite{offutt2001mutation,jia2011analysis} --- often called the
-\textit{do fewer} approach. This approach can be generally divided
-into selective strategies and sampling strategies.
+\textit{do fewer} approach. This approach can be generally divided into
+selective strategies and sampling strategies.
 
@@
 subset of mutation \emph{operators} based on heuristics and
-statistical analysis, and apply this subset of operators to generate
-mutants instead of applying the whole set of mutation
+statistical analysis, and apply this subset of operators to
+generate mutants instead of applying the whole set of mutation
 operators~\cite{offutt1993anexperimental,untch2009onreduced}.
-%Recent work suggests that using statement deletion alone can
-%be an effective approach~\cite{untch2009onreduced}.
 
 Sampling strategies seek to randomly select a set of representative
-mutants.  This was investigated first by
-Acree~\cite{acree1980mutation} and Budd~\cite{budd1980mutation}, who
-proposed using only a small fraction of randomly selected mutants.
-Wong and Mathur found that random sampling fraction as low as 10\%
-could provide accurate results~\cite{jia2011analysis}. It was recently
-found that the fraction required to achieve adequacy on mutation sampling
-increases at a rate of $O(x^{\frac{1}{4}})$ when program size increases
-linearly~\cite{zhang2014empirical}.
+mutants.  This was investigated first by Acree~\cite{acree1980mutation}
+and Budd~\cite{budd1980mutation}, who proposed using only a small fraction of
+randomly selected mutants.  Wong and Mathur found that random sampling fraction
+as low as 10\% could provide accurate results~\cite{jia2011analysis}. It was
+recently found that the fraction required to achieve adequacy on mutation
+sampling increases at a rate of $O(x^{\frac{1}{4}})$ when program size
+increases linearly~\cite{zhang2014empirical}.
 
-Recent work~\cite{zhang2010icse,zhang2013ase} investigating the
-relative merits of random sampling strategies and operator selection
-suggests that random sampling can perform as well as or better than operator
-selection, and a strategy of either sampling based on program elements or
-one combining both program element-based sampling and operator selection
-was the best approach.
+Recent work~\cite{zhang2010icse,zhang2013ase} investigating the relative
+merits of random sampling strategies and operator selection suggests that
+random sampling can perform as well as or better than operator selection, and
+a strategy of either sampling based on program elements or one combining both
+program element-based sampling and operator selection was the best approach.
 
-However, as pointed out by Zhang et al.~\cite{zhang2013ase}, the field
-has a serious lacuna in large scale research, both in the size of the
-programs studied, and in the number and diversity of programs, which
-reduces our confidence. This is true for selective mutation studies,
-sampling studies, and also for comparatively newer studies that attempt
-to combine methods. This is particularly worrisome if mutation analysis
-is to gain wider acceptance among testing professionals.
+However, as pointed out by Zhang et al.~\cite{zhang2013ase}, the field has
+a serious lacuna in large scale research, both in the size of the programs
+studied, and in the number and diversity of programs, which reduces our
+confidence. This is true for selective mutation studies, sampling studies,
+and also for comparatively newer studies that attempt to combine methods. This
+is particularly worrisome if mutation analysis is to gain wider acceptance
+among testing professionals.
 
@@
 studies~\cite{offutt1993experimental,offutt1996anexperimental,wong1995reducing,mresa1999efficiency}
-were conducted on older programming languages such as Fortran, with
-operators specific to the language, and may not directly applicable to
-newer languages such as Java.
+were conducted on older programming languages such as Fortran, with operators
+specific to the language, and may not directly applicable to newer languages
+such as Java.
 
-Finally, with bytecode~\footnote{A \textit{do faster} approach for
-eliminating the compilation step to gain execution speed} based mutation
-engines such as PIT~\cite{pitest} and Javalanche~\cite{javalanche} becoming
-common in both development and research (e.g. \cite{zhang2013ase},
-\cite{gopinath2014code}, and \cite{inozemtseva2014coverage}),
-operators based on source code modification are no longer directly applicable,
-and their equivalents in bytecode need to be identified and compared with other
-approaches.
+Finally, with bytecode~\footnote{A \textit{do faster} approach for eliminating
+the compilation step to gain execution speed} based mutation engines such as
+PIT~\cite{pitest} and Javalanche~\cite{javalanche} becoming common in both
+development and research (e.g. \cite{zhang2013ase}, \cite{gopinath2014code},
+and \cite{inozemtseva2014coverage}), operators based on source code
+modification are no longer directly applicable, and their equivalents in
+bytecode need to be identified and compared with other approaches.
 
-This paper studies different mutant selection strategies on large number of
-Java programs using a popular bytecode-based mutation PIT.
-We sampled $312$ opensource Java project between $50$ to $100K$ non-comment
-lines of code (excluding test cases) from Github and Apache Foundation. This
-set of projects include many of popular Java projects that are regualry used in
-literature (such as Apache Common Lang, Common Math and Joda Time). For the
-mutation analysis of this study, we choose PIT, a fast and easy to use mutation
-analysis tool for Java, which has been used by researchers in the
-past~\cite{gopinath2014code,inozemtseva2014coverage} for its wide range of
-operators.
-% Amin: Total lines of code, total number of mutants
+This paper studies different mutant selection strategies on large number
+of Java programs using a popular bytecode-based mutation PIT.  We sampled
+$312$ opensource Java project between $50$ to $100K$ non-comment lines of
+code (excluding test cases) from Github and Apache Foundation. This set
+of projects include many of popular Java projects that are regualry used
+in literature (such as Apache Common Lang, Common Math and Joda Time). For
+the mutation analysis of this study, we choose PIT, a fast and easy to use
+mutation analysis tool for Java, which has been used by researchers in the
+past~\cite{gopinath2014code,inozemtseva2014coverage} for its wide range
+of operators.
 
-For this study, we experimented four classic mutation selection techniques: Constrained \cite{wong1995reducing}, E-       Selective \cite{offutt1996anexperimental}, Javalanche \cite{javalanche} and N-Selection
-\cite{offutt1993experimental}, along with two sampling approaches: element based \cite{zhang2013ase} and operator based   sampling \cite{wong1995reducing}.
-We compare test effectiveness of each of techniques
-with pure random sampling.
-Our results show that in most cases there is no statistically significant benefit for mutation selection techniques.
-Moreover, in cases with statistically significant benefit, the gain is
-so low that is essentially negligible.
+For this study, we experimented four classic mutation selection
+techniques: Constrained \cite{wong1995reducing}, E-Selective
+\cite{offutt1996anexperimental}, Javalanche \cite{javalanche} and
+N-Selection \cite{offutt1993experimental}, along with two sampling
+approaches: element based \cite{zhang2013ase} and operator based   sampling
+\cite{wong1995reducing}. We compare test effectiveness of each of techniques
+with pure random sampling. Our results show that in most cases there is no
+statistically significant benefit for mutation selection techniques. Moreover,
+in cases with statistically significant benefit, the gain is so low that is
+essentially negligible.
 
-\begin{comment}
-We have attempted to rectify this situation with a large scale study of real
-world programs. As detailed in Section~\ref{sec:methodology}, we sample
-$312$ Java programs from Github, with size ranging from $50$ to $100,000$
-lines (excluding tests), allowing us to draw more widely applicable
-statistical inferences.
-\end{comment}
-
-% For a mutation selection strategy to be considered effective, especially during
-% the development, it should be able to expose as many defect-like behaviors as
-% possible.
-
-% Alex: added
 Given a set of mutants and a universe of test cases, we can approximate the
@@
 \cite{yoo2012regression}.}  Ideally, we would like a set of mutants that
-require as many test cases as possible, if we assume that the original set
-of test cases is populated with useful, non-redundant test cases.  While
-the suites of many open source programs are far from adequate, they should
-satisfy that requirement:  each test was almost always added by considerable
-manual labor, and was at least believed to be useful.  Therefore, any tests
-omitted likely indicate a potential to miss faults.  A good mutation selection
-strategy, therefore, should 1) be as close to the original set of mutants
-as possible, in terms of the test cases it requires in a minimal suite and
-2) require more test cases than a randomly selected set of mutants of the
-same size.
+require as many test cases as possible, if we assume that the original
+set of test cases is populated with useful, non-redundant test cases.
+While the suites of many open source programs are far from adequate,
+they should satisfy that requirement:  each test was almost always added
+by considerable manual labor, and was at least believed to be useful.
+Therefore, any tests omitted likely indicate a potential to miss faults.
+A good mutation selection strategy, therefore, should 1) be as close to the
+original set of mutants as possible, in terms of the test cases it requires
+in a minimal suite and 2) require more test cases than a randomly selected
+set of mutants of the same size.
 
@@
 and execution time as other measures.
-
-% Alex: rm
-% Consider any test in a test suite. It is written with the intent of
-% checking for the absence of some (faulty) behavior. From the perspective of a
-% a tester, the best testsuite is one that checks for the absence
-% of the largest number of faulty behaviors. If tests were equivalent in the
-% amount of behaviors that they verify, then the best testsuite would be one that
-% encouraged adding the largest number of non-redundant test cases. However,
-% it is possible that different tests are not equivalent in the number of
-% behaviors that they check. We can approximate this to some extent by
-% including the number of assert statements within each test~\footnote{We
-% approximate the effect of exception-only test cases by starting the assert
-% count from $1$ rather than $0$}.
 
@@
 Thus it should choose a set of mutants that are killed by a larger number
-of such non-redundant tests at-least in comparison with random selection
-of the same number of mutants as the chosen set. We could also ensure that
-a reduction strategy does not miss out on important tests by running the
-set of non-redundant tests against the full set of mutants to see how many
-of the mutants were detected in comparison with the original number of
-detected mutants. This can again be compared to the test cases selected by
-a random sample of same number of mutants to see if the strategy performed
-better at-least with respect to random sampling. Since this evaluation crtieria
-does not depend on the mutation-adequacy of the test suite under consideration,
+of such non-redundant tests at-least in comparison with random selection of
+the same number of mutants as the chosen set. We could also ensure that a
+reduction strategy does not miss out on important tests by running the set
+of non-redundant tests against the full set of mutants to see how many of
+the mutants were detected in comparison with the original number of detected
+mutants. This can again be compared to the test cases selected by a random
+sample of same number of mutants to see if the strategy performed better
+at-least with respect to random sampling. Since this evaluation crtieria does
+not depend on the mutation-adequacy of the test suite under consideration,
 we can run the evaluation using real world projects which almost always have
@@
 
-\item Our study is the largest so far in terms of
-both the size of programs involved ($50$ to $100,000$ lines excluding tests),
-and the number of programs analyzed ($312$ unique open source projects) for
-mutant reduction strategies. This allows for stronger and more widely
-applicable conclusions about effectiveness.
+\item Our study is the largest so far in terms of both the size of programs
+involved ($50$ to $100,000$ lines excluding tests), and the number of
+programs analyzed ($312$ unique open source projects) for mutant reduction
+strategies. This allows for stronger and more widely applicable conclusions
+about effectiveness.
 
-\item We compare a much larger
-number of mutant reduction strategies than previous studies. Our reduction
-strategies include all the common and influential strategies for
-random sampling, element scoped sampling, operator based sampling,
-and operator selection, that have been proposed in previous studeies.
+\item We compare a much larger number of mutant reduction strategies
+than previous studies. Our reduction strategies include all the common
+and influential strategies for random sampling, element scoped sampling,
+operator based sampling, and operator selection, that have been proposed in
+previous studeies.
 
@@
 selection strategies we study in detail. The analysis is given in
-Section~\ref{sec:analysis}, and the results of our
-experiment are given in Section~\ref{sec:results}, followed by
-detailed discussion of what these results imply in Section
-~\ref{sec:discussion}.
+Section~\ref{sec:analysis}, and the results of our experiment are given in
+Section~\ref{sec:results}, followed by detailed discussion of what these
+results imply in Section ~\ref{sec:discussion}.

### 2015-01-19 support/init.sh
update

@@ -1,0 +1,3 @@
+export TERM=vt100
+export PATH=/scratch/usr/bin:$PATH
+export R_ENVIRON=/scratch/usr/home/.Renviron

### 2015-01-19 src/related.Rnw
format

@@
 
-The idea of mutation analysis was first proposed by Richard Lipton~\cite{mathur2012foundations},
-and formalized by DeMillo et al.~\cite{demillo1978hints} A practical implementation of
-mutation analysis was accomplished by Budd et al.~\cite{budd1980theoretical} in 1980.
+The idea of mutation analysis was first proposed by Richard
+Lipton~\cite{mathur2012foundations}, and formalized by DeMillo et
+al.~\cite{demillo1978hints} A practical implementation of mutation analysis
+was accomplished by Budd et al.~\cite{budd1980theoretical} in 1980.
 
-Mutation analysis was found to subsume different coverage measures~\cite{budd1980mutation,mathur1994empirical,offutt1996subsumption},
-and it was found that the faults produced by mutation analysis were similar to real
-faults in the errors it produced~\cite{daran1996software} and the ease of detection~\cite{andrews2005mutation,andrews2006using}.
-Just et al.~\cite{just2014mutants} investigated the relation between mutation score and test
-case effectiveness using 357 real bugs, and found that the mutation score increased
-with effectiveness for 75\% of the cases, which was better than the 46\% reported
-for structural coverage.
+Mutation analysis was found to subsume different coverage
+measures~\cite{budd1980mutation,mathur1994empirical,offutt1996subsumption},
+and it was found that the faults produced by mutation analysis were similar
+to real faults in the errors it produced~\cite{daran1996software} and the
+ease of detection~\cite{andrews2005mutation,andrews2006using}.  Just et
+al.~\cite{just2014mutants} investigated the relation between mutation score
+and test case effectiveness using 357 real bugs, and found that the mutation
+score increased with effectiveness for 75\% of the cases, which was better
+than the 46\% reported for structural coverage.
 
 The foundational assumptions of mutation analysis are the competent programmer
-hypothesis which states that programmers tend to make very simple mistakes, and
-coupling effect which states that a test case able to detect a fault in
-isolation will continue to detect it even in the presence of other
-faults~\cite{demillo1978hints}. This was confirmed using theoretical analysis by Wah~\cite{wah2000atheoretical,wah2003ananalysis}
-and using empirical studies by Offutt~\cite{offutt1989thecoupling,offutt1992investigations}
+hypothesis which states that programmers tend to make very simple mistakes,
+and coupling effect which states that a test case able to detect a fault
+in isolation will continue to detect it even in the presence of other
+faults~\cite{demillo1978hints}. This was confirmed using theoretical analysis
+by Wah~\cite{wah2000atheoretical,wah2003ananalysis} and using empirical
+studies by Offutt~\cite{offutt1989thecoupling,offutt1992investigations}
 
 There are several approaches to reducing the cost of mutation analysis.
-These were categorized by Offutt and Untch~\cite{offutt2001mutation}
-into three approaches: do \textit{fewer}, \textit{smarter}, and \textit{faster}.
-The \textit{do fewer} approaches include selective mutation and mutant sampling,
-while weak mutation, parallelization of mutation analysis, and space/time trade-offs
-are grouped under the umbrella of \textit{do smarter}. Finally
-\textit{do faster} approaches include mutant schema generation methods,
-code patching etc.
+These were categorized by Offutt and Untch~\cite{offutt2001mutation} into
+three approaches: do \textit{fewer}, \textit{smarter}, and \textit{faster}.
+The \textit{do fewer} approaches include selective mutation and mutant
+sampling, while weak mutation, parallelization of mutation analysis,
+and space/time trade-offs are grouped under the umbrella of \textit{do
+smarter}. Finally \textit{do faster} approaches include mutant schema
+generation methods, code patching etc.
 
@@
 mutation analysis itself. Budd~\cite{budd1980mutation} and
-Acree~\cite{acree1980mutation} showed that even 10\% sampling can achieve 99\%
-accuracy for the final score.  The idea was further investigated by
-Mathur~\cite{mathur1991performance}, Wong et
-al.~\cite{wong1993mutation,wong1995reducing}, and Offutt et
-al.~\cite{offutt1993experimental} using the Mothra~\cite{Mothra}
-mutation operators for Fortran. Mathur~\cite{mathur1991performance,wong1995reducing}
-suggested constrained mutation where only two operators
-were used.%, which were felt to be better than using the entire set.
+Acree~\cite{acree1980mutation} showed that even 10\% sampling
+can achieve 99\% accuracy for the final score.  The idea was
+further investigated by Mathur~\cite{mathur1991performance},
+Wong et al.~\cite{wong1993mutation,wong1995reducing}, and Offutt et
+al.~\cite{offutt1993experimental} using the Mothra~\cite{Mothra} mutation
+operators for Fortran. Mathur~\cite{mathur1991performance,wong1995reducing}
+suggested constrained mutation where only two operators were used.
 
@@
 selection and random sampling criteria. Wong et al.~\cite{wong1995reducing}
-compared x\% selection of each mutant type
-with operator selection using just two mutation operators, and found that both
-achieved similar accuracy and reduction (80\%).
+compared x\% selection of each mutant type with operator selection using
+just two mutation operators, and found that both achieved similar accuracy
+and reduction (80\%).
 
-Mresa et al.\cite{mresa1999efficiency} used the cost of detection of
-mutants as a means of selection to define a set of operators. They
-found that if very high mutation score (close to 100\%) is required,
-x\% selective mutation is better than operator selection, and,
-conversely, for lower scores, operator selection would be better if
-the cost of mutants is considered.
+Mresa et al.\cite{mresa1999efficiency} used the cost of detection of mutants
+as a means of selection to define a set of operators. They found that if very
+high mutation score (close to 100\%) is required, x\% selective mutation is
+better than operator selection, and, conversely, for lower scores, operator
+selection would be better if the cost of mutants is considered.
 
@@
 
-Recently, Zhang et al.~\cite{zhang2013ase} confirmed that sampling as
-few as 5\% of mutants was sufficient for a very high correlation
-(99\%) with full mutation score, while sampling even fewer mutants has
-good potential for retaining a high accuracy of prediction.
-They investigated eight sampling strategies on top of operator-based mutant
-selection and found that sampling strategies based on program components
-(methods in particular) performed best.
+Recently, Zhang et al.~\cite{zhang2013ase} confirmed that sampling as few as
+5\% of mutants was sufficient for a very high correlation (99\%) with full
+mutation score, while sampling even fewer mutants has good potential for
+retaining a high accuracy of prediction.  They investigated eight sampling
+strategies on top of operator-based mutant selection and found that sampling
+strategies based on program components (methods in particular) performed best.
 
-Some studies have tried to find the set of \emph{sufficient mutation
-operators} that reduce the cost of mutation but maintain correlation
-with the full mutation score. Offutt et al.~\cite{offutt1993experimental}
-suggested an $n$-selective approach with step-by-step removal of operators
-with most numerous mutations. Barbosa et al.\cite{barbosa2001toward}
-provided a set of guidelines for selecting such mutation operators.
-Namin et al.\cite{namin2006finding,siami2008sufficient} formulated
-the problem as a variable reduction problem, and
-found that just 28 out of 108 operators in Proteum were sufficient.
+Some studies have tried to find the set of \emph{sufficient mutation operators}
+that reduce the cost of mutation but maintain correlation with the full
+mutation score. Offutt et al.~\cite{offutt1993experimental} suggested
+an $n$-selective approach with step-by-step removal of operators with
+most numerous mutations. Barbosa et al.\cite{barbosa2001toward} provided
+a set of guidelines for selecting such mutation operators.  Namin et
+al.\cite{namin2006finding,siami2008sufficient} formulated the problem as a
+variable reduction problem, and found that just 28 out of 108 operators in
+Proteum were sufficient.
 
@@
 Untch~\cite{untch2009onreduced}, who found that it had the highest
-correlation ($R^2 = 0.97$) with the full mutation score compared to
-other operator selection methods, while generating the smallest number of
-mutants.  This was further reinforced by Deng et al.~\cite{deng2013empirical}
-who defined deletion for different language elements, and found that an
-accuracy of 92\% is achieved while reducing the number of mutants by 80\%.
+correlation ($R^2 = 0.97$) with the full mutation score compared to other
+operator selection methods, while generating the smallest number of mutants.
+This was further reinforced by Deng et al.~\cite{deng2013empirical} who defined
+deletion for different language elements, and found that an accuracy of 92\%
+is achieved while reducing the number of mutants by 80\%.
 
@@
 includes Higher Order Mutants, where by multiple mutations are introduced
-into the same set of mutants, reducing the total number of individual mutants
-by subsuming the component mutants. These have investigated by
-Jia et al.~\cite{jia2009higher,jia2008constructing}, and finds that it can
-reduce the number of mutants by 50\%.
+into the same set of mutants, reducing the total number of individual
+mutants by subsuming the component mutants. These have investigated by Jia
+et al.~\cite{jia2009higher,jia2008constructing}, and finds that it can reduce
+the number of mutants by 50\%.
 

### 2015-01-19 src/methodology.Rnw
updates

@@
-\section{Methodology} \label{sec:methodology} Our selection of
-programs was driven by a few overriding concerns. Our primary
-requirement was that our results had to be as widely applicable as
-possible for real-world programs. Secondly, we strived for a
-statistically significant result, reducing the number of variables
-present in the experiments. For this reason we chose a random sample
-of Java projects from Github~\cite{github} and Apache Software
-Foundation~\cite{apache} that use the popular
-maven~\cite{maven} build system, following the methodology we used
-previously in an ICSE 2014 paper~\cite{gopinath2014code}.
+\section{Methodology}
+\label{sec:methodology}
+Our selection of programs was driven by a few overriding concerns. Our
+primary requirement was that our results had to be as widely applicable as
+possible for real-world programs. Secondly, we strived for a statistically
+significant result, reducing the number of variables present in the
+experiments. For this reason we chose a random sample of Java projects from
+Github~\cite{github} and Apache Software Foundation~\cite{apache} that use
+the popular maven~\cite{maven} build system, following the methodology we
+used previously in an ICSE 2014 paper~\cite{gopinath2014code}.
 
 We ran mutation analysis on this set of projects using
-PIT\cite{pitest}. However, since the operators provided by PIT are
-limited, we extended PIT to provide newer operators that are similar to
-operators provided by other mutation systems. The set of operators that
-we used is provided in Table~\ref{tbl:pitop}.
+PIT\cite{pitest}. However, since the operators provided by PIT are limited,
+we extended PIT to provide newer operators that are similar to operators
+provided by other mutation systems. The set of operators that we used is
+provided in Table~\ref{tbl:pitop}.
 
@@
 Table~\ref{tbl:subsumption}, and a visualization of the subsumption is
-presented in Figure~\ref{fig:subsumption}. This shows that the operators
+presented in Figure~\ref{fig:subsumption}. In the figure, the amount of
+subsumption is indicated by removal of area from the circle, with same
+operators subsuming themselves entirely. This suggests that the operators
 we used were non-redundant, with a maximum subsumption of only $40\%$.
+The Figure~\ref{fig:mutationshare} shows the share of each mutation operators
+in the total number of mutants produced, and the Figure~\ref{fig:mutationkills}
+shows the detection and covering rate of mutants by test cases.
 
-% Figure~\ref{fig:op} shows
-% the distribution of mutants and the relative detection rates of each
-% mutation operator for our projects. In the figure, there are two box-plots
-% corresponding to each mutation operator on the Y-axis. The black box represents
-% the relative frequency of the particular mutation operator in the total
-% mutants \textit{produced}. For example, for projects in the (Randoop) generated set,
-% the operator \pitnvmc contributed about 34\% of the total number of mutants
-% produced while \pitrv contributed about 7\%. Similarly, the blue shaded
-% box-plot represents the relative frequency of particular mutation operator
-% in the total mutants \textit{detected}. For example, \Pitnvmc contribution
-% in the detected mutants was 23\% while that of \Pitrv was 15\%.
-
-For a detailed description of each mutation operator, please refer to PIT documentation~\cite{pitmut}.
-We modified PIT to report the entire test matrix of $tests \times failures$
-rather than just the first failure, and used this for our analysis. To remove
-the effects of random noice, results of each criteria was averaged out of ten
-runs.
+For a detailed description of each mutation operator, please refer to PIT
+documentation~\cite{pitmut}.  We modified PIT to report the entire test
+matrix of $tests \times failures$ rather than just the first failure, and
+used this for our analysis. To remove the effects of random noise, results
+of each criteria was averaged out of ten runs.
 

### 2015-01-19 src/methodology.Rnw
update

@@
+<<tblsubsumption, child='tbl.subsumption.Rnw'>>=
+@
+
+<<tblpitmut, child='tbl.pitmut.Rnw'>>=
+@
+<<figsubsumption, child='fig.subsumption.Rnw'>>=
+@
+
 \section{Methodology}
@@
 of each criteria was averaged out of ten runs.
-
-\begin{table}
-\small{
-\begin{tabular}{ll}
-\hline \hline \\
-\Pitin & Remove negative sign from numbers\\
-\Pitrv & Mutate return values\\
-\Pitm & Mutate arithmetic operators\\
-\Pitvmc & Remove void method calls\\
-\Pitnc & Negate conditional statements\\
-\Pitcb & Modify boundaries in logical conditions\\
-\Piti & Modify increment and decrement statements\\
-\Pitnvmc & Remove non-void method calls, returning default value \\
-\Pitcc & Replace constructor calls, returning null \\
-\Pitic & Replace inline constants with default value \\
-\Pitri & Remove increment and decrement statements \\
-\Pitemv & Replace member variable assignments with default value \\
-\Pites & Modify switch statements \\
-\Pitrs & Replace switch labels with default (thus removing them) \\
-\Pitrc & Replace boolean conditions with true\\
-\Pitnc & Replace boolean conditions with false\\
-\hline
-\end{tabular}
-}
-\caption{PIT Mutation Operators (We have used abbreviations instead of operator names.)}
-\label{tbl:pitop}
-\end{table}
 

### 2015-01-19 src/tbl.pitmut.Rnw
updat

\begin{table}
\small{
\begin{tabular}{ll}
\hline \hline \\
\Pitin & Remove negative sign from numbers\\
\Pitrv & Mutate return values\\
\Pitm & Mutate arithmetic operators\\
\Pitvmc & Remove void method calls\\
\Pitnc & Negate conditional statements\\
\Pitcb & Modify boundaries in logical conditions\\
\Piti & Modify increment and decrement statements\\
\Pitnvmc & Remove non-void method calls, returning default value \\
\Pitcc & Replace constructor calls, returning null \\
\Pitic & Replace inline constants with default value \\
\Pitri & Remove increment and decrement statements \\
\Pitemv & Replace member variable assignments with default value \\
\Pites & Modify switch statements \\
\Pitrs & Replace switch labels with default (thus removing them) \\
\Pitrc & Replace boolean conditions with true\\
\Pitnc & Replace boolean conditions with false\\
\hline
\end{tabular}
}
\caption{PIT Mutation Operators (We have used abbreviations instead of operator names.)}
\label{tbl:pitop}
\end{table}

### 2015-01-19 src/methodology.Rnw
update tables

@@
 we computed their operator subsumption matrix. This is given in
-Table~\ref{tbl:subsumption}, and a visualization of the subsumption is
+Table~\ref{tbl:subsumption}. In the table, the mean number of mutants
+of an operator in the row subsumed by another operator in the column
+is given as the decimal fraction (i.e $1.0$ suggests complete subsumption
+of one mutation operator by the other). A visualization of the subsumption is
 presented in Figure~\ref{fig:subsumption}. In the figure, the amount of

### 2015-01-19 src/tbl.pitmut.Rnw
update tables

@@
-\begin{table}
-\small{
-\begin{tabular}{ll}
-\hline \hline \\
-\Pitin & Remove negative sign from numbers\\
-\Pitrv & Mutate return values\\
-\Pitm & Mutate arithmetic operators\\
-\Pitvmc & Remove void method calls\\
-\Pitnc & Negate conditional statements\\
-\Pitcb & Modify boundaries in logical conditions\\
-\Piti & Modify increment and decrement statements\\
-\Pitnvmc & Remove non-void method calls, returning default value \\
-\Pitcc & Replace constructor calls, returning null \\
-\Pitic & Replace inline constants with default value \\
-\Pitri & Remove increment and decrement statements \\
-\Pitemv & Replace member variable assignments with default value \\
-\Pites & Modify switch statements \\
-\Pitrs & Replace switch labels with default (thus removing them) \\
-\Pitrc & Replace boolean conditions with true\\
-\Pitnc & Replace boolean conditions with false\\
-\hline
-\end{tabular}
-}
-\caption{PIT Mutation Operators (We have used abbreviations instead of operator names.)}
-\label{tbl:pitop}
-\end{table}
+In order to ensure that the operators that we added were not redundant,
+we computed their operator subsumption matrix. This is given in
+Table~\ref{tbl:subsumption}. In the table, the mean number of mutants
+of an operator in the row subsumed by another operator in the column
+is given as the decimal fraction (i.e $1.0$ suggests complete subsumption
+of one mutation operator by the other). A visualization of the subsumption is
+presented in Figure~\ref{fig:subsumption}. In the figure, the amount of
+subsumption is indicated by removal of area from the circle, with same
+operators subsuming themselves entirely. This suggests that the operators
+we used were non-redundant, with a maximum subsumption of only $40\%$.
+The Figure~\ref{fig:mutationshare} shows the share of each mutation operators
+in the total number of mutants produced, and the Figure~\ref{fig:mutationkills}
+shows the detection and covering rate of mutants by test cases.

### 2015-01-19 src/methodology.Rnw
update

@@
 @
-
 <<tblpitmut, child='tbl.pitmut.Rnw'>>=
@@
 in the total number of mutants produced, and the Figure~\ref{fig:mutationkills}
-shows the detection and covering rate of mutants by test cases.
+shows the relative frequency with which tests are able to cover and kill
+different mutation operators.
 

### 2015-01-19 src/methodology.Rnw
update

@@
 \subsection{Sampling Criteria}
-
 We used several different sampling criteria that has been mentioned in the
 literature, For each sampling criteria, we sampled mutants on a decreasing
-power scale, sampling \textit{1/2, 1/4, 1/8, 1/16, 1/32, 1/64} of the total
-mutants.
+power scale, sampling $\frac{1}{2}$, $\frac{1}{4}$, $\frac{1}{8}$,
+$\frac{1}{16}$, $\frac{1}{32}$, $\frac{1}{64}$ of the total mutants.
 
-\subsubsection{x\% selection}
-The simplest sampling approach consisted of using x\% selection as suggested by
-Budd~\cite{budd1980mutation}. In this criteria, we choose a specific
+\subsubsection{Uniform random sampling}
+The simplest sampling approach consisted of using x\% selection as suggested
+by Budd~\cite{budd1980mutation}. In this criteria, we choose a specific
 fraction of the complete set of mutants. This criteria also serves as a
@@
 
-\subsubsection{x\% selection per operator}
-This strategy, first suggested by Wong et al.~\cite{wong1995reducing} samples an equal percentage
-of mutants from each operator.
+\subsubsection{Stratified random sampling over mutation operators}
+This strategy, first suggested by Wong et al.~\cite{wong1995reducing}
+samples an equal percentage of mutants from each operator. While Wong seems
+to treat this as same as x\% selection, without giving any further
+justification as to why it was used instead, we note that this sampling is
+subtly different from pure random sampling in that it provides a stratified
+sampling based on mutation operators.
 
-\subsubsection{Sampling over program elements}
-Following the suggestion of Zhang et al.~\cite{zhang2013ase}, we
-extended x\% selection criteria to sample from within different program
-elements.  We sampled in increasing order of scope,
---- \textit{line}, \textit{method} and \textit{class} (\textit{project}
-scope is just x\% selection).
+\subsubsection{Stratified random sampling over program elements}
+Following the suggestion of Zhang et al.~\cite{zhang2013ase}, we extended
+x\% selection criteria to sample from within different program elements.
+We sampled in increasing order of scope, --- \textit{line}, \textit{method}
+and \textit{class} (\textit{project} scope is just x\% selection).
 
@@
 operator selection. Note that all of these techniques except Javalanche have
-targeted C programs. Thus, some of these operators may be sensible in C but not
-in Java. For example, deletion of return statement is tolerated in C,
+targeted C programs. Thus, some of these operators may be sensible in C but
+not in Java. For example, deletion of return statement is tolerated in C,
 not in Java.  Moreover, there were a few operators that were not supported
@@
 \subsubsection{Constrained Mutation}
-\noindent\textbf{Wong et al. ~\cite{wong1995reducing}.}
-They selected ROR  and ABS  from Mothra for
-mutation analysis. We used operators
-\Pitcb and \Pitnc to model ROR operator. There are no comparable operators to ABS in PIT.
+\noindent\textbf{Wong et al. ~\cite{wong1995reducing}.} They selected ROR
+and ABS from Mothra for mutation analysis. We used operators \Pitcb and
+\Pitnc to model ROR operator. There are no comparable operators to ABS in PIT.
 
 \subsubsection{E-Selective}
-\noindent\textbf{Offut et al. \cite{offutt1996anexperimental}.}
-They selected ABS, UOI, LCR, AOR, ROR from Mothra operators.
-We have used  \Pitin, \Pitm, \Pitcb, and \Pitnc. PIT does not have any operator
-comparable to LCR.
+\noindent\textbf{Offut et al. \cite{offutt1996anexperimental}.} They selected
+ABS, UOI, LCR, AOR, ROR from Mothra operators.  We have used  \Pitin, \Pitm,
+\Pitcb, and \Pitnc. PIT does not have any operator comparable to LCR.
 
@@
 \noindent\textbf{Javalanche \cite{javalanche}.}
-Javalanche uses Negate Jump Condition, Omit Method
- Call, Replace Arithmetic Operator, and Replace Numerical
- Constant operators. We have used \Pitnc, \Pitvmc,
-\Pitnvmc, \Pitm, \Pitic and \Pitemv to model them.
+Javalanche uses Negate Jump Condition, Omit Method Call, Replace Arithmetic
+Operator, and Replace Numerical Constant operators. We have used \Pitnc,
+\Pitvmc, \Pitnvmc, \Pitm, \Pitic and \Pitemv to model them.
 

### 2015-01-19 src/methodology.Rnw
update

@@
 \noindent\textbf{Wong et al. ~\cite{wong1995reducing}.} They selected ROR
-and ABS from Mothra for mutation analysis. We used operators \Pitcb and
-\Pitnc to model ROR operator. There are no comparable operators to ABS in PIT.
+and ABS from Mothra for mutation analysis. The ABS operator was chosen with
+the reasoning that it forces users to consider all parts of the input domain,
+and ROR was chosen because it forces users to consider values of predicates.
+ROR mutates relational operators, while ABS replaces variables and expressions
+by their positive or negative absolute value or zero. \Pitcb and \Pitnc from
+PIT are a good map for ROR. However, we could not map ABS to PIT operators.
+
+% ROR Relational Operator Replacement a > b to b < a
+% ABS Absolute value insertion a = b to a = abs(b), -abs(b), 0
 
@@
 \subsubsection{N-selection}
-\noindent\textbf{Offut et al. ~\cite{offutt1993experimental}.} They suggested removal of
-$n$ most numerous operators. In our experiment, the order of operators was
-\Pitnvmc, \Pitrv, \Pitic, \Pitdc, \Pitnc, \Pitrc, \Pitvmc, \Pitcc, \Pitemv,
-\Pitm, \Pitcb, \Piti, \Pitri, \Pitrs, \Pites, and \Pitin.
-We discarded one at each
-step and evaluated the effectiveness at each $n$.
-%----------------------------------------
+\noindent\textbf{Offut et al. ~\cite{offutt1993experimental}.} They suggested
+removal of $n$ most numerous operators. In our experiment, the order of
+operators was \Pitnvmc, \Pitrv, \Pitic, \Pitdc, \Pitnc, \Pitrc, \Pitvmc,
+\Pitcc, \Pitemv, \Pitm, \Pitcb, \Piti, \Pitri, \Pitrs, \Pites, and \Pitin.
+We discarded one at each step and evaluated the effectiveness at each $n$.
+
 \subsubsection{Statement deletion emulation} \label{subsec:stmtdel}
+The original statement deletion was proposed by Acree~\cite{acree1980onmutation}.
 

### 2015-01-19 src/methodology.Rnw
add varreduction

@@
 by their positive or negative absolute value or zero. \Pitcb and \Pitnc from
-PIT are a good map for ROR. However, we could not map ABS to PIT operators.
+PIT are a good map for ROR. Similarly, \Pitin is able to partially provide ABS
+functionality.
 
@@
 \subsubsection{E-Selective}
-\noindent\textbf{Offut et al. \cite{offutt1996anexperimental}.} They selected
-ABS, UOI, LCR, AOR, ROR from Mothra operators.  We have used  \Pitin, \Pitm,
-\Pitcb, and \Pitnc. PIT does not have any operator comparable to LCR.
+\noindent\textbf{Offut et al. \cite{offutt1996anexperimental}.} Mothra supports
+three main classes of operators; operand mutators, operator (expression)
+mutators and statement mutators. The E-Selective strategy chooses only those
+mutators that modify operators. These for Mothra were ABS, UOI, LCR, AOR, and
+ROR. UOI operates by incrementing or decrementing arithmetic expressions by 1,
+LCR changes the relational operators, and AOR mutates arithmetic operators.
+
+% UOI : Unary insertion : toggle +1, -1
+% LCR : Logical connectives : a && b -> a || b, a, b, T, F
+% AOR : Arithmetic a + b ->  a - b, *,%,a,b
+
+For mapping to PIT, we have tried to follow the spirit of choosing only
+operator mutators form the mutators available in PIT. The operators we have
+used are \Pitin, \Pitm, \Pitcb, \Pitnc, \Pitrc, and \Pitnc.
 
@@
 \noindent\textbf{Namin et al.~\cite{siami2008sufficient}.}
-They have tried to reduce the mutation operators of Proteum analysis
-tool which is for C programs. They suggest 28 operators which many of them
-are not applicable in Java, and some not in PIT.
-We  used by  \Pitin, \Pitm, \Piti, and \Pitnc.
+For variable reduction, Namin framed the question of finding the best set of
+mutation operators as a statistical problem of finding the set of operators
+such that we can best predict the final mutation score. That is, given that
+$M$ is the final mutation score, and $m_1,m_2..m_n$ are mutation scores given
+by $n$ mutation operators, Namin wanted to find the smallest set of mutations
+such that we can predict $M$ from the set of $m_{1..n}$. This boils down to
+finding the linear model
+
+\[M = \alpha m_1 + \beta m_2 ... \omega m_n\]
+
+where $\alpha,\beta .. \omega$ are constants. However we take advantage of the
+limited set of operators to run a complete subset model comparison to obtain
+the best model given by
+\[\mu{M_s} = 0+.55 nmc + .2 rc + .1 dc + .2 rv + .1 cc + .7emv + .02 m + .02 ri \]
+
+with $R^2 = 0.96$. This suggests that the variables we should be interested
+in are \Pitnvmc, \Pitrc, \Pitdc, \Pitrv, \Pitcc, \Pitemv, \Pitm, \Pitri
+
+\begin{comment}
+Call:
+lm(formula = x ~ xnmc + xrc + xdc + xrv + xcc + xemv + xm + xri)
+
+Residuals:
+     Min       1Q   Median       3Q      Max 
+-0.12643 -0.01446 -0.00313  0.00768  0.52589
+
+Coefficients:
+             Estimate Std. Error t value Pr(>|t|)    
+(Intercept)  0.003130   0.004537   0.690  0.49083    
+xnmc         0.549245   0.031977  17.176  < 2e-16 ***
+xrc          0.197321   0.037466   5.267 2.64e-07 ***
+xdc          0.067979   0.027314   2.489  0.01336 *  
+xrv          0.205544   0.028226   7.282 2.87e-12 ***
+xcc         -0.074420   0.023555  -3.159  0.00174 ** 
+xemv         0.071699   0.020909   3.429  0.00069 ***
+xm           0.022937   0.015159   1.513  0.13131    
+xri         -0.026070   0.016472  -1.583  0.11453    
+---
+Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
+
+Residual standard error: 0.05318 on 302 degrees of freedom
+Multiple R-squared:  0.9669,  Adjusted R-squared:  0.9661 
+F-statistic:  1104 on 8 and 302 DF,  p-value: < 2.2e-16
+
+\end{comment}
+
+%The variable reduction procedure given by Namin results in 28 operators of
+%Proteum analysis tool. Unfortunately for us, unlike the previous selection
+%techniques
+
+%They have tried to reduce the mutation operators of Proteum analysis
+%tool which is for C programs. They suggest 28 operators which many of them
+%are not applicable in Java, and some not in PIT.
+%We used \Pitin, \Pitm, \Piti, and \Pitnc.
 
@@
 \subsubsection{Statement deletion emulation} \label{subsec:stmtdel}
-The original statement deletion was proposed by Acree~\cite{acree1980onmutation}.
-
 The statement deletion based operator selection was based on the work by

### 2015-01-19 src/methodology.Rnw
fix methodology

@@
 \noindent\textbf{Offut et al. \cite{offutt1996anexperimental}.} Mothra supports
-three main classes of operators; operand mutators, operator (expression)
-mutators and statement mutators. The E-Selective strategy chooses only those
+three main classes of operators; Replacement (operand) mutators, Expression (operator)
+mutators and Statement mutators. The operator selections used in this paper
+are groupings of these operators, such as ES, ER, RS, RS, and E.
+
+The best strategy identified was E-Selective strategy chooses only those
 mutators that modify operators. These for Mothra were ABS, UOI, LCR, AOR, and
@@
 
+To accomplish the same with Pit, we divided the Pit operators similarly.
+Operand mutators are \Pitic, \Pitemv, and \Pitin. Operator mutators are \Pitm,
+\Pitcb, \Pitnc, \Pitrc, and \Pitdc. Statement mutators are given by \Pitrv,
+\Piti, \Pitvmc, \Pitnvmc, \Pitcc, \Pitri, \Pites, \Pitrs.
+
 % UOI : Unary insertion : toggle +1, -1
@@
 % AOR : Arithmetic a + b ->  a - b, *,%,a,b
-
-For mapping to PIT, we have tried to follow the spirit of choosing only
-operator mutators form the mutators available in PIT. The operators we have
-used are \Pitin, \Pitm, \Pitcb, \Pitnc, \Pitrc, and \Pitnc.
 

### 2015-01-19 src/methodology.Rnw
update

@@
 mutators and Statement mutators. The operator selections used in this paper
-are groupings of these operators, such as ES, ER, RS, RS, and E.
+are groupings of these operators, such as ES, ER, RE, RS, and E.
 
@@
 \Piti, \Pitvmc, \Pitnvmc, \Pitcc, \Pitri, \Pites, \Pitrs.
+
+We report the results of all combinations: ES, ER, RS, E, R, and S
 
@@
 such that we can predict $M$ from the set of $m_{1..n}$. This boils down to
-finding the linear model
+finding the linear model statistically.
 
-\[M = \alpha m_1 + \beta m_2 ... \omega m_n\]
+We take advantage of the limited set of operators to run a complete subset
+model comparison to obtain the best model given by
 
-where $\alpha,\beta .. \omega$ are constants. However we take advantage of the
-limited set of operators to run a complete subset model comparison to obtain
-the best model given by
 \[\mu{M_s} = 0+.55 nmc + .2 rc + .1 dc + .2 rv + .1 cc + .7emv + .02 m + .02 ri \]

### 2015-01-19 src/introduction.Rnw
fix up intro

@@
 
-For this study, we experimented four classic mutation selection
+For this study, we experimented five classic mutation selection
 techniques: Constrained \cite{wong1995reducing}, E-Selective
-\cite{offutt1996anexperimental}, Javalanche \cite{javalanche} and
-N-Selection \cite{offutt1993experimental}, along with two sampling
-approaches: element based \cite{zhang2013ase} and operator based   sampling
+\cite{offutt1996anexperimental}, Javalanche \cite{javalanche},
+Variable Reduction~\cite{namin2006finding} and N-Selection
+\cite{offutt1993experimental}, along with two sampling approaches:
+element based \cite{zhang2013ase} and operator based sampling
 \cite{wong1995reducing}. We compare test effectiveness of each of techniques
@@
 Thus it should choose a set of mutants that are killed by a larger number
-of such non-redundant tests at-least in comparison with random selection of
-the same number of mutants as the chosen set. We could also ensure that a
-reduction strategy does not miss out on important tests by running the set
-of non-redundant tests against the full set of mutants to see how many of
-the mutants were detected in comparison with the original number of detected
-mutants. This can again be compared to the test cases selected by a random
-sample of same number of mutants to see if the strategy performed better
-at-least with respect to random sampling. Since this evaluation crtieria does
-not depend on the mutation-adequacy of the test suite under consideration,
-we can run the evaluation using real world projects which almost always have
-non-adequate test suites.
+of such non-redundant tests at-least in comparison with random selection
+of the same number of mutants as the chosen set. We could also ensure that
+a reduction strategy does not miss out on important tests by running the
+set of non-redundant tests against the full set of mutants to see how many
+of the mutants were detected in comparison with the original number of
+detected mutants~\footnote{This is defined as the operator mutation score
+by Mresa et al.~\cite{mresa1999efficiency}. But the term mutation score is
+already a popular synonym for the mutation fraction detected. We call it the
+strategy effectiveness in this paper}. This can again be compared to the test
+cases selected by a random sample of same number of mutants to see if the
+strategy performed better at-least with respect to random sampling. Since
+this evaluation crtieria does not depend on the mutation-adequacy of the
+test suite under consideration, we can run the evaluation using real world
+projects which almost always have non-adequate test suites.
 

### 2015-01-19 src/tables.Rnw
update

@@
 \begin{table*}[!ht]
-<<tblsingles, child='tbl.singleop.Rnw'>>=
+<<tblsingle,results='asis'>>=
+norder <- c('nmc','rv','ic','dc','nc','rc','vmc','cc','emv','m','cb','i','ri','rs','es','in')
+print(tbl.place(xtable(eff(s.singles.db[norder,]), caption='Single Operators', label='table:singles')), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
 @
-%\caption*{Single Operators}
 \caption {The single operator selection strategy}

### 2015-01-19 src/tables.Rnw
update

@@
 \begin{table*}[!ht]
+<<tblsingle,results='asis'>>=
+norder <- c('nmc','rv','ic','dc','nc','rc','vmc','cc','emv','m','cb','i','ri','rs','es','in')
+print(tbl.place(xtable(eff(s.singles.db[norder,]), caption='Single Operators', label='table:singles')), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
+@
+\caption {The single operator selection strategy}
+\label{tbl:singles}
+\end{table*}
+
+\begin{table*}[!ht]
 %\caption*{Operator Samples x\%}
@@
 \label{tbl:opsample}
+\caption*{
+The test and assert utility shows how good the mutation strategy is with respect to baseline in selecting non-redundant test cases.
+The mutation share is the fraction of mutants produced by the strategy compared to the full set.
+The strategy effectiveness shows how many of the total mutants would be caught by a test suite selected by the strategy mutants.
+}
+
 \end{table*}
@@
 \end{table*}
-
-\begin{table*}[!ht]
-<<tblsingle,results='asis'>>=
-norder <- c('nmc','rv','ic','dc','nc','rc','vmc','cc','emv','m','cb','i','ri','rs','es','in')
-print(tbl.place(xtable(eff(s.singles.db[norder,]), caption='Single Operators', label='table:singles')), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
-@
-\caption {The single operator selection strategy}
-\label{tbl:singles}
-\end{table*}

### 2015-01-19 src/tbl.ttests.Rnw
update

@@
+\begin{table*}[!ht]
 <<results='asis'>>=
@@
 @
+\caption {The t-test for difference between mutants selected by reduction strategies and the baseline. It shows that there is no practical difference between the two.}
+\label{tbl:ttests}
+\end{table*}

### 2015-01-19 src/methodology.Rnw
update
fix javalanche

@@
 \subsubsection{Constrained Mutation}
-\noindent\textbf{Wong et al. ~\cite{wong1995reducing}.} They selected ROR
+\noindent\textbf{Wong et al.~\cite{wong1995reducing}.} They selected ROR
 and ABS from Mothra for mutation analysis. The ABS operator was chosen with
@@
 \subsubsection{E-Selective}
-\noindent\textbf{Offut et al. \cite{offutt1996anexperimental}.} Mothra supports
+\noindent\textbf{Offutt et al.~\cite{offutt1996experimental}.} Mothra supports
 three main classes of operators; Replacement (operand) mutators, Expression (operator)
@@
 \subsubsection{Javalanche}
-\noindent\textbf{Javalanche \cite{javalanche}.}
-Javalanche uses Negate Jump Condition, Omit Method Call, Replace Arithmetic
-Operator, and Replace Numerical Constant operators. We have used \Pitnc,
-\Pitvmc, \Pitnvmc, \Pitm, \Pitic and \Pitemv to model them.
+\noindent\textbf{Javalanche~\cite{schuler2009efficient,schuler2009javalanche}.}
+Javalanche adapts for Java bytecodes the e-selective operator set suggested by
+Offutt et al.~\cite{offutt1996experimental} and translated for C by Andrews
+et al.~\cite{andrews2005mutation}. The original operators adapted by Andrews
+were 1) replacing an integer constant by its predecessor, successor or by a
+small constant 2) replacing arithmetic or boolean operators by an operator
+of the same class 3) negate boolean conditions in control flow and 4)
+statement deletion.
+
+This was adapted to work with bytecodes in Javalanche, and was translated
+to~\cite{schuler2009efficient} 1) replace numerical constant
+operators 2) replace arithmetic operator, 3) negate jump condition. The last
+operator 4) omit method call was added later~\cite{schuler2009javalanche}.
+\footnote{
+We note that we have already given a translation of the original operators
+suggested by Offutt as the idea applies to PIT. Here, we are trying to
+evaluate how the translation implemented by Javalanche works.
+
+We also note that while not published, Javalanche has since added
+more operators in the default set. However it is not clear if they belong
+to a selected set under some criteria or if Javalanche is attempting to
+just increase the repertoire of mutations available.}
+
+These map directly to PIT operators \Pitic, \Pitm, \Pitnc, and \Pitvmc.
 
@@
 with $R^2 = 0.96$. This suggests that the variables we should be interested
-in are \Pitnvmc, \Pitrc, \Pitdc, \Pitrv, \Pitcc, \Pitemv, \Pitm, \Pitri
+in are \Pitnvmc, \Pitrc, \Pitdc, \Pitrv, \Pitcc, \Pitemv, \Pitm, and \Pitri.
 
@@
 \subsubsection{N-selection}
-\noindent\textbf{Offut et al. ~\cite{offutt1993experimental}.} They suggested
+\noindent\textbf{Offutt et al.~\cite{offutt1993experimental}.} They suggested
 removal of $n$ most numerous operators. In our experiment, the order of

### 2015-01-19 src/introduction.Rnw
update

@@
 the compilation step to gain execution speed} based mutation engines such as
-PIT~\cite{pitest} and Javalanche~\cite{javalanche} becoming common in both
+PIT~\cite{pitest} and Javalanche~\cite{schuler2009efficient} becoming common in both
 development and research (e.g. \cite{zhang2013ase}, \cite{gopinath2014code},
@@
 techniques: Constrained \cite{wong1995reducing}, E-Selective
-\cite{offutt1996anexperimental}, Javalanche \cite{javalanche},
+\cite{offutt1996anexperimental}, Javalanche \cite{schuler2009efficient},
 Variable Reduction~\cite{namin2006finding} and N-Selection

### 2015-01-19 src/analysis.Rnw
subsumption
updates
update
udpate

@@
 @
-
 \section{Analysis}
@@
 sample which is taken as the baseline. That is, test utility is given by
-$\left(\frac{|min(T_{strategy})|}{|min(T_{random})|}-1\right)\times 100.0$
+\[\left(\frac{|min(T_{strategy})|}{|min(T_{random})|}-1\right)\times 100.0\]
 
@@
 as the baseline. It is given by
-$\left(\frac{|asserts(min(T_{strategy}))|}{|asserts(min(T_{random}))|}-1\right)\times 100.0$
+\[\left(\frac{|asserts(min(T_{strategy}))|}{|asserts(min(T_{random}))|}-1\right)\times 100.0\]
 
@@
 is then divided by the original number of detected mutants. It is given by
-$\frac{|k(T_{random})|}{|k(M)|}\times 100.0$.
+\[\frac{|k(T_{random})|}{|k(M)|}\times 100.0\]
 
@@
 given by 
-$\frac{|k(T_{strategy})| - |k(T_{random})|}{|k(M)|}\times100.0$.
+\[\frac{|k(T_{strategy})| - |k(T_{random})|}{|k(M)|}\times100.0\]
 
@@
 \caption{The relative contribution of mutation operators in terms of fraction of mutants produced and detected.}
+\label{fig:mutationshare}
 \end{figure*}
@@
 \caption{The relative contribution of mutation operators in terms of fraction of tests killed and covered.}
+\label{fig:mutationkills}
 \end{figure*}
@@
 
-\begin{table*}[!ht]
 <<tblttest, child='tbl.ttests.Rnw'>>=
 @
-%\caption*{Single Operators}
-\caption {The t-test results}
-\label{tbl:ttests}
-\end{table*}

### 2015-01-19 src/discussion.Rnw
update t-test table

@@
 \subsubsection{Operator Selection}
-From Table~\ref{tbl:selective}, we see that except for statement deletion, we
-have negative utility in comparison to baseline for both tests and asserts.
-Even for statement deleition, the utility is just 0.5 tests better than
-baseline. A similar result is present in the strategy effectiveness also,
-where the effectiveness over baseline is either negettive or extremely small.
+From Table~\ref{tbl:selective}, looking at the test and assert utility,
+we see that there are a few selective strategies that seem to score a positive
+test utility. Notably, the statement modification strategy sselective does
+about 1.86\% better than the random selection for test utility, and has similar
+advantage in assert utility. It also seem to have a slight advantage of 0.27\%
+in the strategy effectivenss.
+
+The statistical analysis in Table~\ref{tbl:ttests}
 

### 2015-01-19 src/ttests.Rnw
update t-test table

@@
 eselective.m <- mutant.t.test(db)
+
+db <- subset(common.db, operator=="sselective")
+sselective.t <- mintc.t.test(db)
+sselective.m <- mutant.t.test(db)
+
+db <- subset(common.db, operator=="rselective")
+rselective.t <- mintc.t.test(db)
+rselective.m <- mutant.t.test(db)
+
+db <- subset(common.db, operator=="esselective")
+esselective.t <- mintc.t.test(db)
+esselective.m <- mutant.t.test(db)
+
+db <- subset(common.db, operator=="reselective")
+reselective.t <- mintc.t.test(db)
+reselective.m <- mutant.t.test(db)
+
+db <- subset(common.db, operator=="rsselective")
+rsselective.t <- mintc.t.test(db)
+rsselective.m <- mutant.t.test(db)
 

### 2015-01-19 src/discussion.Rnw
update

--- 2015-01-15 src/discussion.Rnw
@@
 
-To be added.
+We will analyze each of the different types of mutation reduction strategies in
+detail, and summarize the broad patterns we see at the end.
+
+\subsubsection{Operator Selection}
+From Table~\ref{tbl:selective}, looking at the test and assert utility, we
+see that there are a few selective strategies that seem to score a positive
+test utility. Notably, the statement modification strategy sselective does
+about 1.86\% better than the random selection for test utility, and has
+similar advantage in assert utility. It also seem to have a slight advantage
+of 0.27\% in the strategy effectivenss.
+
+The statistical analysis in Table~\ref{tbl:ttests} also suggests a positive
+mean and a $p-value < 0.01$ for this result.
+
+For N-selection, which is given in Table~\ref{tbl:nselection}, The best
+utility was on removal of \Pitnvmc, \Pitrv, \Pitic, \Pitdc, and \Pitnc which
+resulted in a test utility advantage of 2.67\%. It also have the best positive
+strategy effectiveness of 0.29\%. However, the difference was not significant
+using t-tests in Table~\ref{tbl:ttests} $p-value > 0.01$.~\footnote{The
+difference between Table~\ref{tbl:nselection} and Table~\ref{tbl:ttests}
+is due to test or mutant number being zero for baseline, and hence remvoed
+for computing percentage}.
+
+Using single operators, we get a better result of 7.77\% for \Pitrv, which
+is also significant at $p-value < 0.01$.
+
+\subsubsection{Stratified sampling over operators}
+For stratified sampling over operators in Table~\ref{tbl:opsample}, the best
+result appears to be at $\frac{1}{8}$, which gives an advantage of 1.64\% over
+baseline. However, we note that the strategy effectiveness is negative. For
+t-test, since this is a continuum, we only inspected if the strategy as a
+whole (not particular fractions) hold any advantage. The t-test suggests that
+there is no significant difference from the baseline for this kind of sampling.
+
+\subsubsection{Stratified sampling over program elements}
+For stratified sampling over program elements in Table~\ref{tbl:element},
+there appears a small consistent advantage for most sample fractions. The best
+utility achieved was 3.85\% for class based $\frac{1}{16}$ sample. As before,
+as this is a continuum, we only checked whether this kind of sampling has any
+significant advantage as a whole with t-test. The t-test suggests that all
+sampling over elements have a small but consistent advantage $p-value < 0.01$
+
+A general pattern that we can glean from this analysis is that none of
+the mutation reduction strategies appear to be practically better than
+our baseline -- the simplest strategy of all -- the random selection
+strategy. This suggests that at least from the perspective of a software
+tester wishing to use mutation analysis as an evaluation criteria to judge
+when or which tests to add, random sampling is the easiest way to reduce
+the computational requirements of mutation analysis. This assumes even more
+importance when we consider that the adequate random sample of mutants
+increases at a rate less than $O(n^\frac{1}{4})$ when the program size
+increases linearly~\cite{zhang2014empirical}.

### 2015-01-20 src/analysis.Rnw
more explantion of minimal test suite required

@@
 
-Say the original set of mutants is given my $M$, then the reduced set of
-mutants is given by $M_{strategy}$. The strategy choses $|M_{strategy}|$
-mutants on its application. Test suite composed of test cases that
-are able to kill any of the mutants of $M_{strategy}$ is given by
-$T_{strategy}$. The total number of asserts on tests under $T_{strategy}$
+Suppose $M$ and $M_{strategy}$ denote the original set of mutants and  the reduced set of
+mutants, respectively. 
+% The strategy chooses $|M_{strategy}|$ mutants on its application. 
+Test suite composed of test cases that 
+are able to kill an $m$ where  $ m \in M_{strategy}$ is given by
+$T_{strategy}$. The total number of \texttt{assert}s in $T_{strategy}$
 is given by $asserts(T_{strategy})$. We find a minimal test suite that
-is capable of killing all mutants under $M_{strategy}$ by a greedy strategy
+is capable of killing all mutants under $M_{strategy}$ by a greedy algorithm
 of iteratively choosing the test cases with the largest amount of kills
 for remaining mutants, and is given by $min(T_{strategy})$. Similarly,
-for baseline, we use a strategy of randomly choosing the mutants from the
-original set with number of mutants chosen same as the corresponding
-number of mutants that the strategy under consideration chose.
-That is, $|M_{strategy}| = |M_{random}|$. Given any set of tests $T$,
+for baseline, we build set of randomly selected mutants $M_{random}$,
+such that  $|M_{random}| = |M_{strategy}|$. Given any set of tests $T$,
 the total number of mutants that can be killed by the test cases in $T$
@@
 
-The \textit{test utility} is computed as the difference between the number
+The \textit{test utility} approximates the extra tests a selection strategy 
+requires comparing a random sampling that suggest the same number of mutants.
+We  compute it as the difference between the number
 of non-redundant test cases the mutant selection achieved and the number of
@@
 \[\left(\frac{|min(T_{strategy})|}{|min(T_{random})|}-1\right)\times 100.0\]
+
+Positive value test utility denotes that the strategy requires more tests
+and negative test utility denotes that the strategy needs less test cases.
+Values close to zero basically denote that the strategy rouphly suggest the 
+same number of tests. Note that the comparison here is betweeen the size of
+tests and it does not imply any subset relationship between test suites.
 
@@
 baseline, that is 
-\[T.test\left(T_{strategy}\sim{}T_{random}\right)\]
+\[T.test\left(|T_{strategy}|\sim{}|T_{random}|\right)\]
 

### 2015-01-20 src/discussion.Rnw

@@
 
-\subsubsection{Operator Selection}
+\subsection{Operator Selection}
 From Table~\ref{tbl:selective}, looking at the test and assert utility, we
@@
 
-\subsubsection{Stratified sampling over operators}
+\subsection{Stratified sampling over operators}
 For stratified sampling over operators in Table~\ref{tbl:opsample}, the best
@@
 
-\subsubsection{Stratified sampling over program elements}
+\subsection{Stratified sampling over program elements}
 For stratified sampling over program elements in Table~\ref{tbl:element},

### 2015-01-20 src/analysis.Rnw
cleanup after amin

@@
 For the purpose of comparing different mutation reduction strategies, we
-computed the average \textit{test utility}, and \textit{assert utility} of
-different strategies.
+computed the average \textit{test utility}, and \textit{assert utility}
+of different strategies.
 
-We use the mutant reduction strategy to select a subset
-of mutants from the original set. We then collect all test cases that were
-able to kill any of the selected set of mutants. Next we compute the
-non-redundant test cases by discarding any test case that can be removed
-without letting any of the mutants escape. This is repeated and averaged
-over multiple runs, and the average number of non-redundant test cases are
-found.
+We use the mutant reduction strategy to select a subset of mutants from the
+original set. We then collect all test cases that were able to kill any of
+the selected set of mutants. Next we compute the non-redundant test cases
+by discarding any test case that can be removed without letting any of the
+mutants escape. This is repeated and averaged over multiple runs, and the
+average number of non-redundant test cases are found.
 
@@
 
-Suppose $M$ and $M_{strategy}$ denote the original set of mutants and  the reduced set of
-mutants, respectively. 
-% The strategy chooses $|M_{strategy}|$ mutants on its application. 
-Test suite composed of test cases that 
-are able to kill an $m$ where  $ m \in M_{strategy}$ is given by
-$T_{strategy}$. The total number of \texttt{assert}s in $T_{strategy}$
-is given by $asserts(T_{strategy})$. We find a minimal test suite that
-is capable of killing all mutants under $M_{strategy}$ by a greedy algorithm
+Let $M$ and $M_{strategy}$ denote the original set of mutants and the
+reduced set of mutants respectively. Test suite composed of test cases
+that are able to kill an $m$ where  $ m \in M_{strategy}$ is given by
+$T_{strategy}$, and the total number of \texttt{assert}s in $T_{strategy}$
+is given by $asserts(T_{strategy})$. We find a minimal test suite that is
+capable of killing all mutants under $M_{strategy}$ by a greedy algorithm
 of iteratively choosing the test cases with the largest amount of kills
-for remaining mutants, and is given by $min(T_{strategy})$. Similarly,
-for baseline, we build set of randomly selected mutants $M_{random}$,
-such that  $|M_{random}| = |M_{strategy}|$. Given any set of tests $T$,
-the total number of mutants that can be killed by the test cases in $T$
-is given by $k(T)$, and those mutants that are covered by the test cases
-are given by $c(T)$.
+for remaining mutants, and is given by $min(T_{strategy})$. Similarly, for
+baseline, we build a set of randomly selected mutants $M_{random}$, such that
+$|M_{random}| = |M_{strategy}|$. Given any set of tests $T$, the total number
+of mutants that can be killed by the test cases in $T$ is given by $k(T)$,
+and those mutants that are covered by the test cases are given by $c(T)$.
 
@@
 requires comparing a random sampling that suggest the same number of mutants.
-We  compute it as the difference between the number
-of non-redundant test cases the mutant selection achieved and the number of
-non-redundant test cases of a random sample of same number of mutants. 
-The result is reported as a percentage of the non-redundant tests of the random
-sample which is taken as the baseline. That is, test utility is given by
+We  compute it as the difference between the number of non-redundant test
+cases the mutant selection achieved and the number of non-redundant test
+cases of a random sample of same number of mutants.  The result is reported
+as a percentage of the non-redundant tests of the random sample which is
+taken as the baseline. That is, test utility is given by
 \[\left(\frac{|min(T_{strategy})|}{|min(T_{random})|}-1\right)\times 100.0\]
@@
 Positive value test utility denotes that the strategy requires more tests
-and negative test utility denotes that the strategy needs less test cases.
-Values close to zero basically denote that the strategy rouphly suggest the 
-same number of tests. Note that the comparison here is betweeen the size of
-tests and it does not imply any subset relationship between test suites.
+than random selection, and negative test utility denotes that the strategy
+needs less test cases than random.  Values close to zero basically denote
+that the strategy roughly suggest the same number of tests. Note that the
+comparison here is between the size of tests and it does not imply any subset
+relationship between test suites.
 
@@
 selection achieved and the number of assertions the test cases for random
-sample of same number of mutants. As before, it is reported as a percentage of
-the asserts of the non-redundant tests of the random sample which is taken
-as the baseline. It is given by
+sample of same number of mutants. As before, it is reported as a percentage
+of the asserts of the non-redundant tests of the random sample which is
+taken as the baseline. It is given by
 \[\left(\frac{|asserts(min(T_{strategy}))|}{|asserts(min(T_{random}))|}-1\right)\times 100.0\]
@@
 
-\textit{Strategy effectiveness} is computed by collecting all the test cases
-that detected any of the mutants in the selected subset, and applying these
-test cases to the complete set of mutants. The mutation score thus obtained
-is then divided by the original number of detected mutants.
-This is reported as difference from the corresponding baseline effectiveness,
-given by 
+\textit{Strategy effectiveness}~\footnote{Also called mutation score by Mresa
+et al.~\cite{mresa1999efficiency}} is computed by collecting all the test
+cases that detected any of the mutants in the selected subset, and applying
+these test cases to the complete set of mutants. The mutation score thus
+obtained is then divided by the original number of detected mutants.  This is
+reported as difference from the corresponding baseline effectiveness, given by
 \[\frac{|k(T_{strategy})| - |k(T_{random})|}{|k(M)|}\times100.0\]

### 2015-01-20 support/init.sh
udpate

@@ -1,3 +1,4 @@
 export TERM=vt100
 export PATH=/scratch/usr/bin:$PATH
 export R_ENVIRON=/scratch/usr/home/.Renviron
+/bin/bash

### 2015-01-20 src/discussion.Rnw
merging result and discussion

@@
-\section{Discussion}
-\label{sec:discussion}
+\section{Results}
+\label{sec:results}
 
-We will analyze each of the different types of mutation reduction strategies in
-detail, and summarize the broad patterns we see at the end.
+This section present the result of our experimenting different
+mutation selection techniques described in Section \ref{sec:methodology}. 
+Each experiment has been done multiple times (at least ten times).
+We will analyze each of the different types of mutation reduction 
+strategies in detail, and summarize the broad patterns we see at 
+the end.
 
 \subsection{Operator Selection}
-From Table~\ref{tbl:selective}, looking at the test and assert utility, we
-see that there are a few selective strategies that seem to score a positive
-test utility. Notably, the statement modification strategy sselective does
-about 1.86\% better than the random selection for test utility, and has
-similar advantage in assert utility. It also seem to have a slight advantage
+From Table~\ref{tbl:selective}, looking at the test and assert 
+utility, we see that there are a few selective strategies that 
+seem to score a positive test utility. Notably, the statement 
+modification strategy sselective does about 1.86\% better than 
+the random selection for test utility, and has similar advantage 
+in assert utility. It also seem to have a slight advantage
 of 0.27\% in the strategy effectivenss.
 
-The statistical analysis in Table~\ref{tbl:ttests} also suggests a positive
-mean and a $p-value < 0.01$ for this result.
+The statistical analysis in Table~\ref{tbl:ttests} also 
+suggests a positive mean and a $p-value < 0.01$ for this result.
 
-For N-selection, which is given in Table~\ref{tbl:nselection}, The best
-utility was on removal of \Pitnvmc, \Pitrv, \Pitic, \Pitdc, and \Pitnc which
-resulted in a test utility advantage of 2.67\%. It also have the best positive
-strategy effectiveness of 0.29\%. However, the difference was not significant
-using t-tests in Table~\ref{tbl:ttests} $p-value > 0.01$.~\footnote{The
-difference between Table~\ref{tbl:nselection} and Table~\ref{tbl:ttests}
-is due to test or mutant number being zero for baseline, and hence remvoed
-for computing percentage}.
+For N-selection, which is given in Table~\ref{tbl:nselection}, 
+The best utility was on removal of \Pitnvmc, \Pitrv, \Pitic, 
+\Pitdc, and \Pitnc which resulted in a test utility advantage 
+of 2.67\%. It also have the best positive
+strategy effectiveness of 0.29\%. However, the difference was 
+not significant using t-tests in Table~\ref{tbl:ttests} 
+$p-value > 0.01$.~\footnote{The difference between Table
+~\ref{tbl:nselection} and Table~\ref{tbl:ttests}
+is due to test or mutant number being zero for baseline, 
+and hence remvoed for computing percentage}.
 
-Using single operators, we get a better result of 7.77\% for \Pitrv, which
-is also significant at $p-value < 0.01$.
+Using single operators, we get a better result of 
+7.77\% for \Pitrv, which is also significant at $p-value < 0.01$.
 
 \subsection{Stratified sampling over operators}
-For stratified sampling over operators in Table~\ref{tbl:opsample}, the best
-result appears to be at $\frac{1}{8}$, which gives an advantage of 1.64\% over
-baseline. However, we note that the strategy effectiveness is negative. For
-t-test, since this is a continuum, we only inspected if the strategy as a
-whole (not particular fractions) hold any advantage. The t-test suggests that
-there is no significant difference from the baseline for this kind of sampling.
+For stratified sampling over operators in Table~\ref{tbl:opsample}, 
+the best result appears to be at $\frac{1}{8}$, which gives an 
+advantage of 1.64\% over baseline. However, we note that the strategy effectiveness is negative. For t-test, since this is a continuum,
+ we only inspected if the strategy as a whole (not particular 
+fractions) hold any advantage. The t-test suggests that
+there is no significant difference from the baseline for this 
+kind of sampling.
 

### 2015-01-20 src/introduction.Rnw
merging result and discussion

@@
 selection strategies we study in detail. The analysis is given in
-Section~\ref{sec:analysis}, and the results of our experiment are given in
-Section~\ref{sec:results}, followed by detailed discussion of what these
-results imply in Section ~\ref{sec:discussion}.
+Section~\ref{sec:analysis}, and the results of our experiment are detailed in
+Section~\ref{sec:results}. Section ~\ref{sec:conclusion} concludes the paper.

### 2015-01-20 src/paper.Rnw
merging result and discussion

@@
 @
-<<results, child='results.Rnw'>>=
+%<<results, child='results.Rnw'>>=
 @

### 2015-01-20 src/results.Rnw
update tables
fix formating, and cleanup amin's edits

@@
 
-The results for operator selection criteria are given in Table~\ref{tbl:selective}.
-Those of N-Selection are given in Table~\ref{tbl:nselection}.
-The fractional sampling per operator is provided in Table~\ref{tbl:opsample}, and that of element scoped sampling is provided in Table~\ref{tbl:element}.
-Finally, operation selection using just single operators are given in Table~\ref{tbl:singles}.
+This section presents the result of our experimenting different mutation
+selection techniques described in Section \ref{sec:methodology}.  Each
+experiment has been done multiple times (at least ten times).  We will
+analyze each of the different types of mutation reduction strategies in
+detail, and summarize the broad patterns we see at the end.
 
-Our data is available for replication~\cite{ourdata}.
+\subsection{Operator Selection}
+From Table~\ref{tbl:selective}, looking at the test and assert utility, we
+see that there are a few selective strategies that seem to score a positive
+test utility. Notably, the statement modification strategy sselective does
+about 1.86\% better than the random selection for test utility, and has
+similar advantage in assert utility. It also seem to have a slight advantage
+of 0.27\% in the strategy effectivenss.
+
+The statistical analysis in Table~\ref{tbl:ttests} also suggests a positive
+mean and a $p-value < 0.01$ for this result.
+
+For N-selection, which is given in Table~\ref{tbl:nselection}, The best
+utility was on removal of \Pitnvmc, \Pitrv, \Pitic, \Pitdc, and \Pitnc which
+resulted in a test utility advantage of 2.67\%. It also have the best positive
+strategy effectiveness of 0.29\%. However, the difference was not significant
+using t-tests in Table~\ref{tbl:ttests} $p-value > 0.01$.~\footnote{The
+difference between Table ~\ref{tbl:nselection} and Table~\ref{tbl:ttests}
+is due to test or mutant number being zero for baseline, and hence remvoed
+for computing percentage}.
+
+Using single operators, we get a better result of 7.77\% for \Pitrv, which
+is also significant at $p-value < 0.01$.
+
+\subsection{Stratified sampling over operators}
+For stratified sampling over operators in Table~\ref{tbl:opsample}, the best
+result appears to be at $\frac{1}{8}$, which gives an advantage of 1.64\% over
+baseline. However, we note that the strategy effectiveness is negative. For
+t-test, since this is a continuum, we only inspected if the strategy as a
+whole (not particular fractions) hold any advantage. The t-test suggests that
+there is no significant difference from the baseline for this kind of sampling.
+
+\subsection{Stratified sampling over program elements}
+For stratified sampling over program elements in Table~\ref{tbl:element},
+there appears a small consistent advantage for most sample fractions. The best
+utility achieved was 3.85\% for class based $\frac{1}{16}$ sample. As before,
+as this is a continuum, we only checked whether this kind of sampling has any
+significant advantage as a whole with t-test. The t-test suggests that all
+sampling over elements have a small but consistent advantage $p-value < 0.01$
+
+A general pattern that we can glean from this analysis is that none of
+the mutation reduction strategies appear to be practically better than
+our baseline -- the simplest strategy of all -- the random selection
+strategy. This suggests that at least from the perspective of a software
+tester wishing to use mutation analysis as an evaluation criteria to judge
+when or which tests to add, random sampling is the easiest way to reduce
+the computational requirements of mutation analysis. This assumes even more
+importance when we consider that the adequate random sample of mutants
+increases at a rate less than $O(n^\frac{1}{4})$ when the program size
+increases linearly~\cite{zhang2014empirical}.

### 2015-01-20 etc/abstract.tex
update

@@
 Mutation analysis is a well-known method for measuring the quality of
-test suites. However, it is computationally intensive compared to
-other measures, which makes it hard to use in practice. Multiple
-strategies has been proposed to reduce the number of mutants produced,
-and hence reduce the computational requirements.
+test suites. However, it is computationally intensive compared to other
+measures, which makes it hard to use in practice. Multiple strategies have
+been proposed to reduce the number of mutants produced, and hence reduce
+the computational requirements.
 
@@
 problems. There is inconclusive evidence supporting many of the suggested
-reduction strategies due to the limited number and size of of subject
-programs investigated. The lack of a comprehensive study comparing
-at-least the major approaches is another problem. Finally the traditional
-evaluation criteria for mutation reduction approaches relies on
-mutation-adequate test suites which rarely occur in real world. There is
-little evidence that the strategies that perform well using the traditional
-evaluation crtiera leads to better mutation selection for non-adequate
-tests in the real world.
+reduction strategies due to the limited number and size of subject programs
+investigated. The lack of a comprehensive study comparing even major approaches
+is another problem. Finally the traditional evaluation criteria for mutation
+reduction approaches relies on mutation-adequate test suites which rarely occur
+in real world. There is little evidence that the strategies that perform well
+using the traditional evaluation crtiera leads to better mutation selection
+for non-adequate tests in the real world.
 
@@
 
-We extend the traditional reduction crtieria so that it is usable with
-non-mutation adequate test suites, and link it to the actual use of
-mutation analysis during development -- to produce tests that check for
-as many different bugs as possible.
+We propose a noval evaluation criteria of reduction strategies that is
+usable with non-mutation adequate test suites, and link it to the actual
+use of mutation analysis during development -- to produce tests that check
+for as many different bugs as possible.
 
-We evaluate the performance of various selection criteria on 312 opensource
+We evaluate the performance of various selection strategies on 312 opensource
 projects from github, which shows that the popular reduction strategies:
-operator selection, operator based sampling, and element based sampling
-are hardly better than random selection, and often performs worse.
-This suggests a need for further research on better methods of mutation
-reduction strategies.
-
-% Our results can be used to choose an appropriate mutation
-% reduction technique by the reduction and level of fidelity to full
-% mutation results required.
-
-%according to the mutation reduction ratio desired, and
-%how much reduction in accuracy is acceptable.
+operator selection, stratified sampling of mutations based on operators,
+and stratified sampling of mutations based on program elements are hardly
+better than random sampling, and often performs worse.  This suggests a need
+for further research on better methods of mutation reduction strategies.
 
 %4.Saywhatfollowsfromyoursolution
-
-% We find that all sampling approaches perform better than operator
-% selection methods, when considering ability to predict the full
-% mutation score as well as the consistency of mutation reduction ratios
-% achieved.
-
-%and also the consistency of mutation reduction ratios achieved.  Specifically,
-%we find that random selection of a mutant performs better than statement
-%deletion operator selection criteria.
 

### 2015-01-20 src/conclusion.Rnw
conclusion

@@
 This suggests that that none of the well known reduction strategies are
-actually able to consistenly select useful mutants, and the best path forward
+actually able to consistently select useful mutants, and the best path forward
 for a working tester is to rely on the simplest scheme of all -- the random
@@
 be smaller or involve less easily distinguished test suites.
+% TODO: Should we add this.
+%\begin{comment}
+
+There is also an inherent danger to using only a small sample of same academic
+subjects over and over again. We may tend to see patterns that are specific
+to the subjects, which are not present in the wider population. The
+non-performance of the popular strategies against a wider dataset such as
+ours may also be seen as a possible symptom of this over-fitting.
+%\end{comment}

### 2015-01-21 support/init.sh
remove redundant files

@@ -1,4 +1,0 @@
-export TERM=vt100
-export PATH=/scratch/usr/bin:$PATH
-export R_ENVIRON=/scratch/usr/home/.Renviron
-/bin/bash

### 2015-01-21 _tmp/oldabstract.tex
Remove redundant files

Software Engineering relies on the existence of good test-suites to ensure quality of produced artifacts, and various coverage criteria are used to measure how well a test suite performs.
These criteria include statement coverage, branch coverage, and path coverage.

Another approach to judging test suite quality is to generate mutant versions of the program, and measure the effectiveness of test suite in distinguishing these mutants.
This method is called mutation analysis.

It is often assumed that since path coverage subsumes branch coverage, and branch coverage subsumes statement coverage in adequate test suites, the same relationship holds for their efficacy in finding defects.
Previous research suggests that mutation score of a test suite has a high correlation with quality of a test suite.
However, as mutation analysis is a computationally intensive task, various alternatives to it have been explored in the past.
A few studies have suggested branch coverage as an approximation to mutation coverage.
However, the applicability of these studies have been some what limited due to the handful of sample programs that these studies were based on.

We analyze the data from a much larger number of real world projects, and find that statement coverage is the best predictor for quality of test suite.
We further cross validate our result by comparing it with test suite generated randomly, which agrees our findings.
Finally, we suggest a hypothesis as to why this result is not surpricing given the nature of coverage techniques.
We also note a surpricing observation that line coverage approximates path coverage better than branch coverage.

### 2015-01-21 etc/abstract.tex
spellos

@@
 in real world. There is little evidence that the strategies that perform well
-using the traditional evaluation crtiera leads to better mutation selection
+using the traditional evaluation criteria leads to better mutation selection
 for non-adequate tests in the real world.
@@
 
-We propose a noval evaluation criteria of reduction strategies that is
+We propose a novel evaluation criteria of reduction strategies that is
 usable with non-mutation adequate test suites, and link it to the actual
@@
 We evaluate the performance of various selection strategies on 312 opensource
-projects from github, which shows that the popular reduction strategies:
+projects from Github, which shows that the popular reduction strategies:
 operator selection, stratified sampling of mutations based on operators,
